### 2021-05-06 manuscript/article.Rmd
add files

---
title: Evolution, functional diversity, regime shifts, hysteresis, and nonlinearity; ecosystem responses to environmental change.
subtitle: Predictions of a model of an oxic-anoxic microbial ecosystem 
authors:
  - name: Owen L Petchey
    department: Department of Evolutionary Biology and Environmental Studies
    affiliation: University of Zurich
    location: Zurich 8057, Switzerland
    email: owen.petchey@ieu.uzh.ch
  - name: Rainer Krug
    department: Department of Evolutionary Biology and Environmental Studies
    affiliation: University of Zurich
    location: Zurich 8057, Switzerland
    email: rainer.krug@ieu.uzh.ch
  - name: Marcel Suleiman
    department: Department of Evolutionary Biology and Environmental Studies
    affiliation: University of Zurich
    location: Zurich 8057, Switzerland
    email: marcel.suleiman@ieu.uzh.ch

abstract: |
  To be completed
keywords:
  - Biodiversity
  - Evolution
  - Hysteresis
  - Alternate stable states
  - Environmental change
  - Regime shift
  - Threshold
  - Ecosystem
  - Cyanobacteria
  - Sulphur bacteria
bibliography: references.bib
biblio-style: unsrt
output: 
  rticles::arxiv_article:
    keep_tex: true
---

```{r}
library(tidyverse)
library(microxanox)
library(patchwork)
library(here)
source(here("simulations/r functions/various_useful_functions.r"))
```

# Introduction

Types of ecosystem responses to environmental change. What and why. Importance of non-linearity and hysteresis. Feedbacks, diversity / evolution. Includes graphical hypotheses. What is the relative importance of feedbacks (composition) and diversity / evolution.

Ceulemans, R., Wojcik, L.A. & Gaedke, U. (2021). Functional diversity alters the effects of a pulse perturbation on the dynamics of tritrophic food webs. *bioRxiv*, 2021.03.22.436420.

[@dakos2019]

Anoxic-oxic ecosystem shifts as a case study. Contemporary relevance. Intermediate complexity of system... diagram of system, including some panels of subsystems showing some of the positive feedbacks. Central role of inhibition / tolerance. Also showing responses to changes in oxygen diffusivity (justify from Bush et al this as a key environmental driver).

Empirical evidence of variation in organismal tolerance. Across species and evolution experiments. [@schoeffler2019]

Recent experimental evolution studies have demonstrated considerable increases in tolerance. For example, the sulphur bacteria *Desulfovibrio vulgaris* evolved a 32-fold increase in oxygen tolerance [@schoeffler2019] . Furthermore, the evolved strains were capable of oxygen respiration that permits growth. Genome re-sequencing revealed that few mutations were involved. Additionally, the cyanobacterium *Microcystis aeruginosa* evolved a four-fold higher sulphide tolerance via rare spontaneous mutations [@martínclemente2019]. In that study, populations with higher genetic variation and those experiencing slower environmental change (an increase in sulphide concentration) were more likely to persist at high sulphide concentration.

[@rolfe1978] - Factors related to the oxygen tolerance of anaerobic bacteria. [@ramel2015] - "they were able to grow but the final biomasses and the growth yield were lower than that obtained under anaerobic conditions", "Determination of the molar growth yields on lactate suggested that a part of the energy gained from lactate oxidation was derived toward cells protection/repairing against oxidative conditions rather than biosynthesis" [@hamilton2018] - "Cyanobacterial photosynthesis under sulfidic conditions: insights from the isolate Leptolyngbya sp. strain hensonii"

Physiological tolerances to environmental conditions, including interspecific variation in tolerance and evolution of tolerance, are a key component of the engineering of ecosystem for determining their stability (Minervini *et al.* 2014)(Gómez‐Gras *et al.* 2019)(Cuenca Cambronero *et al.* 2018)(Vos *et al.* 2017)(Evans & Wallenstein 2014)(Rolfe *et al.* 1978)(Knoll & Bauld 1989)(Girvan *et al.* 2005).

Questions: - How does variation organismal tolerances affect response

Approach: - Modelling the system with ODEs. - Diversity manipulation (can be considered selection among strains, or selection among species). - Do not include mutation.

# Methods

## The model

Bush et al (2017) contains an excellent description of the model of the ecosystem. Here we only describe the extensions needed for modelling multiple strains/taxa per functional group.

## Measurement of non-linearity and hysteresis

Take from Garnier et al.

Rate-independent hysteresis, because we are considering only stable states, and not rate-dependent hysteresis, which can occur when a lag in the system response to an environmental response causes a difference between the observed system state at time $t$ and the stable state for the environmental conditions present at time $t$.

## Implementation

R package.

# Results

## Figure: Stable states with and without variation.

```{r ss_novar, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
ss_sim_data <- readRDS(here("simulations/sim data/ss_res_2.RDS"))
ss_novar <- ss_sim_data[22,]
p1  <- plot_ss_result1(ss_novar$ss_res[[1]],
                ss_novar$CB_var_gmax_s,
                ss_novar$CB_var_h_s,
                ss_novar$SB_var_gmax_s,
                ss_novar$SB_var_h_s,
                ss_novar$PB_var_gmax_s,
                ss_novar$PB_var_h_s,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1

```

`
```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
#ss_sim_data <- readRDS("working/sim data/ss_res_2.RDS")
ss_var <- ss_sim_data[43,]
p2  <- plot_ss_result1(ss_var$ss_res[[1]],
                ss_var$CB_var_gmax_s,
                ss_var$CB_var_h_s,
                ss_var$SB_var_gmax_s,
                ss_var$SB_var_h_s,
                ss_var$PB_var_gmax_s,
                ss_var$PB_var_h_s,
                filename_prefix = NULL,
                save_image_file = FALSE)
p2

```

## Figure: hysteresis, shift point, nonlinearity, as var increases.

```{r}
ss_sim_data <- readRDS(here("simulations/sim data/ss_res_3.RDS"))

ss_sim_data <- ss_sim_data %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
results <- unnest(ss_sim_data, cols = c(stability_measures))

results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = CB_var_gmax_s, y = hyst_range)) +
  geom_point()

```

## Figure: Temporal switches

To be added. Need to go both ways (oxic to anoxic, and anoxic to oxic).

# Discussion

<https://onlinelibrary.wiley.com/doi/10.1111/gcb.15662?af=R>

# Acknowledgements

SNF
URPP

### 2021-05-06 manuscript/article.tex
add files

\documentclass{article}

\usepackage{arxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{lmodern}        % https://github.com/rstudio/rticles/issues/343
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}
\usepackage{graphicx}

\title{Evolution, functional diversity, regime shifts, hysteresis, and
nonlinearity; ecosystem responses to environmental change.}

\author{
    Owen L Petchey
   \\
    Department of Evolutionary Biology and Environmental Studies \\
    University of Zurich \\
  Zurich 8057, Switzerland \\
  \texttt{\href{mailto:owen.petchey@ieu.uzh.ch}{\nolinkurl{owen.petchey@ieu.uzh.ch}}} \\
   \And
    Rainer Krug
   \\
    Department of Evolutionary Biology and Environmental Studies \\
    University of Zurich \\
  Zurich 8057, Switzerland \\
  \texttt{\href{mailto:rainer.krug@ieu.uzh.ch}{\nolinkurl{rainer.krug@ieu.uzh.ch}}} \\
   \And
    Marcel Suleiman
   \\
    Department of Evolutionary Biology and Environmental Studies \\
    University of Zurich \\
  Zurich 8057, Switzerland \\
  \texttt{\href{mailto:marcel.suleiman@ieu.uzh.ch}{\nolinkurl{marcel.suleiman@ieu.uzh.ch}}} \\
  }

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}

% Pandoc citation processing
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for calculating minipage widths
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}
\maketitle

\def\tightlist{}

\begin{abstract}
To be completed
\end{abstract}

\keywords{
    Biodiversity
   \and
    Evolution
   \and
    Hysteresis
   \and
    Alternate stable states
   \and
    Environmental change
   \and
    Regime shift
   \and
    Threshold
   \and
    Ecosystem
   \and
    Cyanobacteria
   \and
    Sulphur bacteria
  }

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(tidyverse)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## -- Attaching packages --------------------------------------- tidyverse 1.3.0 --
\end{verbatim}

\begin{verbatim}
## v ggplot2 3.3.3     v purrr   0.3.4
## v tibble  3.1.0     v dplyr   1.0.5
## v tidyr   1.1.2     v stringr 1.4.0
## v readr   1.4.0     v forcats 0.5.0
\end{verbatim}

\begin{verbatim}
## -- Conflicts ------------------------------------------ tidyverse_conflicts() --
## x dplyr::filter() masks stats::filter()
## x dplyr::lag()    masks stats::lag()
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(microxanox)}
\FunctionTok{library}\NormalTok{(patchwork)}
\FunctionTok{library}\NormalTok{(here)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## here() starts at /Users/owenpetchey/Desktop/microxanox/diversity_envresp1
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{source}\NormalTok{(}\FunctionTok{here}\NormalTok{(}\StringTok{"simulations/r functions/various\_useful\_functions.r"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Types of ecosystem responses to environmental change. What and why.
Importance of non-linearity and hysteresis. Feedbacks, diversity /
evolution. Includes graphical hypotheses. What is the relative
importance of feedbacks (composition) and diversity / evolution.

Ceulemans, R., Wojcik, L.A. \& Gaedke, U. (2021). Functional diversity
alters the effects of a pulse perturbation on the dynamics of tritrophic
food webs. \emph{bioRxiv}, 2021.03.22.436420.

(Dakos et al. 2019)

Anoxic-oxic ecosystem shifts as a case study. Contemporary relevance.
Intermediate complexity of system\ldots{} diagram of system, including
some panels of subsystems showing some of the positive feedbacks.
Central role of inhibition / tolerance. Also showing responses to
changes in oxygen diffusivity (justify from Bush et al this as a key
environmental driver).

Empirical evidence of variation in organismal tolerance. Across species
and evolution experiments. (Schoeffler et al. 2019)

Recent experimental evolution studies have demonstrated considerable
increases in tolerance. For example, the sulphur bacteria
\emph{Desulfovibrio vulgaris} evolved a 32-fold increase in oxygen
tolerance (Schoeffler et al. 2019) . Furthermore, the evolved strains
were capable of oxygen respiration that permits growth. Genome
re-sequencing revealed that few mutations were involved. Additionally,
the cyanobacterium \emph{Microcystis aeruginosa} evolved a four-fold
higher sulphide tolerance via rare spontaneous mutations
(Martín-Clemente et al. 2019). In that study, populations with higher
genetic variation and those experiencing slower environmental change (an
increase in sulphide concentration) were more likely to persist at high
sulphide concentration.

(Rolfe et al. 1978) - Factors related to the oxygen tolerance of
anaerobic bacteria. (Ramel et al. 2015) - ``they were able to grow but
the final biomasses and the growth yield were lower than that obtained
under anaerobic conditions,'' ``Determination of the molar growth yields
on lactate suggested that a part of the energy gained from lactate
oxidation was derived toward cells protection/repairing against
oxidative conditions rather than biosynthesis'' (Hamilton et al. 2018) -
``Cyanobacterial photosynthesis under sulfidic conditions: insights from
the isolate Leptolyngbya sp. strain hensonii''

Physiological tolerances to environmental conditions, including
interspecific variation in tolerance and evolution of tolerance, are a
key component of the engineering of ecosystem for determining their
stability (Minervini \emph{et al.} 2014)(Gómez‐Gras \emph{et al.}
2019)(Cuenca Cambronero \emph{et al.} 2018)(Vos \emph{et al.}
2017)(Evans \& Wallenstein 2014)(Rolfe \emph{et al.} 1978)(Knoll \&
Bauld 1989)(Girvan \emph{et al.} 2005).

Questions: - How does variation organismal tolerances affect response

Approach: - Modelling the system with ODEs. - Diversity manipulation
(can be considered selection among strains, or selection among species).
- Do not include mutation.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{the-model}{%
\subsection{The model}\label{the-model}}

Bush et al (2017) contains an excellent description of the model of the
ecosystem. Here we only describe the extensions needed for modelling
multiple strains/taxa per functional group.

\hypertarget{measurement-of-non-linearity-and-hysteresis}{%
\subsection{Measurement of non-linearity and
hysteresis}\label{measurement-of-non-linearity-and-hysteresis}}

Take from Garnier et al.

Rate-independent hysteresis, because we are considering only stable
states, and not rate-dependent hysteresis, which can occur when a lag in
the system response to an environmental response causes a difference
between the observed system state at time \(t\) and the stable state for
the environmental conditions present at time \(t\).

\hypertarget{implementation}{%
\subsection{Implementation}\label{implementation}}

R package.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{figure-stable-states-with-and-without-variation.}{%
\subsection{Figure: Stable states with and without
variation.}\label{figure-stable-states-with-and-without-variation.}}

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/ss_novar-1}

}

\caption{your caption}\label{fig:ss_novar}
\end{figure}

`

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/ss_var-1}

}

\caption{your caption}\label{fig:ss_var}
\end{figure}

\hypertarget{figure-hysteresis-shift-point-nonlinearity-as-var-increases.}{%
\subsection{Figure: hysteresis, shift point, nonlinearity, as var
increases.}\label{figure-hysteresis-shift-point-nonlinearity-as-var-increases.}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{ss\_sim\_data }\OtherTok{\textless{}{-}} \FunctionTok{readRDS}\NormalTok{(}\FunctionTok{here}\NormalTok{(}\StringTok{"simulations/sim data/ss\_res\_3.RDS"}\NormalTok{))}

\NormalTok{ss\_sim\_data }\OtherTok{\textless{}{-}}\NormalTok{ ss\_sim\_data }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{group\_by}\NormalTok{(CB\_var\_gmax\_s, CB\_var\_h\_s,}
\NormalTok{           SB\_var\_gmax\_s, SB\_var\_h\_s,}
\NormalTok{           PB\_var\_gmax\_s, PB\_var\_h\_s) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{do}\NormalTok{(}\AttributeTok{stability\_measures =} \FunctionTok{get\_stability\_measures}\NormalTok{(.}\SpecialCharTok{$}\NormalTok{ss\_res[[}\DecValTok{1}\NormalTok{]]))}
\NormalTok{results }\OtherTok{\textless{}{-}} \FunctionTok{unnest}\NormalTok{(ss\_sim\_data, }\AttributeTok{cols =} \FunctionTok{c}\NormalTok{(stability\_measures))}

\NormalTok{results }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{filter}\NormalTok{(Species }\SpecialCharTok{==} \StringTok{"O"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ CB\_var\_gmax\_s, }\AttributeTok{y =}\NormalTok{ hyst\_range)) }\SpecialCharTok{+}
  \FunctionTok{geom\_point}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\includegraphics{article_files/figure-latex/unnamed-chunk-2-1.pdf}

\hypertarget{figure-temporal-switches}{%
\subsection{Figure: Temporal switches}\label{figure-temporal-switches}}

To be added. Need to go both ways (oxic to anoxic, and anoxic to oxic).

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\url{https://onlinelibrary.wiley.com/doi/10.1111/gcb.15662?af=R}

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

SNF URPP

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-dakos2019}{}%
Dakos, Vasilis, Blake Matthews, Andrew P. Hendry, Jonathan Levine,
Nicolas Loeuille, Jon Norberg, Patrik Nosil, Marten Scheffer, and Luc De
Meester. 2019. {``Ecosystem Tipping Points in an Evolving World.''}
\emph{Nature Ecology \& Evolution} 3 (3): 355--62.
\url{https://doi.org/10.1038/s41559-019-0797-2}.

\leavevmode\hypertarget{ref-hamilton2018}{}%
Hamilton, Trinity L., Judith M. Klatt, Dirk de Beer, and Jennifer L.
Macalady. 2018. {``Cyanobacterial Photosynthesis Under Sulfidic
Conditions: Insights from the Isolate Leptolyngbya Sp. Strain
Hensonii.''} \emph{The ISME Journal} 12 (2): 568--84.
\url{https://doi.org/10.1038/ismej.2017.193}.

\leavevmode\hypertarget{ref-martuxednclemente2019}{}%
Martín-Clemente, Elena, Ignacio J. Melero-Jiménez, Elena Bañares-España,
Antonio Flores-Moya, and María J. García-Sánchez. 2019. {``Adaptation
Dynamics and Evolutionary Rescue Under Sulfide Selection in
Cyanobacteria: A Comparative Study Between {\emph{Microcystis
Aeruginosa}} and {\emph{Oscillatoria}} Sp. (Cyanobacteria).''}
\emph{Journal of Phycology} 55 (6): 1348--60.
\url{https://doi.org/10.1111/jpy.12911}.

\leavevmode\hypertarget{ref-ramel2015}{}%
Ramel, Fanny, Gael Brasseur, Laetitia Pieulle, Odile Valette, Agnès
Hirschler-Réa, Marie Laure Fardeau, and Alain Dolla. 2015. {``Growth of
the Obligate Anaerobe Desulfovibrio Vulgaris Hildenborough Under
Continuous Low Oxygen Concentration Sparging: Impact of the
Membrane-Bound Oxygen Reductases.''} \emph{PLOS ONE} 10 (4): e0123455.
\url{https://doi.org/10.1371/journal.pone.0123455}.

\leavevmode\hypertarget{ref-rolfe1978}{}%
Rolfe, Rial D., David J. Hentges, Benedict J. Campbell, and James T.
Barrett. 1978. {``Factors Related to the Oxygen Tolerance of Anaerobic
Bacteria.''} \emph{Applied and Environmental Microbiology} 36 (2):
306--13. \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC291219/}.

\leavevmode\hypertarget{ref-schoeffler2019}{}%
Schoeffler, Marine, Anne-Laure Gaudin, Fanny Ramel, Odile Valette, Yann
Denis, Wagdi Ben Hania, Agnès Hirschler-Réa, and Alain Dolla. 2019.
{``Growth of an Anaerobic Sulfate-Reducing Bacterium Sustained by Oxygen
Respiratory Energy Conservation After O {\textsubscript{2}} -Driven
Experimental Evolution: O {\textsubscript{2}} -Driven Experimental
Evolution of {\emph{Desulfovibrio}}.''} \emph{Environmental
Microbiology} 21 (1): 360--73.
\url{https://doi.org/10.1111/1462-2920.14466}.

\end{CSLReferences}

\bibliographystyle{unsrt}
\bibliography{references.bib}

\end{document}

### 2021-05-06 simulations/experiment_framework.R

@@ -1,0 +1,475 @@
+## Setup R ----
+
+rm(list = ls())
+
+# devtools::install_github("opetchey/microxanox",
+#                          ref="main",
+#                          auth_token = "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",
+#                          build_vignettes = TRUE,
+#                          force = TRUE)
+
+library(tidyverse)
+library(microxanox)
+library(patchwork)
+library(here)
+source(here("simulations/r functions/various_useful_functions.r"))
+
+
+## Initialise general simulation conditions ----
+default_dynamic_model <- bushplus_dynamic_model
+default_event_definition <- event_definition_1
+## no default parameter values
+default_event_interval <- 100
+default_noise_sigma <- 0
+default_minimum_abundances <- rep(100, 3)
+names(default_minimum_abundances) <- c("CB", "PB", "SB") 
+default_sim_duration <- 50000
+default_sim_sample_interval <- 10
+## note that next line (log10a_series is over-ridden with getting stable states)
+#default_log10a_series <- c(-2, -2, -2, -2, -10, -10, -10, -10, -10)
+num_CB_strains <- 9
+num_SB_strains <- 9
+num_PB_strains <- 9
+default_9strain <- new_starter(n_CB = num_CB_strains,
+                             n_SB = num_SB_strains,
+                             n_PB = num_PB_strains,
+                             values_initial_state = "bush_anoxic")
+
+
+## Initialise general steady state finding setting ----
+ssfind_minimum_abundances <- rep(0, 3)
+names(ssfind_minimum_abundances) <- c("CB", "PB", "SB") 
+ssfind_simulation_duration <- 100000
+ssfind_simulation_sampling_interval <- ssfind_simulation_duration
+ssfind_event_interval <- ssfind_simulation_duration
+grid_num_a <- 100 ## number of a_0 values
+a_Os <- 10^seq(-4.5, -1.5, length=grid_num_a) ## sequence of a_0 values
+grid_num_N <- 2 ## number of N values
+initial_CBs <- 10^seq(0, 8, length=grid_num_N) ## sequence of N values
+initial_PBs <- 1e5 ## not varied
+initial_SBs <- 1e5 ## not varied
[…]

### 2021-05-06 simulations/r functions/various_useful_functions.r

@@ -1,0 +1,135 @@
+
+add_strain_var <- function(x,
+                           CB_var_gmax=0, CB_var_h=0,
+                           SB_var_gmax=0, SB_var_h=0,
+                           PB_var_gmax=0, PB_var_h=0) {
+  
+  new_x <- x
+  new_x$CB$g_max_CB <- x$CB$g_max_CB*(1+seq(-CB_var_gmax, CB_var_gmax, length=length(new_x$CB$g_max_CB)))
+  new_x$CB$h_SR_CB <- x$CB$h_SR_CB*(1+seq(-CB_var_h, CB_var_h, length=length(new_x$CB$h_SR_CB)))
+  new_x$SB$g_max_SB <- x$SB$g_max_SB*(1+seq(-SB_var_gmax, SB_var_gmax, length=length(new_x$SB$g_max_SB)))
+  new_x$SB$h_O_SB <- x$SB$h_O_SB*(1+seq(-SB_var_h, SB_var_h, length=length(new_x$SB$h_O_SB)))
+  new_x$PB$g_max_PB <- x$PB$g_max_PB*(1+seq(-PB_var_gmax, PB_var_gmax, length=length(new_x$PB$g_max_PB)))
+  new_x$PB$h_O_PB <- x$PB$h_O_PB*(1+seq(-PB_var_h, PB_var_h, length=length(new_x$PB$h_O_PB)))
+  new_x
+}
+
+
+plot_and_save <- function(CB_var_gmax, CB_var_h,
+                          SB_var_gmax, SB_var_h,
+                          PB_var_gmax, PB_var_h,
+                          sim_res,
+                          file_path_and_prefix) {
+  plot_dynamics(sim_res)
+  ggsave(paste0(file_path_and_prefix,
+                "-CB_", round(CB_var_gmax,3), "_", round(CB_var_h,3),
+                "-SB_", round(SB_var_gmax,3), "_", round(SB_var_h,3),
+                "-PB_", round(PB_var_gmax,3), "_", round(PB_var_h,3),
+                ".pdf"),
+         width = 10)
+  NULL
+}
+
+
+plot_ss_result1 <- function(ss_result,
+                            CB_var_gmax, CB_var_h,
+                            SB_var_gmax, SB_var_h,
+                            PB_var_gmax, PB_var_h,
+                            filename_prefix,
+                            save_image_file = TRUE) {
+  
[…]

### 2021-05-09 manuscript/article.Rmd
stable states overlay plot

@@
 ```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
-#ss_sim_data <- readRDS("working/sim data/ss_res_2.RDS")
-ss_var <- ss_sim_data[43,]
+ss_sim_data <- readRDS(here("simulations/sim data/ss_res_3.RDS"))
+ss_var <- ss_sim_data[20,]
 p2  <- plot_ss_result1(ss_var$ss_res[[1]],
@@
 
+```
+
+```{r}
+ss_sim_data <- readRDS(here("simulations/sim data/ss_res_2.RDS"))
+ss_novar <- ss_sim_data[22,]
+
+ss_sim_data <- readRDS(here("simulations/sim data/ss_res_3.RDS"))
+ss_var <- ss_sim_data[20,]
+
+ss_result1 <- ss_novar$ss_res[[1]]
+ss_result2 <- ss_var$ss_res[[1]]
+
+p_overlay <- plot_ss_result2(ss_novar$ss_res[[1]],
+                             ss_var$ss_res[[1]],
+                             xlims = c(-3, -2.25))
+
+p_overlay
 ```
@@
 
+https://onlinelibrary.wiley.com/doi/10.1111/ele.13760?af=R
+
 # Acknowledgements

### 2021-05-09 simulations/r functions/various_useful_functions.r

@@ -133,3 +133,87 @@ plot_ss_result1 <- function(ss_result,
   
 }
 
+
+plot_ss_result2 <- function(ss_result1,
+                            ss_result2,
+                            xlims) {
+  
+  species_colours <- c(CB = "#024F17", SB = "#7D1402", PB = "#6E0172")
+  
+  #colfunc_CB <- colorRampPalette(c("#B5FFC9", "#024F17"))
+  #colfunc_SB <- colorRampPalette(c("#FCBEB3", "#7D1402"))
+  #colfunc_PB <- colorRampPalette(c("#F9AEFC", "#6E0172"))
+  
+  temp1 <- ss_result1 %>%
+    arrange(a) %>%
+    select(-initial_N_CB, -a_O) %>%
+    mutate(a = 10^a,
+           direction = rep(c("up", "down"), nrow(ss_result1)/2)) %>%
+    gather(species, quantity, 2:(ncol(.)-1)) %>% 
+    mutate(var_type=ifelse(grepl("B_", species), "Organism", "Substrate"),
+           functional_group = case_when(str_detect(species, "CB_") ~ "CB",
+                                        str_detect(species, "SB_") ~ "SB",
+                                        str_detect(species, "PB_") ~ "PB"),
+           functional_group = ifelse(is.na(functional_group), species, functional_group)) %>%
+    group_by(a, direction, var_type, functional_group) %>%
+    summarise(total_quantity = sum(quantity, na.rm = TRUE)) %>%
+    mutate(log10_total_quantity = log10(total_quantity+1))
+  temp2 <- ss_result2 %>%
+    arrange(a) %>%
+    select(-initial_N_CB, -a_O) %>%
+    mutate(a = 10^a,
+           direction = rep(c("up", "down"), nrow(ss_result2)/2)) %>%
+    gather(species, quantity, 2:(ncol(.)-1)) %>% 
+    mutate(var_type=ifelse(grepl("B_", species), "Organism", "Substrate"),
+           functional_group = case_when(str_detect(species, "CB_") ~ "CB",
+                                        str_detect(species, "SB_") ~ "SB",
+                                        str_detect(species, "PB_") ~ "PB"),
+           functional_group = ifelse(is.na(functional_group), species, functional_group)) %>%
[…]

### 2021-05-09 manuscript/article.Rmd
small changes to article

@@
 ---
+
+```{r include = FALSE}
+knitr::opts_chunk$set(include = FALSE,
+                      warning = FALSE,
+                      message = FALSE)
+```
 
@@
 
-```{r}
+```{r ss_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
 ss_sim_data <- readRDS(here("simulations/sim data/ss_res_2.RDS"))
@@
 
-```{r}
+```{r ss_var3, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
 ss_sim_data <- readRDS(here("simulations/sim data/ss_res_3.RDS"))

### 2021-05-09 manuscript/article.tex
small changes to article

@@
   }
-
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\usepackage{framed}
-\definecolor{shadecolor}{RGB}{248,248,248}
-\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\BuiltInTok}[1]{#1}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
-\newcommand{\ExtensionTok}[1]{#1}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ImportTok}[1]{#1}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\NormalTok}[1]{#1}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\RegionMarkerTok}[1]{#1}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
 
@@
   }
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{library}\NormalTok{(tidyverse)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## -- Attaching packages --------------------------------------- tidyverse 1.3.0 --
-\end{verbatim}
-
-\begin{verbatim}
-## v ggplot2 3.3.3     v purrr   0.3.4
-## v tibble  3.1.0     v dplyr   1.0.5
-## v tidyr   1.1.2     v stringr 1.4.0
-## v readr   1.4.0     v forcats 0.5.0
-\end{verbatim}
-
-\begin{verbatim}
-## -- Conflicts ------------------------------------------ tidyverse_conflicts() --
-## x dplyr::filter() masks stats::filter()
-## x dplyr::lag()    masks stats::lag()
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{library}\NormalTok{(microxanox)}
-\FunctionTok{library}\NormalTok{(patchwork)}
-\FunctionTok{library}\NormalTok{(here)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## here() starts at /Users/owenpetchey/Desktop/microxanox/diversity_envresp1
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{source}\NormalTok{(}\FunctionTok{here}\NormalTok{(}\StringTok{"simulations/r functions/various\_useful\_functions.r"}\NormalTok{))}
-\end{Highlighting}
-\end{Shaded}
 
@@
 
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/ss_var2-1}
+
+}
+
+\caption{your caption}\label{fig:ss_var2}
+\end{figure}
+
 \hypertarget{figure-hysteresis-shift-point-nonlinearity-as-var-increases.}{%
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{ss\_sim\_data }\OtherTok{\textless{}{-}} \FunctionTok{readRDS}\NormalTok{(}\FunctionTok{here}\NormalTok{(}\StringTok{"simulations/sim data/ss\_res\_3.RDS"}\NormalTok{))}
+\begin{figure}
 
-\NormalTok{ss\_sim\_data }\OtherTok{\textless{}{-}}\NormalTok{ ss\_sim\_data }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{group\_by}\NormalTok{(CB\_var\_gmax\_s, CB\_var\_h\_s,}
-\NormalTok{           SB\_var\_gmax\_s, SB\_var\_h\_s,}
-\NormalTok{           PB\_var\_gmax\_s, PB\_var\_h\_s) }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{do}\NormalTok{(}\AttributeTok{stability\_measures =} \FunctionTok{get\_stability\_measures}\NormalTok{(.}\SpecialCharTok{$}\NormalTok{ss\_res[[}\DecValTok{1}\NormalTok{]]))}
-\NormalTok{results }\OtherTok{\textless{}{-}} \FunctionTok{unnest}\NormalTok{(ss\_sim\_data, }\AttributeTok{cols =} \FunctionTok{c}\NormalTok{(stability\_measures))}
+{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/ss_var3-1}
 
-\NormalTok{results }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{filter}\NormalTok{(Species }\SpecialCharTok{==} \StringTok{"O"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ CB\_var\_gmax\_s, }\AttributeTok{y =}\NormalTok{ hyst\_range)) }\SpecialCharTok{+}
-  \FunctionTok{geom\_point}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
+}
 
-\includegraphics{article_files/figure-latex/unnamed-chunk-2-1.pdf}
+\caption{your caption}\label{fig:ss_var3}
+\end{figure}
 
@@
 \url{https://onlinelibrary.wiley.com/doi/10.1111/gcb.15662?af=R}
+
+\url{https://onlinelibrary.wiley.com/doi/10.1111/ele.13760?af=R}
 

### 2021-05-09 simulations/r functions/various_useful_functions.r

@@ -185,8 +185,7 @@ plot_ss_result2 <- function(ss_result1,
     ggplot(aes(x=log10(a), y=log10_total_quantity, group=direction)) +
     geom_path(col = species_colours[fg_oi]) +
     ylab('log10(quantity [cells])') +
-    xlab('a') +
-    scale_colour_manual(values = colfunc_CB(num_CB_strains)) +
+    xlab('a')  +
     guides(colour = guide_legend(ncol = 3)) +
     geom_path(data = dplyr::filter(temp2, functional_group == fg_oi),
               linetype = "dashed",

### 2021-05-13 manuscript/article.Rmd
big update

--- 2021-05-06 manuscript/article.Rmd
@@
   - Cyanobacteria
-  - Sulphur bacteria
+  - Sulfur bacteria
 bibliography: references.bib
@@
 
-Types of ecosystem responses to environmental change.
-What and why.
-Importance of non-linearity and hysteresis.
-Feedbacks, diversity / evolution.
-Includes graphical hypotheses.
-What is the relative importance of feedbacks (composition) and diversity / evolution.
+When thinking about ecosystem stability, a key question is how biodiversity influences ecosystem responses to environmental change (figure 1: panel a shows linear response with different gradients, large being with low diversity; panel b shows a linear and a non-linear response starting and ending at the same place; panel c shows a hysteretic response, with greater or less range of hysteresis).
 
-Ceulemans, R., Wojcik, L.A. & Gaedke, U. (2021). Functional diversity alters the effects of a pulse perturbation on the dynamics of tritrophic food webs. *bioRxiv*, 2021.03.22.436420.
+In this context, a directly relevant aspect of biodiversity is variation in functional traits, i.e.
+the traits that determine organismal responses to environmental conditions and that determine the effects of organisms on their environment (citation).
+Variation in functional traits is often termed "functional diversity".
 
-[@dakos2019]
+There is a considerable amount of theory predicting, and evidence supporting, that greater functional diversity leads to lower temporal variability in ecosystem states variables (such as total biomass) (citations).
+The mechanism by which this occurs is that greater functional response diversity causes a weaker relationship between an environmental driver gradient and the ecosystem state (figure 1a), due to the functional turnover along the environmental driver gradient that results from variation in organisms' responses to the environmental driver gradient .
+
+There is less theory about effects of functional diversity on the linearity (figure 1b) and the hysteresis (figure 1c) of ecosystem responses to environmental change.
+@dakos2019b, in their article "Ecosystem tipping points in an evolving world" asked how changes in functional trait distributions (including evolutionary changes) affect the occurrence of tipping points.
+They predict that:
+
+-   In general, greater functional response diversity may decrease the likelihood of a catastrophic ecosystem response (Figure 2a in @dakos2019b).
+Here, we interpret this prediction to be that greater functional response diversity decreases the non-linearity of ecosystem response to environmental driver change, including the extreme non-linearity that can occur when an ecosystem "flips" from one state to another one.
+
+-   Greater functional trait diversity can make a tipping point occur only with greater change in an environmental driver (Figure 2a in @dakos2019b).
+I.e.
+functional trait diversity can increase resilience--the extent of environmental change required to push the ecosystem into another state (@holling1973).
+This could occur if greater functional diversity equates to the presence of organisms with greater tolerance to the environmental driver @dakos2019b.
+
+-   On the other hand, the opposite could occur: greater functional diversity could make a tipping point occur with less change in an environmental driver (i.e.
+may cause lower resilience) (Figure 2c in \@dakos2019b).
+This could occur if there is selection for greater tolerance is causes, incidentally, selection for lower growth rate, perhaps due to a tradeoff between the two traits.
+
+-   Finally, the amount of functional diversity may affect the "recovery trajectory", i.e.
+the relationship between ecosystem state and the environmental driver when the driver change is reversed @dakos2019b.
+Put another way, functional diversity may increase or decrease the amount of hysteresis, and may even result in a recovery with lower non-linearity / no tipping-point (Figure 3 in @dakos2019b).
+
+One reason why these predictions are often indeterminate is that trait distributions can be affected by, and effect, organismal abundances and environmental conditions.
+These numerous resulting feedbacks make predictions from verbal argumentation rather difficult.
+**Discuss Ceulemans, R., Wojcik, L.A.
+& Gaedke, U.
+(2021).
+Functional diversity alters the effects of a pulse perturbation on the dynamics of tritrophic food webs.
+*bioRxiv*, 2021.03.22.436420.**
+
+What of the empirical evidence? Hillebrand...
+
+## Scope of our investigation
+
+Questions: - How does variation organismal tolerances affect response
+
+Approach: - Modelling the system with ODEs. - Diversity manipulation (can be considered selection among strains, or selection among species). - Do not include mutation.
+
+According the the questions (in the Introduction) this is what we did:
+
+Variation in amount of among strain variation, no variation in number of strains, no variation in strength or shape of the of the tradeoff
+
+Effect of among strain variation on how the steady state(s) of the system varies with in different environmental conditions, and on the dynamical response of system to gradual environmental change.
+
+# Methods
+
+## The study ecosystem
 
@@
 
-Empirical evidence of variation in organismal tolerance. Across species and evolution experiments. [@schoeffler2019]
+```{r ecosys_network, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
+knitr::include_graphics(here("manuscript/ecosystem_network.png"))
+```
 
+The model ecosystem contains three types (functional groups) of organism (Figure \ref(fig:ecosys_network)): cyanobacteria ($CB$), sulfate-reducing bacteria ($SB$), and phototrophic sulfur bacteria ($PB$), four chemical substrates (oxygen $O$, phosphorous $P$, reduced sulfur $SR$, and oxidised sulfur $SO$), and four types of flow/interaction (production, consumption, inhibition, and diffusion).
+Particularly important among these interactions are that the cyanobacteria produce oxygen which inhibits the growth of both types of sulfur bacteria.
+And the sulfate-reducing bacteria produce reduced sulfur, such as hydrogen sulphide, which inhibit the growth of cyanobacteria.
+This mutual inhibition (a positive feedback) creates the potential for an oxic cyanobacteria dominated state and an anoxic sulfur bacteria dominated state to be alternate stable states.
+
+Simulation of this ecosystem as a set of ordinary differential equations demonstrated that the presence of alternate stable states depended on the rate at which oxygen diffuses into (or out of) the system [@bush2017].
+Low levels of oxygen diffusivity result in only the anoxic state being stable.
+High levels result in only the oxic state.
+Intermediate oxygen diffusivity allowed alternate stable states, with the occurring state depending on historical conditions.
+Historical dominance of cyanobacteria caused the oxic state to occur, which historical dominance of the sulfur bacteria caused the anoxic state to occur.
+All this was thoroughly and elegantly presented in @bush2017.
+
+As mentioned above, critical for the presence of alternate stable states in this ecosystem is the mutual inhibition between cyanobacteria and sulfur bacteria.
+This mutual inhibition is created by their intolerance of the chemical substrates that the other produces.
 Recent experimental evolution studies have demonstrated considerable increases in tolerance.
-For example, the sulphur bacteria *Desulfovibrio vulgaris* evolved a 32-fold increase in oxygen tolerance [@schoeffler2019] .
-Furthermore, the evolved strains were capable of oxygen respiration that permits growth.
-Genome re-sequencing revealed that few mutations were involved.
-Additionally, the cyanobacterium *Microcystis aeruginosa* evolved a four-fold higher sulphide tolerance via rare spontaneous mutations [@martínclemente2019].
-In that study, populations with higher genetic variation and those experiencing slower environmental change (an increase in sulphide concentration) were more likely to persist at high sulphide concentration.
+For example, the sulfur bacteria *Desulfovibrio vulgaris* evolved a 32-fold increase in oxygen tolerance, via relatively few mutations [@schoeffler2019].
+And the cyanobacterium *Microcystis aeruginosa* evolved a four-fold higher sulfide tolerance via rare spontaneous mutations [@martínclemente2019].
+In that study, populations with higher genetic variation and those experiencing slower environmental change (an increase in sulfide concentration) were more likely to persist at high sulfide concentration.
+Furthemore, there is considerable interspecific variation in tolerances [@schoeffler2019]
+
+Physiological tolerances to environmental conditions, including interspecific variation in tolerance and evolution of tolerance, are a key component of the engineering of ecosystem for determining their stability (Minervini *et al.* 2014)(Gómez‐Gras *et al.* 2019)(Cuenca Cambronero *et al.* 2018)(Vos *et al.* 2017)(Evans & Wallenstein 2014)(Rolfe *et al.* 1978)(Knoll & Bauld 1989)(Girvan *et al.* 2005).
 
@@
 
-Physiological tolerances to environmental conditions, including interspecific variation in tolerance and evolution of tolerance, are a key component of the engineering of ecosystem for determining their stability (Minervini *et al.* 2014)(Gómez‐Gras *et al.* 2019)(Cuenca Cambronero *et al.* 2018)(Vos *et al.* 2017)(Evans & Wallenstein 2014)(Rolfe *et al.* 1978)(Knoll & Bauld 1989)(Girvan *et al.* 2005).
-
-Questions: - How does variation organismal tolerances affect response
-
-Approach: - Modelling the system with ODEs. - Diversity manipulation (can be considered selection among strains, or selection among species). - Do not include mutation.
-
-# Methods
-
 ## The model
 
-Bush et al (2017) contains an excellent description of the model of the ecosystem. Here we only describe the extensions needed for modelling multiple strains/taxa per functional group.
+Bush et al (2017) contains an accessible and complete description of the model of the ecosystem, including rate equations, parameter values, and initial conditions.
+These features are also represented and documented in the `microxanox` R package (**cite the package**).
+Therefore, here we only describe the relatively straightforward extension we used to model multiple strains per functional group.
+
+Each of the strains within each functional groups has its own parameter set and state variable.
+Thus a system with nine strains within each functional group has 27 state variables, plus another four (one for each of the four chemical substrates).
+Other than having potentially different parameter values (e.g.
+maximum growth rate and tolerance parameter) the dynamics of the strains in a functional were described by the same equations.
+Hence, when parameterised with multiple strains per functional group, but no variation among strains (within functional groups), the system behaves identically to when there is only one strain per functional group (see the `microxanox` R package *User Guide* for a demonstration).
+
+The only other necessary modification was to include summation terms in each of the four ordinary differential equations describing the rates of change of the four chemical substrates.
+This was required in order to appropriately account for the production and consumption of these substrates by multiple strains.
+
+## Model dimensions
+
+-   Time: hours
+-   Volume: litres
+-   Substrate quantity: micromoles
+-   Organism quantity: cells
+
+## Creating within functional group diversity
+
+```{r echo = FALSE}
+parms <- microxanox::new_starter()
+G_max <- parms$CB$g_max_CB
+h <- parms$CB$h
+Div_G_max <- 1
+Div_h <- -1
+n <- 9
+x <-1:n
+f_x <- (x-(n+1)/2) / (( n-1)/2)
+D_G_max <- 2^(f_x*Div_G_max)
+G_max_i <- D_G_max * G_max
+D_h_i <- 2^(f_x*Div_h)
+h_i <- D_h_i * h
+```
+
+```{r echo = FALSE, eval = FALSE}
+g_max_CB <- G_max * 2^(seq(-Div_G_max, Div_G_max, length=n))
+h_SR_CB <- h * 2^(-seq(-Div_h, Div_h, length=n))
+ggplot() +
+  geom_point(aes(x = g_max_CB, y = h_SR_CB))
+```
+
+In this section we describe how we created variability among the multiple strains within functional groups.
+Since the process was the same for each functional group, we usually do not in this description subscript parameter names by functional group (though there were functional group specific parameters in all simulations).
+The descriptions in this section gradually become more mathematical; the next paragraph alone should provide the information required to understand all other elements of this report.
+
+We introduced among-strain variability in maximum growth rate (parameter $G_{max}$) and in the tolerance to the relevant inhibiting chemical substrate (parameter $h$).
+Among-strain variability was created such that there was a tradeoff between maximum growth rate and tolerance (i.e.
+high tolerance coinciding with low maximum growth rate) (e.g.
+Figure \@ref(fig:tradeoff).
+Our implementation of the variation and tradeoff contain the assumption of a linear tradeoff of log-log transformed among-strain variation.
+
+```{r tradeoff, out.width="0.5\\linewidth", fig.align="center", fig.cap=c("An example of among-strain variation in growth rate and tolerance, and the tradeoff in the variation."), echo = FALSE}
+ggplot() +
+  geom_point(aes(x = G_max_i, y = h_i)) +
+  xlab("Maximum growth rate") +
+  ylab("Tolerance") +
+  theme_bw(base_size = 20)
+```
+
+For further understanding, please consider a reference maximum growth rate parameter $G_{max}$ and reference tolerance parameter $h$.
+Furthermore, consider the meta-parameters $Div_{G_{max}}$ and $Div_{h}$, which determine the amount of variation among $n$-strains in the growth rate and tolerance parameters.
+To create a tradeoff, the two meta-parameters were always of different sign.
+
+The among strain variation was calculated such that the growth rate of strain $i = 1$ was a factor $1/(2^{Div_{G_{max}}})$ of the reference growth rate, and the growth rate of the $i = n$ strain was a factor $2^{Div_{G_{max}}}$ of the reference growth rate.
+The growth rate of the $i = \{2,...n-1\}$ other strains was the reference growth rate multiplied by a factor that was equally distributed between the factor of the $i = 1$ and $i = n$ strain.
+
+Hence, for example, with the reference growth rate $G_{max} =$ `r G_max`, among strain variation of $Div_{G_{max}} =$ `r Div_G_max`, and nine strains ($n =$ `r n`), then the growth rates of the nine strains are `r round(G_max_i,3)` (Figure \@ref(fig:tradeoff).
+
+(Put another way, the growth rate parameter of the i-th of the $n$ strains in a functional group was calculated as $G_{max, i} = D_i * G_{max}$ where D_i is the i-th element of the set $D = \{2^{f(x)Div_{G_{max}}} | x \in \mathbb{N}, x \leq n\}$, where $f(x) = (x-(n+1)/2) / (( n-1)/2)$.)
 
 ## Measurement of non-linearity and hysteresis
+
+Requires an environmental change... as in Bush, oxygen diffusivity.
 
@@
 
-R package.
+We implemented the model in the `microxanox` package (**cite the package**) of the R programming language (\*\*cite R Core Team*).
+The package contains functions for initialising, running, visualising, and analysing simulations of the system described above.
+Please refer to the `microxanox` package* User Guide\* and *Partial reproduction of Bush et al (2017)* vignettes for further information about it.
 
@@
 
-## Figure: Stable states with and without variation.
+## Figure: Stable states without variation
 
 ```{r ss_novar, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
-ss_sim_data <- readRDS(here("simulations/sim data/ss_res_2.RDS"))
-ss_novar <- ss_sim_data[22,]
+#ss_sim_data <- readRDS(here("simulations/sim data/ss_res_grad1_old_strain_var.RDS"))
+ss_sim_data <- readRDS(here("simulations/sim data/ss_res_grad_new2.RDS"))
+ss_novar <- ss_sim_data[1,]
 p1  <- plot_ss_result1(ss_novar$ss_res[[1]],
@@
 
-`
+X-axis must be labelled log10(a).
+
+## Figure: Stable states with variation and tradeoff
+
 ```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
-#ss_sim_data <- readRDS("working/sim data/ss_res_2.RDS")
-ss_var <- ss_sim_data[43,]
+ss_var <- ss_sim_data[20,]
 p2  <- plot_ss_result1(ss_var$ss_res[[1]],
@@
 
+X-axis must be labelled log10(a).
+
+```{r ss_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
+
+#ss_result1 <- ss_novar$ss_res[[1]]
+#ss_result2 <- ss_var$ss_res[[1]]
+
+p_overlay <- plot_ss_result2(ss_novar$ss_res[[1]],
+                             ss_var$ss_res[[1]],
+                             xlims = c(-7, -1))
+
+p_overlay
+```
+
+X-axis must be labelled log10(a).
+
 ## Figure: hysteresis, shift point, nonlinearity, as var increases.
 
-```{r}
-ss_sim_data <- readRDS(here("simulations/sim data/ss_res_3.RDS"))
+Resolution of a_grid with 100 steps is about 0.03 units, which is about the resolution of the y axis here. Hysteresis range is measures in log10(a) units.
+
+```{r ss_var3, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
+#ss_sim_data <- readRDS(here("simulations/sim data/ss_res_3.RDS"))
 
@@
 
+What does this study tell us about effects of functional diversity on ecosystem stability?
+
+What does this study tell us about the effects of evolution on ecosystem stability?
+
+Need a more process based approach to variation in biodiversity: mutation, genetics,
+
+As mentioned in the Introduction, the numerous feedacks among trait distributions, organismal abundances, and environmental conditions,  resulting feedbacks make predictions from verbal argumentation rather difficult.
+They may also make for context dependent effects of functional diversity.
+I.e.
+functional diversity may delay a tipping point in one context (e.g.
+ecosystem type) but delay it in another.
+This is why we need more investigations, both theoretical and empirical, of effects of functional trait diversity on environmental responses to environmental change.
+
 <https://onlinelibrary.wiley.com/doi/10.1111/gcb.15662?af=R>
+
+<https://onlinelibrary.wiley.com/doi/10.1111/ele.13760?af=R>
 
@@
 
-SNF
-URPP
+SNF URPP

### 2021-05-13 manuscript/article.tex
big update

@@
    \and
-    Sulphur bacteria
+    Sulfur bacteria
   }
@@
 
-Types of ecosystem responses to environmental change. What and why.
-Importance of non-linearity and hysteresis. Feedbacks, diversity /
-evolution. Includes graphical hypotheses. What is the relative
-importance of feedbacks (composition) and diversity / evolution.
+When thinking about ecosystem stability, a key question is how
+biodiversity influences ecosystem responses to environmental change
+(figure 1: panel a shows linear response with different gradients, large
+being with low diversity; panel b shows a linear and a non-linear
+response starting and ending at the same place; panel c shows a
+hysteretic response, with greater or less range of hysteresis).
 
+In this context, a directly relevant aspect of biodiversity is variation
+in functional traits, i.e.~the traits that determine organismal
+responses to environmental conditions and that determine the effects of
+organisms on their environment (citation). Variation in functional
+traits is often termed ``functional diversity.''
+
+There is a considerable amount of theory predicting, and evidence
+supporting, that greater functional diversity leads to lower temporal
+variability in ecosystem states variables (such as total biomass)
+(citations). The mechanism by which this occurs is that greater
+functional response diversity causes a weaker relationship between an
+environmental driver gradient and the ecosystem state (figure 1a), due
+to the functional turnover along the environmental driver gradient that
+results from variation in organisms' responses to the environmental
+driver gradient .
+
+There is less theory about effects of functional diversity on the
+linearity (figure 1b) and the hysteresis (figure 1c) of ecosystem
+responses to environmental change. Dakos et al. (2019), in their article
+``Ecosystem tipping points in an evolving world'' asked how changes in
+functional trait distributions (including evolutionary changes) affect
+the occurrence of tipping points. They predict that:
+
+\begin{itemize}
+\item
+  In general, greater functional response diversity may decrease the
+  likelihood of a catastrophic ecosystem response (Figure 2a in Dakos et
+  al. (2019)). Here, we interpret this prediction to be that greater
+  functional response diversity decreases the non-linearity of ecosystem
+  response to environmental driver change, including the extreme
+  non-linearity that can occur when an ecosystem ``flips'' from one
+  state to another one.
+\item
+  Greater functional trait diversity can make a tipping point occur only
+  with greater change in an environmental driver (Figure 2a in Dakos et
+  al. (2019)). I.e. functional trait diversity can increase
+  resilience--the extent of environmental change required to push the
+  ecosystem into another state (Holling (1973)). This could occur if
+  greater functional diversity equates to the presence of organisms with
+  greater tolerance to the environmental driver Dakos et al. (2019).
+\item
+  On the other hand, the opposite could occur: greater functional
+  diversity could make a tipping point occur with less change in an
+  environmental driver (i.e.~may cause lower resilience) (Figure 2c in
+  @dakos2019b). This could occur if there is selection for greater
+  tolerance is causes, incidentally, selection for lower growth rate,
+  perhaps due to a tradeoff between the two traits.
+\item
+  Finally, the amount of functional diversity may affect the ``recovery
+  trajectory,'' i.e.~the relationship between ecosystem state and the
+  environmental driver when the driver change is reversed Dakos et al.
+  (2019). Put another way, functional diversity may increase or decrease
+  the amount of hysteresis, and may even result in a recovery with lower
+  non-linearity / no tipping-point (Figure 3 in Dakos et al. (2019)).
+\end{itemize}
+
+One reason why these predictions are often indeterminate is that trait
+distributions can be affected by, and effect, organismal abundances and
+environmental conditions. These numerous resulting feedbacks make
+predictions from verbal argumentation rather difficult. \textbf{Discuss
 Ceulemans, R., Wojcik, L.A. \& Gaedke, U. (2021). Functional diversity
 alters the effects of a pulse perturbation on the dynamics of tritrophic
-food webs. \emph{bioRxiv}, 2021.03.22.436420.
+food webs. \emph{bioRxiv}, 2021.03.22.436420.}
 
-(Dakos et al. 2019)
+What of the empirical evidence? Hillebrand\ldots{}
+
+\hypertarget{scope-of-our-investigation}{%
+\subsection{Scope of our
+investigation}\label{scope-of-our-investigation}}
+
+Questions: - How does variation organismal tolerances affect response
+
+Approach: - Modelling the system with ODEs. - Diversity manipulation
+(can be considered selection among strains, or selection among species).
+- Do not include mutation.
+
+According the the questions (in the Introduction) this is what we did:
+
+Variation in amount of among strain variation, no variation in number of
+strains, no variation in strength or shape of the of the tradeoff
+
+Effect of among strain variation on how the steady state(s) of the
+system varies with in different environmental conditions, and on the
+dynamical response of system to gradual environmental change.
+
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
+
+\hypertarget{the-study-ecosystem}{%
+\subsection{The study ecosystem}\label{the-study-ecosystem}}
 
@@
 
-Empirical evidence of variation in organismal tolerance. Across species
-and evolution experiments. (Schoeffler et al. 2019)
+\begin{figure}
 
-Recent experimental evolution studies have demonstrated considerable
-increases in tolerance. For example, the sulphur bacteria
-\emph{Desulfovibrio vulgaris} evolved a 32-fold increase in oxygen
-tolerance (Schoeffler et al. 2019) . Furthermore, the evolved strains
-were capable of oxygen respiration that permits growth. Genome
-re-sequencing revealed that few mutations were involved. Additionally,
-the cyanobacterium \emph{Microcystis aeruginosa} evolved a four-fold
-higher sulphide tolerance via rare spontaneous mutations
-(Martín-Clemente et al. 2019). In that study, populations with higher
-genetic variation and those experiencing slower environmental change (an
-increase in sulphide concentration) were more likely to persist at high
-sulphide concentration.
+{\centering \includegraphics[width=1\linewidth]{/Users/owenpetchey/Desktop/microxanox/diversity_envresp1/manuscript/ecosystem_network}
+
+}
+
+\caption{your caption}\label{fig:ecosys_network}
+\end{figure}
+
+The model ecosystem contains three types (functional groups) of organism
+(Figure \ref(fig:ecosys\_network)): cyanobacteria (\(CB\)),
+sulfate-reducing bacteria (\(SB\)), and phototrophic sulfur bacteria
+(\(PB\)), four chemical substrates (oxygen \(O\), phosphorous \(P\),
+reduced sulfur \(SR\), and oxidised sulfur \(SO\)), and four types of
+flow/interaction (production, consumption, inhibition, and diffusion).
+Particularly important among these interactions are that the
+cyanobacteria produce oxygen which inhibits the growth of both types of
+sulfur bacteria. And the sulfate-reducing bacteria produce reduced
+sulfur, such as hydrogen sulphide, which inhibit the growth of
+cyanobacteria. This mutual inhibition (a positive feedback) creates the
+potential for an oxic cyanobacteria dominated state and an anoxic sulfur
+bacteria dominated state to be alternate stable states.
+
+Simulation of this ecosystem as a set of ordinary differential equations
+demonstrated that the presence of alternate stable states depended on
+the rate at which oxygen diffuses into (or out of) the system (Bush et
+al. 2017). Low levels of oxygen diffusivity result in only the anoxic
+state being stable. High levels result in only the oxic state.
+Intermediate oxygen diffusivity allowed alternate stable states, with
+the occurring state depending on historical conditions. Historical
+dominance of cyanobacteria caused the oxic state to occur, which
+historical dominance of the sulfur bacteria caused the anoxic state to
+occur. All this was thoroughly and elegantly presented in Bush et al.
+(2017).
+
+As mentioned above, critical for the presence of alternate stable states
+in this ecosystem is the mutual inhibition between cyanobacteria and
+sulfur bacteria. This mutual inhibition is created by their intolerance
+of the chemical substrates that the other produces. Recent experimental
+evolution studies have demonstrated considerable increases in tolerance.
+For example, the sulfur bacteria \emph{Desulfovibrio vulgaris} evolved a
+32-fold increase in oxygen tolerance, via relatively few mutations
+(Schoeffler et al. 2019). And the cyanobacterium \emph{Microcystis
+aeruginosa} evolved a four-fold higher sulfide tolerance via rare
+spontaneous mutations (Martín-Clemente et al. 2019). In that study,
+populations with higher genetic variation and those experiencing slower
+environmental change (an increase in sulfide concentration) were more
+likely to persist at high sulfide concentration. Furthemore, there is
+considerable interspecific variation in tolerances (Schoeffler et al.
+2019)
+
+Physiological tolerances to environmental conditions, including
+interspecific variation in tolerance and evolution of tolerance, are a
+key component of the engineering of ecosystem for determining their
+stability (Minervini \emph{et al.} 2014)(Gómez‐Gras \emph{et al.}
+2019)(Cuenca Cambronero \emph{et al.} 2018)(Vos \emph{et al.}
+2017)(Evans \& Wallenstein 2014)(Rolfe \emph{et al.} 1978)(Knoll \&
+Bauld 1989)(Girvan \emph{et al.} 2005).
 
@@
 
-Physiological tolerances to environmental conditions, including
-interspecific variation in tolerance and evolution of tolerance, are a
-key component of the engineering of ecosystem for determining their
-stability (Minervini \emph{et al.} 2014)(Gómez‐Gras \emph{et al.}
-2019)(Cuenca Cambronero \emph{et al.} 2018)(Vos \emph{et al.}
-2017)(Evans \& Wallenstein 2014)(Rolfe \emph{et al.} 1978)(Knoll \&
-Bauld 1989)(Girvan \emph{et al.} 2005).
-
-Questions: - How does variation organismal tolerances affect response
-
-Approach: - Modelling the system with ODEs. - Diversity manipulation
-(can be considered selection among strains, or selection among species).
-- Do not include mutation.
-
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
 \hypertarget{the-model}{%
@@
 
-Bush et al (2017) contains an excellent description of the model of the
-ecosystem. Here we only describe the extensions needed for modelling
-multiple strains/taxa per functional group.
+Bush et al (2017) contains an accessible and complete description of the
+model of the ecosystem, including rate equations, parameter values, and
+initial conditions. These features are also represented and documented
+in the \texttt{microxanox} R package (\textbf{cite the package}).
+Therefore, here we only describe the relatively straightforward
+extension we used to model multiple strains per functional group.
+
+Each of the strains within each functional groups has its own parameter
+set and state variable. Thus a system with nine strains within each
+functional group has 27 state variables, plus another four (one for each
+of the four chemical substrates). Other than having potentially
+different parameter values (e.g.~maximum growth rate and tolerance
+parameter) the dynamics of the strains in a functional were described by
+the same equations. Hence, when parameterised with multiple strains per
+functional group, but no variation among strains (within functional
+groups), the system behaves identically to when there is only one strain
+per functional group (see the \texttt{microxanox} R package \emph{User
+Guide} for a demonstration).
+
+The only other necessary modification was to include summation terms in
+each of the four ordinary differential equations describing the rates of
+change of the four chemical substrates. This was required in order to
+appropriately account for the production and consumption of these
+substrates by multiple strains.
+
+\hypertarget{creating-within-functional-group-diversity}{%
+\subsection{Creating within functional group
+diversity}\label{creating-within-functional-group-diversity}}
+
+In this section we describe how we created variability among the
+multiple strains within functional groups. Since the process was the
+same for each functional group, we usually do not in this description
+subscript parameter names by functional group (though there were
+functional group specific parameters in all simulations). The
+descriptions in this section gradually become more mathematical; the
+next paragraph alone should provide the information required to
+understand all other elements of this report.
+
+We introduced among-strain variability in maximum growth rate (parameter
+\(G_{max}\)) and in the tolerance to the relevant inhibiting chemical
+substrate (parameter \(h\)). Among-strain variability was created such
+that there was a tradeoff between maximum growth rate and tolerance
+(i.e.~high tolerance coinciding with low maximum growth rate)
+(e.g.~Figure @ref(fig:tradeoff). Our implementation of the variation and
+tradeoff contain the assumption of a linear tradeoff of log-log
+transformed among-strain variation.
+
+For further understanding, please consider a reference maximum growth
+rate parameter \(G_{max}\) and reference tolerance parameter \(h\).
+Furthermore, consider the meta-parameters \(Div_{G_{max}}\) and
+\(Div_{h}\), which determine the amount of variation among \(n\)-strains
+in the growth rate and tolerance parameters. To create a tradeoff, the
+two meta-parameters were always of different sign.
+
+The among strain variation was calculated such that the growth rate of
+strain \(i = 1\) was a factor \(1/(2^{Div_{G_{max}}})\) of the reference
+growth rate, and the growth rate of the \(i = n\) strain was a factor
+\(2^{Div_{G_{max}}}\) of the reference growth rate. The growth rate of
+the \(i = \{2,...n-1\}\) other strains was the reference growth rate
+multiplied by a factor that was equally distributed between the factor
+of the \(i = 1\) and \(i = n\) strain.
+
+Hence, for example, with the reference growth rate \(G_{max} =\) 0.05,
+among strain variation of \(Div_{G_{max}} =\) 1, and nine strains
+(\(n =\) 9), then the growth rates of the nine strains are 0.025, 0.03,
+0.035, 0.042, 0.05, 0.059, 0.071, 0.084, 0.1 (Figure @ref(fig:tradeoff).
+
+(Put another way, the growth rate parameter of the i-th of the \(n\)
+strains in a functional group was calculated as
+\(G_{max, i} = D_i * G_{max}\) where D\_i is the i-th element of the set
+\(D = \{2^{f(x)Div_{G_{max}}} | x \in \mathbb{N}, x \leq n\}\), where
+\(f(x) = (x-(n+1)/2) / (( n-1)/2)\).)
 
@@
 hysteresis}\label{measurement-of-non-linearity-and-hysteresis}}
+
+Requires an environmental change\ldots{} as in Bush, oxygen diffusivity.
 
@@
 
-R package.
+We implemented the model in the \texttt{microxanox} package
+(\textbf{cite the package}) of the R programming language (**cite R Core
+Team\emph{). The package contains functions for initialising, running,
+visualising, and analysing simulations of the system described above.
+Please refer to the \texttt{microxanox} package} User Guide* and
+\emph{Partial reproduction of Bush et al (2017)} vignettes for further
+information about it.
 
@@
 
-\hypertarget{figure-stable-states-with-and-without-variation.}{%
-\subsection{Figure: Stable states with and without
-variation.}\label{figure-stable-states-with-and-without-variation.}}
+\hypertarget{figure-stable-states-without-variation}{%
+\subsection{Figure: Stable states without
+variation}\label{figure-stable-states-without-variation}}
 
@@
 
-`
+X-axis must be labelled log10(a).
+
+\hypertarget{figure-stable-states-with-variation-and-tradeoff}{%
+\subsection{Figure: Stable states with variation and
+tradeoff}\label{figure-stable-states-with-variation-and-tradeoff}}
 
@@
 
+X-axis must be labelled log10(a).
+
 \begin{figure}
@@
 
+X-axis must be labelled log10(a).
+
 \hypertarget{figure-hysteresis-shift-point-nonlinearity-as-var-increases.}{%
@@
 increases.}\label{figure-hysteresis-shift-point-nonlinearity-as-var-increases.}}
+
+Resolution of a\_grid with 100 steps is about 0.03 units, which is about
+the resolution of the y axis here. Hysteresis range is measures in
+log10(a) units.
 
@@
 
+What does this study tell us about effects of functional diversity on
+ecosystem stability?
+
+What does this study tell us about the effects of evolution on ecosystem
+stability?
+
+Need a more process based approach to variation in biodiversity:
+mutation, genetics,
+
+As mentioned in the Introduction, the numerous feedacks among trait
+distributions, organismal abundances, and environmental conditions,
+resulting feedbacks make predictions from verbal argumentation rather
+difficult. They may also make for context dependent effects of
+functional diversity. I.e. functional diversity may delay a tipping
+point in one context (e.g.~ecosystem type) but delay it in another. This
+is why we need more investigations, both theoretical and empirical, of
+effects of functional trait diversity on environmental responses to
+environmental change.
+
 \url{https://onlinelibrary.wiley.com/doi/10.1111/gcb.15662?af=R}
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-dakos2019}{}%
+\leavevmode\hypertarget{ref-bush2017}{}%
+Bush, Timothy, Muhe Diao, Rosalind J. Allen, Ruben Sinnige, Gerard
+Muyzer, and Jef Huisman. 2017. {``Oxic-Anoxic Regime Shifts Mediated by
+Feedbacks Between Biogeochemical Processes and Microbial Community
+Dynamics.''} \emph{Nature Communications} 8 (1): 789.
+\url{https://doi.org/10.1038/s41467-017-00912-x}.
+
+\leavevmode\hypertarget{ref-dakos2019b}{}%
 Dakos, Vasilis, Blake Matthews, Andrew P. Hendry, Jonathan Levine,
@@
 \url{https://doi.org/10.1038/ismej.2017.193}.
+
+\leavevmode\hypertarget{ref-holling1973}{}%
+Holling, C S. 1973. {``Resilience and Stability of Ecological
+Systems.''} \emph{Annual Review of Ecology and Systematics} 4 (1):
+1--23. \url{https://doi.org/10.1146/annurev.es.04.110173.000245}.
 

### 2021-05-13 simulations/r functions/various_useful_functions.r

@@ -1,5 +1,37 @@
-
 add_strain_var <- function(x,
+                               CB_var_gmax=0, CB_var_h=0,
+                               SB_var_gmax=0, SB_var_h=0,
+                               PB_var_gmax=0, PB_var_h=0) {
+  
+  new_x <- x
+  new_x$CB$g_max_CB <- x$CB$g_max_CB * 2^(seq(-CB_var_gmax, CB_var_gmax, length=length(new_x$CB$g_max_CB)))
+  new_x$CB$h_SR_CB <- x$CB$h_SR_CB * 2^(seq(-CB_var_h, CB_var_h, length=length(new_x$CB$h_SR_CB)))
+  new_x$SB$g_max_SB <- x$SB$g_max_SB * 2^(seq(-SB_var_gmax, SB_var_gmax, length=length(new_x$SB$g_max_SB)))
+  new_x$SB$h_O_SB <- x$SB$h_O_SB * 2^(seq(-SB_var_h, SB_var_h, length=length(new_x$SB$h_O_SB)))
+  new_x$PB$g_max_PB <- x$PB$g_max_PB * 2^(seq(-PB_var_gmax, PB_var_gmax, length=length(new_x$PB$g_max_PB)))
+  new_x$PB$h_O_PB <- x$PB$h_O_PB * 2^(seq(-PB_var_h, PB_var_h, length=length(new_x$PB$h_O_PB)))
+  new_x
+}
+
+
+plot_and_save <- function(CB_var_gmax, CB_var_h,
+                          SB_var_gmax, SB_var_h,
+                          PB_var_gmax, PB_var_h,
+                          sim_res,
+                          file_path_and_prefix) {
+  plot_dynamics(sim_res)
+  ggsave(paste0(file_path_and_prefix,
+                "-CB_", round(CB_var_gmax,3), "_", round(CB_var_h,3),
+                "-SB_", round(SB_var_gmax,3), "_", round(SB_var_h,3),
+                "-PB_", round(PB_var_gmax,3), "_", round(PB_var_h,3),
+                ".pdf"),
+         width = 10)
+  NULL
+}
+
+
+
+add_strain_var_old <- function(x,
                            CB_var_gmax=0, CB_var_h=0,
                            SB_var_gmax=0, SB_var_h=0,
                            PB_var_gmax=0, PB_var_h=0) {
@@ -45,7 +77,9 @@ plot_ss_result1 <- function(ss_result,
[…]

### 2021-05-13 manuscript/article.Rmd
added text to article

@@
   To be completed
+
 keywords:
@@
 There is less theory about effects of functional diversity on the linearity (figure 1b) and the hysteresis (figure 1c) of ecosystem responses to environmental change.
-@dakos2019b, in their article "Ecosystem tipping points in an evolving world" asked how changes in functional trait distributions (including evolutionary changes) affect the occurrence of tipping points.
-They predict that:
+@dakos2019b, in their article *Ecosystem tipping points in an evolving world* asked how changes in functional trait distributions (including evolutionary changes) affect the occurrence of tipping points.
+They explain that:
 
@@
 
-One reason why these predictions are often indeterminate is that trait distributions can be affected by, and effect, organismal abundances and environmental conditions.
-These numerous resulting feedbacks make predictions from verbal argumentation rather difficult.
-**Discuss Ceulemans, R., Wojcik, L.A.
-& Gaedke, U.
-(2021).
-Functional diversity alters the effects of a pulse perturbation on the dynamics of tritrophic food webs.
-*bioRxiv*, 2021.03.22.436420.**
+These explanations/predictions were based on the verbal/graphical argumentation @dakos2019b.
+There were no mathematical models of ecosystem responses to environmetnal change behind the explanations/predictions.
+@ceulemans2021, in their article *Functional diversity alters the effects of a pulse perturbation on the dynamics of tritrophic food webs*, did employ a such a mathematical model.
 
@@
 
+One reason why the explanations of Dakos et al are often indeterminate is that trait distributions can be affected by, and effect, organismal abundances and environmental conditions.
+These numerous resulting feedbacks may limit the determinancy of explanations based on the verbal/graphical argumentation employed by @dakos2019b.
+They may also make for context dependent effects of functional diversity.
+I.e.
+functional diversity may delay a tipping point in one context (e.g.
+ecosystem type and/or particular parameterisation of a specific system) but delay it in another.
+**Based on our findings, (1) can we make determinate predictions, and (2) what level of generality do our preditions have?** [Possible text: The answers are (1) no, we cannot make determinate predictions: we found sign varying effects of functional trait diversity on the nature of ecosystem responses to environmental change.
+And (2) our predictions have very limited generality.
+This is because we did not aim for general predictions: we investigate a single parameterisation of a single model, with many explicit and implicit assumptions.
+This is why we need more investigations, both theoretical and empirical, of effects of functional trait diversity on environmental responses to environmental change.]
+
+What are the priorities for follow-on modelling studies?
+
+1)  Multifarious environmental driver changes.
+2)  More process based approach to variation in biodiversity: mutation, genetics,
+
 What does this study tell us about effects of functional diversity on ecosystem stability?
@@
 
-Need a more process based approach to variation in biodiversity: mutation, genetics,
+## What are the priorities for subsequent research?
 
-As mentioned in the Introduction, the numerous feedacks among trait distributions, organismal abundances, and environmental conditions,  resulting feedbacks make predictions from verbal argumentation rather difficult.
-They may also make for context dependent effects of functional diversity.
-I.e.
-functional diversity may delay a tipping point in one context (e.g.
-ecosystem type) but delay it in another.
-This is why we need more investigations, both theoretical and empirical, of effects of functional trait diversity on environmental responses to environmental change.
+A research programme that integrates [text from ERC application]. E.g. Global Change Microbiology -- with quote.
+
+Then replicated across numerous ecosystems and taxa.
+That is, we imagine a blue-print / template for proposals that aim to establish such an integrative research programme.
+This template would contain mandatory workpackages and experiments, and sufficient standardisation to allow for rigorous and quantitative across programme meta-analyses
 
@@
 SNF URPP
+
+## Bibliography

### 2021-05-17 manuscript/article.Rmd
article work, mostly

@@
 
-When thinking about ecosystem stability, a key question is how biodiversity influences ecosystem responses to environmental change (figure 1: panel a shows linear response with different gradients, large being with low diversity; panel b shows a linear and a non-linear response starting and ending at the same place; panel c shows a hysteretic response, with greater or less range of hysteresis).
+This report concerns how biodiversity influences the strength and nature of ecosystem responses to environmental change (figure 1: panel a shows linear response with different gradients, large being with low diversity; panel b shows a linear and a non-linear response starting and ending at the same place; panel c shows a hysteretic response, with greater or less range of hysteresis).
+Strong responses of ecosystems to environmental change imply high *sensitivity* and lack of resistance to environmental change, and higher temporal variability in the face of varying environmental conditions.
+Greater *non-linearity* in ecosystem responses increases the potential for surprises, such as when an ecosystem that was resistant to an environmental change becomes unexpectedly sensitive to further change.
+The presence and extent of *hysteresis* in ecosystem responses to environmental driver gradients concerns how readily are ecosystem responses reversed when environmental change is reversed.
 
@@
 Variation in functional traits is often termed "functional diversity".
-
-There is a considerable amount of theory predicting, and evidence supporting, that greater functional diversity leads to lower temporal variability in ecosystem states variables (such as total biomass) (citations).
+There is a considerable amount of theory predicting, and evidence supporting, that greater functional diversity leads to lower temporal variability in ecosystem states variables (such as total biomass) (citations) (Leary, Pennekamp).
 The mechanism by which this occurs is that greater functional response diversity causes a weaker relationship between an environmental driver gradient and the ecosystem state (figure 1a), due to the functional turnover along the environmental driver gradient that results from variation in organisms' responses to the environmental driver gradient .
@@
 These explanations/predictions were based on the verbal/graphical argumentation @dakos2019b.
-There were no mathematical models of ecosystem responses to environmetnal change behind the explanations/predictions.
+There were no mathematical models of ecosystem responses to environmental change behind the explanations/predictions.
 @ceulemans2021, in their article *Functional diversity alters the effects of a pulse perturbation on the dynamics of tritrophic food webs*, did employ a such a mathematical model.
 
-What of the empirical evidence? Hillebrand...
+We discuss empirical studies in the Discussion section (spoiler--there are few, if any, directly relevant ones).
 
@@
 
+What of the empirical evidence? Hillebrand...
+
 What are the priorities for follow-on modelling studies?

### 2021-06-04 manuscript/article.Rmd
Update article.Rmd

@@
 source(here("simulations/r functions/various_useful_functions.r"))
+
+##test
 ```
@@
 
+## Relaxing the biological assumptions of the model
+
 <https://onlinelibrary.wiley.com/doi/10.1111/gcb.15662?af=R>

### 2021-06-04 manuscript/article.Rmd
Update article.Rmd

@@
 
+Microbial performances are highly species-dependent towards abiotic factors, specially when comparing different functional groups of microorganisms like in this study.
+Assumptions of our models could be made much more detailed, resulting in highly complex networks.
+One of the issues that should be discussed is the inhibition role of reduced sulfide compounds to Cyanobacteria.
+While some studies were discussing these inhibition events due to attacking fotosystem (10.1016/0005-2728(79)90045-8; doi.org/10.1128/AEM.70.2.736-744.2004), other studies reported an even strengthen fotosynthesis effect with specific concentration of H2S ( https://doi.org/10.1111/1462-2920.12791).
+In addition, some Cyanobacteria like Leptolyngba are even in need of specific sulfur compounds in order to grow (doi.org/10.1038/ismej.2017.193) and are able to even perform anoxygenic photosynthesis.
+Therefore, the role of H2S seem to be more complicated than our model assumes.
+
+Also the role of light can be discussed, since the functional groups of this study differ in their preferred light intensities (and even wavelength).
+Future assumptions could include gradient of light intensities, in which Cyanobacteria grow faster with high light intensities (10.1074/jbc.R100003200) and phototrophic sulfur bacteria with very low intensities( 10.4319/lo.1992.37.1.0150).
+
 <https://onlinelibrary.wiley.com/doi/10.1111/gcb.15662?af=R>

### 2021-06-09 manuscript/article.Rmd
many additions

--- 2021-05-17 manuscript/article.Rmd
@@
     email: rainer.krug@ieu.uzh.ch
+  - name: Any Others
+    department: Department of Evolutionary Biology and Environmental Studies
+    affiliation: University of Zurich
+    location: Zurich 8057, Switzerland
+    email: any.others@ieu.uzh.ch
   - name: Marcel Suleiman
@@
                       warning = FALSE,
-                      message = FALSE)
+                      message = FALSE,
+                      cache = TRUE)
 ```
@@
 
-This report concerns how biodiversity influences the strength and nature of ecosystem responses to environmental change (figure 1: panel a shows linear response with different gradients, large being with low diversity; panel b shows a linear and a non-linear response starting and ending at the same place; panel c shows a hysteretic response, with greater or less range of hysteresis).
+This report concerns how biodiversity influences the strength and nature of ecosystem responses to environmental change (figure 1; panel(a) three ovals, environment oval with arrow to ecosystem property oval, with biodiversity oval pointing the arrow between environment and ecosystem property; panel (b) shows linear response with different gradients, large being with low diversity; panel (c) shows a linear and a non-linear response starting and ending at the same place; panel (d) shows a hysteretic response, with greater or less range of hysteresis).
 Strong responses of ecosystems to environmental change imply high *sensitivity* and lack of resistance to environmental change, and higher temporal variability in the face of varying environmental conditions.
@@
 There is a considerable amount of theory predicting, and evidence supporting, that greater functional diversity leads to lower temporal variability in ecosystem states variables (such as total biomass) (citations) (Leary, Pennekamp).
-The mechanism by which this occurs is that greater functional response diversity causes a weaker relationship between an environmental driver gradient and the ecosystem state (figure 1a), due to the functional turnover along the environmental driver gradient that results from variation in organisms' responses to the environmental driver gradient .
+The mechanism by which this occurs is that greater functional response diversity causes a weaker relationship between an environmental driver gradient and the ecosystem state (figure 1a/b), due to the functional turnover along the environmental driver gradient that results from variation in organisms' responses to the environmental driver gradient (citation).
 
-There is less theory about effects of functional diversity on the linearity (figure 1b) and the hysteresis (figure 1c) of ecosystem responses to environmental change.
+There is less theory about effects of functional diversity on the linearity (figure 1c) and the hysteresis (figure 1d) of ecosystem responses to environmental change.
 @dakos2019b, in their article *Ecosystem tipping points in an evolving world* asked how changes in functional trait distributions (including evolutionary changes) affect the occurrence of tipping points.
@@
 may cause lower resilience) (Figure 2c in \@dakos2019b).
-This could occur if there is selection for greater tolerance is causes, incidentally, selection for lower growth rate, perhaps due to a tradeoff between the two traits.
+This could occur if there is selection for greater tolerance that causes, incidentally, selection for lower growth rate, perhaps due to a tradeoff between the two traits.
 
@@
 There were no mathematical models of ecosystem responses to environmental change behind the explanations/predictions.
-@ceulemans2021, in their article *Functional diversity alters the effects of a pulse perturbation on the dynamics of tritrophic food webs*, did employ a such a mathematical model.
+@ceulemans2021, in their article *Functional diversity alters the effects of a pulse perturbation on the dynamics of tritrophic food webs*, did employ a such a mathematical model [to be developed].
 
@@
 
-## Scope of our investigation
+## Aim and scope of our investigation
 
-Questions: - How does variation organismal tolerances affect response
+Aim:
 
-Approach: - Modelling the system with ODEs. - Diversity manipulation (can be considered selection among strains, or selection among species). - Do not include mutation.
+* To provide an answer to the question of how trait variation affects the non-linearity, resilience and hysteresis of ecosystem response to an environmental change.
 
-According the the questions (in the Introduction) this is what we did:
+Scope:
 
-Variation in amount of among strain variation, no variation in number of strains, no variation in strength or shape of the of the tradeoff
+* Mathematical modelling of a microbrial ecosystem. Trait diversity manipulation (can be considered selection among strains, or selection among species). (Do not include mutation or recomination).
 
-Effect of among strain variation on how the steady state(s) of the system varies with in different environmental conditions, and on the dynamical response of system to gradual environmental change.
+* Variation in amount of among strain variation, no variation in number of strains, no variation in strength or shape of the of the tradeoff.
+
+* Measurement of the effect on how the steady state(s) of the system varies with in different environmental conditions, and on the dynamical response of system to gradual environmental change.
 
@@
 Furthemore, there is considerable interspecific variation in tolerances [@schoeffler2019]
+
+"Variation in Sulfide Tolerance of Photosystem II in Phylogenetically Diverse Cyanobacteria from Sulfidic Habitats", by Miller and Bebout (2004) [https://aem.asm.org/content/70/2/736.short]
 
@@
 
-```{r tradeoff, out.width="0.5\\linewidth", fig.align="center", fig.cap=c("An example of among-strain variation in growth rate and tolerance, and the tradeoff in the variation."), echo = FALSE}
+```{r tradeoff, include = TRUE, echo = FALSE, out.width="0.5\\linewidth", fig.align="center", fig.cap=c("An example of among-strain variation in growth rate and tolerance, and the tradeoff in the variation.")}
 ggplot() +
@@
 
+## Further relaxing the assumptions
+
+Deterministic -> stochastic : www.pnas.org/cgi/doi/10.1073/pnas.1414708112
+
 ## What are the priorities for subsequent research?

### 2021-06-09 manuscript/article.tex
many additions

@@
    \And
+    Any Others
+   \\
+    Department of Evolutionary Biology and Environmental Studies \\
+    University of Zurich \\
+  Zurich 8057, Switzerland \\
+  \texttt{\href{mailto:any.others@ieu.uzh.ch}{\nolinkurl{any.others@ieu.uzh.ch}}} \\
+   \And
     Marcel Suleiman
@@
 % For Pandoc 2.11+
-\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
  {% don't indent paragraphs
@@
 \newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
@@
 
-When thinking about ecosystem stability, a key question is how
-biodiversity influences ecosystem responses to environmental change
-(figure 1: panel a shows linear response with different gradients, large
-being with low diversity; panel b shows a linear and a non-linear
-response starting and ending at the same place; panel c shows a
-hysteretic response, with greater or less range of hysteresis).
+This report concerns how biodiversity influences the strength and nature
+of ecosystem responses to environmental change (figure 1; panel(a) three
+ovals, environment oval with arrow to ecosystem property oval, with
+biodiversity oval pointing the arrow between environment and ecosystem
+property; panel (b) shows linear response with different gradients,
+large being with low diversity; panel (c) shows a linear and a
+non-linear response starting and ending at the same place; panel (d)
+shows a hysteretic response, with greater or less range of hysteresis).
+Strong responses of ecosystems to environmental change imply high
+\emph{sensitivity} and lack of resistance to environmental change, and
+higher temporal variability in the face of varying environmental
+conditions. Greater \emph{non-linearity} in ecosystem responses
+increases the potential for surprises, such as when an ecosystem that
+was resistant to an environmental change becomes unexpectedly sensitive
+to further change. The presence and extent of \emph{hysteresis} in
+ecosystem responses to environmental driver gradients concerns how
+readily are ecosystem responses reversed when environmental change is
+reversed.
 
@@
 organisms on their environment (citation). Variation in functional
-traits is often termed ``functional diversity.''
-
-There is a considerable amount of theory predicting, and evidence
-supporting, that greater functional diversity leads to lower temporal
-variability in ecosystem states variables (such as total biomass)
-(citations). The mechanism by which this occurs is that greater
-functional response diversity causes a weaker relationship between an
-environmental driver gradient and the ecosystem state (figure 1a), due
-to the functional turnover along the environmental driver gradient that
-results from variation in organisms' responses to the environmental
-driver gradient .
+traits is often termed ``functional diversity.'' There is a considerable
+amount of theory predicting, and evidence supporting, that greater
+functional diversity leads to lower temporal variability in ecosystem
+states variables (such as total biomass) (citations) (Leary, Pennekamp).
+The mechanism by which this occurs is that greater functional response
+diversity causes a weaker relationship between an environmental driver
+gradient and the ecosystem state (figure 1a/b), due to the functional
+turnover along the environmental driver gradient that results from
+variation in organisms' responses to the environmental driver gradient
+(citation).
 
 There is less theory about effects of functional diversity on the
-linearity (figure 1b) and the hysteresis (figure 1c) of ecosystem
+linearity (figure 1c) and the hysteresis (figure 1d) of ecosystem
 responses to environmental change. Dakos et al. (2019), in their article
-``Ecosystem tipping points in an evolving world'' asked how changes in
-functional trait distributions (including evolutionary changes) affect
-the occurrence of tipping points. They predict that:
+\emph{Ecosystem tipping points in an evolving world} asked how changes
+in functional trait distributions (including evolutionary changes)
+affect the occurrence of tipping points. They explain that:
 
@@
   @dakos2019b). This could occur if there is selection for greater
-  tolerance is causes, incidentally, selection for lower growth rate,
+  tolerance that causes, incidentally, selection for lower growth rate,
   perhaps due to a tradeoff between the two traits.
@@
 
-One reason why these predictions are often indeterminate is that trait
-distributions can be affected by, and effect, organismal abundances and
-environmental conditions. These numerous resulting feedbacks make
-predictions from verbal argumentation rather difficult. \textbf{Discuss
-Ceulemans, R., Wojcik, L.A. \& Gaedke, U. (2021). Functional diversity
-alters the effects of a pulse perturbation on the dynamics of tritrophic
-food webs. \emph{bioRxiv}, 2021.03.22.436420.}
+These explanations/predictions were based on the verbal/graphical
+argumentation Dakos et al. (2019). There were no mathematical models of
+ecosystem responses to environmental change behind the
+explanations/predictions. Ceulemans, Wojcik, and Gaedke (2021), in their
+article \emph{Functional diversity alters the effects of a pulse
+perturbation on the dynamics of tritrophic food webs}, did employ a such
+a mathematical model {[}to be developed{]}.
 
-What of the empirical evidence? Hillebrand\ldots{}
+We discuss empirical studies in the Discussion section (spoiler--there
+are few, if any, directly relevant ones).
 
-\hypertarget{scope-of-our-investigation}{%
-\subsection{Scope of our
-investigation}\label{scope-of-our-investigation}}
+\hypertarget{aim-and-scope-of-our-investigation}{%
+\subsection{Aim and scope of our
+investigation}\label{aim-and-scope-of-our-investigation}}
 
-Questions: - How does variation organismal tolerances affect response
+Aim:
 
-Approach: - Modelling the system with ODEs. - Diversity manipulation
-(can be considered selection among strains, or selection among species).
-- Do not include mutation.
+\begin{itemize}
+\tightlist
+\item
+  To provide an answer to the question of how trait variation affects
+  the non-linearity, resilience and hysteresis of ecosystem response to
+  an environmental change.
+\end{itemize}
 
-According the the questions (in the Introduction) this is what we did:
+Scope:
 
-Variation in amount of among strain variation, no variation in number of
-strains, no variation in strength or shape of the of the tradeoff
-
-Effect of among strain variation on how the steady state(s) of the
-system varies with in different environmental conditions, and on the
+\begin{itemize}
+\item
+  Mathematical modelling of a microbrial ecosystem. Trait diversity
+  manipulation (can be considered selection among strains, or selection
+  among species). (Do not include mutation or recomination).
+\item
+  Variation in amount of among strain variation, no variation in number
+  of strains, no variation in strength or shape of the of the tradeoff.
+\item
+  Measurement of the effect on how the steady state(s) of the system
+  varies with in different environmental conditions, and on the
   dynamical response of system to gradual environmental change.
+\end{itemize}
 
@@
 
+``Variation in Sulfide Tolerance of Photosystem II in Phylogenetically
+Diverse Cyanobacteria from Sulfidic Habitats,'' by Miller and Bebout
+(2004) {[}\url{https://aem.asm.org/content/70/2/736.short}{]}
+
 Physiological tolerances to environmental conditions, including
@@
 
+\hypertarget{model-dimensions}{%
+\subsection{Model dimensions}\label{model-dimensions}}
+
+\begin{itemize}
+\tightlist
+\item
+  Time: hours
+\item
+  Volume: litres
+\item
+  Substrate quantity: micromoles
+\item
+  Organism quantity: cells
+\end{itemize}
+
 \hypertarget{creating-within-functional-group-diversity}{%
@@
 transformed among-strain variation.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.5\linewidth]{article_files/figure-latex/tradeoff-1}
+
+}
+
+\caption{An example of among-strain variation in growth rate and tolerance, and the tradeoff in the variation.}\label{fig:tradeoff}
+\end{figure}
 
@@
 
+One reason why the explanations of Dakos et al are often indeterminate
+is that trait distributions can be affected by, and effect, organismal
+abundances and environmental conditions. These numerous resulting
+feedbacks may limit the determinancy of explanations based on the
+verbal/graphical argumentation employed by Dakos et al. (2019). They may
+also make for context dependent effects of functional diversity. I.e.
+functional diversity may delay a tipping point in one context
+(e.g.~ecosystem type and/or particular parameterisation of a specific
+system) but delay it in another. \textbf{Based on our findings, (1) can
+we make determinate predictions, and (2) what level of generality do our
+preditions have?} {[}Possible text: The answers are (1) no, we cannot
+make determinate predictions: we found sign varying effects of
+functional trait diversity on the nature of ecosystem responses to
+environmental change. And (2) our predictions have very limited
+generality. This is because we did not aim for general predictions: we
+investigate a single parameterisation of a single model, with many
+explicit and implicit assumptions. This is why we need more
+investigations, both theoretical and empirical, of effects of functional
+trait diversity on environmental responses to environmental change.{]}
+
+What of the empirical evidence? Hillebrand\ldots{}
+
+What are the priorities for follow-on modelling studies?
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\tightlist
+\item
+  Multifarious environmental driver changes.
+\item
+  More process based approach to variation in biodiversity: mutation,
+  genetics,
+\end{enumerate}
+
 What does this study tell us about effects of functional diversity on
@@
 
-Need a more process based approach to variation in biodiversity:
-mutation, genetics,
+\hypertarget{what-are-the-priorities-for-subsequent-research}{%
+\subsection{What are the priorities for subsequent
+research?}\label{what-are-the-priorities-for-subsequent-research}}
 
-As mentioned in the Introduction, the numerous feedacks among trait
-distributions, organismal abundances, and environmental conditions,
-resulting feedbacks make predictions from verbal argumentation rather
-difficult. They may also make for context dependent effects of
-functional diversity. I.e. functional diversity may delay a tipping
-point in one context (e.g.~ecosystem type) but delay it in another. This
-is why we need more investigations, both theoretical and empirical, of
-effects of functional trait diversity on environmental responses to
-environmental change.
+A research programme that integrates {[}text from ERC application{]}.
+E.g. Global Change Microbiology -- with quote.
+
+Then replicated across numerous ecosystems and taxa. That is, we imagine
+a blue-print / template for proposals that aim to establish such an
+integrative research programme. This template would contain mandatory
+workpackages and experiments, and sufficient standardisation to allow
+for rigorous and quantitative across programme meta-analyses
 
@@
 
+\hypertarget{bibliography}{%
+\subsection*{Bibliography}\label{bibliography}}
+\addcontentsline{toc}{subsection}{Bibliography}
+
 \hypertarget{refs}{}
@@
 \url{https://doi.org/10.1038/s41467-017-00912-x}.
+
+\leavevmode\hypertarget{ref-ceulemans2021}{}%
+Ceulemans, Ruben, Laurie Anne Wojcik, and Ursula Gaedke. 2021.
+{``Functional Diversity Alters the Effects of a Pulse Perturbation on
+the Dynamics of Tritrophic Food Webs.''} \emph{bioRxiv}, March,
+2021.03.22.436420. \url{https://doi.org/10.1101/2021.03.22.436420}.
 

### 2021-06-18 manuscript/article.Rmd
new sims added

@@
 #ss_sim_data <- readRDS(here("simulations/sim data/ss_res_grad1_old_strain_var.RDS"))
-ss_sim_data <- readRDS(here("simulations/sim data/ss_res_grad_new2.RDS"))
+ss_sim_data <- readRDS(here("simulations/sim data/ss_res_CBSBPB_var.RDS"))
 ss_novar <- ss_sim_data[1,]

### 2021-06-18 simulations/experiment_framework.R

@@ -58,80 +58,190 @@ ss_expt <- expand.grid(N_CB = initial_CBs,
 
 
 ## Factorial CB, SB, PB variation experiment ----
-CB_var_gmax_s <- seq(0, 0.1, length=2)
-CB_var_h_s = seq(0, -0.5, length=2)
-SB_var_gmax_s <- seq(0, 0.1, length=2)
-SB_var_h_s = seq(0, -0.5, length=2)
-PB_var_gmax_s <- seq(0, 0.1, length=2)
-PB_var_h_s = seq(0, -0.5, length=2)
+# CB_var_gmax_s <- seq(0, 0.1, length=2)
+# CB_var_h_s = seq(0, -0.5, length=2)
+# SB_var_gmax_s <- seq(0, 0.1, length=2)
+# SB_var_h_s = seq(0, -0.5, length=2)
+# PB_var_gmax_s <- seq(0, 0.1, length=2)
+# PB_var_h_s = seq(0, -0.5, length=2)
+# 
+# var_expt <- crossing(CB_var_gmax_s,
+#                      CB_var_h_s,
+#                      SB_var_gmax_s,
+#                      SB_var_h_s,
+#                      PB_var_gmax_s,
+#                      PB_var_h_s)
+# 
+# var_expt <- var_expt %>%
+#   group_by(CB_var_gmax_s, CB_var_h_s,
+#            SB_var_gmax_s, SB_var_h_s,
+#            PB_var_gmax_s, PB_var_h_s,
+#   ) %>%
+#   do(pars = add_strain_var(default_9strain,
+#                            CB_var_gmax = .$CB_var_gmax_s,
+#                            CB_var_h = .$CB_var_h_s,
+#                            SB_var_gmax = .$SB_var_gmax_s,
+#                            SB_var_h = .$SB_var_h_s,
+#                            PB_var_gmax = .$PB_var_gmax_s,
+#                            PB_var_h = .$PB_var_h_s))
+# var_expt$pars[[38]]$CB
+# var_expt$pars[[1]]$SB
+# var_expt$pars[[1]]$PB
+# 
+# #var_expt <- var_expt[1,]
+# 
+# ## Next chunck of code:
+# ## For each line of var_expt, add strain variation, and get stable states.
+# var_expt <- var_expt %>%
+#   group_by(CB_var_gmax_s, CB_var_h_s,
+#            SB_var_gmax_s, SB_var_h_s,
[…]

### 2021-06-21 manuscript/article.Rmd
various

--- 2021-06-09 manuscript/article.Rmd
@@
 -   On the other hand, the opposite could occur: greater functional diversity could make a tipping point occur with less change in an environmental driver (i.e.
-may cause lower resilience) (Figure 2c in \@dakos2019b).
+may cause lower resilience) (Figure 2c in @dakos2019b).
 This could occur if there is selection for greater tolerance that causes, incidentally, selection for lower growth rate, perhaps due to a tradeoff between the two traits.
@@
 
-* Variation in amount of among strain variation, no variation in number of strains, no variation in strength or shape of the of the tradeoff.
+* Variation in amount of among strain variation, no variation in number of strains, no variation in strength or shape of the of any tradeoff.
 
@@
 Other than having potentially different parameter values (e.g.
-maximum growth rate and tolerance parameter) the dynamics of the strains in a functional were described by the same equations.
+maximum growth rate and tolerance parameters) the dynamics of the strains in a functional were described by the same equations.
 Hence, when parameterised with multiple strains per functional group, but no variation among strains (within functional groups), the system behaves identically to when there is only one strain per functional group (see the `microxanox` R package *User Guide* for a demonstration).
@@
 #ss_sim_data <- readRDS(here("simulations/sim data/ss_res_grad1_old_strain_var.RDS"))
-ss_sim_data <- readRDS(here("simulations/sim data/ss_res_grad_new2.RDS"))
+ss_sim_data <- readRDS(here("simulations/sim data/ss_res_CBvar.RDS"))
 ss_novar <- ss_sim_data[1,]

### 2021-06-21 manuscript/article.Rmd
fixing up down problem rerun

@@
 ```{r ss_novar, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
-#ss_sim_data <- readRDS(here("simulations/sim data/ss_res_grad1_old_strain_var.RDS"))
-ss_sim_data <- readRDS(here("simulations/sim data/ss_res_CBvar.RDS"))
-ss_novar <- ss_sim_data[1,]
-p1  <- plot_ss_result1(ss_novar$ss_res[[1]],
-                ss_novar$CB_var_gmax_s,
-                ss_novar$CB_var_h_s,
-                ss_novar$SB_var_gmax_s,
-                ss_novar$SB_var_h_s,
-                ss_novar$PB_var_gmax_s,
-                ss_novar$PB_var_h_s,
+CBSBPB_data <- readRDS(here("simulations/sim data/ss_res_grad_CBSBPB_var.RDS"))
+
+ss_exp_result <- CBSBPB_data
+result_index <- 1
+
+p1  <- plot_ss_result1(CBSBPB_data,
+                result_index = 1,
                 filename_prefix = NULL,
@@
 
-## Figure: Stable states with variation and tradeoff
+## Figure: CBSBPB Stable states with variation and tradeoff
 
 ```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
-ss_var <- ss_sim_data[20,]
-p2  <- plot_ss_result1(ss_var$ss_res[[1]],
-                ss_var$CB_var_gmax_s,
-                ss_var$CB_var_h_s,
-                ss_var$SB_var_gmax_s,
-                ss_var$SB_var_h_s,
-                ss_var$PB_var_gmax_s,
-                ss_var$PB_var_h_s,
+p2  <- plot_ss_result1(tmp2$ss_res[[1]],
+                tmp2$CB_var_gmax_s,
+                tmp2$CB_var_h_s,
+                tmp2$SB_var_gmax_s,
+                tmp2$SB_var_h_s,
+                tmp2$PB_var_gmax_s,
+                tmp2$PB_var_h_s,
                 filename_prefix = NULL,
@@
 
-```{r ss_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
+```{r ss_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("CBSBPB var"), echo=FALSE}
 
@@
 
-p_overlay <- plot_ss_result2(ss_novar$ss_res[[1]],
-                             ss_var$ss_res[[1]],
+p_overlay <- plot_ss_result2(tmp1$ss_res[[1]],
+                             tmp2$ss_res[[1]],
+                             xlims = c(-7, -1))
+
+p_overlay
+```
+
+X-axis must be labelled log10(a).
+
+## Figure: CB Stable states with variation and tradeoff
+
+```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
+CB_data <- readRDS(here("simulations/sim data/ss_res_grad_CB_var.RDS"))
+tmp3 <- CB_data[20,]
+
+p2  <- plot_ss_result1(tmp3$ss_res[[1]],
+                tmp3$CB_var_gmax_s,
+                tmp3$CB_var_h_s,
+                tmp3$SB_var_gmax_s,
+                tmp3$SB_var_h_s,
+                tmp3$PB_var_gmax_s,
+                tmp3$PB_var_h_s,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p2
+
+```
+
+X-axis must be labelled log10(a).
+
+```{r ss_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("CBSBPB var"), echo=FALSE}
+
+#ss_result1 <- ss_novar$ss_res[[1]]
+#ss_result2 <- ss_var$ss_res[[1]]
+
+p_overlay <- plot_ss_result2(tmp1$ss_res[[1]],
+                             tmp3$ss_res[[1]],
+                             xlims = c(-7, -1))
+
+p_overlay
+```
+
+X-axis must be labelled log10(a).
+
+## Figure: SB Stable states with variation and tradeoff
+
+```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
+SB_data <- readRDS(here("simulations/sim data/ss_res_grad_SB_var.RDS"))
+tmp4 <- SB_data[20,]
+
+p2  <- plot_ss_result1(tmp4$ss_res[[1]],
+                tmp4$CB_var_gmax_s,
+                tmp4$CB_var_h_s,
+                tmp4$SB_var_gmax_s,
+                tmp4$SB_var_h_s,
+                tmp4$PB_var_gmax_s,
+                tmp4$PB_var_h_s,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p2
+
+```
+
+X-axis must be labelled log10(a).
+
+```{r ss_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("CBSBPB var"), echo=FALSE}
+
+#ss_result1 <- ss_novar$ss_res[[1]]
+#ss_result2 <- ss_var$ss_res[[1]]
+
+p_overlay <- plot_ss_result2(tmp1$ss_res[[1]],
+                             tmp4$ss_res[[1]],
                              xlims = c(-7, -1))
@@
 
-ss_sim_data <- ss_sim_data %>%
+CBSBPB_data <- CBSBPB_data %>%
   group_by(CB_var_gmax_s, CB_var_h_s,
@@
   do(stability_measures = get_stability_measures(.$ss_res[[1]]))
-results <- unnest(ss_sim_data, cols = c(stability_measures))
+results <- unnest(CBSBPB_data, cols = c(stability_measures))
 
@@
 
-To be added. Need to go both ways (oxic to anoxic, and anoxic to oxic).
+Maybe... to be added. Need to go both ways (oxic to anoxic, and anoxic to oxic).
 

### 2021-06-21 simulations/experiment_framework.R

@@ -2,11 +2,11 @@
 
 rm(list = ls())
 
-devtools::install_github("opetchey/microxanox",
-                          ref="main",
-                          auth_token = "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",
-                          build_vignettes = FALSE,
-                          force = TRUE)
+# devtools::install_github("opetchey/microxanox",
+#                           ref="main",
+#                           auth_token = "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",
+#                           build_vignettes = FALSE,
+#                           force = TRUE)
 
 library(tidyverse)
 library(microxanox)
@@ -56,213 +56,16 @@ ss_expt <- expand.grid(N_CB = initial_CBs,
 
 
 
-
-## Factorial CB, SB, PB variation experiment ----
-# CB_var_gmax_s <- seq(0, 0.1, length=2)
-# CB_var_h_s = seq(0, -0.5, length=2)
-# SB_var_gmax_s <- seq(0, 0.1, length=2)
-# SB_var_h_s = seq(0, -0.5, length=2)
-# PB_var_gmax_s <- seq(0, 0.1, length=2)
-# PB_var_h_s = seq(0, -0.5, length=2)
-# 
-# var_expt <- crossing(CB_var_gmax_s,
-#                      CB_var_h_s,
-#                      SB_var_gmax_s,
-#                      SB_var_h_s,
-#                      PB_var_gmax_s,
-#                      PB_var_h_s)
-# 
-# var_expt <- var_expt %>%
-#   group_by(CB_var_gmax_s, CB_var_h_s,
-#            SB_var_gmax_s, SB_var_h_s,
-#            PB_var_gmax_s, PB_var_h_s,
-#   ) %>%
-#   do(pars = add_strain_var(default_9strain,
-#                            CB_var_gmax = .$CB_var_gmax_s,
-#                            CB_var_h = .$CB_var_h_s,
-#                            SB_var_gmax = .$SB_var_gmax_s,
-#                            SB_var_h = .$SB_var_h_s,
-#                            PB_var_gmax = .$PB_var_gmax_s,
-#                            PB_var_h = .$PB_var_h_s))
-# var_expt$pars[[38]]$CB
-# var_expt$pars[[1]]$SB
-# var_expt$pars[[1]]$PB
-# 
-# #var_expt <- var_expt[1,]
-# 
[…]

### 2021-06-22 manuscript/article.Rmd
some nice progress

--- 2021-06-21 manuscript/article.Rmd
@@
 ```{r ss_novar, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
-#ss_sim_data <- readRDS(here("simulations/sim data/ss_res_grad1_old_strain_var.RDS"))
-ss_sim_data <- readRDS(here("simulations/sim data/ss_res_CBvar.RDS"))
-ss_novar <- ss_sim_data[1,]
-p1  <- plot_ss_result1(ss_novar$ss_res[[1]],
-                ss_novar$CB_var_gmax_s,
-                ss_novar$CB_var_h_s,
-                ss_novar$SB_var_gmax_s,
-                ss_novar$SB_var_h_s,
-                ss_novar$PB_var_gmax_s,
-                ss_novar$PB_var_h_s,
+CBSBPB_data <- readRDS(here("simulations/sim data/ss_res_grad_CBSBPB_var.RDS"))
+result_index1 <- 1
+p1  <- plot_ss_result1(CBSBPB_data,
+                result_index = result_index1,
                 filename_prefix = NULL,
@@
 
-## Figure: Stable states with variation and tradeoff
+## Figure: CBSBPB Stable states with variation and tradeoff
 
 ```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
-ss_var <- ss_sim_data[20,]
-p2  <- plot_ss_result1(ss_var$ss_res[[1]],
-                ss_var$CB_var_gmax_s,
-                ss_var$CB_var_h_s,
-                ss_var$SB_var_gmax_s,
-                ss_var$SB_var_h_s,
-                ss_var$PB_var_gmax_s,
-                ss_var$PB_var_h_s,
+result_index2 <- 2
+p2  <- plot_ss_result1(CBSBPB_data,
+                result_index = result_index2,
                 filename_prefix = NULL,
@@
 
-```{r ss_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
+```{r ss_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("CBSBPB var"), echo=FALSE}
+p_overlay <- plot_ss_result2(CBSBPB_data[result_index1,]$ss_res[[1]],
+                             CBSBPB_data[result_index2,]$ss_res[[1]],
+                             xlims = c(-7, -1))
+p_overlay
+```
 
-#ss_result1 <- ss_novar$ss_res[[1]]
-#ss_result2 <- ss_var$ss_res[[1]]
+X-axis must be labelled log10(a).
 
-p_overlay <- plot_ss_result2(ss_novar$ss_res[[1]],
-                             ss_var$ss_res[[1]],
+## Figure: CB Stable states with variation and tradeoff
+
+```{r CB_var1, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
+CB_data <- readRDS(here("simulations/sim data/ss_res_grad_CB_var.RDS"))
+p3  <- plot_ss_result1(CB_data,
+                result_index = result_index2,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p3
+```
+
+```{r CB_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
+p_overlay <- plot_ss_result2(CB_data[result_index1,]$ss_res[[1]],
+                             CB_data[result_index2,]$ss_res[[1]],
+                             xlims = c(-7, -1))
+p_overlay
+```
+
+## Figure: SB Stable states with variation and tradeoff
+
+```{r SB_var1, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
+SB_data <- readRDS(here("simulations/sim data/ss_res_grad_SB_var.RDS"))
+p4  <- plot_ss_result1(SB_data,
+                result_index = result_index2,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p4
+
+```
+
+```{r SB_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
+p_overlay <- plot_ss_result2(CB_data[result_index1,]$ss_res[[1]],
+                             SB_data[result_index2,]$ss_res[[1]],
                              xlims = c(-7, -1))
@@
 
-X-axis must be labelled log10(a).
+## Figure: PB Stable states with variation and tradeoff
+
+```{r PB_var1, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
+PB_data <- readRDS(here("simulations/sim data/ss_res_grad_PB_var.RDS"))
+p5  <- plot_ss_result1(PB_data,
+                result_index = result_index2,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p5
+
+```
+
+```{r PB_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
+p_overlay <- plot_ss_result2(CB_data[result_index1,]$ss_res[[1]],
+                             PB_data[result_index2,]$ss_res[[1]],
+                             xlims = c(-7, -1))
+
+p_overlay
+```
+
+## Figure: PB Stable states with variation and tradeoff
+
+```{r SBPB_var1, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
+SBPB_data <- readRDS(here("simulations/sim data/ss_res_grad_SBPB_var.RDS"))
+p6  <- plot_ss_result1(SBPB_data,
+                result_index = result_index2,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p6
+
+```
+
+```{r SBPB_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
+p_overlay <- plot_ss_result2(CB_data[result_index1,]$ss_res[[1]],
+                             SBPB_data[result_index2,]$ss_res[[1]],
+                             xlims = c(-7, -1))
+
+p_overlay
+```
 
@@
 
-ss_sim_data <- ss_sim_data %>%
+CBSBPB_stab_data <- CBSBPB_data %>%
   group_by(CB_var_gmax_s, CB_var_h_s,
@@
   do(stability_measures = get_stability_measures(.$ss_res[[1]]))
-results <- unnest(ss_sim_data, cols = c(stability_measures))
+results1 <- unnest(CBSBPB_stab_data, cols = c(stability_measures)) %>%
+  mutate(var_treat = "CB-SB-PB",
+         var_gmax = CB_var_gmax_s)
 
-results %>%
+CB_stab_data <- CB_data %>%
+  group_by(CB_var_gmax_s, CB_var_h_s,
+           SB_var_gmax_s, SB_var_h_s,
+           PB_var_gmax_s, PB_var_h_s) %>%
+  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
+results2 <- unnest(CB_stab_data, cols = c(stability_measures))  %>%
+  mutate(var_treat = "CB",
+         var_gmax = CB_var_gmax_s)
+
+SB_stab_data <- SB_data %>%
+  group_by(CB_var_gmax_s, CB_var_h_s,
+           SB_var_gmax_s, SB_var_h_s,
+           PB_var_gmax_s, PB_var_h_s) %>%
+  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
+results3 <- unnest(SB_stab_data, cols = c(stability_measures))  %>%
+  mutate(var_treat = "SB",
+         var_gmax = SB_var_gmax_s)
+
+PB_stab_data <- PB_data %>%
+  group_by(CB_var_gmax_s, CB_var_h_s,
+           SB_var_gmax_s, SB_var_h_s,
+           PB_var_gmax_s, PB_var_h_s) %>%
+  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
+results4 <- unnest(PB_stab_data, cols = c(stability_measures))  %>%
+  mutate(var_treat = "PB",
+         var_gmax = PB_var_gmax_s)
+
+SBPB_stab_data <- SBPB_data %>%
+  group_by(CB_var_gmax_s, CB_var_h_s,
+           SB_var_gmax_s, SB_var_h_s,
+           PB_var_gmax_s, PB_var_h_s) %>%
+  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
+results5 <- unnest(SBPB_stab_data, cols = c(stability_measures))  %>%
+  mutate(var_treat = "SBPB",
+         var_gmax = SB_var_gmax_s)
+
+all_stab_results <- results1 %>%
+  bind_rows(results2) %>%
+  bind_rows(results3) %>%
+  bind_rows(results4) %>%
+  bind_rows(results5)
+
+all_stab_results %>%
   filter(Species == "O") %>%
-  ggplot(aes(x = CB_var_gmax_s, y = hyst_range)) +
-  geom_point()
+  ggplot(aes(x = var_gmax, y = hyst_range, col=var_treat)) +
+  geom_jitter()
+
+all_stab_results %>%
+  #filter(var_treat == "CB") %>%
+  filter(Species == "O") %>%
+  ggplot(aes(x = var_gmax,
+             ymin = hyst_min,
+             ymax = hyst_max,
+             fill=var_treat)) +
+  geom_ribbon(alpha = 0.5) +
+  facet_wrap( ~ var_treat)
 

### 2021-06-22 simulations/experiment_framework.R

@@ -14,7 +14,7 @@ library(patchwork)
 library(here)
 source(here("simulations/r functions/various_useful_functions.r"))
 
-options(mc.cores = 16)
+options(mc.cores = 8)
 
 ## Initialise general simulation conditions ----
 default_dynamic_model <- bushplus_dynamic_model
@@ -43,7 +43,7 @@ names(ssfind_minimum_abundances) <- c("CB", "PB", "SB")
 ssfind_simulation_duration <- default_sim_duration
 ssfind_simulation_sampling_interval <- ssfind_simulation_duration
 ssfind_event_interval <- ssfind_simulation_duration
-grid_num_a <- 1000 ## number of a_0 values
+grid_num_a <- 20 ## number of a_0 values
 a_Os <- 10^seq(-7, -1, length=grid_num_a) ## sequence of a_0 values
 grid_num_N <- 2 ## number of N values
 initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
@@ -58,7 +58,7 @@ ss_expt <- expand.grid(N_CB = initial_CBs,
 
 
 ## Gradient CB, SB, PB variation  experiment ----
-var_length <- 20
+var_length <- 2
 CB_var_gmax_s <- seq(0, 0.1, length=var_length) * 0.15789474
 CB_var_h_s = seq(0, -0.5, length=var_length) * 0.15789474
 SB_var_gmax_s <- seq(0, 0.1, length=var_length)
@@ -70,7 +70,7 @@ saveRDS(var_expt, here("simulations/sim data/ss_res_grad_CBSBPB_var.RDS"))
 
 
 ## Gradient CB variation  experiment ----
-var_length <- 20
+#var_length <- 20
 CB_var_gmax_s <- seq(0, 0.1, length=var_length) * 0.15789474
 CB_var_h_s <- seq(0, -0.5, length=var_length) * 0.15789474
 SB_var_gmax_s <- 0 ## seq(0, 0.1, length=var_length)
@@ -82,7 +82,7 @@ saveRDS(var_expt, here("simulations/sim data/ss_res_grad_CB_var.RDS"))
 
 
 ## Gradient SB variation  experiment ----
-var_length <- 20
+#var_length <- 20
 CB_var_gmax_s <- 0 ##seq(0, 0.1, length=var_length) * 0.15789474
[…]

### 2021-06-23 manuscript/article.Rmd
new var pars

@@
 ```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
-result_index2 <- 2
+result_index2 <- 20
 p2  <- plot_ss_result1(CBSBPB_data,

### 2021-06-23 simulations/experiment_framework.R

@@ -43,7 +43,7 @@ names(ssfind_minimum_abundances) <- c("CB", "PB", "SB")
 ssfind_simulation_duration <- default_sim_duration
 ssfind_simulation_sampling_interval <- ssfind_simulation_duration
 ssfind_event_interval <- ssfind_simulation_duration
-grid_num_a <- 20 ## number of a_0 values
+grid_num_a <- 1000 ## number of a_0 values
 a_Os <- 10^seq(-7, -1, length=grid_num_a) ## sequence of a_0 values
 grid_num_N <- 2 ## number of N values
 initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
@@ -58,15 +58,33 @@ ss_expt <- expand.grid(N_CB = initial_CBs,
 
 
 ## Gradient CB, SB, PB variation  experiment ----
-var_length <- 2
+var_length <- 20
 CB_var_gmax_s <- seq(0, 0.1, length=var_length) * 0.15789474
 CB_var_h_s = seq(0, -0.5, length=var_length) * 0.15789474
-SB_var_gmax_s <- seq(0, 0.1, length=var_length)
-SB_var_h_s = seq(0, -0.5, length=var_length)
-PB_var_gmax_s <- seq(0, 0.1, length=var_length)
-PB_var_h_s = seq(0, -0.5, length=var_length)
+SB_var_gmax_s <- seq(0, 0.1, length=var_length) * 0.15789474
+SB_var_h_s = seq(0, -0.5, length=var_length) *  0.15789474
+PB_var_gmax_s <- seq(0, 0.1, length=var_length) *  0.15789474
+PB_var_h_s = seq(0, -0.5, length=var_length) *  0.15789474
 var_expt <- run_ss_var_experiment()
 saveRDS(var_expt, here("simulations/sim data/ss_res_grad_CBSBPB_var.RDS"))
+
+# CBSBPB_data <- readRDS(here("simulations/sim data/ss_res_grad_CBSBPB_var.RDS"))
+# result_index1 <- 1
+# p1  <- plot_ss_result1(CBSBPB_data,
+#                        result_index = result_index1,
+#                        filename_prefix = NULL,
+#                        save_image_file = FALSE)
+# p1
+# result_index2 <- 2
+# p2  <- plot_ss_result1(CBSBPB_data,
[…]

### 2021-06-23 simulations/tests.R

@@ -1,0 +1,569 @@
+## Setup R ----
+
+rm(list = ls())
+
+# devtools::install_github("opetchey/microxanox",
+#                              ref="main",
+#                              auth_token = "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",
+#                              build_vignettes = FALSE,
+#                              force = TRUE)
+
+library(tidyverse)
+library(microxanox)
+library(patchwork)
+library(here)
+source(here("simulations/r functions/various_useful_functions.r"))
+
+options(mc.cores = 8)
+
+## Initialise general simulation conditions ----
+default_dynamic_model <- bushplus_dynamic_model
+default_event_definition <- event_definition_1
+## no default parameter values
+default_event_interval <- 100
+default_noise_sigma <- 0
+default_minimum_abundances <- rep(0, 3)
+names(default_minimum_abundances) <- c("CB", "PB", "SB") 
+default_sim_duration <- 10000
+default_sim_sample_interval <- 10
+## note that next line (log10a_series is over-ridden with getting stable states)
+#default_log10a_series <- c(-2, -2, -2, -2, -10, -10, -10, -10, -10)
+num_CB_strains <- 9
+num_SB_strains <- 9
+num_PB_strains <- 9
+default_9strain <- new_starter(n_CB = num_CB_strains,
+                             n_SB = num_SB_strains,
+                             n_PB = num_PB_strains,
+                             values_initial_state = "bush_ssfig3")
+
+
+## Initialise general steady state finding setting ----
+ssfind_minimum_abundances <- rep(0, 3)
+names(ssfind_minimum_abundances) <- c("CB", "PB", "SB") 
+ssfind_simulation_duration <- default_sim_duration
+ssfind_simulation_sampling_interval <- ssfind_simulation_duration
+ssfind_event_interval <- ssfind_simulation_duration
+grid_num_a <- 20 ## number of a_0 values
+#a_Os <- 10^seq(-7, -1, length=grid_num_a) ## sequence of a_0 values
+a_Os <- 10^-5 ## sequence of a_0 values
[…]

### 2021-06-24 manuscript/article.Rmd
made two experiments

--- 2021-06-21 manuscript/article.Rmd
@@
 
-```{r ss_novar, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
-CBSBPB_data <- readRDS(here("simulations/sim data/ss_res_grad_CBSBPB_var.RDS"))
-
-ss_exp_result <- CBSBPB_data
-result_index <- 1
-
+```{r ss_novar, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("No diversity"), echo=FALSE}
+CBSBPB_data <- readRDS(here("simulations/expt1/data/ss_res_grad_CBSBPB_var.RDS"))
+result_index1 <- 1
 p1  <- plot_ss_result1(CBSBPB_data,
-                result_index = 1,
+                result_index = result_index1,
                 filename_prefix = NULL,
@@
 
-```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
-p2  <- plot_ss_result1(tmp2$ss_res[[1]],
-                tmp2$CB_var_gmax_s,
-                tmp2$CB_var_h_s,
-                tmp2$SB_var_gmax_s,
-                tmp2$SB_var_h_s,
-                tmp2$PB_var_gmax_s,
-                tmp2$PB_var_h_s,
+```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in all functional groups"), echo=FALSE}
+result_index2 <- 20
+p2  <- plot_ss_result1(CBSBPB_data,
+                result_index = result_index2,
                 filename_prefix = NULL,
@@
 
-```{r ss_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("CBSBPB var"), echo=FALSE}
-
-#ss_result1 <- ss_novar$ss_res[[1]]
-#ss_result2 <- ss_var$ss_res[[1]]
-
-p_overlay <- plot_ss_result2(tmp1$ss_res[[1]],
-                             tmp2$ss_res[[1]],
+```{r ss_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in none (solid) and all functional groups."), echo=FALSE}
+p_overlay <- plot_ss_result2(CBSBPB_data[result_index1,]$ss_res[[1]],
+                             CBSBPB_data[result_index2,]$ss_res[[1]],
                              xlims = c(-7, -1))
-
 p_overlay
@@
 
-```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
-CB_data <- readRDS(here("simulations/sim data/ss_res_grad_CB_var.RDS"))
-tmp3 <- CB_data[20,]
-
-p2  <- plot_ss_result1(tmp3$ss_res[[1]],
-                tmp3$CB_var_gmax_s,
-                tmp3$CB_var_h_s,
-                tmp3$SB_var_gmax_s,
-                tmp3$SB_var_h_s,
-                tmp3$PB_var_gmax_s,
-                tmp3$PB_var_h_s,
+```{r CB_var1, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in CB functional group."), echo=FALSE}
+CB_data <- readRDS(here("simulations/expt1/data/ss_res_grad_CB_var.RDS"))
+p3  <- plot_ss_result1(CB_data,
+                result_index = result_index2,
                 filename_prefix = NULL,
                 save_image_file = FALSE)
-p2
+p3
+```
+
+```{r CB_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in none (solid) and CB functional groups."), echo=FALSE}
+p_overlay <- plot_ss_result2(CB_data[result_index1,]$ss_res[[1]],
+                             CB_data[result_index2,]$ss_res[[1]],
+                             xlims = c(-7, -1))
+p_overlay
+```
+
+## Figure: SB Stable states with variation and tradeoff
+
+```{r SB_var1, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in SB functional group."), echo=FALSE}
+SB_data <- readRDS(here("simulations/expt1/data/ss_res_grad_SB_var.RDS"))
+p4  <- plot_ss_result1(SB_data,
+                result_index = result_index2,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p4
 
@@
 
-X-axis must be labelled log10(a).
-
-```{r ss_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("CBSBPB var"), echo=FALSE}
-
-#ss_result1 <- ss_novar$ss_res[[1]]
-#ss_result2 <- ss_var$ss_res[[1]]
-
-p_overlay <- plot_ss_result2(tmp1$ss_res[[1]],
-                             tmp3$ss_res[[1]],
+```{r SB_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in none (solid) and SB functional group."), echo=FALSE}
+p_overlay <- plot_ss_result2(CB_data[result_index1,]$ss_res[[1]],
+                             SB_data[result_index2,]$ss_res[[1]],
                              xlims = c(-7, -1))
@@
 
-X-axis must be labelled log10(a).
+## Figure: PB Stable states with variation and tradeoff
 
-## Figure: SB Stable states with variation and tradeoff
-
-```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
-SB_data <- readRDS(here("simulations/sim data/ss_res_grad_SB_var.RDS"))
-tmp4 <- SB_data[20,]
-
-p2  <- plot_ss_result1(tmp4$ss_res[[1]],
-                tmp4$CB_var_gmax_s,
-                tmp4$CB_var_h_s,
-                tmp4$SB_var_gmax_s,
-                tmp4$SB_var_h_s,
-                tmp4$PB_var_gmax_s,
-                tmp4$PB_var_h_s,
+```{r PB_var1, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in PB functional group."), echo=FALSE}
+PB_data <- readRDS(here("simulations/expt1/data/ss_res_grad_PB_var.RDS"))
+p5  <- plot_ss_result1(PB_data,
+                result_index = result_index2,
                 filename_prefix = NULL,
                 save_image_file = FALSE)
-p2
+p5
 
@@
 
-X-axis must be labelled log10(a).
-
-```{r ss_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("CBSBPB var"), echo=FALSE}
-
-#ss_result1 <- ss_novar$ss_res[[1]]
-#ss_result2 <- ss_var$ss_res[[1]]
-
-p_overlay <- plot_ss_result2(tmp1$ss_res[[1]],
-                             tmp4$ss_res[[1]],
+```{r PB_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in none (solid) and PB functional group."), echo=FALSE}
+p_overlay <- plot_ss_result2(CB_data[result_index1,]$ss_res[[1]],
+                             PB_data[result_index2,]$ss_res[[1]],
                              xlims = c(-7, -1))
@@
 
-X-axis must be labelled log10(a).
+## Figure: SBPB Stable states with variation and tradeoff
+
+```{r SBPB_var1, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in SB and PB functional groups."), echo=FALSE}
+SBPB_data <- readRDS(here("simulations/expt1/data/ss_res_grad_SBPB_var.RDS"))
+p6  <- plot_ss_result1(SBPB_data,
+                result_index = result_index2,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p6
+
+```
+
+```{r SBPB_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in none (solid) and SB and PB functional groups."), echo=FALSE}
+p_overlay <- plot_ss_result2(CB_data[result_index1,]$ss_res[[1]],
+                             SBPB_data[result_index2,]$ss_res[[1]],
+                             xlims = c(-7, -1))
+
+p_overlay
+```
 
@@
 
-```{r ss_var3, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
-#ss_sim_data <- readRDS(here("simulations/sim data/ss_res_3.RDS"))
+```{r echo=FALSE, eval = FALSE}
+#ss_sim_data <- readRDS(here("simulations/expt1/data/ss_res_3.RDS"))
 
-CBSBPB_data <- CBSBPB_data %>%
+CBSBPB_stab_data <- CBSBPB_data %>%
   group_by(CB_var_gmax_s, CB_var_h_s,
@@
   do(stability_measures = get_stability_measures(.$ss_res[[1]]))
-results <- unnest(CBSBPB_data, cols = c(stability_measures))
+results1 <- unnest(CBSBPB_stab_data, cols = c(stability_measures)) %>%
+  mutate(var_treat = "CB-SB-PB",
+         var_gmax = CB_var_gmax_s)
 
-results %>%
+CB_stab_data <- CB_data %>%
+  group_by(CB_var_gmax_s, CB_var_h_s,
+           SB_var_gmax_s, SB_var_h_s,
+           PB_var_gmax_s, PB_var_h_s) %>%
+  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
+results2 <- unnest(CB_stab_data, cols = c(stability_measures))  %>%
+  mutate(var_treat = "CB",
+         var_gmax = CB_var_gmax_s)
+
+SB_stab_data <- SB_data %>%
+  group_by(CB_var_gmax_s, CB_var_h_s,
+           SB_var_gmax_s, SB_var_h_s,
+           PB_var_gmax_s, PB_var_h_s) %>%
+  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
+
+# for(i in 1:20) {
+#   print(i)
+#   junk <- get_stability_measures(SB_data$ss_res[[i]])
+# }
+# ss_object <- SB_data$ss_res[[11]]
+# 
+# temp2 <- filter(temp, Species == "PB_1")
+# get_hysteresis_total(log10(temp2$up+1), log10(temp2$down+1))
+# down <- log10(temp2$down+1)
+# up <- log10(temp2$up+1)
+#
+
+results3 <- unnest(SB_stab_data, cols = c(stability_measures))  %>%
+  mutate(var_treat = "SB",
+         var_gmax = SB_var_gmax_s)
+
+PB_stab_data <- PB_data %>%
+  group_by(CB_var_gmax_s, CB_var_h_s,
+           SB_var_gmax_s, SB_var_h_s,
+           PB_var_gmax_s, PB_var_h_s) %>%
+  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
+results4 <- unnest(PB_stab_data, cols = c(stability_measures))  %>%
+  mutate(var_treat = "PB",
+         var_gmax = PB_var_gmax_s)
+
+SBPB_stab_data <- SBPB_data %>%
+  group_by(CB_var_gmax_s, CB_var_h_s,
+           SB_var_gmax_s, SB_var_h_s,
+           PB_var_gmax_s, PB_var_h_s) %>%
+  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
+results5 <- unnest(SBPB_stab_data, cols = c(stability_measures))  %>%
+  mutate(var_treat = "SB-PB",
+         var_gmax = SB_var_gmax_s)
+
+all_stab_results <- results1 %>%
+  bind_rows(results2) %>%
+  bind_rows(results3) %>%
+  bind_rows(results4) %>%
+  bind_rows(results5)
+
+all_stab_results<- all_stab_results %>%
+  mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB", "PB", "SB-PB", "CB-SB-PB")))
+
+saveRDS(all_stab_results, here("simulations/sim data/stab_measures.RDS"))
+
+```
+
+```{r ss_var3, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
+
+all_stab_results <- readRDS(here("simulations/expt1/data/stab_measures.RDS"))
+
+all_stab_results %>%
   filter(Species == "O") %>%
-  ggplot(aes(x = CB_var_gmax_s, y = hyst_range)) +
-  geom_point()
+  ggplot(aes(x = var_gmax, y = hyst_range, col=var_treat)) +
+  geom_point() +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
+  labs(col = "Community\ncomposition")
+```
+
+```{r ss_var4, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
+all_stab_results %>%
+  #filter(var_treat == "CB") %>%
+  filter(Species == "O") %>%
+  ggplot(aes(x = var_gmax,
+             ymin = hyst_min,
+             ymax = hyst_max,
+             fill=var_treat)) +
+  geom_ribbon(alpha = 0.5) +
+  facet_wrap( ~ var_treat) +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
+  labs(fill = "Community\ncomposition")
 

### 2021-06-24 manuscript/article.tex
made two experiments

@@
 % For Pandoc 2.11+
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
  {% don't indent paragraphs
@@
 \newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
@@
   environmental driver (i.e.~may cause lower resilience) (Figure 2c in
-  @dakos2019b). This could occur if there is selection for greater
-  tolerance that causes, incidentally, selection for lower growth rate,
-  perhaps due to a tradeoff between the two traits.
+  Dakos et al. (2019)). This could occur if there is selection for
+  greater tolerance that causes, incidentally, selection for lower
+  growth rate, perhaps due to a tradeoff between the two traits.
 \item
@@
   Variation in amount of among strain variation, no variation in number
-  of strains, no variation in strength or shape of the of the tradeoff.
+  of strains, no variation in strength or shape of the of any tradeoff.
 \item
@@
 different parameter values (e.g.~maximum growth rate and tolerance
-parameter) the dynamics of the strains in a functional were described by
-the same equations. Hence, when parameterised with multiple strains per
-functional group, but no variation among strains (within functional
+parameters) the dynamics of the strains in a functional were described
+by the same equations. Hence, when parameterised with multiple strains
+per functional group, but no variation among strains (within functional
 groups), the system behaves identically to when there is only one strain
@@
 
-\caption{your caption}\label{fig:ss_novar}
+\caption{No diversity}\label{fig:ss_novar}
 \end{figure}
@@
 
-\hypertarget{figure-stable-states-with-variation-and-tradeoff}{%
-\subsection{Figure: Stable states with variation and
-tradeoff}\label{figure-stable-states-with-variation-and-tradeoff}}
+\hypertarget{figure-cbsbpb-stable-states-with-variation-and-tradeoff}{%
+\subsection{Figure: CBSBPB Stable states with variation and
+tradeoff}\label{figure-cbsbpb-stable-states-with-variation-and-tradeoff}}
 
@@
 
-\caption{your caption}\label{fig:ss_var}
+\caption{Diversity in all functional groups}\label{fig:ss_var}
 \end{figure}
@@
 
-\caption{your caption}\label{fig:ss_var2}
+\caption{Diversity in none (solid) and all functional groups.}\label{fig:ss_var2}
 \end{figure}
@@
 X-axis must be labelled log10(a).
+
+\hypertarget{figure-cb-stable-states-with-variation-and-tradeoff}{%
+\subsection{Figure: CB Stable states with variation and
+tradeoff}\label{figure-cb-stable-states-with-variation-and-tradeoff}}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/CB_var1-1}
+
+}
+
+\caption{Diversity in CB functional group.}\label{fig:CB_var1}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/CB_var2-1}
+
+}
+
+\caption{Diversity in none (solid) and CB functional groups.}\label{fig:CB_var2}
+\end{figure}
+
+\hypertarget{figure-sb-stable-states-with-variation-and-tradeoff}{%
+\subsection{Figure: SB Stable states with variation and
+tradeoff}\label{figure-sb-stable-states-with-variation-and-tradeoff}}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/SB_var1-1}
+
+}
+
+\caption{Diversity in SB functional group.}\label{fig:SB_var1}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/SB_var2-1}
+
+}
+
+\caption{Diversity in none (solid) and SB functional group.}\label{fig:SB_var2}
+\end{figure}
+
+\hypertarget{figure-pb-stable-states-with-variation-and-tradeoff}{%
+\subsection{Figure: PB Stable states with variation and
+tradeoff}\label{figure-pb-stable-states-with-variation-and-tradeoff}}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/PB_var1-1}
+
+}
+
+\caption{Diversity in PB functional group.}\label{fig:PB_var1}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/PB_var2-1}
+
+}
+
+\caption{Diversity in none (solid) and PB functional group.}\label{fig:PB_var2}
+\end{figure}
+
+\hypertarget{figure-sbpb-stable-states-with-variation-and-tradeoff}{%
+\subsection{Figure: SBPB Stable states with variation and
+tradeoff}\label{figure-sbpb-stable-states-with-variation-and-tradeoff}}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/SBPB_var1-1}
+
+}
+
+\caption{Diversity in SB and PB functional groups.}\label{fig:SBPB_var1}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/SBPB_var2-1}
+
+}
+
+\caption{Diversity in none (solid) and SB and PB functional groups.}\label{fig:SBPB_var2}
+\end{figure}
 
@@
 
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/ss_var4-1}
+
+}
+
+\caption{your caption}\label{fig:ss_var4}
+\end{figure}
+
 \hypertarget{figure-temporal-switches}{%
@@
 
-To be added. Need to go both ways (oxic to anoxic, and anoxic to oxic).
+Maybe\ldots{} to be added. Need to go both ways (oxic to anoxic, and
+anoxic to oxic).
 
@@
 stability?
+
+\hypertarget{further-relaxing-the-assumptions}{%
+\subsection{Further relaxing the
+assumptions}\label{further-relaxing-the-assumptions}}
+
+Deterministic -\textgreater{} stochastic :
+www.pnas.org/cgi/doi/10.1073/pnas.1414708112
 

### 2021-06-24 simulations/expt1/experiment_framework.R

@@ -1,0 +1,559 @@
+## Setup R ----
+
+rm(list = ls())
+
+# devtools::install_github("opetchey/microxanox",
+#                              ref="main",
+#                              auth_token = "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",
+#                              build_vignettes = FALSE,
+#                              force = TRUE)
+# 
+library(tidyverse)
+library(microxanox)
+library(patchwork)
+library(here)
+source(here("simulations/r functions/various_useful_functions.r"))
+
+options(mc.cores = 8)
+
+## Initialise general simulation conditions ----
+default_dynamic_model <- bushplus_dynamic_model
+default_event_definition <- event_definition_1
+## no default parameter values
+default_event_interval <- 100
+default_noise_sigma <- 0
+default_minimum_abundances <- rep(0, 3)
+names(default_minimum_abundances) <- c("CB", "PB", "SB") 
+default_sim_duration <- 100000
+default_sim_sample_interval <- 10
+## note that next line (log10a_series is over-ridden with getting stable states)
+#default_log10a_series <- c(-2, -2, -2, -2, -10, -10, -10, -10, -10)
+num_CB_strains <- 9
+num_SB_strains <- 9
+num_PB_strains <- 9
+default_9strain <- new_starter(n_CB = num_CB_strains,
+                             n_SB = num_SB_strains,
+                             n_PB = num_PB_strains,
+                             values_initial_state = "bush_ssfig3")
+
+
+## Initialise general steady state finding setting ----
+ssfind_minimum_abundances <- rep(0, 3)
+names(ssfind_minimum_abundances) <- c("CB", "PB", "SB") 
+ssfind_simulation_duration <- default_sim_duration
+ssfind_simulation_sampling_interval <- ssfind_simulation_duration
+ssfind_event_interval <- ssfind_simulation_duration
+grid_num_a <- 1000 ## number of a_0 values
+a_Os <- 10^seq(-7, -1, length=grid_num_a) ## sequence of a_0 values
+grid_num_N <- 2 ## number of N values
[…]

### 2021-06-24 simulations/expt1/temporal_switching_experiments.R

@@ -1,0 +1,642 @@
+## Setup R ----
+
+rm(list = ls())
+
+# devtools::install_github("opetchey/microxanox",
+#                              ref="main",
+#                              auth_token = "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",
+#                              build_vignettes = FALSE,
+#                              force = TRUE)
+
+library(tidyverse)
+library(microxanox)
+library(patchwork)
+library(here)
+source(here("simulations/r functions/various_useful_functions.r"))
+
+options(mc.cores = 8)
+
+## Initialise general simulation conditions ----
+default_dynamic_model <- bushplus_dynamic_model
+default_event_definition <- event_definition_1
+## no default parameter values
+default_event_interval <- 100
+default_noise_sigma <- 0
+default_minimum_abundances <- rep(10000, 3)
+names(default_minimum_abundances) <- c("CB", "PB", "SB") 
+default_sim_duration <- 50000
+default_sim_sample_interval <- 100
+## note that next line (log10a_series is over-ridden with getting stable states)
+#default_log10a_series <- c(-2, -2, -2, -2, -10, -10, -10, -10, -10)
+num_CB_strains <- 9
+num_SB_strains <- 9
+num_PB_strains <- 9
+default_9strain <- new_starter(n_CB = num_CB_strains,
+                             n_SB = num_SB_strains,
+                             n_PB = num_PB_strains,
+                             values_initial_state = "bush_ssfig3")
+
+
+## Initialise general steady state finding setting ----
+#ssfind_minimum_abundances <- rep(0, 3)
+#names(ssfind_minimum_abundances) <- c("CB", "PB", "SB") 
+#ssfind_simulation_duration <- default_sim_duration
+#ssfind_simulation_sampling_interval <- ssfind_simulation_duration
+#ssfind_event_interval <- ssfind_simulation_duration
+#grid_num_a <- 20 ## number of a_0 values
+#a_Os <- 10^seq(-7, -1, length=grid_num_a) ## sequence of a_0 values
+#grid_num_N <- 2 ## number of N values
+#initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
[…]

### 2021-06-24 simulations/expt2/temporal_switching_experiments.R

@@ -1,0 +1,642 @@
+## Setup R ----
+
+rm(list = ls())
+
+# devtools::install_github("opetchey/microxanox",
+#                              ref="main",
+#                              auth_token = "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",
+#                              build_vignettes = FALSE,
+#                              force = TRUE)
+
+library(tidyverse)
+library(microxanox)
+library(patchwork)
+library(here)
+source(here("simulations/r functions/various_useful_functions.r"))
+
+options(mc.cores = 8)
+
+## Initialise general simulation conditions ----
+default_dynamic_model <- bushplus_dynamic_model
+default_event_definition <- event_definition_1
+## no default parameter values
+default_event_interval <- 100
+default_noise_sigma <- 0
+default_minimum_abundances <- rep(10000, 3)
+names(default_minimum_abundances) <- c("CB", "PB", "SB") 
+default_sim_duration <- 50000
+default_sim_sample_interval <- 100
+## note that next line (log10a_series is over-ridden with getting stable states)
+#default_log10a_series <- c(-2, -2, -2, -2, -10, -10, -10, -10, -10)
+num_CB_strains <- 9
+num_SB_strains <- 9
+num_PB_strains <- 9
+default_9strain <- new_starter(n_CB = num_CB_strains,
+                             n_SB = num_SB_strains,
+                             n_PB = num_PB_strains,
+                             values_initial_state = "bush_ssfig3")
+
+
+## Initialise general steady state finding setting ----
+#ssfind_minimum_abundances <- rep(0, 3)
+#names(ssfind_minimum_abundances) <- c("CB", "PB", "SB") 
+#ssfind_simulation_duration <- default_sim_duration
+#ssfind_simulation_sampling_interval <- ssfind_simulation_duration
+#ssfind_event_interval <- ssfind_simulation_duration
+#grid_num_a <- 20 ## number of a_0 values
+#a_Os <- 10^seq(-7, -1, length=grid_num_a) ## sequence of a_0 values
+#grid_num_N <- 2 ## number of N values
+#initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
[…]

### 2021-06-25 experiments/experiment 1/experiment 1.Rmd
changed to experiment as a unit

---
title: "Experiment 1"
author: "Owen Petchey"
date: "6/25/2021"
output: html_document
---

# Setup

## R

```{r}

rm(list = ls())

knitr::opts_knit$set(progress = TRUE, verbose = TRUE, cache = TRUE)

# devtools::install_github("opetchey/microxanox",
#                              ref="main",
#                              auth_token = "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",
#                              build_vignettes = FALSE,
#                              force = TRUE)

library(tidyverse)
library(microxanox)
library(patchwork)
library(here)
source(here("simulations/r functions/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
options(mc.cores = 8)
```

## General simulation conditions

```{r}
default_dynamic_model <- bushplus_dynamic_model
default_event_definition <- event_definition_1
default_event_interval <- 100
default_noise_sigma <- 0
default_minimum_abundances <- rep(1, 3)
names(default_minimum_abundances) <- c("CB", "PB", "SB") 
default_sim_duration <- 80000
default_sim_sample_interval <- 100
initial_pars_from <- "bush_ssfig3"
## note that next line (log10a_series is over-ridden with getting stable states)
#default_log10a_series <- c(-2, -2, -2, -2, -10, -10, -10, -10, -10)
```

## Define diversity

```{r}
num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9
CB_var_range <- 0.015789474
CB_var_TO <- -5
SB_var_range <- 0.015789474
SB_var_TO <- -20.5
PB_var_range <- 0.015789474
PB_var_TO <- -20.5

num_div_treatment_levels <- 2
```

## Create diversity

```{r}
default_9strain <- new_starter(n_CB = num_CB_strains,
                             n_SB = num_SB_strains,
                             n_PB = num_PB_strains,
                             values_initial_state = initial_pars_from)
CB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * CB_var_range
CB_var_h_s = seq(zero, CB_var_TO, length=num_div_treatment_levels) * CB_var_range
SB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * SB_var_range
SB_var_h_s = seq(zero, SB_var_TO, length=num_div_treatment_levels) * SB_var_range
PB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * PB_var_range
PB_var_h_s = seq(zero, PB_var_TO, length=num_div_treatment_levels) * PB_var_range
var_expt <- tibble(CB_var_gmax_s,
                   CB_var_h_s,
                   SB_var_gmax_s,
                   SB_var_h_s,
                   PB_var_gmax_s,
                   PB_var_h_s)
var_expt <- var_expt %>%
  nest_by(CB_var_gmax_s, CB_var_h_s,
          SB_var_gmax_s, SB_var_h_s,
          PB_var_gmax_s, PB_var_h_s) %>%
  mutate(pars = list(add_strain_var(default_9strain,
                                    CB_var_gmax = CB_var_gmax_s,
                                    CB_var_h = CB_var_h_s,
                                    SB_var_gmax = SB_var_gmax_s,
                                    SB_var_h = SB_var_h_s,
                                    PB_var_gmax = PB_var_gmax_s,
                                    PB_var_h = PB_var_h_s)))
```

## Display diversity

```{r}

CBtraits <- var_expt$pars[[num_div_treatment_levels]]$CB
P <- 1 #10^seq(-5, 5, 0.1)
SR <- 10^seq(0, 3, 0.1)
gr_rateCB1 <- growth1(P, CBtraits$g_max_CB[1], CBtraits$k_CB_P[1]) * inhibition(SR, CBtraits$h_SR_CB[1])
gr_rateCB9 <- growth1(P, CBtraits$g_max_CB[num_CB_strains], CBtraits$k_CB_P[num_CB_strains]) * inhibition(SR, CBtraits$h_SR_CB[num_CB_strains])

CB_TO1 <- ggplot() +
  geom_point(aes(x = CBtraits$h_SR_CB, y = CBtraits$g_max_CB))
CB_TO2 <- ggplot() +
  geom_line(aes( x = log10(SR), y = gr_rateCB1)) +
  geom_line(aes( x = log10(SR), y = gr_rateCB9), col = "blue")

SBtraits <- var_expt$pars[[num_div_treatment_levels]]$SB
P <- 1 #10^seq(-5, 5, 0.1)
SO <- 1
O <- 10^seq(-2.5, 2.5, 0.1)
gr_rateSB1 <- growth2(P, SO, SBtraits$g_max_SB[1], SBtraits$k_SB_P[1], SBtraits$k_SB_SO[1]) *
  inhibition(O, SBtraits$h_O_SB[1])
gr_rateSB9 <- growth2(P, SO, SBtraits$g_max_SB[9], SBtraits$k_SB_P[9], SBtraits$k_SB_SO[9]) *
  inhibition(O, SBtraits$h_O_SB[9])

SB_TO1 <- ggplot() +
  geom_point(aes(x = SBtraits$h_O_SB, y = SBtraits$g_max_SB))
SB_TO2 <- ggplot() +
  geom_line(aes( x = log10(O), y = gr_rateSB1)) +
  geom_line(aes( x = log10(O), y = gr_rateSB9), col = "blue")

PBtraits <- var_expt$pars[[num_div_treatment_levels]]$PB
P <- 1 #10^seq(-5, 5, 0.1)
SO <- 1
O <- 10^seq(-2.5, 2.5, 0.1)
gr_ratePB1 <- growth2(P, SO, PBtraits$g_max_PB[1], PBtraits$k_PB_P[1], PBtraits$k_PB_SR[1]) *
  inhibition(O, PBtraits$h_O_PB[1])
gr_ratePB9 <- growth2(P, SO, PBtraits$g_max_PB[9], PBtraits$k_PB_P[9], PBtraits$k_PB_SR[9]) *
  inhibition(O, PBtraits$h_O_PB[9])

PB_TO1 <- ggplot() +
  geom_point(aes(x = PBtraits$h_O_PB, y = PBtraits$g_max_PB))
PB_TO2 <- ggplot() +
  geom_line(aes( x = log10(O), y = gr_ratePB1)) +
  geom_line(aes( x = log10(O), y = gr_ratePB9), col = "blue")

(CB_TO1 + SB_TO1 + PB_TO1) / (CB_TO2 + SB_TO2 + PB_TO2)
```

# Temporal switching

## Oxic to anoxic

### No diversity

```{r}
default_sim_duration <- 80000
```

```{r}
sim_number <- 1
default_log10a_series <- c(-1, -7, -7)
initial_state <- new_initial_state(num_CB_strains,
                                   num_PB_strains,
                                   num_SB_strains,
                                   values = "bush_ssfig3")
initial_state[grep("CB_", names(initial_state))] <- 10^10/num_CB_strains
sim_res_novar <- run_simulation(parameter_values = var_expt$pars[[sim_number]],
                          initial_state = initial_state)
plot_dynamics(sim_res_novar)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

### Maximum diversity

```{r}
sim_number <- 2
sim_res_highvar <- run_simulation(parameter_values = var_expt$pars[[sim_number]],
                          initial_state = initial_state)
plot_dynamics(sim_res_highvar)
#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)

```

## Anoxic to oxic

### No diversity

```{r}
default_sim_duration <- 60000
```

```{r}
sim_number <- 1
default_log10a_series <- c(-5, -3, -1, -1)
initial_state <- new_initial_state(num_CB_strains,
                                   num_PB_strains,
                                   num_SB_strains,
                                   values = "bush_ssfig3")
initial_state[grep("CB_", names(initial_state))] <- 10/num_CB_strains
sim_res_novar <- run_simulation(parameter_values = var_expt$pars[[sim_number]],
                          initial_state = initial_state)
plot_dynamics(sim_res_novar)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

### Maximum diversity

```{r}
sim_number <- 2
sim_res_highvar <- run_simulation(parameter_values = var_expt$pars[[sim_number]],
                          initial_state = initial_state)
plot_dynamics(sim_res_highvar)
#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)

```

## Anoxic to oxic to anoxic

### No diversity

```{r}
default_sim_duration <- 100000
```

```{r}
default_minimum_abundances <- rep(1000, 3)
names(default_minimum_abundances) <- c("CB", "PB", "SB") 
```

```{r}
sim_number <- 1
default_log10a_series <- c(-1, -6, -1)
initial_state <- new_initial_state(num_CB_strains,
                                   num_PB_strains,
                                   num_SB_strains,
                                   values = "bush_ssfig3")
initial_state[grep("CB_", names(initial_state))] <- 10/num_CB_strains
sim_res_novar <- run_simulation(parameter_values = var_expt$pars[[sim_number]],
                          initial_state = initial_state)
plot_dynamics(sim_res_novar)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

### Maximum diversity

```{r}
sim_number <- 2
sim_res_highvar <- run_simulation(parameter_values = var_expt$pars[[sim_number]],
                          initial_state = initial_state)
plot_dynamics(sim_res_highvar)
#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)

```

### Visualise

```{r}

tmp_novar <- sim_res_novar$result %>%
  filter(time != 0) %>%
  select(-time) %>%
  mutate(direction = rep(c("down", "up"), each = n()/2)) %>%
  pivot_longer(1:(num_CB_strains+num_SB_strains+num_PB_strains+4),
               names_to = "Species", values_to = "Quantity") %>%
  mutate(var_type=ifelse(grepl("B_", Species), "Organism", "Substrate"),
         functional_group = case_when(str_detect(Species, "CB_") ~ "CB",
                                      str_detect(Species, "SB_") ~ "SB",
                                      str_detect(Species, "PB_") ~ "PB"),
         functional_group = ifelse(is.na(functional_group), Species, functional_group)) %>%
  group_by(functional_group, a, var_type, direction) %>%
  summarise(Total_quantity = sum(Quantity))
tmp_highvar <- sim_res_highvar$result %>%
  filter(time != 0) %>%
  select(-time) %>%
  mutate(direction = rep(c("down", "up"), each = n()/2)) %>%
  pivot_longer(1:(num_CB_strains+num_SB_strains+num_PB_strains+4),
               names_to = "Species", values_to = "Quantity") %>%
  mutate(var_type=ifelse(grepl("B_", Species), "Organism", "Substrate"),
         functional_group = case_when(str_detect(Species, "CB_") ~ "CB",
                                      str_detect(Species, "SB_") ~ "SB",
                                      str_detect(Species, "PB_") ~ "PB"),
         functional_group = ifelse(is.na(functional_group), Species, functional_group)) %>%
  group_by(functional_group, a, var_type, direction) %>%
  summarise(Total_quantity = sum(Quantity))

soi <- "O"
ggplot() +
  geom_path(data = filter(tmp_novar,functional_group == soi),
            aes(x=a, y = log10(Total_quantity), group = direction)) +
  geom_path(data = filter(tmp_highvar,functional_group == soi),
            aes(x=a, y = log10(Total_quantity), group = direction),
            linetype = "dashed", lwd=2, col="red") +
  ggtitle("Solid line is with no intraspecific diversity.\nDashed line is with intraspecific diversity")
ggsave(here("simulations/figures/switching_comparison.pdf"), width = 5, height = 4)

```

# Stable state finding

## Setup

```{r}
options(mc.cores = 8)
```

```{r}
ssfind_minimum_abundances <- rep(0, 3)
names(ssfind_minimum_abundances) <- c("CB", "PB", "SB")
ssfind_simulation_duration <- default_sim_duration
ssfind_simulation_sampling_interval <- ssfind_simulation_duration
ssfind_event_interval <- ssfind_simulation_duration
grid_num_a <- 20 ## number of a_0 values
a_Os <- 10^seq(-7, -1, length=grid_num_a) ## sequence of a_0 values
grid_num_N <- 2 ## number of N values
initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
initial_PBs <- 1e8 ## not varied
initial_SBs <- 1e8 ## not varied
# next line creates all possible combinations
ss_expt <- expand.grid(N_CB = initial_CBs,
                      N_PB = initial_PBs,
                      N_SB = initial_SBs,
                      a_O = a_Os)

```

```{r}
var_expt <- run_ss_var_experiment()
```

```{r}
result_index1 <- 1
p1  <- plot_ss_result1(var_expt,
                result_index = result_index1,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1
```

```{r}
result_index2 <- 2
p2  <- plot_ss_result1(var_expt,
                result_index = result_index2,
                filename_prefix = NULL,
                save_image_file = FALSE)
p2

```

```{r}
p_overlay <- plot_ss_result2(var_expt[result_index1,]$ss_res[[1]],
                             var_expt[result_index2,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay

```

### 2021-06-25 experiments/experiment template/experiment template.Rmd
changed to experiment as a unit

--- 2021-06-25 experiments/experiment 1/experiment 1.Rmd
@@
 library(here)
-source(here("simulations/r functions/various_useful_functions.r"))
+source(here("experiments/r functions/various_useful_functions.r"))
 zero <- 0 ## don't change
@@
 CB_var_TO <- -5
-SB_var_range <- 0.015789474
+SB_var_range <- 0.010
 SB_var_TO <- -20.5
-PB_var_range <- 0.015789474
+PB_var_range <- 0.010
 PB_var_TO <- -20.5
@@
   ggtitle("Solid line is with no intraspecific diversity.\nDashed line is with intraspecific diversity")
-ggsave(here("simulations/figures/switching_comparison.pdf"), width = 5, height = 4)
+##ggsave(here("simulations/figures/switching_comparison.pdf"), width = 5, height = 4)
 

### 2021-06-25 manuscript/article.Rmd
changed to experiment as a unit

@@
 These features are also represented and documented in the `microxanox` R package (**cite the package**).
-Therefore, here we only describe the relatively straightforward extension we used to model multiple strains per functional group.
+Therefore, here we only describe the extension we used to model multiple strains per functional group.
 
@@
 Hence, when parameterised with multiple strains per functional group, but no variation among strains (within functional groups), the system behaves identically to when there is only one strain per functional group (see the `microxanox` R package *User Guide* for a demonstration).
-
 The only other necessary modification was to include summation terms in each of the four ordinary differential equations describing the rates of change of the four chemical substrates.
@@
 In this section we describe how we created variability among the multiple strains within functional groups.
-Since the process was the same for each functional group, we usually do not in this description subscript parameter names by functional group (though there were functional group specific parameters in all simulations).
-The descriptions in this section gradually become more mathematical; the next paragraph alone should provide the information required to understand all other elements of this report.
+Introducing variation among multiple strains within a functional group required a number of decisions:
+
+* **The number of strains.** The symbol for this is $n$ subscripted with the functional group code (CB = cyanobacteria, SP = sulphate reducing bacteria, and PB = phototrophic sulphur bacteria).
+E.g.
+$n_{CB}$ is the number of strains of cyanobacteria.
+[add why we only ever had 9].
+* **Which traits to introduce variation in.** We chose the maximum growth rate and the tolerance of growth to an inhibiting substrate.
+E.g.
+maximum growth rate of the cyanobacteria $G_{max,CB}$, and the tolerance of cyanobacterial growth to reduced sulphur $h_{SR,CB}$.
+* **The amount of among strain variation.** The symbol for this is $Div$ (from *Div*ersity) subscripted by the trait/parameter and the functional group.
+E.g.
+* $Div_{G_{max,CB}}$  is the amount of among strain variation in the maximum growth rate $G_{max}$ of the cyanobacteria $CB$.
+* **The correlation between variation in different traits.** This was always negative, so there was a tradeoff.
+Our implementation of the variation and tradeoff contain the assumption of a linear tradeoff of log-log transformed among-strain variation.
+* **The relative amount of among strain variation in different functional groups.** E.g.
+were strains of cyanobacteria very variable compared to strains of the other functional groups.
+We performed several numerical experiments, varying which functional groups had more or less among strain variation.
+
+* $n_{CB}$ - number of strains of cyanobacteria.
+* $n_{SB}$ - number of strains of sulphate reducing bacteria.
+* $n_{PB}$ - number of strains of phototrophic sulphur bacteria.
+* $Div_{G_{max},CB}$ - amount of among strain variation in the maximum growth rate $G_{max}$ of the cyanobacteria $CB$. 
+* $Div_{h,CB}$ - amount of among strain variation in the maximum growth rate $G_{max}$ of the cyanobacteria $CB$. 
+* $Div_{G_{max},SB}$ - amount of among strain variation in the maximum growth rate $G_{max}$ of the sulphate reducing bacteria $SB$. 
+* $Div_{h,SB}$ - amount of among strain variation in the maximum growth rate $G_{max}$ of the sulphate reducing bacteria $SB$. 
+* $Div_{G_{max},PB}$ - amount of among strain variation in the maximum growth rate $G_{max}$ of the phototrophic sulphur bacteria $PB$. 
+* $Div_{h,PB}$ - amount of among strain variation in the maximum growth rate $G_{max}$ of the phototrophic sulphur bacteria $PB$.
 
@@
 ```{r ss_novar, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("No diversity"), echo=FALSE}
-CBSBPB_data <- readRDS(here("simulations/expt1/data/ss_res_grad_CBSBPB_var.RDS"))
+CBSBPB_data <- readRDS(here("simulations/expt2/data/ss_res_grad_CBSBPB_var.RDS"))
 result_index1 <- 1

### 2021-06-25 simulations/expt1/experiment_framework.R

@@ -1,559 +1,0 @@
-## Setup R ----
-
-rm(list = ls())
-
-# devtools::install_github("opetchey/microxanox",
-#                              ref="main",
-#                              auth_token = "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",
-#                              build_vignettes = FALSE,
-#                              force = TRUE)
-# 
-library(tidyverse)
-library(microxanox)
-library(patchwork)
-library(here)
-source(here("simulations/r functions/various_useful_functions.r"))
-
-options(mc.cores = 8)
-
-## Initialise general simulation conditions ----
-default_dynamic_model <- bushplus_dynamic_model
-default_event_definition <- event_definition_1
-## no default parameter values
-default_event_interval <- 100
-default_noise_sigma <- 0
-default_minimum_abundances <- rep(0, 3)
-names(default_minimum_abundances) <- c("CB", "PB", "SB") 
-default_sim_duration <- 100000
-default_sim_sample_interval <- 10
-## note that next line (log10a_series is over-ridden with getting stable states)
-#default_log10a_series <- c(-2, -2, -2, -2, -10, -10, -10, -10, -10)
-num_CB_strains <- 9
-num_SB_strains <- 9
-num_PB_strains <- 9
-default_9strain <- new_starter(n_CB = num_CB_strains,
-                             n_SB = num_SB_strains,
-                             n_PB = num_PB_strains,
-                             values_initial_state = "bush_ssfig3")
-
-
-## Initialise general steady state finding setting ----
-ssfind_minimum_abundances <- rep(0, 3)
-names(ssfind_minimum_abundances) <- c("CB", "PB", "SB") 
-ssfind_simulation_duration <- default_sim_duration
-ssfind_simulation_sampling_interval <- ssfind_simulation_duration
-ssfind_event_interval <- ssfind_simulation_duration
-grid_num_a <- 1000 ## number of a_0 values
-a_Os <- 10^seq(-7, -1, length=grid_num_a) ## sequence of a_0 values
-grid_num_N <- 2 ## number of N values
[…]

### 2021-06-25 simulations/expt1/temporal_switching_experiments.R

@@ -1,642 +1,0 @@
-## Setup R ----
-
-rm(list = ls())
-
-# devtools::install_github("opetchey/microxanox",
-#                              ref="main",
-#                              auth_token = "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",
-#                              build_vignettes = FALSE,
-#                              force = TRUE)
-
-library(tidyverse)
-library(microxanox)
-library(patchwork)
-library(here)
-source(here("simulations/r functions/various_useful_functions.r"))
-
-options(mc.cores = 8)
-
-## Initialise general simulation conditions ----
-default_dynamic_model <- bushplus_dynamic_model
-default_event_definition <- event_definition_1
-## no default parameter values
-default_event_interval <- 100
-default_noise_sigma <- 0
-default_minimum_abundances <- rep(10000, 3)
-names(default_minimum_abundances) <- c("CB", "PB", "SB") 
-default_sim_duration <- 50000
-default_sim_sample_interval <- 100
-## note that next line (log10a_series is over-ridden with getting stable states)
-#default_log10a_series <- c(-2, -2, -2, -2, -10, -10, -10, -10, -10)
-num_CB_strains <- 9
-num_SB_strains <- 9
-num_PB_strains <- 9
-default_9strain <- new_starter(n_CB = num_CB_strains,
-                             n_SB = num_SB_strains,
-                             n_PB = num_PB_strains,
-                             values_initial_state = "bush_ssfig3")
-
-
-## Initialise general steady state finding setting ----
-#ssfind_minimum_abundances <- rep(0, 3)
-#names(ssfind_minimum_abundances) <- c("CB", "PB", "SB") 
-#ssfind_simulation_duration <- default_sim_duration
-#ssfind_simulation_sampling_interval <- ssfind_simulation_duration
-#ssfind_event_interval <- ssfind_simulation_duration
-#grid_num_a <- 20 ## number of a_0 values
-#a_Os <- 10^seq(-7, -1, length=grid_num_a) ## sequence of a_0 values
-#grid_num_N <- 2 ## number of N values
-#initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
[…]

### 2021-06-25 simulations/expt2/experiment_framework.R

@@ -1,559 +1,0 @@
-## Setup R ----
-
-rm(list = ls())
-
-# devtools::install_github("opetchey/microxanox",
-#                              ref="main",
-#                              auth_token = "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",
-#                              build_vignettes = FALSE,
-#                              force = TRUE)
-# 
-library(tidyverse)
-library(microxanox)
-library(patchwork)
-library(here)
-source(here("simulations/r functions/various_useful_functions.r"))
-
-options(mc.cores = 8)
-
-## Initialise general simulation conditions ----
-default_dynamic_model <- bushplus_dynamic_model
-default_event_definition <- event_definition_1
-## no default parameter values
-default_event_interval <- 100
-default_noise_sigma <- 0
-default_minimum_abundances <- rep(0, 3)
-names(default_minimum_abundances) <- c("CB", "PB", "SB") 
-default_sim_duration <- 100000
-default_sim_sample_interval <- 10
-## note that next line (log10a_series is over-ridden with getting stable states)
-#default_log10a_series <- c(-2, -2, -2, -2, -10, -10, -10, -10, -10)
-num_CB_strains <- 9
-num_SB_strains <- 9
-num_PB_strains <- 9
-default_9strain <- new_starter(n_CB = num_CB_strains,
-                             n_SB = num_SB_strains,
-                             n_PB = num_PB_strains,
-                             values_initial_state = "bush_ssfig3")
-
-
-## Initialise general steady state finding setting ----
-ssfind_minimum_abundances <- rep(0, 3)
-names(ssfind_minimum_abundances) <- c("CB", "PB", "SB") 
-ssfind_simulation_duration <- default_sim_duration
-ssfind_simulation_sampling_interval <- ssfind_simulation_duration
-ssfind_event_interval <- ssfind_simulation_duration
-grid_num_a <- 2 ## number of a_0 values
-a_Os <- 10^seq(-7, -1, length=grid_num_a) ## sequence of a_0 values
-grid_num_N <- 2 ## number of N values
[…]

### 2021-06-25 simulations/expt2/temporal_switching_experiments.R

@@ -1,642 +1,0 @@
-## Setup R ----
-
-rm(list = ls())
-
-# devtools::install_github("opetchey/microxanox",
-#                              ref="main",
-#                              auth_token = "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",
-#                              build_vignettes = FALSE,
-#                              force = TRUE)
-
-library(tidyverse)
-library(microxanox)
-library(patchwork)
-library(here)
-source(here("simulations/r functions/various_useful_functions.r"))
-
-options(mc.cores = 8)
-
-## Initialise general simulation conditions ----
-default_dynamic_model <- bushplus_dynamic_model
-default_event_definition <- event_definition_1
-## no default parameter values
-default_event_interval <- 100
-default_noise_sigma <- 0
-default_minimum_abundances <- rep(10000, 3)
-names(default_minimum_abundances) <- c("CB", "PB", "SB") 
-default_sim_duration <- 50000
-default_sim_sample_interval <- 100
-## note that next line (log10a_series is over-ridden with getting stable states)
-#default_log10a_series <- c(-2, -2, -2, -2, -10, -10, -10, -10, -10)
-num_CB_strains <- 9
-num_SB_strains <- 9
-num_PB_strains <- 9
-default_9strain <- new_starter(n_CB = num_CB_strains,
-                             n_SB = num_SB_strains,
-                             n_PB = num_PB_strains,
-                             values_initial_state = "bush_ssfig3")
-
-
-## Initialise general steady state finding setting ----
-#ssfind_minimum_abundances <- rep(0, 3)
-#names(ssfind_minimum_abundances) <- c("CB", "PB", "SB") 
-#ssfind_simulation_duration <- default_sim_duration
-#ssfind_simulation_sampling_interval <- ssfind_simulation_duration
-#ssfind_event_interval <- ssfind_simulation_duration
-#grid_num_a <- 20 ## number of a_0 values
-#a_Os <- 10^seq(-7, -1, length=grid_num_a) ## sequence of a_0 values
-#grid_num_N <- 2 ## number of N values
-#initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
[…]

### 2021-06-29 experiments/experiment 2/experiment 2.Rmd
improved experiment framework

--- 2021-06-25 experiments/experiment template/experiment template.Rmd
@@
 ---
-title: "Experiment 1"
+title: "Experiment 2"
 author: "Owen Petchey"
 date: "6/25/2021"
-output: html_document
+output: 
+  html_document: 
+    keep_md: yes
 ---
@@
 CB_var_TO <- -5
-SB_var_range <- 0.010
+SB_var_range <- 0.0015789474
 SB_var_TO <- -20.5
-PB_var_range <- 0.010
+PB_var_range <- 0.0015789474
 PB_var_TO <- -20.5
@@
 ```{r}
-
-CBtraits <- var_expt$pars[[num_div_treatment_levels]]$CB
-P <- 1 #10^seq(-5, 5, 0.1)
-SR <- 10^seq(0, 3, 0.1)
-gr_rateCB1 <- growth1(P, CBtraits$g_max_CB[1], CBtraits$k_CB_P[1]) * inhibition(SR, CBtraits$h_SR_CB[1])
-gr_rateCB9 <- growth1(P, CBtraits$g_max_CB[num_CB_strains], CBtraits$k_CB_P[num_CB_strains]) * inhibition(SR, CBtraits$h_SR_CB[num_CB_strains])
-
-CB_TO1 <- ggplot() +
-  geom_point(aes(x = CBtraits$h_SR_CB, y = CBtraits$g_max_CB))
-CB_TO2 <- ggplot() +
-  geom_line(aes( x = log10(SR), y = gr_rateCB1)) +
-  geom_line(aes( x = log10(SR), y = gr_rateCB9), col = "blue")
-
-SBtraits <- var_expt$pars[[num_div_treatment_levels]]$SB
-P <- 1 #10^seq(-5, 5, 0.1)
-SO <- 1
-O <- 10^seq(-2.5, 2.5, 0.1)
-gr_rateSB1 <- growth2(P, SO, SBtraits$g_max_SB[1], SBtraits$k_SB_P[1], SBtraits$k_SB_SO[1]) *
-  inhibition(O, SBtraits$h_O_SB[1])
-gr_rateSB9 <- growth2(P, SO, SBtraits$g_max_SB[9], SBtraits$k_SB_P[9], SBtraits$k_SB_SO[9]) *
-  inhibition(O, SBtraits$h_O_SB[9])
-
-SB_TO1 <- ggplot() +
-  geom_point(aes(x = SBtraits$h_O_SB, y = SBtraits$g_max_SB))
-SB_TO2 <- ggplot() +
-  geom_line(aes( x = log10(O), y = gr_rateSB1)) +
-  geom_line(aes( x = log10(O), y = gr_rateSB9), col = "blue")
-
-PBtraits <- var_expt$pars[[num_div_treatment_levels]]$PB
-P <- 1 #10^seq(-5, 5, 0.1)
-SO <- 1
-O <- 10^seq(-2.5, 2.5, 0.1)
-gr_ratePB1 <- growth2(P, SO, PBtraits$g_max_PB[1], PBtraits$k_PB_P[1], PBtraits$k_PB_SR[1]) *
-  inhibition(O, PBtraits$h_O_PB[1])
-gr_ratePB9 <- growth2(P, SO, PBtraits$g_max_PB[9], PBtraits$k_PB_P[9], PBtraits$k_PB_SR[9]) *
-  inhibition(O, PBtraits$h_O_PB[9])
-
-PB_TO1 <- ggplot() +
-  geom_point(aes(x = PBtraits$h_O_PB, y = PBtraits$g_max_PB))
-PB_TO2 <- ggplot() +
-  geom_line(aes( x = log10(O), y = gr_ratePB1)) +
-  geom_line(aes( x = log10(O), y = gr_ratePB9), col = "blue")
-
-(CB_TO1 + SB_TO1 + PB_TO1) / (CB_TO2 + SB_TO2 + PB_TO2)
+display_diversity()
 ```
@@
 ```{r}
-default_sim_duration <- 100000
+default_sim_duration <- 1000000
 ```
@@
 ```{r}
-default_minimum_abundances <- rep(1000, 3)
+default_minimum_abundances <- rep(100, 3)
 names(default_minimum_abundances) <- c("CB", "PB", "SB") 
@@
 ```{r}
-sim_number <- 1
-default_log10a_series <- c(-1, -6, -1)
+sim_number1 <- 1
+default_log10a_series <- c(-1, -8, -1)
 initial_state <- new_initial_state(num_CB_strains,
@@
 initial_state[grep("CB_", names(initial_state))] <- 10/num_CB_strains
-sim_res_novar <- run_simulation(parameter_values = var_expt$pars[[sim_number]],
+sim_res_novar <- run_simulation(parameter_values = var_expt$pars[[sim_number1]],
                           initial_state = initial_state)
 plot_dynamics(sim_res_novar)
-#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
+##ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
 ```
@@
 ```{r}
-sim_number <- 2
-sim_res_highvar <- run_simulation(parameter_values = var_expt$pars[[sim_number]],
+sim_number2 <- 2
+sim_res_highvar <- run_simulation(parameter_values = var_expt$pars[[sim_number2]],
                           initial_state = initial_state)
 plot_dynamics(sim_res_highvar)
-#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)
+##ggsave(here("expteriment 2/figures/switching_highvar.pdf"), width = 10)
 
@@
   ggtitle("Solid line is with no intraspecific diversity.\nDashed line is with intraspecific diversity")
-##ggsave(here("simulations/figures/switching_comparison.pdf"), width = 5, height = 4)
+##ggsave(here("experiment 2/figures/switching_comparison.pdf"), width = 8, height = 10)
 
@@
 var_expt <- run_ss_var_experiment()
+saveRDS(var_expt, here("experiments/experiment 2/data/ss_data.RDS"))
 ```
@@
 
+ss_result1 <- var_expt[result_index1,]$ss_res[[1]]
+ss_result2 <- var_expt[result_index2,]$ss_res[[1]]
+xlims = c(-7, -1)
 ```

### 2021-06-29 experiments/tradeoff strength illustration.Rmd
improved experiment framework

---
title: "Experiment 1"
author: "Owen Petchey"
date: "6/25/2021"
output: html_document
---

# Setup

## R

```{r}

rm(list = ls())

knitr::opts_knit$set(progress = TRUE, verbose = TRUE, cache = TRUE)

# devtools::install_github("opetchey/microxanox",
#                              ref="main",
#                              auth_token = "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",
#                              build_vignettes = FALSE,
#                              force = TRUE)

library(tidyverse)
library(microxanox)
library(patchwork)
library(here)
source(here("experiments/r functions/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
options(mc.cores = 8)

colfunc_CB <- colorRampPalette(c("#B5FFC9", "#024F17"))
colfunc_SB <- colorRampPalette(c("#FCBEB3", "#7D1402"))
colfunc_PB <- colorRampPalette(c("#F9AEFC", "#6E0172"))

```

## General simulation conditions

```{r}
default_dynamic_model <- bushplus_dynamic_model
default_event_definition <- event_definition_1
default_event_interval <- 100
default_noise_sigma <- 0
default_minimum_abundances <- rep(1, 3)
names(default_minimum_abundances) <- c("CB", "PB", "SB") 
default_sim_duration <- 80000
default_sim_sample_interval <- 100
initial_pars_from <- "bush_ssfig3"
## note that next line (log10a_series is over-ridden with getting stable states)
#default_log10a_series <- c(-2, -2, -2, -2, -10, -10, -10, -10, -10)
```

## Define diversity

```{r}
num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9
CB_var_range <- 0.015789474
CB_var_TO <- -20
SB_var_range <- 0.1
SB_var_TO <- -20
PB_var_range <- 0.1
PB_var_TO <- -20

num_div_treatment_levels <- 10
```

## Create diversity

```{r}
default_9strain <- new_starter(n_CB = num_CB_strains,
                             n_SB = num_SB_strains,
                             n_PB = num_PB_strains,
                             values_initial_state = initial_pars_from)
CB_var_gmax_s <- seq(zero, unity*CB_var_TO, length=num_div_treatment_levels) * CB_var_range
CB_var_h_s = seq(zero, unity, length=num_div_treatment_levels) * CB_var_range
SB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * SB_var_range
SB_var_h_s = seq(zero, SB_var_TO, length=num_div_treatment_levels) * SB_var_range
PB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * PB_var_range
PB_var_h_s = seq(zero, PB_var_TO, length=num_div_treatment_levels) * PB_var_range
var_expt <- tibble(CB_var_gmax_s,
                   CB_var_h_s,
                   SB_var_gmax_s,
                   SB_var_h_s,
                   PB_var_gmax_s,
                   PB_var_h_s)
var_expt <- var_expt %>%
  nest_by(CB_var_gmax_s, CB_var_h_s,
          SB_var_gmax_s, SB_var_h_s,
          PB_var_gmax_s, PB_var_h_s) %>%
  mutate(pars = list(add_strain_var(default_9strain,
                                    CB_var_gmax = CB_var_gmax_s,
                                    CB_var_h = CB_var_h_s,
                                    SB_var_gmax = SB_var_gmax_s,
                                    SB_var_h = SB_var_h_s,
                                    PB_var_gmax = PB_var_gmax_s,
                                    PB_var_h = PB_var_h_s)))
```

## Display diversity

```{r}

CBtraits <- tibble(var_expt$pars[[10]]$CB,
                     Diversity = "None",
                   Strength = "Strong")
CBtraits <- bind_rows(CBtraits,
                      tibble(var_expt$pars[[6]]$CB,
                     Diversity = "Medium",
                     Strength = "Strong"))
CBtraits <- bind_rows(CBtraits,
                      tibble(var_expt$pars[[1]]$CB,
                     Diversity = "High",
                     Strength = "Strong"))

````

## Define diversity

```{r}
num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9
CB_var_range <- 0.015789474
CB_var_TO <- -2
SB_var_range <- 0.1
SB_var_TO <- -20
PB_var_range <- 0.1
PB_var_TO <- -20

num_div_treatment_levels <- 10
```

## Create diversity

```{r}
default_9strain <- new_starter(n_CB = num_CB_strains,
                             n_SB = num_SB_strains,
                             n_PB = num_PB_strains,
                             values_initial_state = initial_pars_from)
CB_var_gmax_s <- seq(zero, unity*CB_var_TO, length=num_div_treatment_levels) * CB_var_range
CB_var_h_s = seq(zero, unity, length=num_div_treatment_levels) * CB_var_range
SB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * SB_var_range
SB_var_h_s = seq(zero, SB_var_TO, length=num_div_treatment_levels) * SB_var_range
PB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * PB_var_range
PB_var_h_s = seq(zero, PB_var_TO, length=num_div_treatment_levels) * PB_var_range
var_expt <- tibble(CB_var_gmax_s,
                   CB_var_h_s,
                   SB_var_gmax_s,
                   SB_var_h_s,
                   PB_var_gmax_s,
                   PB_var_h_s)
var_expt <- var_expt %>%
  nest_by(CB_var_gmax_s, CB_var_h_s,
          SB_var_gmax_s, SB_var_h_s,
          PB_var_gmax_s, PB_var_h_s) %>%
  mutate(pars = list(add_strain_var(default_9strain,
                                    CB_var_gmax = CB_var_gmax_s,
                                    CB_var_h = CB_var_h_s,
                                    SB_var_gmax = SB_var_gmax_s,
                                    SB_var_h = SB_var_h_s,
                                    PB_var_gmax = PB_var_gmax_s,
                                    PB_var_h = PB_var_h_s)))
```

```{r}
CBtraits <- bind_rows(CBtraits,
                      tibble(var_expt$pars[[10]]$CB,
                     Diversity = "None",
                     Strength = "Weak"))
CBtraits <- bind_rows(CBtraits,
                      tibble(var_expt$pars[[6]]$CB,
                     Diversity = "Medium",
                     Strength = "Weak"))
CBtraits <- bind_rows(CBtraits,
                      tibble(var_expt$pars[[1]]$CB,
                     Diversity = "High",
                     Strength = "Weak"))

ggplot(CBtraits) +
  geom_point(aes(x = h_SR_CB, y = g_max_CB)) +
  facet_grid(Strength ~ Diversity) +
  xlab("Tolerance trait") +
  ylab("Maximum growth rate")

```

### 2021-06-29 experiments/r functions/various_useful_functions.r

@@ -227,7 +227,7 @@ plot_ss_result2 <- function(ss_result1,
   temp1 <- ss_result1 %>%
     mutate(direction = ifelse(initial_N_CB == 1, "up", "down"),
            a = 10^a) %>%
-    gather(species, quantity, 2:(ncol(.)-6)) %>% 
+    gather(species, quantity, 1:(ncol(.)-6)) %>% 
     mutate(var_type=ifelse(grepl("B_", species), "Organism", "Substrate"),
            functional_group = case_when(str_detect(species, "CB_") ~ "CB",
                                         str_detect(species, "SB_") ~ "SB",
@@ -240,7 +240,7 @@ plot_ss_result2 <- function(ss_result1,
   temp2 <- ss_result2 %>%
     mutate(direction = ifelse(initial_N_CB == 1, "up", "down"),
            a = 10^a) %>%
-    gather(species, quantity, 2:(ncol(.)-6)) %>% 
+    gather(species, quantity, 1:(ncol(.)-6)) %>% 
     mutate(var_type=ifelse(grepl("B_", species), "Organism", "Substrate"),
            functional_group = case_when(str_detect(species, "CB_") ~ "CB",
                                         str_detect(species, "SB_") ~ "SB",
@@ -248,7 +248,8 @@ plot_ss_result2 <- function(ss_result1,
            functional_group = ifelse(is.na(functional_group), species, functional_group)) %>%
     group_by(a, direction, var_type, functional_group) %>%
     summarise(total_quantity = sum(quantity, na.rm = TRUE)) %>%
-    mutate(log10_total_quantity = log10(total_quantity+1))
+    mutate(log10_total_quantity = log10(total_quantity+1),
+           log1 = log10(a))
   
   
   num_CB_strains <- 1
@@ -266,7 +267,7 @@ plot_ss_result2 <- function(ss_result1,
     xlab('a')  +
     guides(colour = guide_legend(ncol = 3)) +
     geom_path(data = dplyr::filter(temp2, functional_group == fg_oi),
-              linetype = "dashed",
[…]

### 2021-06-30 experiments/experiment 2/experiment 2.Rmd
update to experiment framework

@@
 num_PB_strains <- 9
-CB_var_range <- 0.015789474
-CB_var_TO <- -5
-SB_var_range <- 0.0015789474
-SB_var_TO <- -20.5
-PB_var_range <- 0.0015789474
-PB_var_TO <- -20.5
+CB_gmax_div <- 0.015789474
+CB_h_div <- -0.08
+SB_gmax_div <- 0.015789474 * 0.5
+SB_h_div <- -0.323 * 0.5
+PB_gmax_div <- 0.015789474 * 0.5
+PB_h_div <- -0.323 * 0.5
 
@@
                              values_initial_state = initial_pars_from)
-CB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * CB_var_range
-CB_var_h_s = seq(zero, CB_var_TO, length=num_div_treatment_levels) * CB_var_range
-SB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * SB_var_range
-SB_var_h_s = seq(zero, SB_var_TO, length=num_div_treatment_levels) * SB_var_range
-PB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * PB_var_range
-PB_var_h_s = seq(zero, PB_var_TO, length=num_div_treatment_levels) * PB_var_range
+CB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * CB_gmax_div
+CB_var_h_s = seq(zero, unity, length=num_div_treatment_levels) * CB_h_div
+SB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * SB_gmax_div
+SB_var_h_s = seq(zero, unity, length=num_div_treatment_levels) * SB_h_div
+PB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * PB_gmax_div
+PB_var_h_s = seq(zero, unity, length=num_div_treatment_levels) * PB_h_div
 var_expt <- tibble(CB_var_gmax_s,
@@
 plot_dynamics(sim_res_novar)
-##ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
+#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
 ```
@@
 plot_dynamics(sim_res_highvar)
-##ggsave(here("expteriment 2/figures/switching_highvar.pdf"), width = 10)
+#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)
 
@@
   ggtitle("Solid line is with no intraspecific diversity.\nDashed line is with intraspecific diversity")
-##ggsave(here("experiment 2/figures/switching_comparison.pdf"), width = 8, height = 10)
+##ggsave(here("simulations/figures/switching_comparison.pdf"), width = 5, height = 4)
 
@@
 saveRDS(var_expt, here("experiments/experiment 2/data/ss_data.RDS"))
+
 ```
@@
 ```{r}
+
 result_index1 <- 1

### 2021-06-30 experiments/tradeoff strength illustration.Rmd
update to experiment framework

@@
 num_PB_strains <- 9
+CB_gmax_div <- 0.015789474
+CB_h_div <- -0.08
+SB_gmax_div <- 0.015789474
+SB_h_div <- -0.323
+PB_gmax_div <- 0.015789474
+PB_h_div <- -0.323
+
 CB_var_range <- 0.015789474
@@
                              values_initial_state = initial_pars_from)
-CB_var_gmax_s <- seq(zero, unity*CB_var_TO, length=num_div_treatment_levels) * CB_var_range
-CB_var_h_s = seq(zero, unity, length=num_div_treatment_levels) * CB_var_range
-SB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * SB_var_range
-SB_var_h_s = seq(zero, SB_var_TO, length=num_div_treatment_levels) * SB_var_range
-PB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * PB_var_range
-PB_var_h_s = seq(zero, PB_var_TO, length=num_div_treatment_levels) * PB_var_range
-var_expt <- tibble(CB_var_gmax_s,
+CB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * CB_gmax_div
+CB_var_h_s = seq(zero, unity, length=num_div_treatment_levels) * CB_h_div
+SB_var_gmax_s <- 1#seq(zero, unity, length=num_div_treatment_levels) * SB_gmax_div
+SB_var_h_s = 1#seq(zero, unity, length=num_div_treatment_levels) * SB_h_div
+PB_var_gmax_s <- 1#seq(zero, unity, length=num_div_treatment_levels) * PB_gmax_div
+PB_var_h_s = 1#seq(zero, unity, length=num_div_treatment_levels) * PB_h_div
+var_expt <- crossing(CB_var_gmax_s,
                    CB_var_h_s,
@@
 
-CBtraits <- tibble(var_expt$pars[[10]]$CB,
-                     Diversity = "None",
-                   Strength = "Strong")
+med_gmax <- 0.007017544
+med_h <- -0.035555556
+high_gmax <- 0.015789474
+high_h <- -0.080
+
+CBtraits <- tibble(var_expt$pars[[which(var_expt$CB_var_gmax_s == 0 &
+                                          var_expt$CB_var_h_s == 0)]]$CB,
+                     Div_gmax = "None",
+                   Div_h = "None")
 CBtraits <- bind_rows(CBtraits,
-                      tibble(var_expt$pars[[6]]$CB,
-                     Diversity = "Medium",
-                     Strength = "Strong"))
+                      tibble(var_expt$pars[[which(var_expt$CB_var_gmax_s == 0 & abs(var_expt$CB_var_h_s - med_h)<0.0001)]]$CB,
+                     Div_gmax = "None",
+                   Div_h = "Medium"))
 CBtraits <- bind_rows(CBtraits,
-                      tibble(var_expt$pars[[1]]$CB,
-                     Diversity = "High",
-                     Strength = "Strong"))
+                      tibble(var_expt$pars[[which(var_expt$CB_var_gmax_s == 0 & abs(var_expt$CB_var_h_s - high_h)<0.0001)]]$CB,
+                     Div_gmax = "None",
+                   Div_h = "High"))
 
-````
+CBtraits <- bind_rows(CBtraits,
+                      tibble(var_expt$pars[[which(abs(var_expt$CB_var_gmax_s - med_gmax)<0.0001 & abs(var_expt$CB_var_h_s - 0)<0.0001)]]$CB,
+                     Div_gmax = "Medium",
+                   Div_h = "None"))
+CBtraits <- bind_rows(CBtraits,
+                      tibble(var_expt$pars[[which(abs(var_expt$CB_var_gmax_s - med_gmax)<0.0001 & abs(var_expt$CB_var_h_s - med_h)<0.0001)]]$CB,
+                     Div_gmax = "Medium",
+                   Div_h = "Medium"))
+CBtraits <- bind_rows(CBtraits,
+                      tibble(var_expt$pars[[which(abs(var_expt$CB_var_gmax_s - med_gmax)<0.0001 & abs(var_expt$CB_var_h_s - high_h)<0.0001)]]$CB,
+                     Div_gmax = "Medium",
+                   Div_h = "High"))
+
+CBtraits <- bind_rows(CBtraits,
+                      tibble(var_expt$pars[[which(abs(var_expt$CB_var_gmax_s - high_gmax)<0.0001 & abs(var_expt$CB_var_h_s - 0)<0.0001)]]$CB,
+                     Div_gmax = "High",
+                   Div_h = "None"))
+CBtraits <- bind_rows(CBtraits,
+                      tibble(var_expt$pars[[which(abs(var_expt$CB_var_gmax_s - high_gmax)<0.0001 & abs(var_expt$CB_var_h_s - med_h)<0.0001)]]$CB,
+                     Div_gmax = "High",
+                   Div_h = "Medium"))
+CBtraits <- bind_rows(CBtraits,
+                      tibble(var_expt$pars[[which(abs(var_expt$CB_var_gmax_s - high_gmax)<0.0001 & abs(var_expt$CB_var_h_s - high_h)<0.0001)]]$CB,
+                     Div_gmax = "High",
+                   Div_h = "High"))
+
+```
 
@@
 ```{r}
-num_CB_strains <- 9
-num_SB_strains <- 9
-num_PB_strains <- 9
-CB_var_range <- 0.015789474
-CB_var_TO <- -2
-SB_var_range <- 0.1
-SB_var_TO <- -20
-PB_var_range <- 0.1
-PB_var_TO <- -20
-
-num_div_treatment_levels <- 10
+# num_CB_strains <- 9
+# num_SB_strains <- 9
+# num_PB_strains <- 9
+# CB_var_range <- 0.015789474
+# CB_var_TO <- -2
+# SB_var_range <- 0.1
+# SB_var_TO <- -20
+# PB_var_range <- 0.1
+# PB_var_TO <- -20
+# 
+# num_div_treatment_levels <- 10
 ```
@@
 ```{r}
-default_9strain <- new_starter(n_CB = num_CB_strains,
-                             n_SB = num_SB_strains,
-                             n_PB = num_PB_strains,
-                             values_initial_state = initial_pars_from)
-CB_var_gmax_s <- seq(zero, unity*CB_var_TO, length=num_div_treatment_levels) * CB_var_range
-CB_var_h_s = seq(zero, unity, length=num_div_treatment_levels) * CB_var_range
-SB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * SB_var_range
-SB_var_h_s = seq(zero, SB_var_TO, length=num_div_treatment_levels) * SB_var_range
-PB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * PB_var_range
-PB_var_h_s = seq(zero, PB_var_TO, length=num_div_treatment_levels) * PB_var_range
-var_expt <- tibble(CB_var_gmax_s,
-                   CB_var_h_s,
-                   SB_var_gmax_s,
-                   SB_var_h_s,
-                   PB_var_gmax_s,
-                   PB_var_h_s)
-var_expt <- var_expt %>%
-  nest_by(CB_var_gmax_s, CB_var_h_s,
-          SB_var_gmax_s, SB_var_h_s,
-          PB_var_gmax_s, PB_var_h_s) %>%
-  mutate(pars = list(add_strain_var(default_9strain,
-                                    CB_var_gmax = CB_var_gmax_s,
-                                    CB_var_h = CB_var_h_s,
-                                    SB_var_gmax = SB_var_gmax_s,
-                                    SB_var_h = SB_var_h_s,
-                                    PB_var_gmax = PB_var_gmax_s,
-                                    PB_var_h = PB_var_h_s)))
+# default_9strain <- new_starter(n_CB = num_CB_strains,
+#                              n_SB = num_SB_strains,
+#                              n_PB = num_PB_strains,
+#                              values_initial_state = initial_pars_from)
+# CB_var_gmax_s <- seq(zero, unity*CB_var_TO, length=num_div_treatment_levels) * CB_var_range
+# CB_var_h_s = seq(zero, unity, length=num_div_treatment_levels) * CB_var_range
+# SB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * SB_var_range
+# SB_var_h_s = seq(zero, SB_var_TO, length=num_div_treatment_levels) * SB_var_range
+# PB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * PB_var_range
+# PB_var_h_s = seq(zero, PB_var_TO, length=num_div_treatment_levels) * PB_var_range
+# var_expt <- tibble(CB_var_gmax_s,
+#                    CB_var_h_s,
+#                    SB_var_gmax_s,
+#                    SB_var_h_s,
+#                    PB_var_gmax_s,
+#                    PB_var_h_s)
+# var_expt <- var_expt %>%
+#   nest_by(CB_var_gmax_s, CB_var_h_s,
+#           SB_var_gmax_s, SB_var_h_s,
+#           PB_var_gmax_s, PB_var_h_s) %>%
+#   mutate(pars = list(add_strain_var(default_9strain,
+#                                     CB_var_gmax = CB_var_gmax_s,
+#                                     CB_var_h = CB_var_h_s,
+#                                     SB_var_gmax = SB_var_gmax_s,
+#                                     SB_var_h = SB_var_h_s,
+#                                     PB_var_gmax = PB_var_gmax_s,
+#                                     PB_var_h = PB_var_h_s)))
 ```
@@
 ```{r}
-CBtraits <- bind_rows(CBtraits,
-                      tibble(var_expt$pars[[10]]$CB,
-                     Diversity = "None",
-                     Strength = "Weak"))
-CBtraits <- bind_rows(CBtraits,
-                      tibble(var_expt$pars[[6]]$CB,
-                     Diversity = "Medium",
-                     Strength = "Weak"))
-CBtraits <- bind_rows(CBtraits,
-                      tibble(var_expt$pars[[1]]$CB,
-                     Diversity = "High",
-                     Strength = "Weak"))
+# CBtraits <- bind_rows(CBtraits,
+#                       tibble(var_expt$pars[[10]]$CB,
+#                      Diversity = "None",
+#                      Strength = "Weak"))
+# CBtraits <- bind_rows(CBtraits,
+#                       tibble(var_expt$pars[[6]]$CB,
+#                      Diversity = "Medium",
+#                      Strength = "Weak"))
+# CBtraits <- bind_rows(CBtraits,
+#                       tibble(var_expt$pars[[1]]$CB,
+#                      Diversity = "High",
+#                      Strength = "Weak"))
 
@@
   geom_point(aes(x = h_SR_CB, y = g_max_CB)) +
-  facet_grid(Strength ~ Diversity) +
+  facet_grid(Div_gmax ~ Div_h) +
   xlab("Tolerance trait") +

### 2021-06-30 experiments/r functions/various_useful_functions.r

@@ -302,6 +302,9 @@ display_diversity <- function() {
   colfunc_SB <- colorRampPalette(rev(c("#FCBEB3", "#7D1402")))
   colfunc_PB <- colorRampPalette(rev(c("#F9AEFC", "#6E0172")))
   
+  linewd <- 1.5
+  ptsize <- 2
+  
   CBtraits <- var_expt$pars[[num_div_treatment_levels]]$CB
   P <- 1 #10^seq(-5, 5, 0.1)
   SR <- 10^seq(0, 3, 0.1)
@@ -309,14 +312,14 @@ display_diversity <- function() {
   gr_rateCB9 <- growth1(P, CBtraits$g_max_CB[num_CB_strains], CBtraits$k_CB_P[num_CB_strains]) * inhibition(SR, CBtraits$h_SR_CB[num_CB_strains])
   
   CB_TO1 <- ggplot(CBtraits) +
-    geom_point(aes(x = h_SR_CB, y = g_max_CB, col = strain_name)) +
+    geom_point(aes(x = h_SR_CB, y = g_max_CB, col = strain_name), size = ptsize) +
     xlab("Tolerance\n(cyanobacteria to reduced sulphur)") +
     ylab("Maximum growth rate\n(cyanobacteria)") +
     scale_colour_manual(values = colfunc_CB(num_CB_strains)) +
     theme(legend.position="none")
   CB_TO2 <- ggplot() +
-    geom_line(aes( x = log10(SR), y = gr_rateCB1), col = colfunc_CB(num_CB_strains)[1]) +
-    geom_line(aes( x = log10(SR), y = gr_rateCB9), col = colfunc_CB(num_CB_strains)[9]) +
+    geom_line(aes( x = log10(SR), y = gr_rateCB1), col = colfunc_CB(num_CB_strains)[1], size = linewd) +
+    geom_line(aes( x = log10(SR), y = gr_rateCB9), col = colfunc_CB(num_CB_strains)[9], size = linewd) +
     xlab("Reduced sulphur concentration\nin the environment\n(log10 uM per litre)") +
     ylab("Realised growth rate\n(cyanobacteria)")
   
@@ -332,14 +335,14 @@ display_diversity <- function() {
     inhibition(O, SBtraits$h_O_SB[9])
   
   SB_TO1 <- ggplot(SBtraits) +
-    geom_point(aes(x = h_O_SB, y = g_max_SB, col = strain_name))+
[…]

### 2021-06-30 experiments/experiment 1/experiment 1.Rmd
run two experiments

@@
 date: "6/25/2021"
-output: html_document
+output: 
+  html_document: 
+    keep_md: yes
 ---
@@
 
-knitr::opts_knit$set(progress = TRUE, verbose = TRUE, cache = TRUE)
+knitr::opts_knit$set(progress = TRUE, verbose = FALSE, cache = TRUE)
 
@@
 library(here)
-source(here("simulations/r functions/various_useful_functions.r"))
+source(here("experiments/r functions/various_useful_functions.r"))
 zero <- 0 ## don't change
 unity <- 1 ## don't change!!!
-options(mc.cores = 8)
+#options(mc.cores = 8)
 ```
@@
 num_PB_strains <- 9
-CB_var_range <- 0.015789474
-CB_var_TO <- -5
-SB_var_range <- 0.015789474
-SB_var_TO <- -20.5
-PB_var_range <- 0.015789474
-PB_var_TO <- -20.5
+CB_gmax_div <- 0.015789474
+CB_h_div <- -0.08
+SB_gmax_div <- 0.015789474
+SB_h_div <- -0.323
+PB_gmax_div <- 0.015789474
+PB_h_div <- -0.323
 
@@
 initial_state[grep("CB_", names(initial_state))] <- 10/num_CB_strains
-sim_res_novar <- run_simulation(parameter_values = var_expt$pars[[sim_number]],
+sim_res_novar <- run_simulation(parameter_values = var_expt$pars[[sim_number1]],
                           initial_state = initial_state)
@@
 ```{r}
-sim_number <- 2
-sim_res_highvar <- run_simulation(parameter_values = var_expt$pars[[sim_number]],
+sim_number2 <- 2
+sim_res_highvar <- run_simulation(parameter_values = var_expt$pars[[sim_number2]],
                           initial_state = initial_state)
@@
 ```{r}
-options(mc.cores = 8)
+options(mc.cores = 6)
 ```
@@
 ssfind_event_interval <- ssfind_simulation_duration
-grid_num_a <- 20 ## number of a_0 values
+grid_num_a <- 1000 ## number of a_0 values
 a_Os <- 10^seq(-7, -1, length=grid_num_a) ## sequence of a_0 values
@@
 var_expt <- run_ss_var_experiment()
+saveRDS(var_expt, here("experiments/experiment 1/data/ss_data.RDS"))
+
 ```

### 2021-06-30 experiments/experiment 2/experiment 2.Rmd
run two experiments

@@
 
-# devtools::install_github("opetchey/microxanox",
-#                              ref="main",
-#                              auth_token = "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",
-#                              build_vignettes = FALSE,
-#                              force = TRUE)
+devtools::install_github("opetchey/microxanox",
+                             ref="main",
+                             auth_token = "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",
+                             build_vignettes = FALSE,
+                             force = TRUE)
 

### 2021-06-30 experiments/experiment 1/experiment 1.Rmd
moved some functionality into functions!

@@
 ```{r}
-default_9strain <- new_starter(n_CB = num_CB_strains,
-                             n_SB = num_SB_strains,
-                             n_PB = num_PB_strains,
-                             values_initial_state = initial_pars_from)
-CB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * CB_gmax_div
-CB_var_h_s = seq(zero, unity, length=num_div_treatment_levels) * CB_h_div
-SB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * SB_gmax_div
-SB_var_h_s = seq(zero, unity, length=num_div_treatment_levels) * SB_h_div
-PB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * PB_gmax_div
-PB_var_h_s = seq(zero, unity, length=num_div_treatment_levels) * PB_h_div
-var_expt <- tibble(CB_var_gmax_s,
-                   CB_var_h_s,
-                   SB_var_gmax_s,
-                   SB_var_h_s,
-                   PB_var_gmax_s,
-                   PB_var_h_s)
-var_expt <- var_expt %>%
-  nest_by(CB_var_gmax_s, CB_var_h_s,
-          SB_var_gmax_s, SB_var_h_s,
-          PB_var_gmax_s, PB_var_h_s) %>%
-  mutate(pars = list(add_strain_var(default_9strain,
-                                    CB_var_gmax = CB_var_gmax_s,
-                                    CB_var_h = CB_var_h_s,
-                                    SB_var_gmax = SB_var_gmax_s,
-                                    SB_var_h = SB_var_h_s,
-                                    PB_var_gmax = PB_var_gmax_s,
-                                    PB_var_h = PB_var_h_s)))
+var_expt <- create_diversity()
 ```
@@
 ```{r}
-
-tmp_novar <- sim_res_novar$result %>%
-  filter(time != 0) %>%
-  select(-time) %>%
-  mutate(direction = rep(c("down", "up"), each = n()/2)) %>%
-  pivot_longer(1:(num_CB_strains+num_SB_strains+num_PB_strains+4),
-               names_to = "Species", values_to = "Quantity") %>%
-  mutate(var_type=ifelse(grepl("B_", Species), "Organism", "Substrate"),
-         functional_group = case_when(str_detect(Species, "CB_") ~ "CB",
-                                      str_detect(Species, "SB_") ~ "SB",
-                                      str_detect(Species, "PB_") ~ "PB"),
-         functional_group = ifelse(is.na(functional_group), Species, functional_group)) %>%
-  group_by(functional_group, a, var_type, direction) %>%
-  summarise(Total_quantity = sum(Quantity))
-tmp_highvar <- sim_res_highvar$result %>%
-  filter(time != 0) %>%
-  select(-time) %>%
-  mutate(direction = rep(c("down", "up"), each = n()/2)) %>%
-  pivot_longer(1:(num_CB_strains+num_SB_strains+num_PB_strains+4),
-               names_to = "Species", values_to = "Quantity") %>%
-  mutate(var_type=ifelse(grepl("B_", Species), "Organism", "Substrate"),
-         functional_group = case_when(str_detect(Species, "CB_") ~ "CB",
-                                      str_detect(Species, "SB_") ~ "SB",
-                                      str_detect(Species, "PB_") ~ "PB"),
-         functional_group = ifelse(is.na(functional_group), Species, functional_group)) %>%
-  group_by(functional_group, a, var_type, direction) %>%
-  summarise(Total_quantity = sum(Quantity))
-
-soi <- "O"
-ggplot() +
-  geom_path(data = filter(tmp_novar,functional_group == soi),
-            aes(x=a, y = log10(Total_quantity), group = direction)) +
-  geom_path(data = filter(tmp_highvar,functional_group == soi),
-            aes(x=a, y = log10(Total_quantity), group = direction),
-            linetype = "dashed", lwd=2, col="red") +
-  ggtitle("Solid line is with no intraspecific diversity.\nDashed line is with intraspecific diversity")
-##ggsave(here("simulations/figures/switching_comparison.pdf"), width = 5, height = 4)
-
+visualise_temporal_env_eco()
 ```
@@
 ```{r}
-var_expt <- run_ss_var_experiment()
-saveRDS(var_expt, here("experiments/experiment 1/data/ss_data.RDS"))
+#var_expt <- run_ss_var_experiment()
+#saveRDS(var_expt, here("experiments/experiment 1/data/ss_data.RDS"))
 
@@
 ```{r}
+var_expt <- readRDS(here("experiments/experiment 1/data/ss_data.RDS"))
 

### 2021-06-30 experiments/experiment 2/experiment 2.Rmd
moved some functionality into functions!

@@
 
-devtools::install_github("opetchey/microxanox",
-                             ref="main",
-                             auth_token = "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",
-                             build_vignettes = FALSE,
-                             force = TRUE)
+# devtools::install_github("opetchey/microxanox",
+#                              ref="main",
+#                              auth_token = "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",
+#                              build_vignettes = FALSE,
+#                              force = TRUE)
 
@@
 ```{r}
-var_expt <- run_ss_var_experiment()
-saveRDS(var_expt, here("experiments/experiment 2/data/ss_data.RDS"))
+#var_expt <- run_ss_var_experiment()
+#saveRDS(var_expt, here("experiments/experiment 2/data/ss_data.RDS"))
 
@@
 ```{r}
+var_expt <- readRDS(here("experiments/experiment 2/data/ss_data.RDS"))
 

### 2021-07-02 experiments/experiment 1/experiment 1.Rmd
Added version specification and temporary library for microxanox to experiments
re-knitted experiments

@@
 
-# devtools::install_github("opetchey/microxanox",
-#                              ref="main",
-#                              auth_token = "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",
-#                              build_vignettes = FALSE,
-#                              force = TRUE)
+microxanox_release <- "0.2"
+
+tmplib <- tempfile()
+dir.create(tmplib)
+
+### From '?remotes::install_github`:
+# auth_token	
+#   To install from a private repo, generate a personal access token (PAT) in
+#   "https://github.com/settings/tokens" and supply to this argument. This is 
+#   safer than using a password because you can easily delete a PAT without 
+#   affecting any others. Defaults to the GITHUB_PAT environment variable.
+
+remotes::install_github(
+  "opetchey/microxanox",
+  ref = microxanox_release,
+  # auth_token = "ENTER YOUR TOKEN or PROVED AS ENVIRONMENT VARIABLE",
+  build_vignettes = FALSE,
+  force = TRUE,
+  upgrade = FALSE,
+  lib = tmplib
+)
+
+library(microxanox, lib.loc = tmplib)
 
 library(tidyverse)
-library(microxanox)
 library(patchwork)
@@
 ```
+
+## Version of `microxinox` package used: `r packageVersion("microxanox") `
 
@@
 ```
+
+```{r finalise}

### 2021-07-03 experiments/experiment 1/experiment 1.Rmd
set up experiments

@@
 
-## Version of `microxinox` package used: `r packageVersion("microxanox") `
+## Version of `microxanox` package used: `r packageVersion("microxanox") `
 
@@
 
-num_div_treatment_levels <- 2
+num_div_treatment_levels <- 20
 ```
@@
 ```{r}
-sim_number <- 2
+sim_number <- num_div_treatment_levels
 sim_res_highvar <- run_simulation(parameter_values = var_expt$pars[[sim_number]],
@@
 ```{r}
-sim_number2 <- 2
+sim_number2 <- num_div_treatment_levels
 sim_res_highvar <- run_simulation(parameter_values = var_expt$pars[[sim_number2]],
@@
 ```{r}
-#var_expt <- run_ss_var_experiment()
-#saveRDS(var_expt, here("experiments/experiment 1/data/ss_data.RDS"))
+var_expt <- run_ss_var_experiment()
+saveRDS(var_expt, here("experiments/experiment 1/data/ss_data.RDS"))
 
@@
 ```{r}
-result_index2 <- 2
+result_index2 <- num_div_treatment_levels
 p2  <- plot_ss_result1(var_expt,

### 2021-07-03 experiments/experiment 3/experiment 3.Rmd
set up experiments

--- 2021-07-03 experiments/experiment 1/experiment 1.Rmd
@@
 ---
-title: "Experiment 1"
+title: "Experiment 3"
 author: "Owen Petchey"
@@
 CB_h_div <- -0.08
-SB_gmax_div <- 0.015789474
-SB_h_div <- -0.323
-PB_gmax_div <- 0.015789474
-PB_h_div <- -0.323
+SB_gmax_div <- 0.015789474 * 0
+SB_h_div <- -0.323  * 0
+PB_gmax_div <- 0.015789474  * 0
+PB_h_div <- -0.323  * 0
 

### 2021-07-03 experiments/experiment 4/experiment 4.Rmd
set up experiments

--- 2021-07-03 experiments/experiment 1/experiment 1.Rmd
@@
 num_PB_strains <- 9
-CB_gmax_div <- 0.015789474
-CB_h_div <- -0.08
+CB_gmax_div <- 0.015789474 * 0
+CB_h_div <- -0.08 * 0
 SB_gmax_div <- 0.015789474

### 2021-07-03 experiments/experiment 1/experiment 1.Rmd
update experiments

@@
 
-tmplib <- tempfile()
-dir.create(tmplib)
+#tmplib <- tempfile()
+#dir.create(tmplib)
 
@@
 
-remotes::install_github(
-  "opetchey/microxanox",
-  ref = microxanox_release,
-  # auth_token = "ENTER YOUR TOKEN or PROVED AS ENVIRONMENT VARIABLE",
-  build_vignettes = FALSE,
-  force = TRUE,
-  upgrade = FALSE,
-  lib = tmplib
-)
+# remotes::install_github(
+#   "opetchey/microxanox",
+#   ref = microxanox_release,
+#   # auth_token = "ENTER YOUR TOKEN or PROVED AS ENVIRONMENT VARIABLE",
+#   build_vignettes = FALSE,
+#   force = TRUE,
+#   upgrade = FALSE,
+#   lib = tmplib
+# )
 
-library(microxanox, lib.loc = tmplib)
+#library(microxanox, lib.loc = tmplib)
 
+library(microxanox)
 library(tidyverse)
@@
 
-ss_result1 <- var_expt[result_index1,]$ss_res[[1]]
-ss_result2 <- var_expt[result_index2,]$ss_res[[1]]
-xlims = c(-7, -1)
 ```
-
-```{r finalise}

### 2021-07-03 experiments/experiment 2/experiment 2.Rmd
update experiments

@@
 unity <- 1 ## don't change!!!
-options(mc.cores = 8)
+#options(mc.cores = 8)
 ```
@@
 CB_h_div <- -0.08
-SB_gmax_div <- 0.015789474 * 0.5
-SB_h_div <- -0.323 * 0.5
-PB_gmax_div <- 0.015789474 * 0.5
-PB_h_div <- -0.323 * 0.5
+SB_gmax_div <- 0.015789474 * 0
+SB_h_div <- -0.323 * 0
+PB_gmax_div <- 0.015789474 * 0
+PB_h_div <- -0.323 * 0
 
@@
 ```{r}
-#var_expt <- run_ss_var_experiment()
-#saveRDS(var_expt, here("experiments/experiment 2/data/ss_data.RDS"))
+var_expt <- run_ss_var_experiment()
+saveRDS(var_expt, here("experiments/experiment 2/data/ss_data.RDS"))
 
@@
 
-ss_result1 <- var_expt[result_index1,]$ss_res[[1]]
-ss_result2 <- var_expt[result_index2,]$ss_res[[1]]
-xlims = c(-7, -1)
+#ss_result1 <- var_expt[result_index1,]$ss_res[[1]]
+#ss_result2 <- var_expt[result_index2,]$ss_res[[1]]
+#xlims = c(-7, -1)
 ```

### 2021-07-03 experiments/experiment 3/experiment 3.Rmd
update experiments

@@
 num_PB_strains <- 9
-CB_gmax_div <- 0.015789474
-CB_h_div <- -0.08
-SB_gmax_div <- 0.015789474 * 0
-SB_h_div <- -0.323  * 0
-PB_gmax_div <- 0.015789474  * 0
-PB_h_div <- -0.323  * 0
+CB_gmax_div <- 0.015789474 * 0
+CB_h_div <- -0.08 * 0
+SB_gmax_div <- 0.015789474
+SB_h_div <- -0.323
+PB_gmax_div <- 0.015789474
+PB_h_div <- -0.323
 
@@
 var_expt <- run_ss_var_experiment()
-saveRDS(var_expt, here("experiments/experiment 1/data/ss_data.RDS"))
+saveRDS(var_expt, here("experiments/experiment 3/data/ss_data.RDS"))
 
@@
 ```{r}
-var_expt <- readRDS(here("experiments/experiment 1/data/ss_data.RDS"))
+var_expt <- readRDS(here("experiments/experiment 3/data/ss_data.RDS"))
 
@@
 
-ss_result1 <- var_expt[result_index1,]$ss_res[[1]]
-ss_result2 <- var_expt[result_index2,]$ss_res[[1]]
-xlims = c(-7, -1)
+#ss_result1 <- var_expt[result_index1,]$ss_res[[1]]
+#ss_result2 <- var_expt[result_index2,]$ss_res[[1]]
+#xlims = c(-7, -1)
 ```
-
-```{r finalise}

### 2021-07-05 manuscript/article.Rmd
figures and results to discuss

@@
                       message = FALSE,
-                      cache = TRUE)
+                      cache = FALSE)
 ```
@@
 library(here)
-source(here("simulations/r functions/various_useful_functions.r"))
+source(here("experiments/r functions/various_useful_functions.r"))
 ```
@@
 This report concerns how biodiversity influences the strength and nature of ecosystem responses to environmental change (figure 1; panel(a) three ovals, environment oval with arrow to ecosystem property oval, with biodiversity oval pointing the arrow between environment and ecosystem property; panel (b) shows linear response with different gradients, large being with low diversity; panel (c) shows a linear and a non-linear response starting and ending at the same place; panel (d) shows a hysteretic response, with greater or less range of hysteresis).
-Strong responses of ecosystems to environmental change imply high *sensitivity* and lack of resistance to environmental change, and higher temporal variability in the face of varying environmental conditions.
-Greater *non-linearity* in ecosystem responses increases the potential for surprises, such as when an ecosystem that was resistant to an environmental change becomes unexpectedly sensitive to further change.
-The presence and extent of *hysteresis* in ecosystem responses to environmental driver gradients concerns how readily are ecosystem responses reversed when environmental change is reversed.
+Strong responses of ecosystems to environmental change imply high sensitivity and lack of resistance to environmental change, and higher temporal variability in the face of varying environmental conditions.
+Greater non-linearity in ecosystem responses increases the potential for surprises, such as when an ecosystem that was resistant to an environmental change becomes unexpectedly sensitive to further change.
+The presence and extent of hysteresis in ecosystem responses to environmental driver gradients concerns how readily are ecosystem responses reversed when environmental change is reversed.
 
@@
 
--   In general, greater functional response diversity may decrease the likelihood of a catastrophic ecosystem response (Figure 2a in @dakos2019b).
+-   Greater functional response diversity may decrease the likelihood of a catastrophic ecosystem response (Figure 2a in @dakos2019b).
 Here, we interpret this prediction to be that greater functional response diversity decreases the non-linearity of ecosystem response to environmental driver change, including the extreme non-linearity that can occur when an ecosystem "flips" from one state to another one.
@@
 
-These explanations/predictions were based on the verbal/graphical argumentation @dakos2019b.
+These explanations/predictions were based on the verbal and graphical argumentation @dakos2019b.
 There were no mathematical models of ecosystem responses to environmental change behind the explanations/predictions.
-@ceulemans2021, in their article *Functional diversity alters the effects of a pulse perturbation on the dynamics of tritrophic food webs*, did employ a such a mathematical model [to be developed].
+@ceulemans2021, in their article *Functional diversity alters the effects of a pulse perturbation on the dynamics of tritrophic food webs*, did employ a such a mathematical model [text to be developed].
 
@@
 
-* To provide an answer to the question of how trait variation affects the non-linearity, resilience and hysteresis of ecosystem response to an environmental change.
+* To provide an answer to the question of how trait variation affects the resilience and hysteresis of ecosystem response to an environmental change.
 
@@
 
-* Mathematical modelling of a microbrial ecosystem. Trait diversity manipulation (can be considered selection among strains, or selection among species). (Do not include mutation or recomination).
+* Mathematical modelling of a microbial ecosystem.
 
-* Variation in amount of among strain variation, no variation in number of strains, no variation in strength or shape of the of any tradeoff.
+* Trait diversity manipulation (can be considered selection among strains, or selection among species). (Do not include mutation or recombination).
 
-* Measurement of the effect on how the steady state(s) of the system varies with in different environmental conditions, and on the dynamical response of system to gradual environmental change.
+* Variation in amount of among strain variation in two traits, no variation in number of strains, no variation in strength or shape of the of the tradeoff.
+
+* Illustration of the dynamical response to gradual environmental change.
+
+* Measurement of the effect trait diversity on how the steady state(s) of the system varies with environmental conditions.
 
@@
 ```{r ecosys_network, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
-knitr::include_graphics(here("manuscript/ecosystem_network.png"))
+knitr::include_graphics(here("manuscript/figures/ecosystem_network.png"))
 ```
@@
 
+```{r diversity_examples, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
+knitr::include_graphics(here("manuscript/figures/diversity_example.pdf"))
+```
+
+In this section we describe how we created variability among the multiple strains within functional groups.
+In brief, in each functional group we created multiple distinct strains that differed in their maximum growth rate and tolerance to an inhibiting substrate, with a trade-off between the two (e.g.
+higher tolerance assocated with lower maximum growth rate).
+An example of the resulting variation is displayed in Figure \ref(fig:diversity_example)).
+
+A more detailed account of the creation of strains follows now. Introducing variation among multiple strains within a functional group required a number of decisions:
+
+* **The number of strains.** The symbol for this is $n$ subscripted with the functional group code (CB = cyanobacteria, SP = sulphate reducing bacteria, and PB = phototrophic sulphur bacteria).
+E.g.
+$n_{CB}$ is the number of strains of cyanobacteria.
+[add why we only ever had 9].
+* **Which traits to introduce variation in.** We chose the maximum growth rate and the tolerance of growth to an inhibiting substrate.
+E.g.
+maximum growth rate of the cyanobacteria $G_{max,CB}$, and the tolerance of cyanobacterial growth to reduced sulphur $h_{SR,CB}$.
+* **The amount of among strain variation.** The symbol for this is $Div$ (from *Div*ersity) subscripted by the trait/parameter and the functional group.
+E.g.
+* $Div_{G_{max,CB}}$  is the amount of among strain variation in the maximum growth rate $G_{max}$ of the cyanobacteria $CB$.
+* **The correlation between variation in different traits.** This was always negative, so there was a tradeoff.
+Our implementation of the variation and tradeoff contain the assumption of a linear tradeoff of log-log transformed among-strain variation.
+* **The relative amount of among strain variation in different functional groups.** E.g.
+were strains of cyanobacteria very variable compared to strains of the other functional groups.
+We performed several numerical experiments, varying which functional groups had more or less among strain variation.
+* **The distribution of trait variation.** We chose to have among strain variation distributed evenly on a log scale.
+
+The parameters therefore necessary were:
+
+* $n_{CB}$ - number of strains of cyanobacteria.
+* $n_{SB}$ - number of strains of sulphate reducing bacteria.
+* $n_{PB}$ - number of strains of phototrophic sulphur bacteria.
+* $Div_{G_{max,CB}}$ - amount of among strain variation in the maximum growth rate $G_{max}$ of the cyanobacteria $CB$. 
+* $Div_{h_{SR,CB}}$ - amount of among strain variation in the tolerance $h$ of cyanobacteria $CB$ to reduced sulpur compounds $SR$. 
+* $Div_{G_{max,SB}}$ - amount of among strain variation in the maximum growth rate $G_{max}$ of the sulphate reducing bacteria $SB$. 
+* $Div_{h_{O,SB}}$ - amount of among strain variation in the tolerance $h$ of sulphate reducing bacteria $S$ to oxygen $O$. 
+* $Div_{G_{max,PB}}$ - amount of among strain variation in the maximum growth rate $G_{max}$ of the phototrophic sulphur bacteria $PB$. 
+* $Div_{h_{O,PB}}$ - amount of among strain variation in the tolerance $h$ of phototrophic sulphur bacteria $PB$ to oxygen $O$.
+
+For example, cyanobacteria, and a reference maximum growth rate parameter $G_{max,CB}$ and reference tolerance parameter $h_{SR,CB}$.
+Recall that amount of among strain variation is controlled by the two meta-parameters $Div_{G_{max,CB}}$ and $Div_{h_{SR,CB}}$.
+To create a tradeoff, the two meta-parameters were always of different sign.
+The among strain variation was calculated such that the growth rate of strain $i = 1$ was a factor $1/(2^{Div_{G_{max,CB}}})$ of the reference growth rate, and the growth rate of the $i = n$ strain was a factor $2^{Div_{G_{max,CB}}}$ of the reference growth rate.
+The growth rate of the $i = \{2,...n-1\}$ other strains was the reference growth rate multiplied by a factor that was equally distributed between the factor of the $i = 1$ and $i = n$ strain.
+This implementation of the variation and trade-off contains the assumption of a linear trade-off of log-log transformed among-strain variation.
+
 ```{r echo = FALSE}
@@
 
-In this section we describe how we created variability among the multiple strains within functional groups.
-Introducing variation among multiple strains within a functional group required a number of decisions:
-
-* **The number of strains.** The symbol for this is $n$ subscripted with the functional group code (CB = cyanobacteria, SP = sulphate reducing bacteria, and PB = phototrophic sulphur bacteria).
-E.g.
-$n_{CB}$ is the number of strains of cyanobacteria.
-[add why we only ever had 9].
-* **Which traits to introduce variation in.** We chose the maximum growth rate and the tolerance of growth to an inhibiting substrate.
-E.g.
-maximum growth rate of the cyanobacteria $G_{max,CB}$, and the tolerance of cyanobacterial growth to reduced sulphur $h_{SR,CB}$.
-* **The amount of among strain variation.** The symbol for this is $Div$ (from *Div*ersity) subscripted by the trait/parameter and the functional group.
-E.g.
-* $Div_{G_{max,CB}}$  is the amount of among strain variation in the maximum growth rate $G_{max}$ of the cyanobacteria $CB$.
-* **The correlation between variation in different traits.** This was always negative, so there was a tradeoff.
-Our implementation of the variation and tradeoff contain the assumption of a linear tradeoff of log-log transformed among-strain variation.
-* **The relative amount of among strain variation in different functional groups.** E.g.
-were strains of cyanobacteria very variable compared to strains of the other functional groups.
-We performed several numerical experiments, varying which functional groups had more or less among strain variation.
-
-* $n_{CB}$ - number of strains of cyanobacteria.
-* $n_{SB}$ - number of strains of sulphate reducing bacteria.
-* $n_{PB}$ - number of strains of phototrophic sulphur bacteria.
-* $Div_{G_{max},CB}$ - amount of among strain variation in the maximum growth rate $G_{max}$ of the cyanobacteria $CB$. 
-* $Div_{h,CB}$ - amount of among strain variation in the maximum growth rate $G_{max}$ of the cyanobacteria $CB$. 
-* $Div_{G_{max},SB}$ - amount of among strain variation in the maximum growth rate $G_{max}$ of the sulphate reducing bacteria $SB$. 
-* $Div_{h,SB}$ - amount of among strain variation in the maximum growth rate $G_{max}$ of the sulphate reducing bacteria $SB$. 
-* $Div_{G_{max},PB}$ - amount of among strain variation in the maximum growth rate $G_{max}$ of the phototrophic sulphur bacteria $PB$. 
-* $Div_{h,PB}$ - amount of among strain variation in the maximum growth rate $G_{max}$ of the phototrophic sulphur bacteria $PB$.
-
-We introduced among-strain variability in maximum growth rate (parameter $G_{max}$) and in the tolerance to the relevant inhibiting chemical substrate (parameter $h$).
-Among-strain variability was created such that there was a tradeoff between maximum growth rate and tolerance (i.e.
-high tolerance coinciding with low maximum growth rate) (e.g.
-Figure \@ref(fig:tradeoff).
-Our implementation of the variation and tradeoff contain the assumption of a linear tradeoff of log-log transformed among-strain variation.
-
-```{r tradeoff, include = TRUE, echo = FALSE, out.width="0.5\\linewidth", fig.align="center", fig.cap=c("An example of among-strain variation in growth rate and tolerance, and the tradeoff in the variation.")}
+```{r tradeoff, eval = FALSE, include = TRUE, echo = FALSE, out.width="0.5\\linewidth", fig.align="center", fig.cap=c("An example of among-strain variation in growth rate and tolerance, and the tradeoff in the variation.")}
 ggplot() +
@@
 
-For further understanding, please consider a reference maximum growth rate parameter $G_{max}$ and reference tolerance parameter $h$.
-Furthermore, consider the meta-parameters $Div_{G_{max}}$ and $Div_{h}$, which determine the amount of variation among $n$-strains in the growth rate and tolerance parameters.
-To create a tradeoff, the two meta-parameters were always of different sign.
+Hence, for example, with the reference growth rate $G_{max,CB} =$ `r G_max`, among strain variation of $Div_{G_{max,CB}} =$ `r Div_G_max`, and nine strains ($n =$ `r n`), then the growth rates of the nine strains are `r round(G_max_i,3)` (Figure to be added).
 
-The among strain variation was calculated such that the growth rate of strain $i = 1$ was a factor $1/(2^{Div_{G_{max}}})$ of the reference growth rate, and the growth rate of the $i = n$ strain was a factor $2^{Div_{G_{max}}}$ of the reference growth rate.
-The growth rate of the $i = \{2,...n-1\}$ other strains was the reference growth rate multiplied by a factor that was equally distributed between the factor of the $i = 1$ and $i = n$ strain.
-
-Hence, for example, with the reference growth rate $G_{max} =$ `r G_max`, among strain variation of $Div_{G_{max}} =$ `r Div_G_max`, and nine strains ($n =$ `r n`), then the growth rates of the nine strains are `r round(G_max_i,3)` (Figure \@ref(fig:tradeoff).
-
-(Put another way, the growth rate parameter of the i-th of the $n$ strains in a functional group was calculated as $G_{max, i} = D_i * G_{max}$ where D_i is the i-th element of the set $D = \{2^{f(x)Div_{G_{max}}} | x \in \mathbb{N}, x \leq n\}$, where $f(x) = (x-(n+1)/2) / (( n-1)/2)$.)
+(Put another way, the growth rate parameter of the i-th of the $n$ strains in a functional group was calculated as $G_{max, i} = D_i * G_{max}$ where $D_i$ is the i-th element of the set $D = \{2^{f(x)Div_{G_{max}}} | x \in \mathbb{N}, x \leq n\}$, where $f(x) = (x-(n+1)/2) / (( n-1)/2)$.)
 
@@
 
-```{r ss_novar, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("No diversity"), echo=FALSE}
-CBSBPB_data <- readRDS(here("simulations/expt2/data/ss_res_grad_CBSBPB_var.RDS"))
+```{r ss_novar, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Steady states of the ecosystem with no trait diversity, i.e.
+identical trait values for the strains within a functional group."), echo=FALSE}
+CBSBPB_data <- readRDS(here("experiments/experiment 1/data/ss_data.RDS"))
 result_index1 <- 1
@@
 
-```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in all functional groups"), echo=FALSE}
+```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Steady states of the ecosystem with diversity in all functional groups"), echo=FALSE}
 result_index2 <- 20
@@
 
-```{r ss_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in none (solid) and all functional groups."), echo=FALSE}
+```{r ss_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Steady states of the ecosystem without any diversity (solid line) and with diversity in all three functional groups."), echo=FALSE}
 p_overlay <- plot_ss_result2(CBSBPB_data[result_index1,]$ss_res[[1]],
@@
 
-```{r CB_var1, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in CB functional group."), echo=FALSE}
-CB_data <- readRDS(here("simulations/expt1/data/ss_res_grad_CB_var.RDS"))
+```{r CB_var1, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Steady states of the ecosystem with diversity in only the cyanobacteria functional group."), echo=FALSE}
+CB_data <- readRDS(here("experiments/experiment 2/data/ss_data.RDS"))
 p3  <- plot_ss_result1(CB_data,
@@
 
-```{r CB_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in none (solid) and CB functional groups."), echo=FALSE}
+```{r CB_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Steady states of the ecosystem without any diversity (solid line) and with diversity in only the cyanobacteria functional group."), echo=FALSE}
 p_overlay <- plot_ss_result2(CB_data[result_index1,]$ss_res[[1]],
@@
 
-## Figure: SB Stable states with variation and tradeoff
-
-```{r SB_var1, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in SB functional group."), echo=FALSE}
-SB_data <- readRDS(here("simulations/expt1/data/ss_res_grad_SB_var.RDS"))
-p4  <- plot_ss_result1(SB_data,
-                result_index = result_index2,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p4
-
-```
-
-```{r SB_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in none (solid) and SB functional group."), echo=FALSE}
-p_overlay <- plot_ss_result2(CB_data[result_index1,]$ss_res[[1]],
-                             SB_data[result_index2,]$ss_res[[1]],
-                             xlims = c(-7, -1))
-
-p_overlay
-```
-
-## Figure: PB Stable states with variation and tradeoff
-
-```{r PB_var1, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in PB functional group."), echo=FALSE}
-PB_data <- readRDS(here("simulations/expt1/data/ss_res_grad_PB_var.RDS"))
-p5  <- plot_ss_result1(PB_data,
-                result_index = result_index2,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p5
-
-```
-
-```{r PB_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in none (solid) and PB functional group."), echo=FALSE}
-p_overlay <- plot_ss_result2(CB_data[result_index1,]$ss_res[[1]],
-                             PB_data[result_index2,]$ss_res[[1]],
-                             xlims = c(-7, -1))
-
-p_overlay
-```
-
 ## Figure: SBPB Stable states with variation and tradeoff
 
-```{r SBPB_var1, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in SB and PB functional groups."), echo=FALSE}
-SBPB_data <- readRDS(here("simulations/expt1/data/ss_res_grad_SBPB_var.RDS"))
+```{r SBPB_var1, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Steady states of the ecosystem with diversity in only the two sulphur bacteria functional groups."), echo=FALSE}
+SBPB_data <- readRDS(here("experiments/experiment 3/data/ss_data.RDS"))
 p6  <- plot_ss_result1(SBPB_data,
@@
 
-```{r SBPB_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in none (solid) and SB and PB functional groups."), echo=FALSE}
+```{r SBPB_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Steady states of the ecosystem without any diversity (solid line) and with diversity in only the sulphur bacteria functional group."), echo=FALSE}
 p_overlay <- plot_ss_result2(CB_data[result_index1,]$ss_res[[1]],
@@
 
-```{r echo=FALSE, eval = FALSE}
-#ss_sim_data <- readRDS(here("simulations/expt1/data/ss_res_3.RDS"))
+```{r stab1, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Effect of increasing amounts of trait diversity on the extent of the environmental gradient for which bistability (i.e.
+alternative stable states) is present, when different combinations of the three functional groups contain any diversity."), echo=FALSE}
 
-CBSBPB_stab_data <- CBSBPB_data %>%
-  group_by(CB_var_gmax_s, CB_var_h_s,
-           SB_var_gmax_s, SB_var_h_s,
-           PB_var_gmax_s, PB_var_h_s) %>%
-  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
-results1 <- unnest(CBSBPB_stab_data, cols = c(stability_measures)) %>%
-  mutate(var_treat = "CB-SB-PB",
-         var_gmax = CB_var_gmax_s)
-
-CB_stab_data <- CB_data %>%
-  group_by(CB_var_gmax_s, CB_var_h_s,
-           SB_var_gmax_s, SB_var_h_s,
-           PB_var_gmax_s, PB_var_h_s) %>%
-  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
-results2 <- unnest(CB_stab_data, cols = c(stability_measures))  %>%
-  mutate(var_treat = "CB",
-         var_gmax = CB_var_gmax_s)
-
-SB_stab_data <- SB_data %>%
-  group_by(CB_var_gmax_s, CB_var_h_s,
-           SB_var_gmax_s, SB_var_h_s,
-           PB_var_gmax_s, PB_var_h_s) %>%
-  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
-
-# for(i in 1:20) {
-#   print(i)
-#   junk <- get_stability_measures(SB_data$ss_res[[i]])
-# }
-# ss_object <- SB_data$ss_res[[11]]
-# 
-# temp2 <- filter(temp, Species == "PB_1")
-# get_hysteresis_total(log10(temp2$up+1), log10(temp2$down+1))
-# down <- log10(temp2$down+1)
-# up <- log10(temp2$up+1)
-#
-
-results3 <- unnest(SB_stab_data, cols = c(stability_measures))  %>%
-  mutate(var_treat = "SB",
-         var_gmax = SB_var_gmax_s)
-
-PB_stab_data <- PB_data %>%
-  group_by(CB_var_gmax_s, CB_var_h_s,
-           SB_var_gmax_s, SB_var_h_s,
-           PB_var_gmax_s, PB_var_h_s) %>%
-  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
-results4 <- unnest(PB_stab_data, cols = c(stability_measures))  %>%
-  mutate(var_treat = "PB",
-         var_gmax = PB_var_gmax_s)
-
-SBPB_stab_data <- SBPB_data %>%
-  group_by(CB_var_gmax_s, CB_var_h_s,
-           SB_var_gmax_s, SB_var_h_s,
-           PB_var_gmax_s, PB_var_h_s) %>%
-  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
-results5 <- unnest(SBPB_stab_data, cols = c(stability_measures))  %>%
-  mutate(var_treat = "SB-PB",
-         var_gmax = SB_var_gmax_s)
-
-all_stab_results <- results1 %>%
-  bind_rows(results2) %>%
-  bind_rows(results3) %>%
-  bind_rows(results4) %>%
-  bind_rows(results5)
-
-all_stab_results<- all_stab_results %>%
-  mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB", "PB", "SB-PB", "CB-SB-PB")))
-
-saveRDS(all_stab_results, here("simulations/sim data/stab_measures.RDS"))
+knitr::include_graphics(here("manuscript/figures/extent_of_bistab1.pdf"))
 
@@
 
-```{r ss_var3, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
+```{r stab2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Effect of increasing amounts of trait diversity on the upper and lower bound of the environmental gradient for which bistability (i.e.
+alternative stable states) is present, when different combinations of the three functional groups contain any diversity."), echo=FALSE}
 
-all_stab_results <- readRDS(here("simulations/expt1/data/stab_measures.RDS"))
-
-all_stab_results %>%
-  filter(Species == "O") %>%
-  ggplot(aes(x = var_gmax, y = hyst_range, col=var_treat)) +
-  geom_point() +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
-  labs(col = "Community\ncomposition")
-```
-
-```{r ss_var4, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
-all_stab_results %>%
-  #filter(var_treat == "CB") %>%
-  filter(Species == "O") %>%
-  ggplot(aes(x = var_gmax,
-             ymin = hyst_min,
-             ymax = hyst_max,
-             fill=var_treat)) +
-  geom_ribbon(alpha = 0.5) +
-  facet_wrap( ~ var_treat) +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
-  labs(fill = "Community\ncomposition")
+knitr::include_graphics(here("manuscript/figures/extent_of_bistab2.pdf"))
 
@@
 
-## Figure: Temporal switches
+# Discussion
 
-Maybe... to be added. Need to go both ways (oxic to anoxic, and anoxic to oxic).
+We observed that greater trait diversity among the organisms dominating the prevailing ecosystem state can lead to greater resilience of that state.
+We also observed that greater trait diversity among the organisms that occur in an different ecosystem state can reduce resilience.
 
-# Discussion
+The effect of diversity occurs because with greater trait diversity there is a organism with greater tolerance to the deteriorating (from the perspective of the dominant organisms).
+This greater tolerance means that a greater amount of environmental deterioration is required to cause the ecosystem to flip into the alternative state.
+
+In the case study, with three functional groups, the presence or absence of diversity in the different functional groups influences resilience... with only diversity in the CB...
 

### 2021-07-05 experiments/experiment summary/summarise.R

@@ -1,0 +1,85 @@
+rm(list = ls())
+
+library(here)
+library(tidyverse)
+library(microxanox)
+
+CBSBPB_data <- readRDS(here("experiments/experiment 1/data/ss_data.RDS"))
+CB_data <- readRDS(here("experiments/experiment 2/data/ss_data.RDS"))
+SBPB_data <- readRDS(here("experiments/experiment 3/data/ss_data.RDS"))
+
+
+
+CBSBPB_stab_data <- CBSBPB_data %>%
+  group_by(CB_var_gmax_s, CB_var_h_s,
+           SB_var_gmax_s, SB_var_h_s,
+           PB_var_gmax_s, PB_var_h_s) %>%
+  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
+results1 <- unnest(CBSBPB_stab_data, cols = c(stability_measures)) %>%
+  mutate(var_treat = "CB-SB-PB",
+         var_gmax = CB_var_gmax_s)
+
+CB_stab_data <- CB_data %>%
+  group_by(CB_var_gmax_s, CB_var_h_s,
+           SB_var_gmax_s, SB_var_h_s,
+           PB_var_gmax_s, PB_var_h_s) %>%
+  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
+results2 <- unnest(CB_stab_data, cols = c(stability_measures))  %>%
+  mutate(var_treat = "CB",
+         var_gmax = CB_var_gmax_s)
+
+
+SBPB_stab_data <- SBPB_data %>%
+  group_by(CB_var_gmax_s, CB_var_h_s,
+           SB_var_gmax_s, SB_var_h_s,
+           PB_var_gmax_s, PB_var_h_s) %>%
+  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
+results5 <- unnest(SBPB_stab_data, cols = c(stability_measures))  %>%
+  mutate(var_treat = "SB-PB",
+         var_gmax = SB_var_gmax_s)
+
+
+all_stab_results <- results1 %>%
+  bind_rows(results2) %>%
+#  bind_rows(results3) %>%
+ # bind_rows(results4) %>%
+  bind_rows(results5)
+
+all_stab_results<- all_stab_results %>%
+    mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB-PB", "CB-SB-PB")))
[…]

### 2021-07-09 experiments/experiment 1/experiment 1.Rmd
figures and results to discuss
Change installation of microxanox in experiments

@@
 # remotes::install_github(
-#   "opetchey/microxanox",
-#   ref = microxanox_release,
+#   "UZH-PEG/microxanox",
+#   ref = "0.2",
 #   # auth_token = "ENTER YOUR TOKEN or PROVED AS ENVIRONMENT VARIABLE",
@@
 #   force = TRUE,
-#   upgrade = FALSE,
-#   lib = tmplib
+#   upgrade = FALSE
 # )
-
-#library(microxanox, lib.loc = tmplib)
 
@@
 ```{r}
-options(mc.cores = 6)
+options(mc.cores = 4)
 ```

### 2021-07-09 experiments/experiment 2/experiment 2.Rmd
figures and results to discuss
Change installation of microxanox in experiments

@@
 #   force = TRUE,
-#   upgrade = FALSE,
-#   lib = tmplib
+#   upgrade = FALSE
 # )

### 2021-07-09 experiments/experiment 1/experiment 1.Rmd
New microxanox version 0.2.1 - no functinal changes

@@
 
-microxanox_release <- "0.2"
+microxanox_release <- "0.2.1"
 
@@
 #   "UZH-PEG/microxanox",
-#   ref = "0.2",
+#   ref = microxanox_release,
 #   # auth_token = "ENTER YOUR TOKEN or PROVED AS ENVIRONMENT VARIABLE",

### 2021-07-15 experiments/experiment 4/experiment 4.Rmd
add experiment 4 (factorial)

--- 2021-07-03 experiments/experiment 1/experiment 1.Rmd
@@
 ---
-title: "Experiment 1"
+title: "Experiment 4"
 author: "Owen Petchey"
@@
 ```{r}
-var_expt <- create_diversity()
+var_expt <- create_diversity_factorial()
 ```
@@
 
+```{r}
+eval_dynamics_flag <- FALSE
+```
+
 ## Oxic to anoxic
@@
 
-```{r}
+```{r eval = eval_dynamics_flag}
 default_sim_duration <- 80000
@@
 
-```{r}
+```{r eval = eval_dynamics_flag}
 sim_number <- 1
@@
 
-```{r}
+```{r eval = eval_dynamics_flag}
 sim_number <- num_div_treatment_levels
@@
 
-```{r}
+```{r eval = eval_dynamics_flag}
 default_sim_duration <- 60000
@@
 
-```{r}
+```{r eval = eval_dynamics_flag}
 default_sim_duration <- 1000000
@@
 
-```{r}
+```{r eval = eval_dynamics_flag}
 default_minimum_abundances <- rep(100, 3)
@@
 
-```{r}
+```{r eval = eval_dynamics_flag}
 sim_number1 <- 1
@@
 
-```{r}
+```{r eval = eval_dynamics_flag}
 sim_number2 <- num_div_treatment_levels
@@
 
-```{r}
+```{r eval = eval_dynamics_flag}
 visualise_temporal_env_eco()
@@
 ```{r}
-options(mc.cores = 6)
+options(mc.cores = 12)
 ```
@@
 ssfind_event_interval <- ssfind_simulation_duration
-grid_num_a <- 1000 ## number of a_0 values
+grid_num_a <- 1000 #usually 1000 ## number of a_0 values
 a_Os <- 10^seq(-7, -1, length=grid_num_a) ## sequence of a_0 values
@@
 var_expt <- run_ss_var_experiment()
-saveRDS(var_expt, here("experiments/experiment 1/data/ss_data.RDS"))
+saveRDS(var_expt, here("experiments/experiment 4/data/ss_data.RDS"))
 
@@
 ```{r}
-var_expt <- readRDS(here("experiments/experiment 1/data/ss_data.RDS"))
+var_expt <- readRDS(here("experiments/experiment 4/data/ss_data.RDS"))
 
@@
 
-ss_result1 <- var_expt[result_index1,]$ss_res[[1]]
-ss_result2 <- var_expt[result_index2,]$ss_res[[1]]
-xlims = c(-7, -1)
 ```
 
-```{r finalise}
+```{r}
+stab_data <- var_expt %>%
+  group_by(CB_var_gmax_s, CB_var_h_s,
+           SB_var_gmax_s, SB_var_h_s,
+           PB_var_gmax_s, PB_var_h_s) %>%
+  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
+stab_data <- unnest(stab_data, cols = c(stability_measures))
+
+```

### 2021-07-17 experiments/experiment 1/experiment 1.Rmd
correct colour order issue

@@
 output:
+  pdf_document: default
   html_document:
@@
 var_expt <- create_diversity()
+
+var_expt[["pars"]][[20]]$CB
+var_expt[["pars"]][[20]]$SB
+var_expt[["pars"]][[20]]$PB
+
 ```
@@
 ```{r}
-options(mc.cores = 4)
+options(mc.cores = 12)
 ```
@@
 var_expt <- run_ss_var_experiment()
-saveRDS(var_expt, here("experiments/experiment 1/data/ss_data.RDS"))
+saveRDS(var_expt, here("experiments/experiment 1/data/ss_data_latest.RDS"))
 
@@
 ```{r}
-var_expt <- readRDS(here("experiments/experiment 1/data/ss_data.RDS"))
+var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_latest.RDS"))
 
@@
 ```
+
+## negative abundance investigation
+
+```{r}
+
+var_expt$pars[[1]]
+dd <- var_expt$ss_res[[1]]
+dd1 <- filter(dd, PB_1<(-0.0001))
+dd1$a_O
+
+a_Os <- a_Os[355]
+ss_expt <- expand.grid(N_CB = initial_CBs,
+                      N_PB = initial_PBs,
+                      N_SB = initial_SBs,
+                      a_O = a_Os)
+
+var_expt_master <- var_expt
+var_expt <- var_expt[1,]
+var_expt_test <- run_ss_var_experiment()
+res <- var_expt_test$ss_res[[1]]
+#saveRDS(var_expt, here("experiments/experiment 1/data/ss_data.RDS"))
+
+sim_number <- 1
+log10_a <- log10(a_Os[355]) ## very slowly goes anoxic
+#log10_a <- log10(a_Os[354]) ## very slowly goes anoxic
+#log10_a <- log10(a_Os[356]) ## very very very  slowly goes anoxic
+#log10_a <- log10(a_Os[357]) ## does not go anoxic
+
+default_log10a_series <- c(log10_a, log10_a)
+initial_state <- new_initial_state(num_CB_strains,
+                                   num_PB_strains,
+                                   num_SB_strains,
+                                   values = "bush_ssfig3")
+initial_state[grep("CB_", names(initial_state))] <- 10^10/num_CB_strains
+sim_res_novar <- run_simulation(parameter_values = var_expt$pars[[sim_number]],
+                          initial_state = initial_state)
+plot_dynamics(sim_res_novar)
+#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
+
+```

### 2021-07-17 experiments/experiment 3/experiment 3.Rmd
correct colour order issue

@@
 ```{r}
-var_expt <- run_ss_var_experiment()
-saveRDS(var_expt, here("experiments/experiment 3/data/ss_data.RDS"))
+#var_expt <- run_ss_var_experiment()
+#saveRDS(var_expt, here("experiments/experiment 3/data/ss_data.RDS"))
 

### 2021-07-18 experiments/experiment 4/experiment 4.Rmd
remove large negative abundances
explanation in "various_useful_functions" file and at the end of the two experiment files (1 and 4)

@@
 ```
+
+## negative abundance investigation
+
+I (Owen) found that the sampling interval had an effect on the stability of the simulation.
+If the sampling interval was long, then in some rare cases (see below) the odesolver failed, with negative abundances occuring.
+I think this is due to abundances becoming very small, and then the computer having trouble with precision.
+I guess that when a sample is taken, the abundance is somehow altered if it is very low, probably by some rounding.
+
+```{r}
+var_expt$pars[[1]]
+dd <- var_expt$ss_res[[1]]
+dd1 <- filter(dd, PB_1<(-0.0001))
+dd1$a_O
+
+ss_expt_master <- ss_expt
+ss_expt <- ss_expt_master[abs(ss_expt_master$a_O - 1.336984e-05)<1e-10,]
+
+var_expt_master <- var_expt
+#var_expt <- var_expt[1,]
+var_expt_test <- run_ss_var_experiment()
+res <- var_expt_test$ss_res[[1]]
+
+test1 <- ss_by_a_N(ss_expt, var_expt$pars[[1]])
+x <- ss_expt[2,]
+param <- var_expt$pars[[1]]
+get_final_states_a_N(x, param)
+ssfind_parameters <- param
+ssfind_simulation_sampling_interval <- 1000
+## now run inside the function "get_final_states_a_N"
+simres1 <- simres
+ssfind_simulation_sampling_interval <- 5000
+## now run inside the function "get_final_states_a_N"
+simres2 <- simres  # this fails
+
+## now run inside the function "get_final_states_a_N"
+plot_dynamics(simres2)
+
+ggplot() +
+  geom_line(data = simres1$result,
+             mapping = aes(x = time, y = log10(PB_1))) +
+  geom_point(data = simres2$result,
+             mapping = aes(x = time, y = log10(PB_1))) +
+  xlim(c(0, 250000))
+
+ccc <- simres2$result
+
+simres2$result$PB_1
+simres2$result$time
+
+log10_a <- log10(ss_expt$a_O[1]) ## very slowly goes anoxic
+#log10_a <- log10(a_Os[354]) ## very slowly goes anoxic
+#log10_a <- log10(a_Os[356]) ## very very very  slowly goes anoxic
+#log10_a <- log10(a_Os[357]) ## does not go anoxic
+
+default_dynamic_model <- bushplus_dynamic_model
+default_event_definition <- event_definition_1
+default_event_interval <- ssfind_simulation_duration
+default_noise_sigma <- 0
+default_minimum_abundances <- ssfind_minimum_abundances
+default_sim_duration <- ssfind_simulation_duration
+default_sim_sample_interval <- ssfind_simulation_duration
+#initial_pars_from <- "bush_ssfig3"
+
+default_log10a_series <- c(log10_a, log10_a)
+initial_state <- new_initial_state(num_CB_strains,
+                                   num_PB_strains,
+                                   num_SB_strains,
+                                   values = "bush_ssfig3")
+initial_state[grep("CB_", names(initial_state))] <- 10^10/num_CB_strains
+sim_res_novar <- run_simulation(parameter_values = var_expt$pars[[1]],
+                          initial_state = initial_state)
+plot_dynamics(sim_res_novar)
+
+simulation_result <- sim_res_novar
+every_n <- 1
+
+chk <- sim_res_novar$result
+
+sim_res_novar$result %>%
+  ggplot() +
+  geom_line(mapping = aes(x = time, y = PB_1))
+
+#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
+
+```

### 2021-07-18 experiments/experiment 1/experiment-1.Rmd
new experiment 1 sorted

---
title: "experiment 1"
author: "Owen Petchey"
date: "6/25/2021"
output:
  pdf_document: default
  html_document:
    keep_md: yes
---

This experiment supercedes all previous ones.
It is a factorial manipulation of diversity of the three groups.
It takes about 50 hours to run while using 12 cores.

# Setup

## R

```{r}

rm(list = ls())

knitr::opts_knit$set(progress = TRUE, verbose = FALSE, cache = TRUE)

microxanox_release <- "0.2"

#tmplib <- tempfile()
#dir.create(tmplib)

### From '?remotes::install_github`:
# auth_token	
#   To install from a private repo, generate a personal access token (PAT) in
#   "https://github.com/settings/tokens" and supply to this argument. This is 
#   safer than using a password because you can easily delete a PAT without 
#   affecting any others. Defaults to the GITHUB_PAT environment variable.

# remotes::install_github(
#   "opetchey/microxanox",
#   ref = microxanox_release,
#   # auth_token = "ENTER YOUR TOKEN or PROVED AS ENVIRONMENT VARIABLE",
#   build_vignettes = FALSE,
#   force = TRUE,
#   upgrade = FALSE,
#   lib = tmplib
# )

#library(microxanox, lib.loc = tmplib)

library(microxanox)
library(tidyverse)
library(patchwork)
library(here)
source(here("experiments/r functions/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
#options(mc.cores = 8)
eval_dynamics_flag <- FALSE
```

## Version of `microxanox` package used: `r packageVersion("microxanox") `

## General simulation conditions

```{r}
default_dynamic_model <- bushplus_dynamic_model
default_event_definition <- event_definition_1
default_event_interval <- 100
default_noise_sigma <- 0
default_minimum_abundances <- rep(1, 3)
names(default_minimum_abundances) <- c("CB", "PB", "SB")
default_sim_duration <- 80000
default_sim_sample_interval <- 100
initial_pars_from <- "bush_ssfig3"
## note that next line (log10a_series is over-ridden with getting stable states)
#default_log10a_series <- c(-2, -2, -2, -2, -10, -10, -10, -10, -10)
```

## Define diversity

```{r}
num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9
CB_gmax_div <- 0.015789474
CB_h_div <- -0.08
SB_gmax_div <- 0.015789474
SB_h_div <- -0.323
PB_gmax_div <- 0.015789474
PB_h_div <- -0.323

num_div_treatment_levels <- 20
```

## Create diversity

```{r}
var_expt <- create_diversity_factorial()
```

## Display diversity

```{r}
display_diversity(400)
```

# Temporal switching

```{r}
var_expt_levels <- var_expt[,1:6]

no_diversity <- which(rowSums(abs(var_expt_levels))==0)
max_diversty_all <- which(max(rowSums(abs(var_expt_levels))) ==
                            rowSums(abs(var_expt_levels)))
max_only_CB_diversity <- which(max(rowSums(abs(var_expt_levels[,1:2]))) ==
                            rowSums(abs(var_expt_levels[,1:2])) &
                              rowSums(abs(var_expt_levels[,3:6]))==0)
#var_expt_levels[381,]

max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
                            rowSums(abs(var_expt_levels[,3:6])) &
                              rowSums(abs(var_expt_levels[,1:2]))==0)
#var_expt_levels[20,]

```

## Oxic to anoxic

### No diversity

```{r eval = eval_dynamics_flag}
default_sim_duration <- 80000
```

```{r eval = eval_dynamics_flag}
default_log10a_series <- c(-1, -7, -7)
initial_state <- new_initial_state(num_CB_strains,
                                   num_PB_strains,
                                   num_SB_strains,
                                   values = "bush_ssfig3")
initial_state[grep("CB_", names(initial_state))] <- 10^10/num_CB_strains
sim_res_novar1 <- run_simulation(parameter_values = var_expt$pars[[no_diversity]],
                          initial_state = initial_state)
saveRDS(sim_res_novar1, here("experiments/experiment 1/data/sim_res_novar1.RDS"))
```

```{r}
sim_res_novar1 <- readRDS(here("experiments/experiment 1/data/sim_res_novar1.RDS"))
plot_dynamics(sim_res_novar1)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

### Maximum diversity

```{r eval = eval_dynamics_flag}
sim_number <- num_div_treatment_levels
sim_res_highvar1 <- run_simulation(parameter_values = var_expt$pars[[max_diversty_all]],
                          initial_state = initial_state)
saveRDS(sim_res_highvar1, here("experiments/experiment 1/data/sim_res_highvar1.RDS"))
```

```{r}
sim_res_highvar1 <- readRDS(here("experiments/experiment 1/data/sim_res_highvar1.RDS"))
plot_dynamics(sim_res_highvar1)
#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)

```

## Anoxic to oxic

### No diversity

```{r eval = eval_dynamics_flag}
default_sim_duration <- 60000
```

```{r eval = eval_dynamics_flag}
sim_number <- 1
default_log10a_series <- c(-5, -3, -1, -1)
initial_state <- new_initial_state(num_CB_strains,
                                   num_PB_strains,
                                   num_SB_strains,
                                   values = "bush_ssfig3")
initial_state[grep("CB_", names(initial_state))] <- 10/num_CB_strains
sim_res_novar2 <- run_simulation(parameter_values = var_expt$pars[[no_diversity]],
                          initial_state = initial_state)
saveRDS(sim_res_novar2, here("experiments/experiment 1/data/sim_res_novar2.RDS"))
```

```{r}
sim_res_novar2 <- readRDS(here("experiments/experiment 1/data/sim_res_novar2.RDS"))
plot_dynamics(sim_res_novar2)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

### Maximum diversity

```{r eval = eval_dynamics_flag}
sim_number <- num_div_treatment_levels
sim_res_highvar2 <- run_simulation(parameter_values = var_expt$pars[[max_diversty_all]],
                          initial_state = initial_state)
saveRDS(sim_res_highvar2, here("experiments/experiment 1/data/sim_res_highvar2.RDS"))
```

```{r}
sim_res_highvar2 <- readRDS(here("experiments/experiment 1/data/sim_res_highvar2.RDS"))
plot_dynamics(sim_res_highvar2)
#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)

```

## Anoxic to oxic to anoxic

### No diversity

```{r eval = eval_dynamics_flag}
default_sim_duration <- 1000000
```

```{r eval = eval_dynamics_flag}
default_minimum_abundances <- rep(100, 3)
names(default_minimum_abundances) <- c("CB", "PB", "SB")
```

```{r eval = eval_dynamics_flag}
sim_number1 <- 1
default_log10a_series <- c(-1, -8, -1)
initial_state <- new_initial_state(num_CB_strains,
                                   num_PB_strains,
                                   num_SB_strains,
                                   values = "bush_ssfig3")
initial_state[grep("CB_", names(initial_state))] <- 10/num_CB_strains
sim_res_novar3 <- run_simulation(parameter_values = var_expt$pars[[no_diversity]],
                          initial_state = initial_state)
saveRDS(sim_res_novar3, here("experiments/experiment 1/data/sim_res_novar3.RDS"))
```

```{r}
sim_res_novar3 <- readRDS(here("experiments/experiment 1/data/sim_res_novar3.RDS"))
plot_dynamics(sim_res_novar3)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

### Maximum diversity

```{r eval = eval_dynamics_flag}
sim_number2 <- num_div_treatment_levels
sim_res_highvar3 <- run_simulation(parameter_values = var_expt$pars[[max_diversty_all]],
                          initial_state = initial_state)
saveRDS(sim_res_highvar3, here("experiments/experiment 1/data/sim_res_highvar3.RDS"))
```

```{r}
sim_res_highvar3 <- readRDS(here("experiments/experiment 1/data/sim_res_highvar3.RDS"))
plot_dynamics(sim_res_highvar3)
#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)

```

### Visualise

```{r eval = FALSE}
visualise_temporal_env_eco()
```

# Stable state finding

## Setup

```{r}
options(mc.cores = 12)
```

```{r}
ssfind_minimum_abundances <- rep(0, 3)
names(ssfind_minimum_abundances) <- c("CB", "PB", "SB")
ssfind_simulation_duration <- default_sim_duration
ssfind_simulation_sampling_interval <- ssfind_simulation_duration
ssfind_event_interval <- ssfind_simulation_duration
grid_num_a <- 1000 #usually 1000 ## number of a_0 values
a_Os <- 10^seq(-7, -1, length=grid_num_a) ## sequence of a_0 values
grid_num_N <- 2 ## number of N values
initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
initial_PBs <- 1e8 ## not varied
initial_SBs <- 1e8 ## not varied
# next line creates all possible combinations
ss_expt <- expand.grid(N_CB = initial_CBs,
                      N_PB = initial_PBs,
                      N_SB = initial_SBs,
                      a_O = a_Os)

```

## Run stable state finding

*Careful, this simulation takes about 600 hours on a single core

```{r eval = FALSE}
#var_expt <- run_ss_var_experiment()
#saveRDS(var_expt, here("experiments/experiment 1/data/ss_data.RDS"))

```

## Process the stable state data

```{r}
## find various combintions of diversity
var_expt <- readRDS(here("experiments/experiment 1/data/ss_data.RDS"))

var_expt_levels <- var_expt[,1:6]

no_diversity <- which(rowSums(abs(var_expt_levels))==0)
max_diversty_all <- which(max(rowSums(abs(var_expt_levels))) ==
                            rowSums(abs(var_expt_levels)))
max_only_CB_diversity <- which(max(rowSums(abs(var_expt_levels[,1:2]))) ==
                            rowSums(abs(var_expt_levels[,1:2])) &
                              rowSums(abs(var_expt_levels[,3:6]))==0)
#var_expt_levels[381,]

max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
                            rowSums(abs(var_expt_levels[,3:6])) &
                              rowSums(abs(var_expt_levels[,1:2]))==0)
#var_expt_levels[20,]

```

## various graphs

```{r}

p1  <- plot_ss_result1(var_expt,
                result_index = no_diversity,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1
```

```{r}

p2  <- plot_ss_result1(var_expt,
                result_index = max_diversty_all,
                filename_prefix = NULL,
                save_image_file = FALSE)
p2

```

```{r}

p3  <- plot_ss_result1(var_expt,
                result_index = max_only_CB_diversity,
                filename_prefix = NULL,
                save_image_file = FALSE)
p3

```

```{r}

p4  <- plot_ss_result1(var_expt,
                result_index = max_only_SBPB_diversity,
                filename_prefix = NULL,
                save_image_file = FALSE)
p4

```

```{r}
p_overlay1 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
                             var_expt[max_diversty_all,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay1
```

```{r}
p_overlay2 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
                             var_expt[max_only_CB_diversity,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay2
```

```{r}
p_overlay3 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
                             var_expt[max_only_SBPB_diversity,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay3
```

## Calculate stability measures

```{r eval = FALSE}
stab_data <- var_expt %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
stab_data <- unnest(stab_data, cols = c(stability_measures))
#saveRDS(stab_data, here("experiments/experiment 1/data/stab_data.RDS"))
```

## Process and visualise stability measures

```{r}
stab_data <- readRDS(here("experiments/experiment 1/data/stab_data.RDS"))

CB_vars <- unique(stab_data$CB_var_gmax_s)
SB_vars <- unique(stab_data$CB_var_gmax_s)

CB_stab_data <- stab_data %>%
  filter(SB_var_gmax_s == 0) %>%
  mutate(var_treat = "CB",
         var_gmax = CB_var_gmax_s)

SBPB_stab_data <- stab_data %>%
  filter(CB_var_gmax_s == 0) %>%
  mutate(var_treat = "SB-PB",
         var_gmax = SB_var_gmax_s)

for_join <- tibble(CB_var_gmax_s = CB_vars,
                     SB_var_gmax_s = SB_vars)
CBSBPB_stab_data <- stab_data %>%
  right_join(for_join) %>%
  mutate(var_treat = "CB-SB-PB",
         var_gmax = CB_var_gmax_s)

all_stab_results <- CB_stab_data %>%
  bind_rows(SBPB_stab_data) %>%
#  bind_rows(results3) %>%
 # bind_rows(results4) %>%
  bind_rows(CBSBPB_stab_data)

all_stab_results<- all_stab_results %>%
    mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB-PB", "CB-SB-PB")))

#saveRDS(all_stab_results, here("experiments/experiment summary/all_stab.RDS"))

#all_stab_results <- readRDS(here("experiments/experiment summary/all_stab.RDS"))

all_stab_results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax, y = hyst_range, col=var_treat)) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax,
             ymin = hyst_min,
             ymax = hyst_max,
             fill=var_treat)) +
  geom_ribbon(alpha = 0.5) +
  facet_wrap( ~ var_treat, nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") + 
  coord_flip() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )

##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)

```

# Zoom in on SS

```{r eval = FALSE}
a_Os <- 10^seq(-2.479, -2.4785, length=grid_num_a) ## sequence of a_0 values
initial_CBs <- 1#10^seq(0, 0, length=grid_num_N) ## sequence of N values
initial_PBs <- 1e8 ## not varied
initial_SBs <- 1e8 ## not varied
# next line creates all possible combinations
ss_expt <- expand.grid(N_CB = initial_CBs,
                      N_PB = initial_PBs,
                      N_SB = initial_SBs,
                      a_O = a_Os)
var_expt_master <- var_expt
var_expt <- var_expt_master[381,]
```

```{r}
#var_expt <- run_ss_var_experiment()
#saveRDS(var_expt, here("experiments/experiment 1/data/ss_data_zoom.RDS"))
```

```{r}
zoom <- readRDS(here("experiments/experiment 1/data/ss_data_zoom.RDS"))

p1  <- plot_ss_result1(zoom,
                result_index = 1,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1
```

# Negative abundance investigation

I (Owen) found that the sampling interval had an effect on the stability of the simulation. If the sampling interval was long, then in some rare cases (see below) the odesolver failed, with negative abundances occuring. I think this is due to abundances becoming very small, and then the computer having trouble with precision. I guess that when a sample is taken, the abundance is somehow altered if it is very low, probably by some rounding.

```{r eval = FALSE}
var_expt$pars[[1]]
dd <- var_expt$ss_res[[1]]
dd1 <- filter(dd, PB_1<(-0.0001))
dd1$a_O

ss_expt_master <- ss_expt
ss_expt <- ss_expt_master[abs(ss_expt_master$a_O - 1.336984e-05)<1e-10,]

var_expt_master <- var_expt
#var_expt <- var_expt[1,]
var_expt_test <- run_ss_var_experiment()
res <- var_expt_test$ss_res[[1]]

test1 <- ss_by_a_N(ss_expt, var_expt$pars[[1]])
x <- ss_expt[2,]
param <- var_expt$pars[[1]]
get_final_states_a_N(x, param)
ssfind_parameters <- param
ssfind_simulation_sampling_interval <- 1000
## now run inside the function "get_final_states_a_N"
simres1 <- simres
ssfind_simulation_sampling_interval <- 5000
## now run inside the function "get_final_states_a_N"
simres2 <- simres  # this fails

## now run inside the function "get_final_states_a_N"
plot_dynamics(simres2)

ggplot() +
  geom_line(data = simres1$result,
             mapping = aes(x = time, y = log10(PB_1))) +
  geom_point(data = simres2$result,
             mapping = aes(x = time, y = log10(PB_1))) +
  xlim(c(0, 250000))

ccc <- simres2$result

simres2$result$PB_1
simres2$result$time

log10_a <- log10(ss_expt$a_O[1]) ## very slowly goes anoxic
#log10_a <- log10(a_Os[354]) ## very slowly goes anoxic
#log10_a <- log10(a_Os[356]) ## very very very  slowly goes anoxic
#log10_a <- log10(a_Os[357]) ## does not go anoxic

default_dynamic_model <- bushplus_dynamic_model
default_event_definition <- event_definition_1
default_event_interval <- ssfind_simulation_duration
default_noise_sigma <- 0
default_minimum_abundances <- ssfind_minimum_abundances
default_sim_duration <- ssfind_simulation_duration
default_sim_sample_interval <- ssfind_simulation_duration
#initial_pars_from <- "bush_ssfig3"

default_log10a_series <- c(log10_a, log10_a)
initial_state <- new_initial_state(num_CB_strains,
                                   num_PB_strains,
                                   num_SB_strains,
                                   values = "bush_ssfig3")
initial_state[grep("CB_", names(initial_state))] <- 10^10/num_CB_strains
sim_res_novar <- run_simulation(parameter_values = var_expt$pars[[1]],
                          initial_state = initial_state)
plot_dynamics(sim_res_novar)

simulation_result <- sim_res_novar
every_n <- 1

chk <- sim_res_novar$result

sim_res_novar$result %>%
  ggplot() +
  geom_line(mapping = aes(x = time, y = PB_1))

#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)

```

### 2021-07-18 experiments/experiment old/experiment 1/experiment 1.Rmd
new experiment 1 sorted

--- 2021-07-09 experiments/experiment 1/experiment 1.Rmd
@@
 ```{r}
+default_sim_duration <- 1000000
 ssfind_minimum_abundances <- rep(0, 3)
@@
 ```{r}
-var_expt <- run_ss_var_experiment()
-saveRDS(var_expt, here("experiments/experiment 1/data/ss_data.RDS"))
+#var_expt <- run_ss_var_experiment()
+#saveRDS(var_expt, here("experiments/experiment 1/data/ss_data_latest.RDS"))
 
@@
 ```{r}
-var_expt <- readRDS(here("experiments/experiment 1/data/ss_data.RDS"))
+var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_latest.RDS"))
+
+ss_exp_result <- var_expt
+result_index <- 1
 

### 2021-07-18 experiments/experiment old/experiment 1/negative abundance investigation.Rmd
new experiment 1 sorted

--- 2021-07-09 experiments/experiment 1/experiment 1.Rmd
@@
 ---
-title: "Experiment 1"
+title: "negative abundance investigation"
 author: "Owen Petchey"
-date: "6/25/2021"
-output:
-  html_document:
-    keep_md: yes
+date: "7/16/2021"
+output: html_document
 ---
@@
 display_diversity()
+```
+
+# Stable state finding
+
+## Setup
+
+```{r}
+options(mc.cores = 4)
+```
+
+```{r}
+ssfind_minimum_abundances <- rep(0, 3)
+names(ssfind_minimum_abundances) <- c("CB", "PB", "SB")
+ssfind_simulation_duration <- default_sim_duration
+ssfind_simulation_sampling_interval <- ssfind_simulation_duration
+ssfind_event_interval <- ssfind_simulation_duration
+grid_num_a <- 1000 ## number of a_0 values
+a_Os <- 10^seq(-7, -1, length=grid_num_a) ## sequence of a_0 values
+grid_num_N <- 2 ## number of N values
+initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
+initial_PBs <- 1e8 ## not varied
+initial_SBs <- 1e8 ## not varied
+# next line creates all possible combinations
+ss_expt <- expand.grid(N_CB = initial_CBs,
+                      N_PB = initial_PBs,
+                      N_SB = initial_SBs,
+                      a_O = a_Os)
+
+```
+
+```{r}
+a_Os[355]
+
+```
+
+```{r eval = FALSE}
+var_expt <- readRDS(here("experiments/experiment 1/data/ss_data.RDS"))
+
+result_index1 <- 1
+p1  <- plot_ss_result1(var_expt,
+                result_index = result_index1,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p1
+```
+
+```{r eval = FALSE}
+result_index2 <- num_div_treatment_levels
+p2  <- plot_ss_result1(var_expt,
+                result_index = result_index2,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p2
+
+```
+
+```{r eval = FALSE}
+p_overlay <- plot_ss_result2(var_expt[result_index1,]$ss_res[[1]],
+                             var_expt[result_index2,]$ss_res[[1]],
+                             xlims = c(-7, -1))
+p_overlay
+
 ```
@@
 ```{r}
-default_sim_duration <- 80000
+var_expt <- readRDS(here("experiments/experiment 1/data/ss_data.RDS"))
+```
+
+find the negative abundances
+
+```{r}
+var_expt$pars[[1]]
+dd <- var_expt$ss_res[[1]]
+dd1 <- filter(dd, PB_1<(-0.0001))
+dd1$a_O
+```
+
+```{r}
+default_sim_duration <- 1000000
 ```
@@
 sim_number <- 1
-default_log10a_series <- c(-1, -7, -7)
+log10_a <- log10(a_Os[355]) ## very slowly goes anoxic
+#log10_a <- log10(a_Os[354]) ## very slowly goes anoxic
+#log10_a <- log10(a_Os[356]) ## very very very  slowly goes anoxic
+#log10_a <- log10(a_Os[357]) ## does not go anoxic
+
+default_log10a_series <- c(log10_a, log10_a)
 initial_state <- new_initial_state(num_CB_strains,
@@
 #ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
+```
+
+```{r eval = FALSE}
+a_Os <- 10^seq(-7, -1, length=grid_num_a) ## sequence of a_0 values
+a_Os <- a_Os[355]
+ss_expt <- expand.grid(N_CB = initial_CBs,
+                      N_PB = initial_PBs,
+                      N_SB = initial_SBs,
+                      a_O = a_Os)
+
+var_expt_master <- var_expt
+var_expt <- var_expt[1,]
+var_expt_test <- run_ss_var_experiment()
+res <- var_expt_test$ss_res[[1]]
+#saveRDS(var_expt, here("experiments/experiment 1/data/ss_data.RDS"))
+
 ```
@@
 ```
-
-# Stable state finding
-
-## Setup
-
-```{r}
-options(mc.cores = 4)
-```
-
-```{r}
-ssfind_minimum_abundances <- rep(0, 3)
-names(ssfind_minimum_abundances) <- c("CB", "PB", "SB")
-ssfind_simulation_duration <- default_sim_duration
-ssfind_simulation_sampling_interval <- ssfind_simulation_duration
-ssfind_event_interval <- ssfind_simulation_duration
-grid_num_a <- 1000 ## number of a_0 values
-a_Os <- 10^seq(-7, -1, length=grid_num_a) ## sequence of a_0 values
-grid_num_N <- 2 ## number of N values
-initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
-initial_PBs <- 1e8 ## not varied
-initial_SBs <- 1e8 ## not varied
-# next line creates all possible combinations
-ss_expt <- expand.grid(N_CB = initial_CBs,
-                      N_PB = initial_PBs,
-                      N_SB = initial_SBs,
-                      a_O = a_Os)
-
-```
-
-```{r}
-var_expt <- run_ss_var_experiment()
-saveRDS(var_expt, here("experiments/experiment 1/data/ss_data.RDS"))
-
-```
-
-```{r}
-var_expt <- readRDS(here("experiments/experiment 1/data/ss_data.RDS"))
-
-result_index1 <- 1
-p1  <- plot_ss_result1(var_expt,
-                result_index = result_index1,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p1
-```
-
-```{r}
-result_index2 <- num_div_treatment_levels
-p2  <- plot_ss_result1(var_expt,
-                result_index = result_index2,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p2
-
-```
-
-```{r}
-p_overlay <- plot_ss_result2(var_expt[result_index1,]$ss_res[[1]],
-                             var_expt[result_index2,]$ss_res[[1]],
-                             xlims = c(-7, -1))
-p_overlay
-
-```

### 2021-07-18 manuscript/article.Rmd
new experiment 1 sorted

@@
 
+```{r}
+## find various combintions of diversity
+var_expt <- readRDS(here("experiments/experiment 4/data/ss_data.RDS"))
+
+var_expt_levels <- var_expt[,1:6]
+
+no_diversity <- which(rowSums(abs(var_expt_levels))==0)
+max_diversty_all <- which(max(rowSums(abs(var_expt_levels))) ==
+                            rowSums(abs(var_expt_levels)))
+max_only_CB_diversity <- which(max(rowSums(abs(var_expt_levels[,1:2]))) ==
+                            rowSums(abs(var_expt_levels[,1:2])) &
+                              rowSums(abs(var_expt_levels[,3:6]))==0)
+max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
+                            rowSums(abs(var_expt_levels[,3:6])) &
+                              rowSums(abs(var_expt_levels[,1:2]))==0)
+
+```
+
 ```{r ss_novar, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Steady states of the ecosystem with no trait diversity, i.e.
 identical trait values for the strains within a functional group."), echo=FALSE}
-CBSBPB_data <- readRDS(here("experiments/experiment 1/data/ss_data.RDS"))
-result_index1 <- 1
-p1  <- plot_ss_result1(CBSBPB_data,
-                result_index = result_index1,
+p1  <- plot_ss_result1(var_expt,
+                result_index = no_diversity,
                 filename_prefix = NULL,
@@
 p1
-
 ```
@@
 ```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Steady states of the ecosystem with diversity in all functional groups"), echo=FALSE}
-result_index2 <- 20
-p2  <- plot_ss_result1(CBSBPB_data,
-                result_index = result_index2,
+p2  <- plot_ss_result1(var_expt,
+                result_index = max_diversty_all,
                 filename_prefix = NULL,
@@
 p2
-
 ```
@@
 ```{r ss_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Steady states of the ecosystem without any diversity (solid line) and with diversity in all three functional groups."), echo=FALSE}
-p_overlay <- plot_ss_result2(CBSBPB_data[result_index1,]$ss_res[[1]],
-                             CBSBPB_data[result_index2,]$ss_res[[1]],
+p_overlay1 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
+                             var_expt[max_diversty_all,]$ss_res[[1]],
                              xlims = c(-7, -1))
-p_overlay
+p_overlay1
 ```
@@
 ```{r CB_var1, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Steady states of the ecosystem with diversity in only the cyanobacteria functional group."), echo=FALSE}
-CB_data <- readRDS(here("experiments/experiment 2/data/ss_data.RDS"))
-p3  <- plot_ss_result1(CB_data,
-                result_index = result_index2,
+p3  <- plot_ss_result1(var_expt,
+                result_index = max_only_CB_diversity,
                 filename_prefix = NULL,
@@
 ```{r CB_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Steady states of the ecosystem without any diversity (solid line) and with diversity in only the cyanobacteria functional group."), echo=FALSE}
-p_overlay <- plot_ss_result2(CB_data[result_index1,]$ss_res[[1]],
-                             CB_data[result_index2,]$ss_res[[1]],
+p_overlay2 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
+                             var_expt[max_only_CB_diversity,]$ss_res[[1]],
                              xlims = c(-7, -1))
-p_overlay
+p_overlay2
 ```
@@
 ```{r SBPB_var1, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Steady states of the ecosystem with diversity in only the two sulphur bacteria functional groups."), echo=FALSE}
-SBPB_data <- readRDS(here("experiments/experiment 3/data/ss_data.RDS"))
-p6  <- plot_ss_result1(SBPB_data,
-                result_index = result_index2,
+p4  <- plot_ss_result1(var_expt,
+                result_index = max_only_SBPB_diversity,
                 filename_prefix = NULL,
                 save_image_file = FALSE)
-p6
+p4
 
@@
 ```{r SBPB_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Steady states of the ecosystem without any diversity (solid line) and with diversity in only the sulphur bacteria functional group."), echo=FALSE}
-p_overlay <- plot_ss_result2(CB_data[result_index1,]$ss_res[[1]],
-                             SBPB_data[result_index2,]$ss_res[[1]],
+p_overlay3 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
+                             var_expt[max_only_SBPB_diversity,]$ss_res[[1]],
                              xlims = c(-7, -1))
-
-p_overlay
+p_overlay3
 ```

### 2021-07-18 experiments/r functions/various_useful_functions.r

@@ -313,7 +313,7 @@ plot_ss_result2 <- function(ss_result1,
 }
 
 
-display_diversity <- function() {
+display_diversity <- function(this_one) {
   
   colfunc_CB <- colorRampPalette(c("#024F17", "#B5FFC9"))
   colfunc_SB <- colorRampPalette(c("#7D1402", "#FCBEB3"))
@@ -322,7 +322,7 @@ display_diversity <- function() {
   linewd <- 1.5
   ptsize <- 2
   
-  CBtraits <- var_expt$pars[[num_div_treatment_levels]]$CB
+  CBtraits <- var_expt$pars[[this_one]]$CB
   P <- 1 #10^seq(-5, 5, 0.1)
   SR <- 10^seq(0, 3, 0.1)
   gr_rateCB1 <- growth1(P, CBtraits$g_max_CB[1], CBtraits$k_CB_P[1]) * inhibition(SR, CBtraits$h_SR_CB[1])
@@ -342,7 +342,7 @@ display_diversity <- function() {
   
   
   
-  SBtraits <- var_expt$pars[[num_div_treatment_levels]]$SB
+  SBtraits <- var_expt$pars[[this_one]]$SB
   P <- 1 #10^seq(-5, 5, 0.1)
   SO <- 1
   O <- 10^seq(-2.5, 2.5, 0.1)
@@ -363,7 +363,7 @@ display_diversity <- function() {
     xlab("Oxygen concentration\nin the environment\n(log10 uM per litre)") +
     ylab("Realised growth rate\n(sulphate reducing bacteria)")
   
-  PBtraits <- var_expt$pars[[num_div_treatment_levels]]$PB
+  PBtraits <- var_expt$pars[[this_one]]$PB
   P <- 1 #10^seq(-5, 5, 0.1)
   SO <- 1
   O <- 10^seq(-2.5, 2.5, 0.1)

### 2021-07-20 experiments/experiment 1/experiment-1.Rmd
various

@@
 ## find various combintions of diversity
-var_expt <- readRDS(here("experiments/experiment 1/data/ss_data.RDS"))
+var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_300000_small.RDS"))
 
@@
 ```{r}
+library(here)
 zoom <- readRDS(here("experiments/experiment 1/data/ss_data_zoom.RDS"))

### 2021-07-22 experiments/experiment 1/experiment-1.Rmd
update experiment 1

@@
 num_PB_strains <- 9
-CB_gmax_div <- 0.015789474
-CB_h_div <- -0.08
-SB_gmax_div <- 0.015789474
-SB_h_div <- -0.323
-PB_gmax_div <- 0.015789474
-PB_h_div <- -0.323
+CB_gmax_div <- 0.015789474 * 0
+CB_h_div <- -0.08 * 0
+SB_gmax_div <- 0.015789474 * 5
+SB_h_div <- -0.323  * 5
+PB_gmax_div <- 0.015789474  * 5
+PB_h_div <- -0.323  * 5
 
@@
 ```{r}
-display_diversity(400)
+display_diversity(20)
 ```
@@
 
-## Setup
+## Finding
 
@@
 
-## Run stable state finding
+Run stable state finding
 
@@
 #var_expt <- run_ss_var_experiment()
-#saveRDS(var_expt, here("experiments/experiment 1/data/ss_data.RDS"))
+#saveRDS(var_expt, here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS"))
 
@@
 
-## Process the stable state data
+Process the stable state data
+
+Bring in various stable state datasets
+```{r eval = FALSE}
+## sim length 80'000, 20 x 20 factorial, reference maximum diversity
+var_expt1 <- readRDS(here("experiments/experiment 1/data/ss_data_80000.RDS")) %>%
+  mutate(sim_length = 80000)
+stab_data1 <- var_expt1 %>%
+  group_by(CB_var_gmax_s, CB_var_h_s,
+           SB_var_gmax_s, SB_var_h_s,
+           PB_var_gmax_s, PB_var_h_s, sim_length) %>%
+  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
+stab_data1 <- unnest(stab_data1, cols = c(stability_measures))
+saveRDS(stab_data1, here("experiments/experiment 1/data/stab_data_80000.RDS"))
+
+## sim length 1'000'000, 20 x 20 factorial, reference maximum diversity
+var_expt2 <- readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS")) %>%
+  mutate(sim_length = 1000000)
+stab_data2 <- var_expt2 %>%
+  group_by(CB_var_gmax_s, CB_var_h_s,
+           SB_var_gmax_s, SB_var_h_s,
+           PB_var_gmax_s, PB_var_h_s, sim_length) %>%
+  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
+stab_data2 <- unnest(stab_data2, cols = c(stability_measures))
+saveRDS(stab_data2, here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS"))
+
+## sim length 1'000'000, 20 SBPBgrad, 5x maximum diversity
+var_expt3 <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS")) %>%
+  mutate(sim_length = 1000000)
+stab_data3 <- var_expt3 %>%
+  group_by(CB_var_gmax_s, CB_var_h_s,
+           SB_var_gmax_s, SB_var_h_s,
+           PB_var_gmax_s, PB_var_h_s, sim_length) %>%
+  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
+stab_data3 <- unnest(stab_data3, cols = c(stability_measures))
+saveRDS(stab_data3, here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
+
+## sim length 300'000, 20 SBPBgrad, reference maximum diversity
+var_expt4 <- readRDS(here("experiments/experiment 1/data/ss_data_300000_small.RDS")) %>%
+  mutate(sim_length = 300000)
+stab_data4 <- var_expt4 %>%
+  group_by(CB_var_gmax_s, CB_var_h_s,
+           SB_var_gmax_s, SB_var_h_s,
+           PB_var_gmax_s, PB_var_h_s, sim_length) %>%
+  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
+stab_data4 <- unnest(stab_data4, cols = c(stability_measures))
+saveRDS(stab_data4, here("experiments/experiment 1/data/stab_data_300000.RDS"))
+
+```
+
+## SS, no diversity, all diversity, CB only, and SBPB only
 
 ```{r}
-## find various combintions of diversity
-var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_300000_small.RDS"))
+## find various combinations of diversity
+var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS"))
 
@@
 
-## various graphs
-
 ```{r}
@@
 p1
+
+#junk1 <- var_expt[no_diversity,]$ss_res[[1]]
 ```
@@
 p_overlay2
+
+#ss_result1 <- var_expt[no_diversity,]$ss_res[[1]]
+#ss_result2 <- var_expt[max_only_CB_diversity,]$ss_res[[1]]
+
 ```
@@
 p_overlay3
+
+#ss_result3 <- var_expt[max_only_SBPB_diversity,]$ss_res[[1]]
+
 ```
 
-## Calculate stability measures
-
-```{r eval = FALSE}
-stab_data <- var_expt %>%
-  group_by(CB_var_gmax_s, CB_var_h_s,
-           SB_var_gmax_s, SB_var_h_s,
-           PB_var_gmax_s, PB_var_h_s) %>%
-  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
-stab_data <- unnest(stab_data, cols = c(stability_measures))
-#saveRDS(stab_data, here("experiments/experiment 1/data/stab_data.RDS"))
-```
-
-## Process and visualise stability measures
+## Look at stability measures
 
 ```{r}
-stab_data <- readRDS(here("experiments/experiment 1/data/stab_data.RDS"))
+stab_data1 <- readRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS"))
+stab_data2 <- readRDS(here("experiments/experiment 1/data/stab_data_80000.RDS"))
+stab_data <- bind_rows(stab_data1, stab_data2)
 
@@
   filter(Species == "O") %>%
-  ggplot(aes(x = var_gmax, y = hyst_range, col=var_treat)) +
+  ggplot(aes(x = var_gmax, y = hyst_range, col=var_treat, shape = as_factor(sim_length))) +
   geom_point() +
@@
   #filter(var_treat == "CB") %>%
-  filter(Species == "O") %>%
+  filter(Species == "O",
+         sim_length == 1e6) %>%
+  ggplot(aes(x = var_gmax,
+             ymin = hyst_min,
+             ymax = hyst_max,
+             fill=var_treat)) +
+  geom_ribbon(alpha = 0.5) +
+  facet_wrap( ~ var_treat, nrow = 3) +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
+  labs(fill = "Variation in\nonly these\nfunctional groups") + 
+  coord_flip() +
+  theme(
+    strip.background = element_blank(),
+    strip.text.x = element_blank()
+  )
+
+all_stab_results %>%
+  #filter(var_treat == "CB") %>%
+  filter(Species == "O",
+         sim_length == 8e4) %>%
   ggplot(aes(x = var_gmax,
@@
 ##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
+
+```
+
+## Extra SBPB diversity
+
+```{r}
+var_expt_x <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS"))
+stab_data_x <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
+
+p1  <- plot_ss_result1(var_expt_x,
+                result_index = 1,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p1
+
+p1  <- plot_ss_result1(var_expt_x,
+                result_index = 19,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p1
+
+p_overlay1 <- plot_ss_result2(var_expt_x[1,]$ss_res[[1]],
+                             var_expt_x[19,]$ss_res[[1]],
+                             xlims = c(-7, -1))
+p_overlay1
+
+stab_data_x %>%
+  filter(Species == "O") %>%
+  ggplot(aes(x = SB_var_gmax_s, y = hyst_range)) +
+  geom_point() +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
+  labs(col = "Variation in\nonly these\nfunctional groups")
+##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)
+
+stab_data_x %>%
+  #filter(var_treat == "CB") %>%
+  filter(Species == "O") %>%
+  ggplot(aes(x = SB_var_gmax_s,
+             ymin = hyst_min,
+             ymax = hyst_max)) +
+  geom_ribbon(alpha = 0.5) +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
+  coord_flip() +
+  theme(
+    strip.background = element_blank(),
+    strip.text.x = element_blank()
+  )
+
+```
+
+## What effect of changing the length of the simulations
+
+```{r}
+var_expt1 <- readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS"))
+var_expt2 <- readRDS(here("experiments/experiment 1/data/ss_data_80000.RDS"))
+
+p1_short  <- plot_ss_result1(var_expt2,
+                result_index = max_diversty_all,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p1_short
+
+p1_long  <- plot_ss_result1(var_expt1,
+                result_index = max_diversty_all,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p1_long
 

### 2021-07-23 experiments/experiment 1/experiment-1.Rmd
Update experiment-1.Rmd

@@
 num_PB_strains <- 9
-CB_gmax_div <- 0.015789474 * 0
-CB_h_div <- -0.08 * 0
-SB_gmax_div <- 0.015789474 * 5
-SB_h_div <- -0.323  * 5
-PB_gmax_div <- 0.015789474  * 5
-PB_h_div <- -0.323  * 5
+
+## multiplier of SBPB variation
+CB_var_multiplier <- 1
+SBPB_var_multiplier <- 5
+
+CB_gmax_div <- 0.015789474 * CB_var_multiplier
+CB_h_div <- -0.08 * CB_var_multiplier
+SB_gmax_div <- 0.015789474 * SBPB_var_multiplier
+SB_h_div <- -0.323  * SBPB_var_multiplier
+PB_gmax_div <- 0.015789474  * SBPB_var_multiplier
+PB_h_div <- -0.323  * SBPB_var_multiplier
 
@@
 ```{r}
-display_diversity(20)
+display_diversity(400)
 ```
@@
 ##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
+stab_data1 <- readRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS"))
+stab_data_x <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
+stab_data_plus <- bind_rows(stab_data1, stab_data_x)
+stab_data_plus %>%
+  filter(Species == "O",
+         sim_length == 1e6) %>%
+  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range, col = hyst_range)) +
+  geom_point(size = 3)
 
@@
 ```
+
+# Understand about relative and absolute variation in traits
+
+```{r echo = FALSE}
+num_CB_strains <- 9
+num_SB_strains <- 9
+num_PB_strains <- 9
+
+## multiplier of SBPB variation
+CB_var_multiplier <- 1
+SBPB_var_multiplier <- 5
+
+CB_gmax_div <- 0.015789474 * CB_var_multiplier
+CB_h_div <- -0.08 * CB_var_multiplier
+SB_gmax_div <- 0.015789474 * SBPB_var_multiplier
+SB_h_div <- -0.323  * SBPB_var_multiplier
+PB_gmax_div <- 0.015789474  * SBPB_var_multiplier
+PB_h_div <- -0.323  * SBPB_var_multiplier
+
+num_div_treatment_levels <- 2
+
+var_expt <- create_diversity_factorial()
+
+display_diversity(4)
+
+this_one <- 4
+CBtraits <- var_expt$pars[[this_one]]$CB
+P <- 1 #10^seq(-5, 5, 0.1)
+SR <- 10^seq(0, 3, 0.1)
+gr_rateCB1 <- growth1(P, CBtraits$g_max_CB[1], CBtraits$k_CB_P[1]) * inhibition(SR, CBtraits$h_SR_CB[1])
+gr_rateCB9 <- growth1(P, CBtraits$g_max_CB[num_CB_strains], CBtraits$k_CB_P[num_CB_strains]) * inhibition(SR, CBtraits$h_SR_CB[num_CB_strains])
+CB_gr_rates <- (c(gr_rateCB1, gr_rateCB9))
+CB_gr_range <- max(CB_gr_rates) - min(CB_gr_rates)
+CB_gr_range
+
+SBtraits <- var_expt$pars[[this_one]]$SB
+P <- 1 #10^seq(-5, 5, 0.1)
+SO <- 1
+O <- 10^seq(-2.5, 2.5, 0.1)
+gr_rateSB1 <- growth2(P, SO, SBtraits$g_max_SB[1], SBtraits$k_SB_P[1], SBtraits$k_SB_SO[1]) *
+  inhibition(O, SBtraits$h_O_SB[1])
+gr_rateSB9 <- growth2(P, SO, SBtraits$g_max_SB[9], SBtraits$k_SB_P[9], SBtraits$k_SB_SO[9]) *
+    inhibition(O, SBtraits$h_O_SB[9])
+SB_gr_rates <- (c(gr_rateSB1, gr_rateSB9))
+SB_gr_range <- max(SB_gr_rates) - min(SB_gr_rates)
+SB_gr_range
+
+PBtraits <- var_expt$pars[[this_one]]$PB
+P <- 1 #10^seq(-5, 5, 0.1)
+SO <- 1
+O <- 10^seq(-2.5, 2.5, 0.1)
+gr_ratePB1 <- growth2(P, SO, PBtraits$g_max_PB[1], PBtraits$k_PB_P[1], PBtraits$k_PB_SR[1]) *
+  inhibition(O, PBtraits$h_O_PB[1])
+gr_ratePB9 <- growth2(P, SO, PBtraits$g_max_PB[9], PBtraits$k_PB_P[9], PBtraits$k_PB_SR[9]) *
+  inhibition(O, PBtraits$h_O_PB[9])
+PB_gr_rates <- (c(gr_ratePB1, gr_ratePB9))
+PB_gr_range <- max(PB_gr_rates) - min(PB_gr_rates)
+PB_gr_range
+
+```
+
+With the CB diversity multiplier set at `r CB_var_multiplier` and the SB/PB multiplier set at `r SBPB_var_multiplier` the range of realised growth rates of CB is `r CB_gr_range`, range of SB is `r SB_gr_range`, and range of PB is `r PB_gr_range`.

### 2021-07-28 experiments/experiment 1/experiment-1.Rmd
update experiment1

@@
 ## multiplier of SBPB variation
-CB_var_multiplier <- 1
-SBPB_var_multiplier <- 5
+CB_var_multiplier <- 2
+SBPB_var_multiplier <- 6
 
@@
 grid_num_a <- 1000 #usually 1000 ## number of a_0 values
-a_Os <- 10^seq(-7, -1, length=grid_num_a) ## sequence of a_0 values
+a_Os <- 10^seq(-7, -0.5, length=grid_num_a) ## sequence of a_0 values
 grid_num_N <- 2 ## number of N values
@@
 ```{r eval = FALSE}
-#var_expt <- run_ss_var_experiment()
-#saveRDS(var_expt, here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS"))
+var_expt <- run_ss_var_experiment()
+saveRDS(var_expt, here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS"))
 
@@
 saveRDS(stab_data4, here("experiments/experiment 1/data/stab_data_300000.RDS"))
+
+## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
+var_expt5 <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS")) %>%
+  mutate(sim_length = 1000000)
+stab_data5 <- var_expt5 %>%
+  group_by(CB_var_gmax_s, CB_var_h_s,
+           SB_var_gmax_s, SB_var_h_s,
+           PB_var_gmax_s, PB_var_h_s, sim_length) %>%
+  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
+stab_data5 <- unnest(stab_data5, cols = c(stability_measures))
+saveRDS(stab_data5, here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
 
@@
 
+## 2x CB, 6xSBPB diversity
+
+```{r}
+var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS"))
+stab_data <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
+
+p1  <- plot_ss_result1(var_expt,
+                result_index = 1,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p1
+
+p1  <- plot_ss_result1(var_expt,
+                result_index = 400,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p1
+
+p_overlay1 <- plot_ss_result2(var_expt[1,]$ss_res[[1]],
+                             var_expt[400,]$ss_res[[1]],
+                             xlims = c(-7, -1))
+p_overlay1
+
+CB_vars <- unique(stab_data$CB_var_gmax_s)
+SB_vars <- unique(stab_data$SB_var_gmax_s)
+
+CB_stab_data <- stab_data %>%
+  filter(SB_var_gmax_s == 0) %>%
+  mutate(var_treat = "CB",
+         var_gmax = CB_var_gmax_s)
+
+SBPB_stab_data <- stab_data %>%
+  filter(CB_var_gmax_s == 0) %>%
+  mutate(var_treat = "SB-PB",
+         var_gmax = SB_var_gmax_s)
+
+for_join <- tibble(CB_var_gmax_s = CB_vars,
+                     SB_var_gmax_s = SB_vars)
+CBSBPB_stab_data <- stab_data %>%
+  right_join(for_join) %>%
+  mutate(var_treat = "CB-SB-PB",
+         var_gmax = CB_var_gmax_s)
+
+all_stab_results <- CB_stab_data %>%
+  bind_rows(SBPB_stab_data) %>%
+#  bind_rows(results3) %>%
+ # bind_rows(results4) %>%
+  bind_rows(CBSBPB_stab_data)
+
+all_stab_results<- all_stab_results %>%
+    mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB-PB", "CB-SB-PB")))
+
+#saveRDS(all_stab_results, here("experiments/experiment summary/all_stab.RDS"))
+
+#all_stab_results <- readRDS(here("experiments/experiment summary/all_stab.RDS"))
+
+all_stab_results %>%
+  filter(Species == "O") %>%
+  ggplot(aes(x = var_gmax, y = hyst_range, col=var_treat, shape = as_factor(sim_length))) +
+  geom_point() +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
+  labs(col = "Variation in\nonly these\nfunctional groups")
+##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)
+
+all_stab_results %>%
+  #filter(var_treat == "CB") %>%
+  filter(Species == "O",
+         sim_length == 1e6) %>%
+  ggplot(aes(x = var_gmax,
+             ymin = hyst_min,
+             ymax = hyst_max,
+             fill=var_treat)) +
+  geom_ribbon(alpha = 0.5) +
+  facet_wrap( ~ var_treat, nrow = 3) +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
+  labs(fill = "Variation in\nonly these\nfunctional groups") + 
+  coord_flip() +
+  theme(
+    strip.background = element_blank(),
+    strip.text.x = element_blank()
+  )
+
+##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
+stab_data %>%
+  filter(Species == "O",
+         sim_length == 1e6) %>%
+  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range, col = hyst_range)) +
+  geom_point(size = 3)
+
+##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
+
+stab_data %>%
+  filter(Species == "O",
+         sim_length == 1e6) %>%
+  ggplot(aes(x = CB_var_gmax_s, y = hyst_range, col = as.factor(SB_var_gmax_s))) +
+  geom_line(size = 2)
+
+```
+
 ## What effect of changing the length of the simulations

### 2021-08-12 experiments/experiment 1/experiment-1.Rmd
Analysis with least and most tolerant Sulfur Bacteria

@@
 library(here)
+library(parallel)
 source(here("experiments/r functions/various_useful_functions.r"))
@@
 ```{r}
-options(mc.cores = 12)
+options(mc.cores = detectCores())
 ```
@@
 #var_expt_levels[20,]
-
+var_expt_copy <- var_expt
 ```
@@
 
-```{r}
+```{r, fig.height=7.5, fig.width=12}
 
-p2  <- plot_ss_result1(var_expt,
+p2  <- plot_ss_result1_v2(var_expt,
                 result_index = max_diversty_all,
@@
 
+## Analysis with least and most tolerant Sulfur Bacteria
+
+```{r}
+##########################################
+###### Setup copy-pasted from above
+
+num_CB_strains <- 9
+num_SB_strains <- 9
+num_PB_strains <- 9
+
+## multiplier of SBPB variation
+CB_var_multiplier <- 2
+SBPB_var_multiplier <- 6
+
+CB_gmax_div <- 0.015789474 * CB_var_multiplier
+CB_h_div <- -0.08 * CB_var_multiplier
+SB_gmax_div <- 0.015789474 * SBPB_var_multiplier
+SB_h_div <- -0.323  * SBPB_var_multiplier
+PB_gmax_div <- 0.015789474  * SBPB_var_multiplier
+PB_h_div <- -0.323  * SBPB_var_multiplier
+
+num_div_treatment_levels <- 20
+
+var_expt <- create_diversity_factorial()
+
+## rows of interest
+
+var_expt_levels <- var_expt[,1:6]
+no_diversity <- which(rowSums(abs(var_expt_levels))==0)
+max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
+                            rowSums(abs(var_expt_levels[,3:6])) &
+                              rowSums(abs(var_expt_levels[,1:2]))==0)
+
+## Overwriting average values with most and least tolerant values (tolerance and respective growth)
+
+most_tolerant_PB <- var_expt[max_only_SBPB_diversity,]$pars[[1]]$PB
+least_tolerant_PB <- most_tolerant_PB[which.min(most_tolerant_PB$h_O_PB),]
+most_tolerant_PB <- most_tolerant_PB[which.max(most_tolerant_PB$h_O_PB),]
+
+most_tolerant_SB <- var_expt[max_only_SBPB_diversity,]$pars[[1]]$SB
+least_tolerant_SB <- most_tolerant_SB[which.min(most_tolerant_SB$h_O_SB),]
+most_tolerant_SB <- most_tolerant_SB[which.max(most_tolerant_SB$h_O_SB),]
+
+var_expt_most_tolerant_SBPB <- var_expt[no_diversity, ]
+var_expt_most_tolerant_SBPB$pars[[1]]$PB[1:9] <- most_tolerant_PB
+var_expt_most_tolerant_SBPB$pars[[1]]$SB[1:9] <- most_tolerant_SB
+var_expt_most_tolerant_SBPB$pars[[1]]$PB$strain_name <- paste0("PB_",1:9)
+var_expt_most_tolerant_SBPB$pars[[1]]$SB$strain_name <- paste0("SB_",1:9)
+
+var_expt_least_tolerant_SBPB <- var_expt[no_diversity, ]
+var_expt_least_tolerant_SBPB$pars[[1]]$PB[1:9] <- least_tolerant_PB
+var_expt_least_tolerant_SBPB$pars[[1]]$SB[1:9] <- least_tolerant_SB
+var_expt_least_tolerant_SBPB$pars[[1]]$PB$strain_name <- paste0("PB_",1:9)
+var_expt_least_tolerant_SBPB$pars[[1]]$SB$strain_name <- paste0("SB_",1:9)
+## number of cores usable
+options(mc.cores = detectCores()-1)
+
+## setup copy-pasted from above
+default_sim_duration <- 1000000
+ssfind_minimum_abundances <- rep(0, 3)
+names(ssfind_minimum_abundances) <- c("CB", "PB", "SB")
+ssfind_simulation_duration <- default_sim_duration
+ssfind_simulation_sampling_interval <- ssfind_simulation_duration
+ssfind_event_interval <- ssfind_simulation_duration
+grid_num_a <- 1000 #usually 1000 ## number of a_0 values
+a_Os <- 10^seq(-7, -0.5, length=grid_num_a) ## sequence of a_0 values
+grid_num_N <- 2 ## number of N values
+initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
+initial_PBs <- 1e8 ## not varied
+initial_SBs <- 1e8 ## not varied
+# next line creates all possible combinations
+ss_expt <- expand.grid(N_CB = initial_CBs,
+                      N_PB = initial_PBs,
+                      N_SB = initial_SBs,
+                      a_O = a_Os)
+```
+
+```{r eval=FALSE}
+## Here the simulations with least and most tolerantsulfur bacteria are run.
+var_expt <- var_expt_least_tolerant_SBPB
+var_expt_least_tolerant_SBPB <- run_ss_var_experiment()
+saveRDS(var_expt_least_tolerant_SBPB, here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_SBPB_least_tolerant.RDS"))
+
+var_expt <- var_expt_most_tolerant_SBPB
+var_expt_most_tolerant_SBPB <- run_ss_var_experiment()
+saveRDS(var_expt_most_tolerant_SBPB, here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_SBPB_most_tolerant.RDS"))
+```
+
+```{r, fig.height=7.5, fig.width=12}
+var_expt_least_tolerant_SBPB <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_SBPB_least_tolerant.RDS"))
+var_expt_most_tolerant_SBPB <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_SBPB_most_tolerant.RDS"))
+
+plot_ss_result1_v2(var_expt_least_tolerant_SBPB,
+                   result_index = 1,
+                   filename_prefix = NULL,
+                   save_image_file = FALSE) +
+  plot_annotation(caption = 'Least tolerant SB and PB strains + average CB strain')
+
+plot_ss_result1_v2(var_expt_most_tolerant_SBPB,
+                   result_index = 1,
+                   filename_prefix = NULL,
+                   save_image_file = FALSE)+
+  plot_annotation(caption = 'Most tolerant SB and PB strains + average CB strain')
+```
+
+```{r, fig.height=8, fig.width=10, message=FALSE, warning=FALSE}
+plot_ss_result2(var_expt_least_tolerant_SBPB$ss_res[[1]],
+                var_expt_copy[no_diversity,]$ss_res[[1]],
+                xlims = c(-7, -1))+
+  plot_annotation(title = 'Sims with LEAST tolerant SB and PB strains + average CB strain (solid line)\nVersus\nSims with no diversity (average values) (dashed line)')
+
+plot_ss_result2(var_expt_least_tolerant_SBPB$ss_res[[1]],
+                var_expt_copy[max_only_SBPB_diversity,]$ss_res[[1]],
+                xlims = c(-7, -1))+
+  plot_annotation(title = 'Sims with LEAST tolerant SB and PB strains + average CB strain (solid line)\nVersus\nSims with diversity in SBPB, no diversity (average value) in CB (dashed line)')
+
+plot_ss_result2(var_expt_most_tolerant_SBPB$ss_res[[1]],
+                var_expt_copy[no_diversity,]$ss_res[[1]],
+                xlims = c(-7, -1))+
+  plot_annotation(title = 'Sims with MOST tolerant SB and PB strains + average CB strain (solid line)\nVersus\nSims with no diversity (average values) (dashed line)')
+
+plot_ss_result2(var_expt_most_tolerant_SBPB$ss_res[[1]],
+                var_expt_copy[max_only_SBPB_diversity,]$ss_res[[1]],
+                xlims = c(-7, -1))+
+  plot_annotation(title = 'Sims with MOST tolerant SB and PB strains + average CB strain (solid line)\nVersus\nSims with diversity in SBPB, no diversity (average value) in CB (dashed line)')
+```
+
 # Zoom in on SS

### 2021-08-12 experiments/experiment 1/experiment-1.Rmd
corrected: x2x6 to x1x1

@@
 #var_expt_levels[20,]
-var_expt_copy <- var_expt
 ```
@@
 ## multiplier of SBPB variation
-CB_var_multiplier <- 2
-SBPB_var_multiplier <- 6
+CB_var_multiplier <- 1
+SBPB_var_multiplier <- 1
 
@@
 var_expt_least_tolerant_SBPB <- run_ss_var_experiment()
-saveRDS(var_expt_least_tolerant_SBPB, here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_SBPB_least_tolerant.RDS"))
+saveRDS(var_expt_least_tolerant_SBPB, here("experiments/experiment 1/data/ss_data_1e6_x1x1_factorial_SBPB_least_tolerant.RDS"))
 
@@
 var_expt_most_tolerant_SBPB <- run_ss_var_experiment()
-saveRDS(var_expt_most_tolerant_SBPB, here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_SBPB_most_tolerant.RDS"))
+saveRDS(var_expt_most_tolerant_SBPB, here("experiments/experiment 1/data/ss_data_1e6_x1x1_factorial_SBPB_most_tolerant.RDS"))
 ```
@@
 ```{r, fig.height=7.5, fig.width=12}
-var_expt_least_tolerant_SBPB <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_SBPB_least_tolerant.RDS"))
-var_expt_most_tolerant_SBPB <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_SBPB_most_tolerant.RDS"))
+var_expt_least_tolerant_SBPB <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x1x1_factorial_SBPB_least_tolerant.RDS"))
+var_expt_most_tolerant_SBPB <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x1x1_factorial_SBPB_most_tolerant.RDS"))
 
@@
 ```{r, fig.height=8, fig.width=10, message=FALSE, warning=FALSE}
+var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS"))
+var_expt_levels <- var_expt[,1:6]
+no_diversity <- which(rowSums(abs(var_expt_levels))==0)
+max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
+                            rowSums(abs(var_expt_levels[,3:6])) &
+                              rowSums(abs(var_expt_levels[,1:2]))==0)
+
 plot_ss_result2(var_expt_least_tolerant_SBPB$ss_res[[1]],
-                var_expt_copy[no_diversity,]$ss_res[[1]],
+                var_expt[no_diversity,]$ss_res[[1]],
                 xlims = c(-7, -1))+
@@
 plot_ss_result2(var_expt_least_tolerant_SBPB$ss_res[[1]],
-                var_expt_copy[max_only_SBPB_diversity,]$ss_res[[1]],
+                var_expt[max_only_SBPB_diversity,]$ss_res[[1]],
                 xlims = c(-7, -1))+
@@
 plot_ss_result2(var_expt_most_tolerant_SBPB$ss_res[[1]],
-                var_expt_copy[no_diversity,]$ss_res[[1]],
+                var_expt[no_diversity,]$ss_res[[1]],
                 xlims = c(-7, -1))+
@@
 plot_ss_result2(var_expt_most_tolerant_SBPB$ss_res[[1]],
-                var_expt_copy[max_only_SBPB_diversity,]$ss_res[[1]],
+                var_expt[max_only_SBPB_diversity,]$ss_res[[1]],
                 xlims = c(-7, -1))+

### 2021-09-14 experiments/experiment 1/experiment-1.Rmd
add puzzles, and answers :)

--- 2021-07-28 experiments/experiment 1/experiment-1.Rmd
@@
 ```{r}
+## find various combinations of diversity
 var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS"))
@@
 
+var_expt_levels <- var_expt[,1:6]
+
+no_diversity <- which(rowSums(abs(var_expt_levels))==0)
+max_diversty_all <- which(max(rowSums(abs(var_expt_levels))) ==
+                            rowSums(abs(var_expt_levels)))
+max_only_CB_diversity <- which(max(rowSums(abs(var_expt_levels[,1:2]))) ==
+                            rowSums(abs(var_expt_levels[,1:2])) &
+                              rowSums(abs(var_expt_levels[,3:6]))==0)
+#var_expt_levels[381,]
+
+max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
+                            rowSums(abs(var_expt_levels[,3:6])) &
+                              rowSums(abs(var_expt_levels[,1:2]))==0)
+#var_expt_levels[20,]
+
+```
+
+```{r}
+
 p1  <- plot_ss_result1(var_expt,
-                result_index = 1,
+                result_index = no_diversity,
                 filename_prefix = NULL,
@@
 
-p1  <- plot_ss_result1(var_expt,
-                result_index = 400,
+#junk1 <- var_expt[no_diversity,]$ss_res[[1]]
+```
+
+```{r}
+
+p2  <- plot_ss_result1(var_expt,
+                result_index = max_diversty_all,
                 filename_prefix = NULL,
                 save_image_file = FALSE)
-p1
+p2
 
-p_overlay1 <- plot_ss_result2(var_expt[1,]$ss_res[[1]],
-                             var_expt[400,]$ss_res[[1]],
+```
+
+```{r}
+
+p3  <- plot_ss_result1(var_expt,
+                result_index = max_only_CB_diversity,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p3
+
+```
+
+```{r}
+
+p4  <- plot_ss_result1(var_expt,
+                result_index = max_only_SBPB_diversity,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p4
+
+```
+
+```{r}
+p_overlay1 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
+                             var_expt[max_diversty_all,]$ss_res[[1]],
                              xlims = c(-7, -1))
 p_overlay1
+```
+
+```{r}
+p_overlay2 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
+                             var_expt[max_only_CB_diversity,]$ss_res[[1]],
+                             xlims = c(-7, -1))
+p_overlay2
+
+#ss_result1 <- var_expt[no_diversity,]$ss_res[[1]]
+#ss_result2 <- var_expt[max_only_CB_diversity,]$ss_res[[1]]
+
+```
+
+```{r}
+p_overlay3 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
+                             var_expt[max_only_SBPB_diversity,]$ss_res[[1]],
+                             xlims = c(-7, -1))
+p_overlay3
+
+#ss_result3 <- var_expt[max_only_SBPB_diversity,]$ss_res[[1]]
+
+```
+
+```{r}
+tempp1 <- var_expt[no_diversity,]$ss_res[[1]] %>%
+  filter(initial_N_CB == 1e10,
+         log10(a_O) > -4.5, log10(a_O) < -4)
+tempp2 <- var_expt[max_only_SBPB_diversity,]$ss_res[[1]] %>%
+  filter(initial_N_CB == 1e10,
+         log10(a_O) > -4.5, log10(a_O) < -4)
+
+ggplot() +
+  geom_line(mapping = aes(x = log10(tempp1$a_O),
+                          y = log10(tempp1$O))) +
+  geom_line(mapping = aes(x = log10(tempp2$a_O),
+                          y = log10(tempp2$O)),
+            col = "blue")
+
+ggplot() +
+  geom_histogram(mapping = aes(x = log10(tempp1$O) - log10(tempp2$O)),
+            col = "blue")
+
+ggplot() +
+  geom_line(mapping = aes(x = log10(tempp1$a_O),
+    y = log10(tempp1$P) - log10(tempp2$P)),
+            col = "blue")
+
+```
+
+```{r}
 
@@
 
+```
+
+# Some puzzles
+
+## Puzzle 1
+
+When the environment ameliorates for the sulphur bacteria, there is no strain replacement (in final state) along the oxygen diffusivity gradient -- either the system is oxic or the least tolerant strain SB9 dominates.
+And yet the switch to anoxic occurs earlier than when there is no diversity, which suggests there is some role of the more tolerant strains.
+Indeed Uriah showed that the presence of only the most tolerant strain is sufficient to give an earlier switch, even though it is not present in the final state when less tolerant strains are present.
+And he showed that the presence of only the least tolerant strain creates a later switch than when there are more tolerant strains.
+
+The explanation is that the most tolerant strain does play a role, but only a transient one.
+The following dynamics are for the system starting oxic, and with a value of oxygen diffusivity (log10(a_O) = -4.8) for which the system remains oxic if there is no diversity, but switches to anoxic if there is diversity.
+There is only diversity in the sulphur bacteria.
+The most tolerant strain does at first grow, but is then outcompeted by less tolerant strains as the environment ameliorates (temporally).
+
+```{r}
+var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS"))
+var_expt_levels <- var_expt[,1:6]
+no_diversity <- which(rowSums(abs(var_expt_levels))==0)
+max_diversty_all <- which(max(rowSums(abs(var_expt_levels))) ==
+                            rowSums(abs(var_expt_levels)))
+max_only_CB_diversity <- which(max(rowSums(abs(var_expt_levels[,1:2]))) ==
+                            rowSums(abs(var_expt_levels[,1:2])) &
+                              rowSums(abs(var_expt_levels[,3:6]))==0)
+max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
+                            rowSums(abs(var_expt_levels[,3:6])) &
+                              rowSums(abs(var_expt_levels[,1:2]))==0)
+```
+
+```{r eval = eval_dynamics_flag}
+default_sim_duration <- 100000
+```
+
+```{r eval = eval_dynamics_flag}
+default_log10a_series <- c(-4.8, -4.8)
+initial_state <- new_initial_state(num_CB_strains,
+                                   num_PB_strains,
+                                   num_SB_strains,
+                                   values = "bush_ssfig3")
+initial_state[grep("CB_", names(initial_state))] <- 10^10/num_CB_strains
+sim_res_novar1 <- run_simulation(parameter_values = var_expt$pars[[no_diversity]],
+                          initial_state = initial_state)
+saveRDS(sim_res_novar1, here("experiments/experiment 1/data/puzzle1_1.RDS"))
+```
+
+```{r}
+sim_res_novar1 <- readRDS(here("experiments/experiment 1/data/puzzle1_1.RDS"))
+plot_dynamics(sim_res_novar1)
+#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
+```
+
+```{r eval = eval_dynamics_flag}
+sim_res_novar1 <- run_simulation(parameter_values = var_expt$pars[[max_only_SBPB_diversity]],
+                          initial_state = initial_state)
+saveRDS(sim_res_novar1, here("experiments/experiment 1/data/puzzle1_2.RDS"))
+```
+
+```{r}
+sim_res_novar1 <- readRDS(here("experiments/experiment 1/data/puzzle1_2.RDS"))
+plot_dynamics(sim_res_novar1)
+#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
 ```

### 2021-09-15 experiments/experiment 1/experiment-1.Rmd
WORK IN PROGRESS! Conversion `experiment-1.Rmd` step one

@@
 output:
-  pdf_document: default
   html_document:
@@
 
-This experiment supercedes all previous ones.
+This experiment supersedes all previous ones.
 It is a factorial manipulation of diversity of the three groups.
@@
 
-microxanox_release <- "0.2"
+microxanox_release <- "0.2.3_beta"
 
@@
 library(microxanox)
+if (packageVersion("microxanox") < package_version("0.2.3")) {
+  stop("microxanox version needs to be at least 0.2.3!")
+}
 library(tidyverse)
@@
 ```{r}
-default_dynamic_model <- bushplus_dynamic_model
-default_event_definition <- event_definition_1
-default_event_interval <- 100
-default_noise_sigma <- 0
-default_minimum_abundances <- rep(1, 3)
-names(default_minimum_abundances) <- c("CB", "PB", "SB")
-default_sim_duration <- 80000
-default_sim_sample_interval <- 100
-initial_pars_from <- "bush_ssfig3"
+
+# default_dynamic_model <- bushplus_dynamic_model
+# default_event_definition <- event_definition_1
+# default_event_interval <- 100
+# default_noise_sigma <- 0
+# default_minimum_abundances <- rep(1, 3)
+# names(default_minimum_abundances) <- c("CB", "PB", "SB")
+# default_sim_duration <- 80000
+# default_sim_sample_interval <- 100
+# initial_pars_from <- "bush_ssfig3"
 ## note that next line (log10a_series is over-ridden with getting stable states)
 #default_log10a_series <- c(-2, -2, -2, -2, -10, -10, -10, -10, -10)
-```
-
-## Define diversity
-
-```{r}
+
 num_CB_strains <- 9
@@
 
+sp <- new_strain_parameter(
+  n_CB = 9,
+  n_PB = 9,
+  n_SB = 9,
+
+  values_initial_state = "bush_ssfig3"
+)
+
+parameter <- new_runsim_parameter(
+  dynamic_model = bushplus_dynamic_model,
+  event_definition = event_definition_1,
+  event_interval = 100,
+  noise_sigma = 0,
+  minimum_abundances = rep(0, 3),
+  sim_duration = 2000,
+  sim_sample_interval = 100,
+  strain_parameter = sp,
+  log10a_series = c(
+    log10(sp$a_O),
+    log10(sp$a_O)
+  )
+)
+names(parameter$minimum_abundances) <- c("CB", "PB", "SB")
+rm(sp)
+
+```
+
+## Define diversity
+
+```{r}
 ## multiplier of SBPB variation
@@
 num_div_treatment_levels <- 20
+
 ```
@@
 ```{r}
-var_expt <- create_diversity_factorial()
+var_expt <- create_diversity_factorial(
+  zero = zero, unity = unity,
+  num_div_treatment_levels = num_div_treatment_levels,
+  CB_gmax_div = CB_gmax_div, CB_h_div = CB_h_div,
+  SB_gmax_div = SB_gmax_div, SB_h_div = SB_h_div,
+  PB_gmax_div = PB_gmax_div, PB_h_div = PB_h_div,
+  default_9strain = new_strain_parameter(
+    n_CB = num_CB_strains,
+    n_SB = num_SB_strains,
+    n_PB = num_PB_strains,
+    values_initial_state =  "bush_ssfig3"
+  )
+)
 ```
@@
 ```{r}
-display_diversity(400)
+display_diversity(
+  400,
+  var_expt = var_expt,
+  num_CB_strains = num_CB_strains,
+  num_SB_strains = num_SB_strains,
+  num_PB_strains = num_PB_strains
+)
 ```
@@
 ```{r}
-var_expt_levels <- var_expt[,1:6]
-
-no_diversity <- which(rowSums(abs(var_expt_levels))==0)
-max_diversty_all <- which(max(rowSums(abs(var_expt_levels))) ==
-                            rowSums(abs(var_expt_levels)))
-max_only_CB_diversity <- which(max(rowSums(abs(var_expt_levels[,1:2]))) ==
-                            rowSums(abs(var_expt_levels[,1:2])) &
-                              rowSums(abs(var_expt_levels[,3:6]))==0)
-#var_expt_levels[381,]
-
-max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
-                            rowSums(abs(var_expt_levels[,3:6])) &
-                              rowSums(abs(var_expt_levels[,1:2]))==0)
+var_expt_levels <- var_expt[, 1:6]
+
+no_diversity <- which(rowSums(abs(var_expt_levels)) == 0)
+max_diversty_all <- which(
+  max(rowSums(abs(var_expt_levels))) == rowSums(abs(var_expt_levels))
+)
+max_only_CB_diversity <- which(
+  max(rowSums(abs(var_expt_levels[, 1:2]))) == rowSums(abs(var_expt_levels[, 1:2])) &
+  rowSums(abs(var_expt_levels[,3:6])) == 0
+)
+# var_expt_levels[381,]
+
+max_only_SBPB_diversity <- which(
+  max(rowSums(abs(var_expt_levels[, 3:6]))) == rowSums(abs(var_expt_levels[, 3:6])) &
+  rowSums(abs(var_expt_levels[, 1:2])) == 0
+)
 #var_expt_levels[20,]
@@
 ```{r eval = eval_dynamics_flag}
-default_sim_duration <- 80000
-```
-
-```{r eval = eval_dynamics_flag}
-default_log10a_series <- c(-1, -7, -7)
-initial_state <- new_initial_state(num_CB_strains,
+# default_sim_duration <- 80000
+parameter$sim_duration <- 80000
+```
+
+```{r eval = eval_dynamics_flag}
+stop("CHECK PARAMETER VALUES")
+# default_log10a_series <- c(-1, -7, -7)
+parameter$log10a_series <- c(-1, -7, -7)
+parameter$strain_parameter <- var_expt$pars[[no_diversity]]
+parameter$strain_parameter$initial_state <- new_initial_state(
+  num_CB_strains,
   num_PB_strains,
   num_SB_strains,
-                                   values = "bush_ssfig3")
-initial_state[grep("CB_", names(initial_state))] <- 10^10/num_CB_strains
-sim_res_novar1 <- run_simulation(parameter_values = var_expt$pars[[no_diversity]],
-                          initial_state = initial_state)
+  values = "bush_ssfig3"
+)
+parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/num_CB_strains
+sim_res_novar1 <- run_simulation(parameter)
 saveRDS(sim_res_novar1, here("experiments/experiment 1/data/sim_res_novar1.RDS"))
@@
 
-var_expt <- create_diversity_factorial()
-
-display_diversity(4)
+var_expt <- create_diversity_factorial(zero = zero, unity = unity, num_div_treatment_levels = num_div_treatment_levels)
+
+display_diversity(
+ 4,
+  var_expt = var_expt,
+  num_CB_strains = num_CB_strains,
+  num_SB_strains = num_SB_strains,
+  num_PB_strains = num_PB_strains
+)
 

### 2021-09-16 experiments/experiment 1/experiment-1.Rmd
Conversion next step

@@
 
-library(microxanox)
-if (packageVersion("microxanox") < package_version("0.2.3")) {
+library(microxanoxBeta)
+if (packageVersion("microxanoxBeta") < package_version("0.2.3")) {
   stop("microxanox version needs to be at least 0.2.3!")
@@
   noise_sigma = 0,
-  minimum_abundances = rep(0, 3),
+  minimum_abundances = rep(1, 3),
   sim_duration = 2000,
@@
 ```{r eval = eval_dynamics_flag}
-stop("CHECK PARAMETER VALUES")
 # default_log10a_series <- c(-1, -7, -7)
@@
 parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/num_CB_strains
-sim_res_novar1 <- run_simulation(parameter)
-saveRDS(sim_res_novar1, here("experiments/experiment 1/data/sim_res_novar1.RDS"))
+# sim_res_novar1 <- run_simulation(parameter)
+# saveRDS(sim_res_novar1, here("experiments/experiment 1/data/sim_res_novar1.RDS"))
 ```
@@
 ```{r eval = eval_dynamics_flag}
-sim_number <- num_div_treatment_levels
-sim_res_highvar1 <- run_simulation(parameter_values = var_expt$pars[[max_diversty_all]],
-                          initial_state = initial_state)
+# Is this actually needed?
+# sim_number <- num_div_treatment_levels
+
+parameter$strain_parameter <- var_expt$pars[[max_diversty_all]]
+parameter$strain_parameter$initial_state <- sim_res_novar1$strain_parameter$initial_state
+sim_res_highvar1 <- run_simulation(parameter)
 saveRDS(sim_res_highvar1, here("experiments/experiment 1/data/sim_res_highvar1.RDS"))
@@
 ```{r eval = eval_dynamics_flag}
-default_sim_duration <- 60000
-```
-
-```{r eval = eval_dynamics_flag}
-sim_number <- 1
-default_log10a_series <- c(-5, -3, -1, -1)
-initial_state <- new_initial_state(num_CB_strains,
+parameter$sim_duration <- 60000
+```
+
+```{r eval = eval_dynamics_flag}
+# sim_number <- 1
+parameter$log10a_series <- c(-5, -3, -1, -1)
+parameter$strain_parameter <- var_expt$pars[[no_diversity]]
+parameter$strain_parameter$initial_state <- new_initial_state(
+  num_CB_strains,
   num_PB_strains,
   num_SB_strains,
-                                   values = "bush_ssfig3")
-initial_state[grep("CB_", names(initial_state))] <- 10/num_CB_strains
-sim_res_novar2 <- run_simulation(parameter_values = var_expt$pars[[no_diversity]],
-                          initial_state = initial_state)
+  values = "bush_ssfig3"
+)
+parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10/num_CB_strains
+sim_res_novar2 <- run_simulation(parameter)
 saveRDS(sim_res_novar2, here("experiments/experiment 1/data/sim_res_novar2.RDS"))
@@
 sim_number <- num_div_treatment_levels
-sim_res_highvar2 <- run_simulation(parameter_values = var_expt$pars[[max_diversty_all]],
-                          initial_state = initial_state)
+parameter$strain_parameter <- var_expt$pars[[max_diversty_all]]
+parameter$strain_parameter$initial_state <- sim_res_novar2$strain_parameter$initial_state
+sim_res_highvar2 <- run_simulation(parameter)
 saveRDS(sim_res_highvar2, here("experiments/experiment 1/data/sim_res_highvar2.RDS"))
@@
 ```{r eval = eval_dynamics_flag}
-default_sim_duration <- 1000000
-```
-
-```{r eval = eval_dynamics_flag}
-default_minimum_abundances <- rep(100, 3)
-names(default_minimum_abundances) <- c("CB", "PB", "SB")
-```
-
-```{r eval = eval_dynamics_flag}
-sim_number1 <- 1
-default_log10a_series <- c(-1, -8, -1)
-initial_state <- new_initial_state(num_CB_strains,
+parameter$sim_duration <- 1000000
+```
+
+```{r eval = eval_dynamics_flag}
+parameter$minimum_abundances <- rep(100, 3)
+names(parameter$minimum_abundances) <- c("CB", "PB", "SB")
+```
+
+```{r eval = eval_dynamics_flag}
+# sim_number1 <- 1
+stop("CONTINUE HERE!!!!!")
+parameter$log10a_series <- c(-1, -8, -1)
+parameter$strain_parameter <- var_expt$pars[[no_diversity]]
+parameter$strain_parameter$initial_state <- new_initial_state(
+  num_CB_strains,
   num_PB_strains,
   num_SB_strains,
-                                   values = "bush_ssfig3")
-initial_state[grep("CB_", names(initial_state))] <- 10/num_CB_strains
-sim_res_novar3 <- run_simulation(parameter_values = var_expt$pars[[no_diversity]],
-                          initial_state = initial_state)
+  values = "bush_ssfig3"
+)
+parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10/num_CB_strains
+sim_res_novar3 <- run_simulation(parameter)
 saveRDS(sim_res_novar3, here("experiments/experiment 1/data/sim_res_novar3.RDS"))

### 2021-09-20 experiments/experiment 1/experiment-1.Rmd
Intermediate

@@
 num_div_treatment_levels <- 20
-
 ```
@@
 #var_expt_levels[20,]
-
 ```
@@
 parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/num_CB_strains
-# sim_res_novar1 <- run_simulation(parameter)
-# saveRDS(sim_res_novar1, here("experiments/experiment 1/data/sim_res_novar1.RDS"))
+sim_res_novar1 <- run_simulation(parameter)
+saveRDS(sim_res_novar1, here("experiments/experiment 1/data/sim_res_novar1.RDS"))
 ```
@@
 # sim_number1 <- 1
-stop("CONTINUE HERE!!!!!")
 parameter$log10a_series <- c(-1, -8, -1)
@@
 sim_number2 <- num_div_treatment_levels
-sim_res_highvar3 <- run_simulation(parameter_values = var_expt$pars[[max_diversty_all]],
-                          initial_state = initial_state)
+parameter$strain_parameter <- var_expt$pars[[max_diversty_all]]
+parameter$strain_parameter$initial_state <- sim_res_novar3$strain_parameter$initial_state
+sim_res_highvar3 <- run_simulation(parameter)
 saveRDS(sim_res_highvar3, here("experiments/experiment 1/data/sim_res_highvar3.RDS"))
@@
 ```{r}
-default_sim_duration <- 1000000
-ssfind_minimum_abundances <- rep(0, 3)
-names(ssfind_minimum_abundances) <- c("CB", "PB", "SB")
-ssfind_simulation_duration <- default_sim_duration
-ssfind_simulation_sampling_interval <- ssfind_simulation_duration
-ssfind_event_interval <- ssfind_simulation_duration
+# default_sim_duration <- 1000000
+# ssfind_minimum_abundances <- rep(0, 3)
+# names(ssfind_minimum_abundances) <- c("CB", "PB", "SB")
+# sfind_simulation_duration <- default_sim_duration
+# ssfind_simulation_sampling_interval <- ssfind_simulation_duration
+# ssfind_event_interval <- ssfind_simulation_duration
+
+minimum_abundances <- rep(0, 3)
+names(minimum_abundances) <- c("CB", "PB", "SB")
+
 grid_num_a <- 1000 #usually 1000 ## number of a_0 values
@@
 
+parameter <- new_ss_by_a_N_parameter(
+  sim_duration = 1000000,
+  sim_sample_interval = 1000000,
+  minimum_abundances = minimum_abundances,
+  event_interval = 1000000,
+  ss_expt = ss_expt
+)
+rm(minimum_abundances, grid_num_a, a_Os, grid_num_N, initial_CBs, initial_PBs, initial_SBs, ss_expt)
+
+parameter$strain_parameter <- var_expt$pars[[1]] ### <<<
 ```
@@
 ```{r eval = FALSE}
-var_expt <- run_ss_var_experiment()
+# var_expt <- run_ss_var_experiment(parameter, var_expt)
+var_expt <- ss_by_a_N(parameter) ### <<< CHECK
 saveRDS(var_expt, here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS"))
-
 ```

### 2021-09-20 experiments/r functions/various_useful_functions.r

@@ -32,7 +32,7 @@ plot_and_save <- function(CB_var_gmax, CB_var_h,
 }
 
 
-run_ss_var_experiment <- function() {
+run_ss_var_experiment <- function(parameter, var_expt) {
 
   # var_expt <- tibble(CB_var_gmax_s,
   #                    CB_var_h_s,
@@ -83,7 +83,7 @@ run_ss_var_experiment <- function() {
       # SB_var_h = .$SB_var_h_s,
       # PB_var_gmax = .$PB_var_gmax_s,
       # PB_var_h = .$PB_var_h_s),
-      ss_res = ss_by_a_N(ss_expt, .$pars[[1]]),
+      ss_res = ss_by_a_N(parameter$ss_expt, .$pars[[1]]),
     )
   var_expt
 }

### 2021-09-23 experiments/experiment 1/experiment-1.Rmd
run_ss_var_experiment adjusted

@@
 unity <- 1 ## don't change!!!
-#options(mc.cores = 8)
+options(mc.cores = 8)
 eval_dynamics_flag <- FALSE
@@
 ```{r}
-options(mc.cores = 12)
+options(mc.cores = 6)
 ```
@@
 parameter <- new_ss_by_a_N_parameter(
+  dynamic_model = parameter$dynamic_model,
+  event_definition = parameter$event_definition,
+  event_interval = 1000000,
+  noise_sigma = parameter$noise_sigma,
+  minimum_abundances = minimum_abundances,
   sim_duration = 1000000,
   sim_sample_interval = 1000000,
-  minimum_abundances = minimum_abundances,
-  event_interval = 1000000,
+  log10a_series = parameter$log10a_series,
+  solver_method = parameter$solver_method,
   ss_expt = ss_expt
@@
 rm(minimum_abundances, grid_num_a, a_Os, grid_num_N, initial_CBs, initial_PBs, initial_SBs, ss_expt)
-
-parameter$strain_parameter <- var_expt$pars[[1]] ### <<<
 ```
@@
 ```{r eval = FALSE}
-# var_expt <- run_ss_var_experiment(parameter, var_expt)
-var_expt <- ss_by_a_N(parameter) ### <<< CHECK
+
+var_expt_res <- run_ss_var_experiment(parameter, var_expt[1:3,])
+
 saveRDS(var_expt, here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS"))
@@
 var_expt1 <- readRDS(here("experiments/experiment 1/data/ss_data_80000.RDS")) %>%
-  mutate(sim_length = 80000)
+  mutate(sim_length = 80000) %>%
+  mutate(ss_res = ss_by_a_N_result$result)
+
 stab_data1 <- var_expt1 %>%

### 2021-09-23 experiments/r functions/various_useful_functions.r

@@ -71,20 +71,29 @@ run_ss_var_experiment <- function(parameter, var_expt) {
   ## For each line of var_expt, add strain variation, and get stable states.
   var_expt <- var_expt %>%
     group_by(
-      CB_var_gmax_s, CB_var_h_s,
-      SB_var_gmax_s, SB_var_h_s,
-      PB_var_gmax_s, PB_var_h_s,
+      CB_var_gmax_s, 
+      CB_var_h_s,
+      SB_var_gmax_s, 
+      SB_var_h_s,
+      PB_var_gmax_s, 
+      PB_var_h_s,
       data, pars
     ) %>%
-    do( # pars = add_strain_var(default_9strain,
+    do( 
+      # pars = add_strain_var(default_9strain,
       # CB_var_gmax = .$CB_var_gmax_s,
       # CB_var_h = .$CB_var_h_s,
       # SB_var_gmax = .$SB_var_gmax_s,
       # SB_var_h = .$SB_var_h_s,
       # PB_var_gmax = .$PB_var_gmax_s,
       # PB_var_h = .$PB_var_h_s),
-      ss_res = ss_by_a_N(parameter$ss_expt, .$pars[[1]]),
-    )
+      ss_by_a_N_result = {
+        parameter$strain_parameter <- .$pars[[1]]
+        ss_by_a_N(parameter)
+      }
+    ) %>%
+    mutate(ss_res = ss_by_a_N_result$result)
+  
   var_expt
 }
 

### 2021-09-28 experiments/experiment 1/experiment-1.Rmd
Adaptation for stability measures _raw and _log

--- 2021-09-16 experiments/experiment 1/experiment-1.Rmd
@@
 
-This experiment supersedes all previous ones.
+This experiment supercedes all previous ones.
 It is a factorial manipulation of diversity of the three groups.
@@
 
-microxanox_release <- "0.2.3_beta"
+microxanox_release <- "0.2"
 
@@
 
-library(microxanoxBeta)
-if (packageVersion("microxanoxBeta") < package_version("0.2.3")) {
-  stop("microxanox version needs to be at least 0.2.3!")
-}
+library(microxanox)
 library(tidyverse)
@@
 ```{r}
-
-# default_dynamic_model <- bushplus_dynamic_model
-# default_event_definition <- event_definition_1
-# default_event_interval <- 100
-# default_noise_sigma <- 0
-# default_minimum_abundances <- rep(1, 3)
-# names(default_minimum_abundances) <- c("CB", "PB", "SB")
-# default_sim_duration <- 80000
-# default_sim_sample_interval <- 100
-# initial_pars_from <- "bush_ssfig3"
+default_dynamic_model <- bushplus_dynamic_model
+default_event_definition <- event_definition_1
+default_event_interval <- 100
+default_noise_sigma <- 0
+default_minimum_abundances <- rep(1, 3)
+names(default_minimum_abundances) <- c("CB", "PB", "SB")
+default_sim_duration <- 80000
+default_sim_sample_interval <- 100
+initial_pars_from <- "bush_ssfig3"
 ## note that next line (log10a_series is over-ridden with getting stable states)
 #default_log10a_series <- c(-2, -2, -2, -2, -10, -10, -10, -10, -10)
-
+```
+
+## Define diversity
+
+```{r}
 num_CB_strains <- 9
@@
 
-sp <- new_strain_parameter(
-  n_CB = 9,
-  n_PB = 9,
-  n_SB = 9,
-
-  values_initial_state = "bush_ssfig3"
-)
-
-parameter <- new_runsim_parameter(
-  dynamic_model = bushplus_dynamic_model,
-  event_definition = event_definition_1,
-  event_interval = 100,
-  noise_sigma = 0,
-  minimum_abundances = rep(1, 3),
-  sim_duration = 2000,
-  sim_sample_interval = 100,
-  strain_parameter = sp,
-  log10a_series = c(
-    log10(sp$a_O),
-    log10(sp$a_O)
-  )
-)
-names(parameter$minimum_abundances) <- c("CB", "PB", "SB")
-rm(sp)
-
-```
-
-## Define diversity
-
-```{r}
 ## multiplier of SBPB variation
@@
 ```{r}
-var_expt <- create_diversity_factorial(
-  zero = zero, unity = unity,
-  num_div_treatment_levels = num_div_treatment_levels,
-  CB_gmax_div = CB_gmax_div, CB_h_div = CB_h_div,
-  SB_gmax_div = SB_gmax_div, SB_h_div = SB_h_div,
-  PB_gmax_div = PB_gmax_div, PB_h_div = PB_h_div,
-  default_9strain = new_strain_parameter(
-    n_CB = num_CB_strains,
-    n_SB = num_SB_strains,
-    n_PB = num_PB_strains,
-    values_initial_state =  "bush_ssfig3"
-  )
-)
+var_expt <- create_diversity_factorial()
 ```
@@
 ```{r}
-display_diversity(
-  400,
-  var_expt = var_expt,
-  num_CB_strains = num_CB_strains,
-  num_SB_strains = num_SB_strains,
-  num_PB_strains = num_PB_strains
-)
+display_diversity(400)
 ```
@@
 ```{r}
-var_expt_levels <- var_expt[, 1:6]
-
-no_diversity <- which(rowSums(abs(var_expt_levels)) == 0)
-max_diversty_all <- which(
-  max(rowSums(abs(var_expt_levels))) == rowSums(abs(var_expt_levels))
-)
-max_only_CB_diversity <- which(
-  max(rowSums(abs(var_expt_levels[, 1:2]))) == rowSums(abs(var_expt_levels[, 1:2])) &
-  rowSums(abs(var_expt_levels[,3:6])) == 0
-)
-# var_expt_levels[381,]
-
-max_only_SBPB_diversity <- which(
-  max(rowSums(abs(var_expt_levels[, 3:6]))) == rowSums(abs(var_expt_levels[, 3:6])) &
-  rowSums(abs(var_expt_levels[, 1:2])) == 0
-)
+var_expt_levels <- var_expt[,1:6]
+
+no_diversity <- which(rowSums(abs(var_expt_levels))==0)
+max_diversty_all <- which(max(rowSums(abs(var_expt_levels))) ==
+                            rowSums(abs(var_expt_levels)))
+max_only_CB_diversity <- which(max(rowSums(abs(var_expt_levels[,1:2]))) ==
+                            rowSums(abs(var_expt_levels[,1:2])) &
+                              rowSums(abs(var_expt_levels[,3:6]))==0)
+#var_expt_levels[381,]
+
+max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
+                            rowSums(abs(var_expt_levels[,3:6])) &
+                              rowSums(abs(var_expt_levels[,1:2]))==0)
 #var_expt_levels[20,]
@@
 ```{r eval = eval_dynamics_flag}
-# default_sim_duration <- 80000
-parameter$sim_duration <- 80000
+default_sim_duration <- 80000
 ```
@@
 ```{r eval = eval_dynamics_flag}
-# default_log10a_series <- c(-1, -7, -7)
-parameter$log10a_series <- c(-1, -7, -7)
-parameter$strain_parameter <- var_expt$pars[[no_diversity]]
-parameter$strain_parameter$initial_state <- new_initial_state(
-  num_CB_strains,
+default_log10a_series <- c(-1, -7, -7)
+initial_state <- new_initial_state(num_CB_strains,
                                    num_PB_strains,
                                    num_SB_strains,
-  values = "bush_ssfig3"
-)
-parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/num_CB_strains
-# sim_res_novar1 <- run_simulation(parameter)
-# saveRDS(sim_res_novar1, here("experiments/experiment 1/data/sim_res_novar1.RDS"))
+                                   values = "bush_ssfig3")
+initial_state[grep("CB_", names(initial_state))] <- 10^10/num_CB_strains
+sim_res_novar1 <- run_simulation(parameter_values = var_expt$pars[[no_diversity]],
+                          initial_state = initial_state)
+saveRDS(sim_res_novar1, here("experiments/experiment 1/data/sim_res_novar1.RDS"))
 ```
@@
 ```{r eval = eval_dynamics_flag}
-# Is this actually needed?
-# sim_number <- num_div_treatment_levels
-
-parameter$strain_parameter <- var_expt$pars[[max_diversty_all]]
-parameter$strain_parameter$initial_state <- sim_res_novar1$strain_parameter$initial_state
-sim_res_highvar1 <- run_simulation(parameter)
+sim_number <- num_div_treatment_levels
+sim_res_highvar1 <- run_simulation(parameter_values = var_expt$pars[[max_diversty_all]],
+                          initial_state = initial_state)
 saveRDS(sim_res_highvar1, here("experiments/experiment 1/data/sim_res_highvar1.RDS"))
@@
 ```{r eval = eval_dynamics_flag}
-parameter$sim_duration <- 60000
+default_sim_duration <- 60000
 ```
@@
 ```{r eval = eval_dynamics_flag}
-# sim_number <- 1
-parameter$log10a_series <- c(-5, -3, -1, -1)
-parameter$strain_parameter <- var_expt$pars[[no_diversity]]
-parameter$strain_parameter$initial_state <- new_initial_state(
-  num_CB_strains,
+sim_number <- 1
+default_log10a_series <- c(-5, -3, -1, -1)
+initial_state <- new_initial_state(num_CB_strains,
                                    num_PB_strains,
                                    num_SB_strains,
-  values = "bush_ssfig3"
-)
-parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10/num_CB_strains
-sim_res_novar2 <- run_simulation(parameter)
+                                   values = "bush_ssfig3")
+initial_state[grep("CB_", names(initial_state))] <- 10/num_CB_strains
+sim_res_novar2 <- run_simulation(parameter_values = var_expt$pars[[no_diversity]],
+                          initial_state = initial_state)
 saveRDS(sim_res_novar2, here("experiments/experiment 1/data/sim_res_novar2.RDS"))
@@
 sim_number <- num_div_treatment_levels
-parameter$strain_parameter <- var_expt$pars[[max_diversty_all]]
-parameter$strain_parameter$initial_state <- sim_res_novar2$strain_parameter$initial_state
-sim_res_highvar2 <- run_simulation(parameter)
+sim_res_highvar2 <- run_simulation(parameter_values = var_expt$pars[[max_diversty_all]],
+                          initial_state = initial_state)
 saveRDS(sim_res_highvar2, here("experiments/experiment 1/data/sim_res_highvar2.RDS"))
@@
 ```{r eval = eval_dynamics_flag}
-parameter$sim_duration <- 1000000
+default_sim_duration <- 1000000
 ```
@@
 ```{r eval = eval_dynamics_flag}
-parameter$minimum_abundances <- rep(100, 3)
-names(parameter$minimum_abundances) <- c("CB", "PB", "SB")
+default_minimum_abundances <- rep(100, 3)
+names(default_minimum_abundances) <- c("CB", "PB", "SB")
 ```
@@
 ```{r eval = eval_dynamics_flag}
-# sim_number1 <- 1
-stop("CONTINUE HERE!!!!!")
-parameter$log10a_series <- c(-1, -8, -1)
-parameter$strain_parameter <- var_expt$pars[[no_diversity]]
-parameter$strain_parameter$initial_state <- new_initial_state(
-  num_CB_strains,
+sim_number1 <- 1
+default_log10a_series <- c(-1, -8, -1)
+initial_state <- new_initial_state(num_CB_strains,
                                    num_PB_strains,
                                    num_SB_strains,
-  values = "bush_ssfig3"
-)
-parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10/num_CB_strains
-sim_res_novar3 <- run_simulation(parameter)
+                                   values = "bush_ssfig3")
+initial_state[grep("CB_", names(initial_state))] <- 10/num_CB_strains
+sim_res_novar3 <- run_simulation(parameter_values = var_expt$pars[[no_diversity]],
+                          initial_state = initial_state)
 saveRDS(sim_res_novar3, here("experiments/experiment 1/data/sim_res_novar3.RDS"))
@@
 
-#saveRDS(all_stab_results, here("experiments/experiment summary/all_stab.RDS"))
-
-#all_stab_results <- readRDS(here("experiments/experiment summary/all_stab.RDS"))
+saveRDS(all_stab_results, here("experiments/experiment 1/data/all_stab.RDS"))
+
+```
+
+### Raw Stability
+```{r plot1_raw}
+all_stab_results <- readRDS(here("experiments/experiment 1/data/all_stab.RDS"))
 
@@
   filter(Species == "O") %>%
-  ggplot(aes(x = var_gmax, y = hyst_range, col=var_treat, shape = as_factor(sim_length))) +
+  ggplot(aes(x = var_gmax, y = hyst_range_raw, col=var_treat, shape = as_factor(sim_length))) +
   geom_point() +
@@
   ggplot(aes(x = var_gmax,
-             ymin = hyst_min,
-             ymax = hyst_max,
+             ymin = hyst_min_raw,
+             ymax = hyst_max_raw,
              fill=var_treat)) +
@@
          sim_length == 1e6) %>%
-  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range, col = hyst_range)) +
+  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range_raw, col = hyst_range_raw)) +
   geom_point(size = 3)
-
+```
+
+### Log Stability
+```{r plot1_log}
+all_stab_results <- readRDS(here("experiments/experiment 1/data/all_stab.RDS"))
+
+all_stab_results %>%
+  filter(Species == "O") %>%
+  ggplot(aes(x = var_gmax, y = hyst_range_log, col=var_treat, shape = as_factor(sim_length))) +
+  geom_point() +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
+  labs(col = "Variation in\nonly these\nfunctional groups")
+##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)
+
+all_stab_results %>%
+  #filter(var_treat == "CB") %>%
+  filter(Species == "O",
+         sim_length == 1e6) %>%
+  ggplot(aes(x = var_gmax,
+             ymin = hyst_min_log,
+             ymax = hyst_max_log,
+             fill=var_treat)) +
+  geom_ribbon(alpha = 0.5) +
+  facet_wrap( ~ var_treat, nrow = 3) +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
+  labs(fill = "Variation in\nonly these\nfunctional groups") + 
+  coord_flip() +
+  theme(
+    strip.background = element_blank(),
+    strip.text.x = element_blank()
+  )
+
+all_stab_results %>%
+  #filter(var_treat == "CB") %>%
+  filter(Species == "O",
+         sim_length == 8e4) %>%
+  ggplot(aes(x = var_gmax,
+             ymin = hyst_min_log,
+             ymax = hyst_max_log,
+             fill=var_treat)) +
+  geom_ribbon(alpha = 0.5) +
+  facet_wrap( ~ var_treat, nrow = 3) +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
+  labs(fill = "Variation in\nonly these\nfunctional groups") + 
+  coord_flip() +
+  theme(
+    strip.background = element_blank(),
+    strip.text.x = element_blank()
+  )
+
+##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
+stab_data1 <- readRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS"))
+stab_data_x <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
+stab_data_plus <- bind_rows(stab_data1, stab_data_x)
+stab_data_plus %>%
+  filter(Species == "O",
+         sim_length == 1e6) %>%
+  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range_log, col = hyst_range_log)) +
+  geom_point(size = 3)
 ```
@@
 
+### Raw Stability
 ```{r}
@@
   filter(Species == "O") %>%
-  ggplot(aes(x = SB_var_gmax_s, y = hyst_range)) +
+  ggplot(aes(x = SB_var_gmax_s, y = hyst_range_raw)) +
   geom_point() +
@@
   ggplot(aes(x = SB_var_gmax_s,
-             ymin = hyst_min,
-             ymax = hyst_max)) +
+             ymin = hyst_min_raw,
+             ymax = hyst_max_raw)) +
   geom_ribbon(alpha = 0.5) +
@@
   )
-
+```
+### Log Stability
+```{r}
+var_expt_x <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS"))
+stab_data_x <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
+
+p1  <- plot_ss_result1(var_expt_x,
+                result_index = 1,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p1
+
+p1  <- plot_ss_result1(var_expt_x,
+                result_index = 19,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p1
+
+p_overlay1 <- plot_ss_result2(var_expt_x[1,]$ss_res[[1]],
+                             var_expt_x[19,]$ss_res[[1]],
+                             xlims = c(-7, -1))
+p_overlay1
+
+stab_data_x %>%
+  filter(Species == "O") %>%
+  ggplot(aes(x = SB_var_gmax_s, y = hyst_range_log)) +
+  geom_point() +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
+  labs(col = "Variation in\nonly these\nfunctional groups")
+##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)
+
+stab_data_x %>%
+  #filter(var_treat == "CB") %>%
+  filter(Species == "O") %>%
+  ggplot(aes(x = SB_var_gmax_s,
+             ymin = hyst_min_log,
+             ymax = hyst_max_log)) +
+  geom_ribbon(alpha = 0.5) +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
+  coord_flip() +
+  theme(
+    strip.background = element_blank(),
+    strip.text.x = element_blank()
+  )
 ```
@@
 ```{r}
-
 CB_vars <- unique(stab_data$CB_var_gmax_s)
@@
 
+```
+
+### Raw Stability
+```{r}
 all_stab_results %>%
   filter(Species == "O") %>%
-  ggplot(aes(x = var_gmax, y = hyst_range, col=var_treat, shape = as_factor(sim_length))) +
+  ggplot(aes(x = var_gmax, y = hyst_range_raw, col=var_treat, shape = as_factor(sim_length))) +
   geom_point() +
@@
          sim_length == 1e6) %>%
-  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range, col = hyst_range)) +
+  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range_raw, col = hyst_range_raw)) +
   geom_point(size = 3)
@@
          sim_length == 1e6) %>%
-  ggplot(aes(x = CB_var_gmax_s, y = hyst_range, col = as.factor(SB_var_gmax_s))) +
+  ggplot(aes(x = CB_var_gmax_s, y = hyst_range_raw, col = as.factor(SB_var_gmax_s))) +
   geom_line(size = 2)
-
+```
+
+### Log Stability
+```{r}
+all_stab_results %>%
+  filter(Species == "O") %>%
+  ggplot(aes(x = var_gmax, y = hyst_range_log, col=var_treat, shape = as_factor(sim_length))) +
+  geom_point() +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
+  labs(col = "Variation in\nonly these\nfunctional groups")
+##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)
+
+all_stab_results %>%
+  #filter(var_treat == "CB") %>%
+  filter(Species == "O",
+         sim_length == 1e6) %>%
+  ggplot(aes(x = var_gmax,
+             ymin = hyst_min_log,
+             ymax = hyst_max_log,
+             fill=var_treat)) +
+  geom_ribbon(alpha = 0.5) +
+  facet_wrap( ~ var_treat, nrow = 3) +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
+  labs(fill = "Variation in\nonly these\nfunctional groups") + 
+  coord_flip() +
+  theme(
+    strip.background = element_blank(),
+    strip.text.x = element_blank()
+  )
+
+##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
+stab_data %>%
+  filter(Species == "O",
+         sim_length == 1e6) %>%
+  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range_log, col = hyst_range_log)) +
+  geom_point(size = 3)
+
+##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
+
+stab_data %>%
+  filter(Species == "O",
+         sim_length == 1e6) %>%
+  ggplot(aes(x = CB_var_gmax_s, y = hyst_range_log, col = as.factor(SB_var_gmax_s))) +
+  geom_line(size = 2)
 ```
@@
 
-var_expt <- create_diversity_factorial(zero = zero, unity = unity, num_div_treatment_levels = num_div_treatment_levels)
-
-display_diversity(
- 4,
-  var_expt = var_expt,
-  num_CB_strains = num_CB_strains,
-  num_SB_strains = num_SB_strains,
-  num_PB_strains = num_PB_strains
-)
+var_expt <- create_diversity_factorial()
+
+display_diversity(4)
 

### 2021-09-29 experiments/experiment 1/experiment-1.Rmd
various minor update to experiment 1 report

@@
 
-### Maximum diversity
+### Medium diversity
 
@@
 sim_number2 <- num_div_treatment_levels
-sim_res_highvar3 <- run_simulation(parameter_values = var_expt$pars[[max_diversty_all]],
+try_me <- 311
+sim_res_highvar3 <- run_simulation(parameter_values =
+                                     var_expt$pars[[try_me]],
                           initial_state = initial_state)
+# sim_res_highvar3 <- run_simulation(parameter_values =
+#                                      var_expt$pars[[max_diversty_all]],
+#                           initial_state = initial_state)
 saveRDS(sim_res_highvar3, here("experiments/experiment 1/data/sim_res_highvar3.RDS"))
@@
 ```{r eval = FALSE}
+sim_res_novar <- sim_res_novar3
+sim_res_highvar <- sim_res_highvar3
 visualise_temporal_env_eco()
@@
   xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
+  ylab("Extent of bistability region\n[oxygen diffusivity]") +
   labs(col = "Variation in\nonly these\nfunctional groups")
@@
   xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
+  ylab("Oxygen diffusivity\n[uM per hour]") +
   labs(fill = "Variation in\nonly these\nfunctional groups") + 
@@
 
-### Raw Stability
 ```{r}
@@
 p_overlay1
-
+```
+
+### Raw Stability
+
+```{r}
 stab_data_x %>%
@@
   xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
+  ylab("Oxygen diffusivity\n[uM per hour]") +
   coord_flip() +
@@
 ```
+
 ### Log Stability
 ```{r}
-var_expt_x <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS"))
-stab_data_x <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
-
-p1  <- plot_ss_result1(var_expt_x,
-                result_index = 1,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p1
-
-p1  <- plot_ss_result1(var_expt_x,
-                result_index = 19,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p1
-
-p_overlay1 <- plot_ss_result2(var_expt_x[1,]$ss_res[[1]],
-                             var_expt_x[19,]$ss_res[[1]],
-                             xlims = c(-7, -1))
-p_overlay1
 
@@
 
+## I (Owen) do not recall why we made the graphs in this section
+
 ```{r}
@@
 
+### Raw Stability
+
 ```{r}

### 2021-09-29 experiments/r functions/various_useful_functions.r

@@ -498,12 +498,12 @@ visualise_temporal_env_eco <- function() {
   
   soi <- "O"
   ggplot() +
+    geom_path(data = filter(tmp_highvar,functional_group == soi),
+                         aes(x=a, y = log10(Total_quantity), group = direction),
+                         linetype = "dashed", lwd=2, col="red") +
     geom_path(data = filter(tmp_novar,functional_group == soi),
               aes(x=a, y = log10(Total_quantity), group = direction)) +
-    geom_path(data = filter(tmp_highvar,functional_group == soi),
-              aes(x=a, y = log10(Total_quantity), group = direction),
-              linetype = "dashed", lwd=2, col="red") +
-    ggtitle("Solid line is with no intraspecific diversity.\nDashed line is with intraspecific diversity")
+    ggtitle("Black line is with no intraspecific diversity.\nRed line is with intraspecific diversity")
   ##ggsave(here("simulations/figures/switching_comparison.pdf"), width = 5, height = 4)
   
   

### 2021-10-04 experiments/experiment 1/experiment-1.Rmd
Fix run_ss_var_experiment function to work with new parameter format and return consistent and reproducible results

--- 2021-09-23 experiments/experiment 1/experiment-1.Rmd
@@
 ```{r eval = FALSE}
-visualise_temporal_env_eco()
+visualise_temporal_env_eco(sim_res_novar3, sim_res_highvar3)
 ```
@@
 
-```{r eval = FALSE}
-
-var_expt_res <- run_ss_var_experiment(parameter, var_expt[1:3,])
+```{r run_experiment, eval = eval_dynamics_flag}
+
+var_expt_res <- run_ss_var_experiment(parameter, var_expt)
 
@@
 ## sim length 80'000, 20 x 20 factorial, reference maximum diversity
+
 var_expt1 <- readRDS(here("experiments/experiment 1/data/ss_data_80000.RDS")) %>%
-  mutate(sim_length = 80000) %>%
-  mutate(ss_res = ss_by_a_N_result$result)
+  mutate(sim_length = 80000)
 
@@
 saveRDS(stab_data5, here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
-
 ```

### 2021-10-04 experiments/r functions/various_useful_functions.r

@@ -69,32 +69,18 @@ run_ss_var_experiment <- function(parameter, var_expt) {
 
   ## Next chunck of code:
   ## For each line of var_expt, add strain variation, and get stable states.
-  var_expt <- var_expt %>%
-    group_by(
-      CB_var_gmax_s, 
-      CB_var_h_s,
-      SB_var_gmax_s, 
-      SB_var_h_s,
-      PB_var_gmax_s, 
-      PB_var_h_s,
-      data, pars
+  result <- var_expt %>%
+    mutate(
+      ss_by_a_N_result = list({
+        p <- parameter
+        p$strain_parameter <- pars
+        p
+      })
     ) %>%
-    do( 
-      # pars = add_strain_var(default_9strain,
-      # CB_var_gmax = .$CB_var_gmax_s,
-      # CB_var_h = .$CB_var_h_s,
-      # SB_var_gmax = .$SB_var_gmax_s,
-      # SB_var_h = .$SB_var_h_s,
-      # PB_var_gmax = .$PB_var_gmax_s,
-      # PB_var_h = .$PB_var_h_s),
-      ss_by_a_N_result = {
-        parameter$strain_parameter <- .$pars[[1]]
-        ss_by_a_N(parameter)
-      }
-    ) %>%
-    mutate(ss_res = ss_by_a_N_result$result)
+    mutate(ss_by_a_N_result = list(ss_by_a_N(parameter))) %>%
+    mutate(ss_res = ss_by_a_N_result[[1]]$result)
   
-  var_expt
+  return(result)
 }
 
 
@@ -529,7 +515,7 @@ create_diversity_factorial <- function(
 }
 
 
-visualise_temporal_env_eco <- function() {
+visualise_temporal_env_eco <- function(sim_res_novar = NULL, sim_res_highvar = NULL) {
   tmp_novar <- sim_res_novar$result %>%
     filter(time != 0) %>%
     select(-time) %>%

### 2021-10-06 experiments/experiment 1/experiment-1.Rmd
Fix something more

@@
 options(mc.cores = 8)
-eval_dynamics_flag <- FALSE
+eval_dynamics_flag <- TRUE
 ```
@@
 
-num_div_treatment_levels <- 20
+## num_div_treatment_levels <- 20
+
+num_div_treatment_levels <- 3 ## FOR TEST
+
 ```
@@
 
-```{r}
+```{r eval = FALSE}
 display_diversity(
-  400,
+  400, ##seems to be necessary to be smaller than num_div_treatment_levels
   var_expt = var_expt,
@@
 ```{r}
-options(mc.cores = 6)
+options(mc.cores = 7)
 ```
@@
 
-grid_num_a <- 1000 #usually 1000 ## number of a_0 values
+## grid_num_a <- 1000 #usually 1000 ## number of a_0 values
+grid_num_a <- 100 ## FOR TEST
+
 a_Os <- 10^seq(-7, -0.5, length=grid_num_a) ## sequence of a_0 values
@@
 rm(minimum_abundances, grid_num_a, a_Os, grid_num_N, initial_CBs, initial_PBs, initial_SBs, ss_expt)
+saveRDS(parameter, here("experiments/experiment 1/data/TEST_parameter.RDS"))
+saveRDS(var_expt, here("experiments/experiment 1/data/TEST_var_expt.RDS"))
 ```
@@
 ```{r run_experiment, eval = eval_dynamics_flag}
+parameter <- readRDS(here("experiments/experiment 1/data/TEST_parameter.RDS"))
+var_expt <- readRDS(here("experiments/experiment 1/data/TEST_var_expt.RDS"))
 
@@
 Bring in various stable state datasets
-```{r eval = FALSE}
+```{r eval = TRUE}
 ## sim length 80'000, 20 x 20 factorial, reference maximum diversity

### 2021-10-06 experiments/experiment 1/experiment-1.Rmd
one change

@@
 
-```{r eval = FALSE}
+```{r}
 display_diversity(
-  400, ##seems to be necessary to be smaller than num_div_treatment_levels
+  9, ##TEST 
   var_expt = var_expt,

### 2021-10-06 experiments/experiment 1/experiment-1.Rmd
Some more for test

@@
 display_diversity(
-  9, ##TEST 
+  9, ## FOR TEST was 400
   var_expt = var_expt,

### 2021-10-26 experiments/experiment 1/experiment-1.Rmd
Moved R functions to R directory in root of project in preparation for possible structuring as package.

@@
 
-```{r}
+```{r setup}
 
@@
 library(here)
-source(here("experiments/r functions/various_useful_functions.r"))
+source(here("R/various_useful_functions.r"))
 zero <- 0 ## don't change
@@
 ```{r}
-options(mc.cores = 7)
+options(mc.cores = 8)
 ```

### 2021-10-26 experiments/experiment 1/experiment-1.Rmd
Move some more calculations into parallel

@@
 
-rm(list = ls())
+# rm(list = ls())
 
@@
 ```{r eval = TRUE}
+cluster <- multidplyr::new_cluster(7)
+multidplyr::cluster_library(cluster, c("microxanoxBeta", "dplyr"))
+
 ## sim length 80'000, 20 x 20 factorial, reference maximum diversity
-
-var_expt1 <- readRDS(here("experiments/experiment 1/data/ss_data_80000.RDS")) %>%
-  mutate(sim_length = 80000)
-
-stab_data1 <- var_expt1 %>%
-  group_by(CB_var_gmax_s, CB_var_h_s,
-           SB_var_gmax_s, SB_var_h_s,
-           PB_var_gmax_s, PB_var_h_s, sim_length) %>%
-  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
-stab_data1 <- unnest(stab_data1, cols = c(stability_measures))
-saveRDS(stab_data1, here("experiments/experiment 1/data/stab_data_80000.RDS"))
+readRDS(here("experiments/experiment 1/data/ss_data_80000.RDS")) %>%
+  mutate(sim_length = 80000) %>% 
+  multidplyr::partition(cluster) %>%
+  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
+  collect() %>%
+  unnest(cols = c(stability_measures)) %>%
+  saveRDS(here("experiments/experiment 1/data/stab_data_80000.RDS"))
 
 ## sim length 1'000'000, 20 x 20 factorial, reference maximum diversity
-var_expt2 <- readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS")) %>%
-  mutate(sim_length = 1000000)
-stab_data2 <- var_expt2 %>%
-  group_by(CB_var_gmax_s, CB_var_h_s,
-           SB_var_gmax_s, SB_var_h_s,
-           PB_var_gmax_s, PB_var_h_s, sim_length) %>%
-  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
-stab_data2 <- unnest(stab_data2, cols = c(stability_measures))
-saveRDS(stab_data2, here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS"))
+# var_expt2 <- readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS")) %>%
+#   mutate(sim_length = 1000000)
+# # stab_data2 <- var_expt2 %>%
+# #   group_by(CB_var_gmax_s, CB_var_h_s,
+# #            SB_var_gmax_s, SB_var_h_s,
+# #            PB_var_gmax_s, PB_var_h_s, sim_length) %>%
+# #   do(stability_measures = get_stability_measures(.$ss_res[[1]]))
+# stab_data2 <- var_expt2 %>%
+#   mutate(stability_measures = list(get_stability_measures(ss_res)))
+# stab_data2 <- unnest(stab_data2, cols = c(stability_measures))
+# saveRDS(stab_data2, here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS"))
+readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS")) %>%
+  mutate(sim_length = 1000000) %>% 
+  multidplyr::partition(cluster) %>%
+  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
+  collect() %>%
+  unnest(cols = c(stability_measures)) %>%
+  saveRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS"))
 
 ## sim length 1'000'000, 20 SBPBgrad, 5x maximum diversity
-var_expt3 <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS")) %>%
-  mutate(sim_length = 1000000)
-stab_data3 <- var_expt3 %>%
-  group_by(CB_var_gmax_s, CB_var_h_s,
-           SB_var_gmax_s, SB_var_h_s,
-           PB_var_gmax_s, PB_var_h_s, sim_length) %>%
-  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
-stab_data3 <- unnest(stab_data3, cols = c(stability_measures))
-saveRDS(stab_data3, here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
+# var_expt3 <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS")) %>%
+#   mutate(sim_length = 1000000)
+# stab_data3 <- var_expt3 %>%
+#   group_by(CB_var_gmax_s, CB_var_h_s,
+#            SB_var_gmax_s, SB_var_h_s,
+#            PB_var_gmax_s, PB_var_h_s, sim_length) %>%
+#   do(stability_measures = get_stability_measures(.$ss_res[[1]]))
+# stab_data3 <- unnest(stab_data3, cols = c(stability_measures))
+# saveRDS(stab_data3, here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
+readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS")) %>%
+  mutate(sim_length = 1000000) %>% 
+  multidplyr::partition(cluster) %>%
+  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
+  collect() %>%
+  unnest(cols = c(stability_measures)) %>%
+  saveRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
 
 ## sim length 300'000, 20 SBPBgrad, reference maximum diversity
-var_expt4 <- readRDS(here("experiments/experiment 1/data/ss_data_300000_small.RDS")) %>%
-  mutate(sim_length = 300000)
-stab_data4 <- var_expt4 %>%
-  group_by(CB_var_gmax_s, CB_var_h_s,
-           SB_var_gmax_s, SB_var_h_s,
-           PB_var_gmax_s, PB_var_h_s, sim_length) %>%
-  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
-stab_data4 <- unnest(stab_data4, cols = c(stability_measures))
-saveRDS(stab_data4, here("experiments/experiment 1/data/stab_data_300000.RDS"))
+# var_expt4 <- readRDS(here("experiments/experiment 1/data/ss_data_300000_small.RDS")) %>%
+#   mutate(sim_length = 300000)
+# stab_data4 <- var_expt4 %>%
+#   group_by(CB_var_gmax_s, CB_var_h_s,
+#            SB_var_gmax_s, SB_var_h_s,
+#            PB_var_gmax_s, PB_var_h_s, sim_length) %>%
+#   do(stability_measures = get_stability_measures(.$ss_res[[1]]))
+# stab_data4 <- unnest(stab_data4, cols = c(stability_measures))
+# saveRDS(stab_data4, here("experiments/experiment 1/data/stab_data_300000.RDS"))
+readRDS(here("experiments/experiment 1/data/ss_data_300000_small.RDS")) %>%
+  mutate(sim_length = 300000) %>% 
+  multidplyr::partition(cluster) %>%
+  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
+  collect() %>%
+  unnest(cols = c(stability_measures)) %>%
+  saveRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
 
 ## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
-var_expt5 <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS")) %>%
-  mutate(sim_length = 1000000)
-stab_data5 <- var_expt5 %>%
-  group_by(CB_var_gmax_s, CB_var_h_s,
-           SB_var_gmax_s, SB_var_h_s,
-           PB_var_gmax_s, PB_var_h_s, sim_length) %>%
-  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
-stab_data5 <- unnest(stab_data5, cols = c(stability_measures))
-saveRDS(stab_data5, here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
+# var_expt5 <- readRDS(here("experiments/experiment 1/data/stab_data_300000.RDS")) %>%
+#   mutate(sim_length = 1000000)
+# stab_data5 <- var_expt5 %>%
+#   group_by(CB_var_gmax_s, CB_var_h_s,
+#            SB_var_gmax_s, SB_var_h_s,
+#            PB_var_gmax_s, PB_var_h_s, sim_length) %>%
+#   do(stability_measures = get_stability_measures(.$ss_res[[1]]))
+# stab_data5 <- unnest(stab_data5, cols = c(stability_measures))
+# saveRDS(stab_data5, here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
+readRDS(here("experiments/experiment 1/data/stab_data_300000.RDS")) %>%
+  mutate(sim_length = 1000000) %>% 
+  multidplyr::partition(cluster) %>%
+  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
+  collect() %>%
+  unnest(cols = c(stability_measures)) %>%
+  saveRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
 ```

### 2021-10-27 experiments/experiment 1/experiment-1.Rmd
Next spep - only Puzzles left

@@
 unity <- 1 ## don't change!!!
-options(mc.cores = 8)
+options(mc.cores = 7)
 eval_dynamics_flag <- TRUE
@@
 
-```{r}
-options(mc.cores = 8)
+### Setup parameter
+
+```{r}
+options(mc.cores = 7)
 ```
@@
 
-Run stable state finding
+### Run stable state finding
 
@@
 
-Process the stable state data
+### Process the stable state data
 
 Bring in various stable state datasets
-```{r eval = TRUE}
+```{r eval = eval_dynamics_flag}
 cluster <- multidplyr::new_cluster(7)
@@
   unnest(cols = c(stability_measures)) %>%
-  saveRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
+  saveRDS(here("experiments/experiment 1/data/stab_data_300000.RDS"))
 
@@
 # saveRDS(stab_data5, here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
-readRDS(here("experiments/experiment 1/data/stab_data_300000.RDS")) %>%
+x <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS")) %>%
   mutate(sim_length = 1000000) %>% 
@@
 
-```{r}
-stab_data1 <- readRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS"))
-stab_data2 <- readRDS(here("experiments/experiment 1/data/stab_data_80000.RDS"))
-stab_data <- bind_rows(stab_data1, stab_data2)
+### Calculations
+```{r}
+stab_data <- bind_rows(
+  readRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS")), 
+  readRDS(here("experiments/experiment 1/data/stab_data_80000.RDS"))
+)
 
@@
 
-all_stab_results<- all_stab_results %>%
+all_stab_results <- all_stab_results %>%
     mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB-PB", "CB-SB-PB")))
 
-#saveRDS(all_stab_results, here("experiments/experiment summary/all_stab.RDS"))
-
-#all_stab_results <- readRDS(here("experiments/experiment summary/all_stab.RDS"))
+saveRDS(all_stab_results, here("experiments/experiment 1/data/all_stab.RDS"))
+```
+
+### Plot raw
+```{r}
+
+all_stab_results <- readRDS(here("experiments/experiment summary/all_stab.RDS"))
 
@@
 ##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
-stab_data1 <- readRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS"))
-stab_data_x <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
-stab_data_plus <- bind_rows(stab_data1, stab_data_x)
-stab_data_plus %>%
-  filter(Species == "O",
-         sim_length == 1e6) %>%
-  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range, col = hyst_range)) +
+
+bind_rows(
+  readRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS")), 
+  readRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
+) %>%
+  filter(
+    Species == "O",
+    sim_length == 1e6
+  ) %>%
+  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range_raw, col = hyst_range_raw)) +
   geom_point(size = 3)
@@
 
-## Extra SBPB diversity
-
-```{r}
-var_expt_x <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS"))
-stab_data_x <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
-
-p1  <- plot_ss_result1(var_expt_x,
-                result_index = 1,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p1
-
-p1  <- plot_ss_result1(var_expt_x,
-                result_index = 19,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p1
-
-p_overlay1 <- plot_ss_result2(var_expt_x[1,]$ss_res[[1]],
-                             var_expt_x[19,]$ss_res[[1]],
-                             xlims = c(-7, -1))
-p_overlay1
-
-stab_data_x %>%
+### Plot log
+```{r}
+
+all_stab_results <- readRDS(here("experiments/experiment summary/all_stab.RDS"))
+
+all_stab_results %>%
   filter(Species == "O") %>%
-  ggplot(aes(x = SB_var_gmax_s, y = hyst_range)) +
+  ggplot(aes(x = var_gmax, y = hyst_range_log, col=var_treat, shape = as_factor(sim_length))) +
   geom_point() +
@@
 
-stab_data_x %>%
-  #filter(var_treat == "CB") %>%
-  filter(Species == "O") %>%
-  ggplot(aes(x = SB_var_gmax_s,
-             ymin = hyst_min,
-             ymax = hyst_max)) +
-  geom_ribbon(alpha = 0.5) +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
-  coord_flip() +
-  theme(
-    strip.background = element_blank(),
-    strip.text.x = element_blank()
-  )
-
-```
-
-## 2x CB, 6xSBPB diversity
-
-```{r}
-## find various combinations of diversity
-var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS"))
-stab_data <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
-
-var_expt_levels <- var_expt[,1:6]
-
-no_diversity <- which(rowSums(abs(var_expt_levels))==0)
-max_diversty_all <- which(max(rowSums(abs(var_expt_levels))) ==
-                            rowSums(abs(var_expt_levels)))
-max_only_CB_diversity <- which(max(rowSums(abs(var_expt_levels[,1:2]))) ==
-                            rowSums(abs(var_expt_levels[,1:2])) &
-                              rowSums(abs(var_expt_levels[,3:6]))==0)
-#var_expt_levels[381,]
-
-max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
-                            rowSums(abs(var_expt_levels[,3:6])) &
-                              rowSums(abs(var_expt_levels[,1:2]))==0)
-#var_expt_levels[20,]
-
-```
-
-```{r}
-
-p1  <- plot_ss_result1(var_expt,
-                result_index = no_diversity,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p1
-
-#junk1 <- var_expt[no_diversity,]$ss_res[[1]]
-```
-
-```{r}
-
-p2  <- plot_ss_result1(var_expt,
-                result_index = max_diversty_all,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p2
-
-```
-
-```{r}
-
-p3  <- plot_ss_result1(var_expt,
-                result_index = max_only_CB_diversity,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p3
-
-```
-
-```{r}
-
-p4  <- plot_ss_result1(var_expt,
-                result_index = max_only_SBPB_diversity,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p4
-
-```
-
-```{r}
-p_overlay1 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
-                             var_expt[max_diversty_all,]$ss_res[[1]],
-                             xlims = c(-7, -1))
-p_overlay1
-```
-
-```{r}
-p_overlay2 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
-                             var_expt[max_only_CB_diversity,]$ss_res[[1]],
-                             xlims = c(-7, -1))
-p_overlay2
-
-#ss_result1 <- var_expt[no_diversity,]$ss_res[[1]]
-#ss_result2 <- var_expt[max_only_CB_diversity,]$ss_res[[1]]
-
-```
-
-```{r}
-p_overlay3 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
-                             var_expt[max_only_SBPB_diversity,]$ss_res[[1]],
-                             xlims = c(-7, -1))
-p_overlay3
-
-#ss_result3 <- var_expt[max_only_SBPB_diversity,]$ss_res[[1]]
-
-```
-
-```{r}
-tempp1 <- var_expt[no_diversity,]$ss_res[[1]] %>%
-  filter(initial_N_CB == 1e10,
-         log10(a_O) > -4.5, log10(a_O) < -4)
-tempp2 <- var_expt[max_only_SBPB_diversity,]$ss_res[[1]] %>%
-  filter(initial_N_CB == 1e10,
-         log10(a_O) > -4.5, log10(a_O) < -4)
-
-ggplot() +
-  geom_line(mapping = aes(x = log10(tempp1$a_O),
-                          y = log10(tempp1$O))) +
-  geom_line(mapping = aes(x = log10(tempp2$a_O),
-                          y = log10(tempp2$O)),
-            col = "blue")
-
-ggplot() +
-  geom_histogram(mapping = aes(x = log10(tempp1$O) - log10(tempp2$O)),
-            col = "blue")
-
-ggplot() +
-  geom_line(mapping = aes(x = log10(tempp1$a_O),
-    y = log10(tempp1$P) - log10(tempp2$P)),
-            col = "blue")
-
-```
-
-```{r}
-
-CB_vars <- unique(stab_data$CB_var_gmax_s)
-SB_vars <- unique(stab_data$SB_var_gmax_s)
-
-CB_stab_data <- stab_data %>%
-  filter(SB_var_gmax_s == 0) %>%
-  mutate(var_treat = "CB",
-         var_gmax = CB_var_gmax_s)
-
-SBPB_stab_data <- stab_data %>%
-  filter(CB_var_gmax_s == 0) %>%
-  mutate(var_treat = "SB-PB",
-         var_gmax = SB_var_gmax_s)
-
-for_join <- tibble(CB_var_gmax_s = CB_vars,
-                     SB_var_gmax_s = SB_vars)
-CBSBPB_stab_data <- stab_data %>%
-  right_join(for_join) %>%
-  mutate(var_treat = "CB-SB-PB",
-         var_gmax = CB_var_gmax_s)
-
-all_stab_results <- CB_stab_data %>%
-  bind_rows(SBPB_stab_data) %>%
-#  bind_rows(results3) %>%
- # bind_rows(results4) %>%
-  bind_rows(CBSBPB_stab_data)
-
-all_stab_results<- all_stab_results %>%
-    mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB-PB", "CB-SB-PB")))
-
-#saveRDS(all_stab_results, here("experiments/experiment summary/all_stab.RDS"))
-
-#all_stab_results <- readRDS(here("experiments/experiment summary/all_stab.RDS"))
-
-all_stab_results %>%
-  filter(Species == "O") %>%
-  ggplot(aes(x = var_gmax, y = hyst_range, col=var_treat, shape = as_factor(sim_length))) +
-  geom_point() +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
-  labs(col = "Variation in\nonly these\nfunctional groups")
-##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)
-
 all_stab_results %>%
@@
   ggplot(aes(x = var_gmax,
-             ymin = hyst_min,
-             ymax = hyst_max,
+             ymin = hyst_min_log,
+             ymax = hyst_max_log,
              fill=var_treat)) +
@@
 
+all_stab_results %>%
+  #filter(var_treat == "CB") %>%
+  filter(Species == "O",
+         sim_length == 8e4) %>%
+  ggplot(aes(x = var_gmax,
+             ymin = hyst_min_log,
+             ymax = hyst_max_log,
+             fill=var_treat)) +
+  geom_ribbon(alpha = 0.5) +
+  facet_wrap( ~ var_treat, nrow = 3) +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
+  labs(fill = "Variation in\nonly these\nfunctional groups") +
+  coord_flip() +
+  theme(
+    strip.background = element_blank(),
+    strip.text.x = element_blank()
+  )
+
+##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
+
+bind_rows(
+  readRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS")), 
+  readRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
+) %>%
+  filter(
+    Species == "O",
+    sim_length == 1e6
+  ) %>%
+  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range_log, col = hyst_range_log)) +
+  geom_point(size = 3)
+
+```
+
+## Extra SBPB diversity
+
+```{r}
+var_expt_x <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS"))
+stab_data_x <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
+
+p1  <- plot_ss_result1(var_expt_x,
+                result_index = 1,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p1
+
+p1  <- plot_ss_result1(var_expt_x,
+                result_index = 19,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p1
+
+p_overlay1 <- plot_ss_result2(var_expt_x[1,]$ss_res[[1]],
+                             var_expt_x[19,]$ss_res[[1]],
+                             xlims = c(-7, -1))
+p_overlay1
+```
+
+### raw
+```{r}
+stab_data_x %>%
+  filter(Species == "O") %>%
+  ggplot(aes(x = SB_var_gmax_s, y = hyst_range_raw)) +
+  geom_point() +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
+  labs(col = "Variation in\nonly these\nfunctional groups")
+##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)
+
+stab_data_x %>%
+  #filter(var_treat == "CB") %>%
+  filter(Species == "O") %>%
+  ggplot(aes(x = SB_var_gmax_s,
+             ymin = hyst_min_raw,
+             ymax = hyst_max_raw)) +
+  geom_ribbon(alpha = 0.5) +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
+  coord_flip() +
+  theme(
+    strip.background = element_blank(),
+    strip.text.x = element_blank()
+  )
+```
+
+### log
+```{r}
+stab_data_x %>%
+  filter(Species == "O") %>%
+  ggplot(aes(x = SB_var_gmax_s, y = hyst_range_log)) +
+  geom_point() +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
+  labs(col = "Variation in\nonly these\nfunctional groups")
+##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)
+
+stab_data_x %>%
+  #filter(var_treat == "CB") %>%
+  filter(Species == "O") %>%
+  ggplot(aes(x = SB_var_gmax_s,
+             ymin = hyst_min_log,
+             ymax = hyst_max_log)) +
+  geom_ribbon(alpha = 0.5) +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
+  coord_flip() +
+  theme(
+    strip.background = element_blank(),
+    strip.text.x = element_blank()
+  )
+```
+
+## 2x CB, 6xSBPB diversity
+
+```{r}
+## find various combinations of diversity
+var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS"))
+stab_data <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
+
+var_expt_levels <- var_expt[,1:6]
+
+no_diversity <- which(rowSums(abs(var_expt_levels))==0)
+max_diversty_all <- which(max(rowSums(abs(var_expt_levels))) ==
+                            rowSums(abs(var_expt_levels)))
+max_only_CB_diversity <- which(max(rowSums(abs(var_expt_levels[,1:2]))) ==
+                            rowSums(abs(var_expt_levels[,1:2])) &
+                              rowSums(abs(var_expt_levels[,3:6]))==0)
+#var_expt_levels[381,]
+
+max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
+                            rowSums(abs(var_expt_levels[,3:6])) &
+                              rowSums(abs(var_expt_levels[,1:2]))==0)
+#var_expt_levels[20,]
+
+```
+
+```{r}
+
+p1  <- plot_ss_result1(var_expt,
+                result_index = no_diversity,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p1
+
+#junk1 <- var_expt[no_diversity,]$ss_res[[1]]
+```
+
+```{r}
+
+p2  <- plot_ss_result1(var_expt,
+                result_index = max_diversty_all,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p2
+
+```
+
+```{r}
+
+p3  <- plot_ss_result1(var_expt,
+                result_index = max_only_CB_diversity,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p3
+
+```
+
+```{r}
+
+p4  <- plot_ss_result1(var_expt,
+                result_index = max_only_SBPB_diversity,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p4
+
+```
+
+```{r}
+p_overlay1 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
+                             var_expt[max_diversty_all,]$ss_res[[1]],
+                             xlims = c(-7, -1))
+p_overlay1
+```
+
+```{r}
+p_overlay2 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
+                             var_expt[max_only_CB_diversity,]$ss_res[[1]],
+                             xlims = c(-7, -1))
+p_overlay2
+
+#ss_result1 <- var_expt[no_diversity,]$ss_res[[1]]
+#ss_result2 <- var_expt[max_only_CB_diversity,]$ss_res[[1]]
+
+```
+
+```{r}
+p_overlay3 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
+                             var_expt[max_only_SBPB_diversity,]$ss_res[[1]],
+                             xlims = c(-7, -1))
+p_overlay3
+
+#ss_result3 <- var_expt[max_only_SBPB_diversity,]$ss_res[[1]]
+
+```
+
+```{r}
+tempp1 <- var_expt[no_diversity,]$ss_res[[1]] %>%
+  filter(initial_N_CB == 1e10,
+         log10(a_O) > -4.5, log10(a_O) < -4)
+tempp2 <- var_expt[max_only_SBPB_diversity,]$ss_res[[1]] %>%
+  filter(initial_N_CB == 1e10,
+         log10(a_O) > -4.5, log10(a_O) < -4)
+
+ggplot() +
+  geom_line(mapping = aes(x = log10(tempp1$a_O),
+                          y = log10(tempp1$O))) +
+  geom_line(mapping = aes(x = log10(tempp2$a_O),
+                          y = log10(tempp2$O)),
+            col = "blue")
+
+ggplot() +
+  geom_histogram(mapping = aes(x = log10(tempp1$O) - log10(tempp2$O)),
+            col = "blue")
+
+ggplot() +
+  geom_line(mapping = aes(x = log10(tempp1$a_O),
+    y = log10(tempp1$P) - log10(tempp2$P)),
+            col = "blue")
+
+```
+
+```{r}
+CB_vars <- unique(stab_data$CB_var_gmax_s)
+SB_vars <- unique(stab_data$SB_var_gmax_s)
+
+CB_stab_data <- stab_data %>%
+  filter(SB_var_gmax_s == 0) %>%
+  mutate(var_treat = "CB",
+         var_gmax = CB_var_gmax_s)
+
+SBPB_stab_data <- stab_data %>%
+  filter(CB_var_gmax_s == 0) %>%
+  mutate(var_treat = "SB-PB",
+         var_gmax = SB_var_gmax_s)
+
+for_join <- tibble(CB_var_gmax_s = CB_vars,
+                     SB_var_gmax_s = SB_vars)
+CBSBPB_stab_data <- stab_data %>%
+  right_join(for_join) %>%
+  mutate(var_treat = "CB-SB-PB",
+         var_gmax = CB_var_gmax_s)
+
+all_stab_results <- CB_stab_data %>%
+  bind_rows(SBPB_stab_data) %>%
+#  bind_rows(results3) %>%
+ # bind_rows(results4) %>%
+  bind_rows(CBSBPB_stab_data)
+
+all_stab_results<- all_stab_results %>%
+    mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB-PB", "CB-SB-PB")))
+
+#saveRDS(all_stab_results, here("experiments/experiment summary/all_stab.RDS"))
+
+#all_stab_results <- readRDS(here("experiments/experiment summary/all_stab.RDS"))
+```
+
+### raw
+```{r}
+all_stab_results %>%
+  filter(Species == "O") %>%
+  ggplot(aes(x = var_gmax, y = hyst_range_raw, col=var_treat, shape = as_factor(sim_length))) +
+  geom_point() +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
+  labs(col = "Variation in\nonly these\nfunctional groups")
+##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)
+
+all_stab_results %>%
+  #filter(var_treat == "CB") %>%
+  filter(Species == "O",
+         sim_length == 1e6) %>%
+  ggplot(aes(x = var_gmax,
+             ymin = hyst_min_raw,
+             ymax = hyst_max_raw,
+             fill=var_treat)) +
+  geom_ribbon(alpha = 0.5) +
+  facet_wrap( ~ var_treat, nrow = 3) +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
+  labs(fill = "Variation in\nonly these\nfunctional groups") +
+  coord_flip() +
+  theme(
+    strip.background = element_blank(),
+    strip.text.x = element_blank()
+  )
+
 ##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
@@
          sim_length == 1e6) %>%
-  ggplot(aes(x = CB_var_gmax_s, y = hyst_range, col = as.factor(SB_var_gmax_s))) +
+  ggplot(aes(x = CB_var_gmax_s, y = hyst_range_raw, col = as.factor(SB_var_gmax_s))) +
   geom_line(size = 2)
-
+```
+
+### log
+```{r}
+all_stab_results %>%
+  filter(Species == "O") %>%
+  ggplot(aes(x = var_gmax, y = hyst_range_log, col=var_treat, shape = as_factor(sim_length))) +
+  geom_point() +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
+  labs(col = "Variation in\nonly these\nfunctional groups")
+##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)
+
+all_stab_results %>%
+  #filter(var_treat == "CB") %>%
+  filter(Species == "O",
+         sim_length == 1e6) %>%
+  ggplot(aes(x = var_gmax,
+             ymin = hyst_min_log,
+             ymax = hyst_max_log,
+             fill=var_treat)) +
+  geom_ribbon(alpha = 0.5) +
+  facet_wrap( ~ var_treat, nrow = 3) +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
+  labs(fill = "Variation in\nonly these\nfunctional groups") +
+  coord_flip() +
+  theme(
+    strip.background = element_blank(),
+    strip.text.x = element_blank()
+  )
+
+##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
+stab_data %>%
+  filter(Species == "O",
+         sim_length == 1e6) %>%
+  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range_log, col = hyst_range_log)) +
+  geom_point(size = 3)
+
+##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
+
+stab_data %>%
+  filter(Species == "O",
+         sim_length == 1e6) %>%
+  ggplot(aes(x = CB_var_gmax_s, y = hyst_range_log, col = as.factor(SB_var_gmax_s))) +
+  geom_line(size = 2)
 ```
@@
 p1_long
-
 ```
@@
 The most tolerant strain does at first grow, but is then outcompeted by less tolerant strains as the environment ameliorates (temporally).
+
+TODO CHECK THE PARAMETER
 
@@
 ```{r eval = eval_dynamics_flag}
-default_sim_duration <- 100000
+parameter <- readRDS(here("experiments/experiment 1/data/sim_res_novar3.RDS"))
+parameter$sim_duration <- 100000
+parameter$result <- NULL
 ```
@@
 ```{r eval = eval_dynamics_flag}
-default_log10a_series <- c(-4.8, -4.8)
-initial_state <- new_initial_state(num_CB_strains,
-                                   num_PB_strains,
-                                   num_SB_strains,
-                                   values = "bush_ssfig3")
-initial_state[grep("CB_", names(initial_state))] <- 10^10/num_CB_strains
-sim_res_novar1 <- run_simulation(parameter_values = var_expt$pars[[no_diversity]],
-                          initial_state = initial_state)
+parameter$log10a_series <- c(-4.8, -4.8)
+parameter$strain_parameter$initial_state <- new_initial_state(
+  nrow(parameter$strain_parameter$CB),
+  nrow(parameter$strain_parameter$PB),
+  nrow(parameter$strain_parameter$PB),
+  values = "bush_ssfig3"
+)
+parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/nrow(parameter$strain_parameter$CB)
+
+sim_res_novar1 <- run_simulation(parameter)
 saveRDS(sim_res_novar1, here("experiments/experiment 1/data/puzzle1_1.RDS"))

### 2021-11-11 experiments/experiment 1/experiment-1.Rmd
Comparison with main branch

@@
 
-knitr::opts_knit$set(progress = TRUE, verbose = FALSE, cache = TRUE)
+knitr::opts_knit$set(
+  progress = TRUE, 
+  verbose = FALSE, 
+  cache = TRUE
+)
 
@@
 options(mc.cores = 7)
-eval_dynamics_flag <- TRUE
+eval_dynamics_flag <- FALSE
 ```
@@
 
-### Maximum diversity
+### Medium diversity
 
 ```{r eval = eval_dynamics_flag}
+try_me <- 311
 sim_number2 <- num_div_treatment_levels
-parameter$strain_parameter <- var_expt$pars[[max_diversty_all]]
+parameter$strain_parameter <- var_expt$pars[[try_me]]
 parameter$strain_parameter$initial_state <- sim_res_novar3$strain_parameter$initial_state
@@
 
-```{r eval = FALSE}
+```{r eval = FALSE, echo = FALSE}
 visualise_temporal_env_eco(sim_res_novar3, sim_res_highvar3)
@@
 rm(minimum_abundances, grid_num_a, a_Os, grid_num_N, initial_CBs, initial_PBs, initial_SBs, ss_expt)
-saveRDS(parameter, here("experiments/experiment 1/data/TEST_parameter.RDS"))
-saveRDS(var_expt, here("experiments/experiment 1/data/TEST_var_expt.RDS"))
+saveRDS(parameter, here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS"))
+saveRDS(var_expt, here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial.RDS"))
 ```
@@
 ```{r run_experiment, eval = eval_dynamics_flag}
-parameter <- readRDS(here("experiments/experiment 1/data/TEST_parameter.RDS"))
-var_expt <- readRDS(here("experiments/experiment 1/data/TEST_var_expt.RDS"))
-
-var_expt_res <- run_ss_var_experiment(parameter, var_expt)
-
-saveRDS(var_expt, here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS"))
+run_ss_var_experiment(
+  parameter = readRDS(here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS")), 
+  var_expt = readRDS(here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial.RDS"))) %>%
+saveRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS"))
 ```
@@
 ## sim length 80'000, 20 x 20 factorial, reference maximum diversity
-readRDS(here("experiments/experiment 1/data/ss_data_80000.RDS")) %>%
-  mutate(sim_length = 80000) %>% 
-  multidplyr::partition(cluster) %>%
-  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
-  collect() %>%
-  unnest(cols = c(stability_measures)) %>%
-  saveRDS(here("experiments/experiment 1/data/stab_data_80000.RDS"))
+# readRDS(here("experiments/experiment 1/data/ss_data_80000.RDS")) %>%
+#   mutate(sim_length = 80000) %>% 
+#   multidplyr::partition(cluster) %>%
+#   mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
+#   collect() %>%
+#   unnest(cols = c(stability_measures)) %>%
+#   saveRDS(here("experiments/experiment 1/data/stab_data_80000.RDS"))
 
 ## sim length 1'000'000, 20 x 20 factorial, reference maximum diversity
-# var_expt2 <- readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS")) %>%
-#   mutate(sim_length = 1000000)
-# # stab_data2 <- var_expt2 %>%
-# #   group_by(CB_var_gmax_s, CB_var_h_s,
-# #            SB_var_gmax_s, SB_var_h_s,
-# #            PB_var_gmax_s, PB_var_h_s, sim_length) %>%
-# #   do(stability_measures = get_stability_measures(.$ss_res[[1]]))
-# stab_data2 <- var_expt2 %>%
-#   mutate(stability_measures = list(get_stability_measures(ss_res)))
-# stab_data2 <- unnest(stab_data2, cols = c(stability_measures))
-# saveRDS(stab_data2, here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS"))
-readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS")) %>%
-  mutate(sim_length = 1000000) %>% 
-  multidplyr::partition(cluster) %>%
-  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
-  collect() %>%
-  unnest(cols = c(stability_measures)) %>%
-  saveRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS"))
+# readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS")) %>%
+#   mutate(sim_length = 1000000) %>% 
+#   multidplyr::partition(cluster) %>%
+#   mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
+#   collect() %>%
+#   unnest(cols = c(stability_measures)) %>%
+#   saveRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS"))
 
 ## sim length 1'000'000, 20 SBPBgrad, 5x maximum diversity
-# var_expt3 <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS")) %>%
-#   mutate(sim_length = 1000000)
-# stab_data3 <- var_expt3 %>%
-#   group_by(CB_var_gmax_s, CB_var_h_s,
-#            SB_var_gmax_s, SB_var_h_s,
-#            PB_var_gmax_s, PB_var_h_s, sim_length) %>%
-#   do(stability_measures = get_stability_measures(.$ss_res[[1]]))
-# stab_data3 <- unnest(stab_data3, cols = c(stability_measures))
-# saveRDS(stab_data3, here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
-readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS")) %>%
-  mutate(sim_length = 1000000) %>% 
-  multidplyr::partition(cluster) %>%
-  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
-  collect() %>%
-  unnest(cols = c(stability_measures)) %>%
-  saveRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
+# readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS")) %>%
+#   mutate(sim_length = 1000000) %>% 
+#   multidplyr::partition(cluster) %>%
+#   mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
+#   collect() %>%
+#   unnest(cols = c(stability_measures)) %>%
+#   saveRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
 
 ## sim length 300'000, 20 SBPBgrad, reference maximum diversity
-# var_expt4 <- readRDS(here("experiments/experiment 1/data/ss_data_300000_small.RDS")) %>%
-#   mutate(sim_length = 300000)
-# stab_data4 <- var_expt4 %>%
-#   group_by(CB_var_gmax_s, CB_var_h_s,
-#            SB_var_gmax_s, SB_var_h_s,
-#            PB_var_gmax_s, PB_var_h_s, sim_length) %>%
-#   do(stability_measures = get_stability_measures(.$ss_res[[1]]))
-# stab_data4 <- unnest(stab_data4, cols = c(stability_measures))
-# saveRDS(stab_data4, here("experiments/experiment 1/data/stab_data_300000.RDS"))
-readRDS(here("experiments/experiment 1/data/ss_data_300000_small.RDS")) %>%
-  mutate(sim_length = 300000) %>% 
-  multidplyr::partition(cluster) %>%
-  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
-  collect() %>%
-  unnest(cols = c(stability_measures)) %>%
-  saveRDS(here("experiments/experiment 1/data/stab_data_300000.RDS"))
+# readRDS(here("experiments/experiment 1/data/ss_data_300000_small.RDS")) %>%
+#   mutate(sim_length = 300000) %>% 
+#   multidplyr::partition(cluster) %>%
+#   mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
+#   collect() %>%
+#   unnest(cols = c(stability_measures)) %>%
+#   saveRDS(here("experiments/experiment 1/data/stab_data_300000.RDS"))
 
 ## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
-# var_expt5 <- readRDS(here("experiments/experiment 1/data/stab_data_300000.RDS")) %>%
-#   mutate(sim_length = 1000000)
-# stab_data5 <- var_expt5 %>%
-#   group_by(CB_var_gmax_s, CB_var_h_s,
-#            SB_var_gmax_s, SB_var_h_s,
-#            PB_var_gmax_s, PB_var_h_s, sim_length) %>%
-#   do(stability_measures = get_stability_measures(.$ss_res[[1]]))
-# stab_data5 <- unnest(stab_data5, cols = c(stability_measures))
-# saveRDS(stab_data5, here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
-x <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS")) %>%
+readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS")) %>%
   mutate(sim_length = 1000000) %>% 
@@
 ## SS, no diversity, all diversity, CB only, and SBPB only
-
-```{r}
+No Experimental data
+
+```{r, eval = FALSE, echo = FALSE}
 ## find various combinations of diversity
@@
 
-```{r}
+```{r, eval = FALSE, echo = FALSE}
 
@@
 
-```{r}
+```{r, eval = FALSE, echo = FALSE}
 p_overlay1 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
@@
 
-```{r}
+```{r, eval = FALSE, echo = FALSE}
 p_overlay2 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
@@
 
-```{r}
+```{r, eval = FALSE, echo = FALSE}
 p_overlay3 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
@@
 ## Look at stability measures
+No experimental data.
 
 ### Calculations
-```{r}
+```{r, eval = FALSE, echo = FALSE}
 stab_data <- bind_rows(
@@
 ### Plot raw
-```{r}
+```{r, eval = FALSE, echo = FALSE}
 
@@
 ### Plot log
-```{r}
+```{r, eval = FALSE, echo = FALSE}
 
@@
 ## Extra SBPB diversity
-
-```{r}
+No experimental data.
+
+```{r, eval = FALSE, echo = FALSE}
 var_expt_x <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS"))
@@
 ### raw
-```{r}
+```{r, eval = FALSE, echo = FALSE}
 stab_data_x %>%
@@
 ### log
-```{r}
+```{r, eval = FALSE, echo = FALSE}
 stab_data_x %>%
@@
 
-all_stab_results<- all_stab_results %>%
+all_stab_results <- all_stab_results %>%
     mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB-PB", "CB-SB-PB")))
@@
 ## What effect of changing the length of the simulations
-
-```{r}
+No Experimental data.
+
+```{r, eval = FALSE, echo = FALSE}
 var_expt1 <- readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS"))
@@
 
+# FROM HERE NOT CHANGED TO NEW FORMAT!!!!!!
 # Some puzzles
@@
 
-```{r}
+```{r, eval = FALSE, echo = FALSE}
 sim_res_novar1 <- readRDS(here("experiments/experiment 1/data/puzzle1_1.RDS"))
@@
 
-```{r eval = eval_dynamics_flag}
+```{r eval = FALSE, echo = FALSE}
 sim_res_novar1 <- run_simulation(parameter_values = var_expt$pars[[max_only_SBPB_diversity]],
@@
 
-```{r}
+```{r, eval = FALSE, echo = FALSE}
 sim_res_novar1 <- readRDS(here("experiments/experiment 1/data/puzzle1_2.RDS"))
@@
 
-```{r eval = FALSE}
+```{r eval = FALSE, echo = FALSE}
 a_Os <- 10^seq(-2.479, -2.4785, length=grid_num_a) ## sequence of a_0 values
@@
 
-```{r}
+```{r, eval = FALSE, echo = FALSE}
 #var_expt <- run_ss_var_experiment()
@@
 
-```{r}
+```{r, eval = FALSE, echo = FALSE}
 library(here)
@@
 
-```{r eval = FALSE}
+```{r eval = FALSE, echo = FALSE}
 var_expt$pars[[1]]
@@
 
-```{r echo = FALSE}
+```{r echo = FALSE, eval = FALSE}
 num_CB_strains <- 9
@@
 
-With the CB diversity multiplier set at `r CB_var_multiplier` and the SB/PB multiplier set at `r SBPB_var_multiplier` the range of realised growth rates of CB is `r CB_gr_range`, range of SB is `r SB_gr_range`, and range of PB is `r PB_gr_range`.
+<!-- With the CB diversity multiplier set at ` CB_var_multiplier` and the SB/PB multiplier set at ` SBPB_var_multiplier` the range of realised growth rates of CB is ` CB_gr_range`, range of SB is ` SB_gr_range`, and range of PB is ` PB_gr_range`.
+-->

### 2021-11-11 experiments/experiment 1/experiment-1.Rmd
Update experiment-1.Rmd

@@
 
-## num_div_treatment_levels <- 20
-
-num_div_treatment_levels <- 3 ## FOR TEST
+num_div_treatment_levels <- 20
+
+## num_div_treatment_levels <- 3 ## FOR TEST
 
@@
 display_diversity(
-  9, ## FOR TEST was 400
+  400,
   var_expt = var_expt,
@@
 
-### Maximum diversity
+### With diversity
 
@@
 # sim_number <- num_div_treatment_levels
-
-parameter$strain_parameter <- var_expt$pars[[max_diversty_all]]
+try_me <- 311
+#sim_number2 <- num_div_treatment_levels
+parameter$strain_parameter <- var_expt$pars[[try_me]]
+#parameter$strain_parameter <- var_expt$pars[[max_diversty_all]]
 parameter$strain_parameter$initial_state <- sim_res_novar1$strain_parameter$initial_state
@@
 
-### Maximum diversity
+### With diversity
 
 ```{r eval = eval_dynamics_flag}
-sim_number <- num_div_treatment_levels
-parameter$strain_parameter <- var_expt$pars[[max_diversty_all]]
+#sim_number <- num_div_treatment_levels
+try_me <- 311
+#sim_number2 <- num_div_treatment_levels
+parameter$strain_parameter <- var_expt$pars[[try_me]]
+#parameter$strain_parameter <- var_expt$pars[[max_diversty_all]]
 parameter$strain_parameter$initial_state <- sim_res_novar2$strain_parameter$initial_state
@@
 
-### Medium diversity
+### With diversity
 
@@
 try_me <- 311
-sim_number2 <- num_div_treatment_levels
+#sim_number2 <- num_div_treatment_levels
 parameter$strain_parameter <- var_expt$pars[[try_me]]

### 2021-11-12 experiments/experiment 1/experiment-1.Rmd
Use of microxanox 0.3.0 release

@@
 
-microxanox_release <- "0.2.3_beta"
+microxanox_release <- "0.3.0"
 
@@
 
-library(microxanoxBeta)
-if (packageVersion("microxanoxBeta") < package_version("0.2.3")) {
+library(microxanox)
+if (packageVersion("microxanox") < package_version("0.3.0")) {
   stop("microxanox version needs to be at least 0.2.3!")
@@
 cluster <- multidplyr::new_cluster(7)
-multidplyr::cluster_library(cluster, c("microxanoxBeta", "dplyr"))
+multidplyr::cluster_library(cluster, c("microxanox", "dplyr"))
 

### 2021-11-12 experiments/experiment old/experiment 2.Rmd

--- 2021-06-25 experiments/experiment template/experiment template.Rmd
@@
 ---
-title: "Experiment 1"
+title: "Experiment 2"
 author: "Owen Petchey"
 date: "6/25/2021"
-output: html_document
+output:
+  html_document:
+    keep_md: yes
 ---
@@
 ```{r}
-
-CBtraits <- var_expt$pars[[num_div_treatment_levels]]$CB
-P <- 1 #10^seq(-5, 5, 0.1)
-SR <- 10^seq(0, 3, 0.1)
-gr_rateCB1 <- growth1(P, CBtraits$g_max_CB[1], CBtraits$k_CB_P[1]) * inhibition(SR, CBtraits$h_SR_CB[1])
-gr_rateCB9 <- growth1(P, CBtraits$g_max_CB[num_CB_strains], CBtraits$k_CB_P[num_CB_strains]) * inhibition(SR, CBtraits$h_SR_CB[num_CB_strains])
-
-CB_TO1 <- ggplot() +
-  geom_point(aes(x = CBtraits$h_SR_CB, y = CBtraits$g_max_CB))
-CB_TO2 <- ggplot() +
-  geom_line(aes( x = log10(SR), y = gr_rateCB1)) +
-  geom_line(aes( x = log10(SR), y = gr_rateCB9), col = "blue")
-
-SBtraits <- var_expt$pars[[num_div_treatment_levels]]$SB
-P <- 1 #10^seq(-5, 5, 0.1)
-SO <- 1
-O <- 10^seq(-2.5, 2.5, 0.1)
-gr_rateSB1 <- growth2(P, SO, SBtraits$g_max_SB[1], SBtraits$k_SB_P[1], SBtraits$k_SB_SO[1]) *
-  inhibition(O, SBtraits$h_O_SB[1])
-gr_rateSB9 <- growth2(P, SO, SBtraits$g_max_SB[9], SBtraits$k_SB_P[9], SBtraits$k_SB_SO[9]) *
-  inhibition(O, SBtraits$h_O_SB[9])
-
-SB_TO1 <- ggplot() +
-  geom_point(aes(x = SBtraits$h_O_SB, y = SBtraits$g_max_SB))
-SB_TO2 <- ggplot() +
-  geom_line(aes( x = log10(O), y = gr_rateSB1)) +
-  geom_line(aes( x = log10(O), y = gr_rateSB9), col = "blue")
-
-PBtraits <- var_expt$pars[[num_div_treatment_levels]]$PB
-P <- 1 #10^seq(-5, 5, 0.1)
-SO <- 1
-O <- 10^seq(-2.5, 2.5, 0.1)
-gr_ratePB1 <- growth2(P, SO, PBtraits$g_max_PB[1], PBtraits$k_PB_P[1], PBtraits$k_PB_SR[1]) *
-  inhibition(O, PBtraits$h_O_PB[1])
-gr_ratePB9 <- growth2(P, SO, PBtraits$g_max_PB[9], PBtraits$k_PB_P[9], PBtraits$k_PB_SR[9]) *
-  inhibition(O, PBtraits$h_O_PB[9])
-
-PB_TO1 <- ggplot() +
-  geom_point(aes(x = PBtraits$h_O_PB, y = PBtraits$g_max_PB))
-PB_TO2 <- ggplot() +
-  geom_line(aes( x = log10(O), y = gr_ratePB1)) +
-  geom_line(aes( x = log10(O), y = gr_ratePB9), col = "blue")
-
-(CB_TO1 + SB_TO1 + PB_TO1) / (CB_TO2 + SB_TO2 + PB_TO2)
+display_diversity(
+  var_expt = var_expt,
+  num_CB_strains = num_CB_strains,
+  num_SB_strains = num_SB_strains,
+  num_PB_strains = num_PB_strains
+)
 ```
@@
 ```{r}
-default_minimum_abundances <- rep(1000, 3)
+default_minimum_abundances <- rep(100, 3)
 names(default_minimum_abundances) <- c("CB", "PB", "SB")

### 2021-11-12 experiments/experiment 1/experiment-1.Rmd
Test of experiment and change to microxanox 0.3.0 minimum version

@@
 if (packageVersion("microxanox") < package_version("0.3.0")) {
-  stop("microxanox version needs to be at least 0.2.3!")
+  stop("microxanox version needs to be at least 0.3.0!")
 }

### 2021-11-12 experiments/experiment 1/experiment-1.Rmd
with testing of new version

@@
 
-# default_dynamic_model <- bushplus_dynamic_model
-# default_event_definition <- event_definition_1
-# default_event_interval <- 100
-# default_noise_sigma <- 0
-# default_minimum_abundances <- rep(1, 3)
-# names(default_minimum_abundances) <- c("CB", "PB", "SB")
-# default_sim_duration <- 80000
-# default_sim_sample_interval <- 100
-# initial_pars_from <- "bush_ssfig3"
-## note that next line (log10a_series is over-ridden with getting stable states)
-#default_log10a_series <- c(-2, -2, -2, -2, -10, -10, -10, -10, -10)
-
 num_CB_strains <- 9
@@
 sp <- new_strain_parameter(
-  n_CB = 9,
-  n_PB = 9,
-  n_SB = 9,
-
+  n_CB = num_CB_strains,
+  n_PB = num_SB_strains,
+  n_SB = num_PB_strains,
   values_initial_state = "bush_ssfig3"
@@
 
-## num_div_treatment_levels <- 3 ## FOR TEST
-
 ```
@@
 ```{r}
+## Here we get some rows of var_expt that correspond with particular diversity levels
+
 var_expt_levels <- var_expt[, 1:6]
@@
 #var_expt_levels[20,]
+
+medium_diverity_varexp_row <- 311
+
 ```
@@
 ```{r eval = eval_dynamics_flag}
-# default_sim_duration <- 80000
 parameter$sim_duration <- 80000
@@
 ```{r eval = eval_dynamics_flag}
-# default_log10a_series <- c(-1, -7, -7)
 parameter$log10a_series <- c(-1, -7, -7)
@@
 ```{r eval = eval_dynamics_flag}
-# Is this actually needed?
-# sim_number <- num_div_treatment_levels
-try_me <- 311
-#sim_number2 <- num_div_treatment_levels
-parameter$strain_parameter <- var_expt$pars[[try_me]]
-#parameter$strain_parameter <- var_expt$pars[[max_diversty_all]]
+parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
 parameter$strain_parameter$initial_state <- sim_res_novar1$strain_parameter$initial_state
@@
 ```{r eval = eval_dynamics_flag}
-# sim_number <- 1
 parameter$log10a_series <- c(-5, -3, -1, -1)
@@
 ```{r eval = eval_dynamics_flag}
-#sim_number <- num_div_treatment_levels
-try_me <- 311
-#sim_number2 <- num_div_treatment_levels
-parameter$strain_parameter <- var_expt$pars[[try_me]]
-#parameter$strain_parameter <- var_expt$pars[[max_diversty_all]]
+parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
 parameter$strain_parameter$initial_state <- sim_res_novar2$strain_parameter$initial_state
@@
 ```{r eval = eval_dynamics_flag}
-# sim_number1 <- 1
 parameter$log10a_series <- c(-1, -8, -1)
@@
 ```{r eval = eval_dynamics_flag}
-try_me <- 311
-#sim_number2 <- num_div_treatment_levels
-parameter$strain_parameter <- var_expt$pars[[try_me]]
+parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
 parameter$strain_parameter$initial_state <- sim_res_novar3$strain_parameter$initial_state
@@
 
-### Visualise
+### Ecosystem-environment relationship
 
@@
 ```{r}
-# default_sim_duration <- 1000000
-# ssfind_minimum_abundances <- rep(0, 3)
-# names(ssfind_minimum_abundances) <- c("CB", "PB", "SB")
-# sfind_simulation_duration <- default_sim_duration
-# ssfind_simulation_sampling_interval <- ssfind_simulation_duration
-# ssfind_event_interval <- ssfind_simulation_duration
-
 minimum_abundances <- rep(0, 3)
@@
 
-## grid_num_a <- 1000 #usually 1000 ## number of a_0 values
-grid_num_a <- 100 ## FOR TEST
-
+grid_num_a <- 1000 #usually 1000 ## number of a_0 values
+#grid_num_a <- 10 ## FOR TEST
 a_Os <- 10^seq(-7, -0.5, length=grid_num_a) ## sequence of a_0 values
@@
 rm(minimum_abundances, grid_num_a, a_Os, grid_num_N, initial_CBs, initial_PBs, initial_SBs, ss_expt)
+
 saveRDS(parameter, here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS"))
-saveRDS(var_expt, here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial.RDS"))
+saveRDS(var_expt_small, here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial.RDS"))
+```
+
+### for testing
+
+```{r eval = FALSE}
+var_expt_small <- var_expt[c(no_diversity, medium_diverity_varexp_row),]
+saveRDS(parameter, here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS"))
+saveRDS(var_expt_small, here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial_small.RDS"))
+run_ss_var_experiment(
+  parameter = readRDS(here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS")), 
+  var_expt = readRDS(here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial_small.RDS"))) %>%
+saveRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_small.RDS"))
 ```
@@
 
-## sim length 80'000, 20 x 20 factorial, reference maximum diversity
-# readRDS(here("experiments/experiment 1/data/ss_data_80000.RDS")) %>%
-#   mutate(sim_length = 80000) %>% 
-#   multidplyr::partition(cluster) %>%
-#   mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
-#   collect() %>%
-#   unnest(cols = c(stability_measures)) %>%
-#   saveRDS(here("experiments/experiment 1/data/stab_data_80000.RDS"))
-
-## sim length 1'000'000, 20 x 20 factorial, reference maximum diversity
-# readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS")) %>%
-#   mutate(sim_length = 1000000) %>% 
-#   multidplyr::partition(cluster) %>%
-#   mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
-#   collect() %>%
-#   unnest(cols = c(stability_measures)) %>%
-#   saveRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS"))
-
-## sim length 1'000'000, 20 SBPBgrad, 5x maximum diversity
-# readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS")) %>%
-#   mutate(sim_length = 1000000) %>% 
-#   multidplyr::partition(cluster) %>%
-#   mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
-#   collect() %>%
-#   unnest(cols = c(stability_measures)) %>%
-#   saveRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
-
-## sim length 300'000, 20 SBPBgrad, reference maximum diversity
-# readRDS(here("experiments/experiment 1/data/ss_data_300000_small.RDS")) %>%
-#   mutate(sim_length = 300000) %>% 
-#   multidplyr::partition(cluster) %>%
-#   mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
-#   collect() %>%
-#   unnest(cols = c(stability_measures)) %>%
-#   saveRDS(here("experiments/experiment 1/data/stab_data_300000.RDS"))
-
 ## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
-readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS")) %>%
+readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_small.RDS")) %>%
   mutate(sim_length = 1000000) %>% 
@@
   unnest(cols = c(stability_measures)) %>%
-  saveRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
-```
-
-## SS, no diversity, all diversity, CB only, and SBPB only
-No Experimental data
-
-```{r, eval = FALSE, echo = FALSE}
+  saveRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial_small.RDS"))
+```
+
+```{r eval = FALSE}
+## compare version 1 results to the current.
+v1_ss_data <- readRDS(here("experiments/experiment 1/data/version1_ss_data_1e6_x2x6_factorial.RDS"))
+v1_stab_data <- readRDS(here("experiments/experiment 1/data/version1_stab_data_1e6_x2x6_factorial.RDS"))
+
+small_ss_data <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_small.RDS"))
+small_stab_data <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial_small.RDS"))
+
+xxxxx <- small_stab_data %>%
+  select(-data, -pars, -ss_by_a_N_result, -ss_res, -sim_length) %>%
+  filter(Species == "O")
+v1_stab_data %>%
+  filter(CB_var_gmax_s == 0, CB_var_h_s == 0,
+         SB_var_gmax_s == 0, SB_var_h_s == 0,
+         PB_var_gmax_s == 0, PB_var_h_s == 0) %>%
+  filter(Species == "O")
+v1_stab_data %>%
+  slice(9620) %>%
+  filter(Species == "O")
+```
+
+```{r}
 ## find various combinations of diversity
-var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS"))
+var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS"))
+stab_data <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
 
@@
 
-```
-
-```{r, eval = FALSE, echo = FALSE}
+medium_diverity_varexp_row <- 311
+
+```
+
+### Display results
+
+```{r}
 
@@
 
-```{r, eval = FALSE, echo = FALSE}
+```{r}
 
@@
 
-```{r, eval = FALSE, echo = FALSE}
+```{r}
 p_overlay1 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
@@
 
-```{r, eval = FALSE, echo = FALSE}
+```{r}
 p_overlay2 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
@@
 
-```{r, eval = FALSE, echo = FALSE}
+```{r}
 p_overlay3 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
@@
 
-## Look at stability measures
-No experimental data.
-
-### Calculations
-```{r, eval = FALSE, echo = FALSE}
-stab_data <- bind_rows(
-  readRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS")), 
-  readRDS(here("experiments/experiment 1/data/stab_data_80000.RDS"))
-)
-
+```{r}
+tempp1 <- var_expt[no_diversity,]$ss_res[[1]] %>%
+  filter(initial_N_CB == 1e10,
+         log10(a_O) > -4.5, log10(a_O) < -4)
+tempp2 <- var_expt[max_only_SBPB_diversity,]$ss_res[[1]] %>%
+  filter(initial_N_CB == 1e10,
+         log10(a_O) > -4.5, log10(a_O) < -4)
+
+ggplot() +
+  geom_line(mapping = aes(x = log10(tempp1$a_O),
+                          y = log10(tempp1$O))) +
+  geom_line(mapping = aes(x = log10(tempp2$a_O),
+                          y = log10(tempp2$O)),
+            col = "blue")
+
+ggplot() +
+  geom_histogram(mapping = aes(x = log10(tempp1$O) - log10(tempp2$O)),
+            col = "blue")
+
+ggplot() +
+  geom_line(mapping = aes(x = log10(tempp1$a_O),
+    y = log10(tempp1$P) - log10(tempp2$P)),
+            col = "blue")
+
+```
+
+```{r}
 CB_vars <- unique(stab_data$CB_var_gmax_s)
-SB_vars <- unique(stab_data$CB_var_gmax_s)
+SB_vars <- unique(stab_data$SB_var_gmax_s)
 
@@
 
-saveRDS(all_stab_results, here("experiments/experiment 1/data/all_stab.RDS"))
-```
-
-### Plot raw
-```{r, eval = FALSE, echo = FALSE}
-
-all_stab_results <- readRDS(here("experiments/experiment summary/all_stab.RDS"))
-
+#saveRDS(all_stab_results, here("experiments/experiment summary/all_stab.RDS"))
+
+#all_stab_results <- readRDS(here("experiments/experiment summary/all_stab.RDS"))
+```
+
+### Raw
+```{r}
 all_stab_results %>%
@@
 
-all_stab_results %>%
-  #filter(var_treat == "CB") %>%
+##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
+stab_data %>%
   filter(Species == "O",
-         sim_length == 8e4) %>%
-  ggplot(aes(x = var_gmax,
-             ymin = hyst_min_raw,
-             ymax = hyst_max_raw,
-             fill=var_treat)) +
-  geom_ribbon(alpha = 0.5) +
-  facet_wrap( ~ var_treat, nrow = 3) +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
-  labs(fill = "Variation in\nonly these\nfunctional groups") +
-  coord_flip() +
-  theme(
-    strip.background = element_blank(),
-    strip.text.x = element_blank()
-  )
-
-##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
-
-bind_rows(
-  readRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS")), 
-  readRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
-) %>%
-  filter(
-    Species == "O",
-    sim_length == 1e6
-  ) %>%
+         sim_length == 1e6) %>%
   ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range_raw, col = hyst_range_raw)) +
@@
 
-```
-
-### Plot log
-```{r, eval = FALSE, echo = FALSE}
-
-all_stab_results <- readRDS(here("experiments/experiment summary/all_stab.RDS"))
-
+##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
+
+stab_data %>%
+  filter(Species == "O",
+         sim_length == 1e6) %>%
+  ggplot(aes(x = CB_var_gmax_s, y = hyst_range_raw, col = as.factor(SB_var_gmax_s))) +
+  geom_line(size = 2)
+```
+
+### Log transformed
+
+```{r}
 all_stab_results %>%
@@
 
-all_stab_results %>%
-  #filter(var_treat == "CB") %>%
-  filter(Species == "O",
-         sim_length == 8e4) %>%
-  ggplot(aes(x = var_gmax,
-             ymin = hyst_min_log,
-             ymax = hyst_max_log,
-             fill=var_treat)) +
-  geom_ribbon(alpha = 0.5) +
-  facet_wrap( ~ var_treat, nrow = 3) +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
-  labs(fill = "Variation in\nonly these\nfunctional groups") +
-  coord_flip() +
-  theme(
-    strip.background = element_blank(),
-    strip.text.x = element_blank()
-  )
-
-##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
-
-bind_rows(
-  readRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS")), 
-  readRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
-) %>%
-  filter(
-    Species == "O",
-    sim_length == 1e6
-  ) %>%
-  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range_log, col = hyst_range_log)) +
-  geom_point(size = 3)
-
-```
-
-## Extra SBPB diversity
-No experimental data.
-
-```{r, eval = FALSE, echo = FALSE}
-var_expt_x <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS"))
-stab_data_x <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
-
-p1  <- plot_ss_result1(var_expt_x,
-                result_index = 1,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p1
-
-p1  <- plot_ss_result1(var_expt_x,
-                result_index = 19,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p1
-
-p_overlay1 <- plot_ss_result2(var_expt_x[1,]$ss_res[[1]],
-                             var_expt_x[19,]$ss_res[[1]],
-                             xlims = c(-7, -1))
-p_overlay1
-```
-
-### raw
-```{r, eval = FALSE, echo = FALSE}
-stab_data_x %>%
-  filter(Species == "O") %>%
-  ggplot(aes(x = SB_var_gmax_s, y = hyst_range_raw)) +
-  geom_point() +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
-  labs(col = "Variation in\nonly these\nfunctional groups")
-##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)
-
-stab_data_x %>%
-  #filter(var_treat == "CB") %>%
-  filter(Species == "O") %>%
-  ggplot(aes(x = SB_var_gmax_s,
-             ymin = hyst_min_raw,
-             ymax = hyst_max_raw)) +
-  geom_ribbon(alpha = 0.5) +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
-  coord_flip() +
-  theme(
-    strip.background = element_blank(),
-    strip.text.x = element_blank()
-  )
-```
-
-### log
-```{r, eval = FALSE, echo = FALSE}
-stab_data_x %>%
-  filter(Species == "O") %>%
-  ggplot(aes(x = SB_var_gmax_s, y = hyst_range_log)) +
-  geom_point() +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
-  labs(col = "Variation in\nonly these\nfunctional groups")
-##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)
-
-stab_data_x %>%
-  #filter(var_treat == "CB") %>%
-  filter(Species == "O") %>%
-  ggplot(aes(x = SB_var_gmax_s,
-             ymin = hyst_min_log,
-             ymax = hyst_max_log)) +
-  geom_ribbon(alpha = 0.5) +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
-  coord_flip() +
-  theme(
-    strip.background = element_blank(),
-    strip.text.x = element_blank()
-  )
-```
-
-## 2x CB, 6xSBPB diversity
-
-```{r}
-## find various combinations of diversity
-var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS"))
-stab_data <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
-
-var_expt_levels <- var_expt[,1:6]
-
-no_diversity <- which(rowSums(abs(var_expt_levels))==0)
-max_diversty_all <- which(max(rowSums(abs(var_expt_levels))) ==
-                            rowSums(abs(var_expt_levels)))
-max_only_CB_diversity <- which(max(rowSums(abs(var_expt_levels[,1:2]))) ==
-                            rowSums(abs(var_expt_levels[,1:2])) &
-                              rowSums(abs(var_expt_levels[,3:6]))==0)
-#var_expt_levels[381,]
-
-max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
-                            rowSums(abs(var_expt_levels[,3:6])) &
-                              rowSums(abs(var_expt_levels[,1:2]))==0)
-#var_expt_levels[20,]
-
-```
-
-```{r}
-
-p1  <- plot_ss_result1(var_expt,
-                result_index = no_diversity,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p1
-
-#junk1 <- var_expt[no_diversity,]$ss_res[[1]]
-```
-
-```{r}
-
-p2  <- plot_ss_result1(var_expt,
-                result_index = max_diversty_all,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p2
-
-```
-
-```{r}
-
-p3  <- plot_ss_result1(var_expt,
-                result_index = max_only_CB_diversity,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p3
-
-```
-
-```{r}
-
-p4  <- plot_ss_result1(var_expt,
-                result_index = max_only_SBPB_diversity,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p4
-
-```
-
-```{r}
-p_overlay1 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
-                             var_expt[max_diversty_all,]$ss_res[[1]],
-                             xlims = c(-7, -1))
-p_overlay1
-```
-
-```{r}
-p_overlay2 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
-                             var_expt[max_only_CB_diversity,]$ss_res[[1]],
-                             xlims = c(-7, -1))
-p_overlay2
-
-#ss_result1 <- var_expt[no_diversity,]$ss_res[[1]]
-#ss_result2 <- var_expt[max_only_CB_diversity,]$ss_res[[1]]
-
-```
-
-```{r}
-p_overlay3 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
-                             var_expt[max_only_SBPB_diversity,]$ss_res[[1]],
-                             xlims = c(-7, -1))
-p_overlay3
-
-#ss_result3 <- var_expt[max_only_SBPB_diversity,]$ss_res[[1]]
-
-```
-
-```{r}
-tempp1 <- var_expt[no_diversity,]$ss_res[[1]] %>%
-  filter(initial_N_CB == 1e10,
-         log10(a_O) > -4.5, log10(a_O) < -4)
-tempp2 <- var_expt[max_only_SBPB_diversity,]$ss_res[[1]] %>%
-  filter(initial_N_CB == 1e10,
-         log10(a_O) > -4.5, log10(a_O) < -4)
-
-ggplot() +
-  geom_line(mapping = aes(x = log10(tempp1$a_O),
-                          y = log10(tempp1$O))) +
-  geom_line(mapping = aes(x = log10(tempp2$a_O),
-                          y = log10(tempp2$O)),
-            col = "blue")
-
-ggplot() +
-  geom_histogram(mapping = aes(x = log10(tempp1$O) - log10(tempp2$O)),
-            col = "blue")
-
-ggplot() +
-  geom_line(mapping = aes(x = log10(tempp1$a_O),
-    y = log10(tempp1$P) - log10(tempp2$P)),
-            col = "blue")
-
-```
-
-```{r}
-CB_vars <- unique(stab_data$CB_var_gmax_s)
-SB_vars <- unique(stab_data$SB_var_gmax_s)
-
-CB_stab_data <- stab_data %>%
-  filter(SB_var_gmax_s == 0) %>%
-  mutate(var_treat = "CB",
-         var_gmax = CB_var_gmax_s)
-
-SBPB_stab_data <- stab_data %>%
-  filter(CB_var_gmax_s == 0) %>%
-  mutate(var_treat = "SB-PB",
-         var_gmax = SB_var_gmax_s)
-
-for_join <- tibble(CB_var_gmax_s = CB_vars,
-                     SB_var_gmax_s = SB_vars)
-CBSBPB_stab_data <- stab_data %>%
-  right_join(for_join) %>%
-  mutate(var_treat = "CB-SB-PB",
-         var_gmax = CB_var_gmax_s)
-
-all_stab_results <- CB_stab_data %>%
-  bind_rows(SBPB_stab_data) %>%
-#  bind_rows(results3) %>%
- # bind_rows(results4) %>%
-  bind_rows(CBSBPB_stab_data)
-
-all_stab_results <- all_stab_results %>%
-    mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB-PB", "CB-SB-PB")))
-
-#saveRDS(all_stab_results, here("experiments/experiment summary/all_stab.RDS"))
-
-#all_stab_results <- readRDS(here("experiments/experiment summary/all_stab.RDS"))
-```
-
-### raw
-```{r}
-all_stab_results %>%
-  filter(Species == "O") %>%
-  ggplot(aes(x = var_gmax, y = hyst_range_raw, col=var_treat, shape = as_factor(sim_length))) +
-  geom_point() +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
-  labs(col = "Variation in\nonly these\nfunctional groups")
-##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)
-
-all_stab_results %>%
-  #filter(var_treat == "CB") %>%
-  filter(Species == "O",
-         sim_length == 1e6) %>%
-  ggplot(aes(x = var_gmax,
-             ymin = hyst_min_raw,
-             ymax = hyst_max_raw,
-             fill=var_treat)) +
-  geom_ribbon(alpha = 0.5) +
-  facet_wrap( ~ var_treat, nrow = 3) +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
-  labs(fill = "Variation in\nonly these\nfunctional groups") +
-  coord_flip() +
-  theme(
-    strip.background = element_blank(),
-    strip.text.x = element_blank()
-  )
-
-##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
-stab_data %>%
-  filter(Species == "O",
-         sim_length == 1e6) %>%
-  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range_raw, col = hyst_range_raw)) +
-  geom_point(size = 3)
-
-##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
-
-stab_data %>%
-  filter(Species == "O",
-         sim_length == 1e6) %>%
-  ggplot(aes(x = CB_var_gmax_s, y = hyst_range_raw, col = as.factor(SB_var_gmax_s))) +
-  geom_line(size = 2)
-```
-
-### log
-```{r}
-all_stab_results %>%
-  filter(Species == "O") %>%
-  ggplot(aes(x = var_gmax, y = hyst_range_log, col=var_treat, shape = as_factor(sim_length))) +
-  geom_point() +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
-  labs(col = "Variation in\nonly these\nfunctional groups")
-##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)
-
-all_stab_results %>%
-  #filter(var_treat == "CB") %>%
-  filter(Species == "O",
-         sim_length == 1e6) %>%
-  ggplot(aes(x = var_gmax,
-             ymin = hyst_min_log,
-             ymax = hyst_max_log,
-             fill=var_treat)) +
-  geom_ribbon(alpha = 0.5) +
-  facet_wrap( ~ var_treat, nrow = 3) +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
-  labs(fill = "Variation in\nonly these\nfunctional groups") +
-  coord_flip() +
-  theme(
-    strip.background = element_blank(),
-    strip.text.x = element_blank()
-  )
-
 ##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
@@
 
+# FROM HERE NOT CHANGED TO NEW FORMAT!!!!!!
+# Some puzzles
+
 ## What effect of changing the length of the simulations
@@
 ```
-
-# FROM HERE NOT CHANGED TO NEW FORMAT!!!!!!
-# Some puzzles
 
@@
 
-# Zoom in on SS
+## Zoom in on SS
 
@@
 
-# Negative abundance investigation
+## Negative abundance investigation
 
@@
 
-# Understand about relative and absolute variation in traits
+## Understand about relative and absolute variation in traits
 

### 2021-11-12 R/various_useful_functions.r

@@ -530,13 +530,14 @@ visualise_temporal_env_eco <- function(sim_res_novar = NULL, sim_res_highvar = N
   ggplot() +
     geom_path(
       data = filter(tmp_novar, functional_group == soi),
-      aes(x = a, y = log10(Total_quantity), group = direction)
+      aes(x = a, y = log10(Total_quantity), group = direction),
+      lwd = 2
     ) +
     geom_path(
       data = filter(tmp_highvar, functional_group == soi),
       aes(x = a, y = log10(Total_quantity), group = direction),
-      linetype = "dashed", lwd = 2, col = "red"
+      lwd = 1, col = "red"
     ) +
-    ggtitle("Solid line is with no intraspecific diversity.\nDashed line is with intraspecific diversity")
+    ggtitle("Black line is with no diversity.\nRed line is with diversity")
   ## ggsave(here("simulations/figures/switching_comparison.pdf"), width = 5, height = 4)
 }

### 2021-11-13 experiments/12_strains/12_strains.Rmd
reorganisation, and added different number of strains

--- 2021-11-12 experiments/experiment 1/experiment-1.Rmd
@@
 ---
-title: "experiment 1"
+title: "12 strains"
 author: "Owen Petchey"
@@
 eval_dynamics_flag <- FALSE
+plot_ss_results <- FALSE
 ```
@@
 
-num_CB_strains <- 9
-num_SB_strains <- 9
-num_PB_strains <- 9
+num_CB_strains <- 12
+num_SB_strains <- 12
+num_PB_strains <- 12
 
@@
 parameter <- new_runsim_parameter(
+  solver_method = "radau",
   dynamic_model = bushplus_dynamic_model,
   event_definition = event_definition_1,
-  event_interval = 100,
+  event_interval = 10,
   noise_sigma = 0,
@@
 parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/num_CB_strains
+parameter$solver_method <- "lsoda"
 sim_res_novar1 <- run_simulation(parameter)
-saveRDS(sim_res_novar1, here("experiments/experiment 1/data/sim_res_novar1.RDS"))
+saveRDS(sim_res_novar1, here("experiments/12_strains/data/sim_res_novar1.RDS"))
 ```
@@
 ```{r}
-sim_res_novar1 <- readRDS(here("experiments/experiment 1/data/sim_res_novar1.RDS"))
+sim_res_novar1 <- readRDS(here("experiments/12_strains/data/sim_res_novar1.RDS"))
 plot_dynamics(sim_res_novar1)
 #ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
+```
+
+```{r}
+simulation_result <- sim_res_novar1
+
 ```
@@
 sim_res_highvar1 <- run_simulation(parameter)
-saveRDS(sim_res_highvar1, here("experiments/experiment 1/data/sim_res_highvar1.RDS"))
+saveRDS(sim_res_highvar1, here("experiments/12_strains/data/sim_res_highvar1.RDS"))
 ```
@@
 ```{r}
-sim_res_highvar1 <- readRDS(here("experiments/experiment 1/data/sim_res_highvar1.RDS"))
+sim_res_highvar1 <- readRDS(here("experiments/12_strains/data/sim_res_highvar1.RDS"))
 plot_dynamics(sim_res_highvar1)
@@
 sim_res_novar2 <- run_simulation(parameter)
-saveRDS(sim_res_novar2, here("experiments/experiment 1/data/sim_res_novar2.RDS"))
+saveRDS(sim_res_novar2, here("experiments/12_strains/data/sim_res_novar2.RDS"))
 ```
@@
 ```{r}
-sim_res_novar2 <- readRDS(here("experiments/experiment 1/data/sim_res_novar2.RDS"))
+sim_res_novar2 <- readRDS(here("experiments/12_strains/data/sim_res_novar2.RDS"))
 plot_dynamics(sim_res_novar2)
@@
 sim_res_highvar2 <- run_simulation(parameter)
-saveRDS(sim_res_highvar2, here("experiments/experiment 1/data/sim_res_highvar2.RDS"))
+saveRDS(sim_res_highvar2, here("experiments/12_strains/data/sim_res_highvar2.RDS"))
 ```
@@
 ```{r}
-sim_res_highvar2 <- readRDS(here("experiments/experiment 1/data/sim_res_highvar2.RDS"))
+sim_res_highvar2 <- readRDS(here("experiments/12_strains/data/sim_res_highvar2.RDS"))
 plot_dynamics(sim_res_highvar2)
@@
 sim_res_novar3 <- run_simulation(parameter)
-saveRDS(sim_res_novar3, here("experiments/experiment 1/data/sim_res_novar3.RDS"))
+saveRDS(sim_res_novar3, here("experiments/12_strains/data/sim_res_novar3.RDS"))
 ```
@@
 ```{r}
-sim_res_novar3 <- readRDS(here("experiments/experiment 1/data/sim_res_novar3.RDS"))
+sim_res_novar3 <- readRDS(here("experiments/12_strains/data/sim_res_novar3.RDS"))
 plot_dynamics(sim_res_novar3)
@@
 sim_res_highvar3 <- run_simulation(parameter)
-saveRDS(sim_res_highvar3, here("experiments/experiment 1/data/sim_res_highvar3.RDS"))
+saveRDS(sim_res_highvar3, here("experiments/12_strains/data/sim_res_highvar3.RDS"))
 ```
@@
 ```{r}
-sim_res_highvar3 <- readRDS(here("experiments/experiment 1/data/sim_res_highvar3.RDS"))
+sim_res_highvar3 <- readRDS(here("experiments/12_strains/data/sim_res_highvar3.RDS"))
 plot_dynamics(sim_res_highvar3)
@@
 
-saveRDS(parameter, here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS"))
-saveRDS(var_expt_small, here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial.RDS"))
-```
-
-### for testing
-
-```{r eval = FALSE}
-var_expt_small <- var_expt[c(no_diversity, medium_diverity_varexp_row),]
-saveRDS(parameter, here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS"))
-saveRDS(var_expt_small, here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial_small.RDS"))
-run_ss_var_experiment(
-  parameter = readRDS(here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS")), 
-  var_expt = readRDS(here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial_small.RDS"))) %>%
-saveRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_small.RDS"))
+saveRDS(parameter, here("experiments/12_strains/data/parameter_1e6_x2x6_factorial.RDS"))
+saveRDS(var_expt, here("experiments/12_strains/data/var_expt_1e6_x2x6_factorial.RDS"))
 ```
@@
 run_ss_var_experiment(
-  parameter = readRDS(here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS")), 
-  var_expt = readRDS(here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial.RDS"))) %>%
-saveRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS"))
+  parameter = readRDS(here("experiments/12_strains/data/parameter_1e6_x2x6_factorial.RDS")), 
+  var_expt = readRDS(here("experiments/12_strains/data/var_expt_1e6_x2x6_factorial.RDS"))) %>%
+saveRDS(here("experiments/12_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
 ```
@@
 ## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
-readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_small.RDS")) %>%
+readRDS(here("experiments/12_strains/data/ss_data_1e6_x2x6_factorial_small.RDS")) %>%
   mutate(sim_length = 1000000) %>% 
@@
   unnest(cols = c(stability_measures)) %>%
-  saveRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial_small.RDS"))
-```
-
-```{r eval = FALSE}
-## compare version 1 results to the current.
-v1_ss_data <- readRDS(here("experiments/experiment 1/data/version1_ss_data_1e6_x2x6_factorial.RDS"))
-v1_stab_data <- readRDS(here("experiments/experiment 1/data/version1_stab_data_1e6_x2x6_factorial.RDS"))
-
-small_ss_data <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_small.RDS"))
-small_stab_data <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial_small.RDS"))
-
-xxxxx <- small_stab_data %>%
-  select(-data, -pars, -ss_by_a_N_result, -ss_res, -sim_length) %>%
-  filter(Species == "O")
-v1_stab_data %>%
-  filter(CB_var_gmax_s == 0, CB_var_h_s == 0,
-         SB_var_gmax_s == 0, SB_var_h_s == 0,
-         PB_var_gmax_s == 0, PB_var_h_s == 0) %>%
-  filter(Species == "O")
-v1_stab_data %>%
-  slice(9620) %>%
-  filter(Species == "O")
+  saveRDS(here("experiments/12_strains/data/stab_data_1e6_x2x6_factorial_small.RDS"))
 ```
@@
 ## find various combinations of diversity
-var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS"))
-stab_data <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
+var_expt <- readRDS(here("experiments/12_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
+stab_data <- readRDS(here("experiments/12_strains/data/stab_data_1e6_x2x6_factorial.RDS"))
 
@@
 
-```{r}
+```{r eval = plot_ss_results}
 
@@
 
-#junk1 <- var_expt[no_diversity,]$ss_res[[1]]
-```
-
-```{r}
-
 p2  <- plot_ss_result1(var_expt,
@@
 p2
-
-```
-
-```{r}
 
@@
 
-```
-
-```{r}
-
 p4  <- plot_ss_result1(var_expt,
@@
 
-```
-
-```{r}
 p_overlay1 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
@@
 p_overlay1
-```
 
-```{r}
 p_overlay2 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
@@
 
-#ss_result1 <- var_expt[no_diversity,]$ss_res[[1]]
-#ss_result2 <- var_expt[max_only_CB_diversity,]$ss_res[[1]]
-
-```
-
-```{r}
 p_overlay3 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
@@
 
-#ss_result3 <- var_expt[max_only_SBPB_diversity,]$ss_res[[1]]
-
 ```
 
-```{r}
+```{r eval = plot_ss_results}
 tempp1 <- var_expt[no_diversity,]$ss_res[[1]] %>%
@@
 
-```{r}
+```{r eval = plot_ss_results}
 CB_vars <- unique(stab_data$CB_var_gmax_s)
@@
 ### Raw
-```{r}
+```{r eval = plot_ss_results}
 all_stab_results %>%
@@
 
-```{r}
+```{r eval = plot_ss_results}
 all_stab_results %>%
@@
 ```
-
-# FROM HERE NOT CHANGED TO NEW FORMAT!!!!!!
-# Some puzzles
-
-## What effect of changing the length of the simulations
-No Experimental data.
-
-```{r, eval = FALSE, echo = FALSE}
-var_expt1 <- readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS"))
-var_expt2 <- readRDS(here("experiments/experiment 1/data/ss_data_80000.RDS"))
-
-p1_short  <- plot_ss_result1(var_expt2,
-                result_index = max_diversty_all,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p1_short
-
-p1_long  <- plot_ss_result1(var_expt1,
-                result_index = max_diversty_all,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p1_long
-```
-
-## Puzzle 1
-
-When the environment ameliorates for the sulphur bacteria, there is no strain replacement (in final state) along the oxygen diffusivity gradient -- either the system is oxic or the least tolerant strain SB9 dominates.
-And yet the switch to anoxic occurs earlier than when there is no diversity, which suggests there is some role of the more tolerant strains.
-Indeed Uriah showed that the presence of only the most tolerant strain is sufficient to give an earlier switch, even though it is not present in the final state when less tolerant strains are present.
-And he showed that the presence of only the least tolerant strain creates a later switch than when there are more tolerant strains.
-
-The explanation is that the most tolerant strain does play a role, but only a transient one.
-The following dynamics are for the system starting oxic, and with a value of oxygen diffusivity (log10(a_O) = -4.8) for which the system remains oxic if there is no diversity, but switches to anoxic if there is diversity.
-There is only diversity in the sulphur bacteria.
-The most tolerant strain does at first grow, but is then outcompeted by less tolerant strains as the environment ameliorates (temporally).
-
-TODO CHECK THE PARAMETER
-
-```{r}
-var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS"))
-var_expt_levels <- var_expt[,1:6]
-no_diversity <- which(rowSums(abs(var_expt_levels))==0)
-max_diversty_all <- which(max(rowSums(abs(var_expt_levels))) ==
-                            rowSums(abs(var_expt_levels)))
-max_only_CB_diversity <- which(max(rowSums(abs(var_expt_levels[,1:2]))) ==
-                            rowSums(abs(var_expt_levels[,1:2])) &
-                              rowSums(abs(var_expt_levels[,3:6]))==0)
-max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
-                            rowSums(abs(var_expt_levels[,3:6])) &
-                              rowSums(abs(var_expt_levels[,1:2]))==0)
-```
-
-```{r eval = eval_dynamics_flag}
-parameter <- readRDS(here("experiments/experiment 1/data/sim_res_novar3.RDS"))
-parameter$sim_duration <- 100000
-parameter$result <- NULL
-```
-
-```{r eval = eval_dynamics_flag}
-parameter$log10a_series <- c(-4.8, -4.8)
-parameter$strain_parameter$initial_state <- new_initial_state(
-  nrow(parameter$strain_parameter$CB),
-  nrow(parameter$strain_parameter$PB),
-  nrow(parameter$strain_parameter$PB),
-  values = "bush_ssfig3"
-)
-parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/nrow(parameter$strain_parameter$CB)
-
-sim_res_novar1 <- run_simulation(parameter)
-saveRDS(sim_res_novar1, here("experiments/experiment 1/data/puzzle1_1.RDS"))
-```
-
-```{r, eval = FALSE, echo = FALSE}
-sim_res_novar1 <- readRDS(here("experiments/experiment 1/data/puzzle1_1.RDS"))
-plot_dynamics(sim_res_novar1)
-#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
-```
-
-```{r eval = FALSE, echo = FALSE}
-sim_res_novar1 <- run_simulation(parameter_values = var_expt$pars[[max_only_SBPB_diversity]],
-                          initial_state = initial_state)
-saveRDS(sim_res_novar1, here("experiments/experiment 1/data/puzzle1_2.RDS"))
-```
-
-```{r, eval = FALSE, echo = FALSE}
-sim_res_novar1 <- readRDS(here("experiments/experiment 1/data/puzzle1_2.RDS"))
-plot_dynamics(sim_res_novar1)
-#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
-```
-
-## Zoom in on SS
-
-```{r eval = FALSE, echo = FALSE}
-a_Os <- 10^seq(-2.479, -2.4785, length=grid_num_a) ## sequence of a_0 values
-initial_CBs <- 1#10^seq(0, 0, length=grid_num_N) ## sequence of N values
-initial_PBs <- 1e8 ## not varied
-initial_SBs <- 1e8 ## not varied
-# next line creates all possible combinations
-ss_expt <- expand.grid(N_CB = initial_CBs,
-                      N_PB = initial_PBs,
-                      N_SB = initial_SBs,
-                      a_O = a_Os)
-var_expt_master <- var_expt
-var_expt <- var_expt_master[381,]
-```
-
-```{r, eval = FALSE, echo = FALSE}
-#var_expt <- run_ss_var_experiment()
-#saveRDS(var_expt, here("experiments/experiment 1/data/ss_data_zoom.RDS"))
-```
-
-```{r, eval = FALSE, echo = FALSE}
-library(here)
-zoom <- readRDS(here("experiments/experiment 1/data/ss_data_zoom.RDS"))
-
-p1  <- plot_ss_result1(zoom,
-                result_index = 1,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p1
-```
-
-## Negative abundance investigation
-
-I (Owen) found that the sampling interval had an effect on the stability of the simulation.
-If the sampling interval was long, then in some rare cases (see below) the odesolver failed, with negative abundances occuring.
-I think this is due to abundances becoming very small, and then the computer having trouble with precision.
-I guess that when a sample is taken, the abundance is somehow altered if it is very low, probably by some rounding.
-
-```{r eval = FALSE, echo = FALSE}
-var_expt$pars[[1]]
-dd <- var_expt$ss_res[[1]]
-dd1 <- filter(dd, PB_1<(-0.0001))
-dd1$a_O
-
-ss_expt_master <- ss_expt
-ss_expt <- ss_expt_master[abs(ss_expt_master$a_O - 1.336984e-05)<1e-10,]
-
-var_expt_master <- var_expt
-#var_expt <- var_expt[1,]
-var_expt_test <- run_ss_var_experiment()
-res <- var_expt_test$ss_res[[1]]
-
-test1 <- ss_by_a_N(ss_expt, var_expt$pars[[1]])
-x <- ss_expt[2,]
-param <- var_expt$pars[[1]]
-get_final_states_a_N(x, param)
-ssfind_parameters <- param
-ssfind_simulation_sampling_interval <- 1000
-## now run inside the function "get_final_states_a_N"
-simres1 <- simres
-ssfind_simulation_sampling_interval <- 5000
-## now run inside the function "get_final_states_a_N"
-simres2 <- simres  # this fails
-
-## now run inside the function "get_final_states_a_N"
-plot_dynamics(simres2)
-
-ggplot() +
-  geom_line(data = simres1$result,
-             mapping = aes(x = time, y = log10(PB_1))) +
-  geom_point(data = simres2$result,
-             mapping = aes(x = time, y = log10(PB_1))) +
-  xlim(c(0, 250000))
-
-ccc <- simres2$result
-
-simres2$result$PB_1
-simres2$result$time
-
-log10_a <- log10(ss_expt$a_O[1]) ## very slowly goes anoxic
-#log10_a <- log10(a_Os[354]) ## very slowly goes anoxic
-#log10_a <- log10(a_Os[356]) ## very very very  slowly goes anoxic
-#log10_a <- log10(a_Os[357]) ## does not go anoxic
-
-default_dynamic_model <- bushplus_dynamic_model
-default_event_definition <- event_definition_1
-default_event_interval <- ssfind_simulation_duration
-default_noise_sigma <- 0
-default_minimum_abundances <- ssfind_minimum_abundances
-default_sim_duration <- ssfind_simulation_duration
-default_sim_sample_interval <- ssfind_simulation_duration
-#initial_pars_from <- "bush_ssfig3"
-
-default_log10a_series <- c(log10_a, log10_a)
-initial_state <- new_initial_state(num_CB_strains,
-                                   num_PB_strains,
-                                   num_SB_strains,
-                                   values = "bush_ssfig3")
-initial_state[grep("CB_", names(initial_state))] <- 10^10/num_CB_strains
-sim_res_novar <- run_simulation(parameter_values = var_expt$pars[[1]],
-                          initial_state = initial_state)
-plot_dynamics(sim_res_novar)
-
-simulation_result <- sim_res_novar
-every_n <- 1
-
-chk <- sim_res_novar$result
-
-sim_res_novar$result %>%
-  ggplot() +
-  geom_line(mapping = aes(x = time, y = PB_1))
-
-#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
-
-```
-
-## Understand about relative and absolute variation in traits
-
-```{r echo = FALSE, eval = FALSE}
-num_CB_strains <- 9
-num_SB_strains <- 9
-num_PB_strains <- 9
-
-## multiplier of SBPB variation
-CB_var_multiplier <- 1
-SBPB_var_multiplier <- 5
-
-CB_gmax_div <- 0.015789474 * CB_var_multiplier
-CB_h_div <- -0.08 * CB_var_multiplier
-SB_gmax_div <- 0.015789474 * SBPB_var_multiplier
-SB_h_div <- -0.323  * SBPB_var_multiplier
-PB_gmax_div <- 0.015789474  * SBPB_var_multiplier
-PB_h_div <- -0.323  * SBPB_var_multiplier
-
-num_div_treatment_levels <- 2
-
-var_expt <- create_diversity_factorial(zero = zero, unity = unity, num_div_treatment_levels = num_div_treatment_levels)
-
-display_diversity(
- 4,
-  var_expt = var_expt,
-  num_CB_strains = num_CB_strains,
-  num_SB_strains = num_SB_strains,
-  num_PB_strains = num_PB_strains
-)
-
-this_one <- 4
-CBtraits <- var_expt$pars[[this_one]]$CB
-P <- 1 #10^seq(-5, 5, 0.1)
-SR <- 10^seq(0, 3, 0.1)
-gr_rateCB1 <- growth1(P, CBtraits$g_max_CB[1], CBtraits$k_CB_P[1]) * inhibition(SR, CBtraits$h_SR_CB[1])
-gr_rateCB9 <- growth1(P, CBtraits$g_max_CB[num_CB_strains], CBtraits$k_CB_P[num_CB_strains]) * inhibition(SR, CBtraits$h_SR_CB[num_CB_strains])
-CB_gr_rates <- (c(gr_rateCB1, gr_rateCB9))
-CB_gr_range <- max(CB_gr_rates) - min(CB_gr_rates)
-CB_gr_range
-
-SBtraits <- var_expt$pars[[this_one]]$SB
-P <- 1 #10^seq(-5, 5, 0.1)
-SO <- 1
-O <- 10^seq(-2.5, 2.5, 0.1)
-gr_rateSB1 <- growth2(P, SO, SBtraits$g_max_SB[1], SBtraits$k_SB_P[1], SBtraits$k_SB_SO[1]) *
-  inhibition(O, SBtraits$h_O_SB[1])
-gr_rateSB9 <- growth2(P, SO, SBtraits$g_max_SB[9], SBtraits$k_SB_P[9], SBtraits$k_SB_SO[9]) *
-    inhibition(O, SBtraits$h_O_SB[9])
-SB_gr_rates <- (c(gr_rateSB1, gr_rateSB9))
-SB_gr_range <- max(SB_gr_rates) - min(SB_gr_rates)
-SB_gr_range
-
-PBtraits <- var_expt$pars[[this_one]]$PB
-P <- 1 #10^seq(-5, 5, 0.1)
-SO <- 1
-O <- 10^seq(-2.5, 2.5, 0.1)
-gr_ratePB1 <- growth2(P, SO, PBtraits$g_max_PB[1], PBtraits$k_PB_P[1], PBtraits$k_PB_SR[1]) *
-  inhibition(O, PBtraits$h_O_PB[1])
-gr_ratePB9 <- growth2(P, SO, PBtraits$g_max_PB[9], PBtraits$k_PB_P[9], PBtraits$k_PB_SR[9]) *
-  inhibition(O, PBtraits$h_O_PB[9])
-PB_gr_rates <- (c(gr_ratePB1, gr_ratePB9))
-PB_gr_range <- max(PB_gr_rates) - min(PB_gr_rates)
-PB_gr_range
-
-```
-
-<!-- With the CB diversity multiplier set at ` CB_var_multiplier` and the SB/PB multiplier set at ` SBPB_var_multiplier` the range of realised growth rates of CB is ` CB_gr_range`, range of SB is ` SB_gr_range`, and range of PB is ` PB_gr_range`.
--->

### 2021-11-13 experiments/3_strains/3_strains.Rmd
reorganisation, and added different number of strains

--- 2021-11-13 experiments/12_strains/12_strains.Rmd
@@
 ---
-title: "12 strains"
+title: "3 strains"
 author: "Owen Petchey"
-date: "6/25/2021"
+date: "`r format(Sys.time(), '%d %B, %Y')`"
 output:
@@
 
-num_CB_strains <- 12
-num_SB_strains <- 12
-num_PB_strains <- 12
+num_CB_strains <- 3
+num_SB_strains <- 3
+num_PB_strains <- 3
 
@@
 parameter <- new_runsim_parameter(
-  solver_method = "radau",
   dynamic_model = bushplus_dynamic_model,
   event_definition = event_definition_1,
-  event_interval = 10,
+  event_interval = 100,
   noise_sigma = 0,
@@
 display_diversity(
-  400,
+  nrow(var_expt),
   var_expt = var_expt,
@@
 parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/num_CB_strains
-parameter$solver_method <- "lsoda"
 sim_res_novar1 <- run_simulation(parameter)
-saveRDS(sim_res_novar1, here("experiments/12_strains/data/sim_res_novar1.RDS"))
+saveRDS(sim_res_novar1, here("experiments/3_strains/data/sim_res_novar1.RDS"))
 ```
@@
 ```{r}
-sim_res_novar1 <- readRDS(here("experiments/12_strains/data/sim_res_novar1.RDS"))
+sim_res_novar1 <- readRDS(here("experiments/3_strains/data/sim_res_novar1.RDS"))
 plot_dynamics(sim_res_novar1)
 #ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
-```
-
-```{r}
-simulation_result <- sim_res_novar1
-
 ```
@@
 sim_res_highvar1 <- run_simulation(parameter)
-saveRDS(sim_res_highvar1, here("experiments/12_strains/data/sim_res_highvar1.RDS"))
+saveRDS(sim_res_highvar1, here("experiments/3_strains/data/sim_res_highvar1.RDS"))
 ```
@@
 ```{r}
-sim_res_highvar1 <- readRDS(here("experiments/12_strains/data/sim_res_highvar1.RDS"))
+sim_res_highvar1 <- readRDS(here("experiments/3_strains/data/sim_res_highvar1.RDS"))
 plot_dynamics(sim_res_highvar1)
@@
 sim_res_novar2 <- run_simulation(parameter)
-saveRDS(sim_res_novar2, here("experiments/12_strains/data/sim_res_novar2.RDS"))
+saveRDS(sim_res_novar2, here("experiments/3_strains/data/sim_res_novar2.RDS"))
 ```
@@
 ```{r}
-sim_res_novar2 <- readRDS(here("experiments/12_strains/data/sim_res_novar2.RDS"))
+sim_res_novar2 <- readRDS(here("experiments/3_strains/data/sim_res_novar2.RDS"))
 plot_dynamics(sim_res_novar2)
@@
 sim_res_highvar2 <- run_simulation(parameter)
-saveRDS(sim_res_highvar2, here("experiments/12_strains/data/sim_res_highvar2.RDS"))
+saveRDS(sim_res_highvar2, here("experiments/3_strains/data/sim_res_highvar2.RDS"))
 ```
@@
 ```{r}
-sim_res_highvar2 <- readRDS(here("experiments/12_strains/data/sim_res_highvar2.RDS"))
+sim_res_highvar2 <- readRDS(here("experiments/3_strains/data/sim_res_highvar2.RDS"))
 plot_dynamics(sim_res_highvar2)
@@
 sim_res_novar3 <- run_simulation(parameter)
-saveRDS(sim_res_novar3, here("experiments/12_strains/data/sim_res_novar3.RDS"))
+saveRDS(sim_res_novar3, here("experiments/3_strains/data/sim_res_novar3.RDS"))
 ```
@@
 ```{r}
-sim_res_novar3 <- readRDS(here("experiments/12_strains/data/sim_res_novar3.RDS"))
+sim_res_novar3 <- readRDS(here("experiments/3_strains/data/sim_res_novar3.RDS"))
 plot_dynamics(sim_res_novar3)
@@
 sim_res_highvar3 <- run_simulation(parameter)
-saveRDS(sim_res_highvar3, here("experiments/12_strains/data/sim_res_highvar3.RDS"))
+saveRDS(sim_res_highvar3, here("experiments/3_strains/data/sim_res_highvar3.RDS"))
 ```
@@
 ```{r}
-sim_res_highvar3 <- readRDS(here("experiments/12_strains/data/sim_res_highvar3.RDS"))
+sim_res_highvar3 <- readRDS(here("experiments/3_strains/data/sim_res_highvar3.RDS"))
 plot_dynamics(sim_res_highvar3)
@@
 
-saveRDS(parameter, here("experiments/12_strains/data/parameter_1e6_x2x6_factorial.RDS"))
-saveRDS(var_expt, here("experiments/12_strains/data/var_expt_1e6_x2x6_factorial.RDS"))
+saveRDS(parameter, here("experiments/3_strains/data/parameter_1e6_x2x6_factorial.RDS"))
+saveRDS(var_expt, here("experiments/3_strains/data/var_expt_1e6_x2x6_factorial.RDS"))
 ```
@@
 run_ss_var_experiment(
-  parameter = readRDS(here("experiments/12_strains/data/parameter_1e6_x2x6_factorial.RDS")), 
-  var_expt = readRDS(here("experiments/12_strains/data/var_expt_1e6_x2x6_factorial.RDS"))) %>%
-saveRDS(here("experiments/12_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
+  parameter = readRDS(here("experiments/3_strains/data/parameter_1e6_x2x6_factorial.RDS")), 
+  var_expt = readRDS(here("experiments/3_strains/data/var_expt_1e6_x2x6_factorial.RDS"))) %>%
+saveRDS(here("experiments/3_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
 ```
@@
 ## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
-readRDS(here("experiments/12_strains/data/ss_data_1e6_x2x6_factorial_small.RDS")) %>%
+readRDS(here("experiments/3_strains/data/ss_data_1e6_x2x6_factorial_small.RDS")) %>%
   mutate(sim_length = 1000000) %>% 
@@
   unnest(cols = c(stability_measures)) %>%
-  saveRDS(here("experiments/12_strains/data/stab_data_1e6_x2x6_factorial_small.RDS"))
+  saveRDS(here("experiments/3_strains/data/stab_data_1e6_x2x6_factorial_small.RDS"))
 ```
@@
 ## find various combinations of diversity
-var_expt <- readRDS(here("experiments/12_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
-stab_data <- readRDS(here("experiments/12_strains/data/stab_data_1e6_x2x6_factorial.RDS"))
+var_expt <- readRDS(here("experiments/3_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
+stab_data <- readRDS(here("experiments/3_strains/data/stab_data_1e6_x2x6_factorial.RDS"))
 

### 2021-11-13 experiments/6_strains/6_strains.Rmd
reorganisation, and added different number of strains

--- 2021-11-13 experiments/3_strains/3_strains.Rmd
@@
 ---
-title: "3 strains"
+title: "6 strains"
 author: "Owen Petchey"
-date: "`r format(Sys.time(), '%d %B, %Y')`"
+date: "6/25/2021"
 output:
@@
 
-num_CB_strains <- 3
-num_SB_strains <- 3
-num_PB_strains <- 3
+num_CB_strains <- 6
+num_SB_strains <- 6
+num_PB_strains <- 6
 
@@
 display_diversity(
-  nrow(var_expt),
+  400,
   var_expt = var_expt,
@@
 sim_res_novar1 <- run_simulation(parameter)
-saveRDS(sim_res_novar1, here("experiments/3_strains/data/sim_res_novar1.RDS"))
+saveRDS(sim_res_novar1, here("experiments/6_strains/data/sim_res_novar1.RDS"))
 ```
@@
 ```{r}
-sim_res_novar1 <- readRDS(here("experiments/3_strains/data/sim_res_novar1.RDS"))
+sim_res_novar1 <- readRDS(here("experiments/6_strains/data/sim_res_novar1.RDS"))
 plot_dynamics(sim_res_novar1)
@@
 sim_res_highvar1 <- run_simulation(parameter)
-saveRDS(sim_res_highvar1, here("experiments/3_strains/data/sim_res_highvar1.RDS"))
+saveRDS(sim_res_highvar1, here("experiments/6_strains/data/sim_res_highvar1.RDS"))
 ```
@@
 ```{r}
-sim_res_highvar1 <- readRDS(here("experiments/3_strains/data/sim_res_highvar1.RDS"))
+sim_res_highvar1 <- readRDS(here("experiments/6_strains/data/sim_res_highvar1.RDS"))
 plot_dynamics(sim_res_highvar1)
@@
 sim_res_novar2 <- run_simulation(parameter)
-saveRDS(sim_res_novar2, here("experiments/3_strains/data/sim_res_novar2.RDS"))
+saveRDS(sim_res_novar2, here("experiments/6_strains/data/sim_res_novar2.RDS"))
 ```
@@
 ```{r}
-sim_res_novar2 <- readRDS(here("experiments/3_strains/data/sim_res_novar2.RDS"))
+sim_res_novar2 <- readRDS(here("experiments/6_strains/data/sim_res_novar2.RDS"))
 plot_dynamics(sim_res_novar2)
@@
 sim_res_highvar2 <- run_simulation(parameter)
-saveRDS(sim_res_highvar2, here("experiments/3_strains/data/sim_res_highvar2.RDS"))
+saveRDS(sim_res_highvar2, here("experiments/6_strains/data/sim_res_highvar2.RDS"))
 ```
@@
 ```{r}
-sim_res_highvar2 <- readRDS(here("experiments/3_strains/data/sim_res_highvar2.RDS"))
+sim_res_highvar2 <- readRDS(here("experiments/6_strains/data/sim_res_highvar2.RDS"))
 plot_dynamics(sim_res_highvar2)
@@
 sim_res_novar3 <- run_simulation(parameter)
-saveRDS(sim_res_novar3, here("experiments/3_strains/data/sim_res_novar3.RDS"))
+saveRDS(sim_res_novar3, here("experiments/6_strains/data/sim_res_novar3.RDS"))
 ```
@@
 ```{r}
-sim_res_novar3 <- readRDS(here("experiments/3_strains/data/sim_res_novar3.RDS"))
+sim_res_novar3 <- readRDS(here("experiments/6_strains/data/sim_res_novar3.RDS"))
 plot_dynamics(sim_res_novar3)
@@
 sim_res_highvar3 <- run_simulation(parameter)
-saveRDS(sim_res_highvar3, here("experiments/3_strains/data/sim_res_highvar3.RDS"))
+saveRDS(sim_res_highvar3, here("experiments/6_strains/data/sim_res_highvar3.RDS"))
 ```
@@
 ```{r}
-sim_res_highvar3 <- readRDS(here("experiments/3_strains/data/sim_res_highvar3.RDS"))
+sim_res_highvar3 <- readRDS(here("experiments/6_strains/data/sim_res_highvar3.RDS"))
 plot_dynamics(sim_res_highvar3)
@@
 
-saveRDS(parameter, here("experiments/3_strains/data/parameter_1e6_x2x6_factorial.RDS"))
-saveRDS(var_expt, here("experiments/3_strains/data/var_expt_1e6_x2x6_factorial.RDS"))
+saveRDS(parameter, here("experiments/6_strains/data/parameter_1e6_x2x6_factorial.RDS"))
+saveRDS(var_expt, here("experiments/6_strains/data/var_expt_1e6_x2x6_factorial.RDS"))
 ```
@@
 run_ss_var_experiment(
-  parameter = readRDS(here("experiments/3_strains/data/parameter_1e6_x2x6_factorial.RDS")), 
-  var_expt = readRDS(here("experiments/3_strains/data/var_expt_1e6_x2x6_factorial.RDS"))) %>%
-saveRDS(here("experiments/3_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
+  parameter = readRDS(here("experiments/6_strains/data/parameter_1e6_x2x6_factorial.RDS")), 
+  var_expt = readRDS(here("experiments/6_strains/data/var_expt_1e6_x2x6_factorial.RDS"))) %>%
+saveRDS(here("experiments/6_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
 ```
@@
 ## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
-readRDS(here("experiments/3_strains/data/ss_data_1e6_x2x6_factorial_small.RDS")) %>%
+readRDS(here("experiments/6_strains/data/ss_data_1e6_x2x6_factorial_small.RDS")) %>%
   mutate(sim_length = 1000000) %>% 
@@
   unnest(cols = c(stability_measures)) %>%
-  saveRDS(here("experiments/3_strains/data/stab_data_1e6_x2x6_factorial_small.RDS"))
+  saveRDS(here("experiments/6_strains/data/stab_data_1e6_x2x6_factorial_small.RDS"))
 ```
@@
 ## find various combinations of diversity
-var_expt <- readRDS(here("experiments/3_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
-stab_data <- readRDS(here("experiments/3_strains/data/stab_data_1e6_x2x6_factorial.RDS"))
+var_expt <- readRDS(here("experiments/6_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
+stab_data <- readRDS(here("experiments/6_strains/data/stab_data_1e6_x2x6_factorial.RDS"))
 

### 2021-11-13 experiments/9_strains/9_strains.Rmd
reorganisation, and added different number of strains

--- 2021-11-13 experiments/6_strains/6_strains.Rmd
@@
 ---
-title: "6 strains"
+title: "9 strains"
 author: "Owen Petchey"
@@
 
-num_CB_strains <- 6
-num_SB_strains <- 6
-num_PB_strains <- 6
+num_CB_strains <- 9
+num_SB_strains <- 9
+num_PB_strains <- 9
 
@@
 sim_res_novar1 <- run_simulation(parameter)
-saveRDS(sim_res_novar1, here("experiments/6_strains/data/sim_res_novar1.RDS"))
+saveRDS(sim_res_novar1, here("experiments/9_strains/data/sim_res_novar1.RDS"))
 ```
@@
 ```{r}
-sim_res_novar1 <- readRDS(here("experiments/6_strains/data/sim_res_novar1.RDS"))
+sim_res_novar1 <- readRDS(here("experiments/9_strains/data/sim_res_novar1.RDS"))
 plot_dynamics(sim_res_novar1)
@@
 sim_res_highvar1 <- run_simulation(parameter)
-saveRDS(sim_res_highvar1, here("experiments/6_strains/data/sim_res_highvar1.RDS"))
+saveRDS(sim_res_highvar1, here("experiments/9_strains/data/sim_res_highvar1.RDS"))
 ```
@@
 ```{r}
-sim_res_highvar1 <- readRDS(here("experiments/6_strains/data/sim_res_highvar1.RDS"))
+sim_res_highvar1 <- readRDS(here("experiments/9_strains/data/sim_res_highvar1.RDS"))
 plot_dynamics(sim_res_highvar1)
@@
 sim_res_novar2 <- run_simulation(parameter)
-saveRDS(sim_res_novar2, here("experiments/6_strains/data/sim_res_novar2.RDS"))
+saveRDS(sim_res_novar2, here("experiments/9_strains/data/sim_res_novar2.RDS"))
 ```
@@
 ```{r}
-sim_res_novar2 <- readRDS(here("experiments/6_strains/data/sim_res_novar2.RDS"))
+sim_res_novar2 <- readRDS(here("experiments/9_strains/data/sim_res_novar2.RDS"))
 plot_dynamics(sim_res_novar2)
@@
 sim_res_highvar2 <- run_simulation(parameter)
-saveRDS(sim_res_highvar2, here("experiments/6_strains/data/sim_res_highvar2.RDS"))
+saveRDS(sim_res_highvar2, here("experiments/9_strains/data/sim_res_highvar2.RDS"))
 ```
@@
 ```{r}
-sim_res_highvar2 <- readRDS(here("experiments/6_strains/data/sim_res_highvar2.RDS"))
+sim_res_highvar2 <- readRDS(here("experiments/9_strains/data/sim_res_highvar2.RDS"))
 plot_dynamics(sim_res_highvar2)
@@
 sim_res_novar3 <- run_simulation(parameter)
-saveRDS(sim_res_novar3, here("experiments/6_strains/data/sim_res_novar3.RDS"))
+saveRDS(sim_res_novar3, here("experiments/9_strains/data/sim_res_novar3.RDS"))
 ```
@@
 ```{r}
-sim_res_novar3 <- readRDS(here("experiments/6_strains/data/sim_res_novar3.RDS"))
+sim_res_novar3 <- readRDS(here("experiments/9_strains/data/sim_res_novar3.RDS"))
 plot_dynamics(sim_res_novar3)
@@
 sim_res_highvar3 <- run_simulation(parameter)
-saveRDS(sim_res_highvar3, here("experiments/6_strains/data/sim_res_highvar3.RDS"))
+saveRDS(sim_res_highvar3, here("experiments/9_strains/data/sim_res_highvar3.RDS"))
 ```
@@
 ```{r}
-sim_res_highvar3 <- readRDS(here("experiments/6_strains/data/sim_res_highvar3.RDS"))
+sim_res_highvar3 <- readRDS(here("experiments/9_strains/data/sim_res_highvar3.RDS"))
 plot_dynamics(sim_res_highvar3)
@@
 
-saveRDS(parameter, here("experiments/6_strains/data/parameter_1e6_x2x6_factorial.RDS"))
-saveRDS(var_expt, here("experiments/6_strains/data/var_expt_1e6_x2x6_factorial.RDS"))
+saveRDS(parameter, here("experiments/9_strains/data/parameter_1e6_x2x6_factorial.RDS"))
+saveRDS(var_expt, here("experiments/9_strains/data/var_expt_1e6_x2x6_factorial.RDS"))
 ```
@@
 run_ss_var_experiment(
-  parameter = readRDS(here("experiments/6_strains/data/parameter_1e6_x2x6_factorial.RDS")), 
-  var_expt = readRDS(here("experiments/6_strains/data/var_expt_1e6_x2x6_factorial.RDS"))) %>%
-saveRDS(here("experiments/6_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
+  parameter = readRDS(here("experiments/9_strains/data/parameter_1e6_x2x6_factorial.RDS")), 
+  var_expt = readRDS(here("experiments/9_strains/data/var_expt_1e6_x2x6_factorial.RDS"))) %>%
+saveRDS(here("experiments/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
 ```
@@
 ## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
-readRDS(here("experiments/6_strains/data/ss_data_1e6_x2x6_factorial_small.RDS")) %>%
+readRDS(here("experiments/9_strains/data/ss_data_1e6_x2x6_factorial_small.RDS")) %>%
   mutate(sim_length = 1000000) %>% 
@@
   unnest(cols = c(stability_measures)) %>%
-  saveRDS(here("experiments/6_strains/data/stab_data_1e6_x2x6_factorial_small.RDS"))
+  saveRDS(here("experiments/9_strains/data/stab_data_1e6_x2x6_factorial_small.RDS"))
 ```
@@
 ## find various combinations of diversity
-var_expt <- readRDS(here("experiments/6_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
-stab_data <- readRDS(here("experiments/6_strains/data/stab_data_1e6_x2x6_factorial.RDS"))
+var_expt <- readRDS(here("experiments/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
+stab_data <- readRDS(here("experiments/9_strains/data/stab_data_1e6_x2x6_factorial.RDS"))
 

### 2021-11-13 experiments/checks_puzzles/checks_puzzles.Rmd
reorganisation, and added different number of strains

--- 2021-11-12 experiments/experiment 1/experiment-1.Rmd
@@
 saveRDS(parameter, here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS"))
-saveRDS(var_expt_small, here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial.RDS"))
-```
-
-### for testing
-
-```{r eval = FALSE}
-var_expt_small <- var_expt[c(no_diversity, medium_diverity_varexp_row),]
-saveRDS(parameter, here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS"))
-saveRDS(var_expt_small, here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial_small.RDS"))
-run_ss_var_experiment(
-  parameter = readRDS(here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS")), 
-  var_expt = readRDS(here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial_small.RDS"))) %>%
-saveRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_small.RDS"))
+saveRDS(var_expt, here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial.RDS"))
 ```
@@
   saveRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial_small.RDS"))
-```
-
-```{r eval = FALSE}
-## compare version 1 results to the current.
-v1_ss_data <- readRDS(here("experiments/experiment 1/data/version1_ss_data_1e6_x2x6_factorial.RDS"))
-v1_stab_data <- readRDS(here("experiments/experiment 1/data/version1_stab_data_1e6_x2x6_factorial.RDS"))
-
-small_ss_data <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_small.RDS"))
-small_stab_data <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial_small.RDS"))
-
-xxxxx <- small_stab_data %>%
-  select(-data, -pars, -ss_by_a_N_result, -ss_res, -sim_length) %>%
-  filter(Species == "O")
-v1_stab_data %>%
-  filter(CB_var_gmax_s == 0, CB_var_h_s == 0,
-         SB_var_gmax_s == 0, SB_var_h_s == 0,
-         PB_var_gmax_s == 0, PB_var_h_s == 0) %>%
-  filter(Species == "O")
-v1_stab_data %>%
-  slice(9620) %>%
-  filter(Species == "O")
 ```

### 2021-11-13 R/various_useful_functions.r

@@ -139,7 +139,8 @@ plot_ss_result1 <- function(ss_exp_result,
   num_PB_strains <- num_strains$num[num_strains$functional_group == "PB"]
 
   p1 <- temp %>%
-    dplyr::filter(functional_group == "CB") %>%
+    dplyr::filter(functional_group == "CB")  %>%
+    mutate(species = factor(species, levels = unique(species))) %>%
     ggplot(aes(x = log10(a), y = log10_quantity, col = species, linetype = direction)) +
     geom_path() +
     ylab("log10(quantity [cells])") +
@@ -149,7 +150,8 @@ plot_ss_result1 <- function(ss_exp_result,
   # p1
 
   p2 <- temp %>%
-    dplyr::filter(functional_group == "SB") %>%
+    dplyr::filter(functional_group == "SB")  %>%
+    mutate(species = factor(species, levels = unique(species))) %>%
     ggplot(aes(x = log10(a), y = log10_quantity, col = species, linetype = direction)) +
     geom_path() +
     ylab("log10(quantity [cells])") +
@@ -158,7 +160,8 @@ plot_ss_result1 <- function(ss_exp_result,
     guides(colour = guide_legend(ncol = 3))
 
   p3 <- temp %>%
-    dplyr::filter(functional_group == "PB") %>%
+    dplyr::filter(functional_group == "PB")  %>%
+    mutate(species = factor(species, levels = unique(species))) %>%
     ggplot(aes(x = log10(a), y = log10_quantity, col = species, linetype = direction)) +
     geom_path() +
     ylab("log10(quantity [cells])") +
@@ -322,11 +325,13 @@ display_diversity <- function(
   ptsize <- 2
 
   CBtraits <- var_expt$pars[[this_one]]$CB
+  CBtraits$strain_name <- factor(CBtraits$strain_name, levels=CBtraits$strain_name)
+  
   P <- 1 # 10^seq(-5, 5, 0.1)
   SR <- 10^seq(0, 3, 0.1)
   gr_rateCB1 <- growth1(P, CBtraits$g_max_CB[1], CBtraits$k_CB_P[1]) * inhibition(SR, CBtraits$h_SR_CB[1])
[…]

### 2021-11-13 experiments/checks_puzzles/checks_puzzles.Rmd
Update checks_puzzles.Rmd

@@
 ---
-title: "experiment 1"
+title: "Checks and puzzles"
 author: "Owen Petchey"
@@
 ---
-
-This experiment supersedes all previous ones.
-It is a factorial manipulation of diversity of the three groups.
-It takes about 50 hours to run while using 12 cores.
 
@@
 names(parameter$minimum_abundances) <- c("CB", "PB", "SB")
+parameter_master <- parameter
 rm(sp)
@@
 
-num_div_treatment_levels <- 20
+num_div_treatment_levels <- 5
 
@@
 ```
-
-# Temporal switching
 
@@
 
-medium_diverity_varexp_row <- 311
+#medium_diverity_varexp_row <- 311
 
@@
 
-## Oxic to anoxic
+# What effect of changing the length of the simulations
 
-### No diversity
-
-```{r eval = eval_dynamics_flag}
-parameter$sim_duration <- 80000
-```
-
-```{r eval = eval_dynamics_flag}
-parameter$log10a_series <- c(-1, -7, -7)
-parameter$strain_parameter <- var_expt$pars[[no_diversity]]
-parameter$strain_parameter$initial_state <- new_initial_state(
-  num_CB_strains,
-  num_PB_strains,
-  num_SB_strains,
-  values = "bush_ssfig3"
-)
-parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/num_CB_strains
-sim_res_novar1 <- run_simulation(parameter)
-saveRDS(sim_res_novar1, here("experiments/experiment 1/data/sim_res_novar1.RDS"))
-```
-
-```{r}
-sim_res_novar1 <- readRDS(here("experiments/experiment 1/data/sim_res_novar1.RDS"))
-plot_dynamics(sim_res_novar1)
-#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
-```
-
-### With diversity
-
-```{r eval = eval_dynamics_flag}
-parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
-parameter$strain_parameter$initial_state <- sim_res_novar1$strain_parameter$initial_state
-sim_res_highvar1 <- run_simulation(parameter)
-saveRDS(sim_res_highvar1, here("experiments/experiment 1/data/sim_res_highvar1.RDS"))
-```
-
-```{r}
-sim_res_highvar1 <- readRDS(here("experiments/experiment 1/data/sim_res_highvar1.RDS"))
-plot_dynamics(sim_res_highvar1)
-#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)
-
-```
-
-## Anoxic to oxic
-
-### No diversity
-
-```{r eval = eval_dynamics_flag}
-parameter$sim_duration <- 60000
-```
-
-```{r eval = eval_dynamics_flag}
-parameter$log10a_series <- c(-5, -3, -1, -1)
-parameter$strain_parameter <- var_expt$pars[[no_diversity]]
-parameter$strain_parameter$initial_state <- new_initial_state(
-  num_CB_strains,
-  num_PB_strains,
-  num_SB_strains,
-  values = "bush_ssfig3"
-)
-parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10/num_CB_strains
-sim_res_novar2 <- run_simulation(parameter)
-saveRDS(sim_res_novar2, here("experiments/experiment 1/data/sim_res_novar2.RDS"))
-```
-
-```{r}
-sim_res_novar2 <- readRDS(here("experiments/experiment 1/data/sim_res_novar2.RDS"))
-plot_dynamics(sim_res_novar2)
-#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
-```
-
-### With diversity
-
-```{r eval = eval_dynamics_flag}
-parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
-parameter$strain_parameter$initial_state <- sim_res_novar2$strain_parameter$initial_state
-sim_res_highvar2 <- run_simulation(parameter)
-saveRDS(sim_res_highvar2, here("experiments/experiment 1/data/sim_res_highvar2.RDS"))
-```
-
-```{r}
-sim_res_highvar2 <- readRDS(here("experiments/experiment 1/data/sim_res_highvar2.RDS"))
-plot_dynamics(sim_res_highvar2)
-#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)
-
-```
-
-## Anoxic to oxic to anoxic
-
-### No diversity
-
-```{r eval = eval_dynamics_flag}
-parameter$sim_duration <- 1000000
-```
-
-```{r eval = eval_dynamics_flag}
-parameter$minimum_abundances <- rep(100, 3)
-names(parameter$minimum_abundances) <- c("CB", "PB", "SB")
-```
-
-```{r eval = eval_dynamics_flag}
-parameter$log10a_series <- c(-1, -8, -1)
-parameter$strain_parameter <- var_expt$pars[[no_diversity]]
-parameter$strain_parameter$initial_state <- new_initial_state(
-  num_CB_strains,
-  num_PB_strains,
-  num_SB_strains,
-  values = "bush_ssfig3"
-)
-parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10/num_CB_strains
-sim_res_novar3 <- run_simulation(parameter)
-saveRDS(sim_res_novar3, here("experiments/experiment 1/data/sim_res_novar3.RDS"))
-```
-
-```{r}
-sim_res_novar3 <- readRDS(here("experiments/experiment 1/data/sim_res_novar3.RDS"))
-plot_dynamics(sim_res_novar3)
-#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
-```
-
-### With diversity
-
-```{r eval = eval_dynamics_flag}
-parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
-parameter$strain_parameter$initial_state <- sim_res_novar3$strain_parameter$initial_state
-sim_res_highvar3 <- run_simulation(parameter)
-saveRDS(sim_res_highvar3, here("experiments/experiment 1/data/sim_res_highvar3.RDS"))
-```
-
-```{r}
-sim_res_highvar3 <- readRDS(here("experiments/experiment 1/data/sim_res_highvar3.RDS"))
-plot_dynamics(sim_res_highvar3)
-#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)
-
-```
-
-### Ecosystem-environment relationship
-
-```{r eval = FALSE, echo = FALSE}
-visualise_temporal_env_eco(sim_res_novar3, sim_res_highvar3)
-```
-
-# Stable state finding
-
-## Finding
-
-### Setup parameter
+## Setup parameter
 
@@
 options(mc.cores = 7)
-```
 
-```{r}
 minimum_abundances <- rep(0, 3)
@@
   event_definition = parameter$event_definition,
-  event_interval = 1000000,
+  event_interval = 100000,
   noise_sigma = parameter$noise_sigma,
   minimum_abundances = minimum_abundances,
-  sim_duration = 1000000,
-  sim_sample_interval = 1000000,
+  sim_duration = 100000,  ##    Was 1e6
+  sim_sample_interval = 100000,
   log10a_series = parameter$log10a_series,
@@
 
-saveRDS(parameter, here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS"))
-saveRDS(var_expt, here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial.RDS"))
+saveRDS(parameter, here("experiments/checks_puzzles/data/parameter_1e5_x2x6_factorial.RDS"))
+saveRDS(var_expt, here("experiments/checks_puzzles/data/var_expt_1e5_x2x6_factorial.RDS"))
 ```
@@
 run_ss_var_experiment(
-  parameter = readRDS(here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS")), 
-  var_expt = readRDS(here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial.RDS"))) %>%
-saveRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS"))
+  parameter = readRDS(here("experiments/checks_puzzles/data/parameter_1e5_x2x6_factorial.RDS")), 
+  var_expt = readRDS(here("experiments/checks_puzzles/data/var_expt_1e5_x2x6_factorial.RDS"))) %>%
+saveRDS(here("experiments/checks_puzzles/data/ss_data_1e6_x2x5_factorial.RDS"))
 ```
@@
 ## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
-readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_small.RDS")) %>%
-  mutate(sim_length = 1000000) %>% 
+readRDS(here("experiments/checks_puzzles/data/ss_data_1e5_x2x6_factorial.RDS")) %>%
+  mutate(sim_length = 100000) %>% 
   multidplyr::partition(cluster) %>%
@@
   unnest(cols = c(stability_measures)) %>%
-  saveRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial_small.RDS"))
+  saveRDS(here("experiments/checks_puzzles/data/stab_data_1e5_x2x6_factorial.RDS"))
 ```
 
-```{r}
-## find various combinations of diversity
-var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS"))
-stab_data <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
-
-var_expt_levels <- var_expt[,1:6]
-
-no_diversity <- which(rowSums(abs(var_expt_levels))==0)
-max_diversty_all <- which(max(rowSums(abs(var_expt_levels))) ==
-                            rowSums(abs(var_expt_levels)))
-max_only_CB_diversity <- which(max(rowSums(abs(var_expt_levels[,1:2]))) ==
-                            rowSums(abs(var_expt_levels[,1:2])) &
-                              rowSums(abs(var_expt_levels[,3:6]))==0)
-#var_expt_levels[381,]
-
-max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
-                            rowSums(abs(var_expt_levels[,3:6])) &
-                              rowSums(abs(var_expt_levels[,1:2]))==0)
-#var_expt_levels[20,]
-
-medium_diverity_varexp_row <- 311
-
-```
-
-### Display results
-
-```{r}
-
-p1  <- plot_ss_result1(var_expt,
-                result_index = no_diversity,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p1
-
-#junk1 <- var_expt[no_diversity,]$ss_res[[1]]
-```
-
-```{r}
-
-p2  <- plot_ss_result1(var_expt,
-                result_index = max_diversty_all,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p2
-
-```
-
-```{r}
-
-p3  <- plot_ss_result1(var_expt,
-                result_index = max_only_CB_diversity,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p3
-
-```
-
-```{r}
-
-p4  <- plot_ss_result1(var_expt,
-                result_index = max_only_SBPB_diversity,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p4
-
-```
-
-```{r}
-p_overlay1 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
-                             var_expt[max_diversty_all,]$ss_res[[1]],
-                             xlims = c(-7, -1))
-p_overlay1
-```
-
-```{r}
-p_overlay2 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
-                             var_expt[max_only_CB_diversity,]$ss_res[[1]],
-                             xlims = c(-7, -1))
-p_overlay2
-
-#ss_result1 <- var_expt[no_diversity,]$ss_res[[1]]
-#ss_result2 <- var_expt[max_only_CB_diversity,]$ss_res[[1]]
-
-```
-
-```{r}
-p_overlay3 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
-                             var_expt[max_only_SBPB_diversity,]$ss_res[[1]],
-                             xlims = c(-7, -1))
-p_overlay3
-
-#ss_result3 <- var_expt[max_only_SBPB_diversity,]$ss_res[[1]]
-
-```
-
-```{r}
-tempp1 <- var_expt[no_diversity,]$ss_res[[1]] %>%
-  filter(initial_N_CB == 1e10,
-         log10(a_O) > -4.5, log10(a_O) < -4)
-tempp2 <- var_expt[max_only_SBPB_diversity,]$ss_res[[1]] %>%
-  filter(initial_N_CB == 1e10,
-         log10(a_O) > -4.5, log10(a_O) < -4)
-
-ggplot() +
-  geom_line(mapping = aes(x = log10(tempp1$a_O),
-                          y = log10(tempp1$O))) +
-  geom_line(mapping = aes(x = log10(tempp2$a_O),
-                          y = log10(tempp2$O)),
-            col = "blue")
-
-ggplot() +
-  geom_histogram(mapping = aes(x = log10(tempp1$O) - log10(tempp2$O)),
-            col = "blue")
-
-ggplot() +
-  geom_line(mapping = aes(x = log10(tempp1$a_O),
-    y = log10(tempp1$P) - log10(tempp2$P)),
-            col = "blue")
-
-```
-
-```{r}
-CB_vars <- unique(stab_data$CB_var_gmax_s)
-SB_vars <- unique(stab_data$SB_var_gmax_s)
-
-CB_stab_data <- stab_data %>%
-  filter(SB_var_gmax_s == 0) %>%
-  mutate(var_treat = "CB",
-         var_gmax = CB_var_gmax_s)
-
-SBPB_stab_data <- stab_data %>%
-  filter(CB_var_gmax_s == 0) %>%
-  mutate(var_treat = "SB-PB",
-         var_gmax = SB_var_gmax_s)
-
-for_join <- tibble(CB_var_gmax_s = CB_vars,
-                     SB_var_gmax_s = SB_vars)
-CBSBPB_stab_data <- stab_data %>%
-  right_join(for_join) %>%
-  mutate(var_treat = "CB-SB-PB",
-         var_gmax = CB_var_gmax_s)
-
-all_stab_results <- CB_stab_data %>%
-  bind_rows(SBPB_stab_data) %>%
-#  bind_rows(results3) %>%
- # bind_rows(results4) %>%
-  bind_rows(CBSBPB_stab_data)
-
-all_stab_results <- all_stab_results %>%
-    mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB-PB", "CB-SB-PB")))
-
-#saveRDS(all_stab_results, here("experiments/experiment summary/all_stab.RDS"))
-
-#all_stab_results <- readRDS(here("experiments/experiment summary/all_stab.RDS"))
-```
-
-### Raw
-```{r}
-all_stab_results %>%
-  filter(Species == "O") %>%
-  ggplot(aes(x = var_gmax, y = hyst_range_raw, col=var_treat, shape = as_factor(sim_length))) +
-  geom_point() +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
-  labs(col = "Variation in\nonly these\nfunctional groups")
-##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)
-
-all_stab_results %>%
-  #filter(var_treat == "CB") %>%
-  filter(Species == "O",
-         sim_length == 1e6) %>%
-  ggplot(aes(x = var_gmax,
-             ymin = hyst_min_raw,
-             ymax = hyst_max_raw,
-             fill=var_treat)) +
-  geom_ribbon(alpha = 0.5) +
-  facet_wrap( ~ var_treat, nrow = 3) +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
-  labs(fill = "Variation in\nonly these\nfunctional groups") +
-  coord_flip() +
-  theme(
-    strip.background = element_blank(),
-    strip.text.x = element_blank()
-  )
-
-##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
-stab_data %>%
-  filter(Species == "O",
-         sim_length == 1e6) %>%
-  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range_raw, col = hyst_range_raw)) +
-  geom_point(size = 3)
-
-##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
-
-stab_data %>%
-  filter(Species == "O",
-         sim_length == 1e6) %>%
-  ggplot(aes(x = CB_var_gmax_s, y = hyst_range_raw, col = as.factor(SB_var_gmax_s))) +
-  geom_line(size = 2)
-```
-
-### Log transformed
-
-```{r}
-all_stab_results %>%
-  filter(Species == "O") %>%
-  ggplot(aes(x = var_gmax, y = hyst_range_log, col=var_treat, shape = as_factor(sim_length))) +
-  geom_point() +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
-  labs(col = "Variation in\nonly these\nfunctional groups")
-##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)
-
-all_stab_results %>%
-  #filter(var_treat == "CB") %>%
-  filter(Species == "O",
-         sim_length == 1e6) %>%
-  ggplot(aes(x = var_gmax,
-             ymin = hyst_min_log,
-             ymax = hyst_max_log,
-             fill=var_treat)) +
-  geom_ribbon(alpha = 0.5) +
-  facet_wrap( ~ var_treat, nrow = 3) +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
-  labs(fill = "Variation in\nonly these\nfunctional groups") +
-  coord_flip() +
-  theme(
-    strip.background = element_blank(),
-    strip.text.x = element_blank()
-  )
-
-##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
-stab_data %>%
-  filter(Species == "O",
-         sim_length == 1e6) %>%
-  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range_log, col = hyst_range_log)) +
-  geom_point(size = 3)
-
-##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
-
-stab_data %>%
-  filter(Species == "O",
-         sim_length == 1e6) %>%
-  ggplot(aes(x = CB_var_gmax_s, y = hyst_range_log, col = as.factor(SB_var_gmax_s))) +
-  geom_line(size = 2)
-```
-
-# FROM HERE NOT CHANGED TO NEW FORMAT!!!!!!
-# Some puzzles
-
-## What effect of changing the length of the simulations
-No Experimental data.
-
 ```{r, eval = FALSE, echo = FALSE}
-var_expt1 <- readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS"))
-var_expt2 <- readRDS(here("experiments/experiment 1/data/ss_data_80000.RDS"))
+var_expt1 <- readRDS(here("experiments/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
+var_expt2 <- readRDS(here("experiments/checks_puzzles/data/ss_data_1e5_x2x6_factorial.RDS"))
 
@@
 
-## Puzzle 1
+# Puzzle 1
 
@@
 ```{r}
-var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS"))
+#var_expt <- readRDS(here("experiments/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
 var_expt_levels <- var_expt[,1:6]
@@
 ```{r eval = eval_dynamics_flag}
-parameter <- readRDS(here("experiments/experiment 1/data/sim_res_novar3.RDS"))
+parameter <- parameter_master
+parameter$strain_parameter <- var_expt[no_diversity,]$pars[[1]]
 parameter$sim_duration <- 100000
 parameter$result <- NULL
-```
-
-```{r eval = eval_dynamics_flag}
 parameter$log10a_series <- c(-4.8, -4.8)
@@
 sim_res_novar1 <- run_simulation(parameter)
-saveRDS(sim_res_novar1, here("experiments/experiment 1/data/puzzle1_1.RDS"))
+saveRDS(sim_res_novar1, here("experiments/checks_puzzles/data/puzzle1_1.RDS"))
 ```
@@
 ```{r, eval = FALSE, echo = FALSE}
-sim_res_novar1 <- readRDS(here("experiments/experiment 1/data/puzzle1_1.RDS"))
+sim_res_novar1 <- readRDS(here("experiments/checks_puzzles/data/puzzle1_1.RDS"))
 plot_dynamics(sim_res_novar1)
@@
 ```{r eval = FALSE, echo = FALSE}
-sim_res_novar1 <- run_simulation(parameter_values = var_expt$pars[[max_only_SBPB_diversity]],
-                          initial_state = initial_state)
-saveRDS(sim_res_novar1, here("experiments/experiment 1/data/puzzle1_2.RDS"))
+parameter$strain_parameter <- var_expt[max_only_SBPB_diversity,]$pars[[1]]
+#parameter$sim_duration <- 100000
+#parameter$result <- NULL
+#parameter$log10a_series <- c(-5.2, -5.2)
+#parameter$strain_parameter$initial_state <- new_initial_state(
+#  nrow(parameter$strain_parameter$CB),
+#  nrow(parameter$strain_parameter$PB),
+#  nrow(parameter$strain_parameter$PB),
+#  values = "bush_ssfig3"
+#)
+parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/nrow(parameter$strain_parameter$CB)
+sim_res_highvar1 <- run_simulation(parameter)
+saveRDS(sim_res_highvar1, here("experiments/checks_puzzles/data/puzzle1_2.RDS"))
 ```
@@
 ```{r, eval = FALSE, echo = FALSE}
-sim_res_novar1 <- readRDS(here("experiments/experiment 1/data/puzzle1_2.RDS"))
-plot_dynamics(sim_res_novar1)
+sim_res_highvar1 <- readRDS(here("experiments/checks_puzzles/data/puzzle1_2.RDS"))
+plot_dynamics(sim_res_highvar1)
 #ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
@@
 #var_expt <- run_ss_var_experiment()
-#saveRDS(var_expt, here("experiments/experiment 1/data/ss_data_zoom.RDS"))
+#saveRDS(var_expt, here("experiments/checks_puzzles/data/ss_data_zoom.RDS"))
 ```
@@
 library(here)
-zoom <- readRDS(here("experiments/experiment 1/data/ss_data_zoom.RDS"))
+zoom <- readRDS(here("experiments/checks_puzzles/data/ss_data_zoom.RDS"))
 

### 2021-11-25 experiments/0_ss_finding/report.Rmd
added temporal SS finding, and reorganise

---
title: "SS finding report"
author: "Owen Petchey"
date: "11/25/2021"
output: html_document
---

```{r}
library(microxanox)
library(tidyverse)

source(here("R/various_useful_functions.r"))

ss_9s <- readRDS(here("experiments/0_ss_finding/data/9_strain_SS_data.RDS"))
stab_9s <- readRDS(here("experiments/0_ss_finding/data/9_strain_stab_data.RDS"))

```

```{r}
plot_ss_result3(ss_9s, 1)
plot_ss_result3(ss_9s, 2)
plot_ss_result4(ss_9s, 1, 2)
```

```{r}
## Test plot stability

CB_vars <- unique(stab_9s$CB_var_gmax_s)
SB_vars <- unique(stab_9s$SB_var_gmax_s)

CB_stab_9s <- stab_9s %>%
  filter(SB_var_gmax_s == 0) %>%
  mutate(var_treat = "CB",
         var_gmax = CB_var_gmax_s)

SBPB_stab_9s <- stab_9s %>%
  filter(CB_var_gmax_s == 0) %>%
  mutate(var_treat = "SB-PB",
         var_gmax = SB_var_gmax_s)

for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
                   SB_var_gmax_s = sort(SB_vars))
CBSBPB_stab_9s <- stab_9s %>%
  right_join(for_join) %>%
  mutate(var_treat = "CB-SB-PB",
         var_gmax = CB_var_gmax_s)

all_stab_results <- CB_stab_9s %>%
  bind_rows(SBPB_stab_9s) %>%
  #  bind_rows(results3) %>%
  # bind_rows(results4) %>%
  bind_rows(CBSBPB_stab_9s)

all_stab_results <- all_stab_results %>%
  mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB-PB", "CB-SB-PB")))
```

```{r}
all_stab_results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax, y = hyst_range_log, col=var_treat)) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)
```

```{r}
all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax,
             ymin = hyst_min_log,
             ymax = hyst_max_log,
             fill=var_treat)) +
  geom_ribbon(alpha = 0.5) +
  facet_wrap( ~ var_treat, nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )

```

### 2021-11-25 experiments/find discont/find discont.Rmd
added temporal SS finding, and reorganise

--- 2021-11-13 experiments/3_strains/3_strains.Rmd
@@
+---
+title: "find discont"
+author: "Owen Petchey"
+date: "11/15/2021"
+output: html_document
+---
 ---
@@
 
-# Temporal switching
-
-```{r}
-## Here we get some rows of var_expt that correspond with particular diversity levels
-
-var_expt_levels <- var_expt[, 1:6]
-
-no_diversity <- which(rowSums(abs(var_expt_levels)) == 0)
-max_diversty_all <- which(
-  max(rowSums(abs(var_expt_levels))) == rowSums(abs(var_expt_levels))
-)
-max_only_CB_diversity <- which(
-  max(rowSums(abs(var_expt_levels[, 1:2]))) == rowSums(abs(var_expt_levels[, 1:2])) &
-  rowSums(abs(var_expt_levels[,3:6])) == 0
-)
-# var_expt_levels[381,]
-
-max_only_SBPB_diversity <- which(
-  max(rowSums(abs(var_expt_levels[, 3:6]))) == rowSums(abs(var_expt_levels[, 3:6])) &
-  rowSums(abs(var_expt_levels[, 1:2])) == 0
-)
-#var_expt_levels[20,]
-
-medium_diverity_varexp_row <- 311
-
-```
-
-## Oxic to anoxic
-
-### No diversity
-
 ```{r eval = eval_dynamics_flag}
-parameter$sim_duration <- 80000
-```
-
-```{r eval = eval_dynamics_flag}
-parameter$log10a_series <- c(-1, -7, -7)
+parameter$sim_duration <- 8000
+parameter$sim_sample_interval <- parameter$sim_duration
+parameter$log10a_series <- c(-4, -4)
 parameter$strain_parameter <- var_expt$pars[[no_diversity]]
@@
 )
-parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/num_CB_strains
+
+get_final_oxygen <- function(x) {
+  parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10 ^ (x) /
+    num_CB_strains
   sim_res_novar1 <- run_simulation(parameter)
-saveRDS(sim_res_novar1, here("experiments/3_strains/data/sim_res_novar1.RDS"))
-```
+  temp <- sim_res_novar1$result$O
+  temp[length(temp)]
+}
+get_final_oxygen(1)
+get_final_oxygen(2)
+get_final_oxygen(3)
+get_final_oxygen(4)
+get_final_oxygen(5)
+get_final_oxygen(6)
+get_final_oxygen(7)
+get_final_oxygen(8)
+get_final_oxygen(9)
+get_final_oxygen(10)
 
-```{r}
-sim_res_novar1 <- readRDS(here("experiments/3_strains/data/sim_res_novar1.RDS"))
-plot_dynamics(sim_res_novar1)
-#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
-```
-
-### With diversity
-
-```{r eval = eval_dynamics_flag}
-parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
-parameter$strain_parameter$initial_state <- sim_res_novar1$strain_parameter$initial_state
-sim_res_highvar1 <- run_simulation(parameter)
-saveRDS(sim_res_highvar1, here("experiments/3_strains/data/sim_res_highvar1.RDS"))
-```
-
-```{r}
-sim_res_highvar1 <- readRDS(here("experiments/3_strains/data/sim_res_highvar1.RDS"))
-plot_dynamics(sim_res_highvar1)
-#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)
+parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^1/num_CB_strains
+sim_res_novar1 <- run_simulation(parameter)
+sim_res_novar1$result$O
 
 ```
-
-## Anoxic to oxic
-
-### No diversity
-
-```{r eval = eval_dynamics_flag}
-parameter$sim_duration <- 60000
-```
-
-```{r eval = eval_dynamics_flag}
-parameter$log10a_series <- c(-5, -3, -1, -1)
-parameter$strain_parameter <- var_expt$pars[[no_diversity]]
-parameter$strain_parameter$initial_state <- new_initial_state(
-  num_CB_strains,
-  num_PB_strains,
-  num_SB_strains,
-  values = "bush_ssfig3"
-)
-parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10/num_CB_strains
-sim_res_novar2 <- run_simulation(parameter)
-saveRDS(sim_res_novar2, here("experiments/3_strains/data/sim_res_novar2.RDS"))
-```
-
-```{r}
-sim_res_novar2 <- readRDS(here("experiments/3_strains/data/sim_res_novar2.RDS"))
-plot_dynamics(sim_res_novar2)
-#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
-```
-
-### With diversity
-
-```{r eval = eval_dynamics_flag}
-parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
-parameter$strain_parameter$initial_state <- sim_res_novar2$strain_parameter$initial_state
-sim_res_highvar2 <- run_simulation(parameter)
-saveRDS(sim_res_highvar2, here("experiments/3_strains/data/sim_res_highvar2.RDS"))
-```
-
-```{r}
-sim_res_highvar2 <- readRDS(here("experiments/3_strains/data/sim_res_highvar2.RDS"))
-plot_dynamics(sim_res_highvar2)
-#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)
-
-```
-
-## Anoxic to oxic to anoxic
-
-### No diversity
-
-```{r eval = eval_dynamics_flag}
-parameter$sim_duration <- 1000000
-```
-
-```{r eval = eval_dynamics_flag}
-parameter$minimum_abundances <- rep(100, 3)
-names(parameter$minimum_abundances) <- c("CB", "PB", "SB")
-```
-
-```{r eval = eval_dynamics_flag}
-parameter$log10a_series <- c(-1, -8, -1)
-parameter$strain_parameter <- var_expt$pars[[no_diversity]]
-parameter$strain_parameter$initial_state <- new_initial_state(
-  num_CB_strains,
-  num_PB_strains,
-  num_SB_strains,
-  values = "bush_ssfig3"
-)
-parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10/num_CB_strains
-sim_res_novar3 <- run_simulation(parameter)
-saveRDS(sim_res_novar3, here("experiments/3_strains/data/sim_res_novar3.RDS"))
-```
-
-```{r}
-sim_res_novar3 <- readRDS(here("experiments/3_strains/data/sim_res_novar3.RDS"))
-plot_dynamics(sim_res_novar3)
-#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
-```
-
-### With diversity
-
-```{r eval = eval_dynamics_flag}
-parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
-parameter$strain_parameter$initial_state <- sim_res_novar3$strain_parameter$initial_state
-sim_res_highvar3 <- run_simulation(parameter)
-saveRDS(sim_res_highvar3, here("experiments/3_strains/data/sim_res_highvar3.RDS"))
-```
-
-```{r}
-sim_res_highvar3 <- readRDS(here("experiments/3_strains/data/sim_res_highvar3.RDS"))
-plot_dynamics(sim_res_highvar3)
-#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)
-
-```
-
-### Ecosystem-environment relationship
-
-```{r eval = FALSE, echo = FALSE}
-visualise_temporal_env_eco(sim_res_novar3, sim_res_highvar3)
-```
-
-# Stable state finding
-
-## Finding
-
-### Setup parameter
-
-```{r}
-options(mc.cores = 7)
-```
-
-```{r}
-minimum_abundances <- rep(0, 3)
-names(minimum_abundances) <- c("CB", "PB", "SB")
-
-grid_num_a <- 1000 #usually 1000 ## number of a_0 values
-#grid_num_a <- 10 ## FOR TEST
-a_Os <- 10^seq(-7, -0.5, length=grid_num_a) ## sequence of a_0 values
-grid_num_N <- 2 ## number of N values
-initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
-initial_PBs <- 1e8 ## not varied
-initial_SBs <- 1e8 ## not varied
-# next line creates all possible combinations
-ss_expt <- expand.grid(N_CB = initial_CBs,
-                      N_PB = initial_PBs,
-                      N_SB = initial_SBs,
-                      a_O = a_Os)
-
-parameter <- new_ss_by_a_N_parameter(
-  dynamic_model = parameter$dynamic_model,
-  event_definition = parameter$event_definition,
-  event_interval = 1000000,
-  noise_sigma = parameter$noise_sigma,
-  minimum_abundances = minimum_abundances,
-  sim_duration = 1000000,
-  sim_sample_interval = 1000000,
-  log10a_series = parameter$log10a_series,
-  solver_method = parameter$solver_method,
-  ss_expt = ss_expt
-)
-rm(minimum_abundances, grid_num_a, a_Os, grid_num_N, initial_CBs, initial_PBs, initial_SBs, ss_expt)
-
-saveRDS(parameter, here("experiments/3_strains/data/parameter_1e6_x2x6_factorial.RDS"))
-saveRDS(var_expt, here("experiments/3_strains/data/var_expt_1e6_x2x6_factorial.RDS"))
-```
-
-### Run stable state finding
-
-*Careful, this simulation takes about 600 hours on a single core
-
-```{r run_experiment, eval = eval_dynamics_flag}
-run_ss_var_experiment(
-  parameter = readRDS(here("experiments/3_strains/data/parameter_1e6_x2x6_factorial.RDS")), 
-  var_expt = readRDS(here("experiments/3_strains/data/var_expt_1e6_x2x6_factorial.RDS"))) %>%
-saveRDS(here("experiments/3_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
-```
-
-### Process the stable state data
-
-Bring in various stable state datasets
-```{r eval = eval_dynamics_flag}
-cluster <- multidplyr::new_cluster(7)
-multidplyr::cluster_library(cluster, c("microxanox", "dplyr"))
-
-## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
-readRDS(here("experiments/3_strains/data/ss_data_1e6_x2x6_factorial_small.RDS")) %>%
-  mutate(sim_length = 1000000) %>% 
-  multidplyr::partition(cluster) %>%
-  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
-  collect() %>%
-  unnest(cols = c(stability_measures)) %>%
-  saveRDS(here("experiments/3_strains/data/stab_data_1e6_x2x6_factorial_small.RDS"))
-```
-
-```{r}
-## find various combinations of diversity
-var_expt <- readRDS(here("experiments/3_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
-stab_data <- readRDS(here("experiments/3_strains/data/stab_data_1e6_x2x6_factorial.RDS"))
-
-var_expt_levels <- var_expt[,1:6]
-
-no_diversity <- which(rowSums(abs(var_expt_levels))==0)
-max_diversty_all <- which(max(rowSums(abs(var_expt_levels))) ==
-                            rowSums(abs(var_expt_levels)))
-max_only_CB_diversity <- which(max(rowSums(abs(var_expt_levels[,1:2]))) ==
-                            rowSums(abs(var_expt_levels[,1:2])) &
-                              rowSums(abs(var_expt_levels[,3:6]))==0)
-#var_expt_levels[381,]
-
-max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
-                            rowSums(abs(var_expt_levels[,3:6])) &
-                              rowSums(abs(var_expt_levels[,1:2]))==0)
-#var_expt_levels[20,]
-
-medium_diverity_varexp_row <- 311
-
-```
-
-### Display results
-
-```{r eval = plot_ss_results}
-
-p1  <- plot_ss_result1(var_expt,
-                result_index = no_diversity,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p1
-
-p2  <- plot_ss_result1(var_expt,
-                result_index = max_diversty_all,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p2
-
-p3  <- plot_ss_result1(var_expt,
-                result_index = max_only_CB_diversity,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p3
-
-p4  <- plot_ss_result1(var_expt,
-                result_index = max_only_SBPB_diversity,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p4
-
-p_overlay1 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
-                             var_expt[max_diversty_all,]$ss_res[[1]],
-                             xlims = c(-7, -1))
-p_overlay1
-
-p_overlay2 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
-                             var_expt[max_only_CB_diversity,]$ss_res[[1]],
-                             xlims = c(-7, -1))
-p_overlay2
-
-p_overlay3 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
-                             var_expt[max_only_SBPB_diversity,]$ss_res[[1]],
-                             xlims = c(-7, -1))
-p_overlay3
-
-```
-
-```{r eval = plot_ss_results}
-tempp1 <- var_expt[no_diversity,]$ss_res[[1]] %>%
-  filter(initial_N_CB == 1e10,
-         log10(a_O) > -4.5, log10(a_O) < -4)
-tempp2 <- var_expt[max_only_SBPB_diversity,]$ss_res[[1]] %>%
-  filter(initial_N_CB == 1e10,
-         log10(a_O) > -4.5, log10(a_O) < -4)
-
-ggplot() +
-  geom_line(mapping = aes(x = log10(tempp1$a_O),
-                          y = log10(tempp1$O))) +
-  geom_line(mapping = aes(x = log10(tempp2$a_O),
-                          y = log10(tempp2$O)),
-            col = "blue")
-
-ggplot() +
-  geom_histogram(mapping = aes(x = log10(tempp1$O) - log10(tempp2$O)),
-            col = "blue")
-
-ggplot() +
-  geom_line(mapping = aes(x = log10(tempp1$a_O),
-    y = log10(tempp1$P) - log10(tempp2$P)),
-            col = "blue")
-
-```
-
-```{r eval = plot_ss_results}
-CB_vars <- unique(stab_data$CB_var_gmax_s)
-SB_vars <- unique(stab_data$SB_var_gmax_s)
-
-CB_stab_data <- stab_data %>%
-  filter(SB_var_gmax_s == 0) %>%
-  mutate(var_treat = "CB",
-         var_gmax = CB_var_gmax_s)
-
-SBPB_stab_data <- stab_data %>%
-  filter(CB_var_gmax_s == 0) %>%
-  mutate(var_treat = "SB-PB",
-         var_gmax = SB_var_gmax_s)
-
-for_join <- tibble(CB_var_gmax_s = CB_vars,
-                     SB_var_gmax_s = SB_vars)
-CBSBPB_stab_data <- stab_data %>%
-  right_join(for_join) %>%
-  mutate(var_treat = "CB-SB-PB",
-         var_gmax = CB_var_gmax_s)
-
-all_stab_results <- CB_stab_data %>%
-  bind_rows(SBPB_stab_data) %>%
-#  bind_rows(results3) %>%
- # bind_rows(results4) %>%
-  bind_rows(CBSBPB_stab_data)
-
-all_stab_results <- all_stab_results %>%
-    mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB-PB", "CB-SB-PB")))
-
-#saveRDS(all_stab_results, here("experiments/experiment summary/all_stab.RDS"))
-
-#all_stab_results <- readRDS(here("experiments/experiment summary/all_stab.RDS"))
-```
-
-### Raw
-```{r eval = plot_ss_results}
-all_stab_results %>%
-  filter(Species == "O") %>%
-  ggplot(aes(x = var_gmax, y = hyst_range_raw, col=var_treat, shape = as_factor(sim_length))) +
-  geom_point() +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
-  labs(col = "Variation in\nonly these\nfunctional groups")
-##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)
-
-all_stab_results %>%
-  #filter(var_treat == "CB") %>%
-  filter(Species == "O",
-         sim_length == 1e6) %>%
-  ggplot(aes(x = var_gmax,
-             ymin = hyst_min_raw,
-             ymax = hyst_max_raw,
-             fill=var_treat)) +
-  geom_ribbon(alpha = 0.5) +
-  facet_wrap( ~ var_treat, nrow = 3) +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
-  labs(fill = "Variation in\nonly these\nfunctional groups") +
-  coord_flip() +
-  theme(
-    strip.background = element_blank(),
-    strip.text.x = element_blank()
-  )
-
-##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
-stab_data %>%
-  filter(Species == "O",
-         sim_length == 1e6) %>%
-  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range_raw, col = hyst_range_raw)) +
-  geom_point(size = 3)
-
-##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
-
-stab_data %>%
-  filter(Species == "O",
-         sim_length == 1e6) %>%
-  ggplot(aes(x = CB_var_gmax_s, y = hyst_range_raw, col = as.factor(SB_var_gmax_s))) +
-  geom_line(size = 2)
-```
-
-### Log transformed
-
-```{r eval = plot_ss_results}
-all_stab_results %>%
-  filter(Species == "O") %>%
-  ggplot(aes(x = var_gmax, y = hyst_range_log, col=var_treat, shape = as_factor(sim_length))) +
-  geom_point() +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
-  labs(col = "Variation in\nonly these\nfunctional groups")
-##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)
-
-all_stab_results %>%
-  #filter(var_treat == "CB") %>%
-  filter(Species == "O",
-         sim_length == 1e6) %>%
-  ggplot(aes(x = var_gmax,
-             ymin = hyst_min_log,
-             ymax = hyst_max_log,
-             fill=var_treat)) +
-  geom_ribbon(alpha = 0.5) +
-  facet_wrap( ~ var_treat, nrow = 3) +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
-  labs(fill = "Variation in\nonly these\nfunctional groups") +
-  coord_flip() +
-  theme(
-    strip.background = element_blank(),
-    strip.text.x = element_blank()
-  )
-
-##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
-stab_data %>%
-  filter(Species == "O",
-         sim_length == 1e6) %>%
-  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range_log, col = hyst_range_log)) +
-  geom_point(size = 3)
-
-##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
-
-stab_data %>%
-  filter(Species == "O",
-         sim_length == 1e6) %>%
-  ggplot(aes(x = CB_var_gmax_s, y = hyst_range_log, col = as.factor(SB_var_gmax_s))) +
-  geom_line(size = 2)
-```

### 2021-11-25 manuscript/article.Rmd
added temporal SS finding, and reorganise

@@
 
-The model ecosystem contains three types (functional groups) of organism (Figure \ref(fig:ecosys_network)): cyanobacteria ($CB$), sulfate-reducing bacteria ($SB$), and phototrophic sulfur bacteria ($PB$), four chemical substrates (oxygen $O$, phosphorous $P$, reduced sulfur $SR$, and oxidised sulfur $SO$), and four types of flow/interaction (production, consumption, inhibition, and diffusion).
+The model ecosystem contains three types (functional groups) of organism (Figure \@ref(fig:ecosys_network)): cyanobacteria ($CB$), sulfate-reducing bacteria ($SB$), and phototrophic sulfur bacteria ($PB$), four chemical substrates (oxygen $O$, phosphorous $P$, reduced sulfur $SR$, and oxidised sulfur $SO$), and four types of flow/interaction (production, consumption, inhibition, and diffusion).
 Particularly important among these interactions are that the cyanobacteria produce oxygen which inhibits the growth of both types of sulfur bacteria.

### 2021-11-25 supplement/supplement.Rmd
added temporal SS finding, and reorganise

---
title: Supplementary Content
subtitle: Functional diversity ... Predictions of a model of an oxic-anoxic microbial ecosystem 
authors:
  - name: Owen L Petchey
    department: Department of Evolutionary Biology and Environmental Studies
    affiliation: University of Zurich
    location: Zurich 8057, Switzerland
    email: owen.petchey@ieu.uzh.ch
  - name: Rainer Krug
    department: Department of Evolutionary Biology and Environmental Studies
    affiliation: University of Zurich
    location: Zurich 8057, Switzerland
    email: rainer.krug@ieu.uzh.ch
  - name: Any Others
    department: Department of Evolutionary Biology and Environmental Studies
    affiliation: University of Zurich
    location: Zurich 8057, Switzerland
    email: any.others@ieu.uzh.ch
  - name: Marcel Suleiman
    department: Department of Evolutionary Biology and Environmental Studies
    affiliation: University of Zurich
    location: Zurich 8057, Switzerland
    email: marcel.suleiman@ieu.uzh.ch

bibliography: references.bib
biblio-style: unsrt
output: 
  rticles::arxiv_article:
    keep_tex: true
---

```{r include = FALSE}
knitr::opts_chunk$set(include = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE)
```

```{r}
library(tidyverse)
library(microxanox)
library(patchwork)
library(here)
source(here("r/various_useful_functions.r"))
```

# Introduction

...

# Robustness of stable state finding

We now discuss two approaches for finding how the stable state of the system varies along the gradient of oxygen diffusivity when there exists the possibility of multiple stable states. In the main article we report results of the method also described there. Briefly here, we made a separate simulations for each of many values of oxygen diffusivity, ran the simulations for long enough to ensure transients had passed, and recorded the state. We ran multiple simulations per value of oxygen diffusivity, and started them with different initial conditions (either low or high total cyanobacterial abundance), so as to check for presence of alternate stable states. This method used by [Bush et al 2017](https://www.nature.com/articles/s41467-017-00912-x). We hereafter term this "the replication method", since it is effectively achieved by having many independent replicates of the ecosystem, each with a different oxygen diffusivity, and also a separate replicate for each of the different chosen initial conditions.

Here we report the results of a second method. We will show some quantitative differences in results compared to the other method, but also show the results concerning diversity effects are qualitatively the same as obtained with the first method.

The second method involves two simulations for a particular system configuration (parameter set). In one simulation the oxygen diffusivity is *increased* in a step-wise fashion. In the other it is *decreased* in a step-wise fashion. That is, oxygen diffusivity is held at a constant level for long enough for steady state to be reach, that state is recorded, and then a slightly higher (or lower) oxygen diffusivity value is set. Hence, at that time point, the system is effectively started with initial conditions that are the state of the system in the previous time step. We hereafter term this "the temporal method".

The temporal method results in a larger region of bistability than the replication method (Figure \@ref(fig:tempmeth1)). That is, a greater extent of environmental change is required to switch the system to the other state (i.e. the region of bistability is greater). This occurs both during increasing and decreasing oxygen diffusivities. The difference in results occurs because, as mentioned above, the initial conditions differ between the two approaches. For example, in the temporal method, the oxygen concentration in the anoxic state is lower than the initial oxygen concentration in the replication approach, and **Owen guesses that** the sulfide concentration is higher **check that last statement**.

```{r fig_tempmeth1, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Steady state of the system found with the replication method and the temporal method, both with no within functional group diversity."), echo=FALSE}
var_expt <- readRDS(here("experiments/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
no_div_res <- readRDS(here("experiments/9_strains/data/no_div_temporal_ss.RDS"))
## To be completed.
plot_ss_result1(var_expt,
                result_index = 1,
                filename_prefix = NULL,
                save_image_file = FALSE)
ss_result1 <- var_expt$ss_res[[1]] %>%
     mutate(time = NA,
            direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  select(names(no_div_res$all_res))

plot_ss_result3(no_div_res)

plot_ss_result4(ss_result1, 
                no_div_res$all_res,
                xlims = c(-8, 0))
```

Although the temporal method reveals a larger extent of bistability, it also reveals that the effect of increasing functional diversity are the same as those revealed by the replication method:

* Introducing functional diversity in all three functional groups increases the region of bistability relative to when there is no diversity within all functional groups (Figure \@ref(fig:tempmeth2)).
* Introducing functional diversity in only the cyanobacteria function group delays (with respect to the oxygen diffusivity it occurs at) the switch to the anoxic state as oxygen diffusivity is reduced, but has no effect on the oxygen diffusivity at which the anoxic to oxic transition occurs (Figure \@ref(fig:tempmeth3)).
* Introducing function diversity in only the sulfur bacteria delays (with respect to the oxygen diffusivity it occurs at) the switch from anoxic to oxic, and advances the switch from oxic to anoxic (Figure \@ref(fig:tempmeth4).

```{r}
no_div_res <- readRDS(here("experiments/9_strains/data/no_div_temporal_ss.RDS"))
medium_div_res <- readRDS(here("experiments/9_strains/data/medium_div_temporal_ss.RDS"))
medium_divCB_res <- readRDS(here("experiments/9_strains/data/medium_divCB_temporal_ss.RDS"))
medium_divSBPB_res <- readRDS(here("experiments/9_strains/data/medium_divSBPB_temporal_ss.RDS"))
```

```{r tempmeth2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Effect of introducing functional diversity in all functional groups on steady state of the system found with the temporal method."), echo=FALSE}
plot_ss_result4(no_div_res$all_res,
                medium_div_res$all_res,
                xlims = c(-8, 0))
```

```{r tempmeth3, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Effect of introducing functional diversity in only the cyanobacteria functional group on steady state of the system found with the temporal method."), echo=FALSE}
plot_ss_result4(no_div_res$all_res,
                medium_divCB_res$all_res,
                xlims = c(-8, 0))

```

```{r tempmeth4, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Effect of introducing functional diversity in only the sulfur bacteria functional group on steady state of the system found with the temporal method."), echo=FALSE}
plot_ss_result4(no_div_res$all_res,
                medium_divSBPB_res$all_res,
                xlims = c(-8, 0))

```

# Strain richness effect in temporal version

```{r}

no_div_res9 <- readRDS(here("experiments/9_strains/data/no_div_temporal_ss.RDS"))
medium_div_res9 <- readRDS(here("experiments/9_strains/data/medium_div_temporal_ss.RDS"))
medium_divCB_res9 <- readRDS(here("experiments/9_strains/data/medium_divCB_temporal_ss.RDS"))
medium_divSBPB_res9 <- readRDS(here("experiments/9_strains/data/medium_divSBPB_temporal_ss.RDS"))
```

# Finding the separatrix

In the original publication ([Bush et al 2017])(https://www.nature.com/articles/s41467-017-00912-x) Figure 3a shows a separatrix in the cyanobacteria abundance dimension of the system. If the system has initial cyanobacterial abundance greater than the value at the separatrix then the cyanobacterial abundance increases, and the system goes to the oxic stable state. Conversely, if the system has initial cyanobacterial abundance greater than the value at the separatrix then the cyanobacterial abundance decreases, and the system goes to the anoxic stable state.

It is critical to note, however, that the position of the separatrix depends on both the parameters of the system, and the initial conditions of variables other than cyanobacterial abundance. If the system were started with higher initial concentration, then the position of the separatrix would change (as would the values of oxygen diffusivity at which the system tipped from anoxic to oxic, and from oxic to anoxic).

This issue of dependence of the position of the separatrix on the value of initial condition of multiple state variables has particular significance when there are multiple strains per functional group. Then one cannot just vary initial total cyanobacterial abundance (as was done to create the separatrix on Figure 3a in the original publication) but one must also define how the initial abundance of each of the strains varies. One might choose to make each strain have equal initial abundance, and to vary the total (as we did in our implementation of the replication method in the main article).

We could, however, and arguably should, give the most tolerant strain of cyanobacteria higher initial relative abundance when total initial cyanobacterial abundance was low, and the least tolerant strain higher initial relative abundance when total cyanobacterial abundance was high. And we would need to specify the total and relative abundance of all cyanobacteria (and sulfur bactria) strains. Thus, with a system as complex as the 9 strain system, which has 31 state variables the separatrix is very high dimensional, and evaluating (and plotting) it in one dimension requires many assumption. We chose to not attempt to find a meaningful set of assumptions in this study, though not because we think it would be unprofitable to do so, but rather because we did not want to risk distracting attention from findings we consider to be significant enough in the own right.

# Effects of number of strains revealed by the replication method

**Some relevant text is in the main article... check there.** One must choose and additive design or substitutive, or something else.

# Effects of number of strains revealed y the temporal method.

Show counter-intuitive result.

Explain by showing dynamics, and what happens when different initial conditions are used, e.g. a higher O2 concentration similar as in the temporal method.

# Bibliography

### 2021-11-25 R/various_useful_functions.r

@@ -1,4 +1,59 @@
 
+setup_R <- function() {
+  
+  
+  # rm(list = ls())
+  
+  knitr::opts_knit$set(
+    progress = TRUE, 
+    verbose = FALSE, 
+    cache = TRUE
+  )
+  
+  microxanox_release <- "0.3.1"
+  
+  #tmplib <- tempfile()
+  #dir.create(tmplib)
+  
+  
+  ### From '?remotes::install_github`:
+  # auth_token
+  #   To install from a private repo, generate a personal access token (PAT) in
+  #   "https://github.com/settings/tokens" and supply to this argument. This is
+  #   safer than using a password because you can easily delete a PAT without
+  #   affecting any others. Defaults to the GITHUB_PAT environment variable.
+  
+  # remotes::install_github(
+  #   "opetchey/microxanox",
+  #   ref = microxanox_release,
+  #   # auth_token = "ENTER YOUR TOKEN or PROVED AS ENVIRONMENT VARIABLE",
+  #   build_vignettes = FALSE,
+  #   force = TRUE,
+  #   upgrade = FALSE,
+  #   lib = tmplib
+  # )
+  
+  #library(microxanox, lib.loc = tmplib)
+  
+  library(microxanox)
+  if (packageVersion("microxanox") < package_version("0.3.0")) {
+    stop("microxanox version needs to be at least 0.3.0!")
+  }
+  library(tidyverse)
+  library(patchwork)
+  library(here)
+  source(here("R/various_useful_functions.r"))
+  zero <- 0 ## don't change
+  unity <- 1 ## don't change!!!
+  options(mc.cores = 7)
+  eval_dynamics_flag <- FALSE
+  plot_ss_results <- TRUE
+  
+}
+
+
+
+
 
 
 run_ss_var_experiment <- function(parameter, var_expt) {
@@ -550,3 +605,367 @@ visualise_temporal_env_eco <- function(sim_res_novar = NULL, sim_res_highvar = N
     ggtitle("Black line is with no diversity.\nRed line is with diversity")
   ## ggsave(here("simulations/figures/switching_comparison.pdf"), width = 5, height = 4)
 }
+
+
+
+plot_ss_result3 <- function(temporal_ss_result,
+                            this_one,
+                            filename_prefix = NA,
+                            save_image_file = FALSE) {
+  
[…]

### 2021-11-25 experiments/0_ss_finding/run_experiment.R

@@ -1,0 +1,52 @@
+## SS finding experiment
+## 
+## 
+
+
+rm(list = ls())
+library(here)
+source(here("R/various_useful_functions.r"))
+
+num_strains <- 9
+num_CB_strains <- num_strains
+num_SB_strains <- num_strains
+num_PB_strains <- num_strains
+
+source(here("experiments/0_ss_finding/setup_experiment.R"))
+
+
+## Get SS
+var_expt <- var_expt[1:2,]
+expt_res <- run_temporal_ssfind_experiment(parameter,
+                                           var_expt,
+                                           total_initial_abundances = total_initial_abundances,
+                                           cores = 1)
+saveRDS(expt_res, here("experiments/0_ss_finding/data/", paste0(num_strains, "_strain_SS_data.RDS")))
+
+
+## Get stability
+expt_res <- readRDS(here("experiments/0_ss_finding/data/", paste0(num_strains, "_strain_SS_data.RDS")))
+cluster1 <- multidplyr::new_cluster(2)
+multidplyr::cluster_library(cluster1, c("microxanox", "dplyr"))
+stab_data <-  expt_res_single %>%
+  multidplyr::partition(cluster1) %>%
+  mutate(stability_measures = list(get_stability_measures_new(ssfind_result))) %>%
+  collect() %>%
+  unnest(cols = c(stability_measures)) 
+saveRDS(stab_data, here("experiments/0_ss_finding/data/", paste0(num_strains, "_strain_stab_data.RDS")))
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2021-11-25 experiments/0_ss_finding/setup_experiment.R

@@ -1,0 +1,124 @@
+
+# rm(list = ls())
+
+knitr::opts_knit$set(
+  progress = TRUE, 
+  verbose = FALSE, 
+  cache = TRUE
+)
+
+microxanox_release <- "0.3.1"
+
+#tmplib <- tempfile()
+#dir.create(tmplib)
+
+
+### From '?remotes::install_github`:
+# auth_token
+#   To install from a private repo, generate a personal access token (PAT) in
+#   "https://github.com/settings/tokens" and supply to this argument. This is
+#   safer than using a password because you can easily delete a PAT without
+#   affecting any others. Defaults to the GITHUB_PAT environment variable.
+
+# remotes::install_github(
+#   "opetchey/microxanox",
+#   ref = microxanox_release,
+#   # auth_token = "ENTER YOUR TOKEN or PROVED AS ENVIRONMENT VARIABLE",
+#   build_vignettes = FALSE,
+#   force = TRUE,
+#   upgrade = FALSE,
+#   lib = tmplib
+# )
+
+#library(microxanox, lib.loc = tmplib)
+
+library(microxanox)
+if (packageVersion("microxanox") < package_version("0.3.0")) {
+  stop("microxanox version needs to be at least 0.3.0!")
+}
+library(tidyverse)
+library(patchwork)
+library(here)
+source(here("R/various_useful_functions.r"))
+zero <- 0 ## don't change
+unity <- 1 ## don't change!!!
+options(mc.cores = 7)
+eval_ss_flag <- FALSE
+plot_ss_results <- TRUE
+
+
+
+sp <- new_strain_parameter(
+  n_CB = num_CB_strains,
+  n_PB = num_SB_strains,
+  n_SB = num_PB_strains,
+  values_initial_state = "bush_ssfig3"
+)
+
+parameter <- new_runsim_parameter(
+  dynamic_model = bushplus_dynamic_model,
+  event_definition = event_definition_1,
+  event_interval = 100,
+  noise_sigma = 0,
+  minimum_abundances = rep(1, 3),
+  sim_duration = 2000,
+  sim_sample_interval = 100,
+  strain_parameter = sp,
+  log10a_series = c(
+    log10(sp$a_O),
+    log10(sp$a_O)
+  )
+)
+names(parameter$minimum_abundances) <- c("CB", "PB", "SB")
+rm(sp)
+
[…]

### 2021-11-25 experiments/experiment old/experiment summary/summarise.R

@@ -1,85 +1,0 @@
-rm(list = ls())
-
-library(here)
-library(tidyverse)
-library(microxanox)
-
-CBSBPB_data <- readRDS(here("experiments/experiment 1/data/ss_data.RDS"))
-CB_data <- readRDS(here("experiments/experiment 2/data/ss_data.RDS"))
-SBPB_data <- readRDS(here("experiments/experiment 3/data/ss_data.RDS"))
-
-
-
-CBSBPB_stab_data <- CBSBPB_data %>%
-  group_by(CB_var_gmax_s, CB_var_h_s,
-           SB_var_gmax_s, SB_var_h_s,
-           PB_var_gmax_s, PB_var_h_s) %>%
-  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
-results1 <- unnest(CBSBPB_stab_data, cols = c(stability_measures)) %>%
-  mutate(var_treat = "CB-SB-PB",
-         var_gmax = CB_var_gmax_s)
-
-CB_stab_data <- CB_data %>%
-  group_by(CB_var_gmax_s, CB_var_h_s,
-           SB_var_gmax_s, SB_var_h_s,
-           PB_var_gmax_s, PB_var_h_s) %>%
-  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
-results2 <- unnest(CB_stab_data, cols = c(stability_measures))  %>%
-  mutate(var_treat = "CB",
-         var_gmax = CB_var_gmax_s)
-
-
-SBPB_stab_data <- SBPB_data %>%
-  group_by(CB_var_gmax_s, CB_var_h_s,
-           SB_var_gmax_s, SB_var_h_s,
-           PB_var_gmax_s, PB_var_h_s) %>%
-  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
-results5 <- unnest(SBPB_stab_data, cols = c(stability_measures))  %>%
-  mutate(var_treat = "SB-PB",
-         var_gmax = SB_var_gmax_s)
-
-
-all_stab_results <- results1 %>%
-  bind_rows(results2) %>%
-#  bind_rows(results3) %>%
- # bind_rows(results4) %>%
-  bind_rows(results5)
-
-all_stab_results<- all_stab_results %>%
-    mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB-PB", "CB-SB-PB")))
[…]

### 2021-11-26 experiments/0_ss_finding/Error_Test.Rmd
Error isolation and solution steps

---
title: "Test Error"
author: "Rainer M Krug"
date: "11/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  eval = TRUE,
  echo = TRUE,
  error = TRUE,
  messages = TRUE
)

library(here)
source(here("R/various_useful_functions.r"))

num_strains <- 9
num_CB_strains <- num_strains
num_SB_strains <- num_strains
num_PB_strains <- num_strains

source(here("experiments/0_ss_finding/setup_experiment.R"))

## Get SS
var_expt <- var_expt[1:2,]

```

## Load the old data

```{r load}
c1 <- readRDS("~/Documents_Local/git/diversity_envresp1/experiments/0_ss_finding/data/1c_9_strain_SS_data.RDS")
c6 <- readRDS("~/Documents_Local/git/diversity_envresp1/experiments/0_ss_finding/data/6c_9_strain_SS_data.RDS")
```

## The error

```{r error1}
c1 %>% mutate(stability_measures = list(get_stability_measures_new(ssfind_result)))
c6 %>% mutate(stability_measures = list(get_stability_measures_new(ssfind_result)))
```

## Further digging
```{r error2}
c1["ssfind_result"] %>% mutate(stability_measures = list(get_stability_measures_new(ssfind_result)))
c6["ssfind_result"] %>% mutate(stability_measures = list(get_stability_measures_new(ssfind_result)))
```

## Check the attributes
```{r}
attributes(c1["ssfind_result"])
attributes(c6["ssfind_result"])
```

The single core result is a `rowwise_df`, while the multicore is not.

## Fix
Add the `%>% rowwise()` to the function `run_temporal_ssfind_experiment()` inm the microxanox package and regenerate the data (in separate script)

## Load the new data

```{r loadNew}
c1_r <- readRDS("~/Documents_Local/git/diversity_envresp1/experiments/0_ss_finding/data/1c_rowwise_9_strain_SS_data.RDS")
c6_r <- readRDS("~/Documents_Local/git/diversity_envresp1/experiments/0_ss_finding/data/6c_rowwise_9_strain_SS_data.RDS")
```

## Now working

```{r Fixed}
c1_r %>% mutate(stability_measures = list(get_stability_measures_new(ssfind_result)))
c6_r %>% mutate(stability_measures = list(get_stability_measures_new(ssfind_result)))
```

### 2021-11-26 experiments/0_ss_finding/report.Rmd
various

@@
 author: "Owen Petchey"
-date: "11/25/2021"
+date: "`r format(Sys.time(), '%d %B, %Y')`"
 output: html_document
 ---
+
+```{r echo = FALSE}
+knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
+```
 
@@
 library(tidyverse)
+library(patchwork)
+library(here)
 
@@
 plot_ss_result3(ss_9s, 1)
-plot_ss_result3(ss_9s, 2)
-plot_ss_result4(ss_9s, 1, 2)
+plot_ss_result3(ss_9s, 8)
+plot_ss_result4(ss_9s, 1, 8)
 ```

### 2021-11-26 experiments/0_ss_finding/run_experiment.R

@@ -16,19 +16,19 @@ source(here("experiments/0_ss_finding/setup_experiment.R"))
 
 
 ## Get SS
-var_expt <- var_expt[1:2,]
-no_cores = 1
+#var_expt <- var_expt[1:8,]
+num_cores = 12
 expt_res <- run_temporal_ssfind_experiment(parameter,
                                            var_expt,
                                            total_initial_abundances = total_initial_abundances,
-                                           cores = no_cores)
-saveRDS(expt_res, here("experiments/0_ss_finding/data/", paste0(no_cores, "c_rowwise_", num_strains, "_strain_SS_data.RDS")))
+                                           cores = num_cores)
+saveRDS(expt_res, here("experiments/0_ss_finding/data/", paste0(num_strains, "_strain_SS_data.RDS")))
 
 
 ## Get stability
-no_cores = 6
-expt_res <- readRDS(here("experiments/0_ss_finding/data/", paste0(no_cores, "c_rowwise_", num_strains, "_strain_SS_data.RDS")))
-cluster1 <- multidplyr::new_cluster(1)
+num_cores = 12
+expt_res <- readRDS(here("experiments/0_ss_finding/data/", paste0(num_strains, "_strain_SS_data.RDS")))
+cluster1 <- multidplyr::new_cluster(num_cores)
 multidplyr::cluster_library(cluster1, c("microxanox", "dplyr"))
 stab_data <-  expt_res %>%
   multidplyr::partition(cluster1) %>%

### 2021-11-28 experiments/0_ss_finding/report.Rmd
updates

@@
 
+ss_2s <- readRDS(here("experiments/0_ss_finding/data/2_strain_SS_data.RDS"))
+stab_2s <- readRDS(here("experiments/0_ss_finding/data/2_strain_stab_data.RDS")) %>%
+  mutate(num_strains = 2)
+ss_3s <- readRDS(here("experiments/0_ss_finding/data/3_strain_SS_data.RDS"))
+stab_3s <- readRDS(here("experiments/0_ss_finding/data/3_strain_stab_data.RDS")) %>%
+  mutate(num_strains = 3)
+ss_6s <- readRDS(here("experiments/0_ss_finding/data/6_strain_SS_data.RDS"))
+stab_6s <- readRDS(here("experiments/0_ss_finding/data/6_strain_stab_data.RDS")) %>%
+  mutate(num_strains = 6)
 ss_9s <- readRDS(here("experiments/0_ss_finding/data/9_strain_SS_data.RDS"))
-stab_9s <- readRDS(here("experiments/0_ss_finding/data/9_strain_stab_data.RDS"))
+stab_9s <- readRDS(here("experiments/0_ss_finding/data/9_strain_stab_data.RDS")) %>%
+  mutate(num_strains = 9)
+
+all_stab <- stab_2s %>%
+  bind_rows(stab_3s) %>%
+  bind_rows(stab_6s) %>%
+  bind_rows(stab_9s)
 
@@
 plot_ss_result3(ss_9s, 1)
-plot_ss_result3(ss_9s, 8)
-plot_ss_result4(ss_9s, 1, 8)
+plot_ss_result3(ss_9s, 13)
+plot_ss_result4(ss_9s, 1, 13)
+
+plot_ss_result3(ss_3s, 1)
+plot_ss_result3(ss_3s, 13)
+plot_ss_result4(ss_3s, 1, 13)
+
+plot_ss_result5(ss_2s, 15,
+                ss_9s, 15)
+plot_ss_result5(ss_3s, 15,
+                ss_9s, 15)
+plot_ss_result5(ss_6s, 15,
+                ss_9s, 15)
+
+```
+
+```{r}
+## Test plot stability
+
+CB_vars <- unique(all_stab$CB_var_gmax_s)
+SB_vars <- unique(all_stab$SB_var_gmax_s)
+
+CB_all_stab <- all_stab %>%
+  filter(SB_var_gmax_s == 0) %>%
+  mutate(var_treat = "CB",
+         var_gmax = CB_var_gmax_s)
+
+SBPB_all_stab <- all_stab %>%
+  filter(CB_var_gmax_s == 0) %>%
+  mutate(var_treat = "SB-PB",
+         var_gmax = SB_var_gmax_s)
+
+for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
+                   SB_var_gmax_s = sort(SB_vars))
+CBSBPB_all_stab <- all_stab %>%
+  right_join(for_join) %>%
+  mutate(var_treat = "CB-SB-PB",
+         var_gmax = CB_var_gmax_s)
+
+all_stab_results <- CB_all_stab %>%
+  bind_rows(SBPB_all_stab) %>%
+  #  bind_rows(results3) %>%
+  # bind_rows(results4) %>%
+  bind_rows(CBSBPB_all_stab)
+
+all_stab_results <- all_stab_results %>%
+  mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB-PB", "CB-SB-PB")))
+
+all_stab_results_small <- select(all_stab_results, -7:-12)
+```
+
+```{r}
+all_stab_results %>%
+  filter(Species == "O") %>%
+  ggplot(aes(x = var_gmax, y = hyst_range_log, col=var_treat, shape = as.factor(num_strains))) +
+  geom_point() +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
+  labs(col = "Variation in\nonly these\nfunctional groups")
+##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)
+```
+
+```{r}
+all_stab_results %>%
+  #filter(var_treat == "CB") %>%
+  filter(Species == "O") %>%
+  ggplot(aes(x = var_gmax,
+             ymin = hyst_min_log,
+             ymax = hyst_max_log,
+             fill=var_treat)) +
+  geom_ribbon(alpha = 0.5) +
+  facet_grid(num_strains ~ var_treat, scales = "free_y") +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
+  labs(fill = "Variation in\nonly these\nfunctional groups") +
+  coord_flip() +
+  theme(
+    strip.background = element_blank(),
+    strip.text.x = element_blank()
+  )
+
+```
+
+```{r}
+all_stab_results %>%
+  #filter(var_treat == "CB") %>%
+  filter(Species == "O") %>%
+  ggplot(aes(x = var_gmax,
+             col = as.factor(num_strains))) +
+  geom_line(aes(y = hyst_min_log)) +
+  geom_line(aes(y = hyst_max_log)) +
+  facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
+  labs(fill = "Variation in\nonly these\nfunctional groups") +
+  coord_flip() +
+  theme(
+    #strip.background = element_blank(),
+    #strip.text.x = element_blank()
+  )
+
 ```

### 2021-11-28 R/various_useful_functions.r

@@ -835,6 +835,120 @@ plot_ss_result4 <- function(temporal_ss_result,
 }
 
 
+
+
+
+plot_ss_result5 <- function(temporal_ss_result1,
+                            first_one,
+                            temporal_ss_result2,
+                            second_one,
+                            xlims = c(-8, 0)) {
+  
+  species_colours <- c(CB = "#024F17", SB = "#7D1402", PB = "#6E0172")
+  
+  # colfunc_CB <- colorRampPalette(c("#024F17", "#B5FFC9"))
+  # colfunc_SB <- colorRampPalette(c("#7D1402", "#FCBEB3"))
+  # colfunc_PB <- colorRampPalette(c("#6E0172", "#F9AEFC"))
+  
+  #ss_result1 <- filter(ss_result1, if_all(contains("B_"), ~ (.x > -1)))
+  
+  ss_result1 <- temporal_ss_result1$ssfind_result[[first_one]]
+  ss_result2 <- temporal_ss_result2$ssfind_result[[second_one]]
+  
+  
+  temp1 <- ss_result1 %>%
+    mutate(
+      #direction = ifelse(initial_N_CB == 1, "up", "down"),
+      a = 10^a_O
+    ) %>%
+    gather(species, quantity, 2:(ncol(.) - 2)) %>%
+    mutate(
+      var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
+      functional_group = case_when(
+        str_detect(species, "CB_") ~ "CB",
+        str_detect(species, "SB_") ~ "SB",
+        str_detect(species, "PB_") ~ "PB"
+      ),
+      functional_group = ifelse(is.na(functional_group), species, functional_group)
+    ) %>%
+    group_by(a, direction, var_type, functional_group) %>%
+    summarise(total_quantity = sum(quantity, na.rm = TRUE)) %>%
+    mutate(log10_total_quantity = log10(total_quantity + 1))
+  
+  #ss_result2 <- filter(ss_result2, if_all(contains("B_"), ~ (.x > -1)))
+  
+  temp2 <- ss_result2 %>%
+    mutate(
+      #direction = ifelse(initial_N_CB == 1, "up", "down"),
+      a = 10^a_O
+    ) %>%
+    gather(species, quantity, 2:(ncol(.) - 2)) %>%
+    mutate(
+      var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
[…]

### 2021-11-28 experiments/0_ss_finding/run_experiment.R

@@ -7,7 +7,7 @@ rm(list = ls())
 library(here)
 source(here("R/various_useful_functions.r"))
 
-num_strains <- 9
+num_strains <- 6
 num_CB_strains <- num_strains
 num_SB_strains <- num_strains
 num_PB_strains <- num_strains
@@ -16,12 +16,20 @@ source(here("experiments/0_ss_finding/setup_experiment.R"))
 
 #var_expt <- var_expt[1,]
 
+## Estimate time require
 nrow(var_expt)
 wait_time
 length(parameter$log10a_series)
-
-## Get SS
 num_cores = 12
+## constants in following formula come from the excel sheet
+time_estimate <- ( nrow(var_expt) * wait_time * length(parameter$log10a_series) /
+  num_cores * 0.000123965 + 126 )
+time_estimate
+time_estimate / 60 ## minutes
+time_estimate / 60 / 60 ## hours
+time_estimate / 60 / 60 / 24 ## days
+
+
 system.time({
 expt_res <- run_temporal_ssfind_experiment(parameter,
                                            var_expt,

### 2021-11-28 experiments/0_ss_finding/setup_experiment.R

@@ -87,7 +87,9 @@ SB_h_div <- -0.323  * SBPB_var_multiplier
 PB_gmax_div <- 0.015789474  * SBPB_var_multiplier
 PB_h_div <- -0.323  * SBPB_var_multiplier
 
-num_div_treatment_levels <- 5
+num_div_treatment_levels <- 20
+
+
 
 
 
@@ -109,7 +111,22 @@ var_expt <- create_diversity_factorial(
 )
 
 
-
+## some selection of treatments
+CB_vars <- unique(var_expt$CB_var_gmax_s)
+SB_vars <- unique(var_expt$SB_var_gmax_s)
+CB_var_expt <- var_expt %>%
+  filter(SB_var_gmax_s == 0)
+SBPB_var_expt <- var_expt %>%
+  filter(CB_var_gmax_s == 0)
+for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
+                   SB_var_gmax_s = sort(SB_vars))
+CBSBPB_var_expt <- var_expt %>%
+  right_join(for_join)
+var_expt_new <- CB_var_expt %>%
+  bind_rows(SBPB_var_expt) %>%
+  bind_rows(CBSBPB_var_expt) %>%
+  unique()
+var_expt <- var_expt_new
 
 
 wait_time <- 1e6

### 2021-12-14 experiments/0_ss_finding/replication_method/3_strains/3_strains.Rmd
lots

--- 2021-11-13 experiments/3_strains/3_strains.Rmd
@@
 ```{r}
-options(mc.cores = 7)
+options(mc.cores = 12)
 ```
@@
 #grid_num_a <- 10 ## FOR TEST
-a_Os <- 10^seq(-7, -0.5, length=grid_num_a) ## sequence of a_0 values
+a_Os <- 10^seq(-8, -0, length=grid_num_a) ## sequence of a_0 values
 grid_num_N <- 2 ## number of N values
@@
 saveRDS(parameter, here("experiments/3_strains/data/parameter_1e6_x2x6_factorial.RDS"))
-saveRDS(var_expt, here("experiments/3_strains/data/var_expt_1e6_x2x6_factorial.RDS"))
+
+var_expt_9strains <- readRDS(here("experiments/9_strains/data/var_expt_1e6_x2x6_factorial.RDS")) 
+unique_CBs <- unique(var_expt_9strains$CB_var_gmax_s)[c(1, 5, 10, 15, 20)]
+unique_SBs <- unique(var_expt_9strains$SB_var_gmax_s)[c(1, 5, 10, 15, 20)]
+var_expt_smaller <- var_expt %>%
+  filter(CB_var_gmax_s %in% unique_CBs & SB_var_gmax_s %in% unique_SBs)
+
+saveRDS(var_expt_smaller, here("experiments/3_strains/data/var_expt_1e6_x2x6_factorial.RDS"))
 ```
@@
 ```{r run_experiment, eval = eval_dynamics_flag}
+system.time(
 run_ss_var_experiment(
@@
   saveRDS(here("experiments/3_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
+)
 ```
@@
 ```{r eval = eval_dynamics_flag}
-cluster <- multidplyr::new_cluster(7)
+cluster <- multidplyr::new_cluster(12)
 multidplyr::cluster_library(cluster, c("microxanox", "dplyr"))
@@
 ## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
-readRDS(here("experiments/3_strains/data/ss_data_1e6_x2x6_factorial_small.RDS")) %>%
+readRDS(here("experiments/3_strains/data/ss_data_1e6_x2x6_factorial.RDS")) %>%
   mutate(sim_length = 1000000) %>% 
@@
   unnest(cols = c(stability_measures)) %>%
-  saveRDS(here("experiments/3_strains/data/stab_data_1e6_x2x6_factorial_small.RDS"))
+  saveRDS(here("experiments/3_strains/data/stab_data_1e6_x2x6_factorial.RDS"))
 ```
@@
 
-medium_diverity_varexp_row <- 311
+medium_diversity_varexp_row <- 12
 
@@
 
+p5  <- plot_ss_result1(var_expt,
+                result_index = medium_diversity_varexp_row,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+p5
+
 p_overlay1 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
@@
 p_overlay3
+
+p_overlay4 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
+                             var_expt[medium_diversity_varexp_row,]$ss_res[[1]],
+                             xlims = c(-7, -1))
+p_overlay4
 
@@
 
-for_join <- tibble(CB_var_gmax_s = CB_vars,
-                     SB_var_gmax_s = SB_vars)
+for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
+                     SB_var_gmax_s = sort(SB_vars))
 CBSBPB_stab_data <- stab_data %>%
@@
 ```
+
+# Stable state finding 2
+
+```{r eval = FALSE}
+rm(list = ls())
+library(here)
+library(tidyverse)
+library(microxanox)
+library(patchwork)
+source(here("R/various_useful_functions.r"))
+
+parameter = readRDS(here("experiments/3_strains/data/parameter_1e6_x2x6_factorial.RDS"))
+var_expt = readRDS(here("experiments/3_strains/data/var_expt_1e6_x2x6_factorial.RDS"))
+
+var_expt_levels_3s <- var_expt[,1:6]
+
+## here we choose the diversity of the system
+wait_time <- 100000
+parameter$log10a_series <- log10(sort(unique(parameter$ss_expt$a_O)))
+#parameter$log10a_series <- seq(-2.5, -2, 0.025)
+parameter$log10a_series <- seq(-8, 0, length = 100)
+
+no_diverity_varexp_row <- 1
+no_div_res <- get_ss_temporal_method(parameter, var_expt,
+                                     no_diverity_varexp_row,
+                                     wait_time)
+saveRDS(no_div_res, here("experiments/3_strains/data/no_div_temporal_ss.RDS"))
+
+medium_diverity_varexp_row <- 18
+medium_div_res <- get_ss_temporal_method(parameter, var_expt,
+                                     medium_diverity_varexp_row,
+                                     wait_time)
+saveRDS(medium_div_res, here("experiments/3_strains/data/medium_div_temporal_ss.RDS"))
+
+medium_diversity_onlyCB_varexp_row <- 16
+medium_divCB_res <- get_ss_temporal_method(parameter, var_expt,
+                                     medium_diversity_onlyCB_varexp_row,
+                                     wait_time)
+saveRDS(medium_divCB_res, here("experiments/3_strains/data/medium_divCB_temporal_ss.RDS"))
+
+medium_diversity_onlySBPB_varexp_row <- 3
+medium_divSBPB_res <- get_ss_temporal_method(parameter, var_expt,
+                                     medium_diversity_onlySBPB_varexp_row,
+                                     wait_time)
+saveRDS(medium_divSBPB_res, here("experiments/3_strains/data/medium_divSBPB_temporal_ss.RDS"))
+
+```
+
+```{r}
+no_div_res <- readRDS(here("experiments/3_strains/data/no_div_temporal_ss.RDS"))
+medium_div_res <- readRDS(here("experiments/3_strains/data/medium_div_temporal_ss.RDS"))
+medium_divCB_res <- readRDS(here("experiments/3_strains/data/medium_divCB_temporal_ss.RDS"))
+medium_divSBPB_res <- readRDS(here("experiments/3_strains/data/medium_divSBPB_temporal_ss.RDS"))
+
+plot_ss_result3(no_div_res)
+plot_ss_result3(medium_div_res)
+plot_ss_result3(medium_divCB_res)
+plot_ss_result3(medium_divSBPB_res)
+
+plot_ss_result4(no_div_res$all_res,
+                medium_div_res$all_res,
+                xlims = c(-8, 0))
+plot_ss_result4(no_div_res$all_res,
+                medium_divCB_res$all_res,
+                xlims = c(-8, 0))
+plot_ss_result4(no_div_res$all_res,
+                medium_divSBPB_res$all_res,
+                xlims = c(-8, 0))
+
+```

### 2021-12-14 experiments/0_ss_finding/replication_method/6_strains/6_strains.Rmd
lots

--- 2021-11-13 experiments/6_strains/6_strains.Rmd
@@
 author: "Owen Petchey"
-date: "6/25/2021"
+date: "`r format(Sys.time(), '%d %B, %Y')`"
 output:
@@
 unity <- 1 ## don't change!!!
-options(mc.cores = 7)
+options(mc.cores = 12)
 eval_dynamics_flag <- FALSE
@@
 #grid_num_a <- 10 ## FOR TEST
-a_Os <- 10^seq(-7, -0.5, length=grid_num_a) ## sequence of a_0 values
+a_Os <- 10^seq(-8, 0, length=grid_num_a) ## sequence of a_0 values
 grid_num_N <- 2 ## number of N values
@@
 saveRDS(parameter, here("experiments/6_strains/data/parameter_1e6_x2x6_factorial.RDS"))
-saveRDS(var_expt, here("experiments/6_strains/data/var_expt_1e6_x2x6_factorial.RDS"))
+
+var_expt_9strains <- readRDS(here("experiments/9_strains/data/var_expt_1e6_x2x6_factorial.RDS")) 
+unique_CBs <- unique(var_expt_9strains$CB_var_gmax_s)[c(1, 5, 10, 15, 20)]
+unique_SBs <- unique(var_expt_9strains$SB_var_gmax_s)[c(1, 5, 10, 15, 20)]
+var_expt_smaller <- var_expt %>%
+  filter(CB_var_gmax_s %in% unique_CBs & SB_var_gmax_s %in% unique_SBs)
+saveRDS(var_expt_smaller, here("experiments/6_strains/data/var_expt_1e6_x2x6_factorial.RDS"))
 ```
@@
 ## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
-readRDS(here("experiments/6_strains/data/ss_data_1e6_x2x6_factorial_small.RDS")) %>%
+readRDS(here("experiments/6_strains/data/ss_data_1e6_x2x6_factorial.RDS")) %>%
   mutate(sim_length = 1000000) %>% 
@@
   unnest(cols = c(stability_measures)) %>%
-  saveRDS(here("experiments/6_strains/data/stab_data_1e6_x2x6_factorial_small.RDS"))
+  saveRDS(here("experiments/6_strains/data/stab_data_1e6_x2x6_factorial.RDS"))
 ```
@@
 
-medium_diverity_varexp_row <- 311
+medium_diverity_varexp_row <- 12
 

### 2021-12-14 experiments/0_ss_finding/replication_method/9_strains/9_strains.Rmd
lots

--- 2021-11-13 experiments/9_strains/9_strains.Rmd
@@
 
-microxanox_release <- "0.3.0"
+microxanox_release <- "0.3.1"
 
@@
 eval_dynamics_flag <- FALSE
-plot_ss_results <- FALSE
+plot_ss_results <- TRUE
 ```
@@
 
-medium_diverity_varexp_row <- 311
+medium_diverity_varexp_row <- 290
 
@@
 var_expt <- readRDS(here("experiments/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
-stab_data <- readRDS(here("experiments/9_strains/data/stab_data_1e6_x2x6_factorial.RDS"))
+#stab_data <- readRDS(here("experiments/9_strains/data/stab_data_1e6_x2x6_factorial.RDS"))
+#stab_data_smaller <- stab_data %>%
+#  mutate(num_strains = 9) %>%
+#  select(1:6, 11:25)
+#saveRDS(stab_data_smaller, here("experiments/9_strains/data/small_stab_1e6_x2x6_factorial.RDS"))
+
+#var_expt$pars
+
+stab_data <- readRDS(here("experiments/9_strains/data/small_stab_data_1e6_x2x6_factorial.RDS"))
 
@@
 
+p_overlay4 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
+                             var_expt[medium_diverity_varexp_row,]$ss_res[[1]],
+                             xlims = c(-7, -1))
+p_overlay4
+
 ```
@@
 ```
+
+# Stable state finding 2
+
+```{r eval = FALSE}
+rm(list = ls())
+library(here)
+library(tidyverse)
+library(microxanox)
+library(patchwork)
+source(here("R/various_useful_functions.r"))
+
+parameter <- readRDS(here("experiments/9_strains/data/parameter_1e6_x2x6_factorial.RDS"))
+var_expt <- readRDS(here("experiments/9_strains/data/var_expt_1e6_x2x6_factorial.RDS"))
+parameter$ss_expt <- NA
+var_expt_levels <- var_expt[,1:6]
+
+wait_time <- 1000
+#p$log10a_series <- seq(-2.5, -2, 0.025)
+parameter$log10a_series <- seq(-8, 0, length = 10)
+parameter$minimum_abundances["CB"] <- 1
+parameter$minimum_abundances["SB"] <- 1
+parameter$minimum_abundances["PB"] <- 1
+parameter$event_interval <- 100
+parameter$sim_duration <- wait_time * length(parameter$log10a_series)
+parameter$sim_sample_interval <- wait_time
+```
+
+```{r eval = FALSE}
+## Here a test of one run
+no_diverity_varexp_row <- 1
+parameter$strain_parameter <- var_expt$pars[[no_diverity_varexp_row]]
+parameter <- set_temporal_ssfind_initial_state(parameter,
+                                               10^5,
+                                               10^5,
+                                               10^5)
+no_div_res <- run_temporal_ssfind_method(parameter)
+no_div_res
+```
+
+```{r eval = FALSE}
+## here a test of an expt run
+var_expt <- var_expt[1:2,]
+expt_res <- run_temporal_ssfind_experiment(parameter,
+                                           var_expt,
+                                           total_initial_abundances = 10^5)
+```
+
+```{r}
+## test the plotting functions
+plot_ss_result3(expt_res, 1)
+plot_ss_result3(expt_res, 2)
+expt_res$ssfind_result[[1]]
+
+temporal_ss_result <- expt_res
+temporal_ss_result$CB_var_gmax_s[[1]]
+```
+
+```{r eval = FALSE}
+saveRDS(no_div_res, here("experiments/9_strains/data/no_div_temporal_ss.RDS"))
+
+medium_diverity_varexp_row <- 290
+medium_div_res <- get_ss_temporal_method(parameter, var_expt,
+                                     medium_diverity_varexp_row,
+                                     wait_time)
+saveRDS(medium_div_res, here("experiments/9_strains/data/medium_div_temporal_ss.RDS"))
+
+medium_diversity_onlyCB_varexp_row <- 281
+medium_divCB_res <- get_ss_temporal_method(parameter, var_expt,
+                                     medium_diversity_onlyCB_varexp_row,
+                                     wait_time)
+saveRDS(medium_divCB_res, here("experiments/9_strains/data/medium_divCB_temporal_ss.RDS"))
+
+medium_diversity_onlySBPB_varexp_row <- 10
+medium_divSBPB_res <- get_ss_temporal_method(parameter, var_expt,
+                                     medium_diversity_onlySBPB_varexp_row,
+                                     wait_time)
+saveRDS(medium_divSBPB_res, here("experiments/9_strains/data/medium_divSBPB_temporal_ss.RDS"))
+
+```
+
+```{r}
+no_div_res <- readRDS(here("experiments/9_strains/data/no_div_temporal_ss.RDS"))
+medium_div_res <- readRDS(here("experiments/9_strains/data/medium_div_temporal_ss.RDS"))
+medium_divCB_res <- readRDS(here("experiments/9_strains/data/medium_divCB_temporal_ss.RDS"))
+medium_divSBPB_res <- readRDS(here("experiments/9_strains/data/medium_divSBPB_temporal_ss.RDS"))
+
+plot_ss_result3(no_div_res)
+plot_ss_result3(medium_div_res)
+plot_ss_result3(medium_divCB_res)
+plot_ss_result3(medium_divSBPB_res)
+
+plot_ss_result4(no_div_res$all_res,
+                medium_div_res$all_res,
+                xlims = c(-8, 0))
+plot_ss_result4(no_div_res$all_res,
+                medium_divCB_res$all_res,
+                xlims = c(-8, 0))
+plot_ss_result4(no_div_res$all_res,
+                medium_divSBPB_res$all_res,
+                xlims = c(-8, 0))
+
+```
+
+# testing ssfind_temporal method
+
+```{r eval = FALSE}
+rm(list = ls())
+library(here)
+library(tidyverse)
+library(microxanox)
+library(patchwork)
+source(here("R/various_useful_functions.r"))
+
+parameter = readRDS(here("experiments/9_strains/data/parameter_1e6_x2x6_factorial.RDS"))
+var_expt = readRDS(here("experiments/9_strains/data/var_expt_1e6_x2x6_factorial.RDS"))
+var_expt_levels <- var_expt[,1:6]
+
+wait_time <- 100000
+
+parameter$log10a_series <- log10(sort(unique(parameter$ss_expt$a_O)))
+#p$log10a_series <- seq(-2.5, -2, 0.025)
+parameter$log10a_series <- seq(-8, 0, length = 100)
+
+parameter$minimum_abundances["CB"] <- 1
+parameter$minimum_abundances["SB"] <- 1
+parameter$minimum_abundances["PB"] <- 1
+parameter$event_interval <- 100
+parameter$sim_duration <- wait_time * length(p$log10a_series)
+parameter$sim_sample_interval <- wait_time
+parameter$strain_parameter$initial_state <-
+
+#p$strain_parameter <- var_expt$pars[[this_diversity_treatment]]
+
+```
+
+```{r}
+run_temporal_ssfind_method <- function(p)
+```
+
+```{r}
+run_temporal_ssfind_experiment(parameter, var_expt)
+```

### 2021-12-14 experiments/0_ss_finding/temporal_method/report.Rmd
lots

--- 2021-11-28 experiments/0_ss_finding/report.Rmd
@@
 
+all_stab <- stab_9s
+
 ```
@@
 plot_ss_result3(ss_9s, 1)
-plot_ss_result3(ss_9s, 13)
-plot_ss_result4(ss_9s, 1, 13)
+plot_ss_result3(ss_9s, 15)
+plot_ss_result4(ss_9s, 1, 15)
 
 plot_ss_result3(ss_3s, 1)
-plot_ss_result3(ss_3s, 13)
-plot_ss_result4(ss_3s, 1, 13)
+plot_ss_result3(ss_3s, 15)
+plot_ss_result4(ss_3s, 1, 15)
 
@@
   geom_ribbon(alpha = 0.5) +
-  facet_grid(num_strains ~ var_treat, scales = "free_y") +
+  #facet_grid(num_strains ~ var_treat, scales = "fixed") +
+  facet_wrap( ~ var_treat, nrow = 3, scales = "fixed") +
   xlab("Amount of trait variation\n[see text for units]") +

### 2021-12-14 experiments/2_supplement/html_supplement.Rmd
lots

---
title: Supplementary Content
subtitle: Functional diversity ... Predictions of a model of an oxic-anoxic microbial ecosystem 
author: "Owen L Petchey, Rainer Krug, Marcel Suleiman, ???others???"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r include = FALSE, echo = FALSE}
knitr::opts_chunk$set(include = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      cache = TRUE)
```

```{r echo = FALSE}
rm(list = ls())
library(tidyverse)
library(microxanox)
library(patchwork)
library(here)
source(here("r/various_useful_functions.r"))
colfunc_CB <- colorRampPalette(c("#024F17", "#B5FFC9"))
colfunc_SB <- colorRampPalette(c("#7D1402", "#FCBEB3"))
colfunc_PB <- colorRampPalette(c("#6E0172", "#F9AEFC"))
zero <- 0
unity <- 1
```

# Introduction

This document contains the Supporting Content for the report *?????????????*.

# Visualising among strain diversity

The method for creating among strain diversity is explained in the main report. Here we show three visualisations, one for nine strains, one for three, and one for two.

In each, the top row of three graphs shows the diversity and tradeoff in each of the three functional groups. The most tolerant strain is always in the darker shade.The lower row of three graphs shows the relationship between realised growth rate as a function of the respective inhibiting substance, e.g. sulfide for the cyanobacteria. In these lower graphs only the least and most tolerant strains are shown. The lines cross due to the tradeoff shown in the upper graph. At high concentrations of the inhibiting substance the more tolerant strain has higher realised growth rate, while at lower concentrations it is the less tolerant strain that has the higher realised growth rate.

```{r  echo = FALSE}
CB_var_multiplier <- 2
SBPB_var_multiplier <- 6
CB_gmax_div <- 0.015789474 * CB_var_multiplier
CB_h_div <- -0.08 * CB_var_multiplier
SB_gmax_div <- 0.015789474 * SBPB_var_multiplier
SB_h_div <- -0.323  * SBPB_var_multiplier
PB_gmax_div <- 0.015789474  * SBPB_var_multiplier
PB_h_div <- -0.323  * SBPB_var_multiplier
num_div_treatment_levels <- 2
```

## Nine strains

```{r nine-strains, echo = FALSE}

num_CB_strains <- 9
num_PB_strains <- 9
num_SB_strains <- 9
var_expt <- create_diversity_factorial(
  zero = zero, unity = unity,
  num_div_treatment_levels = num_div_treatment_levels,
  CB_gmax_div = CB_gmax_div, CB_h_div = CB_h_div,
  SB_gmax_div = SB_gmax_div, SB_h_div = SB_h_div,
  PB_gmax_div = PB_gmax_div, PB_h_div = PB_h_div,
  default_9strain = new_strain_parameter(
    n_CB = num_CB_strains,
    n_SB = num_SB_strains,
    n_PB = num_PB_strains,
    values_initial_state =  "bush_ssfig3"
  )
)
display_diversity(4,
  var_expt = var_expt,
  num_CB_strains = num_CB_strains,
  num_SB_strains = num_SB_strains,
  num_PB_strains = num_PB_strains
)
```

## Three strains

```{r three-strains, echo = FALSE}

num_CB_strains <- 3
num_PB_strains <- 3
num_SB_strains <- 3
var_expt <- create_diversity_factorial(
  zero = zero, unity = unity,
  num_div_treatment_levels = num_div_treatment_levels,
  CB_gmax_div = CB_gmax_div, CB_h_div = CB_h_div,
  SB_gmax_div = SB_gmax_div, SB_h_div = SB_h_div,
  PB_gmax_div = PB_gmax_div, PB_h_div = PB_h_div,
  default_9strain = new_strain_parameter(
    n_CB = num_CB_strains,
    n_SB = num_SB_strains,
    n_PB = num_PB_strains,
    values_initial_state =  "bush_ssfig3"
  )
)
display_diversity(4,
  var_expt = var_expt,
  num_CB_strains = num_CB_strains,
  num_SB_strains = num_SB_strains,
  num_PB_strains = num_PB_strains
)
```

## Two strains

```{r two-strains, echo = FALSE}

num_CB_strains <- 2
num_PB_strains <- 2
num_SB_strains <- 2
var_expt <- create_diversity_factorial(
  zero = zero, unity = unity,
  num_div_treatment_levels = num_div_treatment_levels,
  CB_gmax_div = CB_gmax_div, CB_h_div = CB_h_div,
  SB_gmax_div = SB_gmax_div, SB_h_div = SB_h_div,
  PB_gmax_div = PB_gmax_div, PB_h_div = PB_h_div,
  default_9strain = new_strain_parameter(
    n_CB = num_CB_strains,
    n_SB = num_SB_strains,
    n_PB = num_PB_strains,
    values_initial_state =  "bush_ssfig3"
  )
)
display_diversity(4,
  var_expt = var_expt,
  num_CB_strains = num_CB_strains,
  num_SB_strains = num_SB_strains,
  num_PB_strains = num_PB_strains
)
```

# Robustness of stable state finding

We now discuss two approaches for finding how the stable state of the system varies along the gradient of oxygen diffusivity when there exists the possibility of multiple stable states. In the main article we describe and report results of the method that we term the *Temporal method*.

Here we also describe and give results of what we term the *Replication method*. In this, we made a separate simulations for each of many values of oxygen diffusivity, ran the simulations for long enough to ensure transients had passed, and recorded the state. We ran multiple simulations per value of oxygen diffusivity, and started them with different initial conditions (either low or high total cyanobacterial abundance), so as to check for presence of alternate stable states. This method used by [Bush et al 2017](https://www.nature.com/articles/s41467-017-00912-x). We term it the replication method since it is achieved by having many independent replicates of the ecosystem, each with a different oxygen diffusivity, and also a separate replicate for each of the different chosen initial conditions.

As is shown in the figures below, the temporal method results in a larger region of bistability than the replication method, but only during increasing oxygen diffusivities. The difference in results occurs because, as mentioned above, the initial conditions differ between the two approaches. For example, in the temporal method, the oxygen concentration in the anoxic state is lower than the initial oxygen concentration in the replication approach, and **Owen guesses that** the sulfide concentration is higher **check that last statement**.

## Replication method, no diversity

In the following graph, the solid (down) line refers to the stable state when cyanobacteria begin at high abundance (favouring the oxic state). The dashed up line refers to when their initial abundnace is low (favouring the anoxic state).Stable states found with the replication method. Please note: i) that near vertical lines indicate the position of a tipping point and hence the system cannot exist on point of that part of the line; ii) the separatrix (the unstable equilibrium) is not shown.

```{r repl_meth1, echo=FALSE}
repl_meth <- readRDS(here("experiments/0_ss_finding/replication_method/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
temp_meth <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_SS_data.RDS"))
## To be completed.
plot_ss_result1(repl_meth,
                result_index = 1,
                filename_prefix = NULL,
                save_image_file = FALSE)
```

## Temporal method, no diversity

Same as for the previous graph.

```{r temp_meth1, echo=FALSE}
plot_ss_result3(temp_meth, 1)
```

## Both methods overlaid, no diversity

Stable states of the two methods overlaid, the temporal method with a dashed line, and the replication method with a solid line.

```{r both_meth1, echo=FALSE}
repl_method_1 <- repl_meth$ss_res[[1]] %>%
     mutate(time = NA,
            direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  select(names(temp_meth$ssfind_result[[1]]))

ss_result1 <- repl_method_1
ss_result2 <- temp_meth$ssfind_result[[1]]

plot_ss_result6(repl_method_1,
                temp_meth$ssfind_result[[1]],
                xlims = c(-8, 0))
```

## Effect of diversity, replication method

The replication method shows the same effects of functional diversity as those revealed by the replication method:

-   Introducing functional diversity in all three functional groups increases the region of bistability relative to when there is no diversity within all functional groups).
-   Introducing functional diversity in only the cyanobacteria function group delays (with respect to the oxygen diffusivity it occurs at) the switch to the anoxic state as oxygen diffusivity is reduced, but has no effect on the oxygen diffusivity at which the anoxic to oxic transition occurs .
-   Introducing function diversity in only the sulfur bacteria delays (with respect to the oxygen diffusivity it occurs at) the switch from anoxic to oxic, and advances the switch from oxic to anoxic.

These results are shown in the figure below, which shows results of the replication method.

```{r echo = FALSE, eval = TRUE}
stab_data <- readRDS(here("experiments/0_ss_finding/replication_method/9_strains/data/small_stab_data_1e6_x2x6_factorial.RDS"))

all_stab <- stab_data

#all_stab <- stab_9s

CB_vars <- unique(all_stab$CB_var_gmax_s)
SB_vars <- unique(all_stab$SB_var_gmax_s)

CB_all_stab <- all_stab %>%
  filter(SB_var_gmax_s == 0) %>%
  mutate(var_treat = "CB",
         var_gmax = CB_var_gmax_s)

SBPB_all_stab <- all_stab %>%
  filter(CB_var_gmax_s == 0) %>%
  mutate(var_treat = "SB-PB",
         var_gmax = SB_var_gmax_s)

for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
                   SB_var_gmax_s = sort(SB_vars))
CBSBPB_all_stab <- all_stab %>%
  right_join(for_join) %>%
  mutate(var_treat = "CB-SB-PB",
         var_gmax = CB_var_gmax_s)

all_stab_results <- CB_all_stab %>%
  bind_rows(SBPB_all_stab) %>%
  #  bind_rows(results3) %>%
  # bind_rows(results4) %>%
  bind_rows(CBSBPB_all_stab)

all_stab_results <- all_stab_results %>%
  mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB-PB", "CB-SB-PB")))

```

```{r echo = FALSE, eval = TRUE}
all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "SR") %>%
  ggplot(aes(x = var_gmax)) +
  #ggplot(aes(x = var_gmax,
  #           col = as.factor(num_strains))) +
  geom_line(aes(y = hyst_min_log), lwd = 2, alpha = 0.8) +
  geom_line(aes(y = hyst_max_log), lwd = 2, alpha = 0.8) +
  facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  #guides(col = guide_legend(title="Number of strains")) +
  theme(
    legend.position="top"
    #strip.background = element_blank(),
    #strip.text.x = element_blank()
  ) +
  geom_hline(yintercept = c(-8, 0), col = "grey", lwd = 3)

#ggsave(here("experiments/1_figures_main_ms/figure_5.pdf"),
#       width = 5, height = 4)

```

The figure above shows the effect of response trait diversity (y-axis) on the positions of the tipping points (show by dark lines), which determine the extent of the region of bistability in the oxygen diffusivity gradient. The left-most region is anoxic only, the middle is oxic or anoxic depending on historical conditions, and the right-most is oxic only. The thick grey vertical lines at -8 and 0 on the x-axis show the extent of the oxygen diffusivity gradient investigated in the simulations.

## Effect of simulation duration

```{r}
rm(list=ls())
library(tidyverse)
library(microxanox)
library(patchwork)
library(here)
source(here("r/various_useful_functions.r"))
colfunc_CB <- colorRampPalette(c("#024F17", "#B5FFC9"))
colfunc_SB <- colorRampPalette(c("#7D1402", "#FCBEB3"))
colfunc_PB <- colorRampPalette(c("#6E0172", "#F9AEFC"))
zero <- 0
unity <- 1
ss_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_SS_data.RDS"))
sort(unique(ss_9s$CB_var_gmax_s))
sort(unique(ss_9s$SB_var_gmax_s))
ss_result <- ss_9s %>%
  filter(abs(CB_var_gmax_s - 0.028254848) < 0.0001,
         abs(SB_var_gmax_s - 0.084764545) < 0.0001)
parameter <- ss_result$parameter[[1]]
parameter$strain_parameter <- ss_result$pars[[1]]

wait_time <- 1e6
#p$log10a_series <- seq(-2.5, -2, 0.025)
parameter$log10a_series <- seq(-8, 0, length = 300)
parameter$sim_duration <- wait_time * length(parameter$log10a_series)
parameter$sim_sample_interval <- wait_time
total_initial_abundances <- 10^5
parameter <- set_temporal_ssfind_initial_state(parameter, total_initial_abundances, 
                total_initial_abundances, total_initial_abundances)
parameter
check_results <- run_temporal_ssfind_method(parameter)

check_results_1e6 <- readRDS(here("experiments/2_supplement/data/check1.RDS"))
junk <- list()
junk$ssfind_result[[1]] <- check_results_1e6
plot_ss_result3(junk, 1)

```

# Finding the separatrix

In the original publication ([Bush et al 2017](<https://www.nature.com/articles/s41467-017-00912-x>)) Figure 3a shows a separatrix in the cyanobacteria abundance - oxygen diffusivity dimensions of the system. If the system has initial cyanobacterial abundance greater than the value at the separatrix then the cyanobacterial abundance increases, and the system goes to the oxic stable state. Conversely, if the system has initial cyanobacterial abundance greater than the value at the separatrix then the cyanobacterial abundance decreases, and the system goes to the anoxic stable state.

It is critical to note, however, that the position of the separatrix depends on both the parameters of the system, and the initial conditions of variables other than cyanobacterial abundance. If the system were started with higher initial concentration, then the position of the separatrix would change (as would the values of oxygen diffusivity at which the system tipped from anoxic to oxic, and from oxic to anoxic).

This issue of dependence of the position of the separatrix on the value of initial condition of multiple state variables has particular significance when there are multiple strains per functional group. Then one cannot just vary initial total cyanobacterial abundance (as was done to create the separatrix on Figure 3a in the original publication) but one must also define how the initial abundance of each of the strains varies. One might choose to make each strain have equal initial abundance, and to vary the total (as we did in our implementation of the replication method in the main article).

We could, however, and arguably should, give the most tolerant strain of cyanobacteria higher initial relative abundance when total initial cyanobacterial abundance was low, and the least tolerant strain higher initial relative abundance when total cyanobacterial abundance was high. And we would need to specify the total and relative abundance of all cyanobacteria (and sulfur bactria) strains. Thus, with a system as complex as the 9 strain system, which has 31 state variables the separatrix is very high dimensional, and evaluating (and plotting) it in one dimension requires many assumption. We chose to not attempt to find a meaningful set of assumptions in this study, though not because we think it would be unprofitable to do so, but rather because we did not want to risk distracting attention from findings we consider to be significant enough in the own right.

# Bibliography

### 2021-12-14 experiments/2_supplement/supplement.Rmd
lots

---
title: Supplementary Content
subtitle: Functional diversity ... Predictions of a model of an oxic-anoxic microbial ecosystem 
authors:
  - name: Owen L Petchey
    department: Department of Evolutionary Biology and Environmental Studies
    affiliation: University of Zurich
    location: Zurich 8057, Switzerland
    email: owen.petchey@ieu.uzh.ch
  - name: Rainer Krug
    department: Department of Evolutionary Biology and Environmental Studies
    affiliation: University of Zurich
    location: Zurich 8057, Switzerland
    email: rainer.krug@ieu.uzh.ch
  - name: Any Others
    department: Department of Evolutionary Biology and Environmental Studies
    affiliation: University of Zurich
    location: Zurich 8057, Switzerland
    email: any.others@ieu.uzh.ch
  - name: Marcel Suleiman
    department: Department of Evolutionary Biology and Environmental Studies
    affiliation: University of Zurich
    location: Zurich 8057, Switzerland
    email: marcel.suleiman@ieu.uzh.ch

bibliography: references.bib
biblio-style: unsrt
output: 
  rticles::arxiv_article:
    keep_tex: true
---

```{r include = FALSE, echo = FALSE}
knitr::opts_chunk$set(include = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE)
```

```{r echo = FALSE}
rm(list = ls())
library(tidyverse)
library(microxanox)
library(patchwork)
library(here)
source(here("r/various_useful_functions.r"))
colfunc_CB <- colorRampPalette(c("#024F17", "#B5FFC9"))
colfunc_SB <- colorRampPalette(c("#7D1402", "#FCBEB3"))
colfunc_PB <- colorRampPalette(c("#6E0172", "#F9AEFC"))
zero <- 0
unity <- 1
```

# Introduction

...

# Visualising among strain diversity

The method for creating among strain diversity is explained in the main report. Here we show three visualisations, one for nine strains, one for three, and one for two.

```{r  echo = FALSE}
CB_var_multiplier <- 2
SBPB_var_multiplier <- 6
CB_gmax_div <- 0.015789474 * CB_var_multiplier
CB_h_div <- -0.08 * CB_var_multiplier
SB_gmax_div <- 0.015789474 * SBPB_var_multiplier
SB_h_div <- -0.323  * SBPB_var_multiplier
PB_gmax_div <- 0.015789474  * SBPB_var_multiplier
PB_h_div <- -0.323  * SBPB_var_multiplier
num_div_treatment_levels <- 2
```

## Nine strains

```{r nine-strains, echo = FALSE}

num_CB_strains <- 9
num_PB_strains <- 9
num_SB_strains <- 9
var_expt <- create_diversity_factorial(
  zero = zero, unity = unity,
  num_div_treatment_levels = num_div_treatment_levels,
  CB_gmax_div = CB_gmax_div, CB_h_div = CB_h_div,
  SB_gmax_div = SB_gmax_div, SB_h_div = SB_h_div,
  PB_gmax_div = PB_gmax_div, PB_h_div = PB_h_div,
  default_9strain = new_strain_parameter(
    n_CB = num_CB_strains,
    n_SB = num_SB_strains,
    n_PB = num_PB_strains,
    values_initial_state =  "bush_ssfig3"
  )
)
display_diversity(4,
  var_expt = var_expt,
  num_CB_strains = num_CB_strains,
  num_SB_strains = num_SB_strains,
  num_PB_strains = num_PB_strains
)
```

## Three strains

```{r three-strains, echo = FALSE}

num_CB_strains <- 3
num_PB_strains <- 3
num_SB_strains <- 3
var_expt <- create_diversity_factorial(
  zero = zero, unity = unity,
  num_div_treatment_levels = num_div_treatment_levels,
  CB_gmax_div = CB_gmax_div, CB_h_div = CB_h_div,
  SB_gmax_div = SB_gmax_div, SB_h_div = SB_h_div,
  PB_gmax_div = PB_gmax_div, PB_h_div = PB_h_div,
  default_9strain = new_strain_parameter(
    n_CB = num_CB_strains,
    n_SB = num_SB_strains,
    n_PB = num_PB_strains,
    values_initial_state =  "bush_ssfig3"
  )
)
display_diversity(4,
  var_expt = var_expt,
  num_CB_strains = num_CB_strains,
  num_SB_strains = num_SB_strains,
  num_PB_strains = num_PB_strains
)
```

## Two strains

```{r two-strains, echo = FALSE}

num_CB_strains <- 2
num_PB_strains <- 2
num_SB_strains <- 2
var_expt <- create_diversity_factorial(
  zero = zero, unity = unity,
  num_div_treatment_levels = num_div_treatment_levels,
  CB_gmax_div = CB_gmax_div, CB_h_div = CB_h_div,
  SB_gmax_div = SB_gmax_div, SB_h_div = SB_h_div,
  PB_gmax_div = PB_gmax_div, PB_h_div = PB_h_div,
  default_9strain = new_strain_parameter(
    n_CB = num_CB_strains,
    n_SB = num_SB_strains,
    n_PB = num_PB_strains,
    values_initial_state =  "bush_ssfig3"
  )
)
display_diversity(4,
  var_expt = var_expt,
  num_CB_strains = num_CB_strains,
  num_SB_strains = num_SB_strains,
  num_PB_strains = num_PB_strains
)
```

# Effect of number of strains

May not need this section, as number of strains effect is shown in figure of main ms.

```{r eval = FALSE, echo = FALSE}

## Figure 2b-f ----

ss_9s <- readRDS(here("experiments/0_ss_finding/data/9_strain_SS_data_1e3.RDS"))
sort(unique(ss_9s$CB_var_gmax_s))
sort(unique(ss_9s$SB_var_gmax_s))
ss_result <- ss_9s %>%
  filter(abs(CB_var_gmax_s - 0) < 0.0001,
         abs(SB_var_gmax_s - 0) < 0.0001,)

#temp <- ss_result$ssfind_result[[1]] %>%

#ss_result <- ss_9s$ssfind_result[[25]]

temp <- ss_result$ssfind_result[[1]] %>%
  mutate(a = 10^a_O) %>%
  # arrange(a) %>%
  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  # select(-initial_N_CB, -a_O) %>%
  gather(species, quantity, 2:(ncol(.) - 2)) %>%
  mutate(
    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
    functional_group = case_when(
      str_detect(species, "CB_5") ~ "CB",
      str_detect(species, "SB_5") ~ "SB",
      str_detect(species, "PB_5") ~ "PB"
    ),
    log10_quantity = log10(quantity + 1)
  )

num_strains <- temp %>%
  group_by(functional_group) %>%
  summarise(num = length(unique(species))) %>%
  na.omit()

num_CB_strains <- num_strains$num[num_strains$functional_group == "CB"]
num_SB_strains <- num_strains$num[num_strains$functional_group == "SB"]
num_PB_strains <- num_strains$num[num_strains$functional_group == "PB"]

line_width <- 2

p1 <- temp %>%
  dplyr::filter(functional_group == "CB")  %>%
  mutate(species = factor(species, levels = unique(species))) %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  scale_colour_manual(values = colfunc_CB(num_CB_strains)) +
  guides(colour = guide_legend(ncol = 3)) +
  theme(legend.position="none") +
  ggtitle("(b) Cyanobacteria")
p1# p1

p2 <- temp %>%
  dplyr::filter(functional_group == "SB")  %>%
  mutate(species = factor(species, levels = unique(species))) %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  scale_colour_manual(values = colfunc_SB(num_SB_strains)) +
  guides(colour = guide_legend(ncol = 3)) +
  theme(legend.position="none") +
  ggtitle("(c) Sulfate reducing bacteria")

p3 <- temp %>%
  dplyr::filter(functional_group == "PB")  %>%
  mutate(species = factor(species, levels = unique(species))) %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  scale_colour_manual(values = colfunc_PB(num_PB_strains)) +
  guides(colour = guide_legend(ncol = 3)) +
  theme(legend.position="none") +
  ggtitle("(d) Phototrophic sulfur bacteria")

p4 <- temp %>%
  dplyr::filter(var_type == "Substrate", species == "O") %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  theme(legend.position="none") +
  ggtitle("(e) Oxygen concentration")

p5 <- temp %>%
  dplyr::filter(var_type == "Substrate", species == "SR") %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width, col = 6) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  theme(legend.position="none") +
  ggtitle("(f) Sulfide concentration")

patchwork <- p1 / p2 / p3 / p4 / p5
patchwork
#ggsave(here("experiments/1_figures_main_ms/figure_2b-f.pdf"))

## Figure 3 ----
## Stable state with diversity in all functional groups.

ss_9s <- readRDS(here("experiments/0_ss_finding/data/9_strain_SS_data_1e3.RDS"))
sort(unique(ss_9s$CB_var_gmax_s))
sort(unique(ss_9s$SB_var_gmax_s))
ss_result <- ss_9s %>%
  filter(abs(CB_var_gmax_s - 0.028254848) < 0.0001,
         abs(SB_var_gmax_s - 0.084764545) < 0.0001)

temp <- ss_result$ssfind_result[[1]] %>%
  mutate(a = 10^a_O) %>%
  # arrange(a) %>%
  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  # select(-initial_N_CB, -a_O) %>%
  gather(species, quantity, 2:(ncol(.) - 2)) %>%
  mutate(
    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
    functional_group = case_when(
      str_detect(species, "CB_") ~ "CB",
      str_detect(species, "SB_") ~ "SB",
      str_detect(species, "PB_") ~ "PB"
    ),
    log10_quantity = log10(quantity + 1)
  )

num_strains <- temp %>%
  group_by(functional_group) %>%
  summarise(num = length(unique(species))) %>%
  na.omit()

num_CB_strains <- num_strains$num[num_strains$functional_group == "CB"]
num_SB_strains <- num_strains$num[num_strains$functional_group == "SB"]
num_PB_strains <- num_strains$num[num_strains$functional_group == "PB"]

line_width <- 2

p1 <- temp %>%
  dplyr::filter(functional_group == "CB")  %>%
  mutate(species = factor(species, levels = unique(species))) %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  scale_colour_manual(values = colfunc_CB(num_CB_strains)) +
  guides(colour = guide_legend(ncol = 3)) +
  theme(legend.position="none") +
  ggtitle("(b) Cyanobacteria")
p1# p1

p2 <- temp %>%
  dplyr::filter(functional_group == "SB")  %>%
  mutate(species = factor(species, levels = unique(species))) %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  scale_colour_manual(values = colfunc_SB(num_SB_strains)) +
  guides(colour = guide_legend(ncol = 3)) +
  theme(legend.position="none") +
  ggtitle("(c) Sulfate reducing bacteria")

p3 <- temp %>%
  dplyr::filter(functional_group == "PB")  %>%
  mutate(species = factor(species, levels = unique(species))) %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  scale_colour_manual(values = colfunc_PB(num_PB_strains)) +
  guides(colour = guide_legend(ncol = 3)) +
  theme(legend.position="none") +
  ggtitle("(d) Phototrophic sulfur bacteria")

p4 <- temp %>%
  dplyr::filter(var_type == "Substrate", species == "O") %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  theme(legend.position="none") +
  ggtitle("(e) Oxygen concentration")

p5 <- temp %>%
  dplyr::filter(var_type == "Substrate", species == "SR") %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width, col = 6) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  theme(legend.position="none") +
  ggtitle("(f) Sulfide concentration")

patchwork <- p1 / p2 / p3 / p4 / p5
patchwork
#ggsave(here("experiments/1_figures_main_ms/figure_3.pdf"))

## Figure 4 ----
## Shows effect of no diversity versus diversity in all functional groups.

ss_9s <- readRDS(here("experiments/0_ss_finding/data/9_strain_SS_data_1e3.RDS"))
sort(unique(ss_9s$CB_var_gmax_s))
sort(unique(ss_9s$SB_var_gmax_s))
ss_result_none <- ss_9s %>%
  filter(abs(CB_var_gmax_s - 0.0) < 0.0001,
         abs(SB_var_gmax_s - 0.0) < 0.0001)
ss_result_CB <- ss_9s %>%
  filter(abs(CB_var_gmax_s - 0.014958449) < 0.0001,
         abs(SB_var_gmax_s - 0.0) < 0.0001)
ss_result_SBPB <- ss_9s %>%
  filter(abs(CB_var_gmax_s - 0.0) < 0.0001,
         abs(SB_var_gmax_s - 0.044875347) < 0.0001)
ss_result_both <- ss_9s %>%
  filter(abs(CB_var_gmax_s - 0.014958449) < 0.0001,
         abs(SB_var_gmax_s - 0.044875347) < 0.0001)

temp_none <- ss_result_none$ssfind_result[[1]] %>%
  mutate(a = 10^a_O) %>%
  # arrange(a) %>%
  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  # select(-initial_N_CB, -a_O) %>%
  gather(species, quantity, 2:(ncol(.) - 2)) %>%
  mutate(
    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
    functional_group = case_when(
      str_detect(species, "CB_") ~ "CB",
      str_detect(species, "SB_") ~ "SB",
      str_detect(species, "PB_") ~ "PB"
    ),
    log10_quantity = log10(quantity + 1)
  )

temp_CB <- ss_result_CB$ssfind_result[[1]] %>%
  mutate(a = 10^a_O) %>%
  # arrange(a) %>%
  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  # select(-initial_N_CB, -a_O) %>%
  gather(species, quantity, 2:(ncol(.) - 2)) %>%
  mutate(
    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
    functional_group = case_when(
      str_detect(species, "CB_") ~ "CB",
      str_detect(species, "SB_") ~ "SB",
      str_detect(species, "PB_") ~ "PB"
    ),
    log10_quantity = log10(quantity + 1)
  )
temp_SBPB <- ss_result_SBPB$ssfind_result[[1]] %>%
  mutate(a = 10^a_O) %>%
  # arrange(a) %>%
  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  # select(-initial_N_CB, -a_O) %>%
  gather(species, quantity, 2:(ncol(.) - 2)) %>%
  mutate(
    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
    functional_group = case_when(
      str_detect(species, "CB_") ~ "CB",
      str_detect(species, "SB_") ~ "SB",
      str_detect(species, "PB_") ~ "PB"
    ),
    log10_quantity = log10(quantity + 1)
  )
temp_both <- ss_result_both$ssfind_result[[1]] %>%
  mutate(a = 10^a_O) %>%
  # arrange(a) %>%
  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  # select(-initial_N_CB, -a_O) %>%
  gather(species, quantity, 2:(ncol(.) - 2)) %>%
  mutate(
    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
    functional_group = case_when(
      str_detect(species, "CB_") ~ "CB",
      str_detect(species, "SB_") ~ "SB",
      str_detect(species, "PB_") ~ "PB"
    ),
    log10_quantity = log10(quantity + 1)
  )

line_width <- 2.5

## a
p1 <- temp_none %>%
  dplyr::filter(var_type == "Substrate", species == "O") %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  geom_path(data = filter(temp_CB, var_type == "Substrate", species == "O"),
            col = "black", lwd = line_width - 1.5) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  theme(legend.position="none") +
  ggtitle("(a) No diversity versus diversity in only cyanobacteria") +
  geom_vline(xintercept = c(-8, 0), col = "grey", lwd = 3)
p2 <- temp_none %>%
  dplyr::filter(var_type == "Substrate", species == "O") %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  geom_path(data = filter(temp_SBPB, var_type == "Substrate", species == "O"),
            col = "black", lwd = line_width - 1.5) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  theme(legend.position="none") +
  ggtitle("(b) No diversity versus diversity in only sulfur bacteria") +
  geom_vline(xintercept = c(-8, 0), col = "grey", lwd = 3)
p3 <- temp_none %>%
  dplyr::filter(var_type == "Substrate", species == "O") %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  geom_path(data = filter(temp_both, var_type == "Substrate", species == "O"),
            col = "black", lwd = line_width - 1.5) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  theme(legend.position="none") +
  ggtitle("(c) No diversity versus diversity all functional groups") +
  geom_vline(xintercept = c(-8, 0), col = "grey", lwd = 3)

p1 / p2 / p3

#ggsave(here("experiments/1_figures_main_ms/figure_4.pdf"),
#       width = 6, height = 5)

## Figure 5 ----
## Region of bistability by diversity and number of strains.

#ss_2s <- readRDS(here("experiments/0_ss_finding/data/2_strain_SS_data.RDS"))
#stab_2s <- readRDS(here("experiments/0_ss_finding/data/2_strain_stab_data.RDS")) %>%
#  mutate(num_strains = 2)
ss_3s <- readRDS(here("experiments/0_ss_finding/data/3_strain_SS_data_1e3.RDS"))
stab_3s <- readRDS(here("experiments/0_ss_finding/data/3_strain_stab_data_1e3.RDS")) %>%
  mutate(num_strains = 3)
#ss_6s <- readRDS(here("experiments/0_ss_finding/data/5-level factorial/6_strain_SS_data.RDS"))
#stab_6s <- readRDS(here("experiments/0_ss_finding/data/5-level factorial/6_strain_stab_data.RDS")) %>%
#  mutate(num_strains = 6)
ss_9s <- readRDS(here("experiments/0_ss_finding/data/9_strain_SS_data_1e3.RDS"))
stab_9s <- readRDS(here("experiments/0_ss_finding/data/9_strain_stab_data_1e3.RDS")) %>%
  mutate(num_strains = 9)

all_stab <- #stab_2s %>%
  bind_rows(stab_3s) %>%
  #bind_rows(stab_6s) %>%
  bind_rows(stab_9s)

#all_stab <- stab_9s

CB_vars <- unique(all_stab$CB_var_gmax_s)
SB_vars <- unique(all_stab$SB_var_gmax_s)

CB_all_stab <- all_stab %>%
  filter(SB_var_gmax_s == 0) %>%
  mutate(var_treat = "CB",
         var_gmax = CB_var_gmax_s)

SBPB_all_stab <- all_stab %>%
  filter(CB_var_gmax_s == 0) %>%
  mutate(var_treat = "SB-PB",
         var_gmax = SB_var_gmax_s)

for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
                   SB_var_gmax_s = sort(SB_vars))
CBSBPB_all_stab <- all_stab %>%
  right_join(for_join) %>%
  mutate(var_treat = "CB-SB-PB",
         var_gmax = CB_var_gmax_s)

all_stab_results <- CB_all_stab %>%
  bind_rows(SBPB_all_stab) %>%
  #  bind_rows(results3) %>%
  # bind_rows(results4) %>%
  bind_rows(CBSBPB_all_stab)

all_stab_results <- all_stab_results %>%
  mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB-PB", "CB-SB-PB")))

all_stab_results_small <- select(all_stab_results, -7:-12)

all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax,
             col = as.factor(num_strains))) +
  geom_line(aes(y = hyst_min_log), lwd = 1.5) +
  geom_line(aes(y = hyst_max_log), lwd = 1.5) +
  facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  guides(col = guide_legend(title="Number of strains")) +
  theme(
    legend.position="top"
    #strip.background = element_blank(),
    #strip.text.x = element_blank()
  ) +
  geom_hline(yintercept = c(-8, 0), col = "grey", lwd = 3)

#ggsave(here("experiments/1_figures_main_ms/figure_5.pdf"),
#       width = 5, height = 4)

temp <- all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O",
         var_treat == "SB-PB",
         num_strains == 9) %>%
  ggplot(aes(x = var_gmax,
             col = as.factor(num_strains))) +
  geom_line(aes(y = hyst_min_log)) +
  geom_line(aes(y = hyst_max_log)) +
  facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  guides(col = guide_legend(title="Number of strains")) +
  theme(
    legend.position="top"
    #strip.background = element_blank(),
    #strip.text.x = element_blank()
  ) +
  geom_hline(yintercept = c(-8, 0), col = "grey", lwd = 3)

## 
## 
```

# Robustness of stable state finding

We now discuss two approaches for finding how the stable state of the system varies along the gradient of oxygen diffusivity when there exists the possibility of multiple stable states. In the main article we report results of the method also described there. Briefly here, we made a separate simulations for each of many values of oxygen diffusivity, ran the simulations for long enough to ensure transients had passed, and recorded the state. We ran multiple simulations per value of oxygen diffusivity, and started them with different initial conditions (either low or high total cyanobacterial abundance), so as to check for presence of alternate stable states. This method used by [Bush et al 2017](https://www.nature.com/articles/s41467-017-00912-x). We hereafter term this "the replication method", since it is effectively achieved by having many independent replicates of the ecosystem, each with a different oxygen diffusivity, and also a separate replicate for each of the different chosen initial conditions.

Here we report the results of a second method. We will show some quantitative differences in results compared to the other method, but also show the results concerning diversity effects are qualitatively the same as obtained with the first method.

The second method involves two simulations for a particular system configuration (parameter set). In one simulation the oxygen diffusivity is *increased* in a step-wise fashion. In the other it is *decreased* in a step-wise fashion. That is, oxygen diffusivity is held at a constant level for long enough for steady state to be reach, that state is recorded, and then a slightly higher (or lower) oxygen diffusivity value is set. Hence, at that time point, the system is effectively started with initial conditions that are the state of the system in the previous time step. We hereafter term this "the temporal method".

The temporal method results in a larger region of bistability than the replication method (Figure \@ref(fig:tempmeth1)). That is, a greater extent of environmental change is required to switch the system to the other state (i.e. the region of bistability is greater). This occurs both during increasing and decreasing oxygen diffusivities. The difference in results occurs because, as mentioned above, the initial conditions differ between the two approaches. For example, in the temporal method, the oxygen concentration in the anoxic state is lower than the initial oxygen concentration in the replication approach, and **Owen guesses that** the sulfide concentration is higher **check that last statement**.

## Replication method

```{r repl_meth1, echo=FALSE}
repl_meth <- readRDS(here("experiments/0_ss_finding/replication_method/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
temp_meth <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_SS_data.RDS"))
## To be completed.
plot_ss_result1(repl_meth,
                result_index = 1,
                filename_prefix = NULL,
                save_image_file = FALSE)
```

## Temporal method

```{r temp_meth1, echo=FALSE}
plot_ss_result3(temp_meth, 1)
```

## Both methods overlaid

```{r both_meth1, echo=FALSE}
repl_method_1 <- repl_meth$ss_res[[1]] %>%
     mutate(time = NA,
            direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  select(names(temp_meth$ssfind_result[[1]]))

ss_result1 <- repl_method_1
ss_result2 <- temp_meth$ssfind_result[[1]]

plot_ss_result6(repl_method_1,
                temp_meth$ssfind_result[[1]],
                xlims = c(-8, 0))
```

## Effect of diversity, replication method

The replication method shows the same effects of functional diversity as those revealed by the replication method:

-   Introducing functional diversity in all three functional groups increases the region of bistability relative to when there is no diversity within all functional groups)..
-   Introducing functional diversity in only the cyanobacteria function group delays (with respect to the oxygen diffusivity it occurs at) the switch to the anoxic state as oxygen diffusivity is reduced, but has no effect on the oxygen diffusivity at which the anoxic to oxic transition occurs .
-   Introducing function diversity in only the sulfur bacteria delays (with respect to the oxygen diffusivity it occurs at) the switch from anoxic to oxic, and advances the switch from oxic to anoxic (Figure \@ref(fig:tempmeth4).

```{r echo = FALSE}
stab_data <- readRDS(here("experiments/0_ss_finding/replication_method/9_strains/data/stab_data_1e6_x2x6_factorial.RDS"))

all_stab <- stab_data

#all_stab <- stab_9s

CB_vars <- unique(all_stab$CB_var_gmax_s)
SB_vars <- unique(all_stab$SB_var_gmax_s)

CB_all_stab <- all_stab %>%
  filter(SB_var_gmax_s == 0) %>%
  mutate(var_treat = "CB",
         var_gmax = CB_var_gmax_s)

SBPB_all_stab <- all_stab %>%
  filter(CB_var_gmax_s == 0) %>%
  mutate(var_treat = "SB-PB",
         var_gmax = SB_var_gmax_s)

for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
                   SB_var_gmax_s = sort(SB_vars))
CBSBPB_all_stab <- all_stab %>%
  right_join(for_join) %>%
  mutate(var_treat = "CB-SB-PB",
         var_gmax = CB_var_gmax_s)

all_stab_results <- CB_all_stab %>%
  bind_rows(SBPB_all_stab) %>%
  #  bind_rows(results3) %>%
  # bind_rows(results4) %>%
  bind_rows(CBSBPB_all_stab)

all_stab_results <- all_stab_results %>%
  mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB-PB", "CB-SB-PB")))

all_stab_results_small <- select(all_stab_results, -7:-12)

all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "SR") %>%
  ggplot(aes(x = var_gmax)) +
  #ggplot(aes(x = var_gmax,
  #           col = as.factor(num_strains))) +
  geom_line(aes(y = hyst_min_log), lwd = 3, alpha = 0.8) +
  geom_line(aes(y = hyst_max_log), lwd = 3, alpha = 0.8) +
  facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  #guides(col = guide_legend(title="Number of strains")) +
  theme(
    legend.position="top"
    #strip.background = element_blank(),
    #strip.text.x = element_blank()
  ) +
  geom_hline(yintercept = c(-8, 0), col = "grey", lwd = 3)

#ggsave(here("experiments/1_figures_main_ms/figure_5.pdf"),
#       width = 5, height = 4)

```

# Finding the separatrix

In the original publication ([Bush et al 2017])(<https://www.nature.com/articles/s41467-017-00912-x>) Figure 3a shows a separatrix in the cyanobacteria abundance - oxygen diffusivity dimensions of the system. If the system has initial cyanobacterial abundance greater than the value at the separatrix then the cyanobacterial abundance increases, and the system goes to the oxic stable state. Conversely, if the system has initial cyanobacterial abundance greater than the value at the separatrix then the cyanobacterial abundance decreases, and the system goes to the anoxic stable state.

It is critical to note, however, that the position of the separatrix depends on both the parameters of the system, and the initial conditions of variables other than cyanobacterial abundance. If the system were started with higher initial concentration, then the position of the separatrix would change (as would the values of oxygen diffusivity at which the system tipped from anoxic to oxic, and from oxic to anoxic).

This issue of dependence of the position of the separatrix on the value of initial condition of multiple state variables has particular significance when there are multiple strains per functional group. Then one cannot just vary initial total cyanobacterial abundance (as was done to create the separatrix on Figure 3a in the original publication) but one must also define how the initial abundance of each of the strains varies. One might choose to make each strain have equal initial abundance, and to vary the total (as we did in our implementation of the replication method in the main article).

We could, however, and arguably should, give the most tolerant strain of cyanobacteria higher initial relative abundance when total initial cyanobacterial abundance was low, and the least tolerant strain higher initial relative abundance when total cyanobacterial abundance was high. And we would need to specify the total and relative abundance of all cyanobacteria (and sulfur bactria) strains. Thus, with a system as complex as the 9 strain system, which has 31 state variables the separatrix is very high dimensional, and evaluating (and plotting) it in one dimension requires many assumption. We chose to not attempt to find a meaningful set of assumptions in this study, though not because we think it would be unprofitable to do so, but rather because we did not want to risk distracting attention from findings we consider to be significant enough in the own right.

# Bibliography

### 2021-12-14 R/various_useful_functions.r

@@ -1083,3 +1083,247 @@ plot_ss_result5 <- function(temporal_ss_result1,
 # 
 
 
+
+plot_ss_result6 <- function(ss_result1,
+                            ss_result2,
+                            xlims = c(-8, 0)) {
+  
+  species_colours <- c(CB = "#024F17", SB = "#7D1402", PB = "#6E0172")
+  
+  # colfunc_CB <- colorRampPalette(c("#024F17", "#B5FFC9"))
+  # colfunc_SB <- colorRampPalette(c("#7D1402", "#FCBEB3"))
+  # colfunc_PB <- colorRampPalette(c("#6E0172", "#F9AEFC"))
+  
+  #ss_result1 <- filter(ss_result1, if_all(contains("B_"), ~ (.x > -1)))
+  
+  #ss_result1 <- temporal_ss_result1$ssfind_result[[first_one]]
+  #ss_result2 <- temporal_ss_result2$ssfind_result[[second_one]]
+  
+  
+  temp1 <- ss_result1 %>%
+    mutate(
+      #direction = ifelse(initial_N_CB == 1, "up", "down"),
+      a = a_O
+    ) %>%
+    gather(species, quantity, 2:(ncol(.) - 2)) %>%
+    mutate(
+      var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
+      functional_group = case_when(
+        str_detect(species, "CB_") ~ "CB",
+        str_detect(species, "SB_") ~ "SB",
+        str_detect(species, "PB_") ~ "PB"
+      ),
+      functional_group = ifelse(is.na(functional_group), species, functional_group)
+    ) %>%
+    group_by(a, direction, var_type, functional_group) %>%
+    summarise(total_quantity = sum(quantity, na.rm = TRUE)) %>%
+    mutate(log10_total_quantity = log10(total_quantity + 1))
+  
+  #ss_result2 <- filter(ss_result2, if_all(contains("B_"), ~ (.x > -1)))
+  
+  temp2 <- ss_result2 %>%
+    mutate(
+      #direction = ifelse(initial_N_CB == 1, "up", "down"),
+      a = 10^a_O
+    ) %>%
+    gather(species, quantity, 2:(ncol(.) - 2)) %>%
+    mutate(
+      var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
+      functional_group = case_when(
+        str_detect(species, "CB_") ~ "CB",
[…]

### 2021-12-14 experiments/0_ss_finding/temporal_method/run_experiment.R

@@ -7,7 +7,7 @@ rm(list = ls())
 library(here)
 source(here("R/various_useful_functions.r"))
 
-num_strains <- 6
+num_strains <- 3
 num_CB_strains <- num_strains
 num_SB_strains <- num_strains
 num_PB_strains <- num_strains
@@ -36,12 +36,12 @@ expt_res <- run_temporal_ssfind_experiment(parameter,
                                            total_initial_abundances = total_initial_abundances,
                                            cores = num_cores)
 })
-saveRDS(expt_res, here("experiments/0_ss_finding/data/", paste0(num_strains, "_strain_SS_data.RDS")))
+saveRDS(expt_res, here("experiments/0_ss_finding/data/", paste0(num_strains, "_strain_SS_data_1e3.RDS")))
 
 
 ## Get stability
 num_cores = 12
-expt_res <- readRDS(here("experiments/0_ss_finding/data/", paste0(num_strains, "_strain_SS_data.RDS")))
+expt_res <- readRDS(here("experiments/0_ss_finding/data/", paste0(num_strains, "_strain_SS_data_1e3.RDS")))
 cluster1 <- multidplyr::new_cluster(num_cores)
 multidplyr::cluster_library(cluster1, c("microxanox", "dplyr"))
 system.time({
@@ -51,7 +51,7 @@ stab_data <-  expt_res %>%
   collect() %>%
   unnest(cols = c(stability_measures)) 
 })
-saveRDS(stab_data, here("experiments/0_ss_finding/data/", paste0(num_strains, "_strain_stab_data.RDS")))
+saveRDS(stab_data, here("experiments/0_ss_finding/data/", paste0(num_strains, "_strain_stab_data_1e3.RDS")))
 
 
 

### 2021-12-14 experiments/0_ss_finding/temporal_method/setup_experiment.R

@@ -131,7 +131,7 @@ var_expt <- var_expt_new
 
 wait_time <- 1e6
 #p$log10a_series <- seq(-2.5, -2, 0.025)
-parameter$log10a_series <- seq(-8, 0, length = 100)
+parameter$log10a_series <- seq(-8, 0, length = 300)
 parameter$minimum_abundances["CB"] <- 1
 parameter$minimum_abundances["SB"] <- 1
 parameter$minimum_abundances["PB"] <- 1

### 2022-01-17 experiments/2_supplement/html_supplement.Rmd
many changes!

@@
 
-The replication method shows the same effects of functional diversity as those revealed by the replication method:
+The replication method shows the same effects of functional diversity as those revealed by the temporal method:
 
@@
 
-```{r}
-rm(list=ls())
-library(tidyverse)
-library(microxanox)
-library(patchwork)
-library(here)
-source(here("r/various_useful_functions.r"))
-colfunc_CB <- colorRampPalette(c("#024F17", "#B5FFC9"))
-colfunc_SB <- colorRampPalette(c("#7D1402", "#FCBEB3"))
-colfunc_PB <- colorRampPalette(c("#6E0172", "#F9AEFC"))
-zero <- 0
-unity <- 1
-ss_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_SS_data.RDS"))
-sort(unique(ss_9s$CB_var_gmax_s))
-sort(unique(ss_9s$SB_var_gmax_s))
-ss_result <- ss_9s %>%
-  filter(abs(CB_var_gmax_s - 0.028254848) < 0.0001,
-         abs(SB_var_gmax_s - 0.084764545) < 0.0001)
-parameter <- ss_result$parameter[[1]]
-parameter$strain_parameter <- ss_result$pars[[1]]
+The results below show the stable states as a function of oxygen diffusivity for a system with intermediate level of diversity in all functional groups.
+There appears to be no effect of using a longer simulation time.
+This shows that the duration of the simulations is sufficient to reach stable state, or very close to it.
 
-wait_time <- 1e6
-#p$log10a_series <- seq(-2.5, -2, 0.025)
-parameter$log10a_series <- seq(-8, 0, length = 300)
-parameter$sim_duration <- wait_time * length(parameter$log10a_series)
-parameter$sim_sample_interval <- wait_time
-total_initial_abundances <- 10^5
-parameter <- set_temporal_ssfind_initial_state(parameter, total_initial_abundances, 
-                total_initial_abundances, total_initial_abundances)
-parameter
-check_results <- run_temporal_ssfind_method(parameter)
+Below is Figure 3 from the main manuscript, in which the duration at each oxygen diffusivity value is 1e6:
 
-check_results_1e6 <- readRDS(here("experiments/2_supplement/data/check1.RDS"))
-junk <- list()
-junk$ssfind_result[[1]] <- check_results_1e6
-plot_ss_result3(junk, 1)
+```{r echo = FALSE, fig.height=10}
 
+single_1e6 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/single_1e6_result.RDS"))
+# sort(unique(ss_9s$CB_var_gmax_s))
+# sort(unique(ss_9s$SB_var_gmax_s))
+# ss_result <- ss_9s %>%
+#   filter(abs(CB_var_gmax_s - 0.028254848) < 0.0001,
+#          abs(SB_var_gmax_s - 0.084764545) < 0.0001,
+#          abs(PB_var_gmax_s - 0.084764545) < 0.0001)
+
+temp <- single_1e6 %>%
+  mutate(a = 10^a_O) %>%
+  # arrange(a) %>%
+  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
+  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
+  # select(-initial_N_CB, -a_O) %>%
+  gather(species, quantity, 2:(ncol(.) - 2)) %>%
+  mutate(
+    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
+    functional_group = case_when(
+      str_detect(species, "CB_") ~ "CB",
+      str_detect(species, "SB_") ~ "SB",
+      str_detect(species, "PB_") ~ "PB"
+    ),
+    log10_quantity = log10(quantity + 1)
+  )
+
+num_strains <- temp %>%
+  group_by(functional_group) %>%
+  summarise(num = length(unique(species))) %>%
+  na.omit()
+
+num_CB_strains <- num_strains$num[num_strains$functional_group == "CB"]
+num_SB_strains <- num_strains$num[num_strains$functional_group == "SB"]
+num_PB_strains <- num_strains$num[num_strains$functional_group == "PB"]
+
+line_width <- 1
+
+p1 <- temp %>%
+  dplyr::filter(functional_group == "CB")  %>%
+  mutate(species = factor(species, levels = unique(species))) %>%
+  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
+  geom_path(lwd = line_width) +
+  ##ylab("log10(quantity [cells])") +
+  ylab("Log(Quantity)") +
+  xlab("Oxygen diffusivity") +
+  scale_colour_manual(values = colfunc_CB(num_CB_strains)) +
+  guides(colour = guide_legend(ncol = 3)) +
+  theme(legend.position="none") +
+  ggtitle("(b) Cyanobacteria")
+#p1# p1
+
+p2 <- temp %>%
+  dplyr::filter(functional_group == "SB")  %>%
+  mutate(species = factor(species, levels = unique(species))) %>%
+  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
+  geom_path(lwd = line_width) +
+  ##ylab("log10(quantity [cells])") +
+  ylab("Log(Quantity)") +
+  xlab("Oxygen diffusivity") +
+  scale_colour_manual(values = colfunc_SB(num_SB_strains)) +
+  guides(colour = guide_legend(ncol = 3)) +
+  theme(legend.position="none") +
+  ggtitle("(c) Sulfate reducing bacteria")
+
+p3 <- temp %>%
+  dplyr::filter(functional_group == "PB")  %>%
+  mutate(species = factor(species, levels = unique(species))) %>%
+  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
+  geom_path(lwd = line_width) +
+  ##ylab("log10(quantity [cells])") +
+  ylab("Log(Quantity)") +
+  xlab("Oxygen diffusivity") +
+  scale_colour_manual(values = colfunc_PB(num_PB_strains)) +
+  guides(colour = guide_legend(ncol = 3)) +
+  theme(legend.position="none") +
+  ggtitle("(d) Phototrophic sulfur bacteria")
+
+p4 <- temp %>%
+  dplyr::filter(var_type == "Substrate", species == "O") %>%
+  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
+  geom_path(lwd = line_width) +
+  ##ylab("log10(quantity [cells])") +
+  ylab("Log(Quantity)") +
+  xlab("Oxygen diffusivity") +
+  theme(legend.position="none") +
+  ggtitle("(e) Oxygen concentration")
+
+p5 <- temp %>%
+  dplyr::filter(var_type == "Substrate", species == "SR") %>%
+  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
+  geom_path(lwd = line_width, col = 6) +
+  ##ylab("log10(quantity [cells])") +
+  ylab("Log(Quantity)") +
+  xlab("Oxygen diffusivity") +
+  theme(legend.position="none") +
+  ggtitle("(f) Sulfide concentration")
+
+patchwork <- p1 / p2 / p3 / p4 / p5
+patchwork
+```
+
+For comparison, here are the results with twice the duration at each oxygen diffusivity:
+
+```{r echo = FALSE, fig.height=10}
+
+single_2e6 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/single_1e6_result.RDS"))
+# sort(unique(ss_9s$CB_var_gmax_s))
+# sort(unique(ss_9s$SB_var_gmax_s))
+# ss_result <- ss_9s %>%
+#   filter(abs(CB_var_gmax_s - 0.028254848) < 0.0001,
+#          abs(SB_var_gmax_s - 0.084764545) < 0.0001,
+#          abs(PB_var_gmax_s - 0.084764545) < 0.0001)
+
+temp <- single_1e6 %>%
+  mutate(a = 10^a_O) %>%
+  # arrange(a) %>%
+  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
+  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
+  # select(-initial_N_CB, -a_O) %>%
+  gather(species, quantity, 2:(ncol(.) - 2)) %>%
+  mutate(
+    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
+    functional_group = case_when(
+      str_detect(species, "CB_") ~ "CB",
+      str_detect(species, "SB_") ~ "SB",
+      str_detect(species, "PB_") ~ "PB"
+    ),
+    log10_quantity = log10(quantity + 1)
+  )
+
+num_strains <- temp %>%
+  group_by(functional_group) %>%
+  summarise(num = length(unique(species))) %>%
+  na.omit()
+
+num_CB_strains <- num_strains$num[num_strains$functional_group == "CB"]
+num_SB_strains <- num_strains$num[num_strains$functional_group == "SB"]
+num_PB_strains <- num_strains$num[num_strains$functional_group == "PB"]
+
+line_width <- 1
+
+p1 <- temp %>%
+  dplyr::filter(functional_group == "CB")  %>%
+  mutate(species = factor(species, levels = unique(species))) %>%
+  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
+  geom_path(lwd = line_width) +
+  ##ylab("log10(quantity [cells])") +
+  ylab("Log(Quantity)") +
+  xlab("Oxygen diffusivity") +
+  scale_colour_manual(values = colfunc_CB(num_CB_strains)) +
+  guides(colour = guide_legend(ncol = 3)) +
+  theme(legend.position="none") +
+  ggtitle("(b) Cyanobacteria")
+#p1# p1
+
+p2 <- temp %>%
+  dplyr::filter(functional_group == "SB")  %>%
+  mutate(species = factor(species, levels = unique(species))) %>%
+  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
+  geom_path(lwd = line_width) +
+  ##ylab("log10(quantity [cells])") +
+  ylab("Log(Quantity)") +
+  xlab("Oxygen diffusivity") +
+  scale_colour_manual(values = colfunc_SB(num_SB_strains)) +
+  guides(colour = guide_legend(ncol = 3)) +
+  theme(legend.position="none") +
+  ggtitle("(c) Sulfate reducing bacteria")
+
+p3 <- temp %>%
+  dplyr::filter(functional_group == "PB")  %>%
+  mutate(species = factor(species, levels = unique(species))) %>%
+  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
+  geom_path(lwd = line_width) +
+  ##ylab("log10(quantity [cells])") +
+  ylab("Log(Quantity)") +
+  xlab("Oxygen diffusivity") +
+  scale_colour_manual(values = colfunc_PB(num_PB_strains)) +
+  guides(colour = guide_legend(ncol = 3)) +
+  theme(legend.position="none") +
+  ggtitle("(d) Phototrophic sulfur bacteria")
+
+p4 <- temp %>%
+  dplyr::filter(var_type == "Substrate", species == "O") %>%
+  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
+  geom_path(lwd = line_width) +
+  ##ylab("log10(quantity [cells])") +
+  ylab("Log(Quantity)") +
+  xlab("Oxygen diffusivity") +
+  theme(legend.position="none") +
+  ggtitle("(e) Oxygen concentration")
+
+p5 <- temp %>%
+  dplyr::filter(var_type == "Substrate", species == "SR") %>%
+  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
+  geom_path(lwd = line_width, col = 6) +
+  ##ylab("log10(quantity [cells])") +
+  ylab("Log(Quantity)") +
+  xlab("Oxygen diffusivity") +
+  theme(legend.position="none") +
+  ggtitle("(f) Sulfide concentration")
+
+patchwork <- p1 / p2 / p3 / p4 / p5
+patchwork
 ```
@@
 We chose to not attempt to find a meaningful set of assumptions in this study, though not because we think it would be unprofitable to do so, but rather because we did not want to risk distracting attention from findings we consider to be significant enough in the own right.
-
-# Bibliography

### 2022-01-17 manuscript (obsolete)/article.tex
many changes!

--- 2021-06-24 manuscript/article.tex
@@
 Strong responses of ecosystems to environmental change imply high
-\emph{sensitivity} and lack of resistance to environmental change, and
-higher temporal variability in the face of varying environmental
-conditions. Greater \emph{non-linearity} in ecosystem responses
-increases the potential for surprises, such as when an ecosystem that
-was resistant to an environmental change becomes unexpectedly sensitive
-to further change. The presence and extent of \emph{hysteresis} in
-ecosystem responses to environmental driver gradients concerns how
-readily are ecosystem responses reversed when environmental change is
-reversed.
+sensitivity and lack of resistance to environmental change, and higher
+temporal variability in the face of varying environmental conditions.
+Greater non-linearity in ecosystem responses increases the potential for
+surprises, such as when an ecosystem that was resistant to an
+environmental change becomes unexpectedly sensitive to further change.
+The presence and extent of hysteresis in ecosystem responses to
+environmental driver gradients concerns how readily are ecosystem
+responses reversed when environmental change is reversed.
 
@@
 \item
-  In general, greater functional response diversity may decrease the
-  likelihood of a catastrophic ecosystem response (Figure 2a in Dakos et
-  al. (2019)). Here, we interpret this prediction to be that greater
-  functional response diversity decreases the non-linearity of ecosystem
-  response to environmental driver change, including the extreme
-  non-linearity that can occur when an ecosystem ``flips'' from one
-  state to another one.
+  Greater functional response diversity may decrease the likelihood of a
+  catastrophic ecosystem response (Figure 2a in Dakos et al. (2019)).
+  Here, we interpret this prediction to be that greater functional
+  response diversity decreases the non-linearity of ecosystem response
+  to environmental driver change, including the extreme non-linearity
+  that can occur when an ecosystem ``flips'' from one state to another
+  one.
 \item
@@
 
-These explanations/predictions were based on the verbal/graphical
+These explanations/predictions were based on the verbal and graphical
 argumentation Dakos et al. (2019). There were no mathematical models of
@@
 perturbation on the dynamics of tritrophic food webs}, did employ a such
-a mathematical model {[}to be developed{]}.
+a mathematical model {[}text to be developed{]}.
 
@@
   To provide an answer to the question of how trait variation affects
-  the non-linearity, resilience and hysteresis of ecosystem response to
-  an environmental change.
+  the resilience and hysteresis of ecosystem response to an
+  environmental change.
 \end{itemize}
@@
 \item
-  Mathematical modelling of a microbrial ecosystem. Trait diversity
-  manipulation (can be considered selection among strains, or selection
-  among species). (Do not include mutation or recomination).
+  Mathematical modelling of a microbial ecosystem.
 \item
-  Variation in amount of among strain variation, no variation in number
-  of strains, no variation in strength or shape of the of any tradeoff.
+  Trait diversity manipulation (can be considered selection among
+  strains, or selection among species). (Do not include mutation or
+  recombination).
 \item
-  Measurement of the effect on how the steady state(s) of the system
-  varies with in different environmental conditions, and on the
-  dynamical response of system to gradual environmental change.
+  Variation in amount of among strain variation in two traits, no
+  variation in number of strains, no variation in strength or shape of
+  the of the tradeoff.
+\item
+  Illustration of the dynamical response to gradual environmental
+  change.
+\item
+  Measurement of the effect trait diversity on how the steady state(s)
+  of the system varies with environmental conditions.
 \end{itemize}
@@
 
-{\centering \includegraphics[width=1\linewidth]{/Users/owenpetchey/Desktop/microxanox/diversity_envresp1/manuscript/ecosystem_network}
+{\centering \includegraphics[width=1\linewidth]{/Users/owenpetchey/Desktop/microxanox/diversity_envresp1/manuscript/figures/ecosystem_network}
 
@@
 in the \texttt{microxanox} R package (\textbf{cite the package}).
-Therefore, here we only describe the relatively straightforward
-extension we used to model multiple strains per functional group.
+Therefore, here we only describe the extension we used to model multiple
+strains per functional group.
 
@@
 per functional group (see the \texttt{microxanox} R package \emph{User
-Guide} for a demonstration).
-
-The only other necessary modification was to include summation terms in
-each of the four ordinary differential equations describing the rates of
-change of the four chemical substrates. This was required in order to
-appropriately account for the production and consumption of these
-substrates by multiple strains.
+Guide} for a demonstration). The only other necessary modification was
+to include summation terms in each of the four ordinary differential
+equations describing the rates of change of the four chemical
+substrates. This was required in order to appropriately account for the
+production and consumption of these substrates by multiple strains.
 
@@
 
-In this section we describe how we created variability among the
-multiple strains within functional groups. Since the process was the
-same for each functional group, we usually do not in this description
-subscript parameter names by functional group (though there were
-functional group specific parameters in all simulations). The
-descriptions in this section gradually become more mathematical; the
-next paragraph alone should provide the information required to
-understand all other elements of this report.
-
-We introduced among-strain variability in maximum growth rate (parameter
-\(G_{max}\)) and in the tolerance to the relevant inhibiting chemical
-substrate (parameter \(h\)). Among-strain variability was created such
-that there was a tradeoff between maximum growth rate and tolerance
-(i.e.~high tolerance coinciding with low maximum growth rate)
-(e.g.~Figure @ref(fig:tradeoff). Our implementation of the variation and
-tradeoff contain the assumption of a linear tradeoff of log-log
-transformed among-strain variation.
-
 \begin{figure}
 
-{\centering \includegraphics[width=0.5\linewidth]{article_files/figure-latex/tradeoff-1}
+{\centering \includegraphics[width=1\linewidth]{/Users/owenpetchey/Desktop/microxanox/diversity_envresp1/manuscript/figures/diversity_example}
 
@@
 
-\caption{An example of among-strain variation in growth rate and tolerance, and the tradeoff in the variation.}\label{fig:tradeoff}
+\caption{your caption}\label{fig:diversity_examples}
 \end{figure}
 
-For further understanding, please consider a reference maximum growth
-rate parameter \(G_{max}\) and reference tolerance parameter \(h\).
-Furthermore, consider the meta-parameters \(Div_{G_{max}}\) and
-\(Div_{h}\), which determine the amount of variation among \(n\)-strains
-in the growth rate and tolerance parameters. To create a tradeoff, the
-two meta-parameters were always of different sign.
+In this section we describe how we created variability among the
+multiple strains within functional groups. In brief, in each functional
+group we created multiple distinct strains that differed in their
+maximum growth rate and tolerance to an inhibiting substrate, with a
+trade-off between the two (e.g.~higher tolerance assocated with lower
+maximum growth rate). An example of the resulting variation is displayed
+in Figure \ref(fig:diversity\_example)).
 
-The among strain variation was calculated such that the growth rate of
-strain \(i = 1\) was a factor \(1/(2^{Div_{G_{max}}})\) of the reference
-growth rate, and the growth rate of the \(i = n\) strain was a factor
-\(2^{Div_{G_{max}}}\) of the reference growth rate. The growth rate of
-the \(i = \{2,...n-1\}\) other strains was the reference growth rate
+A more detailed account of the creation of strains follows now.
+Introducing variation among multiple strains within a functional group
+required a number of decisions:
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{The number of strains.} The symbol for this is \(n\)
+  subscripted with the functional group code (CB = cyanobacteria, SP =
+  sulphate reducing bacteria, and PB = phototrophic sulphur bacteria).
+  E.g. \(n_{CB}\) is the number of strains of cyanobacteria. {[}add why
+  we only ever had 9{]}.
+\item
+  \textbf{Which traits to introduce variation in.} We chose the maximum
+  growth rate and the tolerance of growth to an inhibiting substrate.
+  E.g. maximum growth rate of the cyanobacteria \(G_{max,CB}\), and the
+  tolerance of cyanobacterial growth to reduced sulphur \(h_{SR,CB}\).
+\item
+  \textbf{The amount of among strain variation.} The symbol for this is
+  \(Div\) (from \emph{Div}ersity) subscripted by the trait/parameter and
+  the functional group. E.g. * \(Div_{G_{max,CB}}\) is the amount of
+  among strain variation in the maximum growth rate \(G_{max}\) of the
+  cyanobacteria \(CB\).
+\item
+  \textbf{The correlation between variation in different traits.} This
+  was always negative, so there was a tradeoff. Our implementation of
+  the variation and tradeoff contain the assumption of a linear tradeoff
+  of log-log transformed among-strain variation.
+\item
+  \textbf{The relative amount of among strain variation in different
+  functional groups.} E.g. were strains of cyanobacteria very variable
+  compared to strains of the other functional groups. We performed
+  several numerical experiments, varying which functional groups had
+  more or less among strain variation.
+\item
+  \textbf{The distribution of trait variation.} We chose to have among
+  strain variation distributed evenly on a log scale.
+\end{itemize}
+
+The parameters therefore necessary were:
+
+\begin{itemize}
+\tightlist
+\item
+  \(n_{CB}\) - number of strains of cyanobacteria.
+\item
+  \(n_{SB}\) - number of strains of sulphate reducing bacteria.
+\item
+  \(n_{PB}\) - number of strains of phototrophic sulphur bacteria.
+\item
+  \(Div_{G_{max,CB}}\) - amount of among strain variation in the maximum
+  growth rate \(G_{max}\) of the cyanobacteria \(CB\).
+\item
+  \(Div_{h_{SR,CB}}\) - amount of among strain variation in the
+  tolerance \(h\) of cyanobacteria \(CB\) to reduced sulpur compounds
+  \(SR\).
+\item
+  \(Div_{G_{max,SB}}\) - amount of among strain variation in the maximum
+  growth rate \(G_{max}\) of the sulphate reducing bacteria \(SB\).
+\item
+  \(Div_{h_{O,SB}}\) - amount of among strain variation in the tolerance
+  \(h\) of sulphate reducing bacteria \(S\) to oxygen \(O\).
+\item
+  \(Div_{G_{max,PB}}\) - amount of among strain variation in the maximum
+  growth rate \(G_{max}\) of the phototrophic sulphur bacteria \(PB\).
+\item
+  \(Div_{h_{O,PB}}\) - amount of among strain variation in the tolerance
+  \(h\) of phototrophic sulphur bacteria \(PB\) to oxygen \(O\).
+\end{itemize}
+
+For example, cyanobacteria, and a reference maximum growth rate
+parameter \(G_{max,CB}\) and reference tolerance parameter
+\(h_{SR,CB}\). Recall that amount of among strain variation is
+controlled by the two meta-parameters \(Div_{G_{max,CB}}\) and
+\(Div_{h_{SR,CB}}\). To create a tradeoff, the two meta-parameters were
+always of different sign. The among strain variation was calculated such
+that the growth rate of strain \(i = 1\) was a factor
+\(1/(2^{Div_{G_{max,CB}}})\) of the reference growth rate, and the
+growth rate of the \(i = n\) strain was a factor
+\(2^{Div_{G_{max,CB}}}\) of the reference growth rate. The growth rate
+of the \(i = \{2,...n-1\}\) other strains was the reference growth rate
 multiplied by a factor that was equally distributed between the factor
-of the \(i = 1\) and \(i = n\) strain.
+of the \(i = 1\) and \(i = n\) strain. This implementation of the
+variation and trade-off contains the assumption of a linear trade-off of
+log-log transformed among-strain variation.
 
-Hence, for example, with the reference growth rate \(G_{max} =\) 0.05,
-among strain variation of \(Div_{G_{max}} =\) 1, and nine strains
-(\(n =\) 9), then the growth rates of the nine strains are 0.025, 0.03,
-0.035, 0.042, 0.05, 0.059, 0.071, 0.084, 0.1 (Figure @ref(fig:tradeoff).
+Hence, for example, with the reference growth rate \(G_{max,CB} =\)
+0.05, among strain variation of \(Div_{G_{max,CB}} =\) 1, and nine
+strains (\(n =\) 9), then the growth rates of the nine strains are
+0.025, 0.03, 0.035, 0.042, 0.05, 0.059, 0.071, 0.084, 0.1 (Figure to be
+added).
 
@@
 strains in a functional group was calculated as
-\(G_{max, i} = D_i * G_{max}\) where D\_i is the i-th element of the set
-\(D = \{2^{f(x)Div_{G_{max}}} | x \in \mathbb{N}, x \leq n\}\), where
-\(f(x) = (x-(n+1)/2) / (( n-1)/2)\).)
+\(G_{max, i} = D_i * G_{max}\) where \(D_i\) is the i-th element of the
+set \(D = \{2^{f(x)Div_{G_{max}}} | x \in \mathbb{N}, x \leq n\}\),
+where \(f(x) = (x-(n+1)/2) / (( n-1)/2)\).)
 
@@
 
-\caption{No diversity}\label{fig:ss_novar}
+\caption{Steady states of the ecosystem with no trait diversity, i.e. identical trait values for the strains within a functional group.}\label{fig:ss_novar}
 \end{figure}
@@
 
-\caption{Diversity in all functional groups}\label{fig:ss_var}
+\caption{Steady states of the ecosystem with diversity in all functional groups}\label{fig:ss_var}
 \end{figure}
@@
 
-\caption{Diversity in none (solid) and all functional groups.}\label{fig:ss_var2}
+\caption{Steady states of the ecosystem without any diversity (solid line) and with diversity in all three functional groups.}\label{fig:ss_var2}
 \end{figure}
@@
 
-\caption{Diversity in CB functional group.}\label{fig:CB_var1}
+\caption{Steady states of the ecosystem with diversity in only the cyanobacteria functional group.}\label{fig:CB_var1}
 \end{figure}
@@
 
-\caption{Diversity in none (solid) and CB functional groups.}\label{fig:CB_var2}
-\end{figure}
-
-\hypertarget{figure-sb-stable-states-with-variation-and-tradeoff}{%
-\subsection{Figure: SB Stable states with variation and
-tradeoff}\label{figure-sb-stable-states-with-variation-and-tradeoff}}
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/SB_var1-1}
-
-}
-
-\caption{Diversity in SB functional group.}\label{fig:SB_var1}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/SB_var2-1}
-
-}
-
-\caption{Diversity in none (solid) and SB functional group.}\label{fig:SB_var2}
-\end{figure}
-
-\hypertarget{figure-pb-stable-states-with-variation-and-tradeoff}{%
-\subsection{Figure: PB Stable states with variation and
-tradeoff}\label{figure-pb-stable-states-with-variation-and-tradeoff}}
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/PB_var1-1}
-
-}
-
-\caption{Diversity in PB functional group.}\label{fig:PB_var1}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/PB_var2-1}
-
-}
-
-\caption{Diversity in none (solid) and PB functional group.}\label{fig:PB_var2}
+\caption{Steady states of the ecosystem without any diversity (solid line) and with diversity in only the cyanobacteria functional group.}\label{fig:CB_var2}
 \end{figure}
@@
 
-\caption{Diversity in SB and PB functional groups.}\label{fig:SBPB_var1}
+\caption{Steady states of the ecosystem with diversity in only the two sulphur bacteria functional groups.}\label{fig:SBPB_var1}
 \end{figure}
@@
 
-\caption{Diversity in none (solid) and SB and PB functional groups.}\label{fig:SBPB_var2}
+\caption{Steady states of the ecosystem without any diversity (solid line) and with diversity in only the sulphur bacteria functional group.}\label{fig:SBPB_var2}
 \end{figure}
@@
 
-{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/ss_var3-1}
+{\centering \includegraphics[width=1\linewidth]{/Users/owenpetchey/Desktop/microxanox/diversity_envresp1/manuscript/figures/extent_of_bistab1}
 
@@
 
-\caption{your caption}\label{fig:ss_var3}
+\caption{Effect of increasing amounts of trait diversity on the extent of the environmental gradient for which bistability (i.e.
+alternative stable states) is present, when different combinations of the three functional groups contain any diversity.}\label{fig:stab1}
 \end{figure}
@@
 
-{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/ss_var4-1}
+{\centering \includegraphics[width=1\linewidth]{/Users/owenpetchey/Desktop/microxanox/diversity_envresp1/manuscript/figures/extent_of_bistab2}
 
@@
 
-\caption{your caption}\label{fig:ss_var4}
+\caption{Effect of increasing amounts of trait diversity on the upper and lower bound of the environmental gradient for which bistability (i.e.
+alternative stable states) is present, when different combinations of the three functional groups contain any diversity.}\label{fig:stab2}
 \end{figure}
-
-\hypertarget{figure-temporal-switches}{%
-\subsection{Figure: Temporal switches}\label{figure-temporal-switches}}
-
-Maybe\ldots{} to be added. Need to go both ways (oxic to anoxic, and
-anoxic to oxic).
 
@@
 \section{Discussion}\label{discussion}}
+
+We observed that greater trait diversity among the organisms dominating
+the prevailing ecosystem state can lead to greater resilience of that
+state. We also observed that greater trait diversity among the organisms
+that occur in an different ecosystem state can reduce resilience.
+
+The effect of diversity occurs because with greater trait diversity
+there is a organism with greater tolerance to the deteriorating (from
+the perspective of the dominant organisms). This greater tolerance means
+that a greater amount of environmental deterioration is required to
+cause the ecosystem to flip into the alternative state.
+
+In the case study, with three functional groups, the presence or absence
+of diversity in the different functional groups influences
+resilience\ldots{} with only diversity in the CB\ldots{}
 

### 2022-01-17 R/various_useful_functions.r

@@ -552,6 +552,103 @@ create_diversity_factorial <- function(
 }
 
 
+
+create_diversity_factorial2 <- function(
+  zero, unity,
+  num_div_treatment_levels,
+  CB_gmax_div, CB_h_div,
+  SB_gmax_div, SB_h_div,
+  PB_gmax_div, PB_h_div,
+  default_9strain
+) {
+  # default_9strain <- new_strain_parameter(
+  #   n_CB = num_CB_strains,
+  #   n_SB = num_SB_strains,
+  #   n_PB = num_PB_strains,
+  #   values_initial_state = initial_pars_from
+  # )
+  CB_var_gmax_s <- seq(zero, unity, length = num_div_treatment_levels) * CB_gmax_div
+  CB_var_h_s <- seq(zero, unity, length = num_div_treatment_levels) * CB_h_div
+  SB_var_gmax_s <- seq(zero, unity, length = num_div_treatment_levels) * SB_gmax_div
+  SB_var_h_s <- seq(zero, unity, length = num_div_treatment_levels) * SB_h_div
+  PB_var_gmax_s <- seq(zero, unity, length = num_div_treatment_levels) * PB_gmax_div
+  PB_var_h_s <- seq(zero, unity, length = num_div_treatment_levels) * PB_h_div
+  
+  var_expt <- crossing(
+    CB_index = seq_along(CB_var_gmax_s),
+    SB_index = seq_along(SB_var_gmax_s),
+    PB_index = seq_along(PB_var_gmax_s)
+   )
+  no_var <- var_expt %>%
+    filter(CB_index == 1,
+           SB_index == 1,
+           PB_index == 1)
+  CB_var_expt <- var_expt %>%
+    filter(SB_index == 1,
+           PB_index == 1)
+  SB_var_expt <- var_expt %>%
+    filter(CB_index == 1,
+           PB_index == 1)
+  PB_var_expt <- var_expt %>%
+    filter(CB_index == 1,
+           SB_index == 1)
+  CBSB_var_expt <- var_expt %>%
+    filter(PB_index == 1,
+           CB_index == SB_index)
+  CBPB_var_expt <- var_expt %>%
+    filter(SB_index == 1,
+           CB_index == PB_index)
+  SBPB_var_expt <- var_expt %>%
+    filter(CB_index == 1,
+           SB_index == PB_index)
[…]

### 2022-01-17 experiments/0_ss_finding/temporal_method/div_effects.R

@@ -1,0 +1,33 @@
+rm(list = ls())
+
+## Prelims ----
+library(microxanox)
+library(tidyverse)
+library(patchwork)
+library(here)
+
+colfunc_CB <- colorRampPalette(c("#024F17", "#B5FFC9"))
+colfunc_SB <- colorRampPalette(c("#7D1402", "#FCBEB3"))
+colfunc_PB <- colorRampPalette(c("#6E0172", "#F9AEFC"))
+
+source(here("R/various_useful_functions.r"))
+
+
+
+all_stab_results_small <- readRDS(here("experiments/0_ss_finding/temporal_method/data/all_stab_results_small.RDS"))
+sort(unique(all_stab_results_small$stand_var))
+
+
+reference_var <- 0.47368421
+
+temp <- all_stab_results_small %>%
+  filter(round(stand_var,4) == round(reference_var,4) | stand_var == 0,
+         Species == "CB_tot",
+         num_strains == 9) %>%
+  arrange(var_treat, stand_var) %>%
+  group_by(var_treat) %>%
+  summarise(an2ox_div_effect = hyst_max_log[2]-hyst_max_log[1],
+            ox2an_div_effect = hyst_min_log[2]-hyst_min_log[1])
+  
+temp
+

### 2022-01-17 experiments/0_ss_finding/temporal_method/run_experiment.R

@@ -5,14 +5,21 @@
 
 rm(list = ls())
 library(here)
+
+max_cores <- benchmarkme::get_cpu()$no_of_cores
+
 source(here("R/various_useful_functions.r"))
 
-num_strains <- 3
+i = 2
+
+for(i in c(2, 3, 6, 9)) {
+  
+num_strains <- i
 num_CB_strains <- num_strains
 num_SB_strains <- num_strains
 num_PB_strains <- num_strains
 
-source(here("experiments/0_ss_finding/setup_experiment.R"))
+source(here("experiments/0_ss_finding/temporal_method/setup_experiment.R"))
 
 #var_expt <- var_expt[1,]
 
@@ -36,12 +43,12 @@ expt_res <- run_temporal_ssfind_experiment(parameter,
                                            total_initial_abundances = total_initial_abundances,
                                            cores = num_cores)
 })
-saveRDS(expt_res, here("experiments/0_ss_finding/data/", paste0(num_strains, "_strain_SS_data_1e3.RDS")))
+saveRDS(expt_res, here("experiments/0_ss_finding/temporal_method/data/", paste0(num_strains, "_strain_SS_data_1e3.RDS")))
 
 
 ## Get stability
 num_cores = 12
-expt_res <- readRDS(here("experiments/0_ss_finding/data/", paste0(num_strains, "_strain_SS_data_1e3.RDS")))
+expt_res <- readRDS(here("experiments/0_ss_finding/temporal_method/data/", paste0(num_strains, "_strain_SS_data_1e3.RDS")))
 cluster1 <- multidplyr::new_cluster(num_cores)
 multidplyr::cluster_library(cluster1, c("microxanox", "dplyr"))
 system.time({
@@ -51,7 +58,7 @@ stab_data <-  expt_res %>%
   collect() %>%
   unnest(cols = c(stability_measures)) 
 })
-saveRDS(stab_data, here("experiments/0_ss_finding/data/", paste0(num_strains, "_strain_stab_data_1e3.RDS")))
+saveRDS(stab_data, here("experiments/0_ss_finding/temporal_method/data/", paste0(num_strains, "_strain_stab_data_1e3.RDS")))
 
 
 

### 2022-01-17 experiments/1_figures_main_ms/figures_main_ms_v2.R

@@ -1,0 +1,993 @@
+## Figures for main manuscript
+## 
+## 
+
+## Prelims ----
+library(microxanox)
+library(tidyverse)
+library(patchwork)
+library(here)
+
+colfunc_CB <- colorRampPalette(c("#024F17", "#B5FFC9"))
+colfunc_SB <- colorRampPalette(c("#7D1402", "#FCBEB3"))
+colfunc_PB <- colorRampPalette(c("#6E0172", "#F9AEFC"))
+
+source(here("R/various_useful_functions.r"))
+
+## Figure 1 ----
+## Powerpoint
+
+## Figure 2a ----
+## Keynote
+
+## Figure 2b-f ----
+
+ss_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_SS_data_1e6.RDS"))
+sort(unique(ss_9s$CB_var_gmax_s))
+sort(unique(ss_9s$SB_var_gmax_s))
+ss_result <- ss_9s %>%
+  filter(abs(CB_var_gmax_s - 0) < 0.0001,
+         abs(SB_var_gmax_s - 0) < 0.0001,)
+
+
+
+#temp <- ss_result$ssfind_result[[1]] %>%
+  
+#ss_result <- ss_9s$ssfind_result[[25]]
+
+temp <- ss_result$ssfind_result[[1]] %>%
+  mutate(a = 10^a_O) %>%
+  # arrange(a) %>%
+  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
+  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
+  # select(-initial_N_CB, -a_O) %>%
+  gather(species, quantity, 2:(ncol(.) - 2)) %>%
+  mutate(
+    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
+    functional_group = case_when(
+      str_detect(species, "CB_5") ~ "CB",
+      str_detect(species, "SB_5") ~ "SB",
+      str_detect(species, "PB_5") ~ "PB"
+    ),
+    log10_quantity = log10(quantity + 1)
+  )
+
+num_strains <- temp %>%
+  group_by(functional_group) %>%
+  summarise(num = length(unique(species))) %>%
+  na.omit()
+
+num_CB_strains <- num_strains$num[num_strains$functional_group == "CB"]
+num_SB_strains <- num_strains$num[num_strains$functional_group == "SB"]
[…]

### 2022-01-20 experiments/1_figures_main_ms/Understand_PB.Rmd
Moved figures in single Rmd document and added Illustrative document for PB (Figure 5)

---
title: "Understandin PB"
author: "Rainer M Krug"
date: "1/20/2022"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  cache = FALSE
)
library(microxanox)
library(tidyverse)
library(patchwork)
library(here)

colfunc_CB <- colorRampPalette(c("#024F17", "#B5FFC9"))
colfunc_SB <- colorRampPalette(c("#7D1402", "#FCBEB3"))
colfunc_PB <- colorRampPalette(c("#6E0172", "#F9AEFC"))

source(here("R/various_useful_functions.r"))

plot_fig3 <- function(
  ss_result
){
  temp <- ss_result$ssfind_result[[1]] %>%
    mutate(a = 10^a_O) %>%
    # arrange(a) %>%
    # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
    #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
    # select(-initial_N_CB, -a_O) %>%
    gather(species, quantity, 2:(ncol(.) - 2)) %>%
    mutate(
      var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
      functional_group = case_when(
        str_detect(species, "CB_") ~ "CB",
        str_detect(species, "SB_") ~ "SB",
        str_detect(species, "PB_") ~ "PB"
      ),
      log10_quantity = log10(quantity + 1)
    )

  num_strains <- temp %>%
    group_by(functional_group) %>%
    summarise(num = length(unique(species))) %>%
    na.omit()

  num_CB_strains <- num_strains$num[num_strains$functional_group == "CB"]
  num_SB_strains <- num_strains$num[num_strains$functional_group == "SB"]
  num_PB_strains <- num_strains$num[num_strains$functional_group == "PB"]

  line_width <- 2

  p1 <- temp %>%
    dplyr::filter(functional_group == "CB")  %>%
    mutate(species = factor(species, levels = unique(species))) %>%
    ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
    geom_path(lwd = line_width) +
    ##ylab("log10(quantity [cells])") +
    ylab("Log(Quantity)") +
    xlab("Oxygen diffusivity") +
    scale_colour_manual(values = colfunc_CB(num_CB_strains)) +
    guides(colour = guide_legend(ncol = 3)) +
    theme(legend.position="none") +
    ggtitle("(a) Cyanobacteria")

  p2 <- temp %>%
    dplyr::filter(functional_group == "SB")  %>%
    mutate(species = factor(species, levels = unique(species))) %>%
    ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
    geom_path(lwd = line_width) +
    ##ylab("log10(quantity [cells])") +
    ylab("Log(Quantity)") +
    xlab("Oxygen diffusivity") +
    scale_colour_manual(values = colfunc_SB(num_SB_strains)) +
    guides(colour = guide_legend(ncol = 3)) +
    theme(legend.position="none") +
    ggtitle("(b) Sulfate reducing bacteria")

  p3 <- temp %>%
    dplyr::filter(functional_group == "PB")  %>%
    mutate(species = factor(species, levels = unique(species))) %>%
    ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
    geom_path(lwd = line_width) +
    ##ylab("log10(quantity [cells])") +
    ylab("Log(Quantity)") +
    xlab("Oxygen diffusivity") +
    scale_colour_manual(values = colfunc_PB(num_PB_strains)) +
    guides(colour = guide_legend(ncol = 3)) +
    theme(legend.position="none") +
    ggtitle("(c) Phototrophic sulfur bacteria")

  p4 <- temp %>%
    dplyr::filter(var_type == "Substrate", species == "O") %>%
    ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
    geom_path(lwd = line_width) +
    ##ylab("log10(quantity [cells])") +
    ylab("Log(Quantity)") +
    xlab("Oxygen diffusivity") +
    theme(legend.position="none") +
    ggtitle("(d) Oxygen concentration")

  p5 <- temp %>%
    dplyr::filter(var_type == "Substrate", species == "SR") %>%
    ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
    geom_path(lwd = line_width, col = 6) +
    ##ylab("log10(quantity [cells])") +
    ylab("Log(Quantity)") +
    xlab("Oxygen diffusivity") +
    theme(legend.position="none") +
    ggtitle("(e) Sulfide concentration")
  patchwork <- p1 / p2 / p3 / p4 / p5
  patchwork
}
```

## Figure 5
Region of bistability by diversity and number of strains.

![alt text](figure_5_v2_allstrains.png)

## Figure 3
Stable state with diversity in all functional groups.

```{r fig3_prep}
ss_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_SS_data_1e6.RDS"))

max <- max(ss_9s$PB_var_gmax_s)
f <- 0.625
fv <- f*max

only_PB_variable <- ss_9s %>%
  filter(
    abs(CB_var_gmax_s) < 0.0001,
    abs(SB_var_gmax_s) < 0.0001
  )
only_PB_variable <- only_PB_variable[order(only_PB_variable$PB_var_gmax_s), ]

only_PB_variable$PB_var_gmax_s
```

The following are the same figure for different variabilities in PB. PB Ranges from `r min(ss_9s$PB_var_gmax_s)` to `r max(ss_9s$PB_var_gmax_s)`.

- PB_var_gmax_s: `r max(ss_9s$PB_var_gmax_s)`
- PB_var_gmax_s: `r max(ss_9s$PB_var_gmax_s)`
- PB_var_gmax_s: `r max(ss_9s$PB_var_gmax_s)`

### PB_var_gmax_s ascending
#### v = `r only_PB_variable$PB_var_gmax_s[1] / max(only_PB_variable$PB_var_gmax_s)`

```{r figure3_1, fig.height=7}
plot_fig3(only_PB_variable[1,])
```

#### v = `r only_PB_variable$PB_var_gmax_s[10] / max(only_PB_variable$PB_var_gmax_s)`

```{r figure3_10, fig.height=7}
plot_fig3(only_PB_variable[10,])
```

#### v = `r only_PB_variable$PB_var_gmax_s[12] / max(only_PB_variable$PB_var_gmax_s)`

```{r figure3_12, fig.height=7}
plot_fig3(only_PB_variable[12,])
```

#### v = `r only_PB_variable$PB_var_gmax_s[14] / max(only_PB_variable$PB_var_gmax_s)`

```{r figure3_14, fig.height=7}
plot_fig3(only_PB_variable[14,])
```

#### v = `r only_PB_variable$PB_var_gmax_s[16] / max(only_PB_variable$PB_var_gmax_s)`

```{r figure3_16, fig.height=7}
plot_fig3(only_PB_variable[16,])
```

#### v = `r only_PB_variable$PB_var_gmax_s[18] / max(only_PB_variable$PB_var_gmax_s)`

```{r figure3_18, fig.height=7}
plot_fig3(only_PB_variable[18,])
```

#### v = `r only_PB_variable$PB_var_gmax_s[20] / max(only_PB_variable$PB_var_gmax_s)`

```{r figure3_20, fig.height=7}
plot_fig3(only_PB_variable[20,])
```

### 2022-01-20 experiments/2_supplement/html_supplement.Rmd
correct sim duration effect figures in supplement

@@
 
-single_2e6 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/single_1e6_result.RDS"))
+single_2e6 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/single_2e6_result.RDS"))
 # sort(unique(ss_9s$CB_var_gmax_s))
@@
 
-temp <- single_1e6 %>%
+temp <- single_2e6 %>%
   mutate(a = 10^a_O) %>%

### 2022-01-20 experiments/0_ss_finding/temporal_method/run_single_sim.R

@@ -43,6 +43,7 @@ system.time(
 )
 saveRDS(result_1e6, here("experiments/0_ss_finding/temporal_method/data/single_1e6_result.RDS"))
 
+
 wait_time <-  2e6
 parameter$sim_duration <- wait_time * length(parameter$log10a_series)
 parameter$sim_sample_interval <- wait_time

### 2022-01-20 experiments/2_supplement/html_supplement.Rmd
update supplement

@@
 
-The results below show the stable states as a function of oxygen diffusivity for a system with intermediate level of diversity in all functional groups.
-There appears to be no effect of using a longer simulation time.
-This shows that the duration of the simulations is sufficient to reach stable state, or very close to it.
+The results below show the stable states as a function of oxygen diffusivity for a system with intermediate level of diversity in all functional groups, with either 1'000'000 hours simulation time, or 2'000'000 hours.
+This shows that except very close to the values of oxygen diffusitivity at which a state transition occurs, 1'000'000 hours duration of the simulations is sufficient to reach stable state, or very close to it.
+Very close to the transitions, even at 2'000'000 hours, the dynamics are still transient, with high tolerance strains at high density, even though they will eventually be outcompeted by low tolerance (higher growth rate) strains.
 

### 2022-01-25 experiments/1_figures_main_ms/not_currently_used/Figures.Rmd
cleaning up, getting ready!

---
title: "Figures and Tables"
author: "Rainer M Krug"
date: "1/20/2022"
output: 
  html_document:
  toc: true
  toc_float: true
  toc_collapsed: false
  code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo  = TRUE,
  cache = FALSE
)

library(microxanox)
library(tidyverse)
library(patchwork)
library(here)

colfunc_CB <- colorRampPalette(c("#024F17", "#B5FFC9"))
colfunc_SB <- colorRampPalette(c("#7D1402", "#FCBEB3"))
colfunc_PB <- colorRampPalette(c("#6E0172", "#F9AEFC"))

source(here("R/various_useful_functions.r"))
```

## Figure 2

```{r figure2}
ss_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_SS_data_1e6.RDS"))
sort(unique(ss_9s$CB_var_gmax_s))
sort(unique(ss_9s$SB_var_gmax_s))
ss_result <- ss_9s %>%
  filter(abs(CB_var_gmax_s - 0) < 0.0001,
         abs(SB_var_gmax_s - 0) < 0.0001,
         abs(PB_var_gmax_s - 0) < 0.0001)

#temp <- ss_result$ssfind_result[[1]] %>%

#ss_result <- ss_9s$ssfind_result[[25]]

temp <- ss_result$ssfind_result[[1]] %>%
  mutate(a = 10^a_O) %>%
  # arrange(a) %>%
  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  # select(-initial_N_CB, -a_O) %>%
  gather(species, quantity, 2:(ncol(.) - 2)) %>%
  mutate(
    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
    functional_group = case_when(
      str_detect(species, "CB_5") ~ "CB",
      str_detect(species, "SB_5") ~ "SB",
      str_detect(species, "PB_5") ~ "PB"
    ),
    log10_quantity = log10(quantity + 1)
  )

num_strains <- temp %>%
  group_by(functional_group) %>%
  summarise(num = length(unique(species))) %>%
  na.omit()

num_CB_strains <- num_strains$num[num_strains$functional_group == "CB"]
num_SB_strains <- num_strains$num[num_strains$functional_group == "SB"]
num_PB_strains <- num_strains$num[num_strains$functional_group == "PB"]

line_width <- 2
```

### Figure 2b

```{r figure2b}
p1 <- temp %>%
  dplyr::filter(functional_group == "CB")  %>%
  mutate(species = factor(species, levels = unique(species))) %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  scale_colour_manual(values = colfunc_CB(num_CB_strains)) +
  guides(colour = guide_legend(ncol = 3)) +
  theme(legend.position="none") +
  ggtitle("(b) Cyanobacteria")
p1
```

### Figure 2c

```{r figure2c}

p2 <- temp %>%
  dplyr::filter(functional_group == "SB")  %>%
  mutate(species = factor(species, levels = unique(species))) %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  scale_colour_manual(values = colfunc_SB(num_SB_strains)) +
  guides(colour = guide_legend(ncol = 3)) +
  theme(legend.position="none") +
  ggtitle("(c) Sulfate reducing bacteria")
p2
```

### Figure 2d

```{r figure2d}

p3 <- temp %>%
  dplyr::filter(functional_group == "PB")  %>%
  mutate(species = factor(species, levels = unique(species))) %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  scale_colour_manual(values = colfunc_PB(num_PB_strains)) +
  guides(colour = guide_legend(ncol = 3)) +
  theme(legend.position="none") +
  ggtitle("(d) Phototrophic sulfur bacteria")
p3
```

### Figure 2e

```{r figure2e}

p4 <- temp %>%
  dplyr::filter(var_type == "Substrate", species == "O") %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  theme(legend.position="none") +
  ggtitle("(e) Oxygen concentration")
p4
```

### Figure 2f

```{r figure2f}
p5 <- temp %>%
  dplyr::filter(var_type == "Substrate", species == "SR") %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width, col = 6) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  theme(legend.position="none") +
  ggtitle("(f) Sulfide concentration")
p5
```

### Assembled

```{r figure2b_f}
patchwork <- p1 / p2 / p3 / p4 / p5
ggsave(here("experiments/1_figures_main_ms/figure_2b-f_v2.pdf"))
patchwork
```

## Figure 3
Stable state with diversity in all functional groups.

```{r figure3}
ss_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_SS_data_1e6.RDS"))
sort(unique(ss_9s$CB_var_gmax_s))
sort(unique(ss_9s$SB_var_gmax_s))
ss_result <- ss_9s %>%
  filter(abs(CB_var_gmax_s - 0.028254848) < 0.0001,
         abs(SB_var_gmax_s - 0.084764545) < 0.0001,
         abs(PB_var_gmax_s - 0.084764545) < 0.0001)

temp <- ss_result$ssfind_result[[1]] %>%
  mutate(a = 10^a_O) %>%
  # arrange(a) %>%
  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  # select(-initial_N_CB, -a_O) %>%
  gather(species, quantity, 2:(ncol(.) - 2)) %>%
  mutate(
    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
    functional_group = case_when(
      str_detect(species, "CB_") ~ "CB",
      str_detect(species, "SB_") ~ "SB",
      str_detect(species, "PB_") ~ "PB"
    ),
    log10_quantity = log10(quantity + 1)
  )

num_strains <- temp %>%
  group_by(functional_group) %>%
  summarise(num = length(unique(species))) %>%
  na.omit()

num_CB_strains <- num_strains$num[num_strains$functional_group == "CB"]
num_SB_strains <- num_strains$num[num_strains$functional_group == "SB"]
num_PB_strains <- num_strains$num[num_strains$functional_group == "PB"]

line_width <- 2
```

### Figure 3a

```{r figure3a}
p1 <- temp %>%
  dplyr::filter(functional_group == "CB")  %>%
  mutate(species = factor(species, levels = unique(species))) %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  scale_colour_manual(values = colfunc_CB(num_CB_strains)) +
  guides(colour = guide_legend(ncol = 3)) +
  theme(legend.position="none") +
  ggtitle("(a) Cyanobacteria")
p1
```

### Figure 3b

```{r figure3b}

p2 <- temp %>%
  dplyr::filter(functional_group == "SB")  %>%
  mutate(species = factor(species, levels = unique(species))) %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  scale_colour_manual(values = colfunc_SB(num_SB_strains)) +
  guides(colour = guide_legend(ncol = 3)) +
  theme(legend.position="none") +
  ggtitle("(b) Sulfate reducing bacteria")
p2
```

### Figure 3c

```{r figure3c}
p3 <- temp %>%
  dplyr::filter(functional_group == "PB")  %>%
  mutate(species = factor(species, levels = unique(species))) %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  scale_colour_manual(values = colfunc_PB(num_PB_strains)) +
  guides(colour = guide_legend(ncol = 3)) +
  theme(legend.position="none") +
  ggtitle("(c) Phototrophic sulfur bacteria")
p3
```

### Figure 3d

```{r figure3d}
p4 <- temp %>%
  dplyr::filter(var_type == "Substrate", species == "O") %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  theme(legend.position="none") +
  ggtitle("(d) Oxygen concentration")
p4
```

### Figure 3e

```{r figure3e}
p5 <- temp %>%
  dplyr::filter(var_type == "Substrate", species == "SR") %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width, col = 6) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  theme(legend.position="none") +
  ggtitle("(e) Sulfide concentration")
p5
```

### Figure Assembled
```{r figure3a_f}
patchwork <- p1 / p2 / p3 / p4 / p5
ggsave(here("experiments/1_figures_main_ms/figure_3_v2.pdf"))
patchwork
```

## Figure 4
Shows effect of no diversity versus diversity in all functional groups.

```{r figure4}
ss_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_SS_data_1e6.RDS"))
sort(unique(ss_9s$CB_var_gmax_s))
sort(unique(ss_9s$SB_var_gmax_s))
ss_result_none <- ss_9s %>%
  filter(abs(CB_var_gmax_s - 0.0) < 0.0001,
         abs(SB_var_gmax_s - 0.0) < 0.0001,
         abs(PB_var_gmax_s - 0.0) < 0.0001)
ss_result_CB <- ss_9s %>%
  filter(abs(CB_var_gmax_s - 0.014958449) < 0.0001,
         abs(SB_var_gmax_s - 0.0) < 0.0001,
         abs(PB_var_gmax_s - 0.0) < 0.0001)
ss_result_SB <- ss_9s %>%
  filter(abs(CB_var_gmax_s - 0.0) < 0.0001,
         abs(SB_var_gmax_s - 0.044875347) < 0.0001,
         abs(PB_var_gmax_s - 0.0) < 0.0001)
ss_result_PB <- ss_9s %>%
  filter(abs(CB_var_gmax_s - 0.0) < 0.0001,
         abs(SB_var_gmax_s - 0.0) < 0.0001,
         abs(PB_var_gmax_s - 0.044875347) < 0.0001)
ss_result_CBSB <- ss_9s %>%
  filter(abs(CB_var_gmax_s - 0.014958449) < 0.0001,
         abs(SB_var_gmax_s - 0.044875347) < 0.0001,
         abs(PB_var_gmax_s - 0.0) < 0.0001)
ss_result_CBPB <- ss_9s %>%
  filter(abs(CB_var_gmax_s - 0.014958449) < 0.0001,
         abs(SB_var_gmax_s - 0.0) < 0.0001,
         abs(PB_var_gmax_s - 0.044875347) < 0.0001)
ss_result_SBPB <- ss_9s %>%
  filter(abs(CB_var_gmax_s - 0.0) < 0.0001,
         abs(SB_var_gmax_s - 0.044875347) < 0.0001,
         abs(PB_var_gmax_s - 0.044875347) < 0.0001)
ss_result_CBSBPB <- ss_9s %>%
  filter(abs(CB_var_gmax_s - 0.014958449) < 0.0001,
         abs(SB_var_gmax_s - 0.044875347) < 0.0001,
         abs(PB_var_gmax_s - 0.044875347) < 0.0001)

temp_none <- ss_result_none$ssfind_result[[1]] %>%
  mutate(a = 10^a_O) %>%
  # arrange(a) %>%
  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  # select(-initial_N_CB, -a_O) %>%
  gather(species, quantity, 2:(ncol(.) - 2)) %>%
  mutate(
    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
    functional_group = case_when(
      str_detect(species, "CB_") ~ "CB",
      str_detect(species, "SB_") ~ "SB",
      str_detect(species, "PB_") ~ "PB"
    ),
    log10_quantity = log10(quantity + 1)
  )

temp_CB <- ss_result_CB$ssfind_result[[1]] %>%
  mutate(a = 10^a_O) %>%
  # arrange(a) %>%
  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  # select(-initial_N_CB, -a_O) %>%
  gather(species, quantity, 2:(ncol(.) - 2)) %>%
  mutate(
    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
    functional_group = case_when(
      str_detect(species, "CB_") ~ "CB",
      str_detect(species, "SB_") ~ "SB",
      str_detect(species, "PB_") ~ "PB"
    ),
    log10_quantity = log10(quantity + 1)
  )
temp_SB <- ss_result_SB$ssfind_result[[1]] %>%
  mutate(a = 10^a_O) %>%
  # arrange(a) %>%
  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  # select(-initial_N_CB, -a_O) %>%
  gather(species, quantity, 2:(ncol(.) - 2)) %>%
  mutate(
    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
    functional_group = case_when(
      str_detect(species, "CB_") ~ "CB",
      str_detect(species, "SB_") ~ "SB",
      str_detect(species, "PB_") ~ "PB"
    ),
    log10_quantity = log10(quantity + 1)
  )
temp_PB <- ss_result_PB$ssfind_result[[1]] %>%
  mutate(a = 10^a_O) %>%
  # arrange(a) %>%
  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  # select(-initial_N_CB, -a_O) %>%
  gather(species, quantity, 2:(ncol(.) - 2)) %>%
  mutate(
    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
    functional_group = case_when(
      str_detect(species, "CB_") ~ "CB",
      str_detect(species, "SB_") ~ "SB",
      str_detect(species, "PB_") ~ "PB"
    ),
    log10_quantity = log10(quantity + 1)
  )
temp_CBSB <- ss_result_CBSB$ssfind_result[[1]] %>%
  mutate(a = 10^a_O) %>%
  # arrange(a) %>%
  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  # select(-initial_N_CB, -a_O) %>%
  gather(species, quantity, 2:(ncol(.) - 2)) %>%
  mutate(
    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
    functional_group = case_when(
      str_detect(species, "CB_") ~ "CB",
      str_detect(species, "SB_") ~ "SB",
      str_detect(species, "PB_") ~ "PB"
    ),
    log10_quantity = log10(quantity + 1)
  )
temp_CBPB <- ss_result_CBPB$ssfind_result[[1]] %>%
  mutate(a = 10^a_O) %>%
  # arrange(a) %>%
  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  # select(-initial_N_CB, -a_O) %>%
  gather(species, quantity, 2:(ncol(.) - 2)) %>%
  mutate(
    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
    functional_group = case_when(
      str_detect(species, "CB_") ~ "CB",
      str_detect(species, "SB_") ~ "SB",
      str_detect(species, "PB_") ~ "PB"
    ),
    log10_quantity = log10(quantity + 1)
  )
temp_SBPB <- ss_result_SBPB$ssfind_result[[1]] %>%
  mutate(a = 10^a_O) %>%
  # arrange(a) %>%
  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  # select(-initial_N_CB, -a_O) %>%
  gather(species, quantity, 2:(ncol(.) - 2)) %>%
  mutate(
    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
    functional_group = case_when(
      str_detect(species, "CB_") ~ "CB",
      str_detect(species, "SB_") ~ "SB",
      str_detect(species, "PB_") ~ "PB"
    ),
    log10_quantity = log10(quantity + 1)
  )
temp_CBSBPB <- ss_result_CBSBPB$ssfind_result[[1]] %>%
  mutate(a = 10^a_O) %>%
  # arrange(a) %>%
  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  # select(-initial_N_CB, -a_O) %>%
  gather(species, quantity, 2:(ncol(.) - 2)) %>%
  mutate(
    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
    functional_group = case_when(
      str_detect(species, "CB_") ~ "CB",
      str_detect(species, "SB_") ~ "SB",
      str_detect(species, "PB_") ~ "PB"
    ),
    log10_quantity = log10(quantity + 1)
  )

line_width <- 2.5
```
### Figure 4a

```{r figure4_a}
p1 <- temp_none %>%
  dplyr::filter(var_type == "Substrate", species == "O") %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  geom_path(data = filter(temp_CB, var_type == "Substrate", species == "O"),
            col = "black", lwd = line_width - 1.5) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  theme(legend.position="none") +
  ggtitle("(a) No diversity versus diversity in only CB") +
  geom_vline(xintercept = c(-8, 0), col = "grey", lwd = 3)
p1
```
### Figure 4b

```{r figure4_b}
p2 <- temp_none %>%
  dplyr::filter(var_type == "Substrate", species == "O") %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  geom_path(data = filter(temp_SB, var_type == "Substrate", species == "O"),
            col = "black", lwd = line_width - 1.5) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  theme(legend.position="none") +
  ggtitle("(a) No diversity versus diversity in only SB") +
  geom_vline(xintercept = c(-8, 0), col = "grey", lwd = 3)
p2
```
### Figure 4c

```{r figure4_c}
p3 <- temp_none %>%
  dplyr::filter(var_type == "Substrate", species == "O") %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  geom_path(data = filter(temp_PB, var_type == "Substrate", species == "O"),
            col = "black", lwd = line_width - 1.5) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  theme(legend.position="none") +
  ggtitle("(a) No diversity versus diversity in only PB") +
  geom_vline(xintercept = c(-8, 0), col = "grey", lwd = 3)
p3
```

### Figure 4d

```{r figure4_d}
p4 <- temp_none %>%
  dplyr::filter(var_type == "Substrate", species == "O") %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  geom_path(data = filter(temp_CBSB, var_type == "Substrate", species == "O"),
            col = "black", lwd = line_width - 1.5) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  theme(legend.position="none") +
  ggtitle("(b) No diversity versus diversity in only CB & SB") +
  geom_vline(xintercept = c(-8, 0), col = "grey", lwd = 3)
p4
```

### Figure 4e

```{r figure4_e}
p5 <- temp_none %>%
  dplyr::filter(var_type == "Substrate", species == "O") %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  geom_path(data = filter(temp_CBPB, var_type == "Substrate", species == "O"),
            col = "black", lwd = line_width - 1.5) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  theme(legend.position="none") +
  ggtitle("(b) No diversity versus diversity in only CB & PB") +
  geom_vline(xintercept = c(-8, 0), col = "grey", lwd = 3)
```

### Figure 4f

```{r figure4_f}
p6 <- temp_none %>%
  dplyr::filter(var_type == "Substrate", species == "O") %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  geom_path(data = filter(temp_SBPB, var_type == "Substrate", species == "O"),
            col = "black", lwd = line_width - 1.5) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  theme(legend.position="none") +
  ggtitle("(b) No diversity versus diversity in only SB & PB") +
  geom_vline(xintercept = c(-8, 0), col = "grey", lwd = 3)
p6
```

### Figure 4g

```{r figure4_g}
p7 <- temp_none %>%
  dplyr::filter(var_type == "Substrate", species == "O") %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  geom_path(data = filter(temp_CBSBPB, var_type == "Substrate", species == "O"),
            col = "black", lwd = line_width - 1.5) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  theme(legend.position="none") +
  ggtitle("(c) No diversity versus diversity all functional groups") +
  geom_vline(xintercept = c(-8, 0), col = "grey", lwd = 3)
p7
```

### Assembled

```{r figure4a_f}

p <- ( p1 + p2 + p3 ) / ( p4 + p5 + p6 ) / (plot_spacer() + p7 + plot_spacer())
p
ggsave(here("experiments/1_figures_main_ms/figure_4_v2.pdf"),
       width = 6, height = 5)
p
```

## Figure 5
Region of bistability by diversity and number of strains.

```{r figure5_prepare}
gc()
if (file.exists(here("experiments/0_ss_finding/temporal_method/data/all_stab_results_small.RDS"))) {
  all_stab_results_small <- readRDS(here("experiments/0_ss_finding/temporal_method/data/all_stab_results_small.RDS"))
  all_stab_results <- readRDS(here("experiments/0_ss_finding/temporal_method/data/all_stab_results.RDS"))

} else {
  ss_2s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/2_strain_SS_data_1e6.RDS"))
  stab_2s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/2_strain_stab_data_1e6.RDS")) %>%
    mutate(num_strains = 2)
  ss_2s_sub1 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/2_strain_SS_data_1e6_sub1.RDS"))
  stab_2s_sub1 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/2_strain_stab_data_1e6_sub1.RDS")) %>%
    mutate(num_strains = 2)

  ss_3s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/3_strain_SS_data_1e6.RDS"))
  stab_3s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/3_strain_stab_data_1e6.RDS")) %>%
    mutate(num_strains = 3) 
  ss_3s_sub1 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/3_strain_SS_data_1e6_sub1.RDS"))
  stab_3s_sub1 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/3_strain_stab_data_1e6_sub1.RDS")) %>%
    mutate(num_strains = 3)

  ss_6s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/6_strain_SS_data_1e6.RDS"))
  stab_6s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/6_strain_stab_data_1e6.RDS")) %>%
    mutate(num_strains = 6) 
  ss_6s_sub1 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/6_strain_SS_data_1e6_sub1.RDS"))
  stab_6s_sub1 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/6_strain_stab_data_1e6_sub1.RDS")) %>%
    mutate(num_strains = 6)

  ss_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_SS_data_1e6.RDS"))
  stab_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_stab_data_1e6.RDS")) %>%
    mutate(num_strains = 9) 
  ss_9s_sub1 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_SS_data_1e6_sub1.RDS"))
  stab_9s_sub1 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_stab_data_1e6_sub1.RDS")) %>%
    mutate(num_strains = 9)

  all_stab <- stab_2s %>%
    bind_rows(stab_2s_sub1) %>%
    bind_rows(stab_3s) %>%
    bind_rows(stab_3s_sub1) %>%
    bind_rows(stab_6s) %>%
    bind_rows(stab_6s_sub1) %>%
    bind_rows(stab_9s) %>%
    bind_rows(stab_9s_sub1)

  #all_stab <- stab_9s

  CB_vars <- unique(all_stab$CB_var_gmax_s)
  SB_vars <- unique(all_stab$SB_var_gmax_s)
  PB_vars <- unique(all_stab$PB_var_gmax_s)

  CB_all_stab <- all_stab %>%
    filter(SB_var_gmax_s == 0,
           PB_var_gmax_s == 0) %>%
    ungroup() %>%
    mutate(var_treat = "CB",
           var_gmax = CB_var_gmax_s,
           stand_var = var_gmax / max(var_gmax))
  SB_all_stab <- all_stab %>%
    filter(CB_var_gmax_s == 0,
           PB_var_gmax_s == 0)  %>%
    ungroup() %>%
    mutate(var_treat = "SB",
           var_gmax = SB_var_gmax_s,
           stand_var = var_gmax / max(var_gmax))
  PB_all_stab <- all_stab %>%
    filter(CB_var_gmax_s == 0,
           SB_var_gmax_s == 0) %>%
    ungroup()  %>%
    mutate(var_treat = "PB",
           var_gmax = PB_var_gmax_s,
           stand_var = var_gmax / max(var_gmax))

  for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
                     SB_var_gmax_s = sort(SB_vars))
  CBSB_all_stab <- all_stab %>%
    right_join(for_join)  %>%
    ungroup() %>%
    mutate(var_treat = "CB-SB",
           var_gmax = CB_var_gmax_s,
           stand_var = var_gmax / max(var_gmax)) %>%
    filter(PB_var_gmax_s == 0)

  for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
                     PB_var_gmax_s = sort(PB_vars))
  CBPB_all_stab <- all_stab %>%
    right_join(for_join)  %>%
    ungroup() %>%
    mutate(var_treat = "CB-PB",
           var_gmax = CB_var_gmax_s,
           stand_var = var_gmax / max(var_gmax)) %>%
    filter(SB_var_gmax_s == 0)

  for_join <- tibble(SB_var_gmax_s = sort(SB_vars),
                     PB_var_gmax_s = sort(PB_vars))
  SBPB_all_stab <- all_stab %>%
    right_join(for_join)  %>%
    ungroup() %>%
    mutate(var_treat = "SB-PB",
           var_gmax = SB_var_gmax_s,
           stand_var = var_gmax / max(var_gmax)) %>%
    filter(CB_var_gmax_s == 0)

  for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
                     SB_var_gmax_s = sort(SB_vars),
                     PB_var_gmax_s = sort(PB_vars))
  CBSBPB_all_stab <- all_stab %>%
    right_join(for_join)  %>%
    ungroup() %>%
    mutate(var_treat = "CB-SB-PB",
           var_gmax = CB_var_gmax_s,
           stand_var = var_gmax / max(var_gmax))

  all_stab_results <- CB_all_stab %>%
    bind_rows(SB_all_stab) %>%
    bind_rows(PB_all_stab) %>%
    bind_rows(CBSB_all_stab) %>%
    bind_rows(CBPB_all_stab) %>%
    bind_rows(SBPB_all_stab) %>%
    bind_rows(CBSBPB_all_stab)

  all_stab_results <- all_stab_results %>%
    mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB",
                                                                  "SB",
                                                                  "PB",
                                                                  "CB-SB",
                                                                  "CB-PB",
                                                                  "SB-PB",
                                                                  "CB-SB-PB")))

  all_stab_results_small <- select(all_stab_results, -7:-12)

  saveRDS(
    all_stab_results_small,
    here("experiments/0_ss_finding/temporal_method/data/all_stab_results_small.RDS")
  )
  saveRDS(
    all_stab_results,
    here("experiments/0_ss_finding/temporal_method/data/all_stab_results.RDS")
  )
}

```

```{r figure5}
p <- all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(num_strains == 9) %>%
  filter(Species == "CB_tot") %>%
  ggplot(aes(x = stand_var,
             #col = as.factor(num_strains)
             )) +
  geom_line(aes(y = hyst_min_log), lwd = 1, alpha = 0.3) +
  geom_line(aes(y = hyst_max_log), lwd = 1, alpha = 0.3) +
  facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
  xlab("Standardised amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  guides(col = guide_legend(title="Number of strains")) +
  theme(
    legend.position="top"
    #strip.background = element_blank(),
    #strip.text.x = element_blank()
  ) +
  geom_hline(yintercept = c(-8, 0), col = "grey", lwd = 3)
p
ggsave(here("experiments/1_figures_main_ms/figure_5_v2_9strain_only.pdf"),
       width = 10, height = 8)
p
```

### Figure 5 all strains
```{r figure5_all}
p <- all_stab_results %>%
  #filter(var_treat == "CB") %>%
  #filter(num_strains == 9) %>%
  filter(Species == "CB_tot") %>%
  ggplot(aes(x = stand_var,
             col = as.factor(num_strains)
  )) +
  geom_line(aes(y = hyst_min_log), lwd = 1, alpha = 0.3) +
  geom_line(aes(y = hyst_max_log), lwd = 1, alpha = 0.3) +
  facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
  xlab("Standardised amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  guides(col = guide_legend(title="Number of strains")) +
  theme(
    legend.position="top"
    #strip.background = element_blank(),
    #strip.text.x = element_blank()
  ) +
  geom_hline(yintercept = c(-8, 0), col = "grey", lwd = 3)

p
ggsave(here("experiments/1_figures_main_ms/figure_5_v2_allstrains.pdf"),
       width = 10, height = 8)
p

agg_stab_res <- all_stab_results_small %>%
  mutate(Strain = str_sub(Species, 1, 2)) %>%
  group_by(Strain, var_treat, var_gmax, num_strains) %>%
  summarise(hyst_min_log = min(hyst_min_log),
            hyst_max_log = max(hyst_max_log))
agg_stab_res %>%
  #filter(var_treat == "CB") %>%
  filter(Strain == "CB") %>%
  ggplot(aes(x = var_gmax,
             col = as.factor(num_strains))) +
  geom_line(aes(y = hyst_min_log), lwd = 1, alpha = 0.3) +
  geom_line(aes(y = hyst_max_log), lwd = 1, alpha = 0.3) +
  facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  guides(col = guide_legend(title="Number of strains")) +
  theme(
    legend.position="top"
    #strip.background = element_blank(),
    #strip.text.x = element_blank()
  ) +
  geom_hline(yintercept = c(-8, 0), col = "grey", lwd = 3)

temp <- all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O",
         var_treat == "SB-PB",
         num_strains == 9) %>%
  ggplot(aes(x = var_gmax,
             col = as.factor(num_strains))) +
  geom_line(aes(y = hyst_min_log)) +
  geom_line(aes(y = hyst_max_log)) +
  facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  guides(col = guide_legend(title="Number of strains")) +
  theme(
    legend.position="top"
    #strip.background = element_blank(),
    #strip.text.x = element_blank()
  ) +
  geom_hline(yintercept = c(-8, 0), col = "grey", lwd = 3)
```

## test1 :: Just SB
Looking at some examples
With 3 strains SB_var_gmax_s = 0.07153598 is very different to adjacent
0.06960258 and 0.07346939

```{r test1_justSB}
ss_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/2_strain_SS_data_1e6_sub1.RDS"))
sort(unique(ss_9s$CB_var_gmax_s))
sort(unique(ss_9s$SB_var_gmax_s))
ss_result <- ss_9s %>%
  filter(abs(CB_var_gmax_s - 0) < 0.0001,
         abs(SB_var_gmax_s - 0.06960258) < 0.0001,
         abs(PB_var_gmax_s - 0) < 0.0001)
ss_result$pars[[1]]$SB
ss_result <- ss_9s %>%
  filter(abs(CB_var_gmax_s - 0) < 0.0001,
         abs(SB_var_gmax_s - 0.07153598) < 0.0001,
         abs(PB_var_gmax_s - 0) < 0.0001)
ss_result$pars[[1]]$SB
ss_result <- ss_9s %>%
  filter(abs(CB_var_gmax_s - 0) < 0.0001,
         abs(SB_var_gmax_s - 0.07346939) < 0.0001,
         abs(PB_var_gmax_s - 0) < 0.0001)
ss_result$pars[[1]]$SB

temp <- ss_result$ssfind_result[[1]] %>%
  mutate(a = 10^a_O) %>%
  # arrange(a) %>%
  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  # select(-initial_N_CB, -a_O) %>%
  gather(species, quantity, 2:(ncol(.) - 2)) %>%
  mutate(
    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
    functional_group = case_when(
      str_detect(species, "CB_") ~ "CB",
      str_detect(species, "SB_") ~ "SB",
      str_detect(species, "PB_") ~ "PB"
    ),
    log10_quantity = log10(quantity + 1)
  )

num_strains <- temp %>%
  group_by(functional_group) %>%
  summarise(num = length(unique(species))) %>%
  na.omit()

num_CB_strains <- num_strains$num[num_strains$functional_group == "CB"]
num_SB_strains <- num_strains$num[num_strains$functional_group == "SB"]
num_PB_strains <- num_strains$num[num_strains$functional_group == "PB"]

line_width <- 2

p1 <- temp %>%
  dplyr::filter(functional_group == "CB")  %>%
  mutate(species = factor(species, levels = unique(species))) %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  scale_colour_manual(values = colfunc_CB(num_CB_strains)) +
  guides(colour = guide_legend(ncol = 3)) +
  theme(legend.position="none") +
  ggtitle("(b) Cyanobacteria")
#p1# p1

p2 <- temp %>%
  dplyr::filter(functional_group == "SB")  %>%
  mutate(species = factor(species, levels = unique(species))) %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  scale_colour_manual(values = colfunc_SB(num_SB_strains)) +
  guides(colour = guide_legend(ncol = 3)) +
  theme(legend.position="none") +
  ggtitle("(c) Sulfate reducing bacteria")

p3 <- temp %>%
  dplyr::filter(functional_group == "PB")  %>%
  mutate(species = factor(species, levels = unique(species))) %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  scale_colour_manual(values = colfunc_PB(num_PB_strains)) +
  guides(colour = guide_legend(ncol = 3)) +
  theme(legend.position="none") +
  ggtitle("(d) Phototrophic sulfur bacteria")

p4 <- temp %>%
  dplyr::filter(var_type == "Substrate", species == "O") %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  theme(legend.position="none") +
  ggtitle("(e) Oxygen concentration")

p5 <- temp %>%
  dplyr::filter(var_type == "Substrate", species == "SR") %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width, col = 6) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  theme(legend.position="none") +
  ggtitle("(f) Sulfide concentration")

patchwork <- p1 / p2 / p3 / p4 / p5
patchwork
#ggsave(here("experiments/1_figures_main_ms/figure_3_v2.pdf"))

```

## test1 :: Just PB
Looking at some examples
With 3 strains SB_var_gmax_s = 0.07153598 is very different to adjacent 0.06960258 and 0.07346939
```{r test1_justPB}

ss_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_SS_data_1e6.RDS"))
sort(unique(ss_9s$CB_var_gmax_s))
sort(unique(ss_9s$SB_var_gmax_s))
sort(unique(ss_9s$PB_var_gmax_s))
ss_result <- ss_9s %>%
  filter(abs(CB_var_gmax_s - 0) < 0.0001,
         abs(SB_var_gmax_s - 0) < 0.0001,
         abs(PB_var_gmax_s - 0.06960258) < 0.0001)
ss_result$pars[[1]]$SB
ss_result <- ss_9s %>%
  filter(abs(CB_var_gmax_s - 0) < 0.0001,
         abs(SB_var_gmax_s - 0) < 0.0001,
         abs(PB_var_gmax_s - 0.07153598) < 0.0001)
ss_result$pars[[1]]$SB
ss_result <- ss_9s %>%
  filter(abs(CB_var_gmax_s - 0) < 0.0001,
         abs(SB_var_gmax_s - 0) < 0.0001,
         abs(PB_var_gmax_s - 0.07346939) < 0.0001)
ss_result$pars[[1]]$SB

temp <- ss_result$ssfind_result[[1]] %>%
  mutate(a = 10^a_O) %>%
  # arrange(a) %>%
  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  # select(-initial_N_CB, -a_O) %>%
  gather(species, quantity, 2:(ncol(.) - 2)) %>%
  mutate(
    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
    functional_group = case_when(
      str_detect(species, "CB_") ~ "CB",
      str_detect(species, "SB_") ~ "SB",
      str_detect(species, "PB_") ~ "PB"
    ),
    log10_quantity = log10(quantity + 1)
  )

num_strains <- temp %>%
  group_by(functional_group) %>%
  summarise(num = length(unique(species))) %>%
  na.omit()

num_CB_strains <- num_strains$num[num_strains$functional_group == "CB"]
num_SB_strains <- num_strains$num[num_strains$functional_group == "SB"]
num_PB_strains <- num_strains$num[num_strains$functional_group == "PB"]

line_width <- 2

p1 <- temp %>%
  dplyr::filter(functional_group == "CB")  %>%
  mutate(species = factor(species, levels = unique(species))) %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  scale_colour_manual(values = colfunc_CB(num_CB_strains)) +
  guides(colour = guide_legend(ncol = 3)) +
  theme(legend.position="none") +
  ggtitle("(b) Cyanobacteria")
#p1# p1

p2 <- temp %>%
  dplyr::filter(functional_group == "SB")  %>%
  mutate(species = factor(species, levels = unique(species))) %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  scale_colour_manual(values = colfunc_SB(num_SB_strains)) +
  guides(colour = guide_legend(ncol = 3)) +
  theme(legend.position="none") +
  ggtitle("(c) Sulfate reducing bacteria")

p3 <- temp %>%
  dplyr::filter(functional_group == "PB")  %>%
  mutate(species = factor(species, levels = unique(species))) %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  scale_colour_manual(values = colfunc_PB(num_PB_strains)) +
  guides(colour = guide_legend(ncol = 3)) +
  theme(legend.position="none") +
  ggtitle("(d) Phototrophic sulfur bacteria")

p4 <- temp %>%
  dplyr::filter(var_type == "Substrate", species == "O") %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  theme(legend.position="none") +
  ggtitle("(e) Oxygen concentration")

p5 <- temp %>%
  dplyr::filter(var_type == "Substrate", species == "SR") %>%
  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
  geom_path(lwd = line_width, col = 6) +
  ##ylab("log10(quantity [cells])") +
  ylab("Log(Quantity)") +
  xlab("Oxygen diffusivity") +
  theme(legend.position="none") +
  ggtitle("(f) Sulfide concentration")

patchwork <- p1 / p2 / p3 / p4 / p5
patchwork
#ggsave(here("experiments/1_figures_main_ms/figure_3_v2.pdf"))
```

### 2022-01-25 experiments/2_supplement/html_supplement.Rmd
cleaning up, getting ready!

@@
 
+# Creating among strain diversity
+
+Here we provide additional description of the method used to create strain variation within functional groups. The following should be read only after the relevant sections of the main text.
+
+Take for example the cyanobacteria functional group, a reference maximum growth rate parameter $G_{max,CB}$ and a reference tolerance parameter $h_{SR,CB}$.
+Recall that amount of among strain variation is controlled by the two meta-parameters $Div_{G_{max,CB}}$ and $Div_{h_{SR,CB}}$.
+To create a tradeoff, the two meta-parameters were always of different sign.
+The among strain variation was calculated such that the growth rate of strain $i = 1$ was a factor $1/({2Div_{G_{max,CB}}})$ of the reference growth rate, and the growth rate of the $i = n$ strain was a factor $2Div_{G_{max,CB}}$ of the reference growth rate.
+The growth rate of the $i = {2,...n-1}$ other strains was the reference growth rate multiplied by a factor that was equally distributed between the factor of the $i = 1$ and $i = n$ strain.
+This implementation of the variation and trade-off has the assumption of a linear trade-off of log-log transformed among-strain variation.
+Hence, for example, with the reference growth rate $G_{max,CB} = 0.05$, among strain variation of $Div_{G_{max,CB}} = 1$, and nine strains ($n = 9$), the growth rates of the nine strains are 0.025, 0.03, 0.035, 0.042, 0.05, 0.059, 0.071, 0.084, 0.1.
+Put another way, the growth rate parameter of the $i$-th of the $n$ strains in a functional group was calculated as $G_{max,i} = D_i * G_{max}$ where $D_i$ is the $i$-th element of the set $D = {2f(x)Div_{G_{max}} |x ∈ N, x ≤ n}$, where $f(x) = (x − (n + 1)/2)/((n − 1)/2)$.
+
+This procedure ensures that the range of trait values is independent of the number of strains.
+When there were only two strains, the two strains took the minimum and maximum traits values, as defined by the $Div$ variable for that trait.
+When there were three strains, one had the minimum trait value, one the maximum, and one the mean.
+With nine strains, one had the minimum trait value, one the maximum, one the mean, and three were equally spaced (on log scale) between the minimum and the mean, and the remaining three between the maximum and the mean.
+
 # Visualising among strain diversity
 
-The method for creating among strain diversity is explained in the main report. Here we show three visualisations, one for nine strains, one for three, and one for two.
+Here we show three visualisations, one for nine strains, one for three, and one for two.
 
@@
 
+## Method for finding stable states
+
 We now discuss two approaches for finding how the stable state of the system varies along the gradient of oxygen diffusivity when there exists the possibility of multiple stable states.
@@
 
-## Replication method, no diversity
+### Replication method, no diversity
 
@@
 
-## Temporal method, no diversity
+### Temporal method, no diversity
 
@@
 
-## Both methods overlaid, no diversity
+### Both methods overlaid, no diversity
 
@@
 
-## Effect of diversity, replication method
+### Effect of diversity, replication method
 
@@
 
+### Further information
+
+Here we give some further thoughts regarding the comparison of the temporal and replication method for stable state finding.
+
+A particularly notable difference between the two approaches is in the initial condition.
+In the temporal approach, the initial condition at a new level of oxygen diffusivity is the stable state at the previous level of oxygen diffusivity, while in the approach of Bush et al (2017) the initial conditions are fixed and arbitrary (though this approach is still useful for illustrating the bistability of the system).
+This difference in initial conditions increases the region of bistability in the temporal approach because as a tipping point approaches, the functional group that will dominate after the regime shift starts from much lower abundances than in the approach by Bush et al (2017) and thus requires stronger amelioration of the environment to take over.
+Nevertheless, our main conclusions about the effects of functional trait diversity are the same using either approach.
+
+The temporal approach is particularly useful when investigating the effects of strain richness.
+In preliminary simulations using the Bush et al (2017) approach, we found the counterintuitive result that higher strain richness led to lower resilience.
+We then recalled that we chose to divide the initial total abundance of the cyanobacterial (CB) functional group equally among the strains (termed a substitutive design in biodiversity manipulation experiments).
+This meant that the most tolerant CB strain in a three-strain simulation had higher initial abundance than the same most tolerant CB strain in a nine-strain simulation.
+The greater abundance of the most CB tolerant strain made it possible for a three-strain system to develop to be oxic, whereas the nine-strain system developed to be anoxic, despite identical range of trait variation.
+We could have chosen to do otherwise, for example start with the least tolerant strains of cyanobacteria as more abundant when the system started with high cyanobacterial abundance, and the most tolerant strain as more abundant when the system starts with low cyanobacterial abundance.
+Using the temporal approach removed the need to specify initial abundances (except the very first one), and therefore results were not so determined by the assumptions used to determine the initial conditions.
+
+## Effect of immigration / minimum abundance event
+
+The simulations include two methods to prevent very low densities.
+One is to make a floor density; if densities go below this, then they are set to that floor value.
+Another is to regularly add a density of 1 to all biological state variables.
+Here are the results for adding 1.
+
+```{r}
+## Figure 5 ----
+## Region of bistability by diversity and number of strains.
+
+# ss_2s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/2_strain_SS_data_1e6.RDS"))
+# stab_2s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/2_strain_stab_data_1e6.RDS")) %>%
+#   mutate(num_strains = 2)
+# ss_2s_sub1 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/2_strain_SS_data_1e6_sub1.RDS"))
+# stab_2s_sub1 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/2_strain_stab_data_1e6_sub1.RDS")) %>%
+#   mutate(num_strains = 2)
+# 
+# 
+# ss_3s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/3_strain_SS_data_1e6.RDS"))
+# stab_3s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/3_strain_stab_data_1e6.RDS")) %>%
+#   mutate(num_strains = 3) 
+# ss_3s_sub1 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/3_strain_SS_data_1e6_sub1.RDS"))
+# stab_3s_sub1 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/3_strain_stab_data_1e6_sub1.RDS")) %>%
+#   mutate(num_strains = 3)
+# 
+# 
+# 
+# 
+# ss_6s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/6_strain_SS_data_1e6.RDS"))
+# stab_6s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/6_strain_stab_data_1e6.RDS")) %>%
+#   mutate(num_strains = 6) 
+# ss_6s_sub1 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/6_strain_SS_data_1e6_sub1.RDS"))
+# stab_6s_sub1 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/6_strain_stab_data_1e6_sub1.RDS")) %>%
+#   mutate(num_strains = 6)
+#
+
+# expt_res <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_SS_data_1e6_eventdef2.RDS"))
+# num_cores <- 8
+# expt_res <- expt_res %>%
+#   mutate(ssfind_result = list(get_total_bio(ssfind_result)))
+# cluster1 <- multidplyr::new_cluster(num_cores)
+# multidplyr::cluster_library(cluster1, c("microxanox", "dplyr"))
+# system.time({
+#   stab_data <-  expt_res %>%
+#     multidplyr::partition(cluster1) %>%
+#     mutate(stability_measures = list(get_stability_measures_new(ssfind_result))) %>%
+#     collect() %>%
+#     unnest(cols = c(stability_measures)) 
+# })
+# saveRDS(stab_data, here("experiments/0_ss_finding/temporal_method/data/9_strain_stab_data_1e6_eventdef2.RDS"))
+
+stab_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_stab_data_1e6_eventdef2.RDS")) %>%
+  mutate(num_strains = 9)
+
+stab_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_stab_data_1e6_eventdef2.RDS")) %>%
+  mutate(num_strains = 9)
+
+#ss_9s_sub1 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_SS_data_1e6_sub1.RDS"))
+#stab_9s_sub1 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_stab_data_1e6_sub1.RDS")) %>%
+#  mutate(num_strains = 9)
+
+#stab_9s_diff3 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_stab_data_1e6_diff3.RDS")) %>%
+#  mutate(num_strains = 9)
+
+# all_stab <- stab_2s %>%
+#   bind_rows(stab_2s_sub1) %>%
+#   bind_rows(stab_3s) %>%
+#   bind_rows(stab_3s_sub1) %>%
+#   bind_rows(stab_6s) %>%
+#   bind_rows(stab_6s_sub1) %>%
+#   bind_rows(stab_9s) %>%
+#   bind_rows(stab_9s_sub1) %>%
+#   bind_rows(stab_9s_diff3)
+
+all_stab <- stab_9s
+
+CB_vars <- unique(all_stab$CB_var_gmax_s)
+SB_vars <- unique(all_stab$SB_var_gmax_s)
+PB_vars <- unique(all_stab$PB_var_gmax_s)
+
+CB_all_stab <- all_stab %>%
+  filter(SB_var_gmax_s == 0,
+         PB_var_gmax_s == 0) %>%
+  ungroup() %>%
+  mutate(var_treat = "CB",
+         var_gmax = CB_var_gmax_s,
+         stand_var = var_gmax / max(var_gmax))
+SB_all_stab <- all_stab %>%
+  filter(CB_var_gmax_s == 0,
+         PB_var_gmax_s == 0)  %>%
+  ungroup() %>%
+  mutate(var_treat = "SB",
+         var_gmax = SB_var_gmax_s,
+         stand_var = var_gmax / max(var_gmax))
+PB_all_stab <- all_stab %>%
+  filter(CB_var_gmax_s == 0,
+         SB_var_gmax_s == 0) %>%
+  ungroup()  %>%
+  mutate(var_treat = "PB",
+         var_gmax = PB_var_gmax_s,
+         stand_var = var_gmax / max(var_gmax))
+
+for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
+                   SB_var_gmax_s = sort(SB_vars))
+CBSB_all_stab <- all_stab %>%
+  right_join(for_join)  %>%
+  ungroup() %>%
+  mutate(var_treat = "CB-SB",
+         var_gmax = CB_var_gmax_s,
+         stand_var = var_gmax / max(var_gmax)) %>%
+  filter(PB_var_gmax_s == 0)
+
+for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
+                   PB_var_gmax_s = sort(PB_vars))
+CBPB_all_stab <- all_stab %>%
+  right_join(for_join)  %>%
+  ungroup() %>%
+  mutate(var_treat = "CB-PB",
+         var_gmax = CB_var_gmax_s,
+         stand_var = var_gmax / max(var_gmax)) %>%
+  filter(SB_var_gmax_s == 0)
+
+for_join <- tibble(SB_var_gmax_s = sort(SB_vars),
+                   PB_var_gmax_s = sort(PB_vars))
+SBPB_all_stab <- all_stab %>%
+  right_join(for_join)  %>%
+  ungroup() %>%
+  mutate(var_treat = "SB-PB",
+         var_gmax = SB_var_gmax_s,
+         stand_var = var_gmax / max(var_gmax)) %>%
+  filter(CB_var_gmax_s == 0)
+
+for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
+                   SB_var_gmax_s = sort(SB_vars),
+                   PB_var_gmax_s = sort(PB_vars))
+CBSBPB_all_stab <- all_stab %>%
+  right_join(for_join)  %>%
+  ungroup() %>%
+  mutate(var_treat = "CB-SB-PB",
+         var_gmax = CB_var_gmax_s,
+         stand_var = var_gmax / max(var_gmax))
+
+all_stab_results <- CB_all_stab %>%
+  bind_rows(SB_all_stab) %>%
+  bind_rows(PB_all_stab) %>%
+  bind_rows(CBSB_all_stab) %>%
+  bind_rows(CBPB_all_stab) %>%
+  bind_rows(SBPB_all_stab) %>%
+  bind_rows(CBSBPB_all_stab)
+
+all_stab_results <- all_stab_results %>%
+  mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB",
+                                                                "SB",
+                                                                "PB",
+                                                                "CB-SB",
+                                                                "CB-PB",
+                                                                "SB-PB",
+                                                                "CB-SB-PB")))
+
+all_stab_results_small <- select(all_stab_results, -7:-12)
+
+#saveRDS(all_stab_results_small, here("experiments/0_ss_finding/temporal_method/data/all_stab_results_small.RDS"))
+
+all_stab_results %>%
+  #filter(var_treat == "CB") %>%
+  filter(num_strains == 9) %>%
+  filter(Species == "SB_tot") %>%
+  ggplot(aes(x = stand_var,
+             #col = as.factor(num_strains)
+             )) +
+  geom_line(aes(y = hyst_min_log), lwd = 0.5, alpha = 0.8) +
+  geom_line(aes(y = hyst_max_log), lwd = 0.5, alpha = 0.8) +
+  geom_ribbon(aes(ymin = hyst_min_log, ymax = hyst_max_log), col = "gray", alpha = 0.2) +
+  facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
+  xlab("Standardised amount of trait variation\n[see text for units]") +
+  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
+  labs(fill = "Variation in\nonly these\nfunctional groups") +
+  coord_flip() +
+  guides(col = guide_legend(title="Number of strains")) +
+  theme_bw() +
+  theme(
+    legend.position="top",
+    panel.background = element_blank(),
+    #strip.text.x = element_blank()
+  ) +
+  geom_hline(yintercept = c(-8, 0), col = "grey", lwd = 3) +
+  ggtitle("Bistability region for total SB density")
+
+#ggsave(here("experiments/1_figures_main_ms/figure_5_v2_9strain_only.pdf"),
+#       width = 10, height = 8)
+
+```
+
 ## Effect of simulation duration
+
+### A case where 1'000'000 hours is not long enough
 
@@
 
+### Shorter simulation times
+
+Here 1e4 hours at each oxygen diffusivity level:
+
+```{r}
+## Figure 5 ----
+## Region of bistability by diversity and number of strains.
+
+# ss_2s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/2_strain_SS_data_1e6.RDS"))
+# stab_2s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/2_strain_stab_data_1e6.RDS")) %>%
+#   mutate(num_strains = 2)
+# ss_2s_sub1 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/2_strain_SS_data_1e6_sub1.RDS"))
+# stab_2s_sub1 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/2_strain_stab_data_1e6_sub1.RDS")) %>%
+#   mutate(num_strains = 2)
+# 
+# 
+# ss_3s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/3_strain_SS_data_1e6.RDS"))
+# stab_3s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/3_strain_stab_data_1e6.RDS")) %>%
+#   mutate(num_strains = 3) 
+# ss_3s_sub1 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/3_strain_SS_data_1e6_sub1.RDS"))
+# stab_3s_sub1 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/3_strain_stab_data_1e6_sub1.RDS")) %>%
+#   mutate(num_strains = 3)
+# 
+# 
+# 
+# 
+# ss_6s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/6_strain_SS_data_1e6.RDS"))
+# stab_6s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/6_strain_stab_data_1e6.RDS")) %>%
+#   mutate(num_strains = 6) 
+# ss_6s_sub1 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/6_strain_SS_data_1e6_sub1.RDS"))
+# stab_6s_sub1 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/6_strain_stab_data_1e6_sub1.RDS")) %>%
+#   mutate(num_strains = 6)
+#
+
+# expt_res <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_SS_data_1e6_eventdef2.RDS"))
+# num_cores <- 8
+# expt_res <- expt_res %>%
+#   mutate(ssfind_result = list(get_total_bio(ssfind_result)))
+# cluster1 <- multidplyr::new_cluster(num_cores)
+# multidplyr::cluster_library(cluster1, c("microxanox", "dplyr"))
+# system.time({
+#   stab_data <-  expt_res %>%
+#     multidplyr::partition(cluster1) %>%
+#     mutate(stability_measures = list(get_stability_measures_new(ssfind_result))) %>%
+#     collect() %>%
+#     unnest(cols = c(stability_measures)) 
+# })
+# saveRDS(stab_data, here("experiments/0_ss_finding/temporal_method/data/9_strain_stab_data_1e6_eventdef2.RDS"))
+
+#stab_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_stab_data_1e6_eventdef2.RDS")) %>%
+#  mutate(num_strains = 9)
+
+stab_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_stab_data_1e4_eventdef2.RDS")) %>%
+  mutate(num_strains = 9)
+
+#ss_9s_sub1 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_SS_data_1e6_sub1.RDS"))
+#stab_9s_sub1 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_stab_data_1e6_sub1.RDS")) %>%
+#  mutate(num_strains = 9)
+
+#stab_9s_diff3 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_stab_data_1e6_diff3.RDS")) %>%
+#  mutate(num_strains = 9)
+
+# all_stab <- stab_2s %>%
+#   bind_rows(stab_2s_sub1) %>%
+#   bind_rows(stab_3s) %>%
+#   bind_rows(stab_3s_sub1) %>%
+#   bind_rows(stab_6s) %>%
+#   bind_rows(stab_6s_sub1) %>%
+#   bind_rows(stab_9s) %>%
+#   bind_rows(stab_9s_sub1) %>%
+#   bind_rows(stab_9s_diff3)
+
+all_stab <- stab_9s
+
+CB_vars <- unique(all_stab$CB_var_gmax_s)
+SB_vars <- unique(all_stab$SB_var_gmax_s)
+PB_vars <- unique(all_stab$PB_var_gmax_s)
+
+CB_all_stab <- all_stab %>%
+  filter(SB_var_gmax_s == 0,
+         PB_var_gmax_s == 0) %>%
+  ungroup() %>%
+  mutate(var_treat = "CB",
+         var_gmax = CB_var_gmax_s,
+         stand_var = var_gmax / max(var_gmax))
+SB_all_stab <- all_stab %>%
+  filter(CB_var_gmax_s == 0,
+         PB_var_gmax_s == 0)  %>%
+  ungroup() %>%
+  mutate(var_treat = "SB",
+         var_gmax = SB_var_gmax_s,
+         stand_var = var_gmax / max(var_gmax))
+PB_all_stab <- all_stab %>%
+  filter(CB_var_gmax_s == 0,
+         SB_var_gmax_s == 0) %>%
+  ungroup()  %>%
+  mutate(var_treat = "PB",
+         var_gmax = PB_var_gmax_s,
+         stand_var = var_gmax / max(var_gmax))
+
+for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
+                   SB_var_gmax_s = sort(SB_vars))
+CBSB_all_stab <- all_stab %>%
+  right_join(for_join)  %>%
+  ungroup() %>%
+  mutate(var_treat = "CB-SB",
+         var_gmax = CB_var_gmax_s,
+         stand_var = var_gmax / max(var_gmax)) %>%
+  filter(PB_var_gmax_s == 0)
+
+for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
+                   PB_var_gmax_s = sort(PB_vars))
+CBPB_all_stab <- all_stab %>%
+  right_join(for_join)  %>%
+  ungroup() %>%
+  mutate(var_treat = "CB-PB",
+         var_gmax = CB_var_gmax_s,
+         stand_var = var_gmax / max(var_gmax)) %>%
+  filter(SB_var_gmax_s == 0)
+
+for_join <- tibble(SB_var_gmax_s = sort(SB_vars),
+                   PB_var_gmax_s = sort(PB_vars))
+SBPB_all_stab <- all_stab %>%
+  right_join(for_join)  %>%
+  ungroup() %>%
+  mutate(var_treat = "SB-PB",
+         var_gmax = SB_var_gmax_s,
+         stand_var = var_gmax / max(var_gmax)) %>%
+  filter(CB_var_gmax_s == 0)
+
+for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
+                   SB_var_gmax_s = sort(SB_vars),
+                   PB_var_gmax_s = sort(PB_vars))
+CBSBPB_all_stab <- all_stab %>%
+  right_join(for_join)  %>%
+  ungroup() %>%
+  mutate(var_treat = "CB-SB-PB",
+         var_gmax = CB_var_gmax_s,
+         stand_var = var_gmax / max(var_gmax))
+
+all_stab_results <- CB_all_stab %>%
+  bind_rows(SB_all_stab) %>%
+  bind_rows(PB_all_stab) %>%
+  bind_rows(CBSB_all_stab) %>%
+  bind_rows(CBPB_all_stab) %>%
+  bind_rows(SBPB_all_stab) %>%
+  bind_rows(CBSBPB_all_stab)
+
+all_stab_results <- all_stab_results %>%
+  mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB",
+                                                                "SB",
+                                                                "PB",
+                                                                "CB-SB",
+                                                                "CB-PB",
+                                                                "SB-PB",
+                                                                "CB-SB-PB")))
+
+all_stab_results_small <- select(all_stab_results, -7:-12)
+
+#saveRDS(all_stab_results_small, here("experiments/0_ss_finding/temporal_method/data/all_stab_results_small.RDS"))
+
+all_stab_results %>%
+  #filter(var_treat == "CB") %>%
+  filter(num_strains == 9) %>%
+  filter(Species == "SB_tot") %>%
+  ggplot(aes(x = stand_var,
+             #col = as.factor(num_strains)
+             )) +
+  geom_line(aes(y = hyst_min_log), lwd = 0.5, alpha = 0.8) +
+  geom_line(aes(y = hyst_max_log), lwd = 0.5, alpha = 0.8) +
+  geom_ribbon(aes(ymin = hyst_min_log, ymax = hyst_max_log), col = "gray", alpha = 0.2) +
+  facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
+  xlab("Standardised amount of trait variation\n[see text for units]") +
+  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
+  labs(fill = "Variation in\nonly these\nfunctional groups") +
+  coord_flip() +
+  guides(col = guide_legend(title="Number of strains")) +
+  theme_bw() +
+  theme(
+    legend.position="top",
+    panel.background = element_blank(),
+    #strip.text.x = element_blank()
+  ) +
+  geom_hline(yintercept = c(-8, 0), col = "grey", lwd = 3) +
+  ggtitle("Bistability region for total SB density")
+
+#ggsave(here("experiments/1_figures_main_ms/figure_5_v2_9strain_only.pdf"),
+#       width = 10, height = 8)
+
+```
+
 # Finding the separatrix

### 2022-01-25 R/how_to_install_microxanox.R

@@ -1,0 +1,18 @@
+## how to install microxanox
+
+### From '?remotes::install_github`:
+# auth_token
+#   To install from a private repo, generate a personal access token (PAT) in
+#   "https://github.com/settings/tokens" and supply to this argument. This is
+#   safer than using a password because you can easily delete a PAT without
+#   affecting any others. Defaults to the GITHUB_PAT environment variable.
+
+# remotes::install_github(
+#   "opetchey/microxanox",
+#   ref = microxanox_release,
+#   # auth_token = "ENTER YOUR TOKEN or PROVED AS ENVIRONMENT VARIABLE",
+#   build_vignettes = FALSE,
+#   force = TRUE,
+#   upgrade = FALSE,
+#   lib = tmplib
+# )

### 2022-01-25 experiments/0_ss_finding/temporal_method/check_microxanox_version.R

@@ -1,0 +1,7 @@
+## package version check
+
+if (packageVersion("microxanox") < package_version(microxanox_release)) {
+  stop(paste0("microxanox version needs to be at least ", microxanox_release))
+}
+
+print(paste0("Version of microxanox: ", microxanox_release))

### 2022-01-25 experiments/0_ss_finding/temporal_method/get_div_effects.R

@@ -5,7 +5,9 @@
 rm(list = ls())
 
 ## Prelims ----
+microxanox_release <- "0.4.9"
 library(microxanox)
+source(here::here("experiments/0_ss_finding/temporal_method/check_microxanox_version.R"))
 library(tidyverse)
 library(patchwork)
 library(here)

### 2022-01-25 experiments/0_ss_finding/temporal_method/recalculate_stability_measures.R

@@ -1,0 +1,56 @@
+## Code for recalculating stability measures
+## See file R/how_to_install_microxanox for (surprise) how to install the microxanox package
+
+rm(list = ls())
+library(here)
+microxanox_release <- "0.4.9"
+library(microxanox)
+source(here::here("experiments/0_ss_finding/temporal_method/check_microxanox_version.R"))
+library(tidyverse)
+source(here("R/various_useful_functions.r"))
+max_cores <- benchmarkme::get_cpu()$no_of_cores
+
+
+## Run for 2, 3, 6, and 9 strains
+for(num_strains in c(2, 3, 6, 9)) {
+
+  #num_strains <- 9 ## for testing
+    
+  
+  ## Get stability measures ----
+  expt_res <- readRDS(here("experiments/0_ss_finding/temporal_method/data/",
+                           paste0(num_strains,
+                                  "_strain_SS_data_1e6.RDS")))
+  num_cores <- min(c(max_cores, nrow(expt_res)))
+    ## Get total biomass of CB, of SB, and of PB, to allow calculation of stability of these
+  expt_res <- expt_res %>%
+    mutate(ssfind_result = list(get_total_bio(ssfind_result)))
+  cluster1 <- multidplyr::new_cluster(num_cores)
+  multidplyr::cluster_library(cluster1, c("microxanox", "dplyr"))
+  system.time({
+    stab_data <-  expt_res %>%
+      multidplyr::partition(cluster1) %>%
+      mutate(stability_measures = list(get_stability_measures(ssfind_result))) %>%
+      collect() %>%
+      unnest(cols = c(stability_measures)) 
+  })
+  saveRDS(stab_data,
+          here("experiments/0_ss_finding/temporal_method/data/",
+               paste0(num_strains, "_strain_stab_data_1e6.RDS")))
+  ## End of getting stability measures
+
+  
+}
+## End of number of strains loop
+
+
+
+
+
+
+
+
+
+
+
+

### 2022-01-25 experiments/0_ss_finding/temporal_method/run_experiment.R

@@ -2,18 +2,28 @@
 ## Be careful to not overwrite data files
 
 rm(list = ls())
-library(here)
-source(here("R/various_useful_functions.r"))
-max_cores <- benchmarkme::get_cpu()$no_of_cores
+source(here::here("R/various_useful_functions.r"))
+max_cores <- benchmarkme::get_cpu()$no_of_cores-2
 
 
 ## Run for 2, 3, 6, and 9 strains
 for(num_strains in c(2, 3, 6, 9)) {
 
-  num_strains <- 2 ## for testing
+  #num_strains <- 2 ## for testing
     
   ## Run the code that sets up the experiment
-  source(here("experiments/0_ss_finding/temporal_method/setup_experiment.R"))
+  source(here::here("experiments/0_ss_finding/temporal_method/setup_experiment.R"))
+  
+  ss_data_filename <- here("experiments/0_ss_finding/temporal_method/data/",
+                           paste0("ss_data_",
+                                  num_strains, "strains_waittime",
+                                  formatC(wait_time, format = "e", digits = 0),
+                                  "_", event_def,".RDS"))
+  stab_data_filename <- here("experiments/0_ss_finding/temporal_method/data/",
+                           paste0("stab_data_",
+                                  num_strains, "strains_waittime",
+                                  formatC(wait_time, format = "e", digits = 0),
+                                  "_", event_def,".RDS"))
   
   ## Estimate time require ----
   nrow(var_expt)
@@ -35,18 +45,14 @@ for(num_strains in c(2, 3, 6, 9)) {
                                                total_initial_abundances = total_initial_abundances,
                                                cores = num_cores)
   })
-  saveRDS(expt_res,
-          here("experiments/0_ss_finding/temporal_method/data/",
-               paste0(num_strains, "_strain_SS_data_XXX.RDS")))
+  saveRDS(expt_res, ss_data_filename)
   ## End of run experiment
   
   
   
   ## Get stability measures ----
   num_cores <- min(c(max_cores, nrow(var_expt)))
-  expt_res <- readRDS(here("experiments/0_ss_finding/temporal_method/data/",
-                           paste0(num_strains,
-                                  "_strain_SS_data_1e3.RDS")))
+  expt_res <- readRDS(ss_data_filename)
   ## Get total biomass of CB, of SB, and of PB, to allow calculation of stability of these
   expt_res <- expt_res %>%
[…]

### 2022-01-25 experiments/1_figures_main_ms/figures_main_ms_v1.R

@@ -1,10 +1,11 @@
 ## Figures for main manuscript
 ## 
 ## 
+## 
+## 
+## this file -- version 2 -- makes graphs with all combinations
+## the other file -- version 1 -- makes only graphs for CB, SB-PB, and CB-SB-PB
 
-
-## this file -- version 1 -- makes only graphs for CB, SB-PB, and CB-SB-PB
-## the other file -- version 2 -- makes graphs with all combinations
 
 ## Prelims ----
 library(microxanox)
@@ -26,7 +27,7 @@ source(here("R/various_useful_functions.r"))
 
 ## Figure 2b-f ----
 
-ss_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_SS_data_1e6.RDS"))
+ss_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/ss_data_9strains_waittime1e+02_event_definition_2.RDS"))
 sort(unique(ss_9s$CB_var_gmax_s))
 sort(unique(ss_9s$SB_var_gmax_s))
 ss_result <- ss_9s %>%
@@ -130,13 +131,13 @@ p5 <- temp %>%
 
 patchwork <- p1 / p2 / p3 / p4 / p5
 patchwork
-ggsave(here("experiments/1_figures_main_ms/figure_2b-f_v1.pdf"))
+ggsave(here("experiments/1_figures_main_ms/figure_2b-f.pdf"))
 
 
 ## Figure 3 ----
 ## Stable state with diversity in all functional groups.
 
-ss_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_SS_data_1e6.RDS"))
+ss_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/ss_data_9strains_waittime1e+02_event_definition_2.RDS"))
 sort(unique(ss_9s$CB_var_gmax_s))
 sort(unique(ss_9s$SB_var_gmax_s))
 ss_result <- ss_9s %>%
@@ -234,13 +235,14 @@ p5 <- temp %>%
 
 patchwork <- p1 / p2 / p3 / p4 / p5
 patchwork
-ggsave(here("experiments/1_figures_main_ms/figure_3_v1.pdf"))
+ggsave(here("experiments/1_figures_main_ms/figure_3.pdf"))
 
 
 ## Figure 4 ----
 ## Shows effect of no diversity versus diversity in all functional groups.
 
[…]

### 2022-01-25 experiments/1_figures_main_ms/figures_main_ms_v2.R

@@ -1,1231 +1,0 @@
-## Figures for main manuscript
-## 
-## 
-## 
-## 
-## this file -- version 2 -- makes graphs with all combinations
-## the other file -- version 1 -- makes only graphs for CB, SB-PB, and CB-SB-PB
-
-
-## Prelims ----
-library(microxanox)
-library(tidyverse)
-library(patchwork)
-library(here)
-
-colfunc_CB <- colorRampPalette(c("#024F17", "#B5FFC9"))
-colfunc_SB <- colorRampPalette(c("#7D1402", "#FCBEB3"))
-colfunc_PB <- colorRampPalette(c("#6E0172", "#F9AEFC"))
-
-source(here("R/various_useful_functions.r"))
-
-## Figure 1 ----
-## Powerpoint
-
-## Figure 2a ----
-## Keynote
-
-## Figure 2b-f ----
-
-ss_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_SS_data_1e6.RDS"))
-sort(unique(ss_9s$CB_var_gmax_s))
-sort(unique(ss_9s$SB_var_gmax_s))
-ss_result <- ss_9s %>%
-  filter(abs(CB_var_gmax_s - 0) < 0.0001,
-         abs(SB_var_gmax_s - 0) < 0.0001,
-         abs(PB_var_gmax_s - 0) < 0.0001)
-
-
-
-#temp <- ss_result$ssfind_result[[1]] %>%
-  
-#ss_result <- ss_9s$ssfind_result[[25]]
-
-temp <- ss_result$ssfind_result[[1]] %>%
-  mutate(a = 10^a_O) %>%
-  # arrange(a) %>%
-  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
-  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
-  # select(-initial_N_CB, -a_O) %>%
-  gather(species, quantity, 2:(ncol(.) - 2)) %>%
-  mutate(
-    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
-    functional_group = case_when(
-      str_detect(species, "CB_5") ~ "CB",
-      str_detect(species, "SB_5") ~ "SB",
-      str_detect(species, "PB_5") ~ "PB"
-    ),
-    log10_quantity = log10(quantity + 1)
-  )
-
-num_strains <- temp %>%
-  group_by(functional_group) %>%
[…]

### 2022-01-31 experiments/2_supplement/html_supplement.Rmd
many developments

--- 2022-01-20 experiments/2_supplement/html_supplement.Rmd
@@
 source(here("r/various_useful_functions.r"))
+source(here("experiments/1_figures_main_ms/ms_figure_functions.r"))
+
+#print(fig_div_vs_o2diff_1strain_7row)
+
 colfunc_CB <- colorRampPalette(c("#024F17", "#B5FFC9"))
@@
 
-```{r repl_meth1, echo=FALSE}
+```{r repl_meth1, echo=FALSE, eval = TRUE}
 repl_meth <- readRDS(here("experiments/0_ss_finding/replication_method/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
-temp_meth <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_SS_data.RDS"))
+temp_meth <- readRDS(here("experiments/0_ss_finding/temporal_method/data/ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
 ## To be completed.
@@
 
-```{r temp_meth1, echo=FALSE}
+```{r temp_meth1, echo=FALSE, eval = TRUE}
 plot_ss_result3(temp_meth, 1)
@@
 
-```{r both_meth1, echo=FALSE}
+```{r both_meth1, echo=FALSE, eval = TRUE}
 repl_method_1 <- repl_meth$ss_res[[1]] %>%
@@
 
+### Further information
+
+Here we give some further thoughts regarding the comparison of the temporal and replication method for stable state finding.
+
+A particularly notable difference between the two approaches is in the initial condition.
+In the temporal approach, the initial condition at a new level of oxygen diffusivity is the stable state at the previous level of oxygen diffusivity, while in the approach of Bush et al (2017) the initial conditions are fixed and arbitrary (though this approach is still useful for illustrating the bistability of the system).
+This difference in initial conditions increases the region of bistability in the temporal approach because as a tipping point approaches, the functional group that will dominate after the regime shift starts from much lower abundances than in the approach by Bush et al (2017) and thus requires stronger amelioration of the environment to take over.
+Nevertheless, our main conclusions about the effects of functional trait diversity are the same using either approach.
+
+The temporal approach is particularly useful when investigating the effects of strain richness.
+In preliminary simulations using the Bush et al (2017) approach, we found the counterintuitive result that higher strain richness led to lower resilience.
+We then recalled that we chose to divide the initial total abundance of the cyanobacterial (CB) functional group equally among the strains (termed a substitutive design in biodiversity manipulation experiments).
+This meant that the most tolerant CB strain in a three-strain simulation had higher initial abundance than the same most tolerant CB strain in a nine-strain simulation.
+The greater abundance of the most CB tolerant strain made it possible for a three-strain system to develop to be oxic, whereas the nine-strain system developed to be anoxic, despite identical range of trait variation.
+We could have chosen to do otherwise, for example start with the least tolerant strains of cyanobacteria as more abundant when the system started with high cyanobacterial abundance, and the most tolerant strain as more abundant when the system starts with low cyanobacterial abundance.
+Using the temporal approach removed the need to specify initial abundances (except the very first one), and therefore results were not so determined by the assumptions used to determine the initial conditions.
+
 ## Effect of simulation duration
+
+### Effect of shorter wait times
+
+Wait times of 1e6 hours produce the following results (same as those presented in the main report).
+
+```{r wait_time_1e6, eval = TRUE}
+wait_time <- "1e+06"
+
+#stab_2s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_2strains_waittime", wait_time, "_event_definition_2.RDS")))
+#stab_3s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))
+#stab_6s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_6strains_waittime", wait_time, "_event_definition_2.RDS")))
+stab_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+
+#all_stab <- stab_2s %>%
+  #bind_rows(stab_2s_sub1) %>%
+#  bind_rows(stab_3s) %>%
+  #bind_rows(stab_3s_sub1) %>%
+#  bind_rows(stab_6s) %>%
+  #bind_rows(stab_6s_sub1) %>%
+#  bind_rows(stab_9s)
+  #bind_rows(stab_9s_sub1) %>%
+  #bind_rows(stab_9s_diff3)
+
+all_stab <- stab_9s
+```
+
+```{r wait_time_1e6_2, eval = FALSE}
+p1 <- fig_div_vs_o2diff_1strain_7row(all_stab,
+                                     which_strain = 9,
+                                     figure_title = "1e6 wait time, 9 strains")
+#p1
+p2 <- fig_resilience_vs_div(all_stab, which_strain = 9, figure_title = " ") 
+#p2
+p1 + p2
+
+```
+
+Wait times of 1e5 produce the following results, which qualitatively and often quantitatively very similar to those for wait times of 1e6.
+There is a notable difference when there is variation in only SB, or CB-SB variation treatments with two or three strains:
+
+```{r wait_time_1e5, eval = FALSE}
+
+wait_time <- "1e+05"
+
+stab_2s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_2strains_waittime", wait_time, "_event_definition_2.RDS")))
+stab_3s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))
+stab_6s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_6strains_waittime", wait_time, "_event_definition_2.RDS")))
+stab_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+
+all_stab <- stab_2s %>%
+  #bind_rows(stab_2s_sub1) %>%
+  bind_rows(stab_3s) %>%
+  #bind_rows(stab_3s_sub1) %>%
+  bind_rows(stab_6s) %>%
+  #bind_rows(stab_6s_sub1) %>%
+  bind_rows(stab_9s)
+  #bind_rows(stab_9s_sub1) %>%
+  #bind_rows(stab_9s_diff3)
+
+#all_stab <- stab_9s
+
+fig_div_vs_o2diff_multistrain(all_stab = all_stab,
+                  which_strains = c(2, 3, 6, 9),
+                  figure_title = paste0("Wait time = ", wait_time))
+
+```
+
+Here, moderate increases in diversity have the same effect as with wait times of 1e6.
+However, larger increases in diversity suddenly cause a large reduction in resilience of the anoxic-oxic transition.
+Here is an example of the stable states when diversity is moderate:
+
+```{r}
+wait_time <- "1e+04"
+ss_3s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/ss_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))
+
+#max <- max(ss_3s$PB_var_gmax_s)
+#f <- 0.625
+#fv <- f*max
+
+only_SB_variable <- ss_3s %>%
+  filter(
+    abs(CB_var_gmax_s) < 0.0001,
+    abs(PB_var_gmax_s) < 0.0001
+  )
+only_SB_variable <- only_SB_variable[order(only_SB_variable$SB_var_gmax_s), ]
+
+only_SB_variable$SB_var_gmax_s
+```
+
+```{r}
+fig_state_vs_o2diff(only_SB_variable[13,])
+```
+
+Increases in oxygen diffusivity cause strain replacement in the SB to the more tolerant strains, which then delay the shift. When there is just a little more diversity in the SB, this happens:
+
+```{r}
+fig_state_vs_o2diff(only_SB_variable[14,])
+```
+
+We believe that this phenomenon is caused by an effect that we explain with reference to an anology of using stepping stones to cross a river.
+Increasing diversity in our simulations is akin to increasing the width of the river, but while keeping the number of stepping stones (strains) constant.
+So long as the river is not too wide, we can still cross it, but once the width of the river is such that the stepping stones are too far apart, we can't cross the river.
+And this happens suddenly, the width increases just a tiny bit more, and we suddenly can't cross the river when we could before.
+
+In the simulated microbial ecosystem, the strains are the stepping stones, and it is much hard (takes longer) for strains to replace each other when there is greater distance (in trait space) between them.
+When they can no longer replace each other in the time available, the system behaves as if only the least tolerant, highest growth rate strain (lighted shade of colour) is present.
+In the case illustrated above, this leads to much lower resilience of the anoxic system state.
+
+This phenomena is dependent on having static trait values for the strains.
+If strain traits were dynamic (e.g.
+due to evolution), then we expect this result to not occur, and rather for the effects of diversity with two or three strains to be the same as those with six or nine.
+
+### Even shorter wait times
+
+```{r wait_time_1e4, eval = FALSE}
+
+wait_time <- "1e+04"
+
+stab_2s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_2strains_waittime", wait_time, "_event_definition_2.RDS")))
+stab_3s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))
+stab_6s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_6strains_waittime", wait_time, "_event_definition_2.RDS")))
+stab_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+
+all_stab <- stab_2s %>%
+  #bind_rows(stab_2s_sub1) %>%
+  bind_rows(stab_3s) %>%
+  #bind_rows(stab_3s_sub1) %>%
+  bind_rows(stab_6s) %>%
+  #bind_rows(stab_6s_sub1) %>%
+  bind_rows(stab_9s)
+  #bind_rows(stab_9s_sub1) %>%
+  #bind_rows(stab_9s_diff3)
+
+#all_stab <- stab_9s
+
+fig_div_vs_o2diff_multistrain(all_stab = all_stab,
+                  which_strains = c(2, 3, 6, 9),
+                  figure_title = paste0("Wait time = ", wait_time))
+
+```
+
+```{r wait_time_1e3, eval = FALSE}
+
+wait_time <- "1e+03"
+
+stab_2s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_2strains_waittime", wait_time, "_event_definition_2.RDS")))
+stab_3s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))
+stab_6s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_6strains_waittime", wait_time, "_event_definition_2.RDS")))
+stab_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+
+all_stab <- stab_2s %>%
+  #bind_rows(stab_2s_sub1) %>%
+  bind_rows(stab_3s) %>%
+  #bind_rows(stab_3s_sub1) %>%
+  bind_rows(stab_6s) %>%
+  #bind_rows(stab_6s_sub1) %>%
+  bind_rows(stab_9s)
+  #bind_rows(stab_9s_sub1) %>%
+  #bind_rows(stab_9s_diff3)
+
+#all_stab <- stab_9s
+
+fig_div_vs_o2diff_multistrain(all_stab = all_stab,
+                  which_strains = c(2, 3, 6, 9),
+                  figure_title = paste0("Wait time = ", wait_time))
+
+```
+
+```{r wait_time_1e2, eval = FALSE}
+
+wait_time <- "1e+02"
+
+stab_2s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_2strains_waittime", wait_time, "_event_definition_2.RDS")))
+stab_3s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))
+stab_6s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_6strains_waittime", wait_time, "_event_definition_2.RDS")))
+stab_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+
+all_stab <- stab_2s %>%
+  #bind_rows(stab_2s_sub1) %>%
+  bind_rows(stab_3s) %>%
+  #bind_rows(stab_3s_sub1) %>%
+  bind_rows(stab_6s) %>%
+  #bind_rows(stab_6s_sub1) %>%
+  bind_rows(stab_9s)
+  #bind_rows(stab_9s_sub1) %>%
+  #bind_rows(stab_9s_diff3)
+
+#all_stab <- stab_9s
+
+fig_div_vs_o2diff_multistrain(all_stab = all_stab,
+                  which_strains = c(2, 3, 6, 9),
+                  figure_title = paste0("Wait time = ", wait_time))
+
+```
+
+### Example transient at 1'000'000 hours
 

### 2022-01-31 experiments/1_figures_main_ms/figures_main_ms_v1.R

@@ -18,6 +18,7 @@ colfunc_SB <- colorRampPalette(c("#7D1402", "#FCBEB3"))
 colfunc_PB <- colorRampPalette(c("#6E0172", "#F9AEFC"))
 
 source(here("R/various_useful_functions.r"))
+source(here("experiments/1_figures_main_ms/ms_figure_functions.R"))
 
 ## Figure 1 ----
 ## Powerpoint
@@ -27,7 +28,7 @@ source(here("R/various_useful_functions.r"))
 
 ## Figure 2b-f ----
 
-ss_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/ss_data_9strains_waittime1e+02_event_definition_2.RDS"))
+ss_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
 sort(unique(ss_9s$CB_var_gmax_s))
 sort(unique(ss_9s$SB_var_gmax_s))
 ss_result <- ss_9s %>%
@@ -35,109 +36,14 @@ ss_result <- ss_9s %>%
          abs(SB_var_gmax_s - 0) < 0.0001,
          abs(PB_var_gmax_s - 0) < 0.0001)
 
-
-
-#temp <- ss_result$ssfind_result[[1]] %>%
-  
-#ss_result <- ss_9s$ssfind_result[[25]]
-
-temp <- ss_result$ssfind_result[[1]] %>%
-  mutate(a = 10^a_O) %>%
-  # arrange(a) %>%
-  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
-  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
-  # select(-initial_N_CB, -a_O) %>%
-  gather(species, quantity, 2:(ncol(.) - 2)) %>%
-  mutate(
-    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
-    functional_group = case_when(
-      str_detect(species, "CB_5") ~ "CB",
-      str_detect(species, "SB_5") ~ "SB",
-      str_detect(species, "PB_5") ~ "PB"
-    ),
-    log10_quantity = log10(quantity + 1)
-  )
-
-num_strains <- temp %>%
-  group_by(functional_group) %>%
-  summarise(num = length(unique(species))) %>%
-  na.omit()
-
[…]

### 2022-01-31 experiments/1_figures_main_ms/ms_figure_functions.R

@@ -1,0 +1,692 @@
+## figure functions
+## (since same figures appear in main text and supplement, just with different data)
+##
+
+
+
+fig_div_vs_o2diff_1strain <- function(all_stab, which_strain, figure_title) {
+  
+  CB_vars <- unique(all_stab$CB_var_gmax_s)
+  SB_vars <- unique(all_stab$SB_var_gmax_s)
+  PB_vars <- unique(all_stab$PB_var_gmax_s)
+  
+  CB_all_stab <- all_stab %>%
+    filter(SB_var_gmax_s == 0,
+           PB_var_gmax_s == 0) %>%
+    ungroup() %>%
+    mutate(var_treat = "CB",
+           var_gmax = CB_var_gmax_s,
+           stand_var = var_gmax / max(var_gmax))
+  SB_all_stab <- all_stab %>%
+    filter(CB_var_gmax_s == 0,
+           PB_var_gmax_s == 0)  %>%
+    ungroup() %>%
+    mutate(var_treat = "SB",
+           var_gmax = SB_var_gmax_s,
+           stand_var = var_gmax / max(var_gmax))
+  PB_all_stab <- all_stab %>%
+    filter(CB_var_gmax_s == 0,
+           SB_var_gmax_s == 0) %>%
+    ungroup()  %>%
+    mutate(var_treat = "PB",
+           var_gmax = PB_var_gmax_s,
+           stand_var = var_gmax / max(var_gmax))
+  
+  for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
+                     SB_var_gmax_s = sort(SB_vars))
+  CBSB_all_stab <- all_stab %>%
+    right_join(for_join)  %>%
+    ungroup() %>%
+    mutate(var_treat = "CB-SB",
+           var_gmax = CB_var_gmax_s,
+           stand_var = var_gmax / max(var_gmax)) %>%
+    filter(PB_var_gmax_s == 0)
+  
+  for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
+                     PB_var_gmax_s = sort(PB_vars))
+  CBPB_all_stab <- all_stab %>%
+    right_join(for_join)  %>%
+    ungroup() %>%
+    mutate(var_treat = "CB-PB",
+           var_gmax = CB_var_gmax_s,
+           stand_var = var_gmax / max(var_gmax)) %>%
+    filter(SB_var_gmax_s == 0)
+  
[…]

### 2022-02-02 experiments/2_supplement/supplement.Rmd
working on the supplement

@@
 subtitle: Functional diversity ... Predictions of a model of an oxic-anoxic microbial ecosystem 
-authors:
-  - name: Owen L Petchey
-    department: Department of Evolutionary Biology and Environmental Studies
-    affiliation: University of Zurich
-    location: Zurich 8057, Switzerland
-    email: owen.petchey@ieu.uzh.ch
-  - name: Rainer Krug
-    department: Department of Evolutionary Biology and Environmental Studies
-    affiliation: University of Zurich
-    location: Zurich 8057, Switzerland
-    email: rainer.krug@ieu.uzh.ch
-  - name: Any Others
-    department: Department of Evolutionary Biology and Environmental Studies
-    affiliation: University of Zurich
-    location: Zurich 8057, Switzerland
-    email: any.others@ieu.uzh.ch
-  - name: Marcel Suleiman
-    department: Department of Evolutionary Biology and Environmental Studies
-    affiliation: University of Zurich
-    location: Zurich 8057, Switzerland
-    email: marcel.suleiman@ieu.uzh.ch
-
-bibliography: references.bib
-biblio-style: unsrt
+author: "Owen L Petchey, Rainer Krug, Marcel Suleiman, ???others???"
+date: "`r format(Sys.time(), '%d %B, %Y')`"
 output:
-  rticles::arxiv_article:
-    keep_tex: true
+  bookdown::html_document2:
+    toc: true
+    toc_float:
+      collapsed: true
+      smooth_scroll: true
 ---
@@
 ```{r include = FALSE, echo = FALSE}
-knitr::opts_chunk$set(include = FALSE,
+knitr::opts_chunk$set(include = TRUE,
                       warning = FALSE,
@@
 
-...
+This document contains the Supporting Content for the report *?????????????*.
 
-# Visualising among strain diversity
+# Creating among strain diversity
 
-The method for creating among strain diversity is explained in the main report. Here we show three visualisations, one for nine strains, one for three, and one for two.
+Here we provide additional description of the method used to create strain variation within functional groups. The following should be read only after the relevant sections of the main text.
+
+Take for example the cyanobacteria functional group, a reference maximum growth rate parameter $G_{max,CB}$ and a reference tolerance parameter $h_{SR,CB}$.
+Recall that amount of among strain variation is controlled by the two meta-parameters $Div_{G_{max,CB}}$ and $Div_{h_{SR,CB}}$.
+To create a tradeoff, the two meta-parameters were always of different sign.
+The among strain variation was calculated such that the growth rate of strain $i = 1$ was a factor $1/({2Div_{G_{max,CB}}})$ of the reference growth rate, and the growth rate of the $i = n$ strain was a factor $2Div_{G_{max,CB}}$ of the reference growth rate.
+The growth rate of the $i = {2,...n-1}$ other strains was the reference growth rate multiplied by a factor that was equally distributed between the factor of the $i = 1$ and $i = n$ strain.
+This implementation of the variation and trade-off has the assumption of a linear trade-off of log-log transformed among-strain variation.
+Hence, for example, with the reference growth rate $G_{max,CB} = 0.05$, among strain variation of $Div_{G_{max,CB}} = 1$, and nine strains ($n = 9$), the growth rates of the nine strains are 0.025, 0.03, 0.035, 0.042, 0.05, 0.059, 0.071, 0.084, 0.1.
+Put another way, the growth rate parameter of the $i$-th of the $n$ strains in a functional group was calculated as $G_{max,i} = D_i * G_{max}$ where $D_i$ is the $i$-th element of the set $D = {2f(x)Div_{G_{max}} |x ∈ N, x ≤ n}$, where $f(x) = (x − (n + 1)/2)/((n − 1)/2)$.
+
+This procedure ensures that the range of trait values is independent of the number of strains.
+When there were only two strains, the two strains took the minimum and maximum traits values, as defined by the $Div$ variable for that trait.
+When there were three strains, one had the minimum trait value, one the maximum, and one the mean.
+With nine strains, one had the minimum trait value, one the maximum, one the mean, and three were equally spaced (on log scale) between the minimum and the mean, and the remaining three between the maximum and the mean.
+
+We show three examples of the created variation among strains within functional groups, one for nine strains (Figure \@ref(fig:nine-strain-div)), one for three (Figure \@ref(fig:three-strain-div)), and one for two (Figure \@ref(fig:two-strain-div)).
+In each, three graphs shows the diversity among strains in the maximum growth rate trait and the tolerance trait, plotted against each other and therefore also showing the tradeoff between the two traits.
+
+Notice that in all three cases, the range of trait variation represented by the strains is the same, even though the number of strains differs (a consequence is that the lower row of panels in Figures \@ref(fig:nine-strain-div), \@ref(fig:three-strain-div), and \@ref(fig:two-strain-div) are identical).
+This approach allowed us to independently manipulate trait diversity and number of strains.
 
@@
 
-## Nine strains
+All three examples have the following amounts of trait variation: $Div_{G_{max,CB}}$ = `r round(CB_gmax_div, 3)`, $Div_{h_{SR,CB}}$ = `r round(CB_h_div, 3)`, $Div_{G_{max,SB}}$ = `r round(SB_gmax_div, 3)`, $Div_{h_{O,SB}}$ = `r round(SB_h_div, 3)`, $Div_{G_{max,PB}}$ = `r round(PB_gmax_div, 3)`, $Div_{h_{O,PB}}$ = `r round(PB_h_div, 3)`.
+These are also the maximum amounts of trait variation explored in the simulations.
 
-```{r nine-strains, echo = FALSE}
+(ref:nine-strain-div) Trait variation with nine strains in each of the functional groups.
+In all panels colour indicates the functional group, darker shades show more tolerant-lower growth rate strains, lighter shades show less tolerant-higher growth rate strains.
+
+```{r nine-strain-div, echo = FALSE,  include=TRUE, fig.cap='(ref:nine-strain-div)', fig.align="center", fig.height=3, fig.width=8}
 
@@
   num_SB_strains = num_SB_strains,
-  num_PB_strains = num_PB_strains
+  num_PB_strains = num_PB_strains,
+  which_graphs = 1
 )
@@
 
-## Three strains
+(ref:three-strain-div) Trait variation with three strains in each of the functional groups.
+Note that the three displayed strains are the 1st, 5th, and 9th strains from the nine strain example shown in Figure \@ref(fig:nine-strain-div).
+In all panels colour indicates the functional group, darker shades show more tolerant-lower growth rate strains, lighter shades show less tolerant-higher growth rate strains.
 
-```{r three-strains, echo = FALSE}
+```{r three-strain-div, echo = FALSE,  include=TRUE, fig.cap='(ref:three-strain-div)', fig.height=3, fig.width=8, fig.align="center"}
 
@@
 
-## Two strains
+(ref:two-strain-div) Trait variation with two strains in each of the functional groups.
+Note that the two displayed strains are the 1st and 9th strains from the nine strain example shown in Figure \@ref(fig:nine-strain-div).
+In all panels colour indicates the functional group, darker shades show more tolerant-lower growth rate strains, lighter shades show less tolerant-higher growth rate strains.
 
-```{r two-strains, echo = FALSE}
+```{r two-strain-div, echo = FALSE,  include=TRUE, fig.cap='(ref:two-strain-div)', fig.height=3, fig.width=8, fig.align="center"}
 
@@
 
-# Effect of number of strains
+We also show, in Figure \@ref(fig:growth-rates), the relationship between realised growth rate and the concentration of the respective inhibiting substance, e.g.
+sulfide for the cyanobacteria.
+In these graphs only the least and most tolerant strains are shown.
+The lines cross due to the tradeoff.
+At high concentrations of the inhibiting substance the more tolerant strain has higher realised growth rate, while at lower concentrations it is the less tolerant strain that has the higher realised growth rate.
 
-May not need this section, as number of strains effect is shown in figure of main ms.
+(ref:growth-rates) Response of realised growth rate to variation in concentration of the inhibiting substrate for two strains, namely the most and the least tolerant strain.
+As always colour indicates the functional group, darker shades show more tolerant-lower growth rate strains, lighter shades show less tolerant-higher growth rate strains.
 
-```{r eval = FALSE, echo = FALSE}
+```{r growth-rates, echo = FALSE,  include=TRUE, fig.cap='(ref:growth-rates)', fig.height=3, fig.width=8, fig.align="center"}
+display_diversity(4,
+  var_expt = var_expt,
+  num_CB_strains = num_CB_strains,
+  num_SB_strains = num_SB_strains,
+  num_PB_strains = num_PB_strains,
+  which_graphs = 2
+)
+```
 
-## Figure 2b-f ----
+# Method for finding stable states
 
-ss_9s <- readRDS(here("experiments/0_ss_finding/data/9_strain_SS_data_1e3.RDS"))
-sort(unique(ss_9s$CB_var_gmax_s))
-sort(unique(ss_9s$SB_var_gmax_s))
-ss_result <- ss_9s %>%
-  filter(abs(CB_var_gmax_s - 0) < 0.0001,
-         abs(SB_var_gmax_s - 0) < 0.0001,)
+We now discuss two approaches for finding how the stable state of the system varies along the gradient of oxygen diffusivity when there exists the possibility of multiple stable states.
+In the main article we describe and report results of the method that we term the *Temporal method*.
 
-#temp <- ss_result$ssfind_result[[1]] %>%
+Here we also describe and give results of what we term the *Replication method*.
+In this, we made a separate simulations for each of many values of oxygen diffusivity, ran the simulations for long enough to ensure transients had passed, and recorded the state.
+We ran multiple simulations per value of oxygen diffusivity, and started them with different initial conditions (either low or high total cyanobacterial abundance), so as to check for presence of alternate stable states.
+This method used by [Bush et al 2017](https://www.nature.com/articles/s41467-017-00912-x).
+We term it the replication method since it is achieved by having many independent replicates of the ecosystem, each with a different oxygen diffusivity, and also a separate replicate for each of the different chosen initial conditions.
 
-#ss_result <- ss_9s$ssfind_result[[25]]
+As is shown in the figures below, the temporal method results in a larger region of bistability than the replication method, but only during increasing oxygen diffusivities.
+The difference in results occurs because, as mentioned above, the initial conditions differ between the two approaches.
+For example, in the temporal method, the oxygen concentration in the anoxic state is lower than the initial oxygen concentration in the replication approach, and **Owen guesses that** the sulfide concentration is higher **check that last statement**.
 
-temp <- ss_result$ssfind_result[[1]] %>%
+## Replication method, no diversity
+
+In the following graph, the solid (down) line refers to the stable state when cyanobacteria begin at high abundance (favouring the oxic state).
+The dashed up line refers to when their initial abundnace is low (favouring the anoxic state).Stable states found with the replication method.
+Please note: i) that near vertical lines indicate the position of a tipping point and hence the system cannot exist on point of that part of the line; ii) the separatrix (the unstable equilibrium) is not shown.
+
+```{r repl_meth1, echo=FALSE, eval = FALSE}
+repl_meth <- readRDS(here("experiments/0_ss_finding/replication_method/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
+temp_meth <- readRDS(here("experiments/0_ss_finding/temporal_method/data/ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
+## To be completed.
+plot_ss_result1(repl_meth,
+                result_index = 1,
+                filename_prefix = NULL,
+                save_image_file = FALSE)
+```
+
+## Temporal method, no diversity
+
+Same as for the previous graph.
+
+```{r temp_meth1, echo=FALSE, eval = FALSE}
+plot_ss_result3(temp_meth, 1)
+```
+
+## Both methods overlaid, no diversity
+
+Stable states of the two methods overlaid, the temporal method with a dashed line, and the replication method with a solid line.
+
+```{r both_meth1, echo=FALSE, eval = FALSE}
+repl_method_1 <- repl_meth$ss_res[[1]] %>%
+     mutate(time = NA,
+            direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
+  select(names(temp_meth$ssfind_result[[1]]))
+
+ss_result1 <- repl_method_1
+ss_result2 <- temp_meth$ssfind_result[[1]]
+
+plot_ss_result6(repl_method_1,
+                temp_meth$ssfind_result[[1]],
+                xlims = c(-8, 0))
+```
+
+## Effect of diversity, replication method
+
+The replication method shows the same effects of functional diversity as those revealed by the temporal method:
+
+-   Introducing functional diversity in all three functional groups increases the region of bistability relative to when there is no diversity within all functional groups).
+-   Introducing functional diversity in only the cyanobacteria function group delays (with respect to the oxygen diffusivity it occurs at) the switch to the anoxic state as oxygen diffusivity is reduced, but has no effect on the oxygen diffusivity at which the anoxic to oxic transition occurs .
+-   Introducing function diversity in only the sulfur bacteria delays (with respect to the oxygen diffusivity it occurs at) the switch from anoxic to oxic, and advances the switch from oxic to anoxic.
+
+These results are shown in the figure below, which shows results of the replication method.
+
+```{r echo = FALSE, eval = FALSE}
+stab_data <- readRDS(here("experiments/0_ss_finding/replication_method/9_strains/data/small_stab_data_1e6_x2x6_factorial.RDS"))
+
+all_stab <- stab_data
+
+#all_stab <- stab_9s
+
+CB_vars <- unique(all_stab$CB_var_gmax_s)
+SB_vars <- unique(all_stab$SB_var_gmax_s)
+
+CB_all_stab <- all_stab %>%
+  filter(SB_var_gmax_s == 0) %>%
+  mutate(var_treat = "CB",
+         var_gmax = CB_var_gmax_s)
+
+SBPB_all_stab <- all_stab %>%
+  filter(CB_var_gmax_s == 0) %>%
+  mutate(var_treat = "SB-PB",
+         var_gmax = SB_var_gmax_s)
+
+for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
+                   SB_var_gmax_s = sort(SB_vars))
+CBSBPB_all_stab <- all_stab %>%
+  right_join(for_join) %>%
+  mutate(var_treat = "CB-SB-PB",
+         var_gmax = CB_var_gmax_s)
+
+all_stab_results <- CB_all_stab %>%
+  bind_rows(SBPB_all_stab) %>%
+  #  bind_rows(results3) %>%
+  # bind_rows(results4) %>%
+  bind_rows(CBSBPB_all_stab)
+
+all_stab_results <- all_stab_results %>%
+  mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB-PB", "CB-SB-PB")))
+
+```
+
+```{r echo = FALSE, eval = FALSE}
+all_stab_results %>%
+  #filter(var_treat == "CB") %>%
+  filter(Species == "SR") %>%
+  ggplot(aes(x = var_gmax)) +
+  #ggplot(aes(x = var_gmax,
+  #           col = as.factor(num_strains))) +
+  geom_line(aes(y = hyst_min_log), lwd = 2, alpha = 0.8) +
+  geom_line(aes(y = hyst_max_log), lwd = 2, alpha = 0.8) +
+  facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
+  xlab("Amount of trait variation\n[see text for units]") +
+  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
+  labs(fill = "Variation in\nonly these\nfunctional groups") +
+  coord_flip() +
+  #guides(col = guide_legend(title="Number of strains")) +
+  theme(
+    legend.position="top"
+    #strip.background = element_blank(),
+    #strip.text.x = element_blank()
+  ) +
+  geom_hline(yintercept = c(-8, 0), col = "grey", lwd = 3)
+
+#ggsave(here("experiments/1_figures_main_ms/figure_5.pdf"),
+#       width = 5, height = 4)
+
+```
+
+The figure above shows the effect of response trait diversity (y-axis) on the positions of the tipping points (show by dark lines), which determine the extent of the region of bistability in the oxygen diffusivity gradient.
+The left-most region is anoxic only, the middle is oxic or anoxic depending on historical conditions, and the right-most is oxic only.
+The thick grey vertical lines at -8 and 0 on the x-axis show the extent of the oxygen diffusivity gradient investigated in the simulations.
+
+## Further thoughts
+
+Here we give some further thoughts regarding the comparison of the temporal and replication method for stable state finding.
+
+A particularly notable difference between the two approaches is in the initial condition.
+In the temporal approach, the initial condition at a new level of oxygen diffusivity is the stable state at the previous level of oxygen diffusivity, while in the approach of Bush et al (2017) the initial conditions are fixed and arbitrary (though this approach is still useful for illustrating the bistability of the system).
+This difference in initial conditions increases the region of bistability in the temporal approach because as a tipping point approaches, the functional group that will dominate after the regime shift starts from much lower abundances than in the approach by Bush et al (2017) and thus requires stronger amelioration of the environment to take over.
+Nevertheless, our main conclusions about the effects of functional trait diversity are the same using either approach.
+
+The temporal approach is particularly useful when investigating the effects of strain richness.
+In preliminary simulations using the Bush et al (2017) approach, we found the counterintuitive result that higher strain richness led to lower resilience.
+We then recalled that we chose to divide the initial total abundance of the cyanobacterial (CB) functional group equally among the strains (termed a substitutive design in biodiversity manipulation experiments).
+This meant that the most tolerant CB strain in a three-strain simulation had higher initial abundance than the same most tolerant CB strain in a nine-strain simulation.
+The greater abundance of the most CB tolerant strain made it possible for a three-strain system to develop to be oxic, whereas the nine-strain system developed to be anoxic, despite identical range of trait variation.
+We could have chosen to do otherwise, for example start with the least tolerant strains of cyanobacteria as more abundant when the system started with high cyanobacterial abundance, and the most tolerant strain as more abundant when the system starts with low cyanobacterial abundance.
+Using the temporal approach removed the need to specify initial abundances (except the very first one), and therefore results were not so determined by the assumptions used to determine the initial conditions.
+
+# Effect of simulation duration
+
+*Review what the wait time is.*
+
+Wait times of 1e6 hours produce the following results (same as those presented in the main report).
+
+```{r wait_time_1e6, eval = FALSE}
+wait_time <- "1e+06"
+
+#stab_2s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_2strains_waittime", wait_time, "_event_definition_2.RDS")))
+#stab_3s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))
+#stab_6s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_6strains_waittime", wait_time, "_event_definition_2.RDS")))
+stab_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+
+#all_stab <- stab_2s %>%
+  #bind_rows(stab_2s_sub1) %>%
+#  bind_rows(stab_3s) %>%
+  #bind_rows(stab_3s_sub1) %>%
+#  bind_rows(stab_6s) %>%
+  #bind_rows(stab_6s_sub1) %>%
+#  bind_rows(stab_9s)
+  #bind_rows(stab_9s_sub1) %>%
+  #bind_rows(stab_9s_diff3)
+
+all_stab <- stab_9s
+```
+
+```{r wait_time_1e6_2, eval = FALSE}
+p1 <- fig_div_vs_o2diff_1strain_7row(all_stab,
+                                     which_strain = 9,
+                                     figure_title = "1e6 wait time, 9 strains")
+#p1
+p2 <- fig_resilience_vs_div(all_stab, which_strain = 9, figure_title = " ") 
+#p2
+p1 + p2
+
+```
+
+Wait times of 1e5 produce the following results, which qualitatively and often quantitatively very similar to those for wait times of 1e6.
+There is a notable difference when there is variation in only SB, or CB-SB variation treatments with two or three strains:
+
+```{r wait_time_1e5, eval = FALSE}
+
+wait_time <- "1e+05"
+
+stab_2s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_2strains_waittime", wait_time, "_event_definition_2.RDS")))
+stab_3s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))
+stab_6s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_6strains_waittime", wait_time, "_event_definition_2.RDS")))
+stab_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+
+all_stab <- stab_2s %>%
+  #bind_rows(stab_2s_sub1) %>%
+  bind_rows(stab_3s) %>%
+  #bind_rows(stab_3s_sub1) %>%
+  bind_rows(stab_6s) %>%
+  #bind_rows(stab_6s_sub1) %>%
+  bind_rows(stab_9s)
+  #bind_rows(stab_9s_sub1) %>%
+  #bind_rows(stab_9s_diff3)
+
+#all_stab <- stab_9s
+
+fig_div_vs_o2diff_multistrain(all_stab = all_stab,
+                  which_strains = c(2, 3, 6, 9),
+                  figure_title = paste0("Wait time = ", wait_time))
+
+```
+
+Here, moderate increases in diversity have the same effect as with wait times of 1e6.
+However, larger increases in diversity suddenly cause a large reduction in resilience of the anoxic-oxic transition.
+Here is an example of the stable states when diversity is moderate:
+
+```{r eval = FALSE}
+wait_time <- "1e+04"
+ss_3s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/ss_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))
+
+#max <- max(ss_3s$PB_var_gmax_s)
+#f <- 0.625
+#fv <- f*max
+
+only_SB_variable <- ss_3s %>%
+  filter(
+    abs(CB_var_gmax_s) < 0.0001,
+    abs(PB_var_gmax_s) < 0.0001
+  )
+only_SB_variable <- only_SB_variable[order(only_SB_variable$SB_var_gmax_s), ]
+
+only_SB_variable$SB_var_gmax_s
+```
+
+```{r eval = FALSE}
+fig_state_vs_o2diff(only_SB_variable[13,])
+```
+
+Increases in oxygen diffusivity cause strain replacement in the SB to the more tolerant strains, which then delay the shift. When there is just a little more diversity in the SB, this happens:
+
+```{r eval = FALSE}
+fig_state_vs_o2diff(only_SB_variable[14,])
+```
+
+We believe that this phenomenon is caused by an effect that we explain with reference to an anology of using stepping stones to cross a river.
+Increasing diversity in our simulations is akin to increasing the width of the river, but while keeping the number of stepping stones (strains) constant.
+So long as the river is not too wide, we can still cross it, but once the width of the river is such that the stepping stones are too far apart, we can't cross the river.
+And this happens suddenly, the width increases just a tiny bit more, and we suddenly can't cross the river when we could before.
+
+In the simulated microbial ecosystem, the strains are the stepping stones, and it is much hard (takes longer) for strains to replace each other when there is greater distance (in trait space) between them.
+When they can no longer replace each other in the time available, the system behaves as if only the least tolerant, highest growth rate strain (lighted shade of colour) is present.
+In the case illustrated above, this leads to much lower resilience of the anoxic system state.
+
+This phenomena is dependent on having static trait values for the strains.
+If strain traits were dynamic (e.g.
+due to evolution), then we expect this result to not occur, and rather for the effects of diversity with two or three strains to be the same as those with six or nine.
+
+### Even shorter wait times
+
+```{r wait_time_1e4, eval = FALSE}
+
+wait_time <- "1e+04"
+
+stab_2s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_2strains_waittime", wait_time, "_event_definition_2.RDS")))
+stab_3s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))
+stab_6s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_6strains_waittime", wait_time, "_event_definition_2.RDS")))
+stab_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+
+all_stab <- stab_2s %>%
+  #bind_rows(stab_2s_sub1) %>%
+  bind_rows(stab_3s) %>%
+  #bind_rows(stab_3s_sub1) %>%
+  bind_rows(stab_6s) %>%
+  #bind_rows(stab_6s_sub1) %>%
+  bind_rows(stab_9s)
+  #bind_rows(stab_9s_sub1) %>%
+  #bind_rows(stab_9s_diff3)
+
+#all_stab <- stab_9s
+
+fig_div_vs_o2diff_multistrain(all_stab = all_stab,
+                  which_strains = c(2, 3, 6, 9),
+                  figure_title = paste0("Wait time = ", wait_time))
+
+```
+
+```{r wait_time_1e3, eval = FALSE}
+
+wait_time <- "1e+03"
+
+stab_2s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_2strains_waittime", wait_time, "_event_definition_2.RDS")))
+stab_3s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))
+stab_6s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_6strains_waittime", wait_time, "_event_definition_2.RDS")))
+stab_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+
+all_stab <- stab_2s %>%
+  #bind_rows(stab_2s_sub1) %>%
+  bind_rows(stab_3s) %>%
+  #bind_rows(stab_3s_sub1) %>%
+  bind_rows(stab_6s) %>%
+  #bind_rows(stab_6s_sub1) %>%
+  bind_rows(stab_9s)
+  #bind_rows(stab_9s_sub1) %>%
+  #bind_rows(stab_9s_diff3)
+
+#all_stab <- stab_9s
+
+fig_div_vs_o2diff_multistrain(all_stab = all_stab,
+                  which_strains = c(2, 3, 6, 9),
+                  figure_title = paste0("Wait time = ", wait_time))
+
+```
+
+```{r wait_time_1e2, eval = FALSE}
+
+wait_time <- "1e+02"
+
+stab_2s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_2strains_waittime", wait_time, "_event_definition_2.RDS")))
+stab_3s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))
+stab_6s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_6strains_waittime", wait_time, "_event_definition_2.RDS")))
+stab_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+
+all_stab <- stab_2s %>%
+  #bind_rows(stab_2s_sub1) %>%
+  bind_rows(stab_3s) %>%
+  #bind_rows(stab_3s_sub1) %>%
+  bind_rows(stab_6s) %>%
+  #bind_rows(stab_6s_sub1) %>%
+  bind_rows(stab_9s)
+  #bind_rows(stab_9s_sub1) %>%
+  #bind_rows(stab_9s_diff3)
+
+#all_stab <- stab_9s
+
+fig_div_vs_o2diff_multistrain(all_stab = all_stab,
+                  which_strains = c(2, 3, 6, 9),
+                  figure_title = paste0("Wait time = ", wait_time))
+
+```
+
+### Example of transient dynamics at 1'000'000 hours
+
+The results below show the stable states as a function of oxygen diffusivity for a system with intermediate level of diversity in all functional groups, with either 1'000'000 hours simulation time, or 2'000'000 hours.
+This shows that except very close to the values of oxygen diffusitivity at which a state transition occurs, 1'000'000 hours duration of the simulations is sufficient to reach stable state, or very close to it.
+Very close to the transitions, even at 2'000'000 hours, the dynamics are still transient, with high tolerance strains at high density, even though they will eventually be outcompeted by low tolerance (higher growth rate) strains.
+
+Below is Figure 3 from the main manuscript, in which the duration at each oxygen diffusivity value is 1e6:
+
+```{r echo = FALSE, fig.height=10}
+
+single_1e6 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/single_1e6_result.RDS"))
+# sort(unique(ss_9s$CB_var_gmax_s))
+# sort(unique(ss_9s$SB_var_gmax_s))
+# ss_result <- ss_9s %>%
+#   filter(abs(CB_var_gmax_s - 0.028254848) < 0.0001,
+#          abs(SB_var_gmax_s - 0.084764545) < 0.0001,
+#          abs(PB_var_gmax_s - 0.084764545) < 0.0001)
+
+temp <- single_1e6 %>%
   mutate(a = 10^a_O) %>%
@@
     functional_group = case_when(
-      str_detect(species, "CB_5") ~ "CB",
-      str_detect(species, "SB_5") ~ "SB",
-      str_detect(species, "PB_5") ~ "PB"
+      str_detect(species, "CB_") ~ "CB",
+      str_detect(species, "SB_") ~ "SB",
+      str_detect(species, "PB_") ~ "PB"
     ),
@@
 
-line_width <- 2
+line_width <- 1
 
@@
   ggtitle("(b) Cyanobacteria")
-p1# p1
+#p1# p1
 
@@
 patchwork
-#ggsave(here("experiments/1_figures_main_ms/figure_2b-f.pdf"))
+```
 
-## Figure 3 ----
-## Stable state with diversity in all functional groups.
+For comparison, here are the results with twice the duration at each oxygen diffusivity:
 
-ss_9s <- readRDS(here("experiments/0_ss_finding/data/9_strain_SS_data_1e3.RDS"))
-sort(unique(ss_9s$CB_var_gmax_s))
-sort(unique(ss_9s$SB_var_gmax_s))
-ss_result <- ss_9s %>%
-  filter(abs(CB_var_gmax_s - 0.028254848) < 0.0001,
-         abs(SB_var_gmax_s - 0.084764545) < 0.0001)
+```{r echo = FALSE, fig.height=10, eval = FALSE}
 
-temp <- ss_result$ssfind_result[[1]] %>%
+single_2e6 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/single_2e6_result.RDS"))
+# sort(unique(ss_9s$CB_var_gmax_s))
+# sort(unique(ss_9s$SB_var_gmax_s))
+# ss_result <- ss_9s %>%
+#   filter(abs(CB_var_gmax_s - 0.028254848) < 0.0001,
+#          abs(SB_var_gmax_s - 0.084764545) < 0.0001,
+#          abs(PB_var_gmax_s - 0.084764545) < 0.0001)
+
+temp <- single_2e6 %>%
   mutate(a = 10^a_O) %>%
@@
 patchwork
-#ggsave(here("experiments/1_figures_main_ms/figure_3.pdf"))
-
-## Figure 4 ----
-## Shows effect of no diversity versus diversity in all functional groups.
-
-ss_9s <- readRDS(here("experiments/0_ss_finding/data/9_strain_SS_data_1e3.RDS"))
-sort(unique(ss_9s$CB_var_gmax_s))
-sort(unique(ss_9s$SB_var_gmax_s))
-ss_result_none <- ss_9s %>%
-  filter(abs(CB_var_gmax_s - 0.0) < 0.0001,
-         abs(SB_var_gmax_s - 0.0) < 0.0001)
-ss_result_CB <- ss_9s %>%
-  filter(abs(CB_var_gmax_s - 0.014958449) < 0.0001,
-         abs(SB_var_gmax_s - 0.0) < 0.0001)
-ss_result_SBPB <- ss_9s %>%
-  filter(abs(CB_var_gmax_s - 0.0) < 0.0001,
-         abs(SB_var_gmax_s - 0.044875347) < 0.0001)
-ss_result_both <- ss_9s %>%
-  filter(abs(CB_var_gmax_s - 0.014958449) < 0.0001,
-         abs(SB_var_gmax_s - 0.044875347) < 0.0001)
-
-temp_none <- ss_result_none$ssfind_result[[1]] %>%
-  mutate(a = 10^a_O) %>%
-  # arrange(a) %>%
-  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
-  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
-  # select(-initial_N_CB, -a_O) %>%
-  gather(species, quantity, 2:(ncol(.) - 2)) %>%
-  mutate(
-    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
-    functional_group = case_when(
-      str_detect(species, "CB_") ~ "CB",
-      str_detect(species, "SB_") ~ "SB",
-      str_detect(species, "PB_") ~ "PB"
-    ),
-    log10_quantity = log10(quantity + 1)
-  )
-
-temp_CB <- ss_result_CB$ssfind_result[[1]] %>%
-  mutate(a = 10^a_O) %>%
-  # arrange(a) %>%
-  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
-  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
-  # select(-initial_N_CB, -a_O) %>%
-  gather(species, quantity, 2:(ncol(.) - 2)) %>%
-  mutate(
-    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
-    functional_group = case_when(
-      str_detect(species, "CB_") ~ "CB",
-      str_detect(species, "SB_") ~ "SB",
-      str_detect(species, "PB_") ~ "PB"
-    ),
-    log10_quantity = log10(quantity + 1)
-  )
-temp_SBPB <- ss_result_SBPB$ssfind_result[[1]] %>%
-  mutate(a = 10^a_O) %>%
-  # arrange(a) %>%
-  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
-  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
-  # select(-initial_N_CB, -a_O) %>%
-  gather(species, quantity, 2:(ncol(.) - 2)) %>%
-  mutate(
-    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
-    functional_group = case_when(
-      str_detect(species, "CB_") ~ "CB",
-      str_detect(species, "SB_") ~ "SB",
-      str_detect(species, "PB_") ~ "PB"
-    ),
-    log10_quantity = log10(quantity + 1)
-  )
-temp_both <- ss_result_both$ssfind_result[[1]] %>%
-  mutate(a = 10^a_O) %>%
-  # arrange(a) %>%
-  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
-  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
-  # select(-initial_N_CB, -a_O) %>%
-  gather(species, quantity, 2:(ncol(.) - 2)) %>%
-  mutate(
-    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
-    functional_group = case_when(
-      str_detect(species, "CB_") ~ "CB",
-      str_detect(species, "SB_") ~ "SB",
-      str_detect(species, "PB_") ~ "PB"
-    ),
-    log10_quantity = log10(quantity + 1)
-  )
-
-line_width <- 2.5
-
-## a
-p1 <- temp_none %>%
-  dplyr::filter(var_type == "Substrate", species == "O") %>%
-  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
-  geom_path(lwd = line_width) +
-  geom_path(data = filter(temp_CB, var_type == "Substrate", species == "O"),
-            col = "black", lwd = line_width - 1.5) +
-  ##ylab("log10(quantity [cells])") +
-  ylab("Log(Quantity)") +
-  xlab("Oxygen diffusivity") +
-  theme(legend.position="none") +
-  ggtitle("(a) No diversity versus diversity in only cyanobacteria") +
-  geom_vline(xintercept = c(-8, 0), col = "grey", lwd = 3)
-p2 <- temp_none %>%
-  dplyr::filter(var_type == "Substrate", species == "O") %>%
-  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
-  geom_path(lwd = line_width) +
-  geom_path(data = filter(temp_SBPB, var_type == "Substrate", species == "O"),
-            col = "black", lwd = line_width - 1.5) +
-  ##ylab("log10(quantity [cells])") +
-  ylab("Log(Quantity)") +
-  xlab("Oxygen diffusivity") +
-  theme(legend.position="none") +
-  ggtitle("(b) No diversity versus diversity in only sulfur bacteria") +
-  geom_vline(xintercept = c(-8, 0), col = "grey", lwd = 3)
-p3 <- temp_none %>%
-  dplyr::filter(var_type == "Substrate", species == "O") %>%
-  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
-  geom_path(lwd = line_width) +
-  geom_path(data = filter(temp_both, var_type == "Substrate", species == "O"),
-            col = "black", lwd = line_width - 1.5) +
-  ##ylab("log10(quantity [cells])") +
-  ylab("Log(Quantity)") +
-  xlab("Oxygen diffusivity") +
-  theme(legend.position="none") +
-  ggtitle("(c) No diversity versus diversity all functional groups") +
-  geom_vline(xintercept = c(-8, 0), col = "grey", lwd = 3)
-
-p1 / p2 / p3
-
-#ggsave(here("experiments/1_figures_main_ms/figure_4.pdf"),
-#       width = 6, height = 5)
-
-## Figure 5 ----
-## Region of bistability by diversity and number of strains.
-
-#ss_2s <- readRDS(here("experiments/0_ss_finding/data/2_strain_SS_data.RDS"))
-#stab_2s <- readRDS(here("experiments/0_ss_finding/data/2_strain_stab_data.RDS")) %>%
-#  mutate(num_strains = 2)
-ss_3s <- readRDS(here("experiments/0_ss_finding/data/3_strain_SS_data_1e3.RDS"))
-stab_3s <- readRDS(here("experiments/0_ss_finding/data/3_strain_stab_data_1e3.RDS")) %>%
-  mutate(num_strains = 3)
-#ss_6s <- readRDS(here("experiments/0_ss_finding/data/5-level factorial/6_strain_SS_data.RDS"))
-#stab_6s <- readRDS(here("experiments/0_ss_finding/data/5-level factorial/6_strain_stab_data.RDS")) %>%
-#  mutate(num_strains = 6)
-ss_9s <- readRDS(here("experiments/0_ss_finding/data/9_strain_SS_data_1e3.RDS"))
-stab_9s <- readRDS(here("experiments/0_ss_finding/data/9_strain_stab_data_1e3.RDS")) %>%
-  mutate(num_strains = 9)
-
-all_stab <- #stab_2s %>%
-  bind_rows(stab_3s) %>%
-  #bind_rows(stab_6s) %>%
-  bind_rows(stab_9s)
-
-#all_stab <- stab_9s
-
-CB_vars <- unique(all_stab$CB_var_gmax_s)
-SB_vars <- unique(all_stab$SB_var_gmax_s)
-
-CB_all_stab <- all_stab %>%
-  filter(SB_var_gmax_s == 0) %>%
-  mutate(var_treat = "CB",
-         var_gmax = CB_var_gmax_s)
-
-SBPB_all_stab <- all_stab %>%
-  filter(CB_var_gmax_s == 0) %>%
-  mutate(var_treat = "SB-PB",
-         var_gmax = SB_var_gmax_s)
-
-for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
-                   SB_var_gmax_s = sort(SB_vars))
-CBSBPB_all_stab <- all_stab %>%
-  right_join(for_join) %>%
-  mutate(var_treat = "CB-SB-PB",
-         var_gmax = CB_var_gmax_s)
-
-all_stab_results <- CB_all_stab %>%
-  bind_rows(SBPB_all_stab) %>%
-  #  bind_rows(results3) %>%
-  # bind_rows(results4) %>%
-  bind_rows(CBSBPB_all_stab)
-
-all_stab_results <- all_stab_results %>%
-  mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB-PB", "CB-SB-PB")))
-
-all_stab_results_small <- select(all_stab_results, -7:-12)
-
-all_stab_results %>%
-  #filter(var_treat == "CB") %>%
-  filter(Species == "O") %>%
-  ggplot(aes(x = var_gmax,
-             col = as.factor(num_strains))) +
-  geom_line(aes(y = hyst_min_log), lwd = 1.5) +
-  geom_line(aes(y = hyst_max_log), lwd = 1.5) +
-  facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
-  labs(fill = "Variation in\nonly these\nfunctional groups") +
-  coord_flip() +
-  guides(col = guide_legend(title="Number of strains")) +
-  theme(
-    legend.position="top"
-    #strip.background = element_blank(),
-    #strip.text.x = element_blank()
-  ) +
-  geom_hline(yintercept = c(-8, 0), col = "grey", lwd = 3)
-
-#ggsave(here("experiments/1_figures_main_ms/figure_5.pdf"),
-#       width = 5, height = 4)
-
-temp <- all_stab_results %>%
-  #filter(var_treat == "CB") %>%
-  filter(Species == "O",
-         var_treat == "SB-PB",
-         num_strains == 9) %>%
-  ggplot(aes(x = var_gmax,
-             col = as.factor(num_strains))) +
-  geom_line(aes(y = hyst_min_log)) +
-  geom_line(aes(y = hyst_max_log)) +
-  facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
-  labs(fill = "Variation in\nonly these\nfunctional groups") +
-  coord_flip() +
-  guides(col = guide_legend(title="Number of strains")) +
-  theme(
-    legend.position="top"
-    #strip.background = element_blank(),
-    #strip.text.x = element_blank()
-  ) +
-  geom_hline(yintercept = c(-8, 0), col = "grey", lwd = 3)
-
-## 
-## 
-```
-
-# Robustness of stable state finding
-
-We now discuss two approaches for finding how the stable state of the system varies along the gradient of oxygen diffusivity when there exists the possibility of multiple stable states.
-In the main article we report results of the method also described there.
-Briefly here, we made a separate simulations for each of many values of oxygen diffusivity, ran the simulations for long enough to ensure transients had passed, and recorded the state.
-We ran multiple simulations per value of oxygen diffusivity, and started them with different initial conditions (either low or high total cyanobacterial abundance), so as to check for presence of alternate stable states.
-This method used by [Bush et al 2017](https://www.nature.com/articles/s41467-017-00912-x).
-We hereafter term this "the replication method", since it is effectively achieved by having many independent replicates of the ecosystem, each with a different oxygen diffusivity, and also a separate replicate for each of the different chosen initial conditions.
-
-Here we report the results of a second method.
-We will show some quantitative differences in results compared to the other method, but also show the results concerning diversity effects are qualitatively the same as obtained with the first method.
-
-The second method involves two simulations for a particular system configuration (parameter set).
-In one simulation the oxygen diffusivity is *increased* in a step-wise fashion.
-In the other it is *decreased* in a step-wise fashion.
-That is, oxygen diffusivity is held at a constant level for long enough for steady state to be reach, that state is recorded, and then a slightly higher (or lower) oxygen diffusivity value is set.
-Hence, at that time point, the system is effectively started with initial conditions that are the state of the system in the previous time step.
-We hereafter term this "the temporal method".
-
-The temporal method results in a larger region of bistability than the replication method (Figure \@ref(fig:tempmeth1)).
-That is, a greater extent of environmental change is required to switch the system to the other state (i.e.
-the region of bistability is greater).
-This occurs both during increasing and decreasing oxygen diffusivities.
-The difference in results occurs because, as mentioned above, the initial conditions differ between the two approaches.
-For example, in the temporal method, the oxygen concentration in the anoxic state is lower than the initial oxygen concentration in the replication approach, and **Owen guesses that** the sulfide concentration is higher **check that last statement**.
-
-## Replication method
-
-```{r repl_meth1, echo=FALSE}
-repl_meth <- readRDS(here("experiments/0_ss_finding/replication_method/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
-temp_meth <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_SS_data.RDS"))
-## To be completed.
-plot_ss_result1(repl_meth,
-                result_index = 1,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-```
-
-## Temporal method
-
-```{r temp_meth1, echo=FALSE}
-plot_ss_result3(temp_meth, 1)
-```
-
-## Both methods overlaid
-
-```{r both_meth1, echo=FALSE}
-repl_method_1 <- repl_meth$ss_res[[1]] %>%
-     mutate(time = NA,
-            direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
-  select(names(temp_meth$ssfind_result[[1]]))
-
-ss_result1 <- repl_method_1
-ss_result2 <- temp_meth$ssfind_result[[1]]
-
-plot_ss_result6(repl_method_1,
-                temp_meth$ssfind_result[[1]],
-                xlims = c(-8, 0))
-```
-
-## Effect of diversity, replication method
-
-The replication method shows the same effects of functional diversity as those revealed by the replication method:
-
--   Introducing functional diversity in all three functional groups increases the region of bistability relative to when there is no diversity within all functional groups)..
--   Introducing functional diversity in only the cyanobacteria function group delays (with respect to the oxygen diffusivity it occurs at) the switch to the anoxic state as oxygen diffusivity is reduced, but has no effect on the oxygen diffusivity at which the anoxic to oxic transition occurs .
--   Introducing function diversity in only the sulfur bacteria delays (with respect to the oxygen diffusivity it occurs at) the switch from anoxic to oxic, and advances the switch from oxic to anoxic (Figure \@ref(fig:tempmeth4).
-
-```{r echo = FALSE}
-stab_data <- readRDS(here("experiments/0_ss_finding/replication_method/9_strains/data/stab_data_1e6_x2x6_factorial.RDS"))
-
-all_stab <- stab_data
-
-#all_stab <- stab_9s
-
-CB_vars <- unique(all_stab$CB_var_gmax_s)
-SB_vars <- unique(all_stab$SB_var_gmax_s)
-
-CB_all_stab <- all_stab %>%
-  filter(SB_var_gmax_s == 0) %>%
-  mutate(var_treat = "CB",
-         var_gmax = CB_var_gmax_s)
-
-SBPB_all_stab <- all_stab %>%
-  filter(CB_var_gmax_s == 0) %>%
-  mutate(var_treat = "SB-PB",
-         var_gmax = SB_var_gmax_s)
-
-for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
-                   SB_var_gmax_s = sort(SB_vars))
-CBSBPB_all_stab <- all_stab %>%
-  right_join(for_join) %>%
-  mutate(var_treat = "CB-SB-PB",
-         var_gmax = CB_var_gmax_s)
-
-all_stab_results <- CB_all_stab %>%
-  bind_rows(SBPB_all_stab) %>%
-  #  bind_rows(results3) %>%
-  # bind_rows(results4) %>%
-  bind_rows(CBSBPB_all_stab)
-
-all_stab_results <- all_stab_results %>%
-  mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB-PB", "CB-SB-PB")))
-
-all_stab_results_small <- select(all_stab_results, -7:-12)
-
-all_stab_results %>%
-  #filter(var_treat == "CB") %>%
-  filter(Species == "SR") %>%
-  ggplot(aes(x = var_gmax)) +
-  #ggplot(aes(x = var_gmax,
-  #           col = as.factor(num_strains))) +
-  geom_line(aes(y = hyst_min_log), lwd = 3, alpha = 0.8) +
-  geom_line(aes(y = hyst_max_log), lwd = 3, alpha = 0.8) +
-  facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
-  labs(fill = "Variation in\nonly these\nfunctional groups") +
-  coord_flip() +
-  #guides(col = guide_legend(title="Number of strains")) +
-  theme(
-    legend.position="top"
-    #strip.background = element_blank(),
-    #strip.text.x = element_blank()
-  ) +
-  geom_hline(yintercept = c(-8, 0), col = "grey", lwd = 3)
-
-#ggsave(here("experiments/1_figures_main_ms/figure_5.pdf"),
-#       width = 5, height = 4)
-
 ```
@@
 
-In the original publication ([Bush et al 2017])(<https://www.nature.com/articles/s41467-017-00912-x>) Figure 3a shows a separatrix in the cyanobacteria abundance - oxygen diffusivity dimensions of the system.
+In the original publication ([Bush et al 2017](<https://www.nature.com/articles/s41467-017-00912-x>)) Figure 3a shows a separatrix in the cyanobacteria abundance - oxygen diffusivity dimensions of the system.
 If the system has initial cyanobacterial abundance greater than the value at the separatrix then the cyanobacterial abundance increases, and the system goes to the oxic stable state.

### 2022-02-02 R/various_useful_functions.r

@@ -370,7 +370,8 @@ display_diversity <- function(
   var_expt,
   num_CB_strains,
   num_SB_strains,
-  num_PB_strains
+  num_PB_strains,
+  which_graphs = 3
 ) {
   colfunc_CB <- colorRampPalette(c("#024F17", "#B5FFC9"))
   colfunc_SB <- colorRampPalette(c("#7D1402", "#FCBEB3"))
@@ -389,7 +390,7 @@ display_diversity <- function(
   
   CB_TO1 <- ggplot(CBtraits) +
     geom_point(aes(x = h_SR_CB, y = g_max_CB, col = strain_name), size = ptsize) +
-    xlab("Tolerance\n(cyanobacteria to reduced sulphur)") +
+    xlab("Tolerance\n(cyanobacteria to\nreduced sulphur)") +
     ylab("Maximum growth rate\n(cyanobacteria)") +
     scale_colour_manual(values = colfunc_CB(num_CB_strains)) +
     theme(legend.position = "none")
@@ -414,7 +415,7 @@ display_diversity <- function(
 
   SB_TO1 <- ggplot(SBtraits) +
     geom_point(aes(x = h_O_SB, y = g_max_SB, col = strain_name), size = ptsize) +
-    xlab("Tolerance\n(sulphate reducing bacteria to oxygen)") +
+    xlab("Tolerance\n(sulphate reducing bacteria\nto oxygen)") +
     ylab("Maximum growth rate\n(sulphate reducing bacteria)") +
     scale_colour_manual(values = colfunc_SB(num_SB_strains)) +
     theme(legend.position = "none")
@@ -437,7 +438,7 @@ display_diversity <- function(
 
   PB_TO1 <- ggplot(PBtraits) +
     geom_point(aes(x = h_O_PB, y = g_max_PB, col = strain_name), size = ptsize) +
-    xlab("Tolerance\n(phototrophic sulphur bacteria to oxygen)") +
+    xlab("Tolerance\n(phototrophic sulphur bacteria\nto oxygen)") +
     ylab("Maximum growth rate\n(phototrophic sulphur bacteria") +
     scale_colour_manual(values = colfunc_PB(num_PB_strains)) +
     theme(legend.position = "none")
@@ -447,7 +448,14 @@ display_diversity <- function(
[…]

### 2022-02-03 experiments/1_figures_main_ms/Understand_PB.Rmd
large number of updates, no changes in results though

@@
 ## Figure 5
+
 Region of bistability by diversity and number of strains.
 
-![alt text](figure_5_v2_allstrains.png)
+(*Graphs should be remade/reinserted.*)
 
@@
 ```{r fig3_prep}
-ss_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_SS_data_1e6.RDS"))
+ss_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
 

### 2022-02-03 experiments/2_supplement/supplement.Rmd
large number of updates, no changes in results though

@@
 
-```{r repl_meth1, echo=FALSE, eval = FALSE}
+```{r repl_meth1, echo=FALSE, eval = TRUE}
 repl_meth <- readRDS(here("experiments/0_ss_finding/replication_method/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
@@
 
-```{r temp_meth1, echo=FALSE, eval = FALSE}
+```{r temp_meth1, echo=FALSE, eval = TRUE}
 plot_ss_result3(temp_meth, 1)
@@
 
-```{r both_meth1, echo=FALSE, eval = FALSE}
+```{r both_meth1, echo=FALSE, eval = TRUE}
 repl_method_1 <- repl_meth$ss_res[[1]] %>%
@@
 
-```{r echo = FALSE, eval = FALSE}
+```{r echo = FALSE, eval = TRUE}
 stab_data <- readRDS(here("experiments/0_ss_finding/replication_method/9_strains/data/small_stab_data_1e6_x2x6_factorial.RDS"))
@@
 
-```{r echo = FALSE, eval = FALSE}
+```{r echo = FALSE, eval = TRUE}
 all_stab_results %>%
@@
 
-```{r wait_time_1e6, eval = FALSE}
-wait_time <- "1e+06"
+```{r wait_time_1e6, eval = TRUE}
+all_stab <- readRDS(here("experiments/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS"))
 
-#stab_2s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_2strains_waittime", wait_time, "_event_definition_2.RDS")))
-#stab_3s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))
-#stab_6s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_6strains_waittime", wait_time, "_event_definition_2.RDS")))
-stab_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+wait_time <- 1e6
+num_strains <- 9
+plot_here <- all_stab %>%
+  filter(waittime == wait_time)
+p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
+                                     which_strain = num_strains,
+                                     figure_title = paste0(wait_time,
+                                                           " wait time,\n",
+                                                           num_strains,
+                                                           " strains"))
+p2 <- fig_resilience_vs_div(plot_here,
+                            which_strain = num_strains,
+                            figure_title = " ") 
+p1 + p2
 
-#all_stab <- stab_2s %>%
-  #bind_rows(stab_2s_sub1) %>%
-#  bind_rows(stab_3s) %>%
-  #bind_rows(stab_3s_sub1) %>%
-#  bind_rows(stab_6s) %>%
-  #bind_rows(stab_6s_sub1) %>%
-#  bind_rows(stab_9s)
-  #bind_rows(stab_9s_sub1) %>%
-  #bind_rows(stab_9s_diff3)
-
-all_stab <- stab_9s
 ```
 
-```{r wait_time_1e6_2, eval = FALSE}
-p1 <- fig_div_vs_o2diff_1strain_7row(all_stab,
-                                     which_strain = 9,
-                                     figure_title = "1e6 wait time, 9 strains")
-#p1
-p2 <- fig_resilience_vs_div(all_stab, which_strain = 9, figure_title = " ") 
-#p2
+```{r wait_time_1e5, eval = TRUE}
+
+wait_time <- 1e5
+num_strains <- 9
+plot_here <- all_stab %>%
+  filter(waittime == wait_time)
+p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
+                                     which_strain = num_strains,
+                                     figure_title = paste0(wait_time,
+                                                           " wait time,\n",
+                                                           num_strains,
+                                                           " strains"))
+p2 <- fig_resilience_vs_div(plot_here,
+                            which_strain = num_strains,
+                            figure_title = " ") 
 p1 + p2
+```
 
+```{r wait_time_1e4, eval = TRUE}
+
+wait_time <- 1e4
+num_strains <- 9
+plot_here <- all_stab %>%
+  filter(waittime == wait_time)
+p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
+                                     which_strain = num_strains,
+                                     figure_title = paste0(wait_time,
+                                                           " wait time,\n",
+                                                           num_strains,
+                                                           " strains"))
+p2 <- fig_resilience_vs_div(plot_here,
+                            which_strain = num_strains,
+                            figure_title = " ") 
+p1 + p2
+```
+
+```{r wait_time_1e3, eval = TRUE}
+
+wait_time <- 1e3
+num_strains <- 9
+plot_here <- all_stab %>%
+  filter(waittime == wait_time)
+p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
+                                     which_strain = num_strains,
+                                     figure_title = paste0(wait_time,
+                                                           " wait time,\n",
+                                                           num_strains,
+                                                           " strains"))
+p2 <- fig_resilience_vs_div(plot_here,
+                            which_strain = num_strains,
+                            figure_title = " ") 
+p1 + p2
+```
+
+```{r wait_time_1e2, eval = TRUE}
+
+wait_time <- 1e2
+num_strains <- 9
+plot_here <- all_stab %>%
+  filter(waittime == wait_time)
+p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
+                                     which_strain = num_strains,
+                                     figure_title = paste0(wait_time,
+                                                           " wait time,\n",
+                                                           num_strains,
+                                                           " strains"))
+p2 <- fig_resilience_vs_div(plot_here,
+                            which_strain = num_strains,
+                            figure_title = " ") 
+p1 + p2
 ```
@@
 
-```{r wait_time_1e5, eval = FALSE}
-
-wait_time <- "1e+05"
-
-stab_2s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_2strains_waittime", wait_time, "_event_definition_2.RDS")))
-stab_3s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))
-stab_6s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_6strains_waittime", wait_time, "_event_definition_2.RDS")))
-stab_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
-
-all_stab <- stab_2s %>%
-  #bind_rows(stab_2s_sub1) %>%
-  bind_rows(stab_3s) %>%
-  #bind_rows(stab_3s_sub1) %>%
-  bind_rows(stab_6s) %>%
-  #bind_rows(stab_6s_sub1) %>%
-  bind_rows(stab_9s)
-  #bind_rows(stab_9s_sub1) %>%
-  #bind_rows(stab_9s_diff3)
-
-#all_stab <- stab_9s
-
-fig_div_vs_o2diff_multistrain(all_stab = all_stab,
-                  which_strains = c(2, 3, 6, 9),
-                  figure_title = paste0("Wait time = ", wait_time))
-
-```
-
 Here, moderate increases in diversity have the same effect as with wait times of 1e6.
@@
 
-```{r eval = FALSE}
+```{r eval = TRUE}
 wait_time <- "1e+04"
@@
 
-```{r eval = FALSE}
+```{r eval = TRUE}
 fig_state_vs_o2diff(only_SB_variable[13,])
@@
 
-```{r eval = FALSE}
+```{r eval = TRUE}
 fig_state_vs_o2diff(only_SB_variable[14,])
@@
 due to evolution), then we expect this result to not occur, and rather for the effects of diversity with two or three strains to be the same as those with six or nine.
-
-### Even shorter wait times
-
-```{r wait_time_1e4, eval = FALSE}
-
-wait_time <- "1e+04"
-
-stab_2s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_2strains_waittime", wait_time, "_event_definition_2.RDS")))
-stab_3s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))
-stab_6s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_6strains_waittime", wait_time, "_event_definition_2.RDS")))
-stab_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
-
-all_stab <- stab_2s %>%
-  #bind_rows(stab_2s_sub1) %>%
-  bind_rows(stab_3s) %>%
-  #bind_rows(stab_3s_sub1) %>%
-  bind_rows(stab_6s) %>%
-  #bind_rows(stab_6s_sub1) %>%
-  bind_rows(stab_9s)
-  #bind_rows(stab_9s_sub1) %>%
-  #bind_rows(stab_9s_diff3)
-
-#all_stab <- stab_9s
-
-fig_div_vs_o2diff_multistrain(all_stab = all_stab,
-                  which_strains = c(2, 3, 6, 9),
-                  figure_title = paste0("Wait time = ", wait_time))
-
-```
-
-```{r wait_time_1e3, eval = FALSE}
-
-wait_time <- "1e+03"
-
-stab_2s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_2strains_waittime", wait_time, "_event_definition_2.RDS")))
-stab_3s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))
-stab_6s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_6strains_waittime", wait_time, "_event_definition_2.RDS")))
-stab_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
-
-all_stab <- stab_2s %>%
-  #bind_rows(stab_2s_sub1) %>%
-  bind_rows(stab_3s) %>%
-  #bind_rows(stab_3s_sub1) %>%
-  bind_rows(stab_6s) %>%
-  #bind_rows(stab_6s_sub1) %>%
-  bind_rows(stab_9s)
-  #bind_rows(stab_9s_sub1) %>%
-  #bind_rows(stab_9s_diff3)
-
-#all_stab <- stab_9s
-
-fig_div_vs_o2diff_multistrain(all_stab = all_stab,
-                  which_strains = c(2, 3, 6, 9),
-                  figure_title = paste0("Wait time = ", wait_time))
-
-```
-
-```{r wait_time_1e2, eval = FALSE}
-
-wait_time <- "1e+02"
-
-stab_2s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_2strains_waittime", wait_time, "_event_definition_2.RDS")))
-stab_3s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))
-stab_6s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_6strains_waittime", wait_time, "_event_definition_2.RDS")))
-stab_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
-
-all_stab <- stab_2s %>%
-  #bind_rows(stab_2s_sub1) %>%
-  bind_rows(stab_3s) %>%
-  #bind_rows(stab_3s_sub1) %>%
-  bind_rows(stab_6s) %>%
-  #bind_rows(stab_6s_sub1) %>%
-  bind_rows(stab_9s)
-  #bind_rows(stab_9s_sub1) %>%
-  #bind_rows(stab_9s_diff3)
-
-#all_stab <- stab_9s
-
-fig_div_vs_o2diff_multistrain(all_stab = all_stab,
-                  which_strains = c(2, 3, 6, 9),
-                  figure_title = paste0("Wait time = ", wait_time))
-
-```
 
@@
 
-```{r echo = FALSE, fig.height=10, eval = FALSE}
+```{r echo = FALSE, fig.height=10, eval = TRUE}
 

### 2022-02-03 experiments/0_ss_finding/temporal_method/data_processing.R

@@ -1,0 +1,121 @@
+
+
+library(here)
+library(tidyverse)
+
+
+
+## Process the stability data to a smaller file ----
+
+read_plus <- function(flnm) {
+  print(flnm)
+  readRDS(flnm) %>% 
+    mutate(filename = flnm)
+}
+
+tbl1 <- list.files(path = here("experiments/0_ss_finding/temporal_method/data"),
+                   pattern = "stab_data", 
+                   full.names = T,
+                   recursive = T) %>% 
+  map_df(~read_plus(.))
+
+keep_tbl1 <- tbl1
+
+all_stab <- tbl1 %>%
+  select(-data, -pars, -parameter, -total_initial_abundances, -ssfind_pars, -ssfind_result) %>%
+  separate(filename , sep = "_", into = c(paste0("junk", 1:7), "waittime", paste0("junk", 8:10))) %>%
+  select(-starts_with("junk")) %>%
+  mutate(waittime = parse_number(waittime))
+
+
+
+CB_vars <- unique(all_stab$CB_var_gmax_s)
+SB_vars <- unique(all_stab$SB_var_gmax_s)
+PB_vars <- unique(all_stab$PB_var_gmax_s)
+
+CB_all_stab <- all_stab %>%
+  filter(SB_var_gmax_s == 0,
+         PB_var_gmax_s == 0) %>%
+  ungroup() %>%
+  mutate(var_treat = "CB",
+         var_gmax = CB_var_gmax_s,
+         stand_var = var_gmax / max(var_gmax))
+SB_all_stab <- all_stab %>%
+  filter(CB_var_gmax_s == 0,
+         PB_var_gmax_s == 0)  %>%
+  ungroup() %>%
+  mutate(var_treat = "SB",
+         var_gmax = SB_var_gmax_s,
+         stand_var = var_gmax / max(var_gmax))
+PB_all_stab <- all_stab %>%
+  filter(CB_var_gmax_s == 0,
+         SB_var_gmax_s == 0) %>%
+  ungroup()  %>%
+  mutate(var_treat = "PB",
+         var_gmax = PB_var_gmax_s,
+         stand_var = var_gmax / max(var_gmax))
+
+for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
+                   SB_var_gmax_s = sort(SB_vars))
+CBSB_all_stab <- all_stab %>%
+  right_join(for_join)  %>%
+  ungroup() %>%
[…]

### 2022-02-03 experiments/1_figures_main_ms/ms_figure_functions.R

@@ -286,6 +286,7 @@ fig_state_vs_o2diff <- function(ss_result){
     mutate(species = factor(species, levels = unique(species))) %>%
     ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
     geom_path(lwd = line_width) +
+    #geom_point() +
     ##ylab("log10(quantity [cells])") +
     ylab("Log(Quantity)") +
     xlab("Oxygen diffusivity") +
@@ -293,7 +294,7 @@ fig_state_vs_o2diff <- function(ss_result){
     guides(colour = guide_legend(ncol = 3)) +
     theme(legend.position="none") +
     ggtitle("(a) Cyanobacteria")
-  
+  p1
   p2 <- temp %>%
     dplyr::filter(functional_group == "SB")  %>%
     mutate(species = factor(species, levels = unique(species))) %>%
@@ -444,6 +445,113 @@ fig_state_vs_o2diff_sidebyside <- function(ss_result){
   patchwork
 }
 
+fig_state_vs_o2diff_sidebyside_dots <- function(ss_result){
+  temp <- ss_result$ssfind_result[[1]] %>%
+    mutate(a = 10^a_O) %>%
+    # arrange(a) %>%
+    # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
+    #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
+    # select(-initial_N_CB, -a_O) %>%
+    gather(species, quantity, 2:(ncol(.) - 2)) %>%
+    mutate(
+      var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
+      functional_group = case_when(
+        str_detect(species, "CB_") ~ "CB",
+        str_detect(species, "SB_") ~ "SB",
+        str_detect(species, "PB_") ~ "PB"
+      ),
+      log10_quantity = log10(quantity + 1)
+    )
+  
+  num_strains <- temp %>%
+    group_by(functional_group) %>%
+    summarise(num = length(unique(species))) %>%
+    na.omit()
+  
+  num_CB_strains <- num_strains$num[num_strains$functional_group == "CB"]
+  num_SB_strains <- num_strains$num[num_strains$functional_group == "SB"]
+  num_PB_strains <- num_strains$num[num_strains$functional_group == "PB"]
+  
[…]

### 2022-02-07 experiments/2_supplement/supplement.Rmd
Update supplement.Rmd

@@
 subtitle: Functional diversity ... Predictions of a model of an oxic-anoxic microbial ecosystem 
-author: "Owen L Petchey, Rainer Krug, Marcel Suleiman, ???others???"
+author: "Owen L Petchey, Rainer Krug, Marcel Suleiman, Romana Limberger, ???others???"
 date: "`r format(Sys.time(), '%d %B, %Y')`"

### 2022-02-12 experiments/2_supplement/supplement.Rmd
updated the replication method

@@
 These results are shown in the figure below, which shows results of the replication method.
+
+```{r eval = TRUE}
+all_stab <- readRDS(here("experiments/0_ss_finding/replication_method/processed_data/stab_data_replication_method.RDS"))
+
+simlength <- 1e4
+num_strains <- 2
+plot_here <- all_stab %>%
+  filter(simlength == simlength)
+p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
+                                     which_strain = num_strains,
+                                     figure_title = paste0(simlength,
+                                                           " sim. length,\n",
+                                                           num_strains,
+                                                           " strains"))
+p2 <- fig_resilience_vs_div(plot_here,
+                            which_strain = num_strains,
+                            figure_title = " ") 
+p1 + p2
+
+```
 

### 2022-02-12 R/various_useful_functions.r

@@ -56,7 +56,7 @@ setup_R <- function() {
 
 
 
-run_ss_var_experiment <- function(parameter, var_expt) {
+run_replication_ssfind_experiment <- function(parameter, var_expt) {
 
   # var_expt <- tibble(CB_var_gmax_s,
   #                    CB_var_h_s,
@@ -101,7 +101,7 @@ run_ss_var_experiment <- function(parameter, var_expt) {
         p
       })
     ) %>%
-    mutate(ss_by_a_N_result = list(ss_by_a_N(ss_by_a_N_result))) %>%
+    mutate(ss_by_a_N_result = list(run_replication_ssfind(ss_by_a_N_result))) %>%
     mutate(ss_res = list(ss_by_a_N_result$result))
   
   return(result)

### 2022-02-12 experiments/0_ss_finding/replication_method/data_processing.R

@@ -1,0 +1,121 @@
+
+
+library(here)
+library(tidyverse)
+
+
+
+## Process the stability data to a smaller file ----
+
+read_plus <- function(flnm) {
+  print(flnm)
+  readRDS(flnm) %>% 
+    mutate(filename = flnm)
+}
+
+tbl1 <- list.files(path = here("experiments/0_ss_finding/replication_method/data"),
+                   pattern = "stab_data", 
+                   full.names = T,
+                   recursive = T) %>% 
+  map_df(~read_plus(.))
+
+keep_tbl1 <- tbl1
+
+all_stab <- tbl1 %>%
+  select(-data, -pars, -ss_by_a_N_result, -ss_res) %>%
+  separate(filename , sep = "_", into = c(paste0("junk", 1:8), "simlength", paste0("junk", 9:11))) %>%
+  select(-starts_with("junk")) %>%
+  mutate(simlength = parse_number(simlength))
+
+
+
+CB_vars <- unique(all_stab$CB_var_gmax_s)
+SB_vars <- unique(all_stab$SB_var_gmax_s)
+PB_vars <- unique(all_stab$PB_var_gmax_s)
+
+CB_all_stab <- all_stab %>%
+  filter(SB_var_gmax_s == 0,
+         PB_var_gmax_s == 0) %>%
+  ungroup() %>%
+  mutate(var_treat = "CB",
+         var_gmax = CB_var_gmax_s,
+         stand_var = var_gmax / max(var_gmax))
+SB_all_stab <- all_stab %>%
+  filter(CB_var_gmax_s == 0,
+         PB_var_gmax_s == 0)  %>%
+  ungroup() %>%
+  mutate(var_treat = "SB",
+         var_gmax = SB_var_gmax_s,
+         stand_var = var_gmax / max(var_gmax))
+PB_all_stab <- all_stab %>%
+  filter(CB_var_gmax_s == 0,
+         SB_var_gmax_s == 0) %>%
+  ungroup()  %>%
+  mutate(var_treat = "PB",
+         var_gmax = PB_var_gmax_s,
+         stand_var = var_gmax / max(var_gmax))
+
+for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
+                   SB_var_gmax_s = sort(SB_vars))
+CBSB_all_stab <- all_stab %>%
+  right_join(for_join)  %>%
+  ungroup() %>%
+  mutate(var_treat = "CB-SB",
[…]

### 2022-02-12 experiments/0_ss_finding/replication_method/run_experiment.R

@@ -1,0 +1,64 @@
+## SS finding experiment by replication method
+## Be careful to not overwrite data files
+
+rm(list = ls())
+source(here::here("R/various_useful_functions.r"))
+max_cores <- benchmarkme::get_cpu()$no_of_cores-2
+options(mc.cores = max_cores)
+
+sim_length <- 1e4
+event_def <- "event_definition_2"
+
+## Run for 2, 3, 6, and 9 strains
+for(num_strains in c(2, 3, 6, 9)) {
+  
+  num_strains <- 2 ## for testing
+  
+  ## Run the code that sets up the experiment
+  source(here::here("experiments/0_ss_finding/replication_method/setup_experiment.R"))
+  
+  ss_data_filename <- here("experiments/0_ss_finding/replication_method/data",
+                           paste0("ss_data_",
+                                  num_strains, "strains_sim_length",
+                                  formatC(sim_length, format = "e", digits = 0),
+                                  "_", event_def,".RDS"))
+  stab_data_filename <- here("experiments/0_ss_finding/replication_method/data",
+                             paste0("stab_data_",
+                                    num_strains, "strains_sim_length",
+                                    formatC(sim_length, format = "e", digits = 0),
+                                    "_", event_def,".RDS"))
+
+  #var_expt <- var_expt[1:10,]
+  
+  system.time(
+    run_replication_ssfind_experiment(parameter, var_expt) %>%
+      saveRDS(ss_data_filename)
+  )
+  
+  
+  
+  ## Get stability measures ----
+  num_cores <- min(c(max_cores, nrow(var_expt)))
+  expt_res <- readRDS(ss_data_filename)
+  ## Get total biomass of CB, of SB, and of PB, to allow calculation of stability of these
+  expt_res <- expt_res %>%
+    mutate(ss_res = list(get_total_bio(ss_res)))
+  cluster1 <- multidplyr::new_cluster(num_cores)
+  multidplyr::cluster_library(cluster1, c("microxanox", "dplyr"))
+  system.time({
+    stab_data <-  expt_res %>%
+      multidplyr::partition(cluster1) %>%
+      mutate(stability_measures = list(get_stability_measures_replication_ssfind_result(ss_res))) %>%
+      collect() %>%
+      unnest(cols = c(stability_measures)) %>%
+      mutate(num_strains = num_strains)
+  })
+  saveRDS(stab_data, stab_data_filename)
+  ## End of getting stability measures
+  
+    
+}
+
+
+
+x <- parameter$ss_expt[i, ]

### 2022-02-20 experiments/2_supplement/supplement.Rmd
working on supplement
and other things

--- 2022-02-07 experiments/2_supplement/supplement.Rmd
@@
                       message = FALSE,
-                      cache = FALSE)
+                      cache = TRUE)
 ```
@@
 
+```{r repl_meth1, echo=FALSE, eval = TRUE}
+repl_meth <- readRDS(here("experiments/0_ss_finding/replication_method/data/ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
+temp_meth <- readRDS(here("experiments/0_ss_finding/temporal_method/data/ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
+```
+
 In the following graph, the solid (down) line refers to the stable state when cyanobacteria begin at high abundance (favouring the oxic state).
-The dashed up line refers to when their initial abundnace is low (favouring the anoxic state).Stable states found with the replication method.
+The dashed up line refers to when their initial abundnace is low (favouring the anoxic state).
+Stable states found with the replication method.
 Please note: i) that near vertical lines indicate the position of a tipping point and hence the system cannot exist on point of that part of the line; ii) the separatrix (the unstable equilibrium) is not shown.
 
-```{r repl_meth1, echo=FALSE, eval = TRUE}
-repl_meth <- readRDS(here("experiments/0_ss_finding/replication_method/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
-temp_meth <- readRDS(here("experiments/0_ss_finding/temporal_method/data/ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
+(ref:repl-meth2) Figure caption.
+
+```{r repl-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:repl-meth2)', fig.height=8, fig.width=8, fig.align="center"}
 ## To be completed.
@@
 
-Same as for the previous graph.
+(ref:temp-meth2) ...
 
-```{r temp_meth1, echo=FALSE, eval = TRUE}
+```{r temp-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:temp-meth2)', fig.height=8, fig.width=8, fig.align="center"}
 plot_ss_result3(temp_meth, 1)
@@
 
-```{r both_meth1, echo=FALSE, eval = TRUE}
+(ref:both-meth1) ...
+
+```{r both-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:both-meth1)', fig.height=8, fig.width=8, fig.align="center"}
 repl_method_1 <- repl_meth$ss_res[[1]] %>%
@@
 
-```{r echo = FALSE, eval = TRUE}
+(ref:div-repl-meth1) The figure shows the effect of response trait diversity (y-axis) on the positions of the tipping points (show by dark lines), which determine the extent of the region of bistability in the oxygen diffusivity gradient.
+The left-most region is anoxic only, the middle is oxic or anoxic depending on historical conditions, and the right-most is oxic only.
+The thick grey vertical lines at -8 and 0 on the x-axis show the extent of the oxygen diffusivity gradient investigated in the simulations.
+
+```{r div-repl-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-repl-meth1)', fig.height=8, fig.width=8, fig.align="center"}
+all_stab <- readRDS(here("experiments/0_ss_finding/replication_method/processed_data/stab_data_replication_method.RDS"))
+
+sim_length <- 1e6
+num_strains <- 9
+plot_here <- all_stab %>%
+  filter(simlength == sim_length)
+p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
+                                     which_strain = num_strains,
+                                     figure_title = paste0(sim_length,
+                                                           " sim. length,\n",
+                                                           num_strains,
+                                                           " strains"))
+p2 <- fig_resilience_vs_div(plot_here,
+                            which_strain = num_strains,
+                            figure_title = " ") 
+p1 + p2
+
+```
+
+```{r echo = FALSE, eval = FALSE}
 stab_data <- readRDS(here("experiments/0_ss_finding/replication_method/9_strains/data/small_stab_data_1e6_x2x6_factorial.RDS"))
@@
 
-```{r echo = FALSE, eval = TRUE}
+```{r echo = FALSE, eval = FALSE}
 all_stab_results %>%
@@
 
-The figure above shows the effect of response trait diversity (y-axis) on the positions of the tipping points (show by dark lines), which determine the extent of the region of bistability in the oxygen diffusivity gradient.
-The left-most region is anoxic only, the middle is oxic or anoxic depending on historical conditions, and the right-most is oxic only.
-The thick grey vertical lines at -8 and 0 on the x-axis show the extent of the oxygen diffusivity gradient investigated in the simulations.
-
 ## Further thoughts
@@
 
-*Review what the wait time is.*
+## Diversity effects
 
-Wait times of 1e6 hours produce the following results (same as those presented in the main report).
+Recall that the temporal method for finding stable states involves running the simulation for a certain amount of time, termed the "wait time", at a constant level of oxygen diffusivity.
+At the end of that wait time the state of the system is recorded, and then the oxygen diffusivity is slightly increased or decreased, and the system then simulated again for the duration of the wait time.
 
-```{r wait_time_1e6, eval = TRUE}
+The following figures \@ref(fig:div-temp-meth1)-\@ref(fig:div-temp-meth5) show the effects of diversity with long to shorter wait times.
+
+(ref:div-temp-meth1) Effects of diversity with wait time of 1e6 hours (same figure as in main report).
+
+```{r div-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth1)', fig.height=7, fig.width=6, fig.align="center"}
 all_stab <- readRDS(here("experiments/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS"))
@@
 
-```{r wait_time_1e5, eval = TRUE}
+(ref:div-temp-meth2) Effects of diversity with wait time of 1e5 hours.
+
+```{r div-temp-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth2)', fig.height=7, fig.width=6, fig.align="center"}
 
@@
 
-```{r wait_time_1e4, eval = TRUE}
+(ref:div-temp-meth3) Effects of diversity with wait time of 1e4 hours.
+
+```{r div-temp-meth3, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth3)', fig.height=7, fig.width=6, fig.align="center"}
 
@@
 
-```{r wait_time_1e3, eval = TRUE}
+(ref:div-temp-meth4) Effects of diversity with wait time of 1e3 hours.
 
+```{r div-temp-meth4, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth4)', fig.height=7, fig.width=6, fig.align="center"}
 wait_time <- 1e3
@@
 
-```{r wait_time_1e2, eval = TRUE}
+(ref:div-temp-meth5) Effects of diversity with wait time of 1e2 hours.
+
+```{r div-temp-meth5, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth5)', fig.height=7, fig.width=6, fig.align="center"}
 
@@
 
-Wait times of 1e5 produce the following results, which qualitatively and often quantitatively very similar to those for wait times of 1e6.
-There is a notable difference when there is variation in only SB, or CB-SB variation treatments with two or three strains:
+## Example of transient dynamics at 1e6 hours
 
+The results below show the stable states as a function of oxygen diffusivity for a system with intermediate level of diversity in all functional groups, with either 1'000'000 hours simulation time, or 2'000'000 hours.
+This shows that except very close to the values of oxygen diffusitivity at which a state transition occurs, 1'000'000 hours duration of the simulations is sufficient to reach stable state, or very close to it.
+Very close to the transitions, even at 2'000'000 hours, the dynamics are still transient, with high tolerance strains at high density, even though they will eventually be outcompeted by low tolerance (higher growth rate) strains.
+
+Below is Figure 3 from the main manuscript, in which the duration at each oxygen diffusivity value is 1e6:
+
+(ref:ss-temp-meth3) ...
+
+```{r ss-temp-meth3, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth3)', fig.height=8, fig.width=8, fig.align="center"}
+single_1e6 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/single_1e6_result.RDS"))
+only_SB_variable[13,]$ssfind_result[[1]] <- single_1e6
+fig_state_vs_o2diff_sidebyside_dots(only_SB_variable[13,])
+```
+
+For comparison, here are the results with twice the duration at each oxygen diffusivity:
+
+(ref:ss-temp-meth4) ...
+
+```{r ss-temp-meth4, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth4)', fig.height=8, fig.width=8, fig.align="center"}
+single_2e6 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/single_2e6_result.RDS"))
+only_SB_variable[13,]$ssfind_result[[1]] <- single_2e6
+fig_state_vs_o2diff_sidebyside_dots(only_SB_variable[13,])
+```
+
+# SB diversity effects
+
+Wait times of 1e5 (Figure \@ref(fig:div-temp-meth2) and 1e4 (Figure \@ref(fig:div-temp-meth4) produce qualitatively and often quantitatively very similar to those for wait times of 1e6 (Figure \@ref(fig:div-temp-meth1)).
+There is, however, a notable difference when there is variation in only SB, or CB-SB variation treatments with wait time of 1e4 (Figure \@ref(fig:div-temp-meth4)).
 Here, moderate increases in diversity have the same effect as with wait times of 1e6.
+
 However, larger increases in diversity suddenly cause a large reduction in resilience of the anoxic-oxic transition.
-Here is an example of the stable states when diversity is moderate:
+Figure \@ref(fig:ss-temp-meth1) gives an example of the stable states when diversity is moderate -- increases in oxygen diffusivity cause strain replacement in the SB to the more tolerant strains, which then delay the shift.
 
-```{r eval = TRUE}
+(ref:ss-temp-meth1) Stable state of the system with moderate level of diversity in only SB, and no diversity in the other two groups.
+
+```{r ss-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth1)', fig.height=8, fig.width=8, fig.align="center"}
 wait_time <- "1e+04"
-ss_3s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/ss_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))
+ss_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+#stab_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
 
@@
 
-only_SB_variable <- ss_3s %>%
+only_SB_variable <- ss_9s %>%
   filter(
@@
 
-only_SB_variable$SB_var_gmax_s
+#only_SB_variable$SB_var_gmax_s
+
+fig_state_vs_o2diff_sidebyside_dots(only_SB_variable[13,])
+
+#fig_state_vs_o2diff(only_SB_variable[13,])
 ```
 
-```{r eval = TRUE}
-fig_state_vs_o2diff(only_SB_variable[13,])
-```
+Suprisingly, when there is just a little more diversity in the SB then the anoxic to oxic transition happens earlier, i.e. there is large decrease in resilience \@ref(fig:ss-temp-meth2).
 
-Increases in oxygen diffusivity cause strain replacement in the SB to the more tolerant strains, which then delay the shift. When there is just a little more diversity in the SB, this happens:
+(ref:ss-temp-meth2)  Stable state of the system with higher than moderate level of diversity in only SB, and no diversity in the other two groups.
 
-```{r eval = TRUE}
-fig_state_vs_o2diff(only_SB_variable[14,])
+```{r ss-temp-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth2)', fig.height=8, fig.width=8, fig.align="center"}
+fig_state_vs_o2diff_sidebyside_dots(only_SB_variable[14,])
 ```
@@
 
-### Example of transient dynamics at 1'000'000 hours
+(ref:div-stab-multstrain1)  Effects of diversity on positions of tipping points with different numbers of strains.
 
-The results below show the stable states as a function of oxygen diffusivity for a system with intermediate level of diversity in all functional groups, with either 1'000'000 hours simulation time, or 2'000'000 hours.
-This shows that except very close to the values of oxygen diffusitivity at which a state transition occurs, 1'000'000 hours duration of the simulations is sufficient to reach stable state, or very close to it.
-Very close to the transitions, even at 2'000'000 hours, the dynamics are still transient, with high tolerance strains at high density, even though they will eventually be outcompeted by low tolerance (higher growth rate) strains.
+```{r div-stab-multstrain1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-stab-multstrain1)', fig.height=8, fig.width=8, fig.align="center"}
+all_stab <- readRDS(here("experiments/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS"))
 
-Below is Figure 3 from the main manuscript, in which the duration at each oxygen diffusivity value is 1e6:
+which_strains <- c(2, 3, 6, 9)
+which_wait_time<- 1e6
+figure_title <- " "
 
-```{r echo = FALSE, fig.height=10}
-
-single_1e6 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/single_1e6_result.RDS"))
-# sort(unique(ss_9s$CB_var_gmax_s))
-# sort(unique(ss_9s$SB_var_gmax_s))
-# ss_result <- ss_9s %>%
-#   filter(abs(CB_var_gmax_s - 0.028254848) < 0.0001,
-#          abs(SB_var_gmax_s - 0.084764545) < 0.0001,
-#          abs(PB_var_gmax_s - 0.084764545) < 0.0001)
-
-temp <- single_1e6 %>%
-  mutate(a = 10^a_O) %>%
-  # arrange(a) %>%
-  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
-  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
-  # select(-initial_N_CB, -a_O) %>%
-  gather(species, quantity, 2:(ncol(.) - 2)) %>%
-  mutate(
-    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
-    functional_group = case_when(
-      str_detect(species, "CB_") ~ "CB",
-      str_detect(species, "SB_") ~ "SB",
-      str_detect(species, "PB_") ~ "PB"
-    ),
-    log10_quantity = log10(quantity + 1)
-  )
-
-num_strains <- temp %>%
-  group_by(functional_group) %>%
-  summarise(num = length(unique(species))) %>%
-  na.omit()
-
-num_CB_strains <- num_strains$num[num_strains$functional_group == "CB"]
-num_SB_strains <- num_strains$num[num_strains$functional_group == "SB"]
-num_PB_strains <- num_strains$num[num_strains$functional_group == "PB"]
-
-line_width <- 1
-
-p1 <- temp %>%
-  dplyr::filter(functional_group == "CB")  %>%
-  mutate(species = factor(species, levels = unique(species))) %>%
-  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
-  geom_path(lwd = line_width) +
-  ##ylab("log10(quantity [cells])") +
-  ylab("Log(Quantity)") +
-  xlab("Oxygen diffusivity") +
-  scale_colour_manual(values = colfunc_CB(num_CB_strains)) +
-  guides(colour = guide_legend(ncol = 3)) +
-  theme(legend.position="none") +
-  ggtitle("(b) Cyanobacteria")
-#p1# p1
-
-p2 <- temp %>%
-  dplyr::filter(functional_group == "SB")  %>%
-  mutate(species = factor(species, levels = unique(species))) %>%
-  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
-  geom_path(lwd = line_width) +
-  ##ylab("log10(quantity [cells])") +
-  ylab("Log(Quantity)") +
-  xlab("Oxygen diffusivity") +
-  scale_colour_manual(values = colfunc_SB(num_SB_strains)) +
-  guides(colour = guide_legend(ncol = 3)) +
-  theme(legend.position="none") +
-  ggtitle("(c) Sulfate reducing bacteria")
-
-p3 <- temp %>%
-  dplyr::filter(functional_group == "PB")  %>%
-  mutate(species = factor(species, levels = unique(species))) %>%
-  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
-  geom_path(lwd = line_width) +
-  ##ylab("log10(quantity [cells])") +
-  ylab("Log(Quantity)") +
-  xlab("Oxygen diffusivity") +
-  scale_colour_manual(values = colfunc_PB(num_PB_strains)) +
-  guides(colour = guide_legend(ncol = 3)) +
-  theme(legend.position="none") +
-  ggtitle("(d) Phototrophic sulfur bacteria")
-
-p4 <- temp %>%
-  dplyr::filter(var_type == "Substrate", species == "O") %>%
-  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
-  geom_path(lwd = line_width) +
-  ##ylab("log10(quantity [cells])") +
-  ylab("Log(Quantity)") +
-  xlab("Oxygen diffusivity") +
-  theme(legend.position="none") +
-  ggtitle("(e) Oxygen concentration")
-
-p5 <- temp %>%
-  dplyr::filter(var_type == "Substrate", species == "SR") %>%
-  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
-  geom_path(lwd = line_width, col = 6) +
-  ##ylab("log10(quantity [cells])") +
-  ylab("Log(Quantity)") +
-  xlab("Oxygen diffusivity") +
-  theme(legend.position="none") +
-  ggtitle("(f) Sulfide concentration")
-
-patchwork <- p1 / p2 / p3 / p4 / p5
-patchwork
-```
-
-For comparison, here are the results with twice the duration at each oxygen diffusivity:
-
-```{r echo = FALSE, fig.height=10, eval = TRUE}
-
-single_2e6 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/single_2e6_result.RDS"))
-# sort(unique(ss_9s$CB_var_gmax_s))
-# sort(unique(ss_9s$SB_var_gmax_s))
-# ss_result <- ss_9s %>%
-#   filter(abs(CB_var_gmax_s - 0.028254848) < 0.0001,
-#          abs(SB_var_gmax_s - 0.084764545) < 0.0001,
-#          abs(PB_var_gmax_s - 0.084764545) < 0.0001)
-
-temp <- single_2e6 %>%
-  mutate(a = 10^a_O) %>%
-  # arrange(a) %>%
-  # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
-  #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
-  # select(-initial_N_CB, -a_O) %>%
-  gather(species, quantity, 2:(ncol(.) - 2)) %>%
-  mutate(
-    var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
-    functional_group = case_when(
-      str_detect(species, "CB_") ~ "CB",
-      str_detect(species, "SB_") ~ "SB",
-      str_detect(species, "PB_") ~ "PB"
-    ),
-    log10_quantity = log10(quantity + 1)
-  )
-
-num_strains <- temp %>%
-  group_by(functional_group) %>%
-  summarise(num = length(unique(species))) %>%
-  na.omit()
-
-num_CB_strains <- num_strains$num[num_strains$functional_group == "CB"]
-num_SB_strains <- num_strains$num[num_strains$functional_group == "SB"]
-num_PB_strains <- num_strains$num[num_strains$functional_group == "PB"]
-
-line_width <- 1
-
-p1 <- temp %>%
-  dplyr::filter(functional_group == "CB")  %>%
-  mutate(species = factor(species, levels = unique(species))) %>%
-  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
-  geom_path(lwd = line_width) +
-  ##ylab("log10(quantity [cells])") +
-  ylab("Log(Quantity)") +
-  xlab("Oxygen diffusivity") +
-  scale_colour_manual(values = colfunc_CB(num_CB_strains)) +
-  guides(colour = guide_legend(ncol = 3)) +
-  theme(legend.position="none") +
-  ggtitle("(b) Cyanobacteria")
-#p1# p1
-
-p2 <- temp %>%
-  dplyr::filter(functional_group == "SB")  %>%
-  mutate(species = factor(species, levels = unique(species))) %>%
-  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
-  geom_path(lwd = line_width) +
-  ##ylab("log10(quantity [cells])") +
-  ylab("Log(Quantity)") +
-  xlab("Oxygen diffusivity") +
-  scale_colour_manual(values = colfunc_SB(num_SB_strains)) +
-  guides(colour = guide_legend(ncol = 3)) +
-  theme(legend.position="none") +
-  ggtitle("(c) Sulfate reducing bacteria")
-
-p3 <- temp %>%
-  dplyr::filter(functional_group == "PB")  %>%
-  mutate(species = factor(species, levels = unique(species))) %>%
-  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
-  geom_path(lwd = line_width) +
-  ##ylab("log10(quantity [cells])") +
-  ylab("Log(Quantity)") +
-  xlab("Oxygen diffusivity") +
-  scale_colour_manual(values = colfunc_PB(num_PB_strains)) +
-  guides(colour = guide_legend(ncol = 3)) +
-  theme(legend.position="none") +
-  ggtitle("(d) Phototrophic sulfur bacteria")
-
-p4 <- temp %>%
-  dplyr::filter(var_type == "Substrate", species == "O") %>%
-  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
-  geom_path(lwd = line_width) +
-  ##ylab("log10(quantity [cells])") +
-  ylab("Log(Quantity)") +
-  xlab("Oxygen diffusivity") +
-  theme(legend.position="none") +
-  ggtitle("(e) Oxygen concentration")
-
-p5 <- temp %>%
-  dplyr::filter(var_type == "Substrate", species == "SR") %>%
-  ggplot(aes(x = log10(a), y = log10_quantity, col = species)) +
-  geom_path(lwd = line_width, col = 6) +
-  ##ylab("log10(quantity [cells])") +
-  ylab("Log(Quantity)") +
-  xlab("Oxygen diffusivity") +
-  theme(legend.position="none") +
-  ggtitle("(f) Sulfide concentration")
-
-patchwork <- p1 / p2 / p3 / p4 / p5
-patchwork
+fig_div_vs_o2diff_multistrain(all_stab, which_strains,
+                              which_wait_time, figure_title)
 ```

### 2022-02-20 experiments/0_ss_finding/replication_method/run_experiment.R

@@ -6,29 +6,29 @@ source(here::here("R/various_useful_functions.r"))
 max_cores <- benchmarkme::get_cpu()$no_of_cores-2
 options(mc.cores = max_cores)
 
-sim_length <- 1e4
-event_def <- "event_definition_2"
+sim_length <- 1e6
+event_def <- "event_definition_2" ## not relevant, since no events occur
 
 ## Run for 2, 3, 6, and 9 strains
-for(num_strains in c(2, 3, 6, 9)) {
+#for(num_strains in c(2, 3, 6, 9)) {
   
-  num_strains <- 2 ## for testing
+  num_strains <- 9 ## for testing
   
   ## Run the code that sets up the experiment
   source(here::here("experiments/0_ss_finding/replication_method/setup_experiment.R"))
   
   ss_data_filename <- here("experiments/0_ss_finding/replication_method/data",
-                           paste0("ss_data_",
+                           paste0("test_ss_data_",
                                   num_strains, "strains_sim_length",
                                   formatC(sim_length, format = "e", digits = 0),
                                   "_", event_def,".RDS"))
   stab_data_filename <- here("experiments/0_ss_finding/replication_method/data",
-                             paste0("stab_data_",
+                             paste0("test_stab_data_",
                                     num_strains, "strains_sim_length",
                                     formatC(sim_length, format = "e", digits = 0),
                                     "_", event_def,".RDS"))
 
-  #var_expt <- var_expt[1:10,]
+  var_expt <- var_expt[1,]
   
   system.time(
     run_replication_ssfind_experiment(parameter, var_expt) %>%

### 2022-02-20 experiments/0_ss_finding/replication_method/setup_experiment.R

@@ -78,7 +78,7 @@ minimum_abundances <- rep(1, 3)
 names(minimum_abundances) <- c("CB", "PB", "SB")
 
 grid_num_a <- 300 #usually 1000 ## number of a_0 values
-grid_num_a <- 10 ## FOR TEST
+grid_num_a <- 3 ## FOR TEST
 a_Os <- 10^seq(-8, -0, length=grid_num_a) ## sequence of a_0 values
 grid_num_N <- 2 ## number of N values
 initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
@@ -93,7 +93,7 @@ ss_expt <- expand.grid(N_CB = initial_CBs,
 parameter <- new_replication_ssfind_parameter(
   dynamic_model = parameter$dynamic_model,
   event_definition = eval(parse(text = event_def)),
-  event_interval = 1000,
+  event_interval = sim_length,
   noise_sigma = parameter$noise_sigma,
   minimum_abundances = minimum_abundances,
   sim_duration = sim_length,

### 2022-02-20 experiments/0_ss_finding/temporal_method/run_single_sim.R

@@ -8,7 +8,7 @@ rm(list = ls())
 
 microxanox_release <- "0.4.9"
 library(microxanox)
-source(here::here("experiments/0_ss_finding/temporal_method/check_microxanox_v0.4.9_or_higher.R"))
+source(here::here("experiments/0_ss_finding/temporal_method/check_microxanox_version.R"))
 library(tidyverse)
 library(patchwork)
 library(here)
@@ -17,7 +17,7 @@ zero <- 0 ## don't change
 unity <- 1 ## don't change!!!
 
 ## Re-run sim selected in figure 3 for longer
-ss_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/9_strain_SS_data_1e6.RDS"))
+ss_9s <- readRDS(here("experiments/0_ss_finding/temporal_method/data/stab_data_9strains_waittime1e+06_event_definition_2.RDS"))
 sort(unique(ss_9s$CB_var_gmax_s))
 sort(unique(ss_9s$SB_var_gmax_s))
 ss_result <- ss_9s %>%
@@ -38,7 +38,7 @@ parameter$sim_duration <- wait_time * length(parameter$log10a_series)
 parameter$sim_sample_interval <- wait_time
 parameter$sim_duration
 system.time(
-  result_1e6 <- run_temporal_ssfind_method(parameter)
+  result_1e6 <- run_temporal_ssfind(parameter)
 )
 saveRDS(result_1e6, here("experiments/0_ss_finding/temporal_method/data/single_1e6_result.RDS"))
 
@@ -47,6 +47,6 @@ wait_time <-  2e6
 parameter$sim_duration <- wait_time * length(parameter$log10a_series)
 parameter$sim_sample_interval <- wait_time
 parameter$sim_duration
-result_2e6 <- run_temporal_ssfind_method(parameter)
+result_2e6 <- run_temporal_ssfind(parameter)
 
 saveRDS(result_2e6, here("experiments/0_ss_finding/temporal_method/data/single_2e6_result.RDS"))

### 2022-02-21 experiments/2_supplement/supplement.Rmd
mostly cleaning up

@@
 title: Supplementary Content
-subtitle: Functional diversity ... Predictions of a model of an oxic-anoxic microbial ecosystem 
+subtitle: ??????Insert ms title???????
 author: "Owen L Petchey, Rainer Krug, Marcel Suleiman, Romana Limberger, ???others???"
@@
 
-This document contains the Supporting Content for the report *?????????????*.
+This document contains the Supplementary Content for the report *?????????????*.
 
@@
 
-In the following graph, the solid (down) line refers to the stable state when cyanobacteria begin at high abundance (favouring the oxic state).
+(ref:repl-meth2) Stable states found with the *replication* method.
+The solid (down) line refers to the stable state when cyanobacteria begin at high abundance (favouring the oxic state).
 The dashed up line refers to when their initial abundnace is low (favouring the anoxic state).
-Stable states found with the replication method.
 Please note: i) that near vertical lines indicate the position of a tipping point and hence the system cannot exist on point of that part of the line; ii) the separatrix (the unstable equilibrium) is not shown.
-
-(ref:repl-meth2) Figure caption.
 
@@
                 save_image_file = FALSE)
+
+## Would like to here use the function fig_state_vs_o2diff_sidebyside_dots() (as is used in the next chunk) but there is some incompatibility as the function was written for results from the temporal method, and does not work for those from the replication method.
+Rainer, could you please see if you can make a workaround?
+
 ```
@@
 
-(ref:temp-meth2) ...
+(ref:temp-meth2) Stable states found with the *temporal* method. All other aspects are the same as in Figure \@ref(fig:repl-meth1).
 
 ```{r temp-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:temp-meth2)', fig.height=8, fig.width=8, fig.align="center"}
-plot_ss_result3(temp_meth, 1)
+fig_state_vs_o2diff_sidebyside_dots(temp_meth[1,])
 ```
@@
 
-Stable states of the two methods overlaid, the temporal method with a dashed line, and the replication method with a solid line.
-
-(ref:both-meth1) ...
+(ref:both-meth1) Stable states of the two methods overlaid, the temporal method with a dashed line, and the replication method with a solid line.
 
@@
 
-The replication method shows the same effects of functional diversity as those revealed by the temporal method:
+The replication method shows the same effects of functional diversity as those revealed by the temporal method (Figure \@ref(fig:div-repl-meth1). Namely
 
--   Introducing functional diversity in all three functional groups increases the region of bistability relative to when there is no diversity within all functional groups).
+-   Introducing functional diversity in all three functional groups increases the resilience of both the anoxic and oxic state.
 -   Introducing functional diversity in only the cyanobacteria function group delays (with respect to the oxygen diffusivity it occurs at) the switch to the anoxic state as oxygen diffusivity is reduced, but has no effect on the oxygen diffusivity at which the anoxic to oxic transition occurs .
@@
 
-These results are shown in the figure below, which shows results of the replication method.
-
-(ref:div-repl-meth1) The figure shows the effect of response trait diversity (y-axis) on the positions of the tipping points (show by dark lines), which determine the extent of the region of bistability in the oxygen diffusivity gradient.
+(ref:div-repl-meth1) **Left column of panels**: the effect of response trait diversity (y-axis) on the positions of the tipping points (anoxic to oxic in blue, oxic to anoxic in red), which determine the extent of the region of bistability (green shaded region) in the oxygen diffusivity gradient.
 The left-most region is anoxic only, the middle is oxic or anoxic depending on historical conditions, and the right-most is oxic only.
 The thick grey vertical lines at -8 and 0 on the x-axis show the extent of the oxygen diffusivity gradient investigated in the simulations.
+**Right column of panels**: The effect of diversity on resilience, with positive values on the y-axis indicating that diversity has increased resilience, i.e.
+delayed the shift to the other state.
 
@@
 p1 + p2
-
-```
-
-```{r echo = FALSE, eval = FALSE}
-stab_data <- readRDS(here("experiments/0_ss_finding/replication_method/9_strains/data/small_stab_data_1e6_x2x6_factorial.RDS"))
-
-all_stab <- stab_data
-
-#all_stab <- stab_9s
-
-CB_vars <- unique(all_stab$CB_var_gmax_s)
-SB_vars <- unique(all_stab$SB_var_gmax_s)
-
-CB_all_stab <- all_stab %>%
-  filter(SB_var_gmax_s == 0) %>%
-  mutate(var_treat = "CB",
-         var_gmax = CB_var_gmax_s)
-
-SBPB_all_stab <- all_stab %>%
-  filter(CB_var_gmax_s == 0) %>%
-  mutate(var_treat = "SB-PB",
-         var_gmax = SB_var_gmax_s)
-
-for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
-                   SB_var_gmax_s = sort(SB_vars))
-CBSBPB_all_stab <- all_stab %>%
-  right_join(for_join) %>%
-  mutate(var_treat = "CB-SB-PB",
-         var_gmax = CB_var_gmax_s)
-
-all_stab_results <- CB_all_stab %>%
-  bind_rows(SBPB_all_stab) %>%
-  #  bind_rows(results3) %>%
-  # bind_rows(results4) %>%
-  bind_rows(CBSBPB_all_stab)
-
-all_stab_results <- all_stab_results %>%
-  mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB-PB", "CB-SB-PB")))
-
-```
-
-```{r echo = FALSE, eval = FALSE}
-all_stab_results %>%
-  #filter(var_treat == "CB") %>%
-  filter(Species == "SR") %>%
-  ggplot(aes(x = var_gmax)) +
-  #ggplot(aes(x = var_gmax,
-  #           col = as.factor(num_strains))) +
-  geom_line(aes(y = hyst_min_log), lwd = 2, alpha = 0.8) +
-  geom_line(aes(y = hyst_max_log), lwd = 2, alpha = 0.8) +
-  facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
-  labs(fill = "Variation in\nonly these\nfunctional groups") +
-  coord_flip() +
-  #guides(col = guide_legend(title="Number of strains")) +
-  theme(
-    legend.position="top"
-    #strip.background = element_blank(),
-    #strip.text.x = element_blank()
-  ) +
-  geom_hline(yintercept = c(-8, 0), col = "grey", lwd = 3)
-
-#ggsave(here("experiments/1_figures_main_ms/figure_5.pdf"),
-#       width = 5, height = 4)
 
@@
 
-(ref:div-temp-meth1) Effects of diversity with wait time of 1e6 hours (same figure as in main report).
+(ref:div-temp-meth1) Effects of diversity with wait time of 1e6 hours (same figure as in main report). (All else as in (Figure \@ref(fig:div-repl-meth1)).
 
@@
 
-(ref:div-temp-meth2) Effects of diversity with wait time of 1e5 hours.
+(ref:div-temp-meth2) Effects of diversity with wait time of 1e5 hours. (All else as in (Figure \@ref(fig:div-repl-meth1)).
 
@@
 
-(ref:div-temp-meth3) Effects of diversity with wait time of 1e4 hours.
+(ref:div-temp-meth3) Effects of diversity with wait time of 1e4 hours. (All else as in (Figure \@ref(fig:div-repl-meth1)).
 
@@
 
-(ref:div-temp-meth4) Effects of diversity with wait time of 1e3 hours.
+(ref:div-temp-meth4) Effects of diversity with wait time of 1e3 hours. (All else as in Figure \@ref(fig:div-repl-meth1)).
 
@@
 
-(ref:div-temp-meth5) Effects of diversity with wait time of 1e2 hours.
+(ref:div-temp-meth5) Effects of diversity with wait time of 1e2 hours. (All else as in Figure \@ref(fig:div-repl-meth1)).
 
@@
 
-The results below show the stable states as a function of oxygen diffusivity for a system with intermediate level of diversity in all functional groups, with either 1'000'000 hours simulation time, or 2'000'000 hours.
+The results below show the stable states as a function of oxygen diffusivity for a system with intermediate level of diversity in all functional groups, with either 1'000'000 hours at each oxygen diffusivity level (Figure \@ref(fig:ss-temp-meth3)), or 2'000'000 hours (Figure \@ref(fig:ss-temp-meth4)).
 This shows that except very close to the values of oxygen diffusitivity at which a state transition occurs, 1'000'000 hours duration of the simulations is sufficient to reach stable state, or very close to it.
@@
 
-Below is Figure 3 from the main manuscript, in which the duration at each oxygen diffusivity value is 1e6:
-
-(ref:ss-temp-meth3) ...
+(ref:ss-temp-meth3) Stable states found with the temporal method with duration at each oxygen diffusivity value of 1e6 hours.
+The right column of panels refers to the stable state when oxygen diffusivity is at first high (favouring the oxic state).
+The left column refers to when oxygen diffusivity is at first low (favouring the anoxic state).
+Points (which sometimes are so close as to appear as thick lines) show the stable state at the end of each period of constant oxygen diffusivity.
+Thin lines are for visualisation only, and join the points.
+Grey arrows show the oxygen diffusivity at which the system flips, and the direction of the flip.
+The length of the grey arrows is without meaning.
 
@@
 
-For comparison, here are the results with twice the duration at each oxygen diffusivity:
-
-(ref:ss-temp-meth4) ...
+(ref:ss-temp-meth4) Stable states found with the temporal method with duration at each oxygen diffusivity value of 2e6 hours. All other aspects are as in Figure \@ref(fig:ss-temp-meth3).
 
@@
 Figure \@ref(fig:ss-temp-meth1) gives an example of the stable states when diversity is moderate -- increases in oxygen diffusivity cause strain replacement in the SB to the more tolerant strains, which then delay the shift.
+Suprisingly, when there is just a little more diversity in the SB then the anoxic to oxic transition happens earlier, i.e.
+there is large decrease in resilience \@ref(fig:ss-temp-meth2).
 
-(ref:ss-temp-meth1) Stable state of the system with moderate level of diversity in only SB, and no diversity in the other two groups.
+(ref:ss-temp-meth1) Stable state of the system with moderate level of diversity in only SB, and no diversity in the other two groups. All other aspects are as in Figure \@ref(fig:ss-temp-meth3).
 
@@
 
-Suprisingly, when there is just a little more diversity in the SB then the anoxic to oxic transition happens earlier, i.e. there is large decrease in resilience \@ref(fig:ss-temp-meth2).
-
 (ref:ss-temp-meth2)  Stable state of the system with higher than moderate level of diversity in only SB, and no diversity in the other two groups.
+All other aspects are as in Figure \@ref(fig:ss-temp-meth1).
 
@@
 
-(ref:div-stab-multstrain1)  Effects of diversity on positions of tipping points with different numbers of strains.
+# Effect of number of strains
+
+(ref:div-stab-multstrain1)  Effects of number of strains and of diversity among strains.
 

### 2022-02-21 experiments/1_figures_main_ms/ms_figure_functions.R
Prtly fix for #21

@@ -451,25 +451,50 @@ fig_state_vs_o2diff_sidebyside <- function(ss_result){
 }
 
 fig_state_vs_o2diff_sidebyside_dots <- function(ss_result){
+
+  is_repl <- "ss_by_a_N_result" %in% names(ss_result)
+
+  if (is_repl) {
+    ss_result$ssfind_result <- ss_result$ss_res
+  }
   
   temp1 <- ss_result %>%
     mutate(ssfind_result = list(get_total_bio(ssfind_result)))
-  stab_measures <- get_stability_measures(temp1$ssfind_result[[1]],
-                                          threshold_diff_log10scale = 3) %>%
+
+  if (is_repl){
+    temp1 <- microxanox:::get_stability_measures.replication_ssfind_result(
+      temp1$ssfind_result[[1]],
+      threshold_diff_log10scale = 3
+    )
+  } else {
+    temp1 <- microxanox:::get_stability_measures.temporal_ssfind_result(
+      temp1$ssfind_result[[1]],
+      threshold_diff_log10scale = 3
+    )
+  }
+ 
+  stab_measures <- temp1 %>% 
     filter(Species == "SB_tot") %>%
     select(down=hyst_min_log, up=hyst_max_log) %>%
     pivot_longer(names_to = "direction", values_to = "aO_flip", 1:2) %>%
     mutate(y_start = c(2.5, 7.5),
            y_end = c(7.5, 2.5))
+  
   rm(temp1)
 
+  if (is_repl) {
+    gathcols <- 1:(31)
+  } else {
+    gathcols <- 2:(ncol(ss_result$ssfind_result[[1]]) - 2)
+  }
+  browser()
   temp <- ss_result$ssfind_result[[1]] %>%
     mutate(a = 10^a_O) %>%
     # arrange(a) %>%
     # mutate(direction = rep(c("up", "down"), nrow(ss_result)/2)) %>%
     #mutate(direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
     # select(-initial_N_CB, -a_O) %>%
-    gather(species, quantity, 2:(ncol(.) - 2)) %>%
+    gather(species, quantity, gathcols) %>%
     mutate(
       var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
       functional_group = case_when(
@@ -492,7 +517,7 @@ fig_state_vs_o2diff_sidebyside_dots <- function(ss_result){
   line_width <- 0.2
[…]

### 2022-02-21 experiments/2_supplement/supplement.Rmd
Prtly fix for #21
fixed supplement figure issue

@@
 The difference in results occurs because, as mentioned above, the initial conditions differ between the two approaches.
-For example, in the temporal method, the oxygen concentration in the anoxic state is lower than the initial oxygen concentration in the replication approach, and **Owen guesses that** the sulfide concentration is higher **check that last statement**.
 
@@
 (ref:repl-meth2) Stable states found with the *replication* method.
-The solid (down) line refers to the stable state when cyanobacteria begin at high abundance (favouring the oxic state).
-The dashed up line refers to when their initial abundnace is low (favouring the anoxic state).
-Please note: i) that near vertical lines indicate the position of a tipping point and hence the system cannot exist on point of that part of the line; ii) the separatrix (the unstable equilibrium) is not shown.
+The right column of panels refers to the stable state when oxygen diffusivity is at first high (favouring the oxic state).
+The left column refers to when oxygen diffusivity is at first low (favouring the anoxic state).
+Points (which sometimes are so close as to appear as thick lines) show the stable state at the end of each period of constant oxygen diffusivity.
+Thin lines are for visualisation only, and join the points.
+Grey arrows show the oxygen diffusivity at which the system flips, and the direction of the flip.
+The length of the grey arrows is without meaning.
 
 ```{r repl-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:repl-meth2)', fig.height=8, fig.width=8, fig.align="center"}
-## To be completed.
-plot_ss_result1(repl_meth,
-                result_index = 1,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-
-## Would like to here use the function fig_state_vs_o2diff_sidebyside_dots() (as is used in the next chunk) but there is some incompatibility as the function was written for results from the temporal method, and does not work for those from the replication method.
-Rainer, could you please see if you can make a workaround?
-
+fig_state_vs_o2diff_sidebyside_dots(repl_meth[1,])
 ```
@@
 
-(ref:temp-meth2) Stable states found with the *temporal* method. All other aspects are the same as in Figure \@ref(fig:repl-meth1).
+(ref:temp-meth2) Stable states found with the *temporal* method. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
 
@@
 single_1e6 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/single_1e6_result.RDS"))
-only_SB_variable[13,]$ssfind_result[[1]] <- single_1e6
-fig_state_vs_o2diff_sidebyside_dots(only_SB_variable[13,])
+temp_meth[1,]$ssfind_result[[1]] <- single_1e6
+fig_state_vs_o2diff_sidebyside_dots(temp_meth[1,])
 ```
@@
 single_2e6 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/single_2e6_result.RDS"))
-only_SB_variable[13,]$ssfind_result[[1]] <- single_2e6
-fig_state_vs_o2diff_sidebyside_dots(only_SB_variable[13,])
+temp_meth[1,]$ssfind_result[[1]] <- single_2e6
+fig_state_vs_o2diff_sidebyside_dots(temp_meth[1,])
 ```

### 2022-02-21 experiments/2_supplement/supplement.Rmd
update supplement

@@
 
+## General method
+
 We now discuss two approaches for finding how the stable state of the system varies along the gradient of oxygen diffusivity when there exists the possibility of multiple stable states.
@@
                 xlims = c(-8, 0))
+```
+
+## Effect of abundance change event
+
+**To be completed... waiting for data**
+
+As mentioned in the main report, to avoid very low strain densities, we added 1 unit of density to every biological state variable every 1,000 hours (a slightly different method produced the same results, see the Supplementary Information for details).
+We also test the effect of making an abundance floor of 1 unit that was implemented every 1,000 hours.
+I.e.
+any adundances that were lower than 1 unit were set to 1 unit, every 1,000 hours.
+As shown below, the results with this floor abundance are the same as when 1 unit is added.
+
+(ref:div-temp-eventdef1) **Left column of panels**: the effect of response trait diversity (y-axis) on the positions of the tipping points (anoxic to oxic in blue, oxic to anoxic in red), which determine the extent of the region of bistability (green shaded region) in the oxygen diffusivity gradient.
+The left-most region is anoxic only, the middle is oxic or anoxic depending on historical conditions, and the right-most is oxic only.
+The thick grey vertical lines at -8 and 0 on the x-axis show the extent of the oxygen diffusivity gradient investigated in the simulations.
+**Right column of panels**: The effect of diversity on resilience, with positive values on the y-axis indicating that diversity has increased resilience, i.e.
+delayed the shift to the other state.
+
+```{r div-temp-eventdef1, eval = FALSE, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-eventdef1)', fig.height=8, fig.width=8, fig.align="center"}
+all_stab <- readRDS(here("experiments/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method_eventdef1.RDS"))
+
+sim_length <- 1e6
+num_strains <- 9
+plot_here <- all_stab %>%
+  filter(simlength == sim_length)
+p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
+                                     which_strain = num_strains,
+                                     figure_title = paste0(sim_length,
+                                                           " sim. length,\n",
+                                                           num_strains,
+                                                           " strains"))
+p2 <- fig_resilience_vs_div(plot_here,
+                            which_strain = num_strains,
+                            figure_title = " ") 
+p1 + p2
+
 ```

### 2022-02-22 experiments/2_supplement/supplement.Rmd
#22 `2_supplement`

@@
 ```{r repl_meth1, echo=FALSE, eval = TRUE}
-repl_meth <- readRDS(here("experiments/0_ss_finding/replication_method/data/ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
-temp_meth <- readRDS(here("experiments/0_ss_finding/temporal_method/data/ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
+repl_meth <- readRDS(here("data/0_ss_finding/replication_method/ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
+temp_meth <- readRDS(here("data/0_ss_finding/temporal_method/ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
 ```
@@
 ```{r div-temp-eventdef1, eval = FALSE, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-eventdef1)', fig.height=8, fig.width=8, fig.align="center"}
-all_stab <- readRDS(here("experiments/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method_eventdef1.RDS"))
+all_stab <- readRDS(here("data/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method_eventdef1.RDS"))
 
@@
 ```{r div-repl-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-repl-meth1)', fig.height=8, fig.width=8, fig.align="center"}
-all_stab <- readRDS(here("experiments/0_ss_finding/replication_method/processed_data/stab_data_replication_method.RDS"))
+all_stab <- readRDS(here("data/0_ss_finding/replication_method/processed_data/stab_data_replication_method.RDS"))
 
@@
 ```{r div-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth1)', fig.height=7, fig.width=6, fig.align="center"}
-all_stab <- readRDS(here("experiments/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS"))
+all_stab <- readRDS(here("data/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS"))
 
@@
 ```{r ss-temp-meth3, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth3)', fig.height=8, fig.width=8, fig.align="center"}
-single_1e6 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/single_1e6_result.RDS"))
+single_1e6 <- readRDS(here("data/0_ss_finding/temporal_method/single_1e6_result.RDS"))
 temp_meth[1,]$ssfind_result[[1]] <- single_1e6
@@
 ```{r ss-temp-meth4, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth4)', fig.height=8, fig.width=8, fig.align="center"}
-single_2e6 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/single_2e6_result.RDS"))
+single_2e6 <- readRDS(here("data/0_ss_finding/temporal_method/single_2e6_result.RDS"))
 temp_meth[1,]$ssfind_result[[1]] <- single_2e6
@@
 wait_time <- "1e+04"
-ss_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
-#stab_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+ss_9s <- readRDS(here(paste0("data/0_ss_finding/temporal_method/ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+#stab_9s <- readRDS(here(paste0("data/0_ss_finding/temporal_method/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
 
@@
 ```{r div-stab-multstrain1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-stab-multstrain1)', fig.height=8, fig.width=8, fig.align="center"}
-all_stab <- readRDS(here("experiments/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS"))
+all_stab <- readRDS(here("data/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS"))
 

### 2022-02-26 experiments/2_supplement/supplement.Rmd
PB diversity puzzle progress

@@
 
+# PB diversity effects
+
+```{r echo = FALSE}
+ss_9s <- readRDS(here("data/0_ss_finding/temporal_method/ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
+only_PB_variable <- ss_9s %>%
+  filter(
+    abs(CB_var_gmax_s) < 0.0001,
+    abs(SB_var_gmax_s) < 0.0001
+  )
+only_PB_variable <- only_PB_variable[order(only_PB_variable$PB_var_gmax_s), ]
+
+only_PB_stab <- readRDS(here("data/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS")) %>%
+  filter(
+    num_strains == 9,
+    waittime == 1e6,
+    var_treat == "PB",
+    Species == "SB_tot"
+  )
+only_PB_stab <- only_PB_stab[order(only_PB_stab$PB_var_gmax_s), ]
+
+sim1 <- 2
+sim2 <- 10
+
+aO_flip_sim1 <- only_PB_stab[sim1,"hyst_max_log"]
+aO_flip_sim2 <- only_PB_stab[sim2,"hyst_max_log"]
+
+```
+
+Increases in the diversity within the PB functional group leads to lower resilience of the anoxic state (Figure \@ref(fig:div-temp-meth1), Panel PB, blue line).
+For example, a small amount of variation in only the PB functional group, and no variation in other functional groups, results in transition from anoxic to oxic at approximately $log_{10}$(oxygen diffusivity) = `r round(aO_flip_sim1, 2)` (Figure \@ref(fig:pbdiv-only-1)).
+Whereas, a moderate amount of variation in only the PB functional group, and no variation in other functional groups, results in transition from anoxic to oxic at approximately $log_{10}$(oxygen diffusivity) = `r round(aO_flip_sim2, 2)` (Figure \@ref(fig:pbdiv-only-2)).
+
+(ref:pbdiv-only-1) Right-hand panels show the transition from anoxic to oxic state when oxygen diffusivity increases.
+The results here are for a low amount of variation in only the PB functional group.
+The transition from anoxic to oxic occurs at approximately $log_{10}$(oxygen diffusivity) = `r round(aO_flip_sim1, 2)`.
+All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+
+```{r pbdiv-only-1, echo = FALSE,  include=TRUE, fig.cap='(ref:pbdiv-only-1)', fig.height=8, fig.width=8, fig.align="center"}
+fig_state_vs_o2diff_sidebyside_dots(only_PB_variable[sim1,])
+```
+
+(ref:pbdiv-only-2) Right-hand panels show the transition from anoxic to oxic state when oxygen diffusivity increases.
+The results here are for a moderate amount of variation in only the PB functional group.
+The transition from anoxic to oxic occurs at approximately $log_{10}$(oxygen diffusivity) = `r round(aO_flip_sim2, 2)`.
+All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+
+```{r pbdiv-only-2, echo = FALSE,  include=TRUE, fig.cap='(ref:pbdiv-only-2)', fig.height=8, fig.width=8, fig.align="center"}
+fig_state_vs_o2diff_sidebyside_dots(only_PB_variable[sim2,])
+```
+
+This result is different to the effect of diversity within the CB and SB functional groups, which both cause increases in resilience (Figure \@ref(fig:div-temp-meth1)).
+Why does diversity in the PB functional group reduce the resilience of the state it dominates?
+
+The phototrophic sulfur bacteria (PB) in the model ecosystem produce oxidised sulfur compounds (SO), and consume reduced sulfur compounds (SR).
+Since SR inhibits the cyanobacteria, PB can have a positive effect on CB via their consumption of SR.
+Hence, high growth rates of PB will have a positive effect on on CB, and therefore favour the oxic state.
+We would expect to see that higher diversity of PB is associated with lower SR and higher SO before the transition.
+
+Another pathway by which higher PB growth rate can favour the oxic state is by PB inhibiting PB and SB (and thus favouring CB).
+This effect occurs because PB consumes SR, making less SR available for abiotic oxidation (SR + O -> SO).
+Reduced abiotic oxidation leaves greater amounts of O in the environment, and O inhibits.
+We would expect to see that higher diversity of PB is associated with higher O before the transition.
+
+There is, however, at least one pathway by which PB can favour the anoxic state. PB produces SO which is consumed by SB, and SB produce SR, which inhibits CB.
+
+Looking at the strain replacement that occurs across the oxygen diffusivity gradient, we see that as oxygen diffusivity increases, then the more oxygen tolerant strains of PB replace the less tolerant ones.
+This is because these more tolerant strains have higher realised growth rates under the prevailing environmental conditions (even though they have lower maximum growth rate than lower tolerance strains).
+Having an even more tolerant strain available (which is what happens when there is greater PB diversity) gives the opportunity for even higher realised growth rates, which via the effect pathways mentioned above, can favour the oxic state.
+
+The expected effects of having a more PB tolerant strain (because there is higher PB diversity) is shown in Figure \@ref(fig:pbdiv-only-3)).
+As the transition is approached, higher PB diversity leads to higher oxygen concentration, higher SO concentration, and lower SR concentration, than in a simulation with lower PB diversity.
+All these differences in substrate concentrations are in the direction of favouring the oxic state, and thus the system transitions earlier to the oxic state.
+
+(ref:pbdiv-only-3) Concentrations of three substrates (one in each panel) in a low PB diversity simulation (x-axis) versus concentration in a high PB diversity simuation (y-axis).
+Only a small range of oxygen diffusivity is show, and result only shown for increasing oxygen diffusivity.
+The black line is the 1:1 line.
+
+```{r pbdiv-only-3, echo = FALSE,  include=TRUE, fig.cap='(ref:pbdiv-only-3)', fig.height=5, fig.width=8, fig.align="center"}
+
+stab_9s <- readRDS(here("data/0_ss_finding/temporal_method/ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
+
+ss1 <- only_PB_variable[sim1,]
+ss2 <- only_PB_variable[sim2,]
+
+dd1 <- ss1$ssfind_result[[1]] %>%
+  pivot_longer(names_to = "State_variable", values_to = "Quantity_sim1", 2:32)
+dd2 <- ss2$ssfind_result[[1]] %>%
+  pivot_longer(names_to = "State_variable", values_to = "Quantity_sim2", 2:32)
+dd <- full_join(dd1, dd2)
+rm(ss1, ss2, dd1, dd2)
+
+labs <- seq(-3.5, -3.3, by=0.05)
+
+dd %>%
+  filter(State_variable %in% c("O", "SR", "SO"),
+         direction == "up", 
+         a_O < as.numeric(aO_flip_sim2),
+         a_O > -3.5) %>%
+  ggplot(aes(x = log10(Quantity_sim1),
+                 y = log10(Quantity_sim2),
+                 col = a_O )) +
+  geom_point(lwd = 3) +
+  geom_path() +
+  scale_color_gradient(low = "yellow", high = "red", na.value = NA,
+                       breaks = labs,
+                       labels = labs) +
+  #coord_trans(x = "log10", y = "log10") +
+  facet_wrap( ~ State_variable, scales = "free") +
+  geom_abline(intercept = 0, slope = 1) +
+  xlab("Log10(Concentration)\nLow PB diversity") +
+  ylab("Log10(Concentration)\nHigh PB diversity") +
+  labs(col="Log10(Oxygen diffusivity)") +
+  theme_bw() +
+  theme(legend.position="top")
+
+```
+
+There still remains the question of why the effect of PB diversity saturates.
+We don't currently have a good explanation for this, just as we don't have good explanations for other effects of diversity that are non-linear.
+
 # Effect of number of strains
@@
 all_stab <- readRDS(here("data/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS")) 
-
 which_strains <- c(2, 3, 6, 9)

### 2022-02-27 experiments/2_supplement/supplement.Rmd
work on supplement

@@
 
-(ref:repl-meth2) Stable states found with the *replication* method.
+(ref:repl-meth2) Stable states found with the **replication method**.
 The right column of panels refers to the stable state when oxygen diffusivity is at first high (favouring the oxic state).
@@
 
-(ref:temp-meth2) Stable states found with the *temporal* method. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+(ref:temp-meth2) Stable states found with the **temporal method**. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
 
@@
 
-## Effect of abundance change event
+## Effect of diversity, replication method
 
-**To be completed... waiting for data**
+The replication method shows the same effects of functional diversity as those revealed by the temporal method (Figure \@ref(fig:div-repl-meth1)). Namely
 
-As mentioned in the main report, to avoid very low strain densities, we added 1 unit of density to every biological state variable every 1,000 hours (a slightly different method produced the same results, see the Supplementary Information for details).
-We also test the effect of making an abundance floor of 1 unit that was implemented every 1,000 hours.
-I.e.
-any adundances that were lower than 1 unit were set to 1 unit, every 1,000 hours.
-As shown below, the results with this floor abundance are the same as when 1 unit is added.
+-   Introducing functional diversity in all three functional groups increases the resilience of both the anoxic and oxic state.
+-   Introducing functional diversity in only the cyanobacteria function group delays (with respect to the oxygen diffusivity it occurs at) the switch to the anoxic state as oxygen diffusivity is reduced, but has no effect on the oxygen diffusivity at which the anoxic to oxic transition occurs .
+-   Introducing function diversity in only the sulfur bacteria delays (with respect to the oxygen diffusivity it occurs at) the switch from anoxic to oxic, and advances the switch from oxic to anoxic.
 
-(ref:div-temp-eventdef1) **Left column of panels**: the effect of response trait diversity (y-axis) on the positions of the tipping points (anoxic to oxic in blue, oxic to anoxic in red), which determine the extent of the region of bistability (green shaded region) in the oxygen diffusivity gradient.
+(ref:div-repl-meth1) **Replication method results.** **Left column of panels**: the effect of response trait diversity (y-axis) on the positions of the tipping points (anoxic to oxic in blue, oxic to anoxic in red), which determine the extent of the region of bistability (green shaded region) in the oxygen diffusivity gradient.
 The left-most region is anoxic only, the middle is oxic or anoxic depending on historical conditions, and the right-most is oxic only.
@@
 
-```{r div-temp-eventdef1, eval = FALSE, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-eventdef1)', fig.height=8, fig.width=8, fig.align="center"}
-all_stab <- readRDS(here("data/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method_eventdef1.RDS"))
+```{r div-repl-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-repl-meth1)', fig.height=8, fig.width=8, fig.align="center"}
+all_stab <- readRDS(here("data/0_ss_finding/replication_method/processed_data/stab_data_replication_method.RDS"))
 
@@
 
-## Effect of diversity, replication method
+## Effect of abundance change event
 
-The replication method shows the same effects of functional diversity as those revealed by the temporal method (Figure \@ref(fig:div-repl-meth1). Namely
+As mentioned in the main report, to avoid very low strain densities, we added 1 unit of density to every biological state variable every 1,000 hours (a slightly different method produced the same results, see the Supplementary Information for details).
+We also test the effect of making an abundance floor of 1 unit that was implemented every 1,000 hours.
+I.e.
+any abundances that were lower than 1 unit were set to 1 unit, every 1,000 hours.
+As shown in Figure \@ref(fig:div-temp-eventdef1), the results with this floor abundance are similar as when 1 was added every 1,000 hours.
+Note that a coarser gradient of trait variation was used, hence the saw-tooth patterns.
+A further difference is the large decrease in resilience of the anoxic to oxic transition above moderate levels of diversity in the SB and SB-SB treatments.
+This pattern can also occur with addition of 1 abundance unit (e.g., see Figure \@ref(fig:div-temp-meth3), and is discussed in the section that concerns this below (section [SB diversity effects]).
 
--   Introducing functional diversity in all three functional groups increases the resilience of both the anoxic and oxic state.
--   Introducing functional diversity in only the cyanobacteria function group delays (with respect to the oxygen diffusivity it occurs at) the switch to the anoxic state as oxygen diffusivity is reduced, but has no effect on the oxygen diffusivity at which the anoxic to oxic transition occurs .
--   Introducing function diversity in only the sulfur bacteria delays (with respect to the oxygen diffusivity it occurs at) the switch from anoxic to oxic, and advances the switch from oxic to anoxic.
-
-(ref:div-repl-meth1) **Left column of panels**: the effect of response trait diversity (y-axis) on the positions of the tipping points (anoxic to oxic in blue, oxic to anoxic in red), which determine the extent of the region of bistability (green shaded region) in the oxygen diffusivity gradient.
+(ref:div-temp-eventdef1) **Results with an abundance floor.** **Left column of panels**: the effect of response trait diversity (y-axis) on the positions of the tipping points (anoxic to oxic in blue, oxic to anoxic in red), which determine the extent of the region of bistability (green shaded region) in the oxygen diffusivity gradient.
 The left-most region is anoxic only, the middle is oxic or anoxic depending on historical conditions, and the right-most is oxic only.
@@
 
-```{r div-repl-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-repl-meth1)', fig.height=8, fig.width=8, fig.align="center"}
-all_stab <- readRDS(here("data/0_ss_finding/replication_method/processed_data/stab_data_replication_method.RDS"))
+```{r div-temp-eventdef1, eval = TRUE, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-eventdef1)', fig.height=8, fig.width=8, fig.align="center"}
+all_stab <- readRDS(here("data/0_ss_finding/temporal_method/event_def1/processed_data/stab_data_temporal_method.RDS"))
 
-sim_length <- 1e6
+wait_time <- 1e6
 num_strains <- 9
 plot_here <- all_stab %>%
-  filter(simlength == sim_length)
+  filter(waittime == wait_time)
 p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
@@
 
-(ref:ss-temp-meth3) Stable states found with the temporal method with duration at each oxygen diffusivity value of 1e6 hours.
+(ref:ss-temp-meth3) Stable states found with the temporal method with duration at each oxygen diffusivity value of **1e6 hours**.
 The right column of panels refers to the stable state when oxygen diffusivity is at first high (favouring the oxic state).
@@
 
-(ref:ss-temp-meth4) Stable states found with the temporal method with duration at each oxygen diffusivity value of 2e6 hours. All other aspects are as in Figure \@ref(fig:ss-temp-meth3).
+(ref:ss-temp-meth4) Stable states found with the temporal method with duration at each oxygen diffusivity value of **2e6 hours**. All other aspects are as in Figure \@ref(fig:ss-temp-meth3).
 
@@
 
-(ref:ss-temp-meth1) Stable state of the system with moderate level of diversity in only SB, and no diversity in the other two groups. All other aspects are as in Figure \@ref(fig:ss-temp-meth3).
+(ref:ss-temp-meth1) Stable state of the system with **moderate** level of diversity in only SB, and no diversity in the other two groups. All other aspects are as in Figure \@ref(fig:ss-temp-meth3).
 
@@
 
-(ref:ss-temp-meth2)  Stable state of the system with higher than moderate level of diversity in only SB, and no diversity in the other two groups.
+(ref:ss-temp-meth2)  Stable state of the system with **higher than moderate** level of diversity in only SB, and no diversity in the other two groups.
 All other aspects are as in Figure \@ref(fig:ss-temp-meth1).
@@
 (ref:pbdiv-only-1) Right-hand panels show the transition from anoxic to oxic state when oxygen diffusivity increases.
-The results here are for a low amount of variation in only the PB functional group.
+The results here are for a **low amount of variation in only the PB functional group**.
 The transition from anoxic to oxic occurs at approximately $log_{10}$(oxygen diffusivity) = `r round(aO_flip_sim1, 2)`.
@@
 (ref:pbdiv-only-2) Right-hand panels show the transition from anoxic to oxic state when oxygen diffusivity increases.
-The results here are for a moderate amount of variation in only the PB functional group.
+The results here are for a **moderate amount of variation in only the PB functional group**.
 The transition from anoxic to oxic occurs at approximately $log_{10}$(oxygen diffusivity) = `r round(aO_flip_sim2, 2)`.

### 2022-02-27 experiments/0_ss_finding/temporal_method/data_processing.R

@@ -3,9 +3,9 @@
 library(here)
 library(tidyverse)
 
+## Process the stability data to a smaller file
 
-
-## Process the stability data to a smaller file ----
+##  event def2 ----
 
 read_plus <- function(flnm) {
   print(flnm)
@@ -13,10 +13,10 @@ read_plus <- function(flnm) {
     mutate(filename = flnm)
 }
 
-tbl1 <- list.files(path = here::here("data/0_ss_finding/temporal_method/"),
+tbl1 <- list.files(path = here::here("data/0_ss_finding/temporal_method"),
                    pattern = "stab_data", 
                    full.names = TRUE,
-                   recursive = TRUE) %>% 
+                   recursive = FALSE) %>% 
   map_df(~read_plus(.))
 
 keep_tbl1 <- tbl1
@@ -115,6 +115,121 @@ all_stab_results <- all_stab_results %>%
                                                                 "CB-SB-PB")))
 
 saveRDS(all_stab_results, here::here("data/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS"))
+
+
+
+
+## Event def1 ----
+
+read_plus <- function(flnm) {
+  print(flnm)
+  readRDS(flnm) %>% 
+    mutate(filename = flnm)
+}
+
+tbl1 <- list.files(path = here::here("data/0_ss_finding/temporal_method/event_def1"),
+                   pattern = "stab_data", 
+                   full.names = TRUE,
+                   recursive = FALSE) %>% 
+  map_df(~read_plus(.))
+
+keep_tbl1 <- tbl1
+
+all_stab <- tbl1 %>%
+  select(-data, -pars, -parameter, -total_initial_abundances, -ssfind_pars, -ssfind_result) %>%
+  separate(filename , sep = "_", into = c(paste0("junk", 1:8), "waittime", paste0("junk", 9:11))) %>%
+  select(-starts_with("junk")) %>%
+  mutate(waittime = parse_number(waittime))
+
+
+
+CB_vars <- unique(all_stab$CB_var_gmax_s)
+SB_vars <- unique(all_stab$SB_var_gmax_s)
+PB_vars <- unique(all_stab$PB_var_gmax_s)
+
+CB_all_stab <- all_stab %>%
+  filter(SB_var_gmax_s == 0,
+         PB_var_gmax_s == 0) %>%
+  ungroup() %>%
+  mutate(var_treat = "CB",
[…]

### 2022-03-13 experiments/2_supplement/supplement.Rmd
add hidden SB diversity issue to supplement

@@
 
+## SB diversity effect anoxic to oxic transition
+
 Wait times of 1e5 (Figure \@ref(fig:div-temp-meth2) and 1e4 (Figure \@ref(fig:div-temp-meth4) produce qualitatively and often quantitatively very similar to those for wait times of 1e6 (Figure \@ref(fig:div-temp-meth1)).
@@
 due to evolution), then we expect this result to not occur, and rather for the effects of diversity with two or three strains to be the same as those with six or nine.
+
+## SB diversity effect oxic to anoxic transition
+
+When the environment ameliorates for the sulphur bacteria, there can be limited evidence of strain replacement (in final state) along the oxygen diffusivity gradient -- either the system is oxic or the least tolerant strain SB9 dominates.
+And yet the switch to anoxic occurs earlier than when there is no diversity, which suggests there is some role of the more tolerant strains.
+Indeed Uriah showed that the presence of only the most tolerant strain is sufficient to give an earlier switch, even though it is not present in the final state when less tolerant strains are present.
+And he showed that the presence of only the least tolerant strain creates a later switch than when there are more tolerant strains.
+
+The explanation is that the most tolerant strain does play a role, but only a transient one.
+The following dynamics are for the system starting oxic, and with a value of oxygen diffusivity (log10(a_O) = -4.8) for which the system remains oxic if there is no diversity (Figure \@ref(fig:sb-div-effect3)), but switches to anoxic if there is diversity (Figure \@ref(fig:sb-div-effect4)).
+There is only diversity in the sulphur bacteria.
+The most tolerant strain does at first grow, but is then outcompeted by less tolerant strains as the environment ameliorates (temporally).
+
+```{r echo = FALSE}
+run_sims_this_section <- FALSE
+```
+
+```{r eval = run_sims_this_section, echo = FALSE}
+#var_expt <- readRDS(here("experiments/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
+var_expt_levels <- var_expt[,1:6]
+no_diversity <- which(rowSums(abs(var_expt_levels))==0)
+max_diversty_all <- which(max(rowSums(abs(var_expt_levels))) ==
+                            rowSums(abs(var_expt_levels)))
+max_only_CB_diversity <- which(max(rowSums(abs(var_expt_levels[,1:2]))) ==
+                            rowSums(abs(var_expt_levels[,1:2])) &
+                              rowSums(abs(var_expt_levels[,3:6]))==0)
+max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
+                            rowSums(abs(var_expt_levels[,3:6])) &
+                              rowSums(abs(var_expt_levels[,1:2]))==0)
+```
+
+```{r  eval = run_sims_this_section, echo = FALSE}
+parameter <- parameter_master
+parameter$strain_parameter <- var_expt[no_diversity,]$pars[[1]]
+parameter$sim_duration <- 100000
+parameter$result <- NULL
+parameter$log10a_series <- c(-4.8, -4.8)
+parameter$strain_parameter$initial_state <- new_initial_state(
+  nrow(parameter$strain_parameter$CB),
+  nrow(parameter$strain_parameter$PB),
+  nrow(parameter$strain_parameter$PB),
+  values = "bush_ssfig3"
+)
+parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/nrow(parameter$strain_parameter$CB)
+
+sim_res_novar1 <- run_simulation(parameter)
+saveRDS(sim_res_novar1, here("experiments/checks_puzzles/data/puzzle1_1.RDS"))
+```
+
+(ref:sb-div-effect3)  Dynamics of the system with no diversity in any functional group, and log10(oxygen diffusivity) = -4.8. The system remains oxic when starting in the oxic state.
+
+```{r  sb-div-effect3, echo = FALSE,  include=TRUE, fig.cap='(ref:sb-div-effect3)', fig.height=8, fig.width=8, fig.align="center"}
+sim_res_novar1 <- readRDS(here("experiments/2_supplement/data/puzzle1_1.RDS"))
+plot_dynamics(sim_res_novar1)
+#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
+```
+
+```{r  eval = run_sims_this_section, echo = FALSE}
+parameter$strain_parameter <- var_expt[max_only_SBPB_diversity,]$pars[[1]]
+#parameter$sim_duration <- 100000
+#parameter$result <- NULL
+#parameter$log10a_series <- c(-5.2, -5.2)
+#parameter$strain_parameter$initial_state <- new_initial_state(
+#  nrow(parameter$strain_parameter$CB),
+#  nrow(parameter$strain_parameter$PB),
+#  nrow(parameter$strain_parameter$PB),
+#  values = "bush_ssfig3"
+#)
+parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/nrow(parameter$strain_parameter$CB)
+sim_res_highvar1 <- run_simulation(parameter)
+saveRDS(sim_res_highvar1, here("experiments/checks_puzzles/data/puzzle1_2.RDS"))
+```
+
+(ref:sb-div-effect4) Dynamics of the system with diversity in sulfur bacteria and otherwise exactly the same conditions as in Figure \@ref(fig:sb-div_effect3).
+The system flips from oxic to anoxic, whereas it did not when there was no diversity.
+
+```{r sb-div-effect4, echo = FALSE,  include=TRUE, fig.cap='(ref:sb-div-effect4)', fig.height=8, fig.width=8, fig.align="center"}
+sim_res_highvar1 <- readRDS(here("experiments/2_supplement/data/puzzle1_2.RDS"))
+plot_dynamics(sim_res_highvar1)
+#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
+```
 

### 2022-03-14 experiments/2_supplement/supplement.Rmd
supplement.Rmd: fixed paths
parameter_master is missing.

@@
 library(here)
-source(here("r/various_useful_functions.r"))
-source(here("experiments/1_figures_main_ms/ms_figure_functions.r"))
+source(here("r", "various_useful_functions.r"))
+# source(here("experiments", "1_figures_main_ms", "ms_figure_functions.r"))
+source(here("experiments", "1_figures_main_ms", "figures_main_ms_v1.R"))
 
@@
 ```{r repl_meth1, echo=FALSE, eval = TRUE}
-repl_meth <- readRDS(here("data/0_ss_finding/replication_method/ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
-temp_meth <- readRDS(here("data/0_ss_finding/temporal_method/ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
+repl_meth <- readRDS(here("data", "0_ss_finding", "replication_method", "ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
+temp_meth <- readRDS(here("data", "0_ss_finding", "temporal_method", "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
 ```
@@
 ```{r div-repl-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-repl-meth1)', fig.height=8, fig.width=8, fig.align="center"}
-all_stab <- readRDS(here("data/0_ss_finding/replication_method/processed_data/stab_data_replication_method.RDS"))
+all_stab <- readRDS(here("data", "0_ss_finding", "replication_method", "processed_data", "stab_data_replication_method.RDS"))
 
@@
 ```{r div-temp-eventdef1, eval = TRUE, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-eventdef1)', fig.height=8, fig.width=8, fig.align="center"}
-all_stab <- readRDS(here("data/0_ss_finding/temporal_method/event_def1/processed_data/stab_data_temporal_method.RDS"))
+all_stab <- readRDS(here("data", "0_ss_finding", "temporal_method", "event_def1", "processed_data", "stab_data_temporal_method.RDS"))
 
@@
 ```{r div-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth1)', fig.height=7, fig.width=6, fig.align="center"}
-all_stab <- readRDS(here("data/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS"))
+all_stab <- readRDS(here("data", "0_ss_finding", "temporal_method", "processed_data", "stab_data_temporal_method.RDS"))
 
@@
 ```{r ss-temp-meth3, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth3)', fig.height=8, fig.width=8, fig.align="center"}
-single_1e6 <- readRDS(here("data/0_ss_finding/temporal_method/single_1e6_result.RDS"))
+single_1e6 <- readRDS(here("data", "0_ss_finding", "temporal_method", "single_1e6_result.RDS"))
 temp_meth[1,]$ssfind_result[[1]] <- single_1e6
@@
 ```{r ss-temp-meth4, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth4)', fig.height=8, fig.width=8, fig.align="center"}
-single_2e6 <- readRDS(here("data/0_ss_finding/temporal_method/single_2e6_result.RDS"))
+single_2e6 <- readRDS(here("data", "0_ss_finding", "temporal_method", "single_2e6_result.RDS"))
 temp_meth[1,]$ssfind_result[[1]] <- single_2e6
@@
 wait_time <- "1e+04"
-ss_9s <- readRDS(here(paste0("data/0_ss_finding/temporal_method/ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
-#stab_9s <- readRDS(here(paste0("data/0_ss_finding/temporal_method/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+ss_9s <- readRDS(here(paste0("data", "0_ss_finding", "temporal_method", "ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+#stab_9s <- readRDS(here(paste0("data", "0_ss_finding", "temporal_method", "stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
 
@@
 ```{r eval = run_sims_this_section, echo = FALSE}
-#var_expt <- readRDS(here("experiments/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
+#var_expt <- readRDS(here::here("data", "9_strains", "ss_data_1e6_x2x6_factorial.RDS"))
 var_expt_levels <- var_expt[,1:6]
@@
 sim_res_novar1 <- run_simulation(parameter)
-saveRDS(sim_res_novar1, here("experiments/checks_puzzles/data/puzzle1_1.RDS"))
+dir.create(here::here("data", "2_supplement"), recursive = TRUE, showWarnings = FALSE)
+saveRDS(sim_res_novar1, here::here("data", "2_supplement", "puzzle1_1.RDS"))
 ```
@@
 ```{r  sb-div-effect3, echo = FALSE,  include=TRUE, fig.cap='(ref:sb-div-effect3)', fig.height=8, fig.width=8, fig.align="center"}
-sim_res_novar1 <- readRDS(here("experiments/2_supplement/data/puzzle1_1.RDS"))
+sim_res_novar1 <- readRDS(here::here("data", "2_supplement", "puzzle1_1.RDS"))
 plot_dynamics(sim_res_novar1)
-#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
+#ggsave(here("simulations", "expt2", "figures", "switching_novar.pdf"), width = 10)
 ```
@@
 sim_res_highvar1 <- run_simulation(parameter)
-saveRDS(sim_res_highvar1, here("experiments/checks_puzzles/data/puzzle1_2.RDS"))
+saveRDS(sim_res_highvar1,here::here("data", "2_supplement", "puzzle1_2.RDS"))
 ```
@@
 ```{r sb-div-effect4, echo = FALSE,  include=TRUE, fig.cap='(ref:sb-div-effect4)', fig.height=8, fig.width=8, fig.align="center"}
-sim_res_highvar1 <- readRDS(here("experiments/2_supplement/data/puzzle1_2.RDS"))
+sim_res_highvar1 <- readRDS(here("data", "2_supplement", "puzzle1_2.RDS"))
 plot_dynamics(sim_res_highvar1)
-#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
+#ggsave(here("simulations", "expt2", "figures", "switching_novar.pdf"), width = 10)
 ```
@@
 ```{r echo = FALSE}
-ss_9s <- readRDS(here("data/0_ss_finding/temporal_method/ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
+ss_9s <- readRDS(here::here("data", "0_ss_finding", "temporal_method", "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
 only_PB_variable <- ss_9s %>%
@@
 
-only_PB_stab <- readRDS(here("data/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS")) %>%
+only_PB_stab <- readRDS(here::here("data", "0_ss_finding", "temporal_method", "processed_data", "stab_data_temporal_method.RDS")) %>%
   filter(
@@
 
-stab_9s <- readRDS(here("data/0_ss_finding/temporal_method/ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
+stab_9s <- readRDS(here("data", "0_ss_finding", "temporal_method", "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
 
@@
 ```{r div-stab-multstrain1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-stab-multstrain1)', fig.height=8, fig.width=8, fig.align="center"}
-all_stab <- readRDS(here("data/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS")) 
+all_stab <- readRDS(here("data", "0_ss_finding", "temporal_method", "processed_data", "stab_data_temporal_method.RDS")) 
 which_strains <- c(2, 3, 6, 9)

### 2022-03-14 experiments/2_supplement/supplement.Rmd
Update supplement.Rmd

@@
 ```{r  eval = run_sims_this_section, echo = FALSE}
-parameter <- parameter_master
+
+num_CB_strains <- 9
+num_SB_strains <- 9
+num_PB_strains <- 9
+
+sp <- new_strain_parameter(
+  n_CB = num_CB_strains,
+  n_PB = num_SB_strains,
+  n_SB = num_PB_strains,
+  values_initial_state = "bush_ssfig3"
+)
+
+parameter <- new_runsim_parameter(
+  dynamic_model = bushplus_dynamic_model,
+  event_definition = event_definition_1,
+  event_interval = 100,
+  noise_sigma = 0,
+  minimum_abundances = rep(1, 3),
+  sim_duration = 2000,
+  sim_sample_interval = 100,
+  strain_parameter = sp,
+  log10a_series = c(
+    log10(sp$a_O),
+    log10(sp$a_O)
+  )
+)
+names(parameter$minimum_abundances) <- c("CB", "PB", "SB")
+rm(sp)
+
 parameter$strain_parameter <- var_expt[no_diversity,]$pars[[1]]

### 2022-03-14 experiments/2_supplement/supplement.Rmd
Fixes #24

@@
 wait_time <- "1e+04"
-ss_9s <- readRDS(here(paste0("data", "0_ss_finding", "temporal_method", "ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
-#stab_9s <- readRDS(here(paste0("data", "0_ss_finding", "temporal_method", "stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+ss_9s <- readRDS(here::here("data", "0_ss_finding", "temporal_method", paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+#stab_9s <- readRDS(here::here(\"data", "0_ss_finding", "temporal_method", paste0("stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS"))
 
@@
 ```{r echo = FALSE}
-run_sims_this_section <- FALSE
+run_sims_this_section <- TRUE
 ```
@@
 names(parameter$minimum_abundances) <- c("CB", "PB", "SB")
+
 rm(sp)

### 2022-03-16 experiments/2_supplement/supplement.Rmd
update supplement

--- 2022-03-14 experiments/2_supplement/supplement.Rmd
@@
 
-Notice that in all three cases, the range of trait variation represented by the strains is the same, even though the number of strains differs (a consequence is that the lower row of panels in Figures \@ref(fig:nine-strain-div), \@ref(fig:three-strain-div), and \@ref(fig:two-strain-div) are identical).
+Notice that in all three cases, the range of trait variation represented by the strains is the same, even though the number of strains differs.
 This approach allowed us to independently manipulate trait diversity and number of strains.
+Also note that maximum growth rate of strains is evenly distributed on a log scale, even though it may appear at first site that they are distributed evenly on a linear scale (e.g.
+Figure \@ref(fig:three-strain-div)).
 
@@
 )
+
+#0.05*2^(CB_gmax_div) - 0.05
+#0.05 - 0.05*2^(-CB_gmax_div)
+
 ```
@@
 
-We also show, in Figure \@ref(fig:growth-rates), the relationship between realised growth rate and the concentration of the respective inhibiting substance, e.g.
+A consequence of this variation and of the tradeoffs is shown in  Figure \@ref(fig:growth-rates), which shows the relationship between realised growth rate and the concentration of the respective inhibiting substance, e.g.
 sulfide for the cyanobacteria.
@@
 
-```{r repl_meth1, echo=FALSE, eval = TRUE}
+```{r repl-meth1, echo=FALSE, eval = TRUE}
 repl_meth <- readRDS(here("data", "0_ss_finding", "replication_method", "ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
@@
 
+### Overal effects of diversity
+
 The replication method shows the same effects of functional diversity as those revealed by the temporal method (Figure \@ref(fig:div-repl-meth1)). Namely
@@
 
+```
+
+### An example of stable states
+
+Figure \@ref(fig:repl-meth-ex1) shows an example of stable states along the oxygen diffusivity gradient produced by the replication method for finding stable states.
+The patterns are similar to those produced by the temporal method for finding the stable states (see Figure 3 in the main report), though differ in one respect: some of the more tolerant strains occur in the stable states found by the temporal method (Figure 3 in the main report), while they do not occur in stable states found by the replication method (Figure \@ref(fig:repl-meth-ex1) here).
+We understand that the appearance of these strains is transient, and the difference in their appearance in results of the two methods is due to differences in starting conditions of the two methods, and that this difference influences how long transients are present for.
+Transients close to a state change are likely longer for longer in the temporal method than the replication method.
+
+An interesting feature of these results is that although the position of the oxic to anoxic tipping point is affected by diversity (Figure \@ref(fig:div-repl-meth1) and Figure 3 in the main report) there is no evidence of more tolerant strains being present in the final system state (Figure \@ref(fig:repl-meth-ex1)).
+This phenomenon is explained in Section \@ref(SB2).
+
+(ref:repl-meth-ex1) Stable states found with the **replication method** with intermediate levels of diversity in all functional groups.
+Figure features are otherwise the same as those in Figure \@ref(fig:repl-meth2)).
+
+```{r repl-meth-ex1, echo = FALSE,  include=TRUE, fig.cap='(ref:repl-meth-ex1)', fig.height=8, fig.width=8, fig.align="center"}
+repl_meth <- readRDS(here("data", "0_ss_finding", "replication_method", "ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
+fig_state_vs_o2diff_sidebyside_dots(repl_meth[94,])
 ```
@@
 wait_time <- "1e+04"
-ss_9s <- readRDS(here(paste0("data", "0_ss_finding", "temporal_method", "ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+ss_9s <- readRDS(here("data", "0_ss_finding", "temporal_method", paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
 #stab_9s <- readRDS(here(paste0("data", "0_ss_finding", "temporal_method", "stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
@@
 
-## SB diversity effect oxic to anoxic transition
+## SB diversity effect oxic to anoxic transition {#SB2}
 

### 2022-03-16 experiments/2_supplement/supplement.Rmd

@@
 wait_time <- "1e+04"
-ss_9s <- readRDS(here("data", "0_ss_finding", "temporal_method", paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
-#stab_9s <- readRDS(here(paste0("data", "0_ss_finding", "temporal_method", "stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+ss_9s <- readRDS(here::here("data", "0_ss_finding", "temporal_method", paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+#stab_9s <- readRDS(here::here(\"data", "0_ss_finding", "temporal_method", paste0("stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS"))
 

### 2022-03-25 experiments/2_supplement/supplement.Rmd
Update supplement.Rmd

@@
 
+We generated variation in maximum growth rate $G_{max}$ and tolerance to reduced sulfur $h_{SR}$ or oxygen $h_{O}$ by varying the range of trait values around a reference trait value.
 Take for example the cyanobacteria functional group, a reference maximum growth rate parameter $G_{max,CB}$ and a reference tolerance parameter $h_{SR,CB}$.
 Recall that amount of among strain variation is controlled by the two meta-parameters $Div_{G_{max,CB}}$ and $Div_{h_{SR,CB}}$.
-To create a tradeoff, the two meta-parameters were always of different sign.
+To create a trade-off, the two meta-parameters were always of different sign.
 The among strain variation was calculated such that the growth rate of strain $i = 1$ was a factor $1/({2Div_{G_{max,CB}}})$ of the reference growth rate, and the growth rate of the $i = n$ strain was a factor $2Div_{G_{max,CB}}$ of the reference growth rate.
@@
 We show three examples of the created variation among strains within functional groups, one for nine strains (Figure \@ref(fig:nine-strain-div)), one for three (Figure \@ref(fig:three-strain-div)), and one for two (Figure \@ref(fig:two-strain-div)).
-In each, three graphs shows the diversity among strains in the maximum growth rate trait and the tolerance trait, plotted against each other and therefore also showing the tradeoff between the two traits.
+In each of these three examples, three graphs show the diversity among strains in the maximum growth rate trait and the tolerance trait, plotted against each other and therefore also showing the trade-off between the two traits.
 

### 2022-03-28 experiments/2_supplement/supplement.Rmd
Changes of Supplement text

@@
 Here we provide additional description of the method used to create strain variation within functional groups. The following should be read only after the relevant sections of the main text. 
-
 We generated variation in maximum growth rate $G_{max}$ and tolerance to reduced sulfur $h_{SR}$ or oxygen $h_{O}$ by varying the range of trait values around a reference trait value.
@@
 In all panels colour indicates the functional group, darker shades show more tolerant-lower growth rate strains, lighter shades show less tolerant-higher growth rate strains.
+Tolerance is given as the concentration of the inhibiting substrate where the growth rate of the strain is reduced by 50%.
 
@@
 
-A consequence of this variation and of the tradeoffs is shown in  Figure \@ref(fig:growth-rates), which shows the relationship between realised growth rate and the concentration of the respective inhibiting substance, e.g.
-sulfide for the cyanobacteria.
+A consequence of this variation and of the trade-offs is shown in  Figure \@ref(fig:growth-rates), which shows the relationship between realised growth rate and the concentration in the environment of the respective inhibiting substance, e.g.
+reduced sulfur for the cyanobacteria.
 In these graphs only the least and most tolerant strains are shown.
-The lines cross due to the tradeoff.
+The lines cross due to the trade-off.
 At high concentrations of the inhibiting substance the more tolerant strain has higher realised growth rate, while at lower concentrations it is the less tolerant strain that has the higher realised growth rate.
@@
 Here we also describe and give results of what we term the *Replication method*.
-In this, we made a separate simulations for each of many values of oxygen diffusivity, ran the simulations for long enough to ensure transients had passed, and recorded the state.
+In this, we made separate simulations for each of many values of oxygen diffusivity, ran the simulations for long enough to ensure transients had passed, and recorded the state.
 We ran multiple simulations per value of oxygen diffusivity, and started them with different initial conditions (either low or high total cyanobacterial abundance), so as to check for presence of alternate stable states.
-This method used by [Bush et al 2017](https://www.nature.com/articles/s41467-017-00912-x).
+This method was used by [Bush et al 2017](https://www.nature.com/articles/s41467-017-00912-x).
 We term it the replication method since it is achieved by having many independent replicates of the ecosystem, each with a different oxygen diffusivity, and also a separate replicate for each of the different chosen initial conditions.
@@
 As is shown in the figures below, the temporal method results in a larger region of bistability than the replication method, but only during increasing oxygen diffusivities.
-The difference in results occurs because, as mentioned above, the initial conditions differ between the two approaches.
+The difference in results occurs because, as discussed below, the initial conditions differ between the two approaches.
 
@@
 (ref:repl-meth2) Stable states found with the **replication method**.
-The right column of panels refers to the stable state when oxygen diffusivity is at first high (favouring the oxic state).
-The left column refers to when oxygen diffusivity is at first low (favouring the anoxic state).
+The left column of panels refers to the stable state when oxygen diffusivity is at first high (favouring the oxic state).
+The right column refers to when oxygen diffusivity is at first low (favouring the anoxic state).
 Points (which sometimes are so close as to appear as thick lines) show the stable state at the end of each period of constant oxygen diffusivity.
@@
 
-### Overal effects of diversity
+### Overall effects of diversity
 
@@
 
--   Introducing functional diversity in all three functional groups increases the resilience of both the anoxic and oxic state.
--   Introducing functional diversity in only the cyanobacteria function group delays (with respect to the oxygen diffusivity it occurs at) the switch to the anoxic state as oxygen diffusivity is reduced, but has no effect on the oxygen diffusivity at which the anoxic to oxic transition occurs .
--   Introducing function diversity in only the sulfur bacteria delays (with respect to the oxygen diffusivity it occurs at) the switch from anoxic to oxic, and advances the switch from oxic to anoxic.
+-   Introducing functional diversity in only the cyanobacteria increases the resilience of the oxic state but has no effect on the resilience of the anoxic state. 
+-   Introducing functional diversity in only the sulfate-reducing bacteria increases the resilience of the anoxic state and reduces the resilience of the oxic state.
+-   Introducing functional diversity in only the phototrophic sulfur bacteria reduces the resilience of the anoxic state and has no effect on the resilience of the oxic state. 
+-   Introducing functional diversity in more than one functional group reduces, reverses, or does not change the effect of diversity in individual functional groups.
+For example, introducing functional diversity in all three functional groups reduces the resilience of the oxic state when trait variation is low but increases the resilience of the oxic state when trait variation is high.
 
@@
                                      figure_title = paste0(sim_length,
-                                                           " sim. length,\n",
+                                                           " simulation length,\n",
                                                            num_strains,
@@
 Figure \@ref(fig:repl-meth-ex1) shows an example of stable states along the oxygen diffusivity gradient produced by the replication method for finding stable states.
-The patterns are similar to those produced by the temporal method for finding the stable states (see Figure 3 in the main report), though differ in one respect: some of the more tolerant strains occur in the stable states found by the temporal method (Figure 3 in the main report), while they do not occur in stable states found by the replication method (Figure \@ref(fig:repl-meth-ex1) here).
-We understand that the appearance of these strains is transient, and the difference in their appearance in results of the two methods is due to differences in starting conditions of the two methods, and that this difference influences how long transients are present for.
-Transients close to a state change are likely longer for longer in the temporal method than the replication method.
+The patterns are similar to those produced by the temporal method for finding the stable states (see Figure 4 in the main report), though they differ in one respect: close to the transition back to the state a group dominates, some of the more tolerant strains occur in the stable states found by the temporal method (Figure 4 in the main report), while they do not occur in stable states found by the replication method (Figure \@ref(fig:repl-meth-ex1) here).
+We understand that the appearance of these strains is transient, and the difference in their appearance results from the differences in starting conditions of the two methods.
+Specifically, in the temporal method, the initial condition at a new level of oxygen diffusivity is the stable state at the previous level of oxygen diffusivity, while in the replication method the starting conditions are identical at each level of oxygen diffusivity.
+These differences in starting conditions apparently result in longer persistence of transients in the temporal method than the replication method.
 
-An interesting feature of these results is that although the position of the oxic to anoxic tipping point is affected by diversity (Figure \@ref(fig:div-repl-meth1) and Figure 3 in the main report) there is no evidence of more tolerant strains being present in the final system state (Figure \@ref(fig:repl-meth-ex1)).
+An interesting feature of these results is that although the position of the oxic to anoxic tipping point is affected by diversity in the sulfate-reducing bacteria (Figure \@ref(fig:div-repl-meth1) and Figure 3 in the main report) there is no evidence of more tolerant strains of sulfate-reducing bacteria being present in the final system state (Figure \@ref(fig:repl-meth-ex1)).
 This phenomenon is explained in Section \@ref(SB2).
@@
 
-As mentioned in the main report, to avoid very low strain densities, we added 1 unit of density to every biological state variable every 1,000 hours (a slightly different method produced the same results, see the Supplementary Information for details).
-We also test the effect of making an abundance floor of 1 unit that was implemented every 1,000 hours.
+As mentioned in the main report, to avoid very low strain densities, we added 1 unit of density to every biological state variable every 1,000 hours.
+We here show that a slightly different method produced the same results.
+Specifically, we tested the effect of making an abundance floor of 1 unit that was implemented every 1,000 hours.
 I.e.
-any abundances that were lower than 1 unit were set to 1 unit, every 1,000 hours.
+every 1,000 hours, any abundances that were lower than 1 unit were set to 1 unit.
 As shown in Figure \@ref(fig:div-temp-eventdef1), the results with this floor abundance are similar as when 1 was added every 1,000 hours.
 Note that a coarser gradient of trait variation was used, hence the saw-tooth patterns.
-A further difference is the large decrease in resilience of the anoxic to oxic transition above moderate levels of diversity in the SB and SB-SB treatments.
-This pattern can also occur with addition of 1 abundance unit (e.g., see Figure \@ref(fig:div-temp-meth3), and is discussed in the section that concerns this below (section [SB diversity effects]).
+A further difference is the large decrease in resilience of the anoxic to oxic transition above moderate levels of diversity in the SB and CB-SB treatments.
+This pattern can also occur with addition of 1 abundance unit (e.g., see Figure \@ref(fig:div-temp-meth3)), and is discussed in the section that concerns this below (section [SB diversity effects]).
 
@@
 A particularly notable difference between the two approaches is in the initial condition.
-In the temporal approach, the initial condition at a new level of oxygen diffusivity is the stable state at the previous level of oxygen diffusivity, while in the approach of Bush et al (2017) the initial conditions are fixed and arbitrary (though this approach is still useful for illustrating the bistability of the system).
-This difference in initial conditions increases the region of bistability in the temporal approach because as a tipping point approaches, the functional group that will dominate after the regime shift starts from much lower abundances than in the approach by Bush et al (2017) and thus requires stronger amelioration of the environment to take over.
+In the temporal approach, the initial condition at a new level of oxygen diffusivity is the stable state at the previous level of oxygen diffusivity, while in the approach of [Bush et al 2017](https://www.nature.com/articles/s41467-017-00912-x) the initial conditions are fixed and arbitrary (though this approach is still useful for illustrating the bistability of the system).
+This difference in initial conditions increases the region of bistability in the temporal approach because as a tipping point approaches, the functional group that will dominate after the regime shift starts from much lower abundances than in the approach by [Bush et al 2017](https://www.nature.com/articles/s41467-017-00912-x) and thus requires stronger amelioration of the environment to take over.
 Nevertheless, our main conclusions about the effects of functional trait diversity are the same using either approach.
@@
 The temporal approach is particularly useful when investigating the effects of strain richness.
-In preliminary simulations using the Bush et al (2017) approach, we found the counterintuitive result that higher strain richness led to lower resilience.
+In preliminary simulations using the [Bush et al 2017](https://www.nature.com/articles/s41467-017-00912-x) approach, we found the counterintuitive result that higher strain richness led to lower resilience.
 We then recalled that we chose to divide the initial total abundance of the cyanobacterial (CB) functional group equally among the strains (termed a substitutive design in biodiversity manipulation experiments).
@@
 
-The results below show the stable states as a function of oxygen diffusivity for a system with intermediate level of diversity in all functional groups, with either 1'000'000 hours at each oxygen diffusivity level (Figure \@ref(fig:ss-temp-meth3)), or 2'000'000 hours (Figure \@ref(fig:ss-temp-meth4)).
-This shows that except very close to the values of oxygen diffusitivity at which a state transition occurs, 1'000'000 hours duration of the simulations is sufficient to reach stable state, or very close to it.
-Very close to the transitions, even at 2'000'000 hours, the dynamics are still transient, with high tolerance strains at high density, even though they will eventually be outcompeted by low tolerance (higher growth rate) strains.
+The results below show the stable states as a function of oxygen diffusivity for a system with an intermediate level of diversity in all functional groups, with either 1'000'000 hours at each oxygen diffusivity level (Figure \@ref(fig:ss-temp-meth3)), or 2'000'000 hours (Figure \@ref(fig:ss-temp-meth4)).
+This shows that 1'000'000 hours duration of the simulations are sufficient to reach stable state, except very close to state transitions on the trajectory of recovery (i.e.: cyanobacteria: trajectory up; sulfate-reducing bacteria: trajectory down).
+Very close to these transitions, even at 2'000'000 hours, the dynamics are still transient, with high tolerance strains at high density, even though they will eventually be outcompeted by low tolerance (higher growth rate) strains.
 
 (ref:ss-temp-meth3) Stable states found with the temporal method with duration at each oxygen diffusivity value of **1e6 hours**.
-The right column of panels refers to the stable state when oxygen diffusivity is at first high (favouring the oxic state).
-The left column refers to when oxygen diffusivity is at first low (favouring the anoxic state).
+The left column of panels refers to the stable state when oxygen diffusivity is at first high (favouring the oxic state).
+The right column refers to when oxygen diffusivity is at first low (favouring the anoxic state).
 Points (which sometimes are so close as to appear as thick lines) show the stable state at the end of each period of constant oxygen diffusivity.
@@
 
-## SB diversity effect anoxic to oxic transition
+## SB diversity effect on the anoxic to oxic transition
 
-Wait times of 1e5 (Figure \@ref(fig:div-temp-meth2) and 1e4 (Figure \@ref(fig:div-temp-meth4) produce qualitatively and often quantitatively very similar to those for wait times of 1e6 (Figure \@ref(fig:div-temp-meth1)).
-There is, however, a notable difference when there is variation in only SB, or CB-SB variation treatments with wait time of 1e4 (Figure \@ref(fig:div-temp-meth4)).
+We showed above that wait times of 1e5 (Figure \@ref(fig:div-temp-meth2)) and 1e4 (Figure \@ref(fig:div-temp-meth4)) produce qualitatively and often quantitatively very similar results to those for wait times of 1e6 (Figure \@ref(fig:div-temp-meth1)).
+There is, however, a notable difference when there is variation in only SB, or in CB-SB with wait times of 1e4 (Figure \@ref(fig:div-temp-meth4)).
 Here, moderate increases in diversity have the same effect as with wait times of 1e6.
-
 However, larger increases in diversity suddenly cause a large reduction in resilience of the anoxic-oxic transition.
-Figure \@ref(fig:ss-temp-meth1) gives an example of the stable states when diversity is moderate -- increases in oxygen diffusivity cause strain replacement in the SB to the more tolerant strains, which then delay the shift.
-Suprisingly, when there is just a little more diversity in the SB then the anoxic to oxic transition happens earlier, i.e.
-there is large decrease in resilience \@ref(fig:ss-temp-meth2).
+Figure \@ref(fig:ss-temp-meth1) gives an example of the stable states when diversity is moderate -- increases in oxygen diffusivity cause strain replacement in the SB to the more tolerant strains, which then delay the shift to the oxic state.
+Suprisingly, when there is just a little more diversity in the SB, then the anoxic to oxic transition happens earlier, i.e.
+there is a large decrease in resilience (Figure \@ref(fig:ss-temp-meth2)).
 
@@
 
-We believe that this phenomenon is caused by an effect that we explain with reference to an anology of using stepping stones to cross a river.
-Increasing diversity in our simulations is akin to increasing the width of the river, but while keeping the number of stepping stones (strains) constant.
+We believe that this phenomenon is caused by an effect that we explain with reference to an analogy of using stepping stones to cross a river.
+Increasing diversity in our simulations is akin to increasing the width of the river, but keeping the number of stepping stones (strains) constant.
 So long as the river is not too wide, we can still cross it, but once the width of the river is such that the stepping stones are too far apart, we can't cross the river.
@@
 In the simulated microbial ecosystem, the strains are the stepping stones, and it is much hard (takes longer) for strains to replace each other when there is greater distance (in trait space) between them.
-When they can no longer replace each other in the time available, the system behaves as if only the least tolerant, highest growth rate strain (lighted shade of colour) is present.
+When they can no longer replace each other in the time available, the system behaves as if only the least tolerant, highest growth rate strain (lightest shade of colour) is present.
 In the case illustrated above, this leads to much lower resilience of the anoxic system state.
 
-This phenomena is dependent on having static trait values for the strains.
+This phenomenon is dependent on having static trait values for the strains.
 If strain traits were dynamic (e.g.
@@
 
-## SB diversity effect oxic to anoxic transition {#SB2}
+## SB diversity effect on the oxic to anoxic transition {#SB2}
 
-When the environment ameliorates for the sulphur bacteria, there can be limited evidence of strain replacement (in final state) along the oxygen diffusivity gradient -- either the system is oxic or the least tolerant strain SB9 dominates.
-And yet the switch to anoxic occurs earlier than when there is no diversity, which suggests there is some role of the more tolerant strains.
-Indeed Uriah showed that the presence of only the most tolerant strain is sufficient to give an earlier switch, even though it is not present in the final state when less tolerant strains are present.
-And he showed that the presence of only the least tolerant strain creates a later switch than when there are more tolerant strains.
-
-The explanation is that the most tolerant strain does play a role, but only a transient one.
-The following dynamics are for the system starting oxic, and with a value of oxygen diffusivity (log10(a_O) = -4.8) for which the system remains oxic if there is no diversity (Figure \@ref(fig:sb-div-effect3)), but switches to anoxic if there is diversity (Figure \@ref(fig:sb-div-effect4)).
-There is only diversity in the sulphur bacteria.
-The most tolerant strain does at first grow, but is then outcompeted by less tolerant strains as the environment ameliorates (temporally).
+When the environment ameliorates for the sulfate-reducing bacteria (i.e.
+trajectory down), there is only limited evidence of strain replacement (in final state) along the oxygen diffusivity gradient -- either the system is oxic or the least tolerant strain SB9 dominates.
+And yet the switch to anoxic state occurs earlier than when there is no diversity, which suggests there is some role of the more tolerant strains.
+We here show that the most tolerant strain do play a role, but only a transient one.
+The following dynamics are for the system starting oxic, and with a value of oxygen diffusivity (log10(oxygen diffusivity) = -4.8) for which the system remains oxic if there is no diversity (Figure \@ref(fig:sb-div-effect3)), but switches to anoxic if there is diversity (Figure \@ref(fig:sb-div-effect4)).
+There is only diversity in the two groups of sulfur bacteria.
+The most tolerant strain does at first grow, but is then outcompeted by less tolerant strains as the concentration of the inhibiting substrate (oxygen) declines.
 
@@
 
-(ref:sb-div-effect4) Dynamics of the system with diversity in sulfur bacteria and otherwise exactly the same conditions as in Figure \@ref(fig:sb-div_effect3).
+(ref:sb-div-effect4) Dynamics of the system with diversity in the two groups of sulfur bacteria and otherwise exactly the same conditions as in Figure \@ref(fig:sb-div_effect3).
 The system flips from oxic to anoxic, whereas it did not when there was no diversity.
@@
 For example, a small amount of variation in only the PB functional group, and no variation in other functional groups, results in transition from anoxic to oxic at approximately $log_{10}$(oxygen diffusivity) = `r round(aO_flip_sim1, 2)` (Figure \@ref(fig:pbdiv-only-1)).
-Whereas, a moderate amount of variation in only the PB functional group, and no variation in other functional groups, results in transition from anoxic to oxic at approximately $log_{10}$(oxygen diffusivity) = `r round(aO_flip_sim2, 2)` (Figure \@ref(fig:pbdiv-only-2)).
+Whereas a moderate amount of variation in only the PB functional group, and no variation in other functional groups, results in transition from anoxic to oxic at approximately $log_{10}$(oxygen diffusivity) = `r round(aO_flip_sim2, 2)` (Figure \@ref(fig:pbdiv-only-2)).
 
-(ref:pbdiv-only-1) Right-hand panels show the transition from anoxic to oxic state when oxygen diffusivity increases.
+(ref:pbdiv-only-1) Right-hand panels show the transition from anoxic to oxic state when oxygen diffusivity decreases.
 The results here are for a **low amount of variation in only the PB functional group**.
@@
 
-(ref:pbdiv-only-2) Right-hand panels show the transition from anoxic to oxic state when oxygen diffusivity increases.
+(ref:pbdiv-only-2) Right-hand panels show the transition from anoxic to oxic state when oxygen diffusivity decreases.
 The results here are for a **moderate amount of variation in only the PB functional group**.
@@
 
-This result is different to the effect of diversity within the CB and SB functional groups, which both cause increases in resilience (Figure \@ref(fig:div-temp-meth1)).
+This result is different to the effect of diversity within the CB and SB functional groups, which both cause increases in resilience of the state that they dominate (Figure \@ref(fig:div-temp-meth1)).
 Why does diversity in the PB functional group reduce the resilience of the state it dominates?
 
-The phototrophic sulfur bacteria (PB) in the model ecosystem produce oxidised sulfur compounds (SO), and consume reduced sulfur compounds (SR).
-Since SR inhibits the cyanobacteria, PB can have a positive effect on CB via their consumption of SR.
-Hence, high growth rates of PB will have a positive effect on on CB, and therefore favour the oxic state.
-We would expect to see that higher diversity of PB is associated with lower SR and higher SO before the transition.
+The counter-intuitive effect of diversity in the phototrophic sulfur bacteria (PB) possibly results from their positive effects on the oxic state.
+The phototrophic sulfur bacteria oxidise reduced sulfur to oxidised sulfur.
+Since reduced sulfur inhibits the cyanobacteria (CB), PB can have a positive effect on CB via their consumption of reduced sulfur Hence, high growth rates of PB will have a positive effect on CB, and therefore favour the oxic state.
+We would expect to see that higher diversity of PB is associated with lower concentrations of reduced sulfur and higher concentrations of oxidised sulfur before the transition.
 
-Another pathway by which higher PB growth rate can favour the oxic state is by PB inhibiting PB and SB (and thus favouring CB).
-This effect occurs because PB consumes SR, making less SR available for abiotic oxidation (SR + O -> SO).
-Reduced abiotic oxidation leaves greater amounts of O in the environment, and O inhibits.
-We would expect to see that higher diversity of PB is associated with higher O before the transition.
+Another pathway by which a higher growth rate of PB can favour the oxic state is by indirectly increasing the concentration of oxygen, thus inhibiting themselves and sulfate-reducing bacteria.
+This effect occurs because PB consume reduced sulfur, such that less reduced sulfur is available for abiotic oxidation.
+Consequently, a larger amount of oxygen remains in the environment and inhibits sulfur bacteria.
+We would expect to see that higher diversity of PB is associated with higher concentrations of oxygen before the transition.
 
-There is, however, at least one pathway by which PB can favour the anoxic state. PB produces SO which is consumed by SB, and SB produce SR, which inhibits CB.
+There is, however, at least one pathway by which PB can favour the anoxic state: PB produce oxidised sulfur which is consumed by SB, and SB produce reduced sulfur, which inhibits CB.
 
-Looking at the strain replacement that occurs across the oxygen diffusivity gradient, we see that as oxygen diffusivity increases, then the more oxygen tolerant strains of PB replace the less tolerant ones.
-This is because these more tolerant strains have higher realised growth rates under the prevailing environmental conditions (even though they have lower maximum growth rate than lower tolerance strains).
-Having an even more tolerant strain available (which is what happens when there is greater PB diversity) gives the opportunity for even higher realised growth rates, which via the effect pathways mentioned above, can favour the oxic state.
+Looking at the strain replacement that occurs across the oxygen diffusivity gradient, we see that as oxygen diffusivity increases, the more oxygen tolerant strains of PB replace the less tolerant ones because they have higher realised growth rates under the prevailing environmental conditions.
+Greater PB diversity leads to the availability of strains with higher oxygen tolerance and thus even higher realised growth rates, which via the pathways described above, can favour the oxic state.
 
-The expected effects of having a more PB tolerant strain (because there is higher PB diversity) is shown in Figure \@ref(fig:pbdiv-only-3)).
-As the transition is approached, higher PB diversity leads to higher oxygen concentration, higher SO concentration, and lower SR concentration, than in a simulation with lower PB diversity.
-All these differences in substrate concentrations are in the direction of favouring the oxic state, and thus the system transitions earlier to the oxic state.
+Substrate concentrations close to the anoxic-oxic transition in simulations with low and high PB diversity, respectively, corroborate the expected effects (Figure \@ref(fig:pbdiv-only-3)).
+As the transition is approached, higher PB diversity leads to higher concentration of oxygen, higher concentration of oxidised sulfur (SO), and lower concentration of reduced sulfur (SR), than a simulation with lower PB diversity.
+All these differences in substrate concentrations are in the direction of favouring the oxic state, resulting in the earlier transition to the oxic state.
 
-(ref:pbdiv-only-3) Concentrations of three substrates (one in each panel) in a low PB diversity simulation (x-axis) versus concentration in a high PB diversity simuation (y-axis).
-Only a small range of oxygen diffusivity is show, and result only shown for increasing oxygen diffusivity.
+(ref:pbdiv-only-3) Concentrations of three substrates (O: oxygen; SO: oxidised sulfur; SR: reduced sulfur) in a low PB diversity simulation (x-axis) versus substrate concentration in a high PB diversity simulation (y-axis).
+The figures show only a small range of oxygen diffusivity on the trajectory of increasing oxygen diffusivity.
 The black line is the 1:1 line.
@@
 
-There still remains the question of why the effect of PB diversity saturates.
-We don't currently have a good explanation for this, just as we don't have good explanations for other effects of diversity that are non-linear.
+# Effect of number of strains
 
-# Effect of number of strains
+In the main text, we present results of simulations with nine strains per functional group.
+Here we also explore the effect of number of strains (2, 3, 6, 9) on the position of the two tipping points (Figure \@ref(fig:div-stab-multstrain1)).
+At low to moderate amounts of trait variation, the number of strains did not affect the position of the tipping points.
+However, at high amounts of trait variation, resilience was lower when the functional groups had only two or three strains rather than six or nine.
+This effect was particularly pronounced when there was high variation in only SB or in SB-CB: here, simulations with two or three strains led to dramatically lower resilience of the anoxic state than simulations with six or nine strains.
+We believe that this effect is due to the greater distance in trait space between strains in simulations with two or three strains than in simulations with more strains (also see Section 5).
 
@@
 If the system has initial cyanobacterial abundance greater than the value at the separatrix then the cyanobacterial abundance increases, and the system goes to the oxic stable state.
-Conversely, if the system has initial cyanobacterial abundance greater than the value at the separatrix then the cyanobacterial abundance decreases, and the system goes to the anoxic stable state.
+Conversely, if the system has initial cyanobacterial abundance lower than the value at the separatrix then the cyanobacterial abundance decreases, and the system goes to the anoxic stable state.
 
@@
 And we would need to specify the total and relative abundance of all cyanobacteria (and sulfur bactria) strains.
-Thus, with a system as complex as the 9 strain system, which has 31 state variables the separatrix is very high dimensional, and evaluating (and plotting) it in one dimension requires many assumption.
+Thus, with a system as complex as the 9 strain system, which has 31 state variables the separatrix is very high dimensional, and evaluating (and plotting) it in one dimension requires many assumptions.
 We chose to not attempt to find a meaningful set of assumptions in this study, though not because we think it would be unprofitable to do so, but rather because we did not want to risk distracting attention from findings we consider to be significant enough in the own right.

### 2022-03-29 experiments/2_supplement/supplement.Rmd

@@
 The phototrophic sulfur bacteria oxidise reduced sulfur to oxidised sulfur.
-Since reduced sulfur inhibits the cyanobacteria (CB), PB can have a positive effect on CB via their consumption of reduced sulfur Hence, high growth rates of PB will have a positive effect on CB, and therefore favour the oxic state.
+Since reduced sulfur inhibits the cyanobacteria (CB), PB can have a positive effect on CB via their consumption of reduced sulfur.
+Hence, high growth rates of PB will have a positive effect on CB, and therefore favour the oxic state.
 We would expect to see that higher diversity of PB is associated with lower concentrations of reduced sulfur and higher concentrations of oxidised sulfur before the transition.
@@
   geom_abline(intercept = 0, slope = 1) +
-  xlab("Log10(Concentration)\nLow PB diversity") +
-  ylab("Log10(Concentration)\nHigh PB diversity") +
-  labs(col="Log10(Oxygen diffusivity)") +
+  xlab("log10(concentration) (µM)\nLow PB diversity") +
+  ylab("log10(concentration) (µM)\nHigh PB diversity") +
+  labs(col=expression(paste("log"[10],"(oxygen diffusivity) (h"^{-1}, ")"))) +
   theme_bw() +

### 2022-03-30 experiments/2_supplement/supplement.Rmd
Next step Graphs Appendix

@@
 sim_res_novar1 <- readRDS(here::here("data", "2_supplement", "puzzle1_1.RDS"))
-plot_dynamics(sim_res_novar1)
+p <- plot_dynamics(sim_res_novar1)
+p[[1]] <- p[[1]] + 
+  xlab(NULL) + 
+  ylab(expression(log[10](density)(cells~L^{-1})))
+p[[2]] <- p[[2]] + 
+  xlab(NULL) + 
+  ylab(expression(log[10](density)(cells~L^{-1})))
+p[[3]] <- p[[3]] + 
+  xlab(NULL) + 
+  ylab(expression(log[10](density)(cells~L^{-1})))
+p[[4]] <- p[[4]] + 
+  xlab("time(h)") + 
+  ylab(expression(log[10](concentration)(µM))) + 
+  labs(colour = "substrate")
+
+p
 #ggsave(here("simulations", "expt2", "figures", "switching_novar.pdf"), width = 10)
@@
   geom_abline(intercept = 0, slope = 1) +
-  xlab("log10(concentration) (µM)\nLow PB diversity") +
-  ylab("log10(concentration) (µM)\nHigh PB diversity") +
+  xlab(expression(atop(log[10](concentration)~(µM), Low~PB~diversity))) +
+  ylab(expression(atop(log[10](concentration)~(µM),High~PB~diversity))) +
   labs(col=expression(paste("log"[10],"(oxygen diffusivity) (h"^{-1}, ")"))) +
@@
   theme(legend.position="top")
-
 ```

### 2022-03-30 R/ms_figure_functions.R

@@ -239,7 +239,7 @@ fig_div_vs_o2diff_multistrain <- function(all_stab,
                     fill = as.factor(num_strains)), alpha = 0.2) +
     facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
     xlab("Standardised amount of trait variation") +
-    ylab("Oxygen diffusivity\n[log10 uM per hour]") +
+    ylab(expression(log[10](Oxygen~diffusivity)~(h^{-1}))) +
     #labs(fill = "Variation in\nonly these\nfunctional groups") +
     coord_flip() +
     guides(col = guide_legend(title="Number of strains"),

### 2022-03-30 experiments/2_supplement/supplement.Rmd
change title of supplement

@@
 ---
-title: Supplementary Content
-subtitle: ??????Insert ms title???????
-author: "Owen L Petchey, Rainer Krug, Marcel Suleiman, Romana Limberger, ???others???"
+title: Supplementary Content for the article *The role of functional diversity in ecosystem regime shifts*
+author: "Owen L Petchey, plus all authors of the main article"
 date: "`r format(Sys.time(), '%d %B, %Y')`"

### 2022-03-31 experiments/2_supplement/supplement.Rmd
Update Supplement

@@
 sim_res_highvar1 <- readRDS(here("data", "2_supplement", "puzzle1_2.RDS"))
-plot_dynamics(sim_res_highvar1)
+
+p <- plot_dynamics(sim_res_highvar1)
+p[[1]] <- p[[1]] + 
+  xlab(NULL) + 
+  ylab(expression(log[10](density)(cells~L^{-1})))
+p[[2]] <- p[[2]] + 
+  xlab(NULL) + 
+  ylab(expression(log[10](density)(cells~L^{-1})))
+p[[3]] <- p[[3]] + 
+  xlab(NULL) + 
+  ylab(expression(log[10](density)(cells~L^{-1})))
+p[[4]] <- p[[4]] + 
+  xlab("time(h)") + 
+  ylab(expression(log[10](concentration)(µM))) + 
+  labs(colour = "substrate")
+
+p
+
 #ggsave(here("simulations", "expt2", "figures", "switching_novar.pdf"), width = 10)

### 2022-04-04 experiments/2_supplement/supplement.Rmd
Some more changes - DOES NOT WORK AT THE MOMENT!

@@
 
-```{r repl-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:repl-meth2)', fig.height=8, fig.width=8, fig.align="center"}
-fig_state_vs_o2diff_sidebyside_dots(repl_meth[1,])
+```{r repl-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:repl-meth2)', fig.height=10, fig.width=8, fig.align="center"}
+fig_state_vs_o2diff_sidebyside_alternative(repl_meth[1,])
 ```
@@
 
-```{r temp-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:temp-meth2)', fig.height=8, fig.width=8, fig.align="center"}
-fig_state_vs_o2diff_sidebyside_dots(temp_meth[1,])
+```{r temp-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:temp-meth2)', fig.height=10, fig.width=8, fig.align="center"}
+fig_state_vs_o2diff_sidebyside_alternative(temp_meth[1,])
 ```
@@
 
-```{r repl-meth-ex1, echo = FALSE,  include=TRUE, fig.cap='(ref:repl-meth-ex1)', fig.height=8, fig.width=8, fig.align="center"}
+```{r repl-meth-ex1, echo = FALSE,  include=TRUE, fig.cap='(ref:repl-meth-ex1)', fig.height=10, fig.width=8, fig.align="center"}
 repl_meth <- readRDS(here("data", "0_ss_finding", "replication_method", "ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
-fig_state_vs_o2diff_sidebyside_dots(repl_meth[94,])
+fig_state_vs_o2diff_sidebyside_alternative(repl_meth[94,])
 ```
@@
 
-```{r ss-temp-meth3, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth3)', fig.height=8, fig.width=8, fig.align="center"}
+```{r ss-temp-meth3, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth3)', fig.height=10, fig.width=8, fig.align="center"}
 single_1e6 <- readRDS(here("data", "0_ss_finding", "temporal_method", "single_1e6_result.RDS"))
 temp_meth[1,]$ssfind_result[[1]] <- single_1e6
-fig_state_vs_o2diff_sidebyside_dots(temp_meth[1,])
+fig_state_vs_o2diff_sidebyside_alternative(temp_meth[1,])
 ```
@@
 
-```{r ss-temp-meth4, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth4)', fig.height=8, fig.width=8, fig.align="center"}
+```{r ss-temp-meth4, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth4)', fig.height=10, fig.width=8, fig.align="center"}
 single_2e6 <- readRDS(here("data", "0_ss_finding", "temporal_method", "single_2e6_result.RDS"))
 temp_meth[1,]$ssfind_result[[1]] <- single_2e6
-fig_state_vs_o2diff_sidebyside_dots(temp_meth[1,])
+fig_state_vs_o2diff_sidebyside_alternative(temp_meth[1,])
 ```
@@
 
-```{r ss-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth1)', fig.height=8, fig.width=8, fig.align="center"}
+```{r ss-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth1)', fig.height=10, fig.width=8, fig.align="center"}
 wait_time <- "1e+04"
@@
 
-fig_state_vs_o2diff_sidebyside_dots(only_SB_variable[13,])
+fig_state_vs_o2diff_sidebyside_alternative(only_SB_variable[13,])
 
@@
 
-```{r ss-temp-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth2)', fig.height=8, fig.width=8, fig.align="center"}
-fig_state_vs_o2diff_sidebyside_dots(only_SB_variable[14,])
+```{r ss-temp-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth2)', fig.height=10, fig.width=8, fig.align="center"}
+fig_state_vs_o2diff_sidebyside_alternative(only_SB_variable[14,])
 ```
@@
   xlab(NULL) + 
-  ylab(expression(log[10](density)(cells~L^{-1})))
+  ylab(expression(log[10](density)~(cells~L^{-1}))) +
+  theme_bw()
 p[[2]] <- p[[2]] + 
   xlab(NULL) + 
-  ylab(expression(log[10](density)(cells~L^{-1})))
+  ylab(expression(log[10](density)~(cells~L^{-1}))) +
+  theme_bw()
 p[[3]] <- p[[3]] + 
   xlab(NULL) + 
-  ylab(expression(log[10](density)(cells~L^{-1})))
+  ylab(expression(log[10](density)~(cells~L^{-1}))) +
+  theme_bw()
+p[[4]]$data <- p[[4]]$data %>% 
+  dplyr::filter(species != "a") %>%
+  dplyr::recode(SO = "Oxidised sulfur", O = "Oxygen", SR = "Sulfide")
 p[[4]] <- p[[4]] + 
-  xlab("time(h)") + 
-  ylab(expression(log[10](concentration)(µM))) + 
-  labs(colour = "substrate")
+  xlab("time (h)") + 
+  ylab(expression(log[10](concentration)~(µM))) + 
+  labs(colour = "substrate") +
+  theme_bw()
 
@@
   xlab(NULL) + 
-  ylab(expression(log[10](density)(cells~L^{-1})))
+  ylab(expression(log[10](density)~(cells~L^{-1}))) +
+  theme_bw()
 p[[2]] <- p[[2]] + 
   xlab(NULL) + 
-  ylab(expression(log[10](density)(cells~L^{-1})))
+  ylab(expression(log[10](density)~(cells~L^{-1}))) +
+  theme_bw()
 p[[3]] <- p[[3]] + 
   xlab(NULL) + 
-  ylab(expression(log[10](density)(cells~L^{-1})))
+  ylab(expression(log[10](density)~(cells~L^{-1}))) +
+  theme_bw()
+p[[4]]$data <- p[[4]]$data %>% dplyr::filter(species != "a")
 p[[4]] <- p[[4]] +
-  xlab("time(h)") + 
-  ylab(expression(log[10](concentration)(µM))) + 
-  labs(colour = "substrate")
+  xlab("time (h)") + 
+  ylab(expression(log[10](concentration)~(µM))) + 
+  labs(colour = "substrate") +
+  theme_bw()
 
@@
 
-```{r pbdiv-only-1, echo = FALSE,  include=TRUE, fig.cap='(ref:pbdiv-only-1)', fig.height=8, fig.width=8, fig.align="center"}
-fig_state_vs_o2diff_sidebyside_dots(only_PB_variable[sim1,])
+```{r pbdiv-only-1, echo = FALSE,  include=TRUE, fig.cap='(ref:pbdiv-only-1)', fig.height=10, fig.width=8, fig.align="center"}
+fig_state_vs_o2diff_sidebyside_alternative(only_PB_variable[sim1,])
 ```
@@
 
-```{r pbdiv-only-2, echo = FALSE,  include=TRUE, fig.cap='(ref:pbdiv-only-2)', fig.height=8, fig.width=8, fig.align="center"}
-fig_state_vs_o2diff_sidebyside_dots(only_PB_variable[sim2,])
+```{r pbdiv-only-2, echo = FALSE,  include=TRUE, fig.cap='(ref:pbdiv-only-2)', fig.height=10, fig.width=8, fig.align="center"}
+fig_state_vs_o2diff_sidebyside_alternative(only_PB_variable[sim2,])
 ```

### 2022-04-04 R/various_useful_functions.r

@@ -390,7 +390,7 @@ display_diversity <- function(
   
   CB_TO1 <- ggplot(CBtraits) +
     geom_point(aes(x = h_SR_CB, y = g_max_CB, col = strain_name), size = ptsize) +
-    xlab("Tolerance reduced sulphur(µM)") +
+    xlab("Tolerance of sulfide\n(µM)") +
     ylab(expression(Maximum~growth~rate~(h^{-1}))) +
     scale_colour_manual(values = colfunc_CB(num_CB_strains)) +
     theme_bw() +
@@ -401,7 +401,7 @@ display_diversity <- function(
     theme_bw() +
     geom_line(aes(x = log10(SR), y = gr_rateCB1), col = colfunc_CB(num_CB_strains)[1], size = linewd) +
     geom_line(aes(x = log10(SR), y = gr_rateCB9), col = colfunc_CB(num_CB_strains)[num_CB_strains], size = linewd) +
-    xlab(expression(atop(log[10](red.~sulfur~concentration),(µM)))) +
+    xlab(expression(atop(log[10](sulfide~concentration),(µM)))) +
     ylab(expression(Realised~growth~rate~(h^{-1}))) +
     ggtitle(waiver(), "Cyanobacteria")
   
@@ -420,7 +420,7 @@ display_diversity <- function(
 
   SB_TO1 <- ggplot(SBtraits) +
     geom_point(aes(x = h_O_SB, y = g_max_SB, col = strain_name), size = ptsize) +
-    xlab("Tolerance of oxygen (µM)") +
+    xlab("Tolerance of oxygen\n(µM)") +
     ylab(NULL) +
     scale_colour_manual(values = colfunc_SB(num_SB_strains)) +
     theme_bw() +
@@ -431,7 +431,7 @@ display_diversity <- function(
     theme_bw() +
     geom_line(aes(x = log10(O), y = gr_rateSB1), col = colfunc_SB(num_SB_strains)[1], size = linewd) +
     geom_line(aes(x = log10(O), y = gr_rateSB9), col = colfunc_SB(num_SB_strains)[num_SB_strains], size = linewd) +
-    xlab(expression(atop(log[10](red.~oxygen~concentration),(µM)))) +
+    xlab(expression(atop(log[10](oxygen~concentration),(µM)))) +
     ylab(NULL) +
     ggtitle(waiver(), "Sulfate-reducing bacteria")
   
[…]

### 2022-05-20 experiments/2_supplement/supplement.Rmd

@@
 p[[4]]$data <- p[[4]]$data %>% 
-  dplyr::filter(species != "a") %>%
-  dplyr::recode(SO = "Oxidised sulfur", O = "Oxygen", SR = "Sulfide")
+  dplyr::filter(species != "a")
+p[[4]]$data$species <- p[[4]]$data$species %>%
+  dplyr::recode(SO = "Oxidised sulfur", O = "Oxygen", SR = "Sulfide", P = "Phosphorus")
 p[[4]] <- p[[4]] + 
@@
 p[[4]]$data <- p[[4]]$data %>% dplyr::filter(species != "a")
+p[[4]]$data$species <- p[[4]]$data$species %>%
+  dplyr::recode(SO = "Oxidised sulfur", O = "Oxygen", SR = "Sulfide", P = "Phosphorus")
 p[[4]] <- p[[4]] +
@@
 
+dd$State_variable <- dd$State_variable %>%
+  dplyr::recode(SO = "Oxidised sulfur", O = "Oxygen", SR = "Sulfide", P = "Phosphorus")
+
 dd %>%
-  filter(State_variable %in% c("O", "SR", "SO"),
+  filter(State_variable %in% c("Oxygen", "Sulfide", "Oxidised sulfur"),
          direction == "up",

### 2022-05-31 experiments/2_supplement/supplement.Rmd
Move Fig 5 from figures_main_ms.R to Supplement

@@
 We chose to not attempt to find a meaningful set of assumptions in this study, though not because we think it would be unprofitable to do so, but rather because we did not want to risk distracting attention from findings we consider to be significant enough in the own right.
+
+# Previously figure 5 Main Manuscript
+```{r fig_5_log, echo = FALSE,  include=TRUE, fig.cap='Previously figure 5 Main Manuscript log', fig.height=8, fig.width=8, fig.align="center"}
+## Figure 5 ----
+## Assessing additivity of diversity effect sizes
+## By Uriah
+## Owen switched to SB_tot
+
+all_stab_results_small <- readRDS(here("data/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS"))
+
+wait_time <- 1e6
+all_stab_results9 <- all_stab_results_small %>%
+  distinct() %>%  #there are some duplicated rows....? yes, some treatment combs were repeated when sub1 was made
+  filter(num_strains == 9,
+         Species == "SB_tot",
+         waittime == wait_time)
+
+all_stab_results9 <- all_stab_results9[with(all_stab_results9, order(var_treat, var_gmax)),]
+
+all_stab_results9$method <- "Simulated"
+
+### Things used for plotting ----
+
+### Fig 5 - log ----
+
+agg_stab_strain9 <- combine_fct("EF_log")
+
+agg_stab_strain9_temp <- agg_stab_strain9 %>%
+  dplyr::filter(var_treat=="CB-SB-PB")
+
+agg_stab_strain9 <- agg_stab_strain9 %>%
+  dplyr::filter(var_treat!="CB-SB-PB")
+
+agg_stab_strain9 <- rbind(agg_stab_strain9,
+                          agg_stab_strain9_temp %>% filter(method %in% c("CB+SBPB","Simulated")) %>% mutate(var_treat="CB-SB-PB & CB+SBPB"),
+                          agg_stab_strain9_temp %>% filter(method %in% c("PB+CBSB","Simulated")) %>% mutate(var_treat="CB-SB-PB & PB+CBSB"),
+                          agg_stab_strain9_temp %>% filter(method %in% c("SB+CBPB","Simulated")) %>% mutate(var_treat="CB-SB-PB & SB+CBPB"))
+
+agg_stab_strain9 <- agg_stab_strain9 %>%
+  mutate(method2 = ifelse(agg_stab_strain9$method=="Simulated","Simulated","Calculated")) %>%
+  rename(Calculation=method, Method=method2)%>%
+  mutate(Calculation = factor(Calculation, levels = c("Simulated","CB+SB","CB+PB","SB+PB",
+                                                      "CB+SBPB","PB+CBSB","SB+CBPB")),
+         Method = factor(Method, levels = c("Simulated","Calculated")))
+
+# the legend
+fig5legend <- agg_stab_strain9 %>%
+  filter(Species == "SB_tot", num_strains==9) %>%
+  ggplot(aes(x = stand_var, linetype=Method, col=Calculation)) +
+  geom_line(aes(y = hyst_min_log), size = 1) +
+  geom_line(aes(y = hyst_max_log), size = 1) +
+  scale_color_manual(values = c("black","#e41a1c","#377eb8","#4daf4a","#984ea3","#ff7f00","#a65628")) +
+  scale_linetype_manual(values = c(1,2))+
+  coord_flip() +
+  theme_bw() +
+  theme(legend.position="right")
+
+fig5legend <- ggpubr::get_legend(fig5legend)
+
+# the y and x labels
+# ylab <- ggplot(data.frame(l = "            Standardised amount of trait variation", x = 1, y = 4.1)) +
+ylab <- ggplot(data.frame(l = "Standardised amount of trait variation", x = 1, y = 4.1)) +
+  geom_text(aes(x, y, label = l), angle = 90, size=4.5) + 
+  theme_void() +
+  coord_cartesian(clip = "off")
+
+xlab <- ggplot(data.frame(x = 1, y = 1)) +
+  geom_text(aes(x, y), label = expression('log'[10]*"(oxygen diffusivity) (h"^{-1}*")"), size=4.5) + 
+  theme_void() +
+  coord_cartesian(clip = "off")
+
+# colours and tags used
+colours <- c(Simulated="black",`CB+SB`="#e41a1c",`CB+PB`="#377eb8",
+             `SB+PB`="#4daf4a",`CB+SBPB`="#984ea3",`PB+CBSB`="#ff7f00",
+             `SB+CBPB`="#a65628")
+
+tags <- c(`CB`="a",`SB`="b",`PB`="c",
+          `CB-SB`="d",`CB-PB`="e",`SB-PB`="f",
+          `CB-SB-PB & CB+SBPB`="g",`CB-SB-PB & PB+CBSB`="h",`CB-SB-PB & SB+CBPB`="i")
+
+# The figure
+
+fig5_log <- split(agg_stab_strain9, f=agg_stab_strain9$var_treat, drop = T)
+
+fig5_log <- lapply(fig5_log, function(df){
+  tag <- tags[as.character(unique(df$var_treat))]
+  plot <- df %>%
+    filter(Species == "SB_tot", num_strains==9) %>%
+    ggplot(aes(x = stand_var, linetype=Method, col=Calculation)) +
+    geom_hline(yintercept = c(-8, 0), col = "black", linetype=3) +
+    geom_line(aes(y = hyst_min_log), size = 1) +
+    geom_line(aes(y = hyst_max_log), size = 1) +
+    facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
+    labs(y="Oxygen diffusivity\n[log10 uM per hour]",
+         x="Amount of trait variation\n[see text for units]",
+         linetype="Method",col="Calculation", tag=tag) +
+    scale_color_manual(values = colours[unique(df$Calculation)]) +
+    scale_linetype_manual(values = c(1,2))+
+    coord_flip() +
+    theme_bw()+
+    theme(legend.position="none",
+          axis.title = element_blank(),
+          axis.ticks = element_blank(),
+          axis.text = element_blank())
+
+  if(tag %in% c("a","d")){
+    plot <- plot + theme(axis.text.y = element_text(),
+                         axis.ticks.y = element_line())
+  }
+  if(tag %in% c("h","i")){
+    plot <- plot + theme(axis.text.x = element_text(),
+                         axis.ticks.x = element_line())
+  }
+  if(tag == "g"){
+    plot <- plot + theme(axis.text = element_text(),
+                         axis.ticks = element_line())
+  }
+  plot
+})
+
+ylab + Reduce("+",fig5_log) + fig5legend +
+  plot_spacer() + xlab + plot_spacer() +
+  plot_layout(ncol = 3, heights = c(25,1), widths = c(1,21,3))
+
+# ggsave(here("experiments/1_figures_main_ms/Figure_5_log.pdf"),
+#        width = 8, height = 8)
+
+```
+
+```{r fig_5_linear, echo = FALSE,  include=TRUE, fig.cap='Previously figure 5 Main Manuscript linear', fig.height=8, fig.width=8, fig.align="center"}
+
+### Fig 5 - linear ----
+
+agg_stab_strain9 <- combine_fct("EF_lin")
+
+agg_stab_strain9_temp <- agg_stab_strain9 %>%
+  dplyr::filter(var_treat=="CB-SB-PB")
+
+agg_stab_strain9 <- agg_stab_strain9 %>%
+  dplyr::filter(var_treat!="CB-SB-PB")
+
+agg_stab_strain9 <- rbind(agg_stab_strain9,
+                          agg_stab_strain9_temp %>% filter(method %in% c("CB+SBPB","Simulated")) %>% mutate(var_treat="CB-SB-PB & CB+SBPB"),
+                          agg_stab_strain9_temp %>% filter(method %in% c("PB+CBSB","Simulated")) %>% mutate(var_treat="CB-SB-PB & PB+CBSB"),
+                          agg_stab_strain9_temp %>% filter(method %in% c("SB+CBPB","Simulated")) %>% mutate(var_treat="CB-SB-PB & SB+CBPB"))
+
+agg_stab_strain9 <- agg_stab_strain9 %>%
+  mutate(method2 = ifelse(agg_stab_strain9$method=="Simulated","Simulated","Calculated")) %>%
+  rename(Calculation=method, Method=method2)%>%
+  mutate(Calculation = factor(Calculation, levels = c("Simulated","CB+SB","CB+PB","SB+PB",
+                                                      "CB+SBPB","PB+CBSB","SB+CBPB")),
+         Method = factor(Method, levels = c("Simulated","Calculated")))
+
+fig5_lin <- split(agg_stab_strain9, f=agg_stab_strain9$var_treat, drop = T)
+
+fig5_lin <- lapply(fig5_lin, function(df){
+  tag <- tags[as.character(unique(df$var_treat))]
+  plot <- df %>%
+    filter(Species == "SB_tot", num_strains==9) %>%
+    ggplot(aes(x = stand_var, linetype=Method, col=Calculation)) +
+    geom_hline(yintercept = c(-8, 0), col = "black", linetype=3) +
+    geom_line(aes(y = hyst_min_log), size = 1) +
+    geom_line(aes(y = hyst_max_log), size = 1) +
+    facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
+    labs(y="Oxygen diffusivity\n[log10 uM per hour]",
+         x="Amount of trait variation\n[see text for units]",
+         linetype="Method",col="Calculation", tag=tag) +
+    scale_color_manual(values = colours[unique(df$Calculation)]) +
+    scale_linetype_manual(values = c(1,2))+
+    coord_flip() +
+    theme_bw()+
+    theme(legend.position="none",
+          axis.title = element_blank(),
+          axis.ticks = element_blank(),
+          axis.text = element_blank())
+
+  if(tag %in% c("a","d")){
+    plot <- plot + theme(axis.text.y = element_text(),
+                         axis.ticks.y = element_line())
+  }
+  if(tag %in% c("h","i")){
+    plot <- plot + theme(axis.text.x = element_text(),
+                         axis.ticks.x = element_line())
+  }
+  if(tag == "g"){
+    plot <- plot + theme(axis.text = element_text(),
+                         axis.ticks = element_line())
+  }
+  plot
+})
+
+ylab + Reduce("+",fig5_lin) + fig5legend +
+  plot_spacer() + xlab + plot_spacer() +
+  plot_layout(ncol = 3, heights = c(25,1), widths = c(1,21,3))
+
+# ggsave(here("experiments/1_figures_main_ms/Figure_5_lin.pdf"),
+#        width = 8, height = 8)
+```

### 2022-06-01 R/ms_figure_functions.R
requested changes to figures done

@@ -900,110 +900,27 @@ fig_state_vs_o2diff_sidebyside_alternative <- function(ss_result){
 
 
 fig_resilience_vs_div <- function(all_stab, which_strain, figure_title) {
-  
-  # CB_vars <- unique(all_stab$CB_var_gmax_s)
-  # SB_vars <- unique(all_stab$SB_var_gmax_s)
-  # PB_vars <- unique(all_stab$PB_var_gmax_s)
-  # 
-  # CB_all_stab <- all_stab %>%
-  #   filter(SB_var_gmax_s == 0,
-  #          PB_var_gmax_s == 0) %>%
-  #   ungroup() %>%
-  #   mutate(var_treat = "CB",
-  #          var_gmax = CB_var_gmax_s,
-  #          stand_var = var_gmax / max(var_gmax))
-  # SB_all_stab <- all_stab %>%
-  #   filter(CB_var_gmax_s == 0,
-  #          PB_var_gmax_s == 0)  %>%
-  #   ungroup() %>%
-  #   mutate(var_treat = "SB",
-  #          var_gmax = SB_var_gmax_s,
-  #          stand_var = var_gmax / max(var_gmax))
-  # PB_all_stab <- all_stab %>%
-  #   filter(CB_var_gmax_s == 0,
-  #          SB_var_gmax_s == 0) %>%
-  #   ungroup()  %>%
-  #   mutate(var_treat = "PB",
-  #          var_gmax = PB_var_gmax_s,
-  #          stand_var = var_gmax / max(var_gmax))
-  # 
-  # for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
-  #                    SB_var_gmax_s = sort(SB_vars))
-  # CBSB_all_stab <- all_stab %>%
-  #   right_join(for_join)  %>%
-  #   ungroup() %>%
-  #   mutate(var_treat = "CB-SB",
-  #          var_gmax = CB_var_gmax_s,
-  #          stand_var = var_gmax / max(var_gmax)) %>%
-  #   filter(PB_var_gmax_s == 0)
-  # 
-  # for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
-  #                    PB_var_gmax_s = sort(PB_vars))
-  # CBPB_all_stab <- all_stab %>%
-  #   right_join(for_join)  %>%
-  #   ungroup() %>%
-  #   mutate(var_treat = "CB-PB",
[…]

### 2022-06-02 experiments/2_supplement/supplement.Rmd
requested changes to figures done
changes to supplement

@@
 title: Supplementary Content for the article *The role of functional diversity in ecosystem regime shifts*
-author: "Owen L Petchey, plus all authors of the main article"
+author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
 date: "`r format(Sys.time(), '%d %B, %Y')`"
@@
 
-plot_ss_result6(repl_method_1,
+plot_ss_result6_new(repl_method_1,
                     temp_meth$ssfind_result[[1]],
@@
 
-# Previously figure 5 Main Manuscript
+# (Non-)additivity
+
+We investigated if the effects of trait variation of individual functional groups were additive.
+We compared the tipping point positions as determined by our simulations with the expected position of the respective tipping point if effects of diversity in different functional groups were additive.
+The expected tipping point was calculated by adding the effect sizes (i.e.
+the difference in tipping point position between the no-diversity scenario and a given amount of trait variation) on a linear scale.
+
 ```{r fig_5_log, echo = FALSE,  include=TRUE, fig.cap='Previously figure 5 Main Manuscript log', fig.height=8, fig.width=8, fig.align="center"}
@@
 
-fig5_log <- lapply(fig5_log, function(df){
-  tag <- tags[as.character(unique(df$var_treat))]
-  plot <- df %>%
-    filter(Species == "SB_tot", num_strains==9) %>%
-    ggplot(aes(x = stand_var, linetype=Method, col=Calculation)) +
-    geom_hline(yintercept = c(-8, 0), col = "black", linetype=3) +
-    geom_line(aes(y = hyst_min_log), size = 1) +
-    geom_line(aes(y = hyst_max_log), size = 1) +
-    facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
-    labs(y="Oxygen diffusivity\n[log10 uM per hour]",
-         x="Amount of trait variation\n[see text for units]",
-         linetype="Method",col="Calculation", tag=tag) +
-    scale_color_manual(values = colours[unique(df$Calculation)]) +
-    scale_linetype_manual(values = c(1,2))+
-    coord_flip() +
-    theme_bw()+
-    theme(legend.position="none",
-          axis.title = element_blank(),
-          axis.ticks = element_blank(),
-          axis.text = element_blank())
-
-  if(tag %in% c("a","d")){
-    plot <- plot + theme(axis.text.y = element_text(),
-                         axis.ticks.y = element_line())
-  }
-  if(tag %in% c("h","i")){
-    plot <- plot + theme(axis.text.x = element_text(),
-                         axis.ticks.x = element_line())
-  }
-  if(tag == "g"){
-    plot <- plot + theme(axis.text = element_text(),
-                         axis.ticks = element_line())
-  }
-  plot
-})
-
-ylab + Reduce("+",fig5_log) + fig5legend +
-  plot_spacer() + xlab + plot_spacer() +
-  plot_layout(ncol = 3, heights = c(25,1), widths = c(1,21,3))
+# fig5_log <- lapply(fig5_log, function(df){
+#   tag <- tags[as.character(unique(df$var_treat))]
+#   plot <- df %>%
+#     filter(Species == "SB_tot", num_strains==9) %>%
+#     ggplot(aes(x = stand_var, linetype=Method, col=Calculation)) +
+#     geom_hline(yintercept = c(-8, 0), col = "black", linetype=3) +
+#     geom_line(aes(y = hyst_min_log), size = 1) +
+#     geom_line(aes(y = hyst_max_log), size = 1) +
+#     facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
+#     labs(y="Oxygen diffusivity\n[log10 uM per hour]",
+#          x="Amount of trait variation\n[see text for units]",
+#          linetype="Method",col="Calculation", tag=tag) +
+#     scale_color_manual(values = colours[unique(df$Calculation)]) +
+#     scale_linetype_manual(values = c(1,2))+
+#     coord_flip() +
+#     theme_bw()+
+#     theme(legend.position="none",
+#           axis.title = element_blank(),
+#           axis.ticks = element_blank(),
+#           axis.text = element_blank())
+#   
+#   if(tag %in% c("a","d")){
+#     plot <- plot + theme(axis.text.y = element_text(),
+#                          axis.ticks.y = element_line())
+#   }
+#   if(tag %in% c("h","i")){
+#     plot <- plot + theme(axis.text.x = element_text(),
+#                          axis.ticks.x = element_line())
+#   }
+#   if(tag == "g"){
+#     plot <- plot + theme(axis.text = element_text(),
+#                          axis.ticks = element_line())
+#   }
+#   plot
+# })
+# 
+# 
+# ylab + Reduce("+",fig5_log) + fig5legend +
+#   plot_spacer() + xlab + plot_spacer() +
+#   plot_layout(ncol = 3, heights = c(25,1), widths = c(1,21,3))
 
@@
 
-```{r fig_5_linear, echo = FALSE,  include=TRUE, fig.cap='Previously figure 5 Main Manuscript linear', fig.height=8, fig.width=8, fig.align="center"}
+```{r fig_5_linear, echo = FALSE,  include=TRUE, fig.height=8, fig.width=8, fig.align="center"}
 
@@
 ```
+
+(ref:fig_5_linear)  Figure 9.
+Assessing the additivity or non-additivity of the effects of trait variation.
+Solid black lines depict the position of the two tipping points at different levels of trait variation, as simulated with the model.
+The colored, dashed lines show the expected position of tipping points if effects of diversity in different functional groups were additive.
+The expected tipping point was calculated by adding the effect sizes of trait variation of different functional groups on a linear scale.
+For example, in (d) the effect size of variation in only CB was added to the effect size of variation in only SB.
+In (g), the effect size of variation in only CB was added to the effect size of simultaneous variation in both SB and PB.
+(CB: cyanobacteria, SB: sulfate-reducing bacteria, PB: phototrophic sulfur bacteria).
+The dotted vertical lines at -8 and 0 on the x-axis show the extent of the oxygen diffusivity gradient investigated in the simulations.
+
+When two functional groups varied in traits, the effects of trait variation were additive when one of the groups had no diversity effect on a tipping point but non-additive when both groups had diversity effects on a tipping point (Fig.
+9 a-f).
+High trait variation in cyanobacteria and sulfate-reducing bacteria caused the oxic-anoxic tipping point to occur at lower oxygen diffusivity than expected assuming additivity of the individual effects of diversity in these two groups (Fig.
+9d).
+When the two groups of sulfur bacteria varied in traits, the anoxic-oxic tipping point occurred at lower oxygen diffusivity than expected by additivity (Fig.
+9f).
+
+When all three groups varied in traits, only the diversity effect in phototrophic sulfur bacteria on the oxic-anoxic tipping point was additive; all other effects were non-additive, especially at higher trait variation (Fig.
+9g-i).
+Both tipping points occurred at lower levels of oxygen diffusivity than expected by additivity.
+Interestingly, diversity in the cyanobacteria moved the shift to the oxic state to lower levels of oxygen diffusivity although independent variation in the cyanobacteria had no effect on this tipping point.

### 2022-06-03 experiments/2_supplement/supplement.Rmd
editing supplement

@@
 
-This document contains the Supplementary Content for the report *?????????????*.
+This document contains the Supplementary Content for the report *information to be added once final*.
 
@@
 
-Here we provide additional description of the method used to create strain variation within functional groups. The following should be read only after the relevant sections of the main text. 
+Here we provide additional description of the method used to create strain variation within functional groups.
+The following should be read only after the relevant text in the main report.
 We generated variation in maximum growth rate $G_{max}$ and tolerance to reduced sulfur $h_{SR}$ or oxygen $h_{O}$ by varying the range of trait values around a reference trait value.
@@
 
-In the simulated microbial ecosystem, the strains are the stepping stones, and it is much hard (takes longer) for strains to replace each other when there is greater distance (in trait space) between them.
+In the simulated microbial ecosystem, the strains are the stepping stones, and it is harder (takes longer) for strains to replace each other when there is greater distance (in trait space) between them.
 When they can no longer replace each other in the time available, the system behaves as if only the least tolerant, highest growth rate strain (lightest shade of colour) is present.
@@
 And yet the switch to anoxic state occurs earlier than when there is no diversity, which suggests there is some role of the more tolerant strains.
-We here show that the most tolerant strain do play a role, but only a transient one.
+We here show that the more tolerant strains do play a role, but only a transient one.
 The following dynamics are for the system starting oxic, and with a value of oxygen diffusivity (log10(oxygen diffusivity) = -4.8) for which the system remains oxic if there is no diversity (Figure \@ref(fig:sb-div-effect3)), but switches to anoxic if there is diversity (Figure \@ref(fig:sb-div-effect4)).
@@
 
-(ref:sb-div-effect4) Dynamics of the system with diversity in the two groups of sulfur bacteria and otherwise exactly the same conditions as in Figure \@ref(fig:sb-div_effect3).
+(ref:sb-div-effect4) Dynamics of the system with diversity in the two groups of sulfur bacteria and otherwise exactly the same conditions as in Figure \@ref(fig:sb-div-effect3).
 The system flips from oxic to anoxic, whereas it did not when there was no diversity.
@@
 
-The counter-intuitive effect of diversity in the phototrophic sulfur bacteria (PB) possibly results from their positive effects on the oxic state.
+The counter-intuitive effect of diversity in the phototrophic sulfur bacteria (PB) possibly results from their positive effects on conditions and processes that favour the oxic state.
 The phototrophic sulfur bacteria oxidise reduced sulfur to oxidised sulfur.
@@
 Thus, with a system as complex as the 9 strain system, which has 31 state variables the separatrix is very high dimensional, and evaluating (and plotting) it in one dimension requires many assumptions.
-We chose to not attempt to find a meaningful set of assumptions in this study, though not because we think it would be unprofitable to do so, but rather because we did not want to risk distracting attention from findings we consider to be significant enough in the own right.
+We chose to not attempt to find a meaningful set of assumptions in this study, though not because we think it would be unprofitable to do so, but rather because we did not want to risk distracting attention from findings we consider to be significant enough in their own right.
 
@@
 
-```{r fig_5_log, echo = FALSE,  include=TRUE, fig.cap='Previously figure 5 Main Manuscript log', fig.height=8, fig.width=8, fig.align="center"}
+```{r fig-5-log, echo = FALSE,  include=TRUE, fig.cap='Previously figure 5 Main Manuscript log', fig.height=8, fig.width=8, fig.align="center"}
 ## Figure 5 ----
@@
 
-# fig5_log <- lapply(fig5_log, function(df){
-#   tag <- tags[as.character(unique(df$var_treat))]
-#   plot <- df %>%
-#     filter(Species == "SB_tot", num_strains==9) %>%
-#     ggplot(aes(x = stand_var, linetype=Method, col=Calculation)) +
-#     geom_hline(yintercept = c(-8, 0), col = "black", linetype=3) +
-#     geom_line(aes(y = hyst_min_log), size = 1) +
-#     geom_line(aes(y = hyst_max_log), size = 1) +
-#     facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
-#     labs(y="Oxygen diffusivity\n[log10 uM per hour]",
-#          x="Amount of trait variation\n[see text for units]",
-#          linetype="Method",col="Calculation", tag=tag) +
-#     scale_color_manual(values = colours[unique(df$Calculation)]) +
-#     scale_linetype_manual(values = c(1,2))+
-#     coord_flip() +
-#     theme_bw()+
-#     theme(legend.position="none",
-#           axis.title = element_blank(),
-#           axis.ticks = element_blank(),
-#           axis.text = element_blank())
-#   
-#   if(tag %in% c("a","d")){
-#     plot <- plot + theme(axis.text.y = element_text(),
-#                          axis.ticks.y = element_line())
-#   }
-#   if(tag %in% c("h","i")){
-#     plot <- plot + theme(axis.text.x = element_text(),
-#                          axis.ticks.x = element_line())
-#   }
-#   if(tag == "g"){
-#     plot <- plot + theme(axis.text = element_text(),
-#                          axis.ticks = element_line())
-#   }
-#   plot
-# })
-# 
-# 
-# ylab + Reduce("+",fig5_log) + fig5legend +
-#   plot_spacer() + xlab + plot_spacer() +
-#   plot_layout(ncol = 3, heights = c(25,1), widths = c(1,21,3))
-
-# ggsave(here("experiments/1_figures_main_ms/Figure_5_log.pdf"),
-#        width = 8, height = 8)
-
-```
-
-```{r fig_5_linear, echo = FALSE,  include=TRUE, fig.height=8, fig.width=8, fig.align="center"}
+```
+
+(ref:fig-add-linear) Assessing the additivity or non-additivity of the effects of trait variation.
+Solid black lines depict the position of the two tipping points at different levels of trait variation, as simulated with the model.
+The colored, dashed lines show the expected position of tipping points if effects of diversity in different functional groups were additive.
+The expected tipping point was calculated by adding the effect sizes of trait variation of different functional groups on a linear scale.
+For example, in (d) the effect size of variation in only CB was added to the effect size of variation in only SB.
+In (g), the effect size of variation in only CB was added to the effect size of simultaneous variation in both SB and PB.
+(CB: cyanobacteria, SB: sulfate-reducing bacteria, PB: phototrophic sulfur bacteria).
+The dotted vertical lines at -8 and 0 on the x-axis show the extent of the oxygen diffusivity gradient investigated in the simulations.
+
+```{r fig-add-linear, echo = FALSE,  include=TRUE, fig.height=8, fig.width=8, fig.align="center", fig.cap='(ref:fig-add-linear)'}
 
@@
 
-(ref:fig_5_linear)  Figure 9.
-Assessing the additivity or non-additivity of the effects of trait variation.
-Solid black lines depict the position of the two tipping points at different levels of trait variation, as simulated with the model.
-The colored, dashed lines show the expected position of tipping points if effects of diversity in different functional groups were additive.
-The expected tipping point was calculated by adding the effect sizes of trait variation of different functional groups on a linear scale.
-For example, in (d) the effect size of variation in only CB was added to the effect size of variation in only SB.
-In (g), the effect size of variation in only CB was added to the effect size of simultaneous variation in both SB and PB.
-(CB: cyanobacteria, SB: sulfate-reducing bacteria, PB: phototrophic sulfur bacteria).
-The dotted vertical lines at -8 and 0 on the x-axis show the extent of the oxygen diffusivity gradient investigated in the simulations.
-
 When two functional groups varied in traits, the effects of trait variation were additive when one of the groups had no diversity effect on a tipping point but non-additive when both groups had diversity effects on a tipping point (Fig.
-9 a-f).
+\@ref(fig:fig-add-linear) a-f).
 High trait variation in cyanobacteria and sulfate-reducing bacteria caused the oxic-anoxic tipping point to occur at lower oxygen diffusivity than expected assuming additivity of the individual effects of diversity in these two groups (Fig.
-9d).
+\@ref(fig:fig-add-linear)d).
 When the two groups of sulfur bacteria varied in traits, the anoxic-oxic tipping point occurred at lower oxygen diffusivity than expected by additivity (Fig.
-9f).
+\@ref(fig:fig-add-linear)f).
 
 When all three groups varied in traits, only the diversity effect in phototrophic sulfur bacteria on the oxic-anoxic tipping point was additive; all other effects were non-additive, especially at higher trait variation (Fig.
-9g-i).
+\@ref(fig:fig-add-linear)g-i).
 Both tipping points occurred at lower levels of oxygen diffusivity than expected by additivity.

### 2022-06-08 experiments/2_supplement/supplement.Rmd
changes supplement

@@
 ---
-title: Supplementary Content for the article *The role of functional diversity in ecosystem regime shifts*
+title: Supplementary Content for the article *Functional diversity can facilitate the collapse of an undesirable ecosystem state*
 author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
@@
 We generated variation in maximum growth rate $G_{max}$ and tolerance to reduced sulfur $h_{SR}$ or oxygen $h_{O}$ by varying the range of trait values around a reference trait value.
+To manipulate the amount of variation in a given trait and functional group, we introduced the meta-parameter $Div$ subscripted by the trait and the functional group.
 Take for example the cyanobacteria functional group, a reference maximum growth rate parameter $G_{max,CB}$ and a reference tolerance parameter $h_{SR,CB}$.
-Recall that amount of among strain variation is controlled by the two meta-parameters $Div_{G_{max,CB}}$ and $Div_{h_{SR,CB}}$.
+The amount of among strain variation in the cyanobacteria is controlled by the two meta-parameters $Div_{G_{max,CB}}$ and $Div_{h_{SR,CB}}$.
 To create a trade-off, the two meta-parameters were always of different sign.
@@
 
-(ref:div-repl-meth1) **Replication method results.** **Left column of panels**: the effect of response trait diversity (y-axis) on the positions of the tipping points (anoxic to oxic in blue, oxic to anoxic in red), which determine the extent of the region of bistability (green shaded region) in the oxygen diffusivity gradient.
+(ref:div-repl-meth1) **Replication method results.** **Left column of panels**: the effect of trait diversity (y-axis) on the positions of the tipping points (anoxic to oxic in blue, oxic to anoxic in red), which determine the extent of the region of bistability (green shaded region) in the oxygen diffusivity gradient.
 The left-most region is anoxic only, the middle is oxic or anoxic depending on historical conditions, and the right-most is oxic only.
 The thick grey vertical lines at -8 and 0 on the x-axis show the extent of the oxygen diffusivity gradient investigated in the simulations.
-**Right column of panels**: The effect of diversity on resilience, with positive values on the y-axis indicating that diversity has increased resilience, i.e.
-delayed the shift to the other state.
+**Right column of panels**: The effect size of trait variation on resilience, with positive values on the y-axis indicating that diversity has increased resilience.
 
@@
 
-(ref:div-temp-eventdef1) **Results with an abundance floor.** **Left column of panels**: the effect of response trait diversity (y-axis) on the positions of the tipping points (anoxic to oxic in blue, oxic to anoxic in red), which determine the extent of the region of bistability (green shaded region) in the oxygen diffusivity gradient.
+(ref:div-temp-eventdef1) **Results with an abundance floor.** **Left column of panels**: the effect of trait diversity (y-axis) on the positions of the tipping points (anoxic to oxic in blue, oxic to anoxic in red), which determine the extent of the region of bistability (green shaded region) in the oxygen diffusivity gradient.
 The left-most region is anoxic only, the middle is oxic or anoxic depending on historical conditions, and the right-most is oxic only.
 The thick grey vertical lines at -8 and 0 on the x-axis show the extent of the oxygen diffusivity gradient investigated in the simulations.
-**Right column of panels**: The effect of diversity on resilience, with positive values on the y-axis indicating that diversity has increased resilience, i.e.
+**Right column of panels**: The effect size of trait variation on resilience, with positive values on the y-axis indicating that diversity has increased resilience, i.e.
 delayed the shift to the other state.
@@
 The results below show the stable states as a function of oxygen diffusivity for a system with an intermediate level of diversity in all functional groups, with either 1'000'000 hours at each oxygen diffusivity level (Figure \@ref(fig:ss-temp-meth3)), or 2'000'000 hours (Figure \@ref(fig:ss-temp-meth4)).
-This shows that 1'000'000 hours duration of the simulations are sufficient to reach stable state, except very close to state transitions on the trajectory of recovery (i.e.: cyanobacteria: trajectory up; sulfate-reducing bacteria: trajectory down).
+This shows that 1'000'000 hours duration of the simulations are sufficient to reach stable state, except very close to state transitions on the trajectory of recovery (i.e.: cyanobacteria: trajectory of increasing oxygen diffusivity; sulfate-reducing bacteria: trajectory of decreasing oxygen diffusivit).
 Very close to these transitions, even at 2'000'000 hours, the dynamics are still transient, with high tolerance strains at high density, even though they will eventually be outcompeted by low tolerance (higher growth rate) strains.
@@
 When the environment ameliorates for the sulfate-reducing bacteria (i.e.
-trajectory down), there is only limited evidence of strain replacement (in final state) along the oxygen diffusivity gradient -- either the system is oxic or the least tolerant strain SB9 dominates.
-And yet the switch to anoxic state occurs earlier than when there is no diversity, which suggests there is some role of the more tolerant strains.
+trajectory of decreasing oxygen diffusivity), there is only limited evidence of strain replacement (in final state) along the oxygen diffusivity gradient -- either the system is oxic or the least tolerant strain dominates.
+And yet the switch to anoxic state occurs at higher oxygen diffusivity than when there is no diversity, which suggests there is some role of the more tolerant strains.
 We here show that the more tolerant strains do play a role, but only a transient one.
@@
 
+Among these two pathways, effects of phototrophic sulfur bacteria via abiotic oxidation of sulfide are probably of subordinate importance in natural environments because abiotic oxidation rates of sulfide are very small compared to biotic oxidation rates ([Luther et al 2011]( https://doi.org/10.3389/fmicb.2011.00062)).
+
 There is, however, at least one pathway by which PB can favour the anoxic state: PB produce oxidised sulfur which is consumed by SB, and SB produce reduced sulfur, which inhibits CB.
@@
 Interestingly, diversity in the cyanobacteria moved the shift to the oxic state to lower levels of oxygen diffusivity although independent variation in the cyanobacteria had no effect on this tipping point.
+
+# References
+Bush, T., Diao, M., Allen, R.J., Sinnige, R., Muyzer, G.
+& Huisman, J.
+(2017).
+Oxic-anoxic regime shifts mediated by feedbacks between biogeochemical processes and microbial community dynamics.
+Nat.
+Commun., 8, 789.
+
+Luther, G.W., Findlay, A., MacDonald, D., Owings, S., Hanson, T., Beinart, R., et al.
+(2011).
+Thermodynamics and kinetics of sulfide oxidation by oxygen: a look at inorganically controlled reactions and biologically mediated processes in the environment.
+Front.
+Microbiol., 2, 62.

### 2022-06-09 index.Rmd
make html index

---
title: "Index"
author: "Owen Petchey"
date: "6/9/2022"
output: html_document
---

[supplement](./experiments/2_supplement/supplement.html)

### 2022-06-09 docs/index.Rmd
organise guidance

---
title: "Guide to repository of supplementary resources"
date: ""`r format(Sys.time(), '%d %B, %Y')`""
output: html_document
---

This is a guide to a repository containing various resources associated with the publication **Functional diversity can facilitate the collapse of an undesirable ecosystem state**.

[The repository on github.](https://github.com/UZH-PEG/diversity_envresp1)

[The Supplementary Report (HTML page)](../experiments/2_supplement/supplement.html)

[HTML page about how to reproduce the research.](./docs/How_to_reproduce.html)

[Some animations of results (HTML page)](../experiments/3_animate/report.html)

### 2022-06-09 docs/index.Rmd
update index

@@
 title: "Guide to repository of supplementary resources"
-date: ""`r format(Sys.time(), '%d %B, %Y')`""
+date: "`r format(Sys.time(), '%d %B, %Y')`"
 output: html_document
@@
 
-[Some animations of results (HTML page)](../experiments/3_animate/report.html)
+[Some animations of results (HTML page)](./experiments/3_animate/report.html)

### 2022-06-09 index.Rmd
fixing stuff

@@
 ---
-title: "Index"
-author: "Owen Petchey"
-date: "6/9/2022"
+title: "Guide to repository of supplementary resources"
+date: "`r format(Sys.time(), '%d %B, %Y')`"
 output: html_document
@@
 
-[supplement](./experiments/2_supplement/supplement.html)
+This is a guide to a repository containing various resources associated with the publication **Functional diversity can facilitate the collapse of an undesirable ecosystem state**.
+
+[The repository on github.](https://github.com/UZH-PEG/diversity_envresp1)
+
+[The Supplementary Report (HTML page)](./experiments/2_supplement/supplement.html)
+
+[HTML page about how to reproduce the research.](./docs/How_to_reproduce.html)
+
+[Some animations of results (HTML page)](./experiments/3_animate/report.html)

### 2022-06-09 experiments/2_supplement/supplement.Rmd
changes supplement
update supplement

@@
 ---
-title: Supplementary Content for the article *Functional diversity can facilitate the collapse of an undesirable ecosystem state*
+title: Supplementary Report for the article *Functional diversity can facilitate the collapse of an undesirable ecosystem state*
 author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
@@
 
-This document contains the Supplementary Content for the report *information to be added once final*.
+This document is the Supplementary Report for the report *Functional diversity can facilitate the collapse of an undesirable ecosystem state*.
 
@@
 ```{r repl-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:repl-meth2)', fig.height=10, fig.width=8, fig.align="center"}
-fig_state_vs_o2diff_sidebyside_alternative(repl_meth[1,])
+fig_state_vs_o2diff_sidebyside_alternative_repmeth(repl_meth[1,])
 ```
@@
 We here show that the more tolerant strains do play a role, but only a transient one.
-The following dynamics are for the system starting oxic, and with a value of oxygen diffusivity (log10(oxygen diffusivity) = -4.8) for which the system remains oxic if there is no diversity (Figure \@ref(fig:sb-div-effect3)), but switches to anoxic if there is diversity (Figure \@ref(fig:sb-div-effect4)).
-There is only diversity in the two groups of sulfur bacteria.
+The following dynamics are for the system starting oxic, and with a value of oxygen diffusivity (log10(oxygen diffusivity) = -4.8).
+When there is no diversity within functional groups (i.e.
+two strains that are identical) the system remains oxic (Figure \@ref(fig:sb-div-effect3)).
+When there is diversity (i.e.
+the two strains differ) then the system switches to the anoxic state (Figure \@ref(fig:sb-div-effect4)).
+In these examples there is only diversity in the two groups of sulfur bacteria.
 The most tolerant strain does at first grow, but is then outcompeted by less tolerant strains as the concentration of the inhibiting substrate (oxygen) declines.
@@
 
-(ref:sb-div-effect3)  Dynamics of the system with no diversity in any functional group, and log10(oxygen diffusivity) = -4.8. The system remains oxic when starting in the oxic state.
+(ref:sb-div-effect3)  Dynamics of the system **with no diversity** in any functional group, and log10(oxygen diffusivity) = -4.8.
+The system remains oxic when starting in the oxic state.
+Although two strains are shown in the legend, they have identical parameters, and so their dynamics are identical and only one is visible in the dynamics.
 
@@
 
-(ref:sb-div-effect4) Dynamics of the system with diversity in the two groups of sulfur bacteria and otherwise exactly the same conditions as in Figure \@ref(fig:sb-div-effect3).
+(ref:sb-div-effect4) Dynamics of the system **with diversity** in the two groups of sulfur bacteria and otherwise exactly the same conditions as in Figure \@ref(fig:sb-div-effect3).
 The system flips from oxic to anoxic, whereas it did not when there was no diversity.
@@
 # References
+
 Bush, T., Diao, M., Allen, R.J., Sinnige, R., Muyzer, G.

### 2022-06-09 R/ms_figure_functions.R

@@ -892,6 +892,250 @@ fig_state_vs_o2diff_sidebyside_alternative <- function(ss_result){
   return(patchwork)
 }
 
+fig_state_vs_o2diff_sidebyside_alternative_repmeth <- function(ss_result){
+  
+  is_repl <- "ss_by_a_N_result" %in% names(ss_result)
+  
+  if (is_repl) {
+    ss_result$ssfind_result <- ss_result$ss_res
+  }
+  
+  temp1 <- ss_result %>%
+    mutate(ssfind_result = list(get_total_bio(ssfind_result)))
+  
+  if (is_repl){
+    temp1 <- microxanox:::get_stability_measures.replication_ssfind_result(
+      temp1$ssfind_result[[1]],
+      threshold_diff_log10scale = 3
+    )
+  } else {
+    temp1 <- microxanox:::get_stability_measures.temporal_ssfind_result(
+      temp1$ssfind_result[[1]],
+      threshold_diff_log10scale = 3
+    )
+  }
+  
+  stab_measures <- temp1 %>% 
+    filter(Species == "SB_tot") %>%
+    select(down=hyst_min_log, up=hyst_max_log) %>%
+    pivot_longer(names_to = "direction", values_to = "aO_flip", 1:2) %>%
+    mutate(y_start = c(2.5, 7.5),
+           y_end = c(7.5, 2.5))
+  
+  rm(temp1)
+  
+  if (is_repl) {
+    gathcols <- 1:(31)
+    ss_result$ssfind_result[[1]] <- ss_result$ssfind_result[[1]] %>%
+      mutate(a_O = log10(a_O),
+             direction = ifelse(initial_N_CB == 1, "up", "down"))
+  } else {
+    gathcols <- 2:(ncol(ss_result$ssfind_result[[1]]) - 2)
+  }
+  
+  temp <- ss_result$ssfind_result[[1]] %>%
+    mutate(a = 10^a_O) %>%
+    gather(species, quantity, gathcols) %>%
+    mutate(
+      var_type = ifelse(grepl("B_", species), "Organism", "Substrate"),
+      functional_group = case_when(
+        str_detect(species, "CB_") ~ "CB",
+        str_detect(species, "SB_") ~ "SB",
+        str_detect(species, "PB_") ~ "PB"),
+      log10_quantity = log10(quantity + 1),
+      species = factor(species, levels = unique(species)),
+      functional_group2 = case_when(
[…]

### 2022-08-09 experiments/2_supplement/supplement.Rmd
small changes

@@
       smooth_scroll: true
+    code_folding: hide
 ---

### 2022-08-10 experiments/2_supplement/supplement.Rmd
add graph to supplement

@@
 
+# Is it really functional diversity?
+
+```{r div-stab-multstrain1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-stab-multstrain1)', fig.height=8, fig.width=8, fig.align="center"}
+all_stab <- readRDS(here("data", "0_ss_finding", "temporal_method", "processed_data", "stab_data_temporal_method_ELErevision1.RDS"))
+
+## a fudge to test a test dataset, should be removed when final dataset is available
+all_stab <- all_stab %>%
+  mutate(waittime = ifelse(num_strains == -1, 1e6, waittime))
+
+which_strains <- c(-1, 9)
+which_wait_time <- 1e6
+figure_title <- " "
+
+fig_div_vs_o2diff_maxtolcomp(all_stab, which_strains,
+                              which_wait_time, figure_title)
+```
+
 # Finding the separatrix

### 2022-08-10 R/ms_figure_functions.R

@@ -1459,3 +1459,47 @@ combine_fct <- function(Method="arithmetic"){
                             agg_stab_strain9_CB_SBPB, agg_stab_strain9_CBSB_PB, agg_stab_strain9_CBPB_SB)
   return(agg_stab_strain9)
 }
+
+
+fig_div_vs_o2diff_maxtolcomp <- function(all_stab,
+                                          which_strains,
+                                          which_wait_time,
+                                          figure_title) {
+  
+  all_stab <- all_stab %>%
+    mutate(Treatment = ifelse(num_strains == -1,
+                              "Only most tolerant strain",
+                              "All strains"))
+  
+  p1 <- all_stab %>%
+    #filter(var_treat == "CB") %>%
+    filter(num_strains %in% which_strains, 
+           waittime == which_wait_time) %>%
+    filter(Species == "SB_tot") %>%
+    ggplot(aes(x = stand_var,
+               col = Treatment)) +
+    facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
+    geom_line(aes(y = hyst_min_log, col = Treatment), lwd = 0.5, alpha = 0.8) +
+    geom_line(aes(y = hyst_max_log), lwd = 0.5, alpha = 0.8) +
+    geom_ribbon(aes(ymin = hyst_min_log, ymax = hyst_max_log,
+                    col = Treatment,
+                    fill = Treatment), alpha = 0.2) +
+    facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
+    xlab("Standardised amount of trait variation") +
+    ylab(expression(log[10](oxygen~diffusivity)~(h^{-1}))) +
+    #labs(fill = "Variation in\nonly these\nfunctional groups") +
+    coord_flip() +
+    guides(col = guide_legend(title="Strains present"),
+           fill = guide_none()) +
+    theme_bw() +
+    theme(
+      legend.position="top",
+      panel.background = element_blank(),
+      #strip.text.x = element_blank()
+    ) +
+    geom_hline(yintercept = c(-8, 0), col = "grey", lwd = 3) +
+    ggtitle(figure_title)
+  
+  p1
+  
+}

### 2022-09-12 experiments/2_supplement/supplement.Rmd
revision 1.1.1

--- 2022-08-09 experiments/2_supplement/supplement.Rmd
@@
 
+# Is it really functional diversity?
+
+Reviewer 1: "This made me wonder whether the same (or at least a very similar) results regarding the change in resilience of the system states could also be obtained with just a single strain per functional group, whose tolerance to the inhibiting substance is systematically increased.
+This could be tested fairly easily by re-running the simulations behind Fig.
+3 with just the most tolerant (and slowest growing) strain of each functional group present."
+
+We made new simulations with communities composed of functional groups all containing nine strains just as before, but then only retained in each functional group the one strain with the greatest tolerance.
+E.g., in a simulation with variation in the only the SB group (and no variation in the CB or PB groups) then the CB and PB groups (as before) each had only one strain with the mean tolerance value (which is also the maximum there), whereas the SB group contained one strain with higher tolerance.
+We also performed simulations in which we retained 9 strains in each functional group, but set the tolerance of all nine to the maximum tolerance value.
+Results were the same as those presented below
+
+For most of the explored combinations and values of functional diversity the results are the same (Figure \@ref(fig:max-tol1)).
+There are differences when there is high functional diversity / high tolerance in the SB, in the CB-SB, and in the CB-SB-PB combinations.
+(These are also the situations in which we had already found that number of strains can be important (Fig.
+7.1 in the original version of the Supplement).) We look at these more closely below.
+
+(ref:max-tol1) Effects of strain variation on position of tipping points compared between simulations with all (nine) strains present and simulations where only the most tolerant strain is present.
+
+```{r max-tol1, echo = FALSE,  include=TRUE, fig.cap='(ref:max-tol1)', fig.height=8, fig.width=8, fig.align="center"}
+#all_stab <- readRDS(here("data", "0_ss_finding", "temporal_method", "processed_data", "stab_data_temporal_method_ELErevision1.2.RDS"))
+
+## here the version with only one strain per group
+all_stab <- readRDS(here("data", "0_ss_finding", "temporal_method",
+                         "ele_rev1.1",
+                         "stab_data_temporal_method_ELErevision1.1.RDS"))
+
+which_strains <- c(-1, 9)
+which_wait_time <- 1e6
+figure_title <- " "
+
+fig_div_vs_o2diff_maxtolcomp(all_stab, which_strains,
+                              which_wait_time, figure_title)
+```
+
+```{r echo = FALSE}
+nine_strains <- readRDS(here("data",
+                          "0_ss_finding",
+                          "temporal_method",
+                          "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
+maxtolonly_strains <- readRDS(here("data",
+                          "0_ss_finding",
+                          "temporal_method",
+                          "ele_rev1.1",
+                          "ss_data_-1strains_waittime1e+06_event_definition_2.RDS"))
+
+#nine_strains$parameter[[1]]$strain_parameter
+#maxtolonly_strains[134,]$parameter[[1]]$strain_parameter
+```
+
+## SB only, high diversity
+
+With only the most tolerance SB strain, the position of the oxic to anoxic tipping point at high SB diversity appears to be at very low oxygen diffusivity, compared to when all nine strains are present (Figure \@ref(fig:max-tol1)).
+A corresponding simulations from which the position of the tipping points are calculated are shown in Figures \@ref(fig:max-tol2) (nine strains) and \@ref(fig:max-tol3) (most tolerant strain only).
+We see that the effect of oxygen diffusivity on the stable state is quite different in the case of only the most tolerant strain only--at low oxygen diffusivity there is variation around a stable state with all three functional groups coexisting--this never occured when there were multiple strains varying in tolerance, or when there was only one strain with mean tolerance.
+Furthermore, the state of the system is independent of the direction of change in oxygen diffusivity.
+I.e.
+there is no region of bistability (no alternate stable states).
+
+The algorithm used to detect state changes is working incorrectly in this specific situation.
+Here is the description of the algorithm from the main text: "We calculated the tipping point position of the oxic to anoxic (anoxic-oxic transition as the minimum (maximum) level of oxygen diffusivity at which the total density of sulfate-reducing bacteria was greater than 1000 abundance units different between the increasing and decreasing oxygen diffusivity simulation." This is not of great concern, however, as there are no state transitions to detect.
+
+We now wish to return to an aspect of the reviewer comment: It is correct that in Fig.
+4 when oxygen diffusivity increased, the two dominant functional groups (the sulfur bacteria groups) are dominated by the most tolerant strain before the state transition.
+And when oxygen diffusivity decreased, the dominant functional group (the cyanobacteria) is dominated by the most tolerant strain before the state transition.
+It is worth noting, however, that the transitions that occur are to states dominated by the least tolerant-highest growth rate strain.
+This raises the possibility that less tolerant strains may influence the results.
+
+Indeed, in the SB case, absence of the high growth rate SB strain precludes the formation of a stable state that does not include cyanobacteria.
+It seems that the most tolerant SB strain does not have a high enough growth rate to itself exclude the cyanobacteria.
+Cyanobacteria are therefore always present, regardless of the oxygen diffusivity.
+(The stable states of the system then display a complex relationship with oxygen diffusivity that our algorithm for detecting tipping points is not well suited to, hence the rather odd positions of the tipping points.)
+
+(ref:max-tol2) Stable states found with nine strains of SB and high diversity. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+
+```{r max-tol2, echo = FALSE,  include=TRUE, fig.cap='(ref:max-tol2)', fig.height=10, fig.width=8, fig.align="center"}
+## max SB_var_gmax_s is 0.09473684
+nine_strain_one <- filter(nine_strains,
+       CB_var_gmax_s == 0,
+       abs(SB_var_gmax_s - 0.09473684) < 0.001,
+       PB_var_gmax_s == 0)
+fig_state_vs_o2diff_sidebyside_alternative(nine_strain_one)
+```
+
+(ref:max-tol3) Stable states found with the single most tolerant SB and high diversity. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+
+```{r max-tol3, echo = FALSE,  include=TRUE, fig.cap='(ref:max-tol3)', fig.height=10, fig.width=8, fig.align="center"}
+max_tol_one <- filter(maxtolonly_strains,
+       CB_var_gmax_s == 0,
+       abs(SB_var_gmax_s - 0.09473684) < 0.001,
+       PB_var_gmax_s == 0)
+fig_state_vs_o2diff_sidebyside_alternative(max_tol_one)
+```
+
+### What causes variation in response to oxygen diffusivity (SB)?
+
+In the ecosystem shown in Figure \@ref(fig:max-tol3), where there was quite high tolerance SB strain, there was large variation in state variables along the oxygen diffusivity gradient at values less than about -4.5.
+To examine what might be causing this, we simulated the ecosystem at a constant oxygen diffusivity of $log_{10}$ oxygen diffusivity of -6 (Figure \@ref(fig:SB-maxtol-dyn1)).
+We see that the dynamics are qualitatively different from other cases in which there is a stable state reached in such a simulation.
+It appears that the high tolerance SB strain is able to initiate a transition to an anoxic state, but is not able to create a stable anoxic stable state.
+This dynamical situation was not presented in the ecosystem in which high tolerance and low tolerance strains were present.
+
+```{r echo = FALSE}
+#nine_strain_one$pars[[1]]
+#max_tol_one$pars[[1]]
+#fig_state_vs_o2diff_sidebyside_alternative(nine_strain_one)
+#fig_state_vs_o2diff_sidebyside_alternative(max_tol_one)
+parameter <- max_tol_one$parameter[[1]]
+parameter$strain_parameter <- max_tol_one$pars[[1]]
+#parameter$strain_parameter <- ss_result$pars[[1]]
+total_initial_abundances <- 10^5
+parameter <- set_temporal_ssfind_initial_state(parameter,
+                                               total_initial_abundances,
+                                               total_initial_abundances,
+                                               total_initial_abundances)
+parameter$log10a_series <- c(-6, -6)
+wait_time <-  1e5
+parameter$sim_duration <- wait_time * length(parameter$log10a_series)
+parameter$sim_sample_interval <- 10
+#parameter$sim_duration
+test1 <- run_simulation(parameter)
+```
+
+(ref:SB-maxtol-dyn1) Temporal dynamics of an ecosystem with a single SB strain with high tolerance, the same one as in Figure \@ref(fig:max-tol3) simulated with constant $log_{10}(oxygen diffusivity) of -6.
+
+```{r SB-maxtol-dyn1, echo = FALSE,  include=TRUE, fig.cap='(ref:SB-maxtol-dyn1)', fig.height=10, fig.width=8, fig.align="center"}
+plot_dynamics(test1)
+```
+
+## CB-SB only, high diversity
+
+As in the SB only case, the absence of lower tolerance-higher growth rate strains changes the system to a parameter space where it does not display alternate states, at least within the range of oxygen diffusivities simulated (Figure \@ref(fig:max-tol5)).
+
+(ref:max-tol4)  Stable states found with nine strains of CB and SB and high diversity. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+
+```{r max-tol4, echo = FALSE,  include=TRUE, fig.cap='(ref:max-tol4)', fig.height=10, fig.width=8, fig.align="center"}
+filter(nine_strains,
+       abs(CB_var_gmax_s - 0.026592798) < 0.001,
+       abs(SB_var_gmax_s - 0.079778395) < 0.001,
+       PB_var_gmax_s == 0) %>%
+  fig_state_vs_o2diff_sidebyside_alternative()
+```
+
+(ref:max-tol5)  Stable states found with the single most tolerant CB strain and SB strain and high diversity. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+
+```{r max-tol5, echo = FALSE,  include=TRUE, fig.cap='(ref:max-tol5)', fig.height=10, fig.width=8, fig.align="center"}
+max_tol_one_CBSB <- filter(maxtolonly_strains,
+       abs(CB_var_gmax_s - 0.026592798) < 0.001,
+       abs(SB_var_gmax_s - 0.079778395) < 0.001,
+       PB_var_gmax_s == 0)
+fig_state_vs_o2diff_sidebyside_alternative(max_tol_one_CBSB)
+```
+
+### What causes variation in response to oxygen diffusivity (CB-SB)?
+
+In the ecosystem shown in Figure \@ref(fig:max-tol5), where there was quite high tolerance CB strain and SB strain, there was large variation in state variables along the oxygen diffusivity gradient at values less than about -6.5.
+To examine what might be causing this, we simulated the ecosystem at a constant oxygen diffusivity of $log_{10}$ oxygen diffusivity of -6 (Figure \@ref(fig:CBSB-maxtol-dyn1)).
+We see that the dynamics are qualitatively different from other cases in which there is a stable state reached in such a simulation.
+It appears that the high tolerance SB strain is able to initiate a transition to an anoxic state, but is not able to create a stable anoxic stable state.
+
+```{r echo = FALSE}
+#nine_strain_one$pars[[1]]
+#max_tol_one$pars[[1]]
+#fig_state_vs_o2diff_sidebyside_alternative(nine_strain_one)
+#fig_state_vs_o2diff_sidebyside_alternative(max_tol_one)
+parameter <- max_tol_one_CBSB$parameter[[1]]
+parameter$strain_parameter <- max_tol_one$pars[[1]]
+#parameter$strain_parameter <- ss_result$pars[[1]]
+total_initial_abundances <- 10^5
+parameter <- set_temporal_ssfind_initial_state(parameter,
+                                               total_initial_abundances,
+                                               total_initial_abundances,
+                                               total_initial_abundances)
+parameter$log10a_series <- c(-7, -7)
+wait_time <-  1e5
+parameter$sim_duration <- wait_time * length(parameter$log10a_series)
+parameter$sim_sample_interval <- 10
+#parameter$sim_duration
+test1 <- run_simulation(parameter)
+```
+
+(ref:CBSB-maxtol-dyn1) Temporal dynamics of an ecosystem with a single CB strain with high tolerance and a single SB strain with high tolerance, the same one as in Figure \@ref(fig:max-tol5) simulated with constant $log_{10}(oxygen diffusivity) of -6.
+
+```{r CBSB-maxtol-dyn1, echo = FALSE,  include=TRUE, fig.cap='(ref:CBSB-maxtol-dyn1)', fig.height=10, fig.width=8, fig.align="center"}
+plot_dynamics(test1)
+```
+
+## CB-SB-PB, high diversity
+
+In the CB-SB-PB case when only the most tolerant strain of all functional groups is present, the resilience of the oxic state is greater than when variation in strain tolerance is present.
+Looked at from another perspective, comparing CB-SB and CB-SB-PB both with only the most tolerant strains, we see that presence of a high tolerance PB strain (in CB-SB-PB) allows the formation of an anoxic cyanobacteria-free stable state (whereas there was no such state in CB-SB).
+We interpret this as presence of a high tolerance PB strain stabilising the anoxic state, perhaps by increasing the availability of oxidised sulfur which is a resource for SB.
+
+(ref:max-tol6) Stable states found with nine strains of CB-SB-PB and high diversity. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+
+```{r max-tol6, echo = FALSE,  include=TRUE, fig.cap='(ref:max-tol6)', fig.height=10, fig.width=8, fig.align="center"}
+filter(nine_strains,
+       abs(CB_var_gmax_s - 0.026592798) < 0.001,
+       abs(SB_var_gmax_s - 0.079778395) < 0.001,
+       abs(PB_var_gmax_s - 0.079778395) < 0.001) %>%
+  fig_state_vs_o2diff_sidebyside_alternative()
+
+```
+
+(ref:max-tol7) Stable states found with the single most tolerant CB strain, SB strain, and PB strain, and high diversity. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+
+```{r max-tol7, echo = FALSE,  include=TRUE, fig.cap='(ref:max-tol7)', fig.height=10, fig.width=8, fig.align="center"}
+filter(maxtolonly_strains,
+       abs(CB_var_gmax_s - 0.026592798) < 0.001,
+       abs(SB_var_gmax_s - 0.079778395) < 0.001,
+       abs(PB_var_gmax_s - 0.079778395) < 0.001) %>%
+  fig_state_vs_o2diff_sidebyside_alternative()
+```
+
+### Why only at high diversity?
+
+Why do these effects only occur at high diversities?
+The likely reason is that at high diversities then the most tolerant strain has particularly low growth rate, and so it may have the tolerance required to persist, it does not have the growth rate required to dominate.
+
 # Finding the separatrix

### 2022-09-12 experiments/0_ss_finding/temporal_method/run_experiment_onestrain.R

@@ -1,0 +1,105 @@
+## SS finding experiment by temporal method
+## Be careful to not overwrite data files
+
+rm(list = ls())
+source(here::here("R/various_useful_functions.r"))
+max_cores <- benchmarkme::get_cpu()$no_of_cores-2
+
+
+## setup experiment with two strains
+num_strains <- 2
+source(here::here("experiments/0_ss_finding/temporal_method/setup_experiment.R"))
+
+## keep only the most tolerant strain
+#var_expt <- var_expt[1:2,]
+for(i in 1:nrow(var_expt)) {
+  temp_pars <- var_expt$pars[i][[1]]
+  temp_pars$CB <- temp_pars$CB[which(temp_pars$CB$h_SR_CB==max(temp_pars$CB$h_SR_CB))[1],]
+  temp_pars$PB <- temp_pars$PB[which(temp_pars$PB$h_O_PB==max(temp_pars$PB$h_O_PB))[1],]
+  temp_pars$SB <- temp_pars$SB[which(temp_pars$SB$h_O_SB==max(temp_pars$SB$h_O_SB))[1],]
+  initial_subtrates <- temp_pars$initial_state[!str_detect(names(temp_pars$initial_state), "B_")]
+  temp_pars$initial_state <- c(NA, NA, NA, initial_subtrates)
+  names(temp_pars$initial_state) <- c("CB_1", "PB_1", "SB_1", names(initial_subtrates))
+  var_expt$pars[i][[1]] <- temp_pars
+}
+num_strains <- -1 ## use this to label that only the most tolerant strain is kept
+
+
+datadir <- here::here("data/0_ss_finding/temporal_method")
+dir.create(datadir, recursive = TRUE, showWarnings = FALSE)
+
+ss_data_filename <- file.path(datadir,
+                              paste0("ss_data_",
+                                     num_strains, "strains_waittime",
+                                     formatC(wait_time, format = "e", digits = 0),
+                                     "_", event_def, ".RDS"))
+stab_data_filename <- file.path(datadir,
+                                paste0("stab_data_",
+                                       num_strains, "strains_waittime",
+                                       formatC(wait_time, format = "e", digits = 0),
+                                       "_", event_def, ".RDS"))
+
+
+
+## Estimate time require ----
+nrow(var_expt)
+wait_time
+length(parameter$log10a_series)
+num_cores <- min(c(max_cores, nrow(var_expt)))
+## constants in following formula come from the excel sheet
[…]

### 2022-09-12 experiments/2_supplement/supplement.Rmd
update 1.1.2

@@
 
-We made new simulations with communities composed of functional groups all containing nine strains just as before, but then only retained in each functional group the one strain with the greatest tolerance.
-E.g., in a simulation with variation in the only the SB group (and no variation in the CB or PB groups) then the CB and PB groups (as before) each had only one strain with the mean tolerance value (which is also the maximum there), whereas the SB group contained one strain with higher tolerance.
-We also performed simulations in which we retained 9 strains in each functional group, but set the tolerance of all nine to the maximum tolerance value.
-Results were the same as those presented below
-
-For most of the explored combinations and values of functional diversity the results are the same (Figure \@ref(fig:max-tol1)).
+We made new simulations with communities composed of functional groups all containing only the strain with the greatest tolerance.
+E.g., in a simulation to be compared with variation in the only the SB group (and no variation in the CB or PB groups) then the CB and PB groups (as before) each had only one strain with the mean tolerance value (which is also the maximum there), whereas the SB group contained one strain with higher tolerance.
+(We also performed simulations in which we retained 9 strains in each functional group, but set the tolerance of all nine to the maximum tolerance value.
+Results were the same as those presented below.)
+
+For most of the explored combinations and amounts of functional diversity the results are the same (Figure \@ref(fig:max-tol1)).
 There are differences when there is high functional diversity / high tolerance in the SB, in the CB-SB, and in the CB-SB-PB combinations.
-(These are also the situations in which we had already found that number of strains can be important (Fig.
-7.1 in the original version of the Supplement).) We look at these more closely below.
+We look at these more closely below.
 
@@
 Why do these effects only occur at high diversities?
-The likely reason is that at high diversities then the most tolerant strain has particularly low growth rate, and so it may have the tolerance required to persist, it does not have the growth rate required to dominate.
+The likely reason is that at high diversities then the most tolerant strain has particularly low growth rate, and so it may have the tolerance required to increase and persist, it does not have the growth rate required to dominate.
 

### 2022-09-16 experiments/1_figures_main_ms/equations for fig2.Rmd
various revisions

---
title: "Growth and inhibition functions"
author: "Owen Petchey"
date: '2022-09-16'
output: html_document
---

# Growth and inhibition functions

The rate of change in population densities is given by the growth rate - death rate (Bush *et al.* 2018). Growth rate is the growth rate in absence of any inhibition multiplied by the amount of inhibition.

Growth rate in the absence of inhibition was modeled with the Monod equation with multiplicative kinetics when two substrates determine growth rate:

$g_j(X, Y) = g_{max,j} (\frac{X}{K_{j,X} + X})(\frac{Y}{K_{j,Y} + Y})$

$g_{max,j}$ is the maximum specific growth rate of strain $j$. $X$ is the concentration of substrate 1, and $Y$ is the concentration of substrate 2. $K_{j,X}$ and $K_{j,Y}$ are the half-saturation constants of species $j$ on substrates $X$ and $Y$.

Inhibition of growth by a substrate was modelled with the Haldane equation:

$h_j(X) = \frac{1}{1+ (X / H_{j,X})}$

$H_{j,X}$ can be thought of as a half-inhibition constant: the concentration of $X$ at which the growth rate of species $j$ is reduced by 50%.

For further information details of the functions used to model system, please see the original publication by Bush *et al.* (2018)

### 2022-09-16 experiments/2_supplement/supplement.Rmd
various revisions

@@
 
-# Is it really functional diversity?
-
-Reviewer 1: "This made me wonder whether the same (or at least a very similar) results regarding the change in resilience of the system states could also be obtained with just a single strain per functional group, whose tolerance to the inhibiting substance is systematically increased.
+# Are the results driven by functional diversity?
+
+During the review process we received the following comment: *I think the authors have not shown sufficiently clearly that their results are actually driven by functional diversity.
+Fig.
+4 shows that on the collapse trajectory, the dominating functional group is itself dominated by the most tolerant strain.
+This is also true for the suppressed group on its recovery trajectory shortly before the tipping point.
+This made me wonder whether the same (or at least a very similar) results regarding the change in resilience of the system states could also be obtained with just a single strain per functional group, whose tolerance to the inhibiting substance is systematically increased.
 This could be tested fairly easily by re-running the simulations behind Fig.
-3 with just the most tolerant (and slowest growing) strain of each functional group present."
+3 with just the most tolerant (and slowest growing) strain of each functional group present.* In this section we discuss this matter.
+
+Our first realisation was that we had not adequately stated what component of functional diversity we manipulated.
+We revised to state *Functional diversity has multiple components, and we manipulate only one of these, namely the range of trait space represented, which has been termed functional richness, and measured as the convex hull volume ([Villéger et al.
+2008](https://esajournals.onlinelibrary.wiley.com/doi/abs/10.1890/07-1206.1)).*
+
+Since we manipulated the range of trait space represented (sensu [Villéger et al 2008](https://esajournals.onlinelibrary.wiley.com/doi/abs/10.1890/07-1206.1)), and manipulated nothing else, we manipulated only functional diversity.
+Logically then, any effects of this manipulation must be due to the functional diversity manipulation.
+That is, regardless of the process / mechanism by which functional diversity causes an effect, it is appropriate to state that functional diversity drives the results.
+
+The reviewer’s comment motivated us to consider two questions:
+
+1. By what mechanism does functional diversity affect ecosystem stability in this study? 
+2. Could the observed effects of functional diversity also be created by manipulations of trait values that do not alter functional diversity?
+
+Question 1.
+In research concerning biodiversity and ecosystem functioning there was considerable debate about the phenomenon that high yielding species are more likely to be present in more diverse communities.
+This phenomenon was sometimes responsible for a large proportion of observed effects of biodiversity on ecosystem function.
+The debate was to a large extent resolved by recognising that biodiversity effects can result from two sources: a selection/sampling effect, and a complementarity effect.
+Both are now considered valid and important mechanisms by which diversity (including functional diversity) affects ecosystem functioning.
+We view the presence of more extreme trait values in more functionally diverse communities as an analogue of the sampling/selection effect of biodiversity, and a valid mechanism by which increased functional diversity can affect ecosystem stability.
+For example, let us assume for the moment that, indeed, only the single maximum tolerance strain present in each functional group of an ecosystem determines the resilience of that ecosystem.
+Then we would say that variation in resilience with diversity operates only by the "sampling effect".
+If we also assume that higher tolerance causes higher ecosystem resilience, then a more functionally diverse ecosystem will have higher maximum tolerance trait, and so higher resilience.
+And an ecosystem with more strains per functional group will have higher resilience (Figure \@ref(fig:samp-effect1)).
+
+Hence, even if all of the observed effects of our functional diversity manipulation were only due to presence of one strain (e.g.
+the most tolerant one), this can be considered an effect of functional diversity.
+
+(ref:samp-effect1) A simple phenomenological model of the effect of number of strains in an ecosystem on the resilience of that ecosystem, when the resilience of a ecosystem is determined only by the maximum trait value of the strains present in that ecosystem.
+Each data point is a different ecosystem, with the strains in each ecosystem drawn at random from a pool of 20 strains.
+Each of the 20 strains was assigned a trait value drawn at random from a uniform distribution with minimum 0 and maximum 1.
+The blue line is the fit of a generalised additive model and the grey ribbon shows the 1 standard error confidence range.
+
+```{r samp-effect1, echo = FALSE,  include=TRUE, fig.cap='(ref:samp-effect1)', fig.height=5, fig.width=6, fig.align="center"}
+if(!("tidyverse" %in% .packages()))
+  library(tidyverse)
+
+number_of_species <- 20
+species_trait <- tibble(species_name = paste0("Species-", letters[1:20]),
+                        trait_value = runif(number_of_species))
+
+richness_levels <- seq(1, 10, 1)
+compositions_per_richness_level <- 10
+expt <- crossing(richness = richness_levels,
+                 composition = paste0("Comp-", 1:compositions_per_richness_level)) %>%
+  mutate(composition = paste0(composition, "-", richness),
+         resilience_max_trait = NA)
+
+for(i in 1:nrow(expt))
+  expt$resilience_max_trait[i] = max(sample(species_trait$trait_value, expt$richness[i]))
+
+ggplot(expt, aes(x = richness, y = resilience_max_trait)) +
+  geom_point() +
+  xlab("Number of strains") +
+  ylab("Resilience if only the tolerance of\nthe most tolerant strain determines resilience.") +
+  geom_smooth(method = "gam")
+
+```
+
+**Question 2.
+It is possible that all of the observed effects of functional diversity operate via this sampling effect, and thus could also be created when there is only one maximum tolerance strain in each functional group?.**
 
 We made new simulations with communities composed of functional groups all containing only the strain with the greatest tolerance.
-E.g., in a simulation to be compared with variation in the only the SB group (and no variation in the CB or PB groups) then the CB and PB groups (as before) each had only one strain with the mean tolerance value (which is also the maximum there), whereas the SB group contained one strain with higher tolerance.
+E.g., in a simulation to be compared with variation in the only the SB group (and no variation in the CB or PB groups) then the CB and PB groups (as before) each had only one strain with the mean tolerance value, whereas the SB group contained one strain with higher tolerance.
 (We also performed simulations in which we retained 9 strains in each functional group, but set the tolerance of all nine to the maximum tolerance value.
@@
 
-The algorithm used to detect state changes is working incorrectly in this specific situation.
-Here is the description of the algorithm from the main text: "We calculated the tipping point position of the oxic to anoxic (anoxic-oxic transition as the minimum (maximum) level of oxygen diffusivity at which the total density of sulfate-reducing bacteria was greater than 1000 abundance units different between the increasing and decreasing oxygen diffusivity simulation." This is not of great concern, however, as there are no state transitions to detect.
-
 We now wish to return to an aspect of the reviewer comment: It is correct that in Fig.
@@
 Cyanobacteria are therefore always present, regardless of the oxygen diffusivity.
-(The stable states of the system then display a complex relationship with oxygen diffusivity that our algorithm for detecting tipping points is not well suited to, hence the rather odd positions of the tipping points.)
+The stable states of the system then display a complex relationship with oxygen diffusivity that our algorithm for detecting tipping points is not well suited to, hence the rather odd positions of the indicated tipping points.
 
@@
 
-(ref:max-tol3) Stable states found with the single most tolerant SB and high diversity. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+(ref:max-tol3) Stable states found with the single most tolerant SB and high diversity.
+All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+As mentioned in the text, the algorithm used to detect the position of the tipping points is not working correctly here, and so the grey arrows should be ignored.
 
@@
 ```{r SB-maxtol-dyn1, echo = FALSE,  include=TRUE, fig.cap='(ref:SB-maxtol-dyn1)', fig.height=10, fig.width=8, fig.align="center"}
-plot_dynamics(test1)
+p <- plot_dynamics(test1)
+p[[1]] <- p[[1]] + 
+  xlab(NULL) + 
+  ylab(expression(log[10](density)~(cells~L^{-1}))) +
+  theme_bw()
+p[[2]] <- p[[2]] + 
+  xlab(NULL) + 
+  ylab(expression(log[10](density)~(cells~L^{-1}))) +
+  theme_bw()
+p[[3]] <- p[[3]] + 
+  xlab(NULL) + 
+  ylab(expression(log[10](density)~(cells~L^{-1}))) +
+  theme_bw()
+p[[4]]$data <- p[[4]]$data %>% 
+  dplyr::filter(species != "a")
+p[[4]]$data$species <- p[[4]]$data$species %>%
+  dplyr::recode(SO = "Oxidised sulfur", O = "Oxygen", SR = "Sulfide", P = "Phosphorus")
+p[[4]] <- p[[4]] + 
+  xlab("time (h)") + 
+  ylab(expression(log[10](concentration)~(µM))) + 
+  labs(colour = "substrate") +
+  theme_bw()
+
+p
 ```
@@
 
-(ref:max-tol5)  Stable states found with the single most tolerant CB strain and SB strain and high diversity. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+(ref:max-tol5)  Stable states found with the single most tolerant CB strain and SB strain and high diversity.
+All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+As mentioned in the text, the algorithm used to detect the position of the tipping points is not working correctly here, and so the grey arrows should be ignored.
 
@@
 ```{r CBSB-maxtol-dyn1, echo = FALSE,  include=TRUE, fig.cap='(ref:CBSB-maxtol-dyn1)', fig.height=10, fig.width=8, fig.align="center"}
-plot_dynamics(test1)
+p <- plot_dynamics(test1)
+p[[1]] <- p[[1]] + 
+  xlab(NULL) + 
+  ylab(expression(log[10](density)~(cells~L^{-1}))) +
+  theme_bw()
+p[[2]] <- p[[2]] + 
+  xlab(NULL) + 
+  ylab(expression(log[10](density)~(cells~L^{-1}))) +
+  theme_bw()
+p[[3]] <- p[[3]] + 
+  xlab(NULL) + 
+  ylab(expression(log[10](density)~(cells~L^{-1}))) +
+  theme_bw()
+p[[4]]$data <- p[[4]]$data %>% 
+  dplyr::filter(species != "a")
+p[[4]]$data$species <- p[[4]]$data$species %>%
+  dplyr::recode(SO = "Oxidised sulfur", O = "Oxygen", SR = "Sulfide", P = "Phosphorus")
+p[[4]] <- p[[4]] + 
+  xlab("time (h)") + 
+  ylab(expression(log[10](concentration)~(µM))) + 
+  labs(colour = "substrate") +
+  theme_bw()
+
+p
 ```
@@
 
+# Growth and inhibition functions
+
+Bush et al. (2018) used the Monod equation for growth, with multiplicative kinetics when two substrates determine growth rate:
+
+$g_j(X, Y) = g_{max,j} (\frac{X}{K_{j,X} + X})(\frac{Y}{K_{j,Y} + Y})$
+
+g_{max,j} is the maximum specific growth rate of strain $j$
+
+$X$ is the concentration of substrate 1, and $Y$ is the concentration of substrate 2.
+
+K_{j,X} and K_{j,Y} are the half-saturation constants of species $j$ on substrates $X$ and $Y$.
+
 # References

### 2022-09-28 experiments/2_supplement/supplement.Rmd
put growth and inhibition functions section in supplement

@@
 This document is the Supplementary Report for the report *Functional diversity can facilitate the collapse of an undesirable ecosystem state*.
+
+# Growth and inhibition functions
+
+The rate of change in population densities is given by the growth rate - death rate [Bush et al 2017](https://www.nature.com/articles/s41467-017-00912-x).
+Growth rate is the growth rate in absence of any inhibition multiplied by the amount of inhibition.
+
+Growth rate in the absence of inhibition was modeled with the Monod equation with multiplicative kinetics when two substrates determine growth rate:
+
+$g_j(X, Y) = g_{max,j} (\frac{X}{K_{j,X} + X})(\frac{Y}{K_{j,Y} + Y})$
+
+$g_{max,j}$ is the maximum specific growth rate of strain $j$.
+$X$ is the concentration of substrate 1, and $Y$ is the concentration of substrate 2.
+$K_{j,X}$ and $K_{j,Y}$ are the half-saturation constants of species $j$ on substrates $X$ and $Y$.
+
+Inhibition of growth by a substrate was modelled with the Haldane equation:
+
+$h_j(X) = \frac{1}{1+ (X / H_{j,X})}$
+
+$H_{j,X}$ can be thought of as a half-inhibition constant: the concentration of $X$ at which the growth rate of species $j$ is reduced by 50%.
+
+For further information details of the functions used to model system, please see the original publication by Bush *et al.* (2018)
 
@@
 
-(ref:samp-effect1) A simple phenomenological model of the effect of number of strains in an ecosystem on the resilience of that ecosystem, when the resilience of a ecosystem is determined only by the maximum trait value of the strains present in that ecosystem.
+(ref:samp-effect1) A simple phenomenological model of the effect of number of strains in an ecosystem on the resilience of that ecosystem, when the resilience of a ecosystem is linearly proportional to the maximum trait value of the strains present in that ecosystem.
 Each data point is a different ecosystem, with the strains in each ecosystem drawn at random from a pool of 20 strains.
@@
   library(tidyverse)
-
+set.seed(12345)
 number_of_species <- 20
@@
 
-fig_div_vs_o2diff_maxtolcomp(all_stab, which_strains,
+plot_1 <- fig_div_vs_o2diff_maxtolcomp(all_stab, which_strains,
                               which_wait_time, figure_title)
+plot_1 +
+  xlab("Standardised amount of trait variation used to create nine strains\nof which either all nine are retained, or only the most tolerant is retained.") +
+  guides(col=guide_legend(title="Which strains are retained", title.position = "top"))
 ```
@@
 
-# Growth and inhibition functions
-
-Bush et al. (2018) used the Monod equation for growth, with multiplicative kinetics when two substrates determine growth rate:
-
-$g_j(X, Y) = g_{max,j} (\frac{X}{K_{j,X} + X})(\frac{Y}{K_{j,Y} + Y})$
-
-g_{max,j} is the maximum specific growth rate of strain $j$
-
-$X$ is the concentration of substrate 1, and $Y$ is the concentration of substrate 2.
-
-K_{j,X} and K_{j,Y} are the half-saturation constants of species $j$ on substrates $X$ and $Y$.
-
 # References

### 2022-09-28 experiments/2_supplement/supplement.Rmd
update figures

@@
 (ref:max-tol1) Effects of strain variation on position of tipping points compared between simulations with all (nine) strains present and simulations where only the most tolerant strain is present.
+In the SB and CB-SB treatments there is missing data in the case with only the most tolerant strain when there were no alternate stable states and therefore no tipping points.
 
@@
 figure_title <- " "
+
+## remove data where there are no stable states
+## this subset is identified by inspection of the figure
+all_stab <- all_stab %>%
+  filter(!(var_treat == "SB" & stand_var > 0.88 & num_strains == -1),
+         !(var_treat == "CB-SB" & stand_var > 0.84 & num_strains == -1))
 
@@
        PB_var_gmax_s == 0)
-fig_state_vs_o2diff_sidebyside_alternative(nine_strain_one)
+ss_result <- nine_strain_one
+fig_state_vs_o2diff_sidebyside_alternative_leftfliponly(nine_strain_one)
 ```
@@
        PB_var_gmax_s == 0)
-fig_state_vs_o2diff_sidebyside_alternative(max_tol_one)
+fig_state_vs_o2diff_sidebyside_alternative_nofliparrows(max_tol_one)
 ```
@@
        PB_var_gmax_s == 0) %>%
-  fig_state_vs_o2diff_sidebyside_alternative()
+fig_state_vs_o2diff_sidebyside_alternative_leftfliponly()
 ```
@@
        PB_var_gmax_s == 0)
-fig_state_vs_o2diff_sidebyside_alternative(max_tol_one_CBSB)
+fig_state_vs_o2diff_sidebyside_alternative_nofliparrows(max_tol_one_CBSB)
 ```

### 2022-09-28 R/ms_figure_functions.R

@@ -675,7 +675,8 @@ fig_state_vs_o2diff_sidebyside_alternative <- function(ss_result){
     select(down=hyst_min_log, up=hyst_max_log) %>%
     pivot_longer(names_to = "direction", values_to = "aO_flip", 1:2) %>%
     mutate(y_start = c(2.5, 7.5),
-           y_end = c(7.5, 2.5))
+           y_end = c(7.5, 2.5)) #%>%
+    #filter(aO_flip != 0, aO_flip != -8)
   
   rm(temp1)
   
@@ -839,6 +840,468 @@ fig_state_vs_o2diff_sidebyside_alternative <- function(ss_result){
                  col = "#bbbbbbff", lwd = arrow_lwd,
                  arrow = arrow(length=unit(0.30,"cm"),
                                ends="first", type = "closed")) +
+    geom_path(lwd = line_width, col=6) +
+    geom_point(size = point_size, col=6) +
+    labs(tag="e", x=expression('log'[10]*"(oxygen diffusivity) (h"^{-1}*")"))+
+    theme_bw() +
+    theme(legend.position="none",
+          axis.title.y = element_blank(),
+          axis.title.x = element_text(size=13),
+          strip.background = element_rect(fill = "white"),
+          strip.background.x = element_blank(),
+          strip.text.x = element_blank(),
+          strip.text.y = element_text(size=12),
+          plot.margin = margin(t=-1, b=-1)) +
+    facet_grid(substrate2 ~ direction)
+  
+  
+  
+  ylab1 <- ggplot(data.frame(x = 1, y = 4.1)) +
+    geom_text(aes(x, y),label= expression('log'[10]*"(density) (cells L"^{-1}*")"),
+              angle = 90, size=4.5) + 
+    theme_void() +
+    coord_cartesian(clip = "off") +
+    theme(plot.margin = margin(t=-1, b=-1, l=-1))
+  
+  
+  ylab2 <- ggplot(data.frame(x = 1, y = 4.1)) +
+    geom_text(aes(x, y),label= expression('log'[10]*"(concentration) ("*mu*"M)"),
+              angle = 90, size=4.5) + 
+    theme_void() +
+    coord_cartesian(clip = "off") +
+    theme(plot.margin = margin(t=-1, b=-1, l=-1))
+  
+  
[…]

### 2022-10-03 experiments/2_supplement/supplement.Rmd
changes to supplement

@@
 
-We made new simulations with communities composed of functional groups all containing only the strain with the greatest tolerance.
-E.g., in a simulation to be compared with variation in the only the SB group (and no variation in the CB or PB groups) then the CB and PB groups (as before) each had only one strain with the mean tolerance value, whereas the SB group contained one strain with higher tolerance.
-(We also performed simulations in which we retained 9 strains in each functional group, but set the tolerance of all nine to the maximum tolerance value.
-Results were the same as those presented below.)
-
-For most of the explored combinations and amounts of functional diversity the results are the same (Figure \@ref(fig:max-tol1)).
-There are differences when there is high functional diversity / high tolerance in the SB, in the CB-SB, and in the CB-SB-PB combinations.
-We look at these more closely below.
+To test if the diversity effects on resilience were driven entirely by the most tolerant strains, we made additional simulations where functional groups contained only the strain with greatest tolerance and lowest maximum growth rate.
+That is, for each of the 20 levels of trait variation, we ran simulations where each functional group had only one strain, and its trait values corresponded with those of the most tolerant strain for the given level of trait variation.
+We also manipulated in which of the functional groups tolerance increased.
+For example, in a simulation to be compared with variation in only the SB group (and no variation in the CB or PB groups), the SB group contained the strain with highest tolerance, whereas CB and PB each contained the strain with mean tolerance.
+We then compared the tipping point positions resulting from this tolerance manipulation with the tipping point positions resulting from the diversity manipulation presented in the main text.
+
+To exclude that differences between the tolerance manipulation and the diversity manipulation were driven by the difference in number of strains, we also performed simulations in which we retained nine strains in each functional group but set the tolerance of all nine strains to the maximum tolerance value.
+Results were the same as those presented below from simulations with one strain.
+
+For most of the explored combinations and amounts of functional diversity/tolerance the tipping point positions did not differ between the diversity manipulation and the tolerance manipulation (Figure \@ref(fig:max-tol1)).
+However, the tipping point positions did differ between the diversity manipulation and the tolerance manipulation when diversity/tolerance in the SB group was high (i.e.
+in the combinations SB only, CB-SB, and CB-SB-PB).
 
@@
 
-## SB only, high diversity
-
-With only the most tolerance SB strain, the position of the oxic to anoxic tipping point at high SB diversity appears to be at very low oxygen diffusivity, compared to when all nine strains are present (Figure \@ref(fig:max-tol1)).
-A corresponding simulations from which the position of the tipping points are calculated are shown in Figures \@ref(fig:max-tol2) (nine strains) and \@ref(fig:max-tol3) (most tolerant strain only).
-We see that the effect of oxygen diffusivity on the stable state is quite different in the case of only the most tolerant strain only--at low oxygen diffusivity there is variation around a stable state with all three functional groups coexisting--this never occured when there were multiple strains varying in tolerance, or when there was only one strain with mean tolerance.
-Furthermore, the state of the system is independent of the direction of change in oxygen diffusivity.
-I.e.
-there is no region of bistability (no alternate stable states).
-
-We now wish to return to an aspect of the reviewer comment: It is correct that in Fig.
-4 when oxygen diffusivity increased, the two dominant functional groups (the sulfur bacteria groups) are dominated by the most tolerant strain before the state transition.
-And when oxygen diffusivity decreased, the dominant functional group (the cyanobacteria) is dominated by the most tolerant strain before the state transition.
-It is worth noting, however, that the transitions that occur are to states dominated by the least tolerant-highest growth rate strain.
-This raises the possibility that less tolerant strains may influence the results.
-
-Indeed, in the SB case, absence of the high growth rate SB strain precludes the formation of a stable state that does not include cyanobacteria.
+## High tolerance vs. high diversity in only the SB
+
+When the SB contained only one strain with very high tolerance and low maximum growth rate, there were no alternate stable states, i.e.
+the state of the system was independent of the direction of change in oxygen diffusivity (Figure \@ref(fig:max-tol3)).
+Furthermore, at low oxygen diffusivity the system varied around a stable state with all three functional groups coexisting –this never occurred when there were multiple strains varying in tolerance (Figure \@ref(fig:max-tol2)), or when there was only one strain with mean tolerance.
+
+Apparently, absence of SB strains with high growth rate precludes the formation of a stable state that does not include cyanobacteria.
 It seems that the most tolerant SB strain does not have a high enough growth rate to itself exclude the cyanobacteria.
 Cyanobacteria are therefore always present, regardless of the oxygen diffusivity.
-The stable states of the system then display a complex relationship with oxygen diffusivity that our algorithm for detecting tipping points is not well suited to, hence the rather odd positions of the indicated tipping points.
-
-(ref:max-tol2) Stable states found with nine strains of SB and high diversity. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+
+(ref:max-tol2) Relationship of ecosystem state variables and oxygen diffusivity when there is variation among nine strains of SB and the amount of variation is high.
+All other aspects are the same as in Figure \@ref(fig:repl-meth2).
 
@@
 
-(ref:max-tol3) Stable states found with the single most tolerant SB and high diversity.
+(ref:max-tol3) Relationship of ecosystem state variables and oxygen diffusivity when SB contained only the most tolerant strain, with trait values corresponding with the diversity level of the previous figure.
 All other aspects are the same as in Figure \@ref(fig:repl-meth2).
-As mentioned in the text, the algorithm used to detect the position of the tipping points is not working correctly here, and so the grey arrows should be ignored.
 
@@
 
-In the ecosystem shown in Figure \@ref(fig:max-tol3), where there was quite high tolerance SB strain, there was large variation in state variables along the oxygen diffusivity gradient at values less than about -4.5.
+In the ecosystem shown in Figure \@ref(fig:max-tol3), where the SB contained one strain with quite high tolerance, there was large variation in state variables along the oxygen diffusivity gradient at values less than about -4.5.
 To examine what might be causing this, we simulated the ecosystem at a constant oxygen diffusivity of $log_{10}$ oxygen diffusivity of -6 (Figure \@ref(fig:SB-maxtol-dyn1)).
-We see that the dynamics are qualitatively different from other cases in which there is a stable state reached in such a simulation.
-It appears that the high tolerance SB strain is able to initiate a transition to an anoxic state, but is not able to create a stable anoxic stable state.
+We see that the dynamics are qualitatively different from other cases in which there is a stable state reached in such a simulation (Figure \@ref(fig:sb-div-effect4)).
+It appears that the high tolerance SB strain is able to initiate a transition to an anoxic state, but is not able to create a stable anoxic state.
 This dynamical situation was not presented in the ecosystem in which high tolerance and low tolerance strains were present.
@@
 
-(ref:SB-maxtol-dyn1) Temporal dynamics of an ecosystem with a single SB strain with high tolerance, the same one as in Figure \@ref(fig:max-tol3) simulated with constant $log_{10}(oxygen diffusivity) of -6.
+(ref:SB-maxtol-dyn1) Temporal dynamics of an ecosystem with a single SB strain with high tolerance, the same one as in Figure \@ref(fig:max-tol3) simulated with constant $log_{10}$ oxygen diffusivity of -6.
 
@@
 
-## CB-SB only, high diversity
+## High diversity vs. high tolerance in CB and SB
 
@@
 
-(ref:max-tol5)  Stable states found with the single most tolerant CB strain and SB strain and high diversity.
-All other aspects are the same as in Figure \@ref(fig:repl-meth2).
-As mentioned in the text, the algorithm used to detect the position of the tipping points is not working correctly here, and so the grey arrows should be ignored.
+(ref:max-tol5)  Stable states found with the single most tolerant CB strain and SB strain and high diversity. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
 

### 2022-10-03 experiments/2_supplement/supplement.Rmd
changes to supplement

@@
 in the combinations SB only, CB-SB, and CB-SB-PB).
+We show below that
 
@@
 
-(ref:max-tol2) Relationship of ecosystem state variables and oxygen diffusivity when there is variation among nine strains of SB and the amount of variation is high.
-All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+(ref:max-tol2) Stable states found when there is variation among nine strains of SB and the amount of variation is high. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
 
@@
 
-(ref:max-tol3) Relationship of ecosystem state variables and oxygen diffusivity when SB contained only the most tolerant strain, with trait values corresponding with the diversity level of the previous figure.
+(ref:max-tol3) Stable states found when SB contained only the most tolerant strain, with trait values corresponding with the diversity level of the previous figure.
 All other aspects are the same as in Figure \@ref(fig:repl-meth2).
@@
 
-In the ecosystem shown in Figure \@ref(fig:max-tol3), where the SB contained one strain with quite high tolerance, there was large variation in state variables along the oxygen diffusivity gradient at values less than about -4.5.
+In the ecosystem shown in Figure \@ref(fig:max-tol3), where the SB contained one strain with very high tolerance, there was large variation in state variables along the oxygen diffusivity gradient at values less than about -4.5.
 To examine what might be causing this, we simulated the ecosystem at a constant oxygen diffusivity of $log_{10}$ oxygen diffusivity of -6 (Figure \@ref(fig:SB-maxtol-dyn1)).
@@
 It appears that the high tolerance SB strain is able to initiate a transition to an anoxic state, but is not able to create a stable anoxic state.
-This dynamical situation was not presented in the ecosystem in which high tolerance and low tolerance strains were present.
+This dynamical situation was not present in the ecosystem in which high tolerance and low tolerance strains were present.
 
@@
 
-## High diversity vs. high tolerance in CB and SB
+## High tolerance vs. high diversity in CB and SB
 
@@
 
-(ref:max-tol4)  Stable states found with nine strains of CB and SB and high diversity. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+(ref:max-tol4)  Stables states found when there is high trait variation among nine strains of CB and SB. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
 
@@
 
-(ref:max-tol5)  Stable states found with the single most tolerant CB strain and SB strain and high diversity. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+(ref:max-tol5)  Stable states found when CB and SB each contain only the single most tolerant strain with trait values corresponding with the diversity level of the previous figure.
+All other aspects are the same as in Figure \@ref(fig:repl-meth2).
 
@@
 
-In the ecosystem shown in Figure \@ref(fig:max-tol5), where there was quite high tolerance CB strain and SB strain, there was large variation in state variables along the oxygen diffusivity gradient at values less than about -6.5.
+In the ecosystem shown in Figure \@ref(fig:max-tol5), where CB and SB each contained only one strain with very high tolerance, there was large variation in state variables along the oxygen diffusivity gradient at values less than about -6.5.
 To examine what might be causing this, we simulated the ecosystem at a constant oxygen diffusivity of $log_{10}$ oxygen diffusivity of -6 (Figure \@ref(fig:CBSB-maxtol-dyn1)).
-We see that the dynamics are qualitatively different from other cases in which there is a stable state reached in such a simulation.
-It appears that the high tolerance SB strain is able to initiate a transition to an anoxic state, but is not able to create a stable anoxic stable state.
+We see that the dynamics are qualitatively different from other cases in which there is a stable state reached in such a simulation (Figure \@ref(fig:sb-div-effect4)).
+It appears that the SB strain with high tolerance is able to initiate a transition to an anoxic state, but is not able to create a stable anoxic state.
 
@@
 
-## CB-SB-PB, high diversity
-
-In the CB-SB-PB case when only the most tolerant strain of all functional groups is present, the resilience of the oxic state is greater than when variation in strain tolerance is present.
-Looked at from another perspective, comparing CB-SB and CB-SB-PB both with only the most tolerant strains, we see that presence of a high tolerance PB strain (in CB-SB-PB) allows the formation of an anoxic cyanobacteria-free stable state (whereas there was no such state in CB-SB).
+## High tolerance vs. high diversity in CB-SB-PB
+
+When in each of the three functional groups only the most tolerant strain is present, the resilience of the oxic state is greater than when there is variation in strain tolerance within groups.
+Looked at from another perspective, comparing CB-SB and CB-SB-PB both with only the most tolerant strains, presence of a high tolerance PB strain (in CB-SB-PB) allows the formation of an anoxic cyanobacteria-free stable state (whereas there was no such state in CB-SB).
 We interpret this as presence of a high tolerance PB strain stabilising the anoxic state, perhaps by increasing the availability of oxidised sulfur which is a resource for SB.
+Nevertheless, absence of SB strains with high growth rate seems to shift the oxic-anoxic tipping point to lower oxygen diffusivity.
 
@@
 
-(ref:max-tol7) Stable states found with the single most tolerant CB strain, SB strain, and PB strain, and high diversity. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+(ref:max-tol7) Stable states found with the single most tolerant CB strain, SB strain, and PB strain, with trait values corresponding with the diversity level in the previous figure.
+All other aspects are the same as in Figure \@ref(fig:repl-meth2).
 
@@
 
-### Why only at high diversity?
-
-Why do these effects only occur at high diversities?
-The likely reason is that at high diversities then the most tolerant strain has particularly low growth rate, and so it may have the tolerance required to increase and persist, it does not have the growth rate required to dominate.
+## Why only at high diversity/tolerance?
+
+Why do these effects only occur at high diversity/tolerance?
+The likely reason is that at high diversities the most tolerant strain has particularly low growth rate, and so it may have the tolerance required to increase and persist, but not the growth rate required to dominate.
 

### 2022-10-05 experiments/2_supplement/supplement.Rmd
Update supplement.Rmd

@@
 
-### What causes variation in response to oxygen diffusivity (SB)?
+### What causes the variation in response to oxygen diffusivity (SB)?
 
@@
 
-### What causes variation in response to oxygen diffusivity (CB-SB)?
+### What causes the variation in response to oxygen diffusivity (CB-SB)?
 
 In the ecosystem shown in Figure \@ref(fig:max-tol5), where CB and SB each contained only one strain with very high tolerance, there was large variation in state variables along the oxygen diffusivity gradient at values less than about -6.5.
-To examine what might be causing this, we simulated the ecosystem at a constant oxygen diffusivity of $log_{10}$ oxygen diffusivity of -6 (Figure \@ref(fig:CBSB-maxtol-dyn1)).
+To examine what might be causing this, we simulated the ecosystem at a constant oxygen diffusivity of $log_{10}$ oxygen diffusivity of -7 (Figure \@ref(fig:CBSB-maxtol-dyn1)).
 We see that the dynamics are qualitatively different from other cases in which there is a stable state reached in such a simulation (Figure \@ref(fig:sb-div-effect4)).
@@
 
-(ref:CBSB-maxtol-dyn1) Temporal dynamics of an ecosystem with a single CB strain with high tolerance and a single SB strain with high tolerance, the same one as in Figure \@ref(fig:max-tol5) simulated with constant $log_{10}(oxygen diffusivity) of -6.
+(ref:CBSB-maxtol-dyn1) Temporal dynamics of an ecosystem with a single CB strain with high tolerance and a single SB strain with high tolerance, the same one as in Figure \@ref(fig:max-tol5) simulated with constant $log_{10}(oxygen diffusivity)$ of -6.
 

### 2022-10-23 reports/animations/report.Rmd
large revision
Completely restructured and updated to microxanox version 0.9.1

---
title: "State change and diversity animations"
author: "Owen Petchey"
date: "6/1/2022"
output:
  bookdown::html_document2:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(here)
```

# Cyanobacteria

## No diversity

```{r}
include_graphics(here("experiments/3_animate/mp4s/CB_no_div.mp4"))
```

## Some diversity

```{r}
include_graphics(here("experiments/3_animate/mp4s/CB_medium_div.mp4"))
```

# Sulfate reducing bacteria

## No diversity

```{r}
include_graphics(here("experiments/3_animate/mp4s/SB_no_div.mp4"))
```

## Some diversity

```{r}
include_graphics(here("experiments/3_animate/mp4s/SB_medium_div.mp4"))
```

# Phototrophic sulfur bacteria

## No diversity

```{r}
include_graphics(here("experiments/3_animate/mp4s/PB_no_div.mp4"))
```

## Some diversity

```{r}
include_graphics(here("experiments/3_animate/mp4s/PB_medium_div.mp4"))
```

# Oxygen concentration

## No diversity

```{r}
include_graphics(here("experiments/3_animate/mp4s/O_no_div.mp4"))
```

## Some diversity

```{r}
include_graphics(here("experiments/3_animate/mp4s/O_medium_div.mp4"))
```

# Reduced sulfur concentration

## No diversity

```{r}
include_graphics(here("experiments/3_animate/mp4s/SR_no_div.mp4"))
```

## Some diversity

```{r}
include_graphics(here("experiments/3_animate/mp4s/SR_medium_div.mp4"))
```

# Sulfate concentration

## No diversity

```{r}
include_graphics(here("experiments/3_animate/mp4s/SO_no_div.mp4"))
```

## Some diversity

```{r}
include_graphics(here("experiments/3_animate/mp4s/SO_medium_div.mp4"))
```

# Phospate concentration

## No diversity

```{r}
include_graphics(here("experiments/3_animate/mp4s/P_no_div.mp4"))
```

## Some diversity

```{r}
include_graphics(here("experiments/3_animate/mp4s/P_medium_div.mp4"))
```

### 2022-10-23 reports/old/checks_puzzles/checks_puzzles.Rmd
large revision
Completely restructured and updated to microxanox version 0.9.1

--- 2021-11-13 experiments/checks_puzzles/checks_puzzles.Rmd
@@
 
-## Setup parameter
+## Setup and processing
 
-```{r}
+Run a shorter sim:
+
+```{r eval = eval_dynamics_flag}
+
+sim_length <- 100000
+
 options(mc.cores = 7)
@@
   event_definition = parameter$event_definition,
-  event_interval = 100000,
+  event_interval = sim_length,
   noise_sigma = parameter$noise_sigma,
   minimum_abundances = minimum_abundances,
-  sim_duration = 100000,  ##    Was 1e6
-  sim_sample_interval = 100000,
+  sim_duration = sim_length,  ##    Was 1e6
+  sim_sample_interval = sim_length,
   log10a_series = parameter$log10a_series,
@@
 
-### Run stable state finding
-
 *Careful, this simulation takes about 600 hours on a single core
@@
   var_expt = readRDS(here("experiments/checks_puzzles/data/var_expt_1e5_x2x6_factorial.RDS"))) %>%
-saveRDS(here("experiments/checks_puzzles/data/ss_data_1e6_x2x5_factorial.RDS"))
+  saveRDS(here("experiments/checks_puzzles/data/ss_data_1e5_x2x6_factorial.RDS"))
 ```
-
-### Process the stable state data
 
@@
 
-```{r, eval = FALSE, echo = FALSE}
+## Visualise
+
+```{r}
 var_expt1 <- readRDS(here("experiments/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
@@
 p1_short  <- plot_ss_result1(var_expt2,
-                result_index = max_diversty_all,
+                result_index = nrow(var_expt2),
                 filename_prefix = NULL,
@@
 p1_long  <- plot_ss_result1(var_expt1,
-                result_index = max_diversty_all,
+                result_index = nrow(var_expt1),
                 filename_prefix = NULL,
@@
 
-# Puzzle 1
+## Continute here to check the stability measures.
+
+# Hidden effect of sulphur bacteria diversity
 
@@
 
-```{r, eval = FALSE, echo = FALSE}
+```{r}
 sim_res_novar1 <- readRDS(here("experiments/checks_puzzles/data/puzzle1_1.RDS"))
@@
 
-```{r eval = FALSE, echo = FALSE}
+```{r eval = eval_dynamics_flag}
 parameter$strain_parameter <- var_expt[max_only_SBPB_diversity,]$pars[[1]]
@@
 
-```{r, eval = FALSE, echo = FALSE}
+```{r}
 sim_res_highvar1 <- readRDS(here("experiments/checks_puzzles/data/puzzle1_2.RDS"))
@@
 
-## Zoom in on SS
+# Zoom in on SS
 
@@
 
-## Negative abundance investigation
+# Negative abundance investigation
 
@@
 
-## Understand about relative and absolute variation in traits
+# Understand about relative and absolute variation in traits
 

### 2022-10-23 reports/supplement/supplement_0.9.1.Rmd
large revision
Completely restructured and updated to microxanox version 0.9.1

--- 2022-10-05 experiments/2_supplement/supplement.Rmd
@@
 # source(here("experiments", "1_figures_main_ms", "ms_figure_functions.r"))
-source(here("experiments", "1_figures_main_ms", "figures_main_ms_v1.R"))
+source(here("R/ms_figure_functions.R"))
 
@@
 unity <- 1
+```
+
+```{r}
+microxanox_version_here <- "0.9.1"
+microxanox_version_path <- paste0("microxanox_v", microxanox_version_here)
+if (packageVersion("microxanox") < package_version(microxanox_version_here)) {
+  stop(paste0("microxanox version needs to be at least ", microxanox_version_here))
+}
+print(paste0("Version of microxanox: ", microxanox_version_here))
 ```
@@
 ```{r repl-meth1, echo=FALSE, eval = TRUE}
-repl_meth <- readRDS(here("data", "0_ss_finding", "replication_method", "ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
-temp_meth <- readRDS(here("data", "0_ss_finding", "temporal_method", "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
+repl_meth <- readRDS(here("data",
+                          microxanox_version_path,
+                          "replication_method",
+                          "event_definition_2",
+                          "ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
+temp_meth <- readRDS(here("data",
+                          microxanox_version_path,
+                          "temporal_method",
+                          "event_definition_2",
+                          "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
 ```
@@
 ```{r both-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:both-meth1)', fig.height=8, fig.width=8, fig.align="center"}
+
 repl_method_1 <- repl_meth$ss_res[[1]] %>%
@@
 ```{r div-repl-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-repl-meth1)', fig.height=8, fig.width=8, fig.align="center"}
-all_stab <- readRDS(here("data", "0_ss_finding", "replication_method", "processed_data", "stab_data_replication_method.RDS"))
-
-sim_length <- 1e6
+all_stab <- readRDS(here("data", 
+                         microxanox_version_path,
+                         "replication_method",
+                         "event_definition_2",
+                         "processed_data",
+                         "all_stab_data.RDS"))
+
+sim_length <- 1e6 ## currently a problem in how sim length is parsed by the data processing step
 num_strains <- 9
@@
 ```{r repl-meth-ex1, echo = FALSE,  include=TRUE, fig.cap='(ref:repl-meth-ex1)', fig.height=10, fig.width=8, fig.align="center"}
-repl_meth <- readRDS(here("data", "0_ss_finding", "replication_method", "ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
+repl_meth <- readRDS(here("data",
+                          microxanox_version_path,
+                          "replication_method",
+                          "event_definition_2",
+                          "ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
 fig_state_vs_o2diff_sidebyside_alternative(repl_meth[94,])
@@
 
-```{r div-temp-eventdef1, eval = TRUE, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-eventdef1)', fig.height=8, fig.width=8, fig.align="center"}
-all_stab <- readRDS(here("data", "0_ss_finding", "temporal_method", "event_def1", "processed_data", "stab_data_temporal_method.RDS"))
-
-wait_time <- 1e6
+```{r div-temp-eventdef1, eval = FALSE, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-eventdef1)', fig.height=8, fig.width=8, fig.align="center"}
+all_stab <- readRDS(here("data",
+                          microxanox_version_path,
+                          "temporal_method",
+                          "event_definition_1",
+                          "processed_data",
+                         "all_stab_data.RDS"))
+
+sim_length <- 1e6
 num_strains <- 9
@@
 ```{r div-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth1)', fig.height=7, fig.width=6, fig.align="center"}
-all_stab <- readRDS(here("data", "0_ss_finding", "temporal_method", "processed_data", "stab_data_temporal_method.RDS"))
+all_stab <- readRDS(here("data",
+                         microxanox_version_path,
+                         "temporal_method",
+                         "event_definition_2",
+                         "processed_data",
+                         "all_stab_data.RDS"))
 
@@
 
-```{r ss-temp-meth3, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth3)', fig.height=10, fig.width=8, fig.align="center"}
-single_1e6 <- readRDS(here("data", "0_ss_finding", "temporal_method", "single_1e6_result.RDS"))
+```{r ss-temp-meth3, eval = FALSE, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth3)', fig.height=10, fig.width=8, fig.align="center"}
+
+## data made with the "run_single_sim.r" file in the ss_find, temporal method folder.
+
+single_1e6 <- readRDS(here("data",
+                           microxanox_version_path, 
+                           "temporal_method",
+                           "single_sims",
+                           "single_1e6_result.RDS"))
 temp_meth[1,]$ssfind_result[[1]] <- single_1e6
@@
 
-```{r ss-temp-meth4, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth4)', fig.height=10, fig.width=8, fig.align="center"}
-single_2e6 <- readRDS(here("data", "0_ss_finding", "temporal_method", "single_2e6_result.RDS"))
+```{r ss-temp-meth4, eval = FALSE, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth4)', fig.height=10, fig.width=8, fig.align="center"}
+single_2e6 <- readRDS(here("data",
+                           microxanox_version_path, 
+                           "temporal_method",
+                           "single_sims",
+                           "single_2e6_result.RDS"))
 temp_meth[1,]$ssfind_result[[1]] <- single_2e6
@@
 wait_time <- "1e+04"
-ss_9s <- readRDS(here::here("data", "0_ss_finding", "temporal_method", paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
-#stab_9s <- readRDS(here::here(\"data", "0_ss_finding", "temporal_method", paste0("stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS"))
+ss_9s <- readRDS(here::here("data",
+                            microxanox_version_path, 
+                            "temporal_method",
+                            "event_definition_2",
+                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+#stab_9s <- readRDS(here::here(\"data", "0_ss_finding", "temporal_method", microxanox_version_path, paste0("stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS"))
 
@@
 
-fig_state_vs_o2diff_sidebyside_alternative(only_SB_variable[13,])
+fig_state_vs_o2diff_sidebyside_alternative(only_SB_variable[14,])
 
@@
 ```{r ss-temp-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth2)', fig.height=10, fig.width=8, fig.align="center"}
-fig_state_vs_o2diff_sidebyside_alternative(only_SB_variable[14,])
+fig_state_vs_o2diff_sidebyside_alternative(only_SB_variable[15,])
 ```
@@
 ```{r eval = run_sims_this_section, echo = FALSE}
-#var_expt <- readRDS(here::here("data", "9_strains", "ss_data_1e6_x2x6_factorial.RDS"))
 var_expt_levels <- var_expt[,1:6]
@@
 sim_res_novar1 <- run_simulation(parameter)
-dir.create(here::here("data", "2_supplement"), recursive = TRUE, showWarnings = FALSE)
-saveRDS(sim_res_novar1, here::here("data", "2_supplement", "puzzle1_1.RDS"))
+
+saveRDS(sim_res_novar1, here("data",
+                             microxanox_version_path,
+                             "temporal_method",
+                             "puzzles",
+                             "puzzle1_1.RDS"))
 ```
@@
 ```{r  sb-div-effect3, echo = FALSE,  include=TRUE, fig.cap='(ref:sb-div-effect3)', fig.height=8, fig.width=8, fig.align="center"}
-sim_res_novar1 <- readRDS(here::here("data", "2_supplement", "puzzle1_1.RDS"))
+sim_res_novar1 <- readRDS(here("data",
+                             microxanox_version_path,
+                             "temporal_method",
+                             "puzzles",
+                             "puzzle1_1.RDS"))
 p <- plot_dynamics(sim_res_novar1)
@@
 sim_res_highvar1 <- run_simulation(parameter)
-saveRDS(sim_res_highvar1,here::here("data", "2_supplement", "puzzle1_2.RDS"))
+saveRDS(sim_res_highvar1,
+        here("data",
+             microxanox_version_path,
+             "temporal_method",
+             "puzzles",
+             "puzzle1_2.RDS"))
 ```
@@
 ```{r sb-div-effect4, echo = FALSE,  include=TRUE, fig.cap='(ref:sb-div-effect4)', fig.height=8, fig.width=8, fig.align="center"}
-sim_res_highvar1 <- readRDS(here("data", "2_supplement", "puzzle1_2.RDS"))
+sim_res_highvar1 <- readRDS(here("data",
+             microxanox_version_path,
+             "temporal_method",
+             "puzzles",
+             "puzzle1_2.RDS"))
 
@@
 ```{r echo = FALSE}
-ss_9s <- readRDS(here::here("data", "0_ss_finding", "temporal_method", "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
+ss_9s <- readRDS(here("data",
+                            microxanox_version_path,
+                            "temporal_method",
+                            "event_definition_2",
+                            "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
 only_PB_variable <- ss_9s %>%
@@
 
-only_PB_stab <- readRDS(here::here("data", "0_ss_finding", "temporal_method", "processed_data", "stab_data_temporal_method.RDS")) %>%
+only_PB_stab <- readRDS(here("data",
+                                   microxanox_version_path,
+                                   "temporal_method",
+                                   "event_definition_2",
+                                   "processed_data",
+                                   "all_stab_data.RDS")) %>%
   filter(
@@
 
-stab_9s <- readRDS(here("data", "0_ss_finding", "temporal_method", "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
+stab_9s <- readRDS(here("data", 
+                        microxanox_version_path,
+                        "temporal_method", 
+                        "event_definition_2",
+                        "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
 
@@
 ```{r div-stab-multstrain1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-stab-multstrain1)', fig.height=8, fig.width=8, fig.align="center"}
-all_stab <- readRDS(here("data", "0_ss_finding", "temporal_method", "processed_data", "stab_data_temporal_method.RDS"))
+all_stab <- readRDS(here("data",
+                         microxanox_version_path,
+                         "temporal_method", 
+                         "event_definition_2",
+                         "processed_data", "all_stab_data.RDS"))
 which_strains <- c(2, 3, 6, 9)
@@
 
-## here the version with only one strain per group
-all_stab <- readRDS(here("data", "0_ss_finding", "temporal_method",
-                         "ele_rev1.1",
-                         "stab_data_temporal_method_ELErevision1.1.RDS"))
+## read the data
+all_stab <- readRDS(here("data",
+                         microxanox_version_path,
+                         "temporal_method", 
+                         "event_definition_2",
+                         "processed_data",
+                         "all_stab_data.RDS"))
 
@@
 nine_strains <- readRDS(here("data",
-                          "0_ss_finding",
-                          "temporal_method",
+                         microxanox_version_path,
+                         "temporal_method", 
+                         "event_definition_2",
                           "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
 maxtolonly_strains <- readRDS(here("data",
-                          "0_ss_finding",
-                          "temporal_method",
-                          "ele_rev1.1",
+                         microxanox_version_path,
+                         "temporal_method", 
+                         "event_definition_2",
                           "ss_data_-1strains_waittime1e+06_event_definition_2.RDS"))
@@
 
-all_stab_results_small <- readRDS(here("data/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS"))
+all_stab_results_small <- readRDS(here("data",
+                         microxanox_version_path,
+                         "temporal_method", 
+                         "event_definition_2",
+                         "processed_data", "all_stab_data.RDS"))
 

### 2022-10-23 R/make_data_folders.R

@@ -1,0 +1,34 @@
+## make data folder structure
+
+result <- NA
+
+if(dir.exists(here("data",
+                   microxanox_path)))
+  result <- paste0("Data folders exist already for results using ", microxanox_path)
+
+if(!dir.exists(here("data",
+                   microxanox_path))) {
+  result <- paste0("New folders created for results using ", microxanox_path)
+  res1 <- dir.create(here("data",
+                          microxanox_path,
+                          "temporal_method",
+                          "event_definition_1",
+                          "processed_data"),
+                     recursive = TRUE)
+  res2 <- dir.create(here("data",
+                          microxanox_path,
+                          "temporal_method",
+                          "event_definition_2",
+                          "processed_data"),
+                     recursive = TRUE)
+  res3 <- dir.create(here("data",
+                          microxanox_path,
+                          "temporal_method",
+                          "puzzles"))
+  res4 <- dir.create(here("data",
+                          microxanox_path,
+                          "temporal_method",
+                          "single_sims"))
+  if(res1 & res2 & res3 & res4)
+    result <- paste0("New folders created for results using ", microxanox_path)
+}

### 2022-10-23 experiments/0_ss_finding/replication_method/run_experiment.R

@@ -1,67 +1,0 @@
-## SS finding experiment by replication method
-## Be careful to not overwrite data files
-
-rm(list = ls())
-source(here::here("R/various_useful_functions.r"))
-max_cores <- benchmarkme::get_cpu()$no_of_cores-2
-options(mc.cores = max_cores)
-
-sim_length <- 1e6
-event_def <- "event_definition_2" ## not relevant, since no events occur
-
-## Run for 2, 3, 6, and 9 strains
-#for(num_strains in c(2, 3, 6, 9)) {
-
-  num_strains <- 9 ## for testing
-
-  ## Run the code that sets up the experiment
-  source(here::here("experiments/0_ss_finding/replication_method/setup_experiment.R"))
-
-  datadir <- here::here("data/0_ss_finding/replication_method/")
-  dir.create(datadir, showWarnings = FALSE, recursive = TRUE)
-  
-  ss_data_filename <- file.path(datadir,
-                                paste0("test_ss_data_",
-                                       num_strains, "strains_sim_length",
-                                       formatC(sim_length, format = "e", digits = 0),
-                                       "_", event_def,".RDS"))
-  stab_data_filename <- file.path(datadir,
-                                  paste0("test_stab_data_",
-                                         num_strains, "strains_sim_length",
-                                         formatC(sim_length, format = "e", digits = 0),
-                                         "_", event_def,".RDS"))
-
-  var_expt <- var_expt[1,]
-
-  system.time(
-    run_replication_ssfind_experiment(parameter, var_expt) %>%
-      saveRDS(ss_data_filename)
-  )
-
-
-
-  ## Get stability measures ----
-  num_cores <- min(c(max_cores, nrow(var_expt)))
-  expt_res <- readRDS(ss_data_filename)
-  ## Get total biomass of CB, of SB, and of PB, to allow calculation of stability of these
-  expt_res <- expt_res %>%
-    mutate(ss_res = list(get_total_bio(ss_res)))
-  cluster1 <- multidplyr::new_cluster(num_cores)
-  multidplyr::cluster_library(cluster1, c("microxanox", "dplyr"))
-  system.time({
-    stab_data <-  expt_res %>%
-      multidplyr::partition(cluster1) %>%
-      mutate(stability_measures = list(get_stability_measures_replication_ssfind_result(ss_res))) %>%
-      collect() %>%
-      unnest(cols = c(stability_measures)) %>%
[…]

### 2022-10-23 experiments/0_ss_finding/temporal_method/check_microxanox_version.R

@@ -1,7 +1,0 @@
-## package version check
-
-if (packageVersion("microxanox") < package_version(microxanox_release)) {
-  stop(paste0("microxanox version needs to be at least ", microxanox_release))
-}
-
-print(paste0("Version of microxanox: ", microxanox_release))

### 2022-10-23 experiments/0_ss_finding/temporal_method/data_processing.R

@@ -1,236 +1,0 @@
-
-
-library(here)
-library(tidyverse)
-
-## Process the stability data to a smaller file
-
-##  event def2 ----
-
-read_plus <- function(flnm) {
-  print(flnm)
-  readRDS(flnm) %>% 
-    mutate(filename = flnm)
-}
-
-tbl1 <- list.files(path = here::here("data/0_ss_finding/temporal_method"),
-                   pattern = "stab_data", 
-                   full.names = TRUE,
-                   recursive = FALSE) %>% 
-  map_df(~read_plus(.))
-
-keep_tbl1 <- tbl1
-
-all_stab <- tbl1 %>%
-  select(-data, -pars, -parameter, -total_initial_abundances, -ssfind_pars, -ssfind_result) %>%
-  separate(filename , sep = "_", into = c(paste0("junk", 1:7), "waittime", paste0("junk", 8:10))) %>%
-  select(-starts_with("junk")) %>%
-  mutate(waittime = parse_number(waittime))
-
-
-
-CB_vars <- unique(all_stab$CB_var_gmax_s)
-SB_vars <- unique(all_stab$SB_var_gmax_s)
-PB_vars <- unique(all_stab$PB_var_gmax_s)
-
-CB_all_stab <- all_stab %>%
-  filter(SB_var_gmax_s == 0,
-         PB_var_gmax_s == 0) %>%
-  ungroup() %>%
-  mutate(var_treat = "CB",
-         var_gmax = CB_var_gmax_s,
-         stand_var = var_gmax / max(var_gmax))
-SB_all_stab <- all_stab %>%
-  filter(CB_var_gmax_s == 0,
-         PB_var_gmax_s == 0)  %>%
-  ungroup() %>%
-  mutate(var_treat = "SB",
-         var_gmax = SB_var_gmax_s,
-         stand_var = var_gmax / max(var_gmax))
-PB_all_stab <- all_stab %>%
-  filter(CB_var_gmax_s == 0,
-         SB_var_gmax_s == 0) %>%
-  ungroup()  %>%
-  mutate(var_treat = "PB",
-         var_gmax = PB_var_gmax_s,
-         stand_var = var_gmax / max(var_gmax))
-
-for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
-                   SB_var_gmax_s = sort(SB_vars))
-CBSB_all_stab <- all_stab %>%
-  right_join(for_join)  %>%
[…]

### 2022-10-23 experiments/0_ss_finding/temporal_method/run_experiment.R

@@ -1,89 +1,0 @@
-## SS finding experiment by temporal method
-## Be careful to not overwrite data files
-
-rm(list = ls())
-source(here::here("R/various_useful_functions.r"))
-max_cores <- benchmarkme::get_cpu()$no_of_cores-2
-
-
-## Run for 2, 3, 6, and 9 strains
-for(num_strains in c(2, 3, 6, 9)) {
-
-  #num_strains <- 2 ## for testing
-    
-  ## Run the code that sets up the experiment
-  source(here::here("experiments/0_ss_finding/temporal_method/setup_experiment.R"))
-  
-  datadir <- here::here("data/0_ss_finding/temporal_method/")
-  dir.create(datadir, recursive = TRUE, showWarnings = FALSE)
-  
-  ss_data_filename <- file.path(datadir,
-                                paste0("ss_data_",
-                                       num_strains, "strains_waittime",
-                                       formatC(wait_time, format = "e", digits = 0),
-                                       "_", event_def,".RDS"))
-  stab_data_filename <- file.path(datadir,
-                                  paste0("stab_data_",
-                                         num_strains, "strains_waittime",
-                                         formatC(wait_time, format = "e", digits = 0),
-                                         "_", event_def,".RDS"))
-  
-  ## Estimate time require ----
-  nrow(var_expt)
-  wait_time
-  length(parameter$log10a_series)
-  num_cores <- min(c(max_cores, nrow(var_expt)))
-  ## constants in following formula come from the excel sheet
-  time_estimate <- ( nrow(var_expt) * wait_time * length(parameter$log10a_series) /
-                       num_cores * 0.000123965 + 126 )
-  time_estimate
-  time_estimate / 60 ## minutes
-  time_estimate / 60 / 60 ## hours
-  time_estimate / 60 / 60 / 24 ## days
-  
-  ## Run experiment ----
-  system.time({
-    expt_res <- run_temporal_ssfind_experiment(parameter,
-                                               var_expt,
-                                               total_initial_abundances = total_initial_abundances,
-                                               cores = num_cores)
-  })
-  saveRDS(expt_res, ss_data_filename)
-  ## End of run experiment
-  
-  
-  
-  ## Get stability measures ----
-  num_cores <- min(c(max_cores, nrow(var_expt)))
-  expt_res <- readRDS(ss_data_filename)
[…]

### 2022-10-23 experiments/0_ss_finding/temporal_method/run_experiment_onestrain.R

@@ -1,105 +1,0 @@
-## SS finding experiment by temporal method
-## Be careful to not overwrite data files
-
-rm(list = ls())
-source(here::here("R/various_useful_functions.r"))
-max_cores <- benchmarkme::get_cpu()$no_of_cores-2
-
-
-## setup experiment with two strains
-num_strains <- 2
-source(here::here("experiments/0_ss_finding/temporal_method/setup_experiment.R"))
-
-## keep only the most tolerant strain
-#var_expt <- var_expt[1:2,]
-for(i in 1:nrow(var_expt)) {
-  temp_pars <- var_expt$pars[i][[1]]
-  temp_pars$CB <- temp_pars$CB[which(temp_pars$CB$h_SR_CB==max(temp_pars$CB$h_SR_CB))[1],]
-  temp_pars$PB <- temp_pars$PB[which(temp_pars$PB$h_O_PB==max(temp_pars$PB$h_O_PB))[1],]
-  temp_pars$SB <- temp_pars$SB[which(temp_pars$SB$h_O_SB==max(temp_pars$SB$h_O_SB))[1],]
-  initial_subtrates <- temp_pars$initial_state[!str_detect(names(temp_pars$initial_state), "B_")]
-  temp_pars$initial_state <- c(NA, NA, NA, initial_subtrates)
-  names(temp_pars$initial_state) <- c("CB_1", "PB_1", "SB_1", names(initial_subtrates))
-  var_expt$pars[i][[1]] <- temp_pars
-}
-num_strains <- -1 ## use this to label that only the most tolerant strain is kept
-
-
-datadir <- here::here("data/0_ss_finding/temporal_method")
-dir.create(datadir, recursive = TRUE, showWarnings = FALSE)
-
-ss_data_filename <- file.path(datadir,
-                              paste0("ss_data_",
-                                     num_strains, "strains_waittime",
-                                     formatC(wait_time, format = "e", digits = 0),
-                                     "_", event_def, ".RDS"))
-stab_data_filename <- file.path(datadir,
-                                paste0("stab_data_",
-                                       num_strains, "strains_waittime",
-                                       formatC(wait_time, format = "e", digits = 0),
-                                       "_", event_def, ".RDS"))
-
-
-
-## Estimate time require ----
-nrow(var_expt)
-wait_time
-length(parameter$log10a_series)
-num_cores <- min(c(max_cores, nrow(var_expt)))
-## constants in following formula come from the excel sheet
[…]

### 2022-10-23 experiments/0_ss_finding/temporal_method/setup_experiment.R

@@ -1,137 +1,0 @@
-## see file R/how_to_install_microxanox for (surprise) how to install the microxanox package
-
-library(here)
-microxanox_release <- "0.9.1"
-library(microxanox)
-source(here::here("experiments/0_ss_finding/temporal_method/check_microxanox_version.R"))
-library(tidyverse)
-library(patchwork)
-source(here("R/various_useful_functions.r"))
-zero <- 0 ## don't change
-unity <- 1 ## don't change!!!
-options(mc.cores = 7)
-eval_ss_flag <- FALSE
-plot_ss_results <- TRUE
-
-num_CB_strains <- num_strains
-num_SB_strains <- num_strains
-num_PB_strains <- num_strains
-
-sp <- new_strain_parameter(
-  n_CB = num_CB_strains,
-  n_PB = num_SB_strains,
-  n_SB = num_PB_strains,
-  values_initial_state = "bush_ssfig3"
-)
-
-parameter <- new_runsim_parameter(
-  dynamic_model = bushplus_dynamic_model,
-  event_definition = event_definition_2,
-  event_interval = 100,
-  noise_sigma = 0,
-  minimum_abundances = rep(1, 3),
-  sim_duration = 2000,
-  sim_sample_interval = 100,
-  strain_parameter = sp,
-  log10a_series = c(
-    log10(sp$a_O),
-    log10(sp$a_O)
-  )
-)
-names(parameter$minimum_abundances) <- c("CB", "PB", "SB")
-rm(sp)
-
-
-
-
-## Define diversity
-## multiplier of SBPB variation
-CB_var_multiplier <- 2
-SBPB_var_multiplier <- 6
-
-CB_gmax_div <- 0.015789474 * CB_var_multiplier
-CB_h_div <- -0.08 * CB_var_multiplier
-SB_gmax_div <- 0.015789474 * SBPB_var_multiplier
-SB_h_div <- -0.323  * SBPB_var_multiplier
-PB_gmax_div <- 0.015789474  * SBPB_var_multiplier
-PB_h_div <- -0.323  * SBPB_var_multiplier
-
-num_div_treatment_levels <- 20
-
-## resolution for sub1
-#num_div_treatment_levels <- 50
-
-
-
-## Create diversity
-var_expt <- create_diversity_factorial2(
-  zero = zero, unity = unity,
-  num_div_treatment_levels = num_div_treatment_levels,
[…]

### 2022-10-23 experiments/1_figures_main_ms/figures_main_ms_v1.R

@@ -1,496 +1,0 @@
-## Figures for main manuscript
-## 
-## 
-## 
-## 
-## this file -- version 2 -- makes graphs with all combinations
-## the other file -- version 1 -- makes only graphs for CB, SB-PB, and CB-SB-PB
-
-
-## Prelims ----
-rm(list=ls())
-library(microxanox)
-library(tidyverse)
-library(patchwork)
-library(here)
-library(ggpubr)
-
-colfunc_CB <- colorRampPalette(c("#024F17", "#B5FFC9"))
-colfunc_SB <- colorRampPalette(c("#7D1402", "#FCBEB3"))
-colfunc_PB <- colorRampPalette(c("#6E0172", "#F9AEFC"))
-
-source(here("R/various_useful_functions.r"))
-source(here("R/ms_figure_functions.R"))
-
-## Figure 1 ----
-## Powerpoint
-## Conceptual figure
-
-## Figure 2 ----
-## Keynote
-## Model system
-
-## Figure 3 ----
-## Effects of diversity on position of tipping points and effect sizes
-## Two column
-
-
-all_stab <- readRDS(here("data/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS"))
-
-## ele_rev1.3
-all_stab <- readRDS(here("data/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method_ELErevision1.3.RDS"))
-
-
-wait_time <- 1e6
-num_strains <- 9
-plot_here <- all_stab %>%
-  filter(waittime == wait_time)
-p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
-                                     which_strain = num_strains,
-                                     figure_title = NULL
-                                     # figure_title = paste0(wait_time,
-                                     #                       " wait time,\n",
-                                     #                       num_strains,
-                                     #                       " strains")
-                                     )
-p2 <- fig_resilience_vs_div(plot_here,
-                            which_strain = num_strains,
[…]

### 2022-10-23 experiments/replication_method/data_processing.R

@@ -1,0 +1,135 @@
+
+
+library(here)
+library(tidyverse)
+
+
+
+## Process the stability data to a smaller file ----
+
+read_plus <- function(flnm) {
+  print(flnm)
+  readRDS(flnm) %>% 
+    mutate(filename = flnm)
+}
+
+file_list <- list.files(path = here("data",
+                                    microxanox_path,
+                                    "replication_method",
+                                    event_definition),
+                        pattern = "stab_data", 
+                        full.names = TRUE,
+                        recursive = FALSE)
+
+#file_list <- file_list[1:3]
+
+tbl1 <-  file_list %>%
+  map_df(~read_plus(.))
+
+keep_tbl1 <- tbl1
+
+#keep_tbl1$filename[1]
+
+all_stab <- tbl1 %>%
+  select(-data, -pars, -ss_by_a_N_result, -ss_res) %>%
+  separate(filename , sep = "_", into = c(paste0("junk", 1:9), "simlength", paste0("junk", 10:12))) %>%
+  select(-starts_with("junk")) %>%
+  mutate(simlength = parse_number(simlength))
+
+
+
+CB_vars <- unique(all_stab$CB_var_gmax_s)
+SB_vars <- unique(all_stab$SB_var_gmax_s)
+PB_vars <- unique(all_stab$PB_var_gmax_s)
+
+CB_all_stab <- all_stab %>%
+  filter(SB_var_gmax_s == 0,
+         PB_var_gmax_s == 0) %>%
+  ungroup() %>%
+  mutate(var_treat = "CB",
+         var_gmax = CB_var_gmax_s,
+         stand_var = var_gmax / max(var_gmax))
+SB_all_stab <- all_stab %>%
+  filter(CB_var_gmax_s == 0,
+         PB_var_gmax_s == 0)  %>%
+  ungroup() %>%
+  mutate(var_treat = "SB",
+         var_gmax = SB_var_gmax_s,
+         stand_var = var_gmax / max(var_gmax))
+PB_all_stab <- all_stab %>%
+  filter(CB_var_gmax_s == 0,
+         SB_var_gmax_s == 0) %>%
+  ungroup()  %>%
+  mutate(var_treat = "PB",
+         var_gmax = PB_var_gmax_s,
+         stand_var = var_gmax / max(var_gmax))
+
+for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
[…]

### 2022-10-23 experiments/replication_method/run_experiment.R

@@ -1,0 +1,65 @@
+## SS finding experiment by replication method
+## Be careful to not overwrite data files
+
+
+max_cores <- benchmarkme::get_cpu()$no_of_cores-2
+options(mc.cores = max_cores)
+
+## Run for 2, 3, 6, and 9 strains
+#for(num_strains in c(2, 3, 6, 9)) {
+
+  num_strains <- 9 ## for testing
+
+  ## Run the code that sets up the experiment
+  source(here("experiments/replication_method/setup_experiment.R"))
+
+  datadir <- here::here("data",
+                        microxanox_path,
+                        "replication_method",
+                        event_definition)
+  
+  ss_data_filename <- file.path(datadir,
+                                paste0("ss_data_",
+                                       num_strains, "strains_sim_length",
+                                       formatC(sim_length, format = "e", digits = 0),
+                                       "_", event_def,".RDS"))
+  stab_data_filename <- file.path(datadir,
+                                  paste0("stab_data_",
+                                         num_strains, "strains_sim_length",
+                                         formatC(sim_length, format = "e", digits = 0),
+                                         "_", event_def,".RDS"))
+
+  #var_expt <- var_expt[1,]
+
+  system.time(
+    run_replication_ssfind_experiment(parameter, var_expt) %>%
+      saveRDS(ss_data_filename)
+  )
+
+
+
+  ## Get stability measures ----
+  num_cores <- min(c(max_cores, nrow(var_expt)))
+  expt_res <- readRDS(ss_data_filename)
+  ## Get total biomass of CB, of SB, and of PB, to allow calculation of stability of these
+  expt_res <- expt_res %>%
+    mutate(ss_res = list(get_total_bio(ss_res)))
+  cluster1 <- multidplyr::new_cluster(num_cores)
+  multidplyr::cluster_library(cluster1, c("microxanox", "dplyr"))
+  system.time({
+    stab_data <-  expt_res %>%
+      multidplyr::partition(cluster1) %>%
+      mutate(stability_measures = list(get_stability_measures_replication_ssfind_result(ss_res))) %>%
+      collect() %>%
+      unnest(cols = c(stability_measures)) %>%
+      mutate(num_strains = num_strains)
+  })
+  saveRDS(stab_data, stab_data_filename)
+  ## End of getting stability measures
+
+
+#}
+
+
+
+#x <- parameter$ss_expt[i, ]

### 2022-10-23 experiments/replication_method/setup_experiment.R

@@ -1,0 +1,99 @@
+## see file R/how_to_install_microxanox for (surprise) how to install the microxanox package
+
+zero <- 0 ## don't change
+unity <- 1 ## don't change!!!
+
+
+num_CB_strains <- num_strains
+num_SB_strains <- num_strains
+num_PB_strains <- num_strains
+
+sp <- new_strain_parameter(
+  n_CB = num_CB_strains,
+  n_PB = num_SB_strains,
+  n_SB = num_PB_strains,
+  values_initial_state = "bush_ssfig3"
+)
+
+parameter <- new_runsim_parameter(
+  dynamic_model = bushplus_dynamic_model,
+  event_definition = event_definition_2,
+  event_interval = 100,
+  noise_sigma = 0,
+  minimum_abundances = rep(1, 3),
+  sim_duration = 2000,
+  sim_sample_interval = 100,
+  strain_parameter = sp,
+  log10a_series = c(
+    log10(sp$a_O),
+    log10(sp$a_O)
+  )
+)
+names(parameter$minimum_abundances) <- c("CB", "PB", "SB")
+rm(sp)
+
+
+
+
+## Define diversity
+## multiplier of SBPB variation
+CB_var_multiplier <- 2
+SBPB_var_multiplier <- 6
+
+CB_gmax_div <- 0.015789474 * CB_var_multiplier
+CB_h_div <- -0.08 * CB_var_multiplier
+SB_gmax_div <- 0.015789474 * SBPB_var_multiplier
+SB_h_div <- -0.323  * SBPB_var_multiplier
+PB_gmax_div <- 0.015789474  * SBPB_var_multiplier
+PB_h_div <- -0.323  * SBPB_var_multiplier
+
+num_div_treatment_levels <- 20
+
+## resolution for sub1
+#num_div_treatment_levels <- 50
+
+## Create diversity
+var_expt <- create_diversity_factorial2(
+  zero = zero, unity = unity,
+  num_div_treatment_levels = num_div_treatment_levels,
+  CB_gmax_div = CB_gmax_div, CB_h_div = CB_h_div,
+  SB_gmax_div = SB_gmax_div, SB_h_div = SB_h_div,
+  PB_gmax_div = PB_gmax_div, PB_h_div = PB_h_div,
+  default_9strain = new_strain_parameter(
+    n_CB = num_CB_strains,
+    n_SB = num_SB_strains,
+    n_PB = num_PB_strains,
[…]

### 2022-10-23 experiments/run_all.R

@@ -1,0 +1,80 @@
+# Preliminaries -----
+
+rm(list = ls())
+
+## Load some libraries and source files of functions ----
+library(here)
+library(microxanox)
+library(tidyverse)
+source(here("R/various_useful_functions.r"))
+
+## Set and check microxanox version ----
+microxanox_version_required <- "0.9.1"
+source(here("R/check_microxanox_version.R"))
+
+# **************************************************************
+# Only continue if previous check of required microxanox passes.
+# **************************************************************
+
+# Note that the version specific path component has been set to:
+microxanox_path
+
+## Make data folder structure, if required ----
+source(here("R/make_data_folders.R"))
+result
+
+
+# Run temporal method stable state finding ----
+
+## event_definition_2 ----
+event_definition <- "event_definition_2"
+
+### different wait times ----
+wait_time <- 1e6
+#source(here("experiments/temporal_method/run_experiment.r"))
+
+wait_time <- 1e5
+#source(here("experiments/temporal_method/run_experiment.r"))
+
+wait_time <- 1e4
+#source(here("experiments/temporal_method/run_experiment.r"))
+
+wait_time <- 1e3
+#source(here("experiments/temporal_method/run_experiment.r"))
+
+wait_time <- 1e2
+#source(here("experiments/temporal_method/run_experiment.r"))
+
+### Only most tolerant strain ----
+wait_time <- 1e6
+#source(here("experiments/temporal_method/run_experiment_onestrain.r"))
+
+### Process and save data ----
+#source(here("experiments/temporal_method/data_processing.r"))
+
+### Make a couple of individual simulations, one with longer duration ----
+#source(here("experiments/temporal_method/run_single_sims.r"))
+
+## event_definition_1 ----
+event_def <- "event_definition_1"
+
+### Only one wait time ----
+wait_time <- 1e6
+#source(here("experiments/temporal_method/run_experiment.r"))
+
+## Process and save data ----
+#source(here("experiments/temporal_method/data_processing.r"))
+
+
+
+# Run replication method stable state finding ----
+
+event_def <- "event_definition_2"
+sim_length <- 1e6
+#source(here("experiments/replication_method/run_experiment.r"))
+#source(here("experiments/replication_method/data_processing.r"))
+
+
+
+# Run animations code ----
+# Look in the reports/animations folder and run the code there

### 2022-10-23 experiments/temporal_method/data_processing.R

@@ -1,0 +1,125 @@
+
+## Process the stability data to a smaller file
+
+read_plus <- function(flnm) {
+  print(flnm)
+  readRDS(flnm) %>% 
+    mutate(filename = flnm)
+}
+
+file_list <- list.files(path = here("data",
+                               microxanox_path,
+                               "temporal_method",
+                               event_def),
+                   pattern = "stab_data", 
+                   full.names = TRUE,
+                   recursive = FALSE)
+
+#file_list <- file_list[1:3]
+
+tbl1 <-  file_list %>%
+  map_df(~read_plus(.))
+
+keep_tbl1 <- tbl1
+
+all_stab <- tbl1 %>%
+  select(-data, -pars, -parameter, -total_initial_abundances, -ssfind_pars, -ssfind_result) %>%
+  separate(filename , sep = "_", into = c(paste0("junk", 1:8), "waittime", paste0("junk", 9:11))) %>%
+  select(-starts_with("junk")) %>%
+  mutate(waittime = parse_number(waittime))
+
+
+
+CB_vars <- unique(all_stab$CB_var_gmax_s)
+SB_vars <- unique(all_stab$SB_var_gmax_s)
+PB_vars <- unique(all_stab$PB_var_gmax_s)
+
+CB_all_stab <- all_stab %>%
+  filter(SB_var_gmax_s == 0,
+         PB_var_gmax_s == 0) %>%
+  ungroup() %>%
+  mutate(var_treat = "CB",
+         var_gmax = CB_var_gmax_s,
+         stand_var = var_gmax / max(var_gmax))
+SB_all_stab <- all_stab %>%
+  filter(CB_var_gmax_s == 0,
+         PB_var_gmax_s == 0)  %>%
+  ungroup() %>%
+  mutate(var_treat = "SB",
+         var_gmax = SB_var_gmax_s,
+         stand_var = var_gmax / max(var_gmax))
+PB_all_stab <- all_stab %>%
+  filter(CB_var_gmax_s == 0,
+         SB_var_gmax_s == 0) %>%
+  ungroup()  %>%
+  mutate(var_treat = "PB",
+         var_gmax = PB_var_gmax_s,
+         stand_var = var_gmax / max(var_gmax))
+
+for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
+                   SB_var_gmax_s = sort(SB_vars))
+CBSB_all_stab <- all_stab %>%
[…]

### 2022-10-23 experiments/temporal_method/old/recalculate_stability_measures.R

@@ -1,0 +1,67 @@
+## Code for recalculating stability measures
+## See file R/how_to_install_microxanox for (surprise) how to install the microxanox package
+
+rm(list = ls())
+library(here)
+microxanox_release <- "0.4.9"
+library(microxanox)
+source(here::here("experiments/0_ss_finding/temporal_method/check_microxanox_version.R"))
+library(tidyverse)
+source(here("R/various_useful_functions.r"))
+max_cores <- benchmarkme::get_cpu()$no_of_cores
+
+wait_time <- 1e6
+event_def <- "event_definition_2"
+datadir <- here::here("data/0_ss_finding/temporal_method/")
+
+## Run for 2, 3, 6, and 9 strains
+for(num_strains in c(2, 3, 6, 9)) {
+
+  num_strains <- 9 ## for testing
+  
+  
+  ss_data_filename <- file.path(datadir,
+                                paste0("ss_data_",
+                                       num_strains, "strains_waittime",
+                                       formatC(wait_time, format = "e", digits = 0),
+                                       "_", event_def,".RDS"))
+  stab_data_filename <- file.path(datadir,
+                                  paste0("stab_data_",
+                                         num_strains, "strains_waittime",
+                                         formatC(wait_time, format = "e", digits = 0),
+                                         "_", event_def,".RDS"))
+  
+  
+  ## Get stability measures ----
+  expt_res <- readRDS(ss_data_filename)
+  num_cores <- min(c(max_cores, nrow(expt_res)))
+    ## Get total biomass of CB, of SB, and of PB, to allow calculation of stability of these
+  expt_res <- expt_res %>%
+    mutate(ssfind_result = list(get_total_bio(ssfind_result)))
+  cluster1 <- multidplyr::new_cluster(num_cores)
+  multidplyr::cluster_library(cluster1, c("microxanox", "dplyr"))
+  system.time({
+    stab_data <-  expt_res %>%
+      multidplyr::partition(cluster1) %>%
+      mutate(stability_measures = list(get_stability_measures(ssfind_result))) %>%
+      collect() %>%
+      unnest(cols = c(stability_measures)) 
+  })
+  saveRDS(stab_data, stab_data_filename)
+  ## End of getting stability measures
+
+  
+}
+## End of number of strains loop
+
+
+
+
+
+
+
+
+
+
+
+

### 2022-10-23 experiments/temporal_method/run_experiment_onestrain.R

@@ -1,0 +1,103 @@
+## SS finding experiment by temporal method
+## Be careful to not overwrite data files
+
+max_cores <- benchmarkme::get_cpu()$no_of_cores-2
+
+## setup experiment with two strains
+num_strains <- 2
+source(here::here("experiments/0_ss_finding/temporal_method/setup_experiment.R"))
+
+## keep only the most tolerant strain
+#var_expt <- var_expt[1:2,]
+for(i in 1:nrow(var_expt)) {
+  temp_pars <- var_expt$pars[i][[1]]
+  temp_pars$CB <- temp_pars$CB[which(temp_pars$CB$h_SR_CB==max(temp_pars$CB$h_SR_CB))[1],]
+  temp_pars$PB <- temp_pars$PB[which(temp_pars$PB$h_O_PB==max(temp_pars$PB$h_O_PB))[1],]
+  temp_pars$SB <- temp_pars$SB[which(temp_pars$SB$h_O_SB==max(temp_pars$SB$h_O_SB))[1],]
+  initial_subtrates <- temp_pars$initial_state[!str_detect(names(temp_pars$initial_state), "B_")]
+  temp_pars$initial_state <- c(NA, NA, NA, initial_subtrates)
+  names(temp_pars$initial_state) <- c("CB_1", "PB_1", "SB_1", names(initial_subtrates))
+  var_expt$pars[i][[1]] <- temp_pars
+}
+num_strains <- -1 ## use this to label that only the most tolerant strain is kept
+
+
+datadir <- here::here("data",
+                      microxanox_path,
+                      "temporal_method")
+#dir.create(datadir, recursive = TRUE, showWarnings = FALSE)
+
+ss_data_filename <- file.path(datadir,
+                              paste0("ss_data_",
+                                     num_strains, "strains_waittime",
+                                     formatC(wait_time, format = "e", digits = 0),
+                                     "_", event_def,".RDS"))
+stab_data_filename <- file.path(datadir,
+                                paste0("stab_data_",
+                                       num_strains, "strains_waittime",
+                                       formatC(wait_time, format = "e", digits = 0),
+                                       "_", event_def,".RDS"))
+
+
+## Estimate time require ----
+nrow(var_expt)
+wait_time
+length(parameter$log10a_series)
+num_cores <- min(c(max_cores, nrow(var_expt)))
+## constants in following formula come from the excel sheet
[…]

### 2022-10-23 experiments/temporal_method/run_single_sims.R

@@ -1,0 +1,61 @@
+## Note that the microxanox function "get_ssbyaN_parameter" may be useful here, though the code below
+## would need to be changed in order to use it.
+## See file R/how_to_install_microxanox for (surprise) how to install the microxanox package
+
+
+
+rm(list = ls())
+
+
+microxanox_version_here <- "0.9.1"
+microxanox_version_path <- paste0("microxanox_v", microxanox_version_here)
+
+
+library(microxanox)
+source(here::here("experiments/0_ss_finding/temporal_method/check_microxanox_version.R"))
+library(tidyverse)
+library(patchwork)
+library(here)
+source(here("R/various_useful_functions.r"))
+zero <- 0 ## don't change
+unity <- 1 ## don't change!!!
+
+## Re-run sim selected in figure 3 for longer
+ss_9s <- readRDS(here::here("data/0_ss_finding/temporal_method",
+                            microxanox_version_path,
+                            "stab_data_9strains_waittime1e+06_event_definition_2.RDS"))
+sort(unique(ss_9s$CB_var_gmax_s))
+sort(unique(ss_9s$SB_var_gmax_s))
+ss_result <- ss_9s %>%
+  filter(abs(CB_var_gmax_s - 0.028254848) < 0.0001,
+         abs(SB_var_gmax_s - 0.084764545) < 0.0001,
+         abs(PB_var_gmax_s - 0.084764545) < 0.0001)
+parameter <- ss_result$parameter[[1]]
+parameter$strain_parameter <- ss_result$pars[[1]]
+
+total_initial_abundances <- 10^5
+parameter <- set_temporal_ssfind_initial_state(parameter,
+                                               total_initial_abundances,
+                                               total_initial_abundances,
+                                               total_initial_abundances)
+
+wait_time <-  1e6
+parameter$sim_duration <- wait_time * length(parameter$log10a_series)
+parameter$sim_sample_interval <- wait_time
+parameter$sim_duration
+system.time(
+  result_1e6 <- run_temporal_ssfind(parameter)
+)
+saveRDS(result_1e6, here::here("data/0_ss_finding/temporal_method",
+                               microxanox_version_path,
+                               "single_sims",
+                               "single_1e6_result.RDS"))
+
+
+wait_time <-  2e6
+parameter$sim_duration <- wait_time * length(parameter$log10a_series)
+parameter$sim_sample_interval <- wait_time
+parameter$sim_duration
[…]

### 2022-10-23 experiments/temporal_method/setup_experiment.R

@@ -1,0 +1,130 @@
+## see file R/how_to_install_microxanox for (surprise) how to install the microxanox package
+
+zero <- 0 ## don't change
+unity <- 1 ## don't change!!!
+options(mc.cores = 7)
+eval_ss_flag <- FALSE
+plot_ss_results <- TRUE
+
+num_CB_strains <- num_strains
+num_SB_strains <- num_strains
+num_PB_strains <- num_strains
+
+sp <- new_strain_parameter(
+  n_CB = num_CB_strains,
+  n_PB = num_SB_strains,
+  n_SB = num_PB_strains,
+  values_initial_state = "bush_ssfig3"
+)
+
+parameter <- new_runsim_parameter(
+  dynamic_model = bushplus_dynamic_model,
+  event_definition = event_definition_2,
+  event_interval = 100,
+  noise_sigma = 0,
+  minimum_abundances = rep(1, 3),
+  sim_duration = 2000,
+  sim_sample_interval = 100,
+  strain_parameter = sp,
+  log10a_series = c(
+    log10(sp$a_O),
+    log10(sp$a_O)
+  )
+)
+names(parameter$minimum_abundances) <- c("CB", "PB", "SB")
+rm(sp)
+
+
+
+
+## Define diversity
+## multiplier of SBPB variation
+CB_var_multiplier <- 2
+SBPB_var_multiplier <- 6
+
+CB_gmax_div <- 0.015789474 * CB_var_multiplier
+CB_h_div <- -0.08 * CB_var_multiplier
+SB_gmax_div <- 0.015789474 * SBPB_var_multiplier
+SB_h_div <- -0.323  * SBPB_var_multiplier
+PB_gmax_div <- 0.015789474  * SBPB_var_multiplier
+PB_h_div <- -0.323  * SBPB_var_multiplier
+
+num_div_treatment_levels <- 20
+
+## resolution for sub1
+#num_div_treatment_levels <- 50
+
+
+
+## Create diversity
+var_expt <- create_diversity_factorial2(
+  zero = zero, unity = unity,
+  num_div_treatment_levels = num_div_treatment_levels,
+  CB_gmax_div = CB_gmax_div, CB_h_div = CB_h_div,
+  SB_gmax_div = SB_gmax_div, SB_h_div = SB_h_div,
+  PB_gmax_div = PB_gmax_div, PB_h_div = PB_h_div,
+  default_9strain = new_strain_parameter(
+    n_CB = num_CB_strains,
[…]

### 2022-10-23 reports/animations/animate1.R

@@ -1,0 +1,102 @@
+## Prelims ----
+rm(list = ls())
+library(tidyverse)
+library(microxanox)
+library(patchwork)
+library(gganimate)
+library(here)
+library(scales)
+source(here("r", "various_useful_functions.r"))
+source(here("r", "ms_figure_functions.r"))
+source(here("experiments/3_animate/animation_functions.R"))
+colfunc_CB <- colorRampPalette(c("#024F17", "#B5FFC9"))
+colfunc_SB <- colorRampPalette(c("#7D1402", "#FCBEB3"))
+colfunc_PB <- colorRampPalette(c("#6E0172", "#F9AEFC"))
+zero <- 0
+unity <- 1
+
+## load data ----
+ss_9s <- readRDS(here("data", "0_ss_finding", "temporal_method", "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
+
+## set animation render parameters
+nframes <- 500#100
+fps <- 30
+height <- 2
+width <- 5
+units <- "in"
+res <- 600
+
+## no diversity ----
+ss_result <- ss_9s %>%
+  filter(abs(CB_var_gmax_s - 0.0) < 0.0001,
+         abs(SB_var_gmax_s - 0.0) < 0.0001,
+         abs(PB_var_gmax_s - 0.0) < 0.0001)
+this_div <- "no_div"
+
+this_func_group <- "CB"
+p1_ann <- plot_ann(ss_result, func_group = this_func_group)
+anim_save_wrap(p1_ann, this_func_group, this_div)
+
+this_func_group <- "SB"
+p1_ann <- plot_ann(ss_result, func_group = this_func_group)
+anim_save_wrap(p1_ann, this_func_group, this_div)
+
+this_func_group <- "PB"
+p1_ann <- plot_ann(ss_result, func_group = this_func_group)
+anim_save_wrap(p1_ann, this_func_group, this_div)
+
+this_func_group <- NA
+this_substrate <- "O"
+p1_ann <- plot_ann(ss_result, func_group = this_func_group, this_substrate = this_substrate)
+anim_save_wrap(p1_ann, this_func_group, this_div, this_substrate)
+
+this_substrate <- "SO"
+p1_ann <- plot_ann(ss_result, func_group = this_func_group, this_substrate = this_substrate)
+anim_save_wrap(p1_ann, this_func_group, this_div, this_substrate)
+
+this_substrate <- "SR"
[…]

### 2022-10-23 reports/manuscript/figures_main_ms_v1.R

@@ -1,0 +1,506 @@
+## Figures for main manuscript
+## 
+## 
+## 
+## 
+## this file -- version 2 -- makes graphs with all combinations
+## the other file -- version 1 -- makes only graphs for CB, SB-PB, and CB-SB-PB
+
+
+## Prelims ----
+rm(list=ls())
+library(microxanox)
+library(tidyverse)
+library(patchwork)
+library(here)
+library(ggpubr)
+
+## Set and check microxanox version ----
+microxanox_version_required <- "0.9.1"
+source(here("R/check_microxanox_version.R"))
+# Note that the version specific path component has been set to:
+microxanox_path
+
+colfunc_CB <- colorRampPalette(c("#024F17", "#B5FFC9"))
+colfunc_SB <- colorRampPalette(c("#7D1402", "#FCBEB3"))
+colfunc_PB <- colorRampPalette(c("#6E0172", "#F9AEFC"))
+
+source(here("R/various_useful_functions.r"))
+source(here("R/ms_figure_functions.R"))
+
+## Figure 1 ----
+## Powerpoint
+## Conceptual figure
+
+## Figure 2 ----
+## Keynote
+## Model system
+
+## Figure 3 ----
+## Effects of diversity on position of tipping points and effect sizes
+## Two column
+all_stab <- readRDS(here("data",
+                         microxanox_path,
+                         "temporal_method",
+                         "event_definition_2",
+                         "processed_data",
+                         "all_stab_data.RDS"))
+
+wait_time <- 1e6
+num_strains <- 9
+plot_here <- all_stab %>%
+  filter(waittime == wait_time)
+p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
+                                     which_strain = num_strains,
+                                     figure_title = NULL
+                                     # figure_title = paste0(wait_time,
+                                     #                       " wait time,\n",
+                                     #                       num_strains,
[…]

### 2022-10-23 reports/old/experiment old/experiment summary/summarise.R

@@ -1,0 +1,85 @@
+rm(list = ls())
+
+library(here)
+library(tidyverse)
+library(microxanox)
+
+CBSBPB_data <- readRDS(here("experiments/experiment 1/data/ss_data.RDS"))
+CB_data <- readRDS(here("experiments/experiment 2/data/ss_data.RDS"))
+SBPB_data <- readRDS(here("experiments/experiment 3/data/ss_data.RDS"))
+
+
+
+CBSBPB_stab_data <- CBSBPB_data %>%
+  group_by(CB_var_gmax_s, CB_var_h_s,
+           SB_var_gmax_s, SB_var_h_s,
+           PB_var_gmax_s, PB_var_h_s) %>%
+  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
+results1 <- unnest(CBSBPB_stab_data, cols = c(stability_measures)) %>%
+  mutate(var_treat = "CB-SB-PB",
+         var_gmax = CB_var_gmax_s)
+
+CB_stab_data <- CB_data %>%
+  group_by(CB_var_gmax_s, CB_var_h_s,
+           SB_var_gmax_s, SB_var_h_s,
+           PB_var_gmax_s, PB_var_h_s) %>%
+  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
+results2 <- unnest(CB_stab_data, cols = c(stability_measures))  %>%
+  mutate(var_treat = "CB",
+         var_gmax = CB_var_gmax_s)
+
+
+SBPB_stab_data <- SBPB_data %>%
+  group_by(CB_var_gmax_s, CB_var_h_s,
+           SB_var_gmax_s, SB_var_h_s,
+           PB_var_gmax_s, PB_var_h_s) %>%
+  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
+results5 <- unnest(SBPB_stab_data, cols = c(stability_measures))  %>%
+  mutate(var_treat = "SB-PB",
+         var_gmax = SB_var_gmax_s)
+
+
+all_stab_results <- results1 %>%
+  bind_rows(results2) %>%
+#  bind_rows(results3) %>%
+ # bind_rows(results4) %>%
+  bind_rows(results5)
+
+all_stab_results<- all_stab_results %>%
+    mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB-PB", "CB-SB-PB")))
[…]

### 2022-11-12 reports/supplement/old_supplement_0.9.1.Rmd
updated supplement

--- 2022-10-23 reports/supplement/supplement_0.9.1.Rmd
@@
 
-# Are the results driven by functional diversity?
-
-During the review process we received the following comment: *I think the authors have not shown sufficiently clearly that their results are actually driven by functional diversity.
-Fig.
-4 shows that on the collapse trajectory, the dominating functional group is itself dominated by the most tolerant strain.
-This is also true for the suppressed group on its recovery trajectory shortly before the tipping point.
-This made me wonder whether the same (or at least a very similar) results regarding the change in resilience of the system states could also be obtained with just a single strain per functional group, whose tolerance to the inhibiting substance is systematically increased.
-This could be tested fairly easily by re-running the simulations behind Fig.
-3 with just the most tolerant (and slowest growing) strain of each functional group present.* In this section we discuss this matter.
-
-Our first realisation was that we had not adequately stated what component of functional diversity we manipulated.
-We revised to state *Functional diversity has multiple components, and we manipulate only one of these, namely the range of trait space represented, which has been termed functional richness, and measured as the convex hull volume ([Villéger et al.
-2008](https://esajournals.onlinelibrary.wiley.com/doi/abs/10.1890/07-1206.1)).*
-
-Since we manipulated the range of trait space represented (sensu [Villéger et al 2008](https://esajournals.onlinelibrary.wiley.com/doi/abs/10.1890/07-1206.1)), and manipulated nothing else, we manipulated only functional diversity.
-Logically then, any effects of this manipulation must be due to the functional diversity manipulation.
-That is, regardless of the process / mechanism by which functional diversity causes an effect, it is appropriate to state that functional diversity drives the results.
-
-The reviewer’s comment motivated us to consider two questions:
-
-1. By what mechanism does functional diversity affect ecosystem stability in this study? 
-2. Could the observed effects of functional diversity also be created by manipulations of trait values that do not alter functional diversity?
-
-Question 1.
-In research concerning biodiversity and ecosystem functioning there was considerable debate about the phenomenon that high yielding species are more likely to be present in more diverse communities.
-This phenomenon was sometimes responsible for a large proportion of observed effects of biodiversity on ecosystem function.
-The debate was to a large extent resolved by recognising that biodiversity effects can result from two sources: a selection/sampling effect, and a complementarity effect.
-Both are now considered valid and important mechanisms by which diversity (including functional diversity) affects ecosystem functioning.
-We view the presence of more extreme trait values in more functionally diverse communities as an analogue of the sampling/selection effect of biodiversity, and a valid mechanism by which increased functional diversity can affect ecosystem stability.
-For example, let us assume for the moment that, indeed, only the single maximum tolerance strain present in each functional group of an ecosystem determines the resilience of that ecosystem.
-Then we would say that variation in resilience with diversity operates only by the "sampling effect".
-If we also assume that higher tolerance causes higher ecosystem resilience, then a more functionally diverse ecosystem will have higher maximum tolerance trait, and so higher resilience.
-And an ecosystem with more strains per functional group will have higher resilience (Figure \@ref(fig:samp-effect1)).
-
-Hence, even if all of the observed effects of our functional diversity manipulation were only due to presence of one strain (e.g.
-the most tolerant one), this can be considered an effect of functional diversity.
+# Underlying mechanisms
+
+In the main text we show that trait variation can affect resilience.
+In this supplementary section, we discuss the mechanism(s) underlying the observed diversity effects.
+We first explain the two major classes of mechanisms known to drive diversity effects, and then use additional simulations to elucidate the mechanisms operating in our study.
+
+## Complementarity versus sampling effect
+
+Research about the relationship between biodiversity and ecosystem functioning has identified two major mechanisms by which diversity affects ecosystem functioning: the selection/sampling effect and the complementarity effect (Loreau & Hector 2001).
+The sampling effect occurs when more diverse communities have higher functioning because they have a higher probability of containing the best-performing species, i.e.
+the diversity effect is driven by only one (or few) species (Cardinale et al.
+2011).
+In contrast, the complementarity effect occurs when higher ecosystem functioning in more diverse communities is due to niche differences or positive interactions among species, i.e.
+the diversity effect is driven by many species (Cardinale et al.
+2011).
+Both effects are considered valid and important mechanisms by which diversity affects ecosystem functioning (Cardinale et al.
+2006, 2011, 2012; Fargione et al.
+2007).
+
+Similarly, the complementarity effect and the sampling effect are important mechanisms by which diversity affects stability (Loreau & Mazancourt 2013; Loreau et al.
+2021) and resilience (Steiner et al.
+2006; Hughes & Stachowicz 2011).
+For example, diversity can stabilize aggregate ecosystem properties (e.g.
+community biomass) when species differ in their responses to environmental factors and therefore respond asynchronously to environmental fluctuations (temporal complementarity effect; Loreau & Mazancourt 2013).
+However, when considering ecosystem responses to directional environmental change or pulse disturbances rather than to environmental fluctuations, the sampling effect might be of particular importance (Steiner et al.
+2006): more diverse systems might absorb a greater amount of change by having a higher chance of containing species with high environmental tolerance.
+In this scenario, the positive diversity effect on resilience is driven by one (or few) species.
+From a conservation perspective, however, one would nevertheless strive to maintain diversity and not only the most tolerant species because of the uncertainties associated with environmental change: we do not know with sufficient certainty which stressors will change in a given ecosystem and which traits will therefore be relevant in the future.
 
@@
 
-**Question 2.
-It is possible that all of the observed effects of functional diversity operate via this sampling effect, and thus could also be created when there is only one maximum tolerance strain in each functional group?.**
-
-To test if the diversity effects on resilience were driven entirely by the most tolerant strains, we made additional simulations where functional groups contained only the strain with greatest tolerance and lowest maximum growth rate.
-That is, for each of the 20 levels of trait variation, we ran simulations where each functional group had only one strain, and its trait values corresponded with those of the most tolerant strain for the given level of trait variation.
+## Do the observed diversity effects operate via the sampling effect?
+
+We investigated if the diversity effects observed in our study were in line with the sampling effect, that is, driven entirely by the presence of the most tolerant strain.
+Specifically, we ran additional simulations where functional groups contained only the strain with greatest tolerance and lowest maximum growth rate.
+That is, for each of the 20 levels of trait variation, we made simulations where each functional group had only one strain, and its trait values corresponded with those of the most tolerant strain for the given level of trait variation.
 We also manipulated in which of the functional groups tolerance increased.
@@
 We then compared the tipping point positions resulting from this tolerance manipulation with the tipping point positions resulting from the diversity manipulation presented in the main text.
+If the observed diversity effects are caused by the sampling effect, we expect there to be no difference between the tolerance manipulation and the diversity manipulation.
 
@@
 in the combinations SB only, CB-SB, and CB-SB-PB).
-We show below that
+We show below that...(TO DO: Summarize results).
 

### 2022-11-12 R/make_data_folders.R

@@ -29,6 +29,12 @@ if(!dir.exists(here("data",
                           microxanox_path,
                           "temporal_method",
                           "single_sims"))
-  if(res1 & res2 & res3 & res4)
+  res5 <- dir.create(here("data",
+                          microxanox_path,
+                          "replication_method",
+                          "event_definition_2",
+                          "processed_data"),
+                     recursive = TRUE)
+  if(res1 & res2 & res3 & res4 & res5)
     result <- paste0("New folders created for results using ", microxanox_path)
 }

### 2022-11-12 experiments/temporal_method/old/get_div_effects.R

@@ -16,7 +16,7 @@ colfunc_CB <- colorRampPalette(c("#024F17", "#B5FFC9"))
 colfunc_SB <- colorRampPalette(c("#7D1402", "#FCBEB3"))
 colfunc_PB <- colorRampPalette(c("#6E0172", "#F9AEFC"))
 
-source(here("R/various_useful_functions.r"))
+source(here("R/various_useful_functions.R"))
 
 
 

### 2022-11-12 experiments/temporal_method/old/recalculate_stability_measures.R

@@ -7,7 +7,7 @@ microxanox_release <- "0.4.9"
 library(microxanox)
 source(here::here("experiments/0_ss_finding/temporal_method/check_microxanox_version.R"))
 library(tidyverse)
-source(here("R/various_useful_functions.r"))
+source(here("R/various_useful_functions.R"))
 max_cores <- benchmarkme::get_cpu()$no_of_cores
 
 wait_time <- 1e6

### 2022-11-12 experiments/temporal_method/run_single_sims.R

@@ -16,7 +16,7 @@ source(here::here("experiments/0_ss_finding/temporal_method/check_microxanox_ver
 library(tidyverse)
 library(patchwork)
 library(here)
-source(here("R/various_useful_functions.r"))
+source(here("R/various_useful_functions.R"))
 zero <- 0 ## don't change
 unity <- 1 ## don't change!!!
 

### 2022-11-12 reports/animations/animate1.R

@@ -6,8 +6,7 @@ library(patchwork)
 library(gganimate)
 library(here)
 library(scales)
-source(here("r", "various_useful_functions.r"))
-source(here("r", "ms_figure_functions.r"))
+source(here("r", "various_useful_functions.R"))
 source(here("experiments/3_animate/animation_functions.R"))
 colfunc_CB <- colorRampPalette(c("#024F17", "#B5FFC9"))
 colfunc_SB <- colorRampPalette(c("#7D1402", "#FCBEB3"))

### 2022-11-12 reports/manuscript/figures_main_ms_v1.R

@@ -25,7 +25,7 @@ colfunc_CB <- colorRampPalette(c("#024F17", "#B5FFC9"))
 colfunc_SB <- colorRampPalette(c("#7D1402", "#FCBEB3"))
 colfunc_PB <- colorRampPalette(c("#6E0172", "#F9AEFC"))
 
-source(here("R/various_useful_functions.r"))
+source(here("R/various_useful_functions.R"))
 source(here("R/ms_figure_functions.R"))
 
 ## Figure 1 ----

### 2022-11-15 index.Rmd
update index
mostly animation code updated

@@
 
-[The Supplementary Report (HTML page)](./experiments/2_supplement/supplement.html)
+[The respository on Zenodo with DOI 10.5281/zenodo.6334544.](https://doi.org/10.5281/zenodo.6334544)
 
-[HTML page about how to reproduce the research.](./docs/How_to_reproduce.html)
+[The Supplementary Report (HTML page)](./reports/supplement/supplement_0.9.1.html)
 
-[Some animations of results (HTML page)](./experiments/3_animate/report.html)
+[Instructions of how to reproduce the research (HTML page).](./docs/How_to_reproduce.html)
+
+[Some animations of results (HTML page)](./reports/animations/report.html)

### 2022-11-15 reports/animations/report.Rmd
mostly animation code updated

@@
 ```{r}
-include_graphics(here("experiments/3_animate/mp4s/CB_no_div.mp4"))
+include_graphics(here("reports/animations/mp4s/CB_no_div.mp4"))
 ```
@@
 ```{r}
-include_graphics(here("experiments/3_animate/mp4s/CB_medium_div.mp4"))
+include_graphics(here("reports/animations/mp4s/CB_medium_div.mp4"))
 ```
@@
 ```{r}
-include_graphics(here("experiments/3_animate/mp4s/SB_no_div.mp4"))
+include_graphics(here("reports/animations/mp4s/SB_no_div.mp4"))
 ```
@@
 ```{r}
-include_graphics(here("experiments/3_animate/mp4s/SB_medium_div.mp4"))
+include_graphics(here("reports/animations/mp4s/SB_medium_div.mp4"))
 ```
@@
 ```{r}
-include_graphics(here("experiments/3_animate/mp4s/PB_no_div.mp4"))
+include_graphics(here("reports/animations/mp4s/PB_no_div.mp4"))
 ```
@@
 ```{r}
-include_graphics(here("experiments/3_animate/mp4s/PB_medium_div.mp4"))
+include_graphics(here("reports/animations/mp4s/PB_medium_div.mp4"))
 ```
@@
 ```{r}
-include_graphics(here("experiments/3_animate/mp4s/O_no_div.mp4"))
+include_graphics(here("reports/animations/mp4s/O_no_div.mp4"))
 ```
@@
 ```{r}
-include_graphics(here("experiments/3_animate/mp4s/O_medium_div.mp4"))
+include_graphics(here("reports/animations/mp4s/O_medium_div.mp4"))
 ```
@@
 ```{r}
-include_graphics(here("experiments/3_animate/mp4s/SR_no_div.mp4"))
+include_graphics(here("reports/animations/mp4s/SR_no_div.mp4"))
 ```
@@
 ```{r}
-include_graphics(here("experiments/3_animate/mp4s/SR_medium_div.mp4"))
+include_graphics(here("reports/animations/mp4s/SR_medium_div.mp4"))
 ```
@@
 ```{r}
-include_graphics(here("experiments/3_animate/mp4s/SO_no_div.mp4"))
+include_graphics(here("reports/animations/mp4s/SO_no_div.mp4"))
 ```
@@
 ```{r}
-include_graphics(here("experiments/3_animate/mp4s/SO_medium_div.mp4"))
+include_graphics(here("reports/animations/mp4s/SO_medium_div.mp4"))
 ```
@@
 ```{r}
-include_graphics(here("experiments/3_animate/mp4s/P_no_div.mp4"))
+include_graphics(here("reports/animations/mp4s/P_no_div.mp4"))
 ```
@@
 ```{r}
-include_graphics(here("experiments/3_animate/mp4s/P_medium_div.mp4"))
+include_graphics(here("reports/animations/mp4s/P_medium_div.mp4"))
 ```

### 2022-11-15 reports/animations/animation_functions.R

@@ -2,7 +2,7 @@
 
 anim_save_wrap <- function(plot_anim, this_fg, this_div, this_substrate = NA) {
   if(is.na(this_substrate))
-  anim_save(here::here(paste0("experiments/3_animate/",
+  anim_save(here::here(paste0("reports/animations/gifs/",
                              this_fg ,"_", this_div, ".gif")),
             p1_ann,
             nframes = nframes,
@@ -10,7 +10,7 @@ anim_save_wrap <- function(plot_anim, this_fg, this_div, this_substrate = NA) {
             height = height, width = width, units = units,
             res = res)
   if(!is.na(this_substrate))
-    anim_save(here::here(paste0("experiments/3_animate/",
+    anim_save(here::here(paste0("reports/animations/gifs/",
                                 this_substrate ,"_", this_div, ".gif")),
               p1_ann,
               nframes = nframes,

### 2022-11-15 reports/supplement/supplement_0.9.1.Rmd
update supplement

@@
 library(here)
-source(here("r", "various_useful_functions.r"))
-# source(here("experiments", "1_figures_main_ms", "ms_figure_functions.r"))
+source(here("r", "various_useful_functions.R"))
+# source(here("experiments", "1_figures_main_ms", "ms_figure_functions.R"))
 source(here("R/ms_figure_functions.R"))
@@
 
-As is shown in the figures below, the temporal method results in a larger region of bistability than the replication method, but only during increasing oxygen diffusivities.
-The difference in results occurs because, as discussed below, the initial conditions differ between the two approaches.
+As is shown in the figures below, the temporal and replication methods result in very similar regions of bistability.
 
@@
 
-The replication method shows the same effects of functional diversity as those revealed by the temporal method (Figure \@ref(fig:div-repl-meth1)). Namely
-
--   Introducing functional diversity in only the cyanobacteria increases the resilience of the oxic state but has no effect on the resilience of the anoxic state. 
+The replication method shows qualitatively the same effects of functional diversity (Figure \@ref(fig:div-repl-meth1)) as those revealed by the temporal method. Namely
+
+-   Introducing functional diversity in only the cyanobacteria increases the resilience of the oxic state and slightly decreases the resilience of the anoxic state. 
 -   Introducing functional diversity in only the sulfate-reducing bacteria increases the resilience of the anoxic state and reduces the resilience of the oxic state.
@@
 Specifically, in the temporal method, the initial condition at a new level of oxygen diffusivity is the stable state at the previous level of oxygen diffusivity, while in the replication method the starting conditions are identical at each level of oxygen diffusivity.
-These differences in starting conditions apparently result in longer persistence of transients in the temporal method than the replication method.
+These differences in starting conditions apparently result in longer duration of transients in the temporal method than the replication method.
 
@@
 
-```{r div-temp-eventdef1, eval = FALSE, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-eventdef1)', fig.height=8, fig.width=8, fig.align="center"}
+```{r div-temp-eventdef1, eval = TRUE, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-eventdef1)', fig.height=8, fig.width=8, fig.align="center"}
 all_stab <- readRDS(here("data",
@@
 
-sim_length <- 1e6
+wait_time <- 1e6
 num_strains <- 9
@@
                                      which_strain = num_strains,
-                                     figure_title = paste0(sim_length,
-                                                           " simulation length,\n",
+                                     figure_title = paste0(wait_time,
+                                                           " wait time,\n",
                                                            num_strains,
@@
 In the temporal approach, the initial condition at a new level of oxygen diffusivity is the stable state at the previous level of oxygen diffusivity, while in the approach of [Bush et al 2017](https://www.nature.com/articles/s41467-017-00912-x) the initial conditions are fixed and arbitrary (though this approach is still useful for illustrating the bistability of the system).
-This difference in initial conditions increases the region of bistability in the temporal approach because as a tipping point approaches, the functional group that will dominate after the regime shift starts from much lower abundances than in the approach by [Bush et al 2017](https://www.nature.com/articles/s41467-017-00912-x) and thus requires stronger amelioration of the environment to take over.
-Nevertheless, our main conclusions about the effects of functional trait diversity are the same using either approach.
 
@@
 The results below show the stable states as a function of oxygen diffusivity for a system with an intermediate level of diversity in all functional groups, with either 1'000'000 hours at each oxygen diffusivity level (Figure \@ref(fig:ss-temp-meth3)), or 2'000'000 hours (Figure \@ref(fig:ss-temp-meth4)).
-This shows that 1'000'000 hours duration of the simulations are sufficient to reach stable state, except very close to state transitions on the trajectory of recovery (i.e.: cyanobacteria: trajectory of increasing oxygen diffusivity; sulfate-reducing bacteria: trajectory of decreasing oxygen diffusivit).
+This shows that 1'000'000 hours duration of the simulations are sufficient to reach stable state, except very close to state transitions on the trajectory of recovery (i.e.: cyanobacteria: trajectory of increasing oxygen diffusivity; sulfate-reducing bacteria: trajectory of decreasing oxygen diffusivity).
 Very close to these transitions, even at 2'000'000 hours, the dynamics are still transient, with high tolerance strains at high density, even though they will eventually be outcompeted by low tolerance (higher growth rate) strains.
@@
 
-```{r ss-temp-meth3, eval = FALSE, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth3)', fig.height=10, fig.width=8, fig.align="center"}
-
-## data made with the "run_single_sim.r" file in the ss_find, temporal method folder.
+```{r ss-temp-meth3, eval = TRUE, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth3)', fig.height=10, fig.width=8, fig.align="center"}
+
+temp_meth <- readRDS(here("data",
+                          microxanox_version_path,
+                          "temporal_method",
+                          "event_definition_2",
+                          "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
+
+## data made with the "run_single_sim.R" file in the ss_find, temporal method folder.
 
@@
 
-```{r ss-temp-meth4, eval = FALSE, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth4)', fig.height=10, fig.width=8, fig.align="center"}
+```{r ss-temp-meth4, eval = TRUE, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth4)', fig.height=10, fig.width=8, fig.align="center"}
 single_2e6 <- readRDS(here("data",
@@
 
-# Are the results driven by functional diversity?
-
-During the review process we received the following comment: *I think the authors have not shown sufficiently clearly that their results are actually driven by functional diversity.
-Fig.
-4 shows that on the collapse trajectory, the dominating functional group is itself dominated by the most tolerant strain.
-This is also true for the suppressed group on its recovery trajectory shortly before the tipping point.
-This made me wonder whether the same (or at least a very similar) results regarding the change in resilience of the system states could also be obtained with just a single strain per functional group, whose tolerance to the inhibiting substance is systematically increased.
-This could be tested fairly easily by re-running the simulations behind Fig.
-3 with just the most tolerant (and slowest growing) strain of each functional group present.* In this section we discuss this matter.
-
-Our first realisation was that we had not adequately stated what component of functional diversity we manipulated.
-We revised to state *Functional diversity has multiple components, and we manipulate only one of these, namely the range of trait space represented, which has been termed functional richness, and measured as the convex hull volume ([Villéger et al.
-2008](https://esajournals.onlinelibrary.wiley.com/doi/abs/10.1890/07-1206.1)).*
-
-Since we manipulated the range of trait space represented (sensu [Villéger et al 2008](https://esajournals.onlinelibrary.wiley.com/doi/abs/10.1890/07-1206.1)), and manipulated nothing else, we manipulated only functional diversity.
-Logically then, any effects of this manipulation must be due to the functional diversity manipulation.
-That is, regardless of the process / mechanism by which functional diversity causes an effect, it is appropriate to state that functional diversity drives the results.
-
-The reviewer’s comment motivated us to consider two questions:
-
-1. By what mechanism does functional diversity affect ecosystem stability in this study? 
-2. Could the observed effects of functional diversity also be created by manipulations of trait values that do not alter functional diversity?
-
-Question 1.
-In research concerning biodiversity and ecosystem functioning there was considerable debate about the phenomenon that high yielding species are more likely to be present in more diverse communities.
-This phenomenon was sometimes responsible for a large proportion of observed effects of biodiversity on ecosystem function.
-The debate was to a large extent resolved by recognising that biodiversity effects can result from two sources: a selection/sampling effect, and a complementarity effect.
-Both are now considered valid and important mechanisms by which diversity (including functional diversity) affects ecosystem functioning.
-We view the presence of more extreme trait values in more functionally diverse communities as an analogue of the sampling/selection effect of biodiversity, and a valid mechanism by which increased functional diversity can affect ecosystem stability.
-For example, let us assume for the moment that, indeed, only the single maximum tolerance strain present in each functional group of an ecosystem determines the resilience of that ecosystem.
-Then we would say that variation in resilience with diversity operates only by the "sampling effect".
-If we also assume that higher tolerance causes higher ecosystem resilience, then a more functionally diverse ecosystem will have higher maximum tolerance trait, and so higher resilience.
-And an ecosystem with more strains per functional group will have higher resilience (Figure \@ref(fig:samp-effect1)).
-
-Hence, even if all of the observed effects of our functional diversity manipulation were only due to presence of one strain (e.g.
-the most tolerant one), this can be considered an effect of functional diversity.
+# Underlying mechanisms
+
+In the main text we show that trait variation can affect resilience.
+In this supplementary section, we discuss the mechanism(s) underlying the observed diversity effects.
+We first explain the two major classes of mechanisms known to drive diversity effects, and then use additional simulations to elucidate the mechanisms operating in our study.
+
+## Complementarity and sampling effect
+
+Research about the relationship between biodiversity and ecosystem functioning has identified two major mechanisms by which diversity affects ecosystem functioning: the selection/sampling effect and the complementarity effect (Loreau & Hector 2001).
+The sampling effect occurs when more diverse communities have higher functioning because they have a higher probability of containing the best-performing species, i.e.
+the diversity effect is driven by only one (or few) species (Cardinale et al.
+2011).
+In contrast, the complementarity effect occurs when higher ecosystem functioning in more diverse communities is due to niche differences or positive interactions among species, i.e.
+the diversity effect is driven by many species (Cardinale et al.
+2011).
+Both effects are considered valid and important mechanisms by which diversity affects ecosystem functioning (Cardinale et al.
+2006, 2011, 2012; Fargione et al.
+2007).
+
+Similarly, the complementarity effect and the sampling effect are important mechanisms by which diversity affects stability (Loreau & Mazancourt 2013; Loreau et al.
+2021) and resilience (Steiner et al.
+2006; Hughes & Stachowicz 2011).
+For example, diversity can stabilize aggregate ecosystem properties (e.g.
+community biomass) when species differ in their responses to environmental factors and therefore respond asynchronously to environmental fluctuations (temporal complementarity effect; Loreau & Mazancourt 2013).
+However, when considering ecosystem responses to directional environmental change or pulse disturbances rather than to environmental fluctuations, the sampling effect might be of particular importance (Steiner et al.
+2006): more diverse systems might absorb a greater amount of change by having a higher chance of containing species with high environmental tolerance.
+In this scenario, the positive diversity effect on resilience is driven by one (or few) species.
+From a conservation perspective, however, one would nevertheless strive to maintain diversity and not only the most tolerant species because of the uncertainties associated with environmental change: we do not know with sufficient certainty which stressors will change in a given ecosystem and which traits will therefore be relevant in the future.
 
@@
 For most of the explored combinations and amounts of functional diversity/tolerance the tipping point positions did not differ between the diversity manipulation and the tolerance manipulation (Figure \@ref(fig:max-tol1)).
-However, the tipping point positions did differ between the diversity manipulation and the tolerance manipulation when diversity/tolerance in the SB group was high (i.e.
-in the combinations SB only, CB-SB, and CB-SB-PB).
-We show below that
+However, in some cases there were effects, three of which are described in the follow sections.
 
 (ref:max-tol1) Effects of strain variation on position of tipping points compared between simulations with all (nine) strains present and simulations where only the most tolerant strain is present.
-In the SB and CB-SB treatments there is missing data in the case with only the most tolerant strain when there were no alternate stable states and therefore no tipping points.
 
@@
 ## this subset is identified by inspection of the figure
-all_stab <- all_stab %>%
-  filter(!(var_treat == "SB" & stand_var > 0.88 & num_strains == -1),
-         !(var_treat == "CB-SB" & stand_var > 0.84 & num_strains == -1))
+#all_stab <- all_stab %>%
+#  filter(!(var_treat == "CB-SB" & stand_var > 0.84 & num_strains == -1))
 
@@
 
-When the SB contained only one strain with very high tolerance and low maximum growth rate, there were no alternate stable states, i.e.
-the state of the system was independent of the direction of change in oxygen diffusivity (Figure \@ref(fig:max-tol3)).
-Furthermore, at low oxygen diffusivity the system varied around a stable state with all three functional groups coexisting –this never occurred when there were multiple strains varying in tolerance (Figure \@ref(fig:max-tol2)), or when there was only one strain with mean tolerance.
-
-Apparently, absence of SB strains with high growth rate precludes the formation of a stable state that does not include cyanobacteria.
+When SB contained multiple strains varying in growth rate (and tolerance) there were only two stable states (Figure \@ref(fig:max-tol2)), as was previously reported.
+When, however, only one SB strain with very high tolerance and low maximum growth rate was present, there three stable states: the two previously found, and another where all three functional groups coexisted (Figure \@ref(fig:max-tol3)) – this never occurred when there were multiple strains varying in tolerance.
+
+Apparently, at low oxygen diffusivity levels, the absence of SB strains with high growth rate precludes the formation of a stable state that does not include cyanobacteria.
 It seems that the most tolerant SB strain does not have a high enough growth rate to itself exclude the cyanobacteria.
 Cyanobacteria are therefore always present, regardless of the oxygen diffusivity.
+We do not have an explanation of why the cyanobacteria are, however, excluded at intermediate oxygen diffusivities.
 
@@
        PB_var_gmax_s == 0)
-fig_state_vs_o2diff_sidebyside_alternative_nofliparrows(max_tol_one)
-```
-
-### What causes the variation in response to oxygen diffusivity (SB)?
+fig_state_vs_o2diff_sidebyside_alternative(max_tol_one)
+```
 
@@
 
-## High tolerance vs. high diversity in CB and SB
-
-As in the SB only case, the absence of lower tolerance-higher growth rate strains changes the system to a parameter space where it does not display alternate states, at least within the range of oxygen diffusivities simulated (Figure \@ref(fig:max-tol5)).
-
-(ref:max-tol4)  Stables states found when there is high trait variation among nine strains of CB and SB. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
-
-```{r max-tol4, echo = FALSE,  include=TRUE, fig.cap='(ref:max-tol4)', fig.height=10, fig.width=8, fig.align="center"}
-filter(nine_strains,
-       abs(CB_var_gmax_s - 0.026592798) < 0.001,
-       abs(SB_var_gmax_s - 0.079778395) < 0.001,
-       PB_var_gmax_s == 0) %>%
-fig_state_vs_o2diff_sidebyside_alternative_leftfliponly()
-```
+## High tolerance vs. high diversity in CB-SB
+
+In the SB-SB case, presence of only the high tolerance strain could cause the system to not display any alternate stable states (Figure \@ref(fig:max-tol5)).
 
@@
        PB_var_gmax_s == 0)
-fig_state_vs_o2diff_sidebyside_alternative_nofliparrows(max_tol_one_CBSB)
-```
-
-### What causes the variation in response to oxygen diffusivity (CB-SB)?
-
-In the ecosystem shown in Figure \@ref(fig:max-tol5), where CB and SB each contained only one strain with very high tolerance, there was large variation in state variables along the oxygen diffusivity gradient at values less than about -6.5.
-To examine what might be causing this, we simulated the ecosystem at a constant oxygen diffusivity of $log_{10}$ oxygen diffusivity of -7 (Figure \@ref(fig:CBSB-maxtol-dyn1)).
-We see that the dynamics are qualitatively different from other cases in which there is a stable state reached in such a simulation (Figure \@ref(fig:sb-div-effect4)).
-It appears that the SB strain with high tolerance is able to initiate a transition to an anoxic state, but is not able to create a stable anoxic state.
-
-```{r echo = FALSE}
-#nine_strain_one$pars[[1]]
-#max_tol_one$pars[[1]]
-#fig_state_vs_o2diff_sidebyside_alternative(nine_strain_one)
-#fig_state_vs_o2diff_sidebyside_alternative(max_tol_one)
-parameter <- max_tol_one_CBSB$parameter[[1]]
-parameter$strain_parameter <- max_tol_one$pars[[1]]
-#parameter$strain_parameter <- ss_result$pars[[1]]
-total_initial_abundances <- 10^5
-parameter <- set_temporal_ssfind_initial_state(parameter,
-                                               total_initial_abundances,
-                                               total_initial_abundances,
-                                               total_initial_abundances)
-parameter$log10a_series <- c(-7, -7)
-wait_time <-  1e5
-parameter$sim_duration <- wait_time * length(parameter$log10a_series)
-parameter$sim_sample_interval <- 10
-#parameter$sim_duration
-test1 <- run_simulation(parameter)
-```
-
-(ref:CBSB-maxtol-dyn1) Temporal dynamics of an ecosystem with a single CB strain with high tolerance and a single SB strain with high tolerance, the same one as in Figure \@ref(fig:max-tol5) simulated with constant $log_{10}(oxygen diffusivity)$ of -6.
-
-```{r CBSB-maxtol-dyn1, echo = FALSE,  include=TRUE, fig.cap='(ref:CBSB-maxtol-dyn1)', fig.height=10, fig.width=8, fig.align="center"}
-p <- plot_dynamics(test1)
-p[[1]] <- p[[1]] + 
-  xlab(NULL) + 
-  ylab(expression(log[10](density)~(cells~L^{-1}))) +
-  theme_bw()
-p[[2]] <- p[[2]] + 
-  xlab(NULL) + 
-  ylab(expression(log[10](density)~(cells~L^{-1}))) +
-  theme_bw()
-p[[3]] <- p[[3]] + 
-  xlab(NULL) + 
-  ylab(expression(log[10](density)~(cells~L^{-1}))) +
-  theme_bw()
-p[[4]]$data <- p[[4]]$data %>% 
-  dplyr::filter(species != "a")
-p[[4]]$data$species <- p[[4]]$data$species %>%
-  dplyr::recode(SO = "Oxidised sulfur", O = "Oxygen", SR = "Sulfide", P = "Phosphorus")
-p[[4]] <- p[[4]] + 
-  xlab("time (h)") + 
-  ylab(expression(log[10](concentration)~(µM))) + 
-  labs(colour = "substrate") +
-  theme_bw()
-
-p
+max_tol_one_CBSB <- filter(maxtolonly_strains,
+       abs(CB_var_gmax_s - 0.028254848) < 0.001,
+       abs(SB_var_gmax_s - 0.084764545) < 0.001,
+       PB_var_gmax_s == 0)
+
+fig_state_vs_o2diff_sidebyside_alternative(max_tol_one_CBSB)
 ```
@@
 When in each of the three functional groups only the most tolerant strain is present, the resilience of the oxic state is greater than when there is variation in strain tolerance within groups.
-Looked at from another perspective, comparing CB-SB and CB-SB-PB both with only the most tolerant strains, presence of a high tolerance PB strain (in CB-SB-PB) allows the formation of an anoxic cyanobacteria-free stable state (whereas there was no such state in CB-SB).
-We interpret this as presence of a high tolerance PB strain stabilising the anoxic state, perhaps by increasing the availability of oxidised sulfur which is a resource for SB.
-Nevertheless, absence of SB strains with high growth rate seems to shift the oxic-anoxic tipping point to lower oxygen diffusivity.
+It is not entirely clear why this effect only occurs only in this combination.
 
@@
 \@ref(fig:fig-add-linear)d).
-When the two groups of sulfur bacteria varied in traits, the anoxic-oxic tipping point occurred at lower oxygen diffusivity than expected by additivity (Fig.
+When the two groups of sulfur bacteria varied in traits, the anoxic-oxic tipping point occurred at higher oxygen diffusivity than expected by additivity (Fig.
 \@ref(fig:fig-add-linear)f).
@@
 \@ref(fig:fig-add-linear)g-i).
-Both tipping points occurred at lower levels of oxygen diffusivity than expected by additivity.
-Interestingly, diversity in the cyanobacteria moved the shift to the oxic state to lower levels of oxygen diffusivity although independent variation in the cyanobacteria had no effect on this tipping point.
+
+# Comparing the effects of different treatments
+
+(ref:comp-comb) Another method for comparing the effects of different diversity treatments.
+Some lines (treatment combinations) are over-plotted and therefore show identical effects of some combinations.
+
+```{r comp-comb, echo = FALSE,  include=TRUE, fig.height=8, fig.width=8, fig.align="center", fig.cap='(ref:comp-comb)'}
+
+all_stab <- readRDS(here("data",
+                         microxanox_version_path,
+                         "temporal_method",
+                         "event_definition_2",
+                         "processed_data",
+                         "all_stab_data.RDS"))
+wait_time <- 1e6
+which_strain <- 9
+plot_here <- all_stab %>%
+  filter(waittime == wait_time)
+
+  p1 <- plot_here %>%
+    #filter(var_treat == "CB") %>%
+    filter(num_strains == which_strain) %>%
+    filter(Species == "SB_tot") %>%
+    ggplot(aes(x = stand_var
+               #col = as.factor(num_strains))
+    )) +
+    geom_line(aes(y = hyst_min_log, col=var_treat), lwd = 1, alpha = 0.8) +
+    geom_line(aes(y = hyst_max_log, col=var_treat), lwd = 1, alpha = 0.8) +
+    #geom_ribbon(aes(ymin = hyst_min_log, ymax = hyst_max_log),
+    #            fill = "green", alpha = 0.1) +
+    #facet_grid(var_treat ~ ., scales = "fixed") +
+    xlab("Standardised amount of trait variation") +
+    ylab(expression(log[10](oxygen~diffusivity)~(h^{-1}))) +
+    #labs(fill = "Variation in\nonly these\nfunctional groups") +
+    coord_flip() +
+    #guides(col = guide_legend(title="Number of strains"),
+    #       fill = guide_none()) +
+    theme_bw() +
+    theme(
+      legend.position="top",
+      panel.background = element_blank(),
+      #strip.text.x = element_blank()
+    ) +
+    geom_hline(yintercept = c(-8, 0), col = "grey", lwd = 3) #+
+    #geom_text(aes(x = 0.95, y = -8.1, label = label), colour = "black") +
+    #ggtitle(figure_title)
+
+  p1
+
+```
+
+# CB diversity effects
+
+Increased CB diversity causes a slight decrease in the resilience of the anoxic state.
+The following two figures show the state responses to oxygen diffusivity with low Figure \@ref(fig:ss-CB-only1) and high Figure \@ref(fig:ss-CB-only2) levels of CB diversity.
+
+The difference in the position of the anoxic to oxic tipping point is small.
+It is, in fact the smallest it could be, as it is the smallest step size in oxygen diffusivity used in the simulations.
+Furthermore, we think the presence of higher strain diversity can increase the rate of response of the system (since there is a strain with higher growth rate than in low diversity levels) and that this difference in response rates is likely responsible for the very small difference in resilience.
+
+(ref:ss-CB-only1) Stable state of the system with **low** level of diversity in only CB, and no diversity in the other two groups. All other aspects are as in Figure \@ref(fig:ss-temp-meth3).
+
+```{r ss-CB-only1, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-CB-only1)', fig.height=10, fig.width=8, fig.align="center"}
+wait_time <- "1e+06"
+ss_9s <- readRDS(here::here("data",
+                            microxanox_version_path, 
+                            "temporal_method",
+                            "event_definition_2",
+                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+#stab_9s <- readRDS(here::here(\"data", "0_ss_finding", "temporal_method", microxanox_version_path, paste0("stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS"))
+
+#max <- max(ss_3s$PB_var_gmax_s)
+#f <- 0.625
+#fv <- f*max
+
+only_CB_variable <- ss_9s %>%
+  filter(
+    abs(SB_var_gmax_s) < 0.0001,
+    abs(PB_var_gmax_s) < 0.0001
+  )
+only_CB_variable <- only_CB_variable[order(only_CB_variable$CB_var_gmax_s), ]
+
+#only_CB_variable$CB_var_gmax_s
+
+fig_state_vs_o2diff_sidebyside_alternative(only_CB_variable[2,])
+
+#fig_state_vs_o2diff(only_SB_variable[13,])
+```
+
+(ref:ss-CB-only2) Stable state of the system with **high** level of diversity in only CB, and no diversity in the other two groups. All other aspects are as in Figure \@ref(fig:ss-temp-meth3).
+
+```{r ss-CB-only2, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-CB-only2)', fig.height=10, fig.width=8, fig.align="center"}
+
+fig_state_vs_o2diff_sidebyside_alternative(only_CB_variable[20,])
+
+#fig_state_vs_o2diff(only_SB_variable[13,])
+```
 

### 2022-11-16 reports/supplement/supplement_0.9.1.Rmd
First attempt at #27 https://github.com/UZH-PEG/diversity_envresp1/issues/27

@@
 Microbiol., 2, 62.
+
+# ADDED BY RAINER Issue #27
+
+## 
+```{r}
+
+## PB
+only_PB_variable <- ss_9s %>%
+  filter(
+    abs(CB_var_gmax_s) < 0.0001,
+    abs(SB_var_gmax_s) < 0.0001
+  )
+only_PB_variable <- only_PB_variable[order(only_PB_variable$PB_var_gmax_s), ]
+
+## CB
+only_CB_variable <- ss_9s %>%
+  filter(
+    abs(PB_var_gmax_s) < 0.0001,
+    abs(SB_var_gmax_s) < 0.0001
+  )
+only_CB_variable <- only_CB_variable[order(only_CB_variable$CB_var_gmax_s), ]
+
+## SB
+only_SB_variable <- ss_9s %>%
+  filter(
+    abs(PB_var_gmax_s) < 0.0001,
+    abs(CB_var_gmax_s) < 0.0001
+  )
+only_SB_variable <- only_SB_variable[order(only_SB_variable$SB_var_gmax_s), ]
+
+## PB_CB
+only_PB_CB_variable <- ss_9s %>%
+  filter(
+    abs(SB_var_gmax_s) < 0.0001
+  )
+only_PB_CB_variable <- only_PB_CB_variable[order(only_PB_CB_variable$PB_var_gmax_s), ]
+
+## CB_SB
+only_CB_SB_variable <- ss_9s %>%
+  filter(
+    abs(PB_var_gmax_s) < 0.0001
+  )
+only_CB_SB_variable <- only_CB_SB_variable[order(only_CB_SB_variable$PB_var_gmax_s), ]
+
+## PB_SB
+only_PB_SB_variable <- ss_9s %>%
+  filter(
+    abs(CB_var_gmax_s) < 0.0001
+  )
+only_PB_SB_variable <- only_PB_SB_variable[order(only_PB_SB_variable$PB_var_gmax_s), ]
+
+## CB_PB_SB
+only_CB_PB_SB_variable <- ss_9s
+only_CB_PB_SB_variable <- only_CB_PB_SB_variable[order(only_CB_PB_SB_variable$PB_var_gmax_s), ]
+
+```
+
+## PB
+```{r echo = FALSE,  include=TRUE, fig.height=10, fig.width=8, fig.align="center"}
+fig_state_vs_o2diff_sidebyside_alternative(only_PB_variable[sim1,])
+fig_state_vs_o2diff_sidebyside_alternative(only_PB_variable[sim2,])
+```
+
+## CB
+```{r echo = FALSE,  include=TRUE, fig.height=10, fig.width=8, fig.align="center"}
+sim3 <- 19
+fig_state_vs_o2diff_sidebyside_alternative(only_CB_variable[sim1,])
+fig_state_vs_o2diff_sidebyside_alternative(only_CB_variable[sim2,])
+fig_state_vs_o2diff_sidebyside_alternative(only_CB_variable[sim3,])
+```
+
+## SB
+```{r echo = FALSE,  include=TRUE, fig.height=10, fig.width=8, fig.align="center"}
+fig_state_vs_o2diff_sidebyside_alternative(only_SB_variable[sim1,])
+fig_state_vs_o2diff_sidebyside_alternative(only_SB_variable[sim2,])
+```
+
+## PB & CB
+```{r echo = FALSE,  include=TRUE, fig.height=10, fig.width=8, fig.align="center"}
+fig_state_vs_o2diff_sidebyside_alternative(only_PB_CB_variable[sim1,])
+fig_state_vs_o2diff_sidebyside_alternative(only_PB_CB_variable[sim2,])
+```
+
+## CB & SB
+```{r echo = FALSE,  include=TRUE,, fig.height=10, fig.width=8, fig.align="center"}
+fig_state_vs_o2diff_sidebyside_alternative(only_CB_SB_variable[sim1,])
+fig_state_vs_o2diff_sidebyside_alternative(only_CB_SB_variable[sim2,])
+```
+
+## PB & SB
+```{r echo = FALSE,  include=TRUE, fig.height=10, fig.width=8, fig.align="center"}
+fig_state_vs_o2diff_sidebyside_alternative(only_PB_SB_variable[sim1,])
+fig_state_vs_o2diff_sidebyside_alternative(only_PB_SB_variable[sim2,])
+```
+
+## CB & PB & SB
+```{r echo = FALSE,  include=TRUE, fig.height=10, fig.width=8, fig.align="center"}
+fig_state_vs_o2diff_sidebyside_alternative(only_CB_PB_SB_variable[sim1,])
+fig_state_vs_o2diff_sidebyside_alternative(only_CB_PB_SB_variable[sim2,])
+```

### 2022-11-16 reports/supplement/allssplots_maxtol_0.9.1.Rmd
added all ss plots

--- 2022-11-15 reports/supplement/supplement_0.9.1.Rmd
@@
 ---
-title: Supplementary Report for the article *Functional diversity can facilitate the collapse of an undesirable ecosystem state*
+title: All stable state plots, with only the maximum tolerance strain
 author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
@@
 
-# Introduction
-
-This document is the Supplementary Report for the report *Functional diversity can facilitate the collapse of an undesirable ecosystem state*.
-
-# Growth and inhibition functions
-
-The rate of change in population densities is given by the growth rate - death rate [Bush et al 2017](https://www.nature.com/articles/s41467-017-00912-x).
-Growth rate is the growth rate in absence of any inhibition multiplied by the amount of inhibition.
-
-Growth rate in the absence of inhibition was modeled with the Monod equation with multiplicative kinetics when two substrates determine growth rate:
-
-$g_j(X, Y) = g_{max,j} (\frac{X}{K_{j,X} + X})(\frac{Y}{K_{j,Y} + Y})$
-
-$g_{max,j}$ is the maximum specific growth rate of strain $j$.
-$X$ is the concentration of substrate 1, and $Y$ is the concentration of substrate 2.
-$K_{j,X}$ and $K_{j,Y}$ are the half-saturation constants of species $j$ on substrates $X$ and $Y$.
-
-Inhibition of growth by a substrate was modelled with the Haldane equation:
-
-$h_j(X) = \frac{1}{1+ (X / H_{j,X})}$
-
-$H_{j,X}$ can be thought of as a half-inhibition constant: the concentration of $X$ at which the growth rate of species $j$ is reduced by 50%.
-
-For further information details of the functions used to model system, please see the original publication by Bush *et al.* (2018)
-
-# Creating among strain diversity
-
-Here we provide additional description of the method used to create strain variation within functional groups.
-The following should be read only after the relevant text in the main report.
-We generated variation in maximum growth rate $G_{max}$ and tolerance to reduced sulfur $h_{SR}$ or oxygen $h_{O}$ by varying the range of trait values around a reference trait value.
-To manipulate the amount of variation in a given trait and functional group, we introduced the meta-parameter $Div$ subscripted by the trait and the functional group.
-Take for example the cyanobacteria functional group, a reference maximum growth rate parameter $G_{max,CB}$ and a reference tolerance parameter $h_{SR,CB}$.
-The amount of among strain variation in the cyanobacteria is controlled by the two meta-parameters $Div_{G_{max,CB}}$ and $Div_{h_{SR,CB}}$.
-To create a trade-off, the two meta-parameters were always of different sign.
-The among strain variation was calculated such that the growth rate of strain $i = 1$ was a factor $1/({2Div_{G_{max,CB}}})$ of the reference growth rate, and the growth rate of the $i = n$ strain was a factor $2Div_{G_{max,CB}}$ of the reference growth rate.
-The growth rate of the $i = {2,...n-1}$ other strains was the reference growth rate multiplied by a factor that was equally distributed between the factor of the $i = 1$ and $i = n$ strain.
-This implementation of the variation and trade-off has the assumption of a linear trade-off of log-log transformed among-strain variation.
-Hence, for example, with the reference growth rate $G_{max,CB} = 0.05$, among strain variation of $Div_{G_{max,CB}} = 1$, and nine strains ($n = 9$), the growth rates of the nine strains are 0.025, 0.03, 0.035, 0.042, 0.05, 0.059, 0.071, 0.084, 0.1.
-Put another way, the growth rate parameter of the $i$-th of the $n$ strains in a functional group was calculated as $G_{max,i} = D_i * G_{max}$ where $D_i$ is the $i$-th element of the set $D = {2f(x)Div_{G_{max}} |x ∈ N, x ≤ n}$, where $f(x) = (x − (n + 1)/2)/((n − 1)/2)$.
-
-This procedure ensures that the range of trait values is independent of the number of strains.
-When there were only two strains, the two strains took the minimum and maximum traits values, as defined by the $Div$ variable for that trait.
-When there were three strains, one had the minimum trait value, one the maximum, and one the mean.
-With nine strains, one had the minimum trait value, one the maximum, one the mean, and three were equally spaced (on log scale) between the minimum and the mean, and the remaining three between the maximum and the mean.
-
-We show three examples of the created variation among strains within functional groups, one for nine strains (Figure \@ref(fig:nine-strain-div)), one for three (Figure \@ref(fig:three-strain-div)), and one for two (Figure \@ref(fig:two-strain-div)).
-In each of these three examples, three graphs show the diversity among strains in the maximum growth rate trait and the tolerance trait, plotted against each other and therefore also showing the trade-off between the two traits.
-
-Notice that in all three cases, the range of trait variation represented by the strains is the same, even though the number of strains differs.
-This approach allowed us to independently manipulate trait diversity and number of strains.
-Also note that maximum growth rate of strains is evenly distributed on a log scale, even though it may appear at first site that they are distributed evenly on a linear scale (e.g.
-Figure \@ref(fig:three-strain-div)).
-
-```{r  echo = FALSE}
-CB_var_multiplier <- 2
-SBPB_var_multiplier <- 6
-CB_gmax_div <- 0.015789474 * CB_var_multiplier
-CB_h_div <- -0.08 * CB_var_multiplier
-SB_gmax_div <- 0.015789474 * SBPB_var_multiplier
-SB_h_div <- -0.323  * SBPB_var_multiplier
-PB_gmax_div <- 0.015789474  * SBPB_var_multiplier
-PB_h_div <- -0.323  * SBPB_var_multiplier
-num_div_treatment_levels <- 2
-```
-
-All three examples have the following amounts of trait variation: $Div_{G_{max,CB}}$ = `r round(CB_gmax_div, 3)`, $Div_{h_{SR,CB}}$ = `r round(CB_h_div, 3)`, $Div_{G_{max,SB}}$ = `r round(SB_gmax_div, 3)`, $Div_{h_{O,SB}}$ = `r round(SB_h_div, 3)`, $Div_{G_{max,PB}}$ = `r round(PB_gmax_div, 3)`, $Div_{h_{O,PB}}$ = `r round(PB_h_div, 3)`.
-These are also the maximum amounts of trait variation explored in the simulations.
-
-(ref:nine-strain-div) Trait variation with nine strains in each of the functional groups.
-In all panels colour indicates the functional group, darker shades show more tolerant-lower growth rate strains, lighter shades show less tolerant-higher growth rate strains.
-Tolerance is given as the concentration of the inhibiting substrate where the growth rate of the strain is reduced by 50%.
-
-```{r nine-strain-div, echo = FALSE,  include=TRUE, fig.cap='(ref:nine-strain-div)', fig.align="center", fig.height=3, fig.width=8}
-
-num_CB_strains <- 9
-num_PB_strains <- 9
-num_SB_strains <- 9
-var_expt <- create_diversity_factorial(
-  zero = zero, unity = unity,
-  num_div_treatment_levels = num_div_treatment_levels,
-  CB_gmax_div = CB_gmax_div, CB_h_div = CB_h_div,
-  SB_gmax_div = SB_gmax_div, SB_h_div = SB_h_div,
-  PB_gmax_div = PB_gmax_div, PB_h_div = PB_h_div,
-  default_9strain = new_strain_parameter(
-    n_CB = num_CB_strains,
-    n_SB = num_SB_strains,
-    n_PB = num_PB_strains,
-    values_initial_state =  "bush_ssfig3"
-  )
-)
-display_diversity(4,
-  var_expt = var_expt,
-  num_CB_strains = num_CB_strains,
-  num_SB_strains = num_SB_strains,
-  num_PB_strains = num_PB_strains,
-  which_graphs = 1
-)
-```
-
-(ref:three-strain-div) Trait variation with three strains in each of the functional groups.
-Note that the three displayed strains are the 1st, 5th, and 9th strains from the nine strain example shown in Figure \@ref(fig:nine-strain-div).
-In all panels colour indicates the functional group, darker shades show more tolerant-lower growth rate strains, lighter shades show less tolerant-higher growth rate strains.
-Tolerance is given as the concentration of the inhibiting substrate where the growth rate of the strain is reduced by 50%.
-
-```{r three-strain-div, echo = FALSE,  include=TRUE, fig.cap='(ref:three-strain-div)', fig.height=3, fig.width=8, fig.align="center"}
-
-num_CB_strains <- 3
-num_PB_strains <- 3
-num_SB_strains <- 3
-var_expt <- create_diversity_factorial(
-  zero = zero, unity = unity,
-  num_div_treatment_levels = num_div_treatment_levels,
-  CB_gmax_div = CB_gmax_div, CB_h_div = CB_h_div,
-  SB_gmax_div = SB_gmax_div, SB_h_div = SB_h_div,
-  PB_gmax_div = PB_gmax_div, PB_h_div = PB_h_div,
-  default_9strain = new_strain_parameter(
-    n_CB = num_CB_strains,
-    n_SB = num_SB_strains,
-    n_PB = num_PB_strains,
-    values_initial_state =  "bush_ssfig3"
-  )
-)
-display_diversity(4,
-  var_expt = var_expt,
-  num_CB_strains = num_CB_strains,
-  num_SB_strains = num_SB_strains,
-  num_PB_strains = num_PB_strains,
-  which_graphs = 1
-)
-
-#0.05*2^(CB_gmax_div) - 0.05
-#0.05 - 0.05*2^(-CB_gmax_div)
-
-```
-
-(ref:two-strain-div) Trait variation with two strains in each of the functional groups.
-Note that the two displayed strains are the 1st and 9th strains from the nine strain example shown in Figure \@ref(fig:nine-strain-div).
-In all panels colour indicates the functional group, darker shades show more tolerant-lower growth rate strains, lighter shades show less tolerant-higher growth rate strains.
-Tolerance is given as the concentration of the inhibiting substrate where the growth rate of the strain is reduced by 50%.
-
-```{r two-strain-div, echo = FALSE,  include=TRUE, fig.cap='(ref:two-strain-div)', fig.height=3, fig.width=8, fig.align="center"}
-
-num_CB_strains <- 2
-num_PB_strains <- 2
-num_SB_strains <- 2
-var_expt <- create_diversity_factorial(
-  zero = zero, unity = unity,
-  num_div_treatment_levels = num_div_treatment_levels,
-  CB_gmax_div = CB_gmax_div, CB_h_div = CB_h_div,
-  SB_gmax_div = SB_gmax_div, SB_h_div = SB_h_div,
-  PB_gmax_div = PB_gmax_div, PB_h_div = PB_h_div,
-  default_9strain = new_strain_parameter(
-    n_CB = num_CB_strains,
-    n_SB = num_SB_strains,
-    n_PB = num_PB_strains,
-    values_initial_state =  "bush_ssfig3"
-  )
-)
-display_diversity(4,
-  var_expt = var_expt,
-  num_CB_strains = num_CB_strains,
-  num_SB_strains = num_SB_strains,
-  num_PB_strains = num_PB_strains,
-  which_graphs = 1
-)
-```
-
-A consequence of this variation and of the trade-offs is shown in  Figure \@ref(fig:growth-rates), which shows the relationship between realised growth rate and the concentration in the environment of the respective inhibiting substance, e.g.
-reduced sulfur for the cyanobacteria.
-In these graphs only the least and most tolerant strains are shown.
-The lines cross due to the trade-off.
-At high concentrations of the inhibiting substance the more tolerant strain has higher realised growth rate, while at lower concentrations it is the less tolerant strain that has the higher realised growth rate.
-
-(ref:growth-rates) Response of realised growth rate to variation in concentration of the inhibiting substrate for two strains, namely the most and the least tolerant strain.
-As always colour indicates the functional group, darker shades show more tolerant-lower growth rate strains, lighter shades show less tolerant-higher growth rate strains.
-
-```{r growth-rates, echo = FALSE,  include=TRUE, fig.cap='(ref:growth-rates)', fig.height=3, fig.width=8, fig.align="center"}
-display_diversity(4,
-  var_expt = var_expt,
-  num_CB_strains = num_CB_strains,
-  num_SB_strains = num_SB_strains,
-  num_PB_strains = num_PB_strains,
-  which_graphs = 2
-)
-```
-
-# Method for finding stable states
-
-## General method
-
-We now discuss two approaches for finding how the stable state of the system varies along the gradient of oxygen diffusivity when there exists the possibility of multiple stable states.
-In the main article we describe and report results of the method that we term the *Temporal method*.
-
-Here we also describe and give results of what we term the *Replication method*.
-In this, we made separate simulations for each of many values of oxygen diffusivity, ran the simulations for long enough to ensure transients had passed, and recorded the state.
-We ran multiple simulations per value of oxygen diffusivity, and started them with different initial conditions (either low or high total cyanobacterial abundance), so as to check for presence of alternate stable states.
-This method was used by [Bush et al 2017](https://www.nature.com/articles/s41467-017-00912-x).
-We term it the replication method since it is achieved by having many independent replicates of the ecosystem, each with a different oxygen diffusivity, and also a separate replicate for each of the different chosen initial conditions.
-
-As is shown in the figures below, the temporal and replication methods result in very similar regions of bistability.
-
-### Replication method, no diversity
-
-```{r repl-meth1, echo=FALSE, eval = TRUE}
-repl_meth <- readRDS(here("data",
-                          microxanox_version_path,
-                          "replication_method",
-                          "event_definition_2",
-                          "ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
-temp_meth <- readRDS(here("data",
-                          microxanox_version_path,
-                          "temporal_method",
-                          "event_definition_2",
-                          "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
-```
-
-(ref:repl-meth2) Stable states found with the **replication method**.
-The left column of panels refers to the stable state when oxygen diffusivity is at first high (favouring the oxic state).
-The right column refers to when oxygen diffusivity is at first low (favouring the anoxic state).
-Points (which sometimes are so close as to appear as thick lines) show the stable state at the end of each period of constant oxygen diffusivity.
-Thin lines are for visualisation only, and join the points.
-Grey arrows show the oxygen diffusivity at which the system flips, and the direction of the flip.
-The length of the grey arrows is without meaning.
-
-```{r repl-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:repl-meth2)', fig.height=10, fig.width=8, fig.align="center"}
-fig_state_vs_o2diff_sidebyside_alternative_repmeth(repl_meth[1,])
-```
-
-### Temporal method, no diversity
-
-(ref:temp-meth2) Stable states found with the **temporal method**. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
-
-```{r temp-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:temp-meth2)', fig.height=10, fig.width=8, fig.align="center"}
-fig_state_vs_o2diff_sidebyside_alternative(temp_meth[1,])
-```
-
-### Both methods overlaid, no diversity
-
-(ref:both-meth1) Stable states of the two methods overlaid, the temporal method with a dashed line, and the replication method with a solid line.
-
-```{r both-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:both-meth1)', fig.height=8, fig.width=8, fig.align="center"}
-
-repl_method_1 <- repl_meth$ss_res[[1]] %>%
-     mutate(time = NA,
-            direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
-  select(names(temp_meth$ssfind_result[[1]]))
-
-ss_result1 <- repl_method_1
-ss_result2 <- temp_meth$ssfind_result[[1]]
-
-plot_ss_result6_new(repl_method_1,
-                    temp_meth$ssfind_result[[1]],
-                    xlims = c(-8, 0))
-```
-
-## Effect of diversity, replication method
-
-### Overall effects of diversity
-
-The replication method shows qualitatively the same effects of functional diversity (Figure \@ref(fig:div-repl-meth1)) as those revealed by the temporal method. Namely
-
--   Introducing functional diversity in only the cyanobacteria increases the resilience of the oxic state and slightly decreases the resilience of the anoxic state. 
--   Introducing functional diversity in only the sulfate-reducing bacteria increases the resilience of the anoxic state and reduces the resilience of the oxic state.
--   Introducing functional diversity in only the phototrophic sulfur bacteria reduces the resilience of the anoxic state and has no effect on the resilience of the oxic state. 
--   Introducing functional diversity in more than one functional group reduces, reverses, or does not change the effect of diversity in individual functional groups.
-For example, introducing functional diversity in all three functional groups reduces the resilience of the oxic state when trait variation is low but increases the resilience of the oxic state when trait variation is high.
-
-(ref:div-repl-meth1) **Replication method results.** **Left column of panels**: the effect of trait diversity (y-axis) on the positions of the tipping points (anoxic to oxic in blue, oxic to anoxic in red), which determine the extent of the region of bistability (green shaded region) in the oxygen diffusivity gradient.
-The left-most region is anoxic only, the middle is oxic or anoxic depending on historical conditions, and the right-most is oxic only.
-The thick grey vertical lines at -8 and 0 on the x-axis show the extent of the oxygen diffusivity gradient investigated in the simulations.
-**Right column of panels**: The effect size of trait variation on resilience, with positive values on the y-axis indicating that diversity has increased resilience.
-
-```{r div-repl-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-repl-meth1)', fig.height=8, fig.width=8, fig.align="center"}
-all_stab <- readRDS(here("data", 
-                         microxanox_version_path,
-                         "replication_method",
-                         "event_definition_2",
-                         "processed_data",
-                         "all_stab_data.RDS"))
-
-sim_length <- 1e6 ## currently a problem in how sim length is parsed by the data processing step
-num_strains <- 9
-plot_here <- all_stab %>%
-  filter(simlength == sim_length)
-p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
-                                     which_strain = num_strains,
-                                     figure_title = paste0(sim_length,
-                                                           " simulation length,\n",
-                                                           num_strains,
-                                                           " strains"))
-p2 <- fig_resilience_vs_div(plot_here,
-                            which_strain = num_strains,
-                            figure_title = " ")
-p1 + p2
-
-```
-
-### An example of stable states
-
-Figure \@ref(fig:repl-meth-ex1) shows an example of stable states along the oxygen diffusivity gradient produced by the replication method for finding stable states.
-The patterns are similar to those produced by the temporal method for finding the stable states (see Figure 4 in the main report), though they differ in one respect: close to the transition back to the state a group dominates, some of the more tolerant strains occur in the stable states found by the temporal method (Figure 4 in the main report), while they do not occur in stable states found by the replication method (Figure \@ref(fig:repl-meth-ex1) here).
-We understand that the appearance of these strains is transient, and the difference in their appearance results from the differences in starting conditions of the two methods.
-Specifically, in the temporal method, the initial condition at a new level of oxygen diffusivity is the stable state at the previous level of oxygen diffusivity, while in the replication method the starting conditions are identical at each level of oxygen diffusivity.
-These differences in starting conditions apparently result in longer duration of transients in the temporal method than the replication method.
-
-An interesting feature of these results is that although the position of the oxic to anoxic tipping point is affected by diversity in the sulfate-reducing bacteria (Figure \@ref(fig:div-repl-meth1) and Figure 3 in the main report) there is no evidence of more tolerant strains of sulfate-reducing bacteria being present in the final system state (Figure \@ref(fig:repl-meth-ex1)).
-This phenomenon is explained in Section \@ref(SB2).
-
-(ref:repl-meth-ex1) Stable states found with the **replication method** with intermediate levels of diversity in all functional groups.
-Figure features are otherwise the same as those in Figure \@ref(fig:repl-meth2)).
-
-```{r repl-meth-ex1, echo = FALSE,  include=TRUE, fig.cap='(ref:repl-meth-ex1)', fig.height=10, fig.width=8, fig.align="center"}
-repl_meth <- readRDS(here("data",
-                          microxanox_version_path,
-                          "replication_method",
-                          "event_definition_2",
-                          "ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
-fig_state_vs_o2diff_sidebyside_alternative(repl_meth[94,])
-```
-
-## Effect of abundance change event
-
-As mentioned in the main report, to avoid very low strain densities, we added 1 unit of density to every biological state variable every 1,000 hours.
-We here show that a slightly different method produced the same results.
-Specifically, we tested the effect of making an abundance floor of 1 unit that was implemented every 1,000 hours.
-I.e.
-every 1,000 hours, any abundances that were lower than 1 unit were set to 1 unit.
-As shown in Figure \@ref(fig:div-temp-eventdef1), the results with this floor abundance are similar as when 1 was added every 1,000 hours.
-Note that a coarser gradient of trait variation was used, hence the saw-tooth patterns.
-A further difference is the large decrease in resilience of the anoxic to oxic transition above moderate levels of diversity in the SB and CB-SB treatments.
-This pattern can also occur with addition of 1 abundance unit (e.g., see Figure \@ref(fig:div-temp-meth3)), and is discussed in the section that concerns this below (section [SB diversity effects]).
-
-(ref:div-temp-eventdef1) **Results with an abundance floor.** **Left column of panels**: the effect of trait diversity (y-axis) on the positions of the tipping points (anoxic to oxic in blue, oxic to anoxic in red), which determine the extent of the region of bistability (green shaded region) in the oxygen diffusivity gradient.
-The left-most region is anoxic only, the middle is oxic or anoxic depending on historical conditions, and the right-most is oxic only.
-The thick grey vertical lines at -8 and 0 on the x-axis show the extent of the oxygen diffusivity gradient investigated in the simulations.
-**Right column of panels**: The effect size of trait variation on resilience, with positive values on the y-axis indicating that diversity has increased resilience, i.e.
-delayed the shift to the other state.
-
-```{r div-temp-eventdef1, eval = TRUE, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-eventdef1)', fig.height=8, fig.width=8, fig.align="center"}
-all_stab <- readRDS(here("data",
-                          microxanox_version_path,
-                          "temporal_method",
-                          "event_definition_1",
-                          "processed_data",
-                         "all_stab_data.RDS"))
-
-wait_time <- 1e6
-num_strains <- 9
-plot_here <- all_stab %>%
-  filter(waittime == wait_time)
-p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
-                                     which_strain = num_strains,
-                                     figure_title = paste0(wait_time,
-                                                           " wait time,\n",
-                                                           num_strains,
-                                                           " strains"))
-p2 <- fig_resilience_vs_div(plot_here,
-                            which_strain = num_strains,
-                            figure_title = " ")
-p1 + p2
-
-```
-
-## Further thoughts
-
-Here we give some further thoughts regarding the comparison of the temporal and replication method for stable state finding.
-
-A particularly notable difference between the two approaches is in the initial condition.
-In the temporal approach, the initial condition at a new level of oxygen diffusivity is the stable state at the previous level of oxygen diffusivity, while in the approach of [Bush et al 2017](https://www.nature.com/articles/s41467-017-00912-x) the initial conditions are fixed and arbitrary (though this approach is still useful for illustrating the bistability of the system).
-
-The temporal approach is particularly useful when investigating the effects of strain richness.
-In preliminary simulations using the [Bush et al 2017](https://www.nature.com/articles/s41467-017-00912-x) approach, we found the counterintuitive result that higher strain richness led to lower resilience.
-We then recalled that we chose to divide the initial total abundance of the cyanobacterial (CB) functional group equally among the strains (termed a substitutive design in biodiversity manipulation experiments).
-This meant that the most tolerant CB strain in a three-strain simulation had higher initial abundance than the same most tolerant CB strain in a nine-strain simulation.
-The greater abundance of the most CB tolerant strain made it possible for a three-strain system to develop to be oxic, whereas the nine-strain system developed to be anoxic, despite identical range of trait variation.
-We could have chosen to do otherwise, for example start with the least tolerant strains of cyanobacteria as more abundant when the system started with high cyanobacterial abundance, and the most tolerant strain as more abundant when the system starts with low cyanobacterial abundance.
-Using the temporal approach removed the need to specify initial abundances (except the very first one), and therefore results were not so determined by the assumptions used to determine the initial conditions.
-
-# Effect of simulation duration
-
-## Diversity effects
-
-Recall that the temporal method for finding stable states involves running the simulation for a certain amount of time, termed the "wait time", at a constant level of oxygen diffusivity.
-At the end of that wait time the state of the system is recorded, and then the oxygen diffusivity is slightly increased or decreased, and the system then simulated again for the duration of the wait time.
-
-The following figures \@ref(fig:div-temp-meth1)-\@ref(fig:div-temp-meth5) show the effects of diversity with long to shorter wait times.
-
-(ref:div-temp-meth1) Effects of diversity with wait time of 1e6 hours (same figure as in main report). (All else as in (Figure \@ref(fig:div-repl-meth1)).
-
-```{r div-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth1)', fig.height=7, fig.width=6, fig.align="center"}
-all_stab <- readRDS(here("data",
-                         microxanox_version_path,
-                         "temporal_method",
-                         "event_definition_2",
-                         "processed_data",
-                         "all_stab_data.RDS"))
-
-wait_time <- 1e6
-num_strains <- 9
-plot_here <- all_stab %>%
-  filter(waittime == wait_time)
-p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
-                                     which_strain = num_strains,
-                                     figure_title = paste0(wait_time,
-                                                           " wait time,\n",
-                                                           num_strains,
-                                                           " strains"))
-p2 <- fig_resilience_vs_div(plot_here,
-                            which_strain = num_strains,
-                            figure_title = " ")
-p1 + p2
-
-```
-
-(ref:div-temp-meth2) Effects of diversity with wait time of 1e5 hours. (All else as in (Figure \@ref(fig:div-repl-meth1)).
-
-```{r div-temp-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth2)', fig.height=7, fig.width=6, fig.align="center"}
-
-wait_time <- 1e5
-num_strains <- 9
-plot_here <- all_stab %>%
-  filter(waittime == wait_time)
-p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
-                                     which_strain = num_strains,
-                                     figure_title = paste0(wait_time,
-                                                           " wait time,\n",
-                                                           num_strains,
-                                                           " strains"))
-p2 <- fig_resilience_vs_div(plot_here,
-                            which_strain = num_strains,
-                            figure_title = " ")
-p1 + p2
-```
-
-(ref:div-temp-meth3) Effects of diversity with wait time of 1e4 hours. (All else as in (Figure \@ref(fig:div-repl-meth1)).
-
-```{r div-temp-meth3, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth3)', fig.height=7, fig.width=6, fig.align="center"}
-
-wait_time <- 1e4
-num_strains <- 9
-plot_here <- all_stab %>%
-  filter(waittime == wait_time)
-p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
-                                     which_strain = num_strains,
-                                     figure_title = paste0(wait_time,
-                                                           " wait time,\n",
-                                                           num_strains,
-                                                           " strains"))
-p2 <- fig_resilience_vs_div(plot_here,
-                            which_strain = num_strains,
-                            figure_title = " ")
-p1 + p2
-```
-
-(ref:div-temp-meth4) Effects of diversity with wait time of 1e3 hours. (All else as in Figure \@ref(fig:div-repl-meth1)).
-
-```{r div-temp-meth4, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth4)', fig.height=7, fig.width=6, fig.align="center"}
-wait_time <- 1e3
-num_strains <- 9
-plot_here <- all_stab %>%
-  filter(waittime == wait_time)
-p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
-                                     which_strain = num_strains,
-                                     figure_title = paste0(wait_time,
-                                                           " wait time,\n",
-                                                           num_strains,
-                                                           " strains"))
-p2 <- fig_resilience_vs_div(plot_here,
-                            which_strain = num_strains,
-                            figure_title = " ")
-p1 + p2
-```
-
-(ref:div-temp-meth5) Effects of diversity with wait time of 1e2 hours. (All else as in Figure \@ref(fig:div-repl-meth1)).
-
-```{r div-temp-meth5, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth5)', fig.height=7, fig.width=6, fig.align="center"}
-
-wait_time <- 1e2
-num_strains <- 9
-plot_here <- all_stab %>%
-  filter(waittime == wait_time)
-p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
-                                     which_strain = num_strains,
-                                     figure_title = paste0(wait_time,
-                                                           " wait time,\n",
-                                                           num_strains,
-                                                           " strains"))
-p2 <- fig_resilience_vs_div(plot_here,
-                            which_strain = num_strains,
-                            figure_title = " ")
-p1 + p2
-```
-
-## Example of transient dynamics at 1e6 hours
-
-The results below show the stable states as a function of oxygen diffusivity for a system with an intermediate level of diversity in all functional groups, with either 1'000'000 hours at each oxygen diffusivity level (Figure \@ref(fig:ss-temp-meth3)), or 2'000'000 hours (Figure \@ref(fig:ss-temp-meth4)).
-This shows that 1'000'000 hours duration of the simulations are sufficient to reach stable state, except very close to state transitions on the trajectory of recovery (i.e.: cyanobacteria: trajectory of increasing oxygen diffusivity; sulfate-reducing bacteria: trajectory of decreasing oxygen diffusivity).
-Very close to these transitions, even at 2'000'000 hours, the dynamics are still transient, with high tolerance strains at high density, even though they will eventually be outcompeted by low tolerance (higher growth rate) strains.
-
-(ref:ss-temp-meth3) Stable states found with the temporal method with duration at each oxygen diffusivity value of **1e6 hours**.
-The left column of panels refers to the stable state when oxygen diffusivity is at first high (favouring the oxic state).
-The right column refers to when oxygen diffusivity is at first low (favouring the anoxic state).
-Points (which sometimes are so close as to appear as thick lines) show the stable state at the end of each period of constant oxygen diffusivity.
-Thin lines are for visualisation only, and join the points.
-Grey arrows show the oxygen diffusivity at which the system flips, and the direction of the flip.
-The length of the grey arrows is without meaning.
-
-```{r ss-temp-meth3, eval = TRUE, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth3)', fig.height=10, fig.width=8, fig.align="center"}
-
-temp_meth <- readRDS(here("data",
-                          microxanox_version_path,
-                          "temporal_method",
-                          "event_definition_2",
-                          "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
-
-## data made with the "run_single_sim.R" file in the ss_find, temporal method folder.
-
-single_1e6 <- readRDS(here("data",
-                           microxanox_version_path, 
-                           "temporal_method",
-                           "single_sims",
-                           "single_1e6_result.RDS"))
-temp_meth[1,]$ssfind_result[[1]] <- single_1e6
-fig_state_vs_o2diff_sidebyside_alternative(temp_meth[1,])
-```
-
-(ref:ss-temp-meth4) Stable states found with the temporal method with duration at each oxygen diffusivity value of **2e6 hours**. All other aspects are as in Figure \@ref(fig:ss-temp-meth3).
-
-```{r ss-temp-meth4, eval = TRUE, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth4)', fig.height=10, fig.width=8, fig.align="center"}
-single_2e6 <- readRDS(here("data",
-                           microxanox_version_path, 
-                           "temporal_method",
-                           "single_sims",
-                           "single_2e6_result.RDS"))
-temp_meth[1,]$ssfind_result[[1]] <- single_2e6
-fig_state_vs_o2diff_sidebyside_alternative(temp_meth[1,])
-```
-
-# SB diversity effects
-
-## SB diversity effect on the anoxic to oxic transition
-
-We showed above that wait times of 1e5 (Figure \@ref(fig:div-temp-meth2)) and 1e4 (Figure \@ref(fig:div-temp-meth4)) produce qualitatively and often quantitatively very similar results to those for wait times of 1e6 (Figure \@ref(fig:div-temp-meth1)).
-There is, however, a notable difference when there is variation in only SB, or in CB-SB with wait times of 1e4 (Figure \@ref(fig:div-temp-meth4)).
-Here, moderate increases in diversity have the same effect as with wait times of 1e6.
-However, larger increases in diversity suddenly cause a large reduction in resilience of the anoxic-oxic transition.
-Figure \@ref(fig:ss-temp-meth1) gives an example of the stable states when diversity is moderate -- increases in oxygen diffusivity cause strain replacement in the SB to the more tolerant strains, which then delay the shift to the oxic state.
-Suprisingly, when there is just a little more diversity in the SB, then the anoxic to oxic transition happens earlier, i.e.
-there is a large decrease in resilience (Figure \@ref(fig:ss-temp-meth2)).
-
-(ref:ss-temp-meth1) Stable state of the system with **moderate** level of diversity in only SB, and no diversity in the other two groups. All other aspects are as in Figure \@ref(fig:ss-temp-meth3).
-
-```{r ss-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth1)', fig.height=10, fig.width=8, fig.align="center"}
-wait_time <- "1e+04"
-ss_9s <- readRDS(here::here("data",
-                            microxanox_version_path, 
-                            "temporal_method",
-                            "event_definition_2",
-                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
-#stab_9s <- readRDS(here::here(\"data", "0_ss_finding", "temporal_method", microxanox_version_path, paste0("stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS"))
-
-#max <- max(ss_3s$PB_var_gmax_s)
-#f <- 0.625
-#fv <- f*max
-
-only_SB_variable <- ss_9s %>%
-  filter(
-    abs(CB_var_gmax_s) < 0.0001,
-    abs(PB_var_gmax_s) < 0.0001
-  )
-only_SB_variable <- only_SB_variable[order(only_SB_variable$SB_var_gmax_s), ]
-
-#only_SB_variable$SB_var_gmax_s
-
-fig_state_vs_o2diff_sidebyside_alternative(only_SB_variable[14,])
-
-#fig_state_vs_o2diff(only_SB_variable[13,])
-```
-
-(ref:ss-temp-meth2)  Stable state of the system with **higher than moderate** level of diversity in only SB, and no diversity in the other two groups.
-All other aspects are as in Figure \@ref(fig:ss-temp-meth1).
-
-```{r ss-temp-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth2)', fig.height=10, fig.width=8, fig.align="center"}
-fig_state_vs_o2diff_sidebyside_alternative(only_SB_variable[15,])
-```
-
-We believe that this phenomenon is caused by an effect that we explain with reference to an analogy of using stepping stones to cross a river.
-Increasing diversity in our simulations is akin to increasing the width of the river, but keeping the number of stepping stones (strains) constant.
-So long as the river is not too wide, we can still cross it, but once the width of the river is such that the stepping stones are too far apart, we can't cross the river.
-And this happens suddenly, the width increases just a tiny bit more, and we suddenly can't cross the river when we could before.
-
-In the simulated microbial ecosystem, the strains are the stepping stones, and it is harder (takes longer) for strains to replace each other when there is greater distance (in trait space) between them.
-When they can no longer replace each other in the time available, the system behaves as if only the least tolerant, highest growth rate strain (lightest shade of colour) is present.
-In the case illustrated above, this leads to much lower resilience of the anoxic system state.
-
-This phenomenon is dependent on having static trait values for the strains.
-If strain traits were dynamic (e.g.
-due to evolution), then we expect this result to not occur, and rather for the effects of diversity with two or three strains to be the same as those with six or nine.
-
-## SB diversity effect on the oxic to anoxic transition {#SB2}
-
-When the environment ameliorates for the sulfate-reducing bacteria (i.e.
-trajectory of decreasing oxygen diffusivity), there is only limited evidence of strain replacement (in final state) along the oxygen diffusivity gradient -- either the system is oxic or the least tolerant strain dominates.
-And yet the switch to anoxic state occurs at higher oxygen diffusivity than when there is no diversity, which suggests there is some role of the more tolerant strains.
-We here show that the more tolerant strains do play a role, but only a transient one.
-The following dynamics are for the system starting oxic, and with a value of oxygen diffusivity (log10(oxygen diffusivity) = -4.8).
-When there is no diversity within functional groups (i.e.
-two strains that are identical) the system remains oxic (Figure \@ref(fig:sb-div-effect3)).
-When there is diversity (i.e.
-the two strains differ) then the system switches to the anoxic state (Figure \@ref(fig:sb-div-effect4)).
-In these examples there is only diversity in the two groups of sulfur bacteria.
-The most tolerant strain does at first grow, but is then outcompeted by less tolerant strains as the concentration of the inhibiting substrate (oxygen) declines.
-
-```{r echo = FALSE}
-run_sims_this_section <- TRUE
-```
-
-```{r eval = run_sims_this_section, echo = FALSE}
-var_expt_levels <- var_expt[,1:6]
-no_diversity <- which(rowSums(abs(var_expt_levels))==0)
-max_diversty_all <- which(max(rowSums(abs(var_expt_levels))) ==
-                            rowSums(abs(var_expt_levels)))
-max_only_CB_diversity <- which(max(rowSums(abs(var_expt_levels[,1:2]))) ==
-                            rowSums(abs(var_expt_levels[,1:2])) &
-                              rowSums(abs(var_expt_levels[,3:6]))==0)
-max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
-                            rowSums(abs(var_expt_levels[,3:6])) &
-                              rowSums(abs(var_expt_levels[,1:2]))==0)
-```
-
-```{r  eval = run_sims_this_section, echo = FALSE}
-
-num_CB_strains <- 9
-num_SB_strains <- 9
-num_PB_strains <- 9
-
-sp <- new_strain_parameter(
-  n_CB = num_CB_strains,
-  n_PB = num_SB_strains,
-  n_SB = num_PB_strains,
-  values_initial_state = "bush_ssfig3"
-)
-
-parameter <- new_runsim_parameter(
-  dynamic_model = bushplus_dynamic_model,
-  event_definition = event_definition_1,
-  event_interval = 100,
-  noise_sigma = 0,
-  minimum_abundances = rep(1, 3),
-  sim_duration = 2000,
-  sim_sample_interval = 100,
-  strain_parameter = sp,
-  log10a_series = c(
-    log10(sp$a_O),
-    log10(sp$a_O)
-  )
-)
-names(parameter$minimum_abundances) <- c("CB", "PB", "SB")
-
-rm(sp)
-
-parameter$strain_parameter <- var_expt[no_diversity,]$pars[[1]]
-parameter$sim_duration <- 100000
-parameter$result <- NULL
-parameter$log10a_series <- c(-4.8, -4.8)
-parameter$strain_parameter$initial_state <- new_initial_state(
-  nrow(parameter$strain_parameter$CB),
-  nrow(parameter$strain_parameter$PB),
-  nrow(parameter$strain_parameter$PB),
-  values = "bush_ssfig3"
-)
-parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/nrow(parameter$strain_parameter$CB)
-
-sim_res_novar1 <- run_simulation(parameter)
-
-saveRDS(sim_res_novar1, here("data",
-                             microxanox_version_path,
-                             "temporal_method",
-                             "puzzles",
-                             "puzzle1_1.RDS"))
-```
-
-(ref:sb-div-effect3)  Dynamics of the system **with no diversity** in any functional group, and log10(oxygen diffusivity) = -4.8.
-The system remains oxic when starting in the oxic state.
-Although two strains are shown in the legend, they have identical parameters, and so their dynamics are identical and only one is visible in the dynamics.
-
-```{r  sb-div-effect3, echo = FALSE,  include=TRUE, fig.cap='(ref:sb-div-effect3)', fig.height=8, fig.width=8, fig.align="center"}
-sim_res_novar1 <- readRDS(here("data",
-                             microxanox_version_path,
-                             "temporal_method",
-                             "puzzles",
-                             "puzzle1_1.RDS"))
-p <- plot_dynamics(sim_res_novar1)
-p[[1]] <- p[[1]] + 
-  xlab(NULL) + 
-  ylab(expression(log[10](density)~(cells~L^{-1}))) +
-  theme_bw()
-p[[2]] <- p[[2]] + 
-  xlab(NULL) + 
-  ylab(expression(log[10](density)~(cells~L^{-1}))) +
-  theme_bw()
-p[[3]] <- p[[3]] + 
-  xlab(NULL) + 
-  ylab(expression(log[10](density)~(cells~L^{-1}))) +
-  theme_bw()
-p[[4]]$data <- p[[4]]$data %>% 
-  dplyr::filter(species != "a")
-p[[4]]$data$species <- p[[4]]$data$species %>%
-  dplyr::recode(SO = "Oxidised sulfur", O = "Oxygen", SR = "Sulfide", P = "Phosphorus")
-p[[4]] <- p[[4]] + 
-  xlab("time (h)") + 
-  ylab(expression(log[10](concentration)~(µM))) + 
-  labs(colour = "substrate") +
-  theme_bw()
-
-p
-#ggsave(here("simulations", "expt2", "figures", "switching_novar.pdf"), width = 10)
-```
-
-```{r  eval = run_sims_this_section, echo = FALSE}
-parameter$strain_parameter <- var_expt[max_only_SBPB_diversity,]$pars[[1]]
-#parameter$sim_duration <- 100000
-#parameter$result <- NULL
-#parameter$log10a_series <- c(-5.2, -5.2)
-#parameter$strain_parameter$initial_state <- new_initial_state(
-#  nrow(parameter$strain_parameter$CB),
-#  nrow(parameter$strain_parameter$PB),
-#  nrow(parameter$strain_parameter$PB),
-#  values = "bush_ssfig3"
-#)
-parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/nrow(parameter$strain_parameter$CB)
-sim_res_highvar1 <- run_simulation(parameter)
-saveRDS(sim_res_highvar1,
-        here("data",
-             microxanox_version_path,
-             "temporal_method",
-             "puzzles",
-             "puzzle1_2.RDS"))
-```
-
-(ref:sb-div-effect4) Dynamics of the system **with diversity** in the two groups of sulfur bacteria and otherwise exactly the same conditions as in Figure \@ref(fig:sb-div-effect3).
-The system flips from oxic to anoxic, whereas it did not when there was no diversity.
-
-```{r sb-div-effect4, echo = FALSE,  include=TRUE, fig.cap='(ref:sb-div-effect4)', fig.height=8, fig.width=8, fig.align="center"}
-sim_res_highvar1 <- readRDS(here("data",
-             microxanox_version_path,
-             "temporal_method",
-             "puzzles",
-             "puzzle1_2.RDS"))
-
-p <- plot_dynamics(sim_res_highvar1)
-p[[1]] <- p[[1]] + 
-  xlab(NULL) + 
-  ylab(expression(log[10](density)~(cells~L^{-1}))) +
-  theme_bw()
-p[[2]] <- p[[2]] + 
-  xlab(NULL) + 
-  ylab(expression(log[10](density)~(cells~L^{-1}))) +
-  theme_bw()
-p[[3]] <- p[[3]] + 
-  xlab(NULL) + 
-  ylab(expression(log[10](density)~(cells~L^{-1}))) +
-  theme_bw()
-p[[4]]$data <- p[[4]]$data %>% dplyr::filter(species != "a")
-p[[4]]$data$species <- p[[4]]$data$species %>%
-  dplyr::recode(SO = "Oxidised sulfur", O = "Oxygen", SR = "Sulfide", P = "Phosphorus")
-p[[4]] <- p[[4]] +
-  xlab("time (h)") + 
-  ylab(expression(log[10](concentration)~(µM))) + 
-  labs(colour = "substrate") +
-  theme_bw()
-
-p
-
-#ggsave(here("simulations", "expt2", "figures", "switching_novar.pdf"), width = 10)
-```
-
-# PB diversity effects
-
-```{r echo = FALSE}
-ss_9s <- readRDS(here("data",
-                            microxanox_version_path,
-                            "temporal_method",
-                            "event_definition_2",
-                            "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
-only_PB_variable <- ss_9s %>%
-  filter(
-    abs(CB_var_gmax_s) < 0.0001,
-    abs(SB_var_gmax_s) < 0.0001
-  )
-only_PB_variable <- only_PB_variable[order(only_PB_variable$PB_var_gmax_s), ]
-
-only_PB_stab <- readRDS(here("data",
-                                   microxanox_version_path,
-                                   "temporal_method",
-                                   "event_definition_2",
-                                   "processed_data",
-                                   "all_stab_data.RDS")) %>%
-  filter(
-    num_strains == 9,
-    waittime == 1e6,
-    var_treat == "PB",
-    Species == "SB_tot"
-  )
-only_PB_stab <- only_PB_stab[order(only_PB_stab$PB_var_gmax_s), ]
-
-sim1 <- 2
-sim2 <- 10
-
-aO_flip_sim1 <- only_PB_stab[sim1,"hyst_max_log"]
-aO_flip_sim2 <- only_PB_stab[sim2,"hyst_max_log"]
-
-```
-
-Increases in the diversity within the PB functional group leads to lower resilience of the anoxic state (Figure \@ref(fig:div-temp-meth1), Panel PB, blue line).
-For example, a small amount of variation in only the PB functional group, and no variation in other functional groups, results in transition from anoxic to oxic at approximately $log_{10}$(oxygen diffusivity) = `r round(aO_flip_sim1, 2)` (Figure \@ref(fig:pbdiv-only-1)).
-Whereas a moderate amount of variation in only the PB functional group, and no variation in other functional groups, results in transition from anoxic to oxic at approximately $log_{10}$(oxygen diffusivity) = `r round(aO_flip_sim2, 2)` (Figure \@ref(fig:pbdiv-only-2)).
-
-(ref:pbdiv-only-1) Right-hand panels show the transition from anoxic to oxic state when oxygen diffusivity decreases.
-The results here are for a **low amount of variation in only the PB functional group**.
-The transition from anoxic to oxic occurs at approximately $log_{10}$(oxygen diffusivity) = `r round(aO_flip_sim1, 2)`.
-All other aspects are the same as in Figure \@ref(fig:repl-meth2).
-
-```{r pbdiv-only-1, echo = FALSE,  include=TRUE, fig.cap='(ref:pbdiv-only-1)', fig.height=10, fig.width=8, fig.align="center"}
-fig_state_vs_o2diff_sidebyside_alternative(only_PB_variable[sim1,])
-```
-
-(ref:pbdiv-only-2) Right-hand panels show the transition from anoxic to oxic state when oxygen diffusivity decreases.
-The results here are for a **moderate amount of variation in only the PB functional group**.
-The transition from anoxic to oxic occurs at approximately $log_{10}$(oxygen diffusivity) = `r round(aO_flip_sim2, 2)`.
-All other aspects are the same as in Figure \@ref(fig:repl-meth2).
-
-```{r pbdiv-only-2, echo = FALSE,  include=TRUE, fig.cap='(ref:pbdiv-only-2)', fig.height=10, fig.width=8, fig.align="center"}
-fig_state_vs_o2diff_sidebyside_alternative(only_PB_variable[sim2,])
-```
-
-This result is different to the effect of diversity within the CB and SB functional groups, which both cause increases in resilience of the state that they dominate (Figure \@ref(fig:div-temp-meth1)).
-Why does diversity in the PB functional group reduce the resilience of the state it dominates?
-
-The counter-intuitive effect of diversity in the phototrophic sulfur bacteria (PB) possibly results from their positive effects on conditions and processes that favour the oxic state.
-The phototrophic sulfur bacteria oxidise reduced sulfur to oxidised sulfur.
-Since reduced sulfur inhibits the cyanobacteria (CB), PB can have a positive effect on CB via their consumption of reduced sulfur.
-Hence, high growth rates of PB will have a positive effect on CB, and therefore favour the oxic state.
-We would expect to see that higher diversity of PB is associated with lower concentrations of reduced sulfur and higher concentrations of oxidised sulfur before the transition.
-
-Another pathway by which a higher growth rate of PB can favour the oxic state is by indirectly increasing the concentration of oxygen, thus inhibiting themselves and sulfate-reducing bacteria.
-This effect occurs because PB consume reduced sulfur, such that less reduced sulfur is available for abiotic oxidation.
-Consequently, a larger amount of oxygen remains in the environment and inhibits sulfur bacteria.
-We would expect to see that higher diversity of PB is associated with higher concentrations of oxygen before the transition.
-
-Among these two pathways, effects of phototrophic sulfur bacteria via abiotic oxidation of sulfide are probably of subordinate importance in natural environments because abiotic oxidation rates of sulfide are very small compared to biotic oxidation rates ([Luther et al 2011]( https://doi.org/10.3389/fmicb.2011.00062)).
-
-There is, however, at least one pathway by which PB can favour the anoxic state: PB produce oxidised sulfur which is consumed by SB, and SB produce reduced sulfur, which inhibits CB.
-
-Looking at the strain replacement that occurs across the oxygen diffusivity gradient, we see that as oxygen diffusivity increases, the more oxygen tolerant strains of PB replace the less tolerant ones because they have higher realised growth rates under the prevailing environmental conditions.
-Greater PB diversity leads to the availability of strains with higher oxygen tolerance and thus even higher realised growth rates, which via the pathways described above, can favour the oxic state.
-
-Substrate concentrations close to the anoxic-oxic transition in simulations with low and high PB diversity, respectively, corroborate the expected effects (Figure \@ref(fig:pbdiv-only-3)).
-As the transition is approached, higher PB diversity leads to higher concentration of oxygen, higher concentration of oxidised sulfur (SO), and lower concentration of reduced sulfur (SR), than a simulation with lower PB diversity.
-All these differences in substrate concentrations are in the direction of favouring the oxic state, resulting in the earlier transition to the oxic state.
-
-(ref:pbdiv-only-3) Concentrations of three substrates (O: oxygen; SO: oxidised sulfur; SR: reduced sulfur) in a low PB diversity simulation (x-axis) versus substrate concentration in a high PB diversity simulation (y-axis).
-The figures show only a small range of oxygen diffusivity on the trajectory of increasing oxygen diffusivity.
-The black line is the 1:1 line.
-
-```{r pbdiv-only-3, echo = FALSE,  include=TRUE, fig.cap='(ref:pbdiv-only-3)', fig.height=5, fig.width=8, fig.align="center"}
-
-stab_9s <- readRDS(here("data", 
-                        microxanox_version_path,
-                        "temporal_method", 
-                        "event_definition_2",
-                        "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
-
-ss1 <- only_PB_variable[sim1,]
-ss2 <- only_PB_variable[sim2,]
-
-dd1 <- ss1$ssfind_result[[1]] %>%
-  pivot_longer(names_to = "State_variable", values_to = "Quantity_sim1", 2:32)
-dd2 <- ss2$ssfind_result[[1]] %>%
-  pivot_longer(names_to = "State_variable", values_to = "Quantity_sim2", 2:32)
-dd <- full_join(dd1, dd2)
-rm(ss1, ss2, dd1, dd2)
-
-labs <- seq(-3.5, -3.3, by=0.05)
-
-dd$State_variable <- dd$State_variable %>%
-  dplyr::recode(SO = "Oxidised sulfur", O = "Oxygen", SR = "Sulfide", P = "Phosphorus")
-
-dd %>%
-  filter(State_variable %in% c("Oxygen", "Sulfide", "Oxidised sulfur"),
-         direction == "up",
-         a_O < as.numeric(aO_flip_sim2),
-         a_O > -3.5) %>%
-  ggplot(aes(x = log10(Quantity_sim1),
-                 y = log10(Quantity_sim2),
-                 col = a_O )) +
-  geom_point(lwd = 3) +
-  geom_path() +
-  scale_color_gradient(low = "yellow", high = "red", na.value = NA,
-                       breaks = labs,
-                       labels = labs) +
-  #coord_trans(x = "log10", y = "log10") +
-  facet_wrap( ~ State_variable, scales = "free") +
-  geom_abline(intercept = 0, slope = 1) +
-  xlab(expression(atop(log[10](concentration)~(µM), Low~PB~diversity))) +
-  ylab(expression(atop(log[10](concentration)~(µM),High~PB~diversity))) +
-  labs(col=expression(paste("log"[10],"(oxygen diffusivity) (h"^{-1}, ")"))) +
-  theme_bw() +
-  theme(legend.position="top")
-```
-
-# Effect of number of strains
-
-In the main text, we present results of simulations with nine strains per functional group.
-Here we also explore the effect of number of strains (2, 3, 6, 9) on the position of the two tipping points (Figure \@ref(fig:div-stab-multstrain1)).
-At low to moderate amounts of trait variation, the number of strains did not affect the position of the tipping points.
-However, at high amounts of trait variation, resilience was lower when the functional groups had only two or three strains rather than six or nine.
-This effect was particularly pronounced when there was high variation in only SB or in SB-CB: here, simulations with two or three strains led to dramatically lower resilience of the anoxic state than simulations with six or nine strains.
-We believe that this effect is due to the greater distance in trait space between strains in simulations with two or three strains than in simulations with more strains (also see Section 5).
-
-(ref:div-stab-multstrain1)  Effects of number of strains and of diversity among strains.
-
-```{r div-stab-multstrain1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-stab-multstrain1)', fig.height=8, fig.width=8, fig.align="center"}
-all_stab <- readRDS(here("data",
-                         microxanox_version_path,
-                         "temporal_method", 
-                         "event_definition_2",
-                         "processed_data", "all_stab_data.RDS"))
-which_strains <- c(2, 3, 6, 9)
-which_wait_time<- 1e6
-figure_title <- " "
-
-fig_div_vs_o2diff_multistrain(all_stab, which_strains,
-                              which_wait_time, figure_title)
-```
-
-# Underlying mechanisms
-
-In the main text we show that trait variation can affect resilience.
-In this supplementary section, we discuss the mechanism(s) underlying the observed diversity effects.
-We first explain the two major classes of mechanisms known to drive diversity effects, and then use additional simulations to elucidate the mechanisms operating in our study.
-
-## Complementarity and sampling effect
-
-Research about the relationship between biodiversity and ecosystem functioning has identified two major mechanisms by which diversity affects ecosystem functioning: the selection/sampling effect and the complementarity effect (Loreau & Hector 2001).
-The sampling effect occurs when more diverse communities have higher functioning because they have a higher probability of containing the best-performing species, i.e.
-the diversity effect is driven by only one (or few) species (Cardinale et al.
-2011).
-In contrast, the complementarity effect occurs when higher ecosystem functioning in more diverse communities is due to niche differences or positive interactions among species, i.e.
-the diversity effect is driven by many species (Cardinale et al.
-2011).
-Both effects are considered valid and important mechanisms by which diversity affects ecosystem functioning (Cardinale et al.
-2006, 2011, 2012; Fargione et al.
-2007).
-
-Similarly, the complementarity effect and the sampling effect are important mechanisms by which diversity affects stability (Loreau & Mazancourt 2013; Loreau et al.
-2021) and resilience (Steiner et al.
-2006; Hughes & Stachowicz 2011).
-For example, diversity can stabilize aggregate ecosystem properties (e.g.
-community biomass) when species differ in their responses to environmental factors and therefore respond asynchronously to environmental fluctuations (temporal complementarity effect; Loreau & Mazancourt 2013).
-However, when considering ecosystem responses to directional environmental change or pulse disturbances rather than to environmental fluctuations, the sampling effect might be of particular importance (Steiner et al.
-2006): more diverse systems might absorb a greater amount of change by having a higher chance of containing species with high environmental tolerance.
-In this scenario, the positive diversity effect on resilience is driven by one (or few) species.
-From a conservation perspective, however, one would nevertheless strive to maintain diversity and not only the most tolerant species because of the uncertainties associated with environmental change: we do not know with sufficient certainty which stressors will change in a given ecosystem and which traits will therefore be relevant in the future.
-
-(ref:samp-effect1) A simple phenomenological model of the effect of number of strains in an ecosystem on the resilience of that ecosystem, when the resilience of a ecosystem is linearly proportional to the maximum trait value of the strains present in that ecosystem.
-Each data point is a different ecosystem, with the strains in each ecosystem drawn at random from a pool of 20 strains.
-Each of the 20 strains was assigned a trait value drawn at random from a uniform distribution with minimum 0 and maximum 1.
-The blue line is the fit of a generalised additive model and the grey ribbon shows the 1 standard error confidence range.
-
-```{r samp-effect1, echo = FALSE,  include=TRUE, fig.cap='(ref:samp-effect1)', fig.height=5, fig.width=6, fig.align="center"}
-if(!("tidyverse" %in% .packages()))
-  library(tidyverse)
-set.seed(12345)
-number_of_species <- 20
-species_trait <- tibble(species_name = paste0("Species-", letters[1:20]),
-                        trait_value = runif(number_of_species))
-
-richness_levels <- seq(1, 10, 1)
-compositions_per_richness_level <- 10
-expt <- crossing(richness = richness_levels,
-                 composition = paste0("Comp-", 1:compositions_per_richness_level)) %>%
-  mutate(composition = paste0(composition, "-", richness),
-         resilience_max_trait = NA)
-
-for(i in 1:nrow(expt))
-  expt$resilience_max_trait[i] = max(sample(species_trait$trait_value, expt$richness[i]))
-
-ggplot(expt, aes(x = richness, y = resilience_max_trait)) +
-  geom_point() +
-  xlab("Number of strains") +
-  ylab("Resilience if only the tolerance of\nthe most tolerant strain determines resilience.") +
-  geom_smooth(method = "gam")
-
-```
-
-## Do the observed diversity effects operate via the sampling effect?
-
-We investigated if the diversity effects observed in our study were in line with the sampling effect, that is, driven entirely by the presence of the most tolerant strain.
-Specifically, we ran additional simulations where functional groups contained only the strain with greatest tolerance and lowest maximum growth rate.
-That is, for each of the 20 levels of trait variation, we made simulations where each functional group had only one strain, and its trait values corresponded with those of the most tolerant strain for the given level of trait variation.
-We also manipulated in which of the functional groups tolerance increased.
-For example, in a simulation to be compared with variation in only the SB group (and no variation in the CB or PB groups), the SB group contained the strain with highest tolerance, whereas CB and PB each contained the strain with mean tolerance.
-We then compared the tipping point positions resulting from this tolerance manipulation with the tipping point positions resulting from the diversity manipulation presented in the main text.
-If the observed diversity effects are caused by the sampling effect, we expect there to be no difference between the tolerance manipulation and the diversity manipulation.
-
-To exclude that differences between the tolerance manipulation and the diversity manipulation were driven by the difference in number of strains, we also performed simulations in which we retained nine strains in each functional group but set the tolerance of all nine strains to the maximum tolerance value.
-Results were the same as those presented below from simulations with one strain.
-
-For most of the explored combinations and amounts of functional diversity/tolerance the tipping point positions did not differ between the diversity manipulation and the tolerance manipulation (Figure \@ref(fig:max-tol1)).
-However, in some cases there were effects, three of which are described in the follow sections.
-
-(ref:max-tol1) Effects of strain variation on position of tipping points compared between simulations with all (nine) strains present and simulations where only the most tolerant strain is present.
-
-```{r max-tol1, echo = FALSE,  include=TRUE, fig.cap='(ref:max-tol1)', fig.height=8, fig.width=8, fig.align="center"}
-#all_stab <- readRDS(here("data", "0_ss_finding", "temporal_method", "processed_data", "stab_data_temporal_method_ELErevision1.2.RDS"))
-
-## read the data
-all_stab <- readRDS(here("data",
-                         microxanox_version_path,
-                         "temporal_method", 
-                         "event_definition_2",
-                         "processed_data",
-                         "all_stab_data.RDS"))
-
-which_strains <- c(-1, 9)
-which_wait_time <- 1e6
-figure_title <- " "
-
-## remove data where there are no stable states
-## this subset is identified by inspection of the figure
-#all_stab <- all_stab %>%
-#  filter(!(var_treat == "CB-SB" & stand_var > 0.84 & num_strains == -1))
-
-plot_1 <- fig_div_vs_o2diff_maxtolcomp(all_stab, which_strains,
-                              which_wait_time, figure_title)
-plot_1 +
-  xlab("Standardised amount of trait variation used to create nine strains\nof which either all nine are retained, or only the most tolerant is retained.") +
-  guides(col=guide_legend(title="Which strains are retained", title.position = "top"))
-```
-
-```{r echo = FALSE}
-nine_strains <- readRDS(here("data",
-                         microxanox_version_path,
-                         "temporal_method", 
-                         "event_definition_2",
-                          "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
-maxtolonly_strains <- readRDS(here("data",
-                         microxanox_version_path,
-                         "temporal_method", 
-                         "event_definition_2",
-                          "ss_data_-1strains_waittime1e+06_event_definition_2.RDS"))
-
-#nine_strains$parameter[[1]]$strain_parameter
-#maxtolonly_strains[134,]$parameter[[1]]$strain_parameter
-```
-
-## High tolerance vs. high diversity in only the SB
-
-When SB contained multiple strains varying in growth rate (and tolerance) there were only two stable states (Figure \@ref(fig:max-tol2)), as was previously reported.
-When, however, only one SB strain with very high tolerance and low maximum growth rate was present, there three stable states: the two previously found, and another where all three functional groups coexisted (Figure \@ref(fig:max-tol3)) – this never occurred when there were multiple strains varying in tolerance.
-
-Apparently, at low oxygen diffusivity levels, the absence of SB strains with high growth rate precludes the formation of a stable state that does not include cyanobacteria.
-It seems that the most tolerant SB strain does not have a high enough growth rate to itself exclude the cyanobacteria.
-Cyanobacteria are therefore always present, regardless of the oxygen diffusivity.
-We do not have an explanation of why the cyanobacteria are, however, excluded at intermediate oxygen diffusivities.
-
-(ref:max-tol2) Stable states found when there is variation among nine strains of SB and the amount of variation is high. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
-
-```{r max-tol2, echo = FALSE,  include=TRUE, fig.cap='(ref:max-tol2)', fig.height=10, fig.width=8, fig.align="center"}
-## max SB_var_gmax_s is 0.09473684
-nine_strain_one <- filter(nine_strains,
-       CB_var_gmax_s == 0,
-       abs(SB_var_gmax_s - 0.09473684) < 0.001,
-       PB_var_gmax_s == 0)
-ss_result <- nine_strain_one
-fig_state_vs_o2diff_sidebyside_alternative_leftfliponly(nine_strain_one)
-```
-
-(ref:max-tol3) Stable states found when SB contained only the most tolerant strain, with trait values corresponding with the diversity level of the previous figure.
-All other aspects are the same as in Figure \@ref(fig:repl-meth2).
-
-```{r max-tol3, echo = FALSE,  include=TRUE, fig.cap='(ref:max-tol3)', fig.height=10, fig.width=8, fig.align="center"}
-max_tol_one <- filter(maxtolonly_strains,
-       CB_var_gmax_s == 0,
-       abs(SB_var_gmax_s - 0.09473684) < 0.001,
-       PB_var_gmax_s == 0)
-fig_state_vs_o2diff_sidebyside_alternative(max_tol_one)
-```
-
-In the ecosystem shown in Figure \@ref(fig:max-tol3), where the SB contained one strain with very high tolerance, there was large variation in state variables along the oxygen diffusivity gradient at values less than about -4.5.
-To examine what might be causing this, we simulated the ecosystem at a constant oxygen diffusivity of $log_{10}$ oxygen diffusivity of -6 (Figure \@ref(fig:SB-maxtol-dyn1)).
-We see that the dynamics are qualitatively different from other cases in which there is a stable state reached in such a simulation (Figure \@ref(fig:sb-div-effect4)).
-It appears that the high tolerance SB strain is able to initiate a transition to an anoxic state, but is not able to create a stable anoxic state.
-This dynamical situation was not present in the ecosystem in which high tolerance and low tolerance strains were present.
-
-```{r echo = FALSE}
-#nine_strain_one$pars[[1]]
-#max_tol_one$pars[[1]]
-#fig_state_vs_o2diff_sidebyside_alternative(nine_strain_one)
-#fig_state_vs_o2diff_sidebyside_alternative(max_tol_one)
-parameter <- max_tol_one$parameter[[1]]
-parameter$strain_parameter <- max_tol_one$pars[[1]]
-#parameter$strain_parameter <- ss_result$pars[[1]]
-total_initial_abundances <- 10^5
-parameter <- set_temporal_ssfind_initial_state(parameter,
-                                               total_initial_abundances,
-                                               total_initial_abundances,
-                                               total_initial_abundances)
-parameter$log10a_series <- c(-6, -6)
-wait_time <-  1e5
-parameter$sim_duration <- wait_time * length(parameter$log10a_series)
-parameter$sim_sample_interval <- 10
-#parameter$sim_duration
-test1 <- run_simulation(parameter)
-```
-
-(ref:SB-maxtol-dyn1) Temporal dynamics of an ecosystem with a single SB strain with high tolerance, the same one as in Figure \@ref(fig:max-tol3) simulated with constant $log_{10}$ oxygen diffusivity of -6.
-
-```{r SB-maxtol-dyn1, echo = FALSE,  include=TRUE, fig.cap='(ref:SB-maxtol-dyn1)', fig.height=10, fig.width=8, fig.align="center"}
-p <- plot_dynamics(test1)
-p[[1]] <- p[[1]] + 
-  xlab(NULL) + 
-  ylab(expression(log[10](density)~(cells~L^{-1}))) +
-  theme_bw()
-p[[2]] <- p[[2]] + 
-  xlab(NULL) + 
-  ylab(expression(log[10](density)~(cells~L^{-1}))) +
-  theme_bw()
-p[[3]] <- p[[3]] + 
-  xlab(NULL) + 
-  ylab(expression(log[10](density)~(cells~L^{-1}))) +
-  theme_bw()
-p[[4]]$data <- p[[4]]$data %>% 
-  dplyr::filter(species != "a")
-p[[4]]$data$species <- p[[4]]$data$species %>%
-  dplyr::recode(SO = "Oxidised sulfur", O = "Oxygen", SR = "Sulfide", P = "Phosphorus")
-p[[4]] <- p[[4]] + 
-  xlab("time (h)") + 
-  ylab(expression(log[10](concentration)~(µM))) + 
-  labs(colour = "substrate") +
-  theme_bw()
-
-p
-```
-
-## High tolerance vs. high diversity in CB-SB
-
-In the SB-SB case, presence of only the high tolerance strain could cause the system to not display any alternate stable states (Figure \@ref(fig:max-tol5)).
-
-(ref:max-tol5)  Stable states found when CB and SB each contain only the single most tolerant strain with trait values corresponding with the diversity level of the previous figure.
-All other aspects are the same as in Figure \@ref(fig:repl-meth2).
-
-```{r max-tol5, echo = FALSE,  include=TRUE, fig.cap='(ref:max-tol5)', fig.height=10, fig.width=8, fig.align="center"}
-max_tol_one_CBSB <- filter(maxtolonly_strains,
-       abs(CB_var_gmax_s - 0.026592798) < 0.001,
-       abs(SB_var_gmax_s - 0.079778395) < 0.001,
-       PB_var_gmax_s == 0)
-max_tol_one_CBSB <- filter(maxtolonly_strains,
-       abs(CB_var_gmax_s - 0.028254848) < 0.001,
-       abs(SB_var_gmax_s - 0.084764545) < 0.001,
-       PB_var_gmax_s == 0)
-
-fig_state_vs_o2diff_sidebyside_alternative(max_tol_one_CBSB)
-```
-
-## High tolerance vs. high diversity in CB-SB-PB
-
-When in each of the three functional groups only the most tolerant strain is present, the resilience of the oxic state is greater than when there is variation in strain tolerance within groups.
-It is not entirely clear why this effect only occurs only in this combination.
-
-(ref:max-tol6) Stable states found with nine strains of CB-SB-PB and high diversity. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
-
-```{r max-tol6, echo = FALSE,  include=TRUE, fig.cap='(ref:max-tol6)', fig.height=10, fig.width=8, fig.align="center"}
-filter(nine_strains,
-       abs(CB_var_gmax_s - 0.026592798) < 0.001,
-       abs(SB_var_gmax_s - 0.079778395) < 0.001,
-       abs(PB_var_gmax_s - 0.079778395) < 0.001) %>%
-  fig_state_vs_o2diff_sidebyside_alternative()
-
-```
-
-(ref:max-tol7) Stable states found with the single most tolerant CB strain, SB strain, and PB strain, with trait values corresponding with the diversity level in the previous figure.
-All other aspects are the same as in Figure \@ref(fig:repl-meth2).
-
-```{r max-tol7, echo = FALSE,  include=TRUE, fig.cap='(ref:max-tol7)', fig.height=10, fig.width=8, fig.align="center"}
-filter(maxtolonly_strains,
-       abs(CB_var_gmax_s - 0.026592798) < 0.001,
-       abs(SB_var_gmax_s - 0.079778395) < 0.001,
-       abs(PB_var_gmax_s - 0.079778395) < 0.001) %>%
-  fig_state_vs_o2diff_sidebyside_alternative()
-```
-
-## Why only at high diversity/tolerance?
-
-Why do these effects only occur at high diversity/tolerance?
-The likely reason is that at high diversities the most tolerant strain has particularly low growth rate, and so it may have the tolerance required to increase and persist, but not the growth rate required to dominate.
-
-# Finding the separatrix
-
-In the original publication ([Bush et al 2017](<https://www.nature.com/articles/s41467-017-00912-x>)) Figure 3a shows a separatrix in the cyanobacteria abundance - oxygen diffusivity dimensions of the system.
-If the system has initial cyanobacterial abundance greater than the value at the separatrix then the cyanobacterial abundance increases, and the system goes to the oxic stable state.
-Conversely, if the system has initial cyanobacterial abundance lower than the value at the separatrix then the cyanobacterial abundance decreases, and the system goes to the anoxic stable state.
-
-It is critical to note, however, that the position of the separatrix depends on both the parameters of the system, and the initial conditions of variables other than cyanobacterial abundance.
-If the system were started with higher initial concentration, then the position of the separatrix would change (as would the values of oxygen diffusivity at which the system tipped from anoxic to oxic, and from oxic to anoxic).
-
-This issue of dependence of the position of the separatrix on the value of initial condition of multiple state variables has particular significance when there are multiple strains per functional group.
-Then one cannot just vary initial total cyanobacterial abundance (as was done to create the separatrix on Figure 3a in the original publication) but one must also define how the initial abundance of each of the strains varies.
-One might choose to make each strain have equal initial abundance, and to vary the total (as we did in our implementation of the replication method in the main article).
-
-We could, however, and arguably should, give the most tolerant strain of cyanobacteria higher initial relative abundance when total initial cyanobacterial abundance was low, and the least tolerant strain higher initial relative abundance when total cyanobacterial abundance was high.
-And we would need to specify the total and relative abundance of all cyanobacteria (and sulfur bactria) strains.
-Thus, with a system as complex as the 9 strain system, which has 31 state variables the separatrix is very high dimensional, and evaluating (and plotting) it in one dimension requires many assumptions.
-We chose to not attempt to find a meaningful set of assumptions in this study, though not because we think it would be unprofitable to do so, but rather because we did not want to risk distracting attention from findings we consider to be significant enough in their own right.
-
-# (Non-)additivity
-
-We investigated if the effects of trait variation of individual functional groups were additive.
-We compared the tipping point positions as determined by our simulations with the expected position of the respective tipping point if effects of diversity in different functional groups were additive.
-The expected tipping point was calculated by adding the effect sizes (i.e.
-the difference in tipping point position between the no-diversity scenario and a given amount of trait variation) on a linear scale.
-
-```{r fig-5-log, echo = FALSE,  include=TRUE, fig.cap='Previously figure 5 Main Manuscript log', fig.height=8, fig.width=8, fig.align="center"}
-## Figure 5 ----
-## Assessing additivity of diversity effect sizes
-## By Uriah
-## Owen switched to SB_tot
-
-all_stab_results_small <- readRDS(here("data",
-                         microxanox_version_path,
-                         "temporal_method", 
-                         "event_definition_2",
-                         "processed_data", "all_stab_data.RDS"))
-
-wait_time <- 1e6
-all_stab_results9 <- all_stab_results_small %>%
-  distinct() %>%  #there are some duplicated rows....? yes, some treatment combs were repeated when sub1 was made
-  filter(num_strains == 9,
-         Species == "SB_tot",
-         waittime == wait_time)
-
-all_stab_results9 <- all_stab_results9[with(all_stab_results9, order(var_treat, var_gmax)),]
-
-all_stab_results9$method <- "Simulated"
-
-### Things used for plotting ----
-
-### Fig 5 - log ----
-
-agg_stab_strain9 <- combine_fct("EF_log")
-
-agg_stab_strain9_temp <- agg_stab_strain9 %>%
-  dplyr::filter(var_treat=="CB-SB-PB")
-
-agg_stab_strain9 <- agg_stab_strain9 %>%
-  dplyr::filter(var_treat!="CB-SB-PB")
-
-agg_stab_strain9 <- rbind(agg_stab_strain9,
-                          agg_stab_strain9_temp %>% filter(method %in% c("CB+SBPB","Simulated")) %>% mutate(var_treat="CB-SB-PB & CB+SBPB"),
-                          agg_stab_strain9_temp %>% filter(method %in% c("PB+CBSB","Simulated")) %>% mutate(var_treat="CB-SB-PB & PB+CBSB"),
-                          agg_stab_strain9_temp %>% filter(method %in% c("SB+CBPB","Simulated")) %>% mutate(var_treat="CB-SB-PB & SB+CBPB"))
-
-agg_stab_strain9 <- agg_stab_strain9 %>%
-  mutate(method2 = ifelse(agg_stab_strain9$method=="Simulated","Simulated","Calculated")) %>%
-  rename(Calculation=method, Method=method2)%>%
-  mutate(Calculation = factor(Calculation, levels = c("Simulated","CB+SB","CB+PB","SB+PB",
-                                                      "CB+SBPB","PB+CBSB","SB+CBPB")),
-         Method = factor(Method, levels = c("Simulated","Calculated")))
-
-# the legend
-fig5legend <- agg_stab_strain9 %>%
-  filter(Species == "SB_tot", num_strains==9) %>%
-  ggplot(aes(x = stand_var, linetype=Method, col=Calculation)) +
-  geom_line(aes(y = hyst_min_log), size = 1) +
-  geom_line(aes(y = hyst_max_log), size = 1) +
-  scale_color_manual(values = c("black","#e41a1c","#377eb8","#4daf4a","#984ea3","#ff7f00","#a65628")) +
-  scale_linetype_manual(values = c(1,2))+
-  coord_flip() +
-  theme_bw() +
-  theme(legend.position="right")
-
-fig5legend <- ggpubr::get_legend(fig5legend)
-
-# the y and x labels
-# ylab <- ggplot(data.frame(l = "            Standardised amount of trait variation", x = 1, y = 4.1)) +
-ylab <- ggplot(data.frame(l = "Standardised amount of trait variation", x = 1, y = 4.1)) +
-  geom_text(aes(x, y, label = l), angle = 90, size=4.5) + 
-  theme_void() +
-  coord_cartesian(clip = "off")
-
-xlab <- ggplot(data.frame(x = 1, y = 1)) +
-  geom_text(aes(x, y), label = expression('log'[10]*"(oxygen diffusivity) (h"^{-1}*")"), size=4.5) + 
-  theme_void() +
-  coord_cartesian(clip = "off")
-
-# colours and tags used
-colours <- c(Simulated="black",`CB+SB`="#e41a1c",`CB+PB`="#377eb8",
-             `SB+PB`="#4daf4a",`CB+SBPB`="#984ea3",`PB+CBSB`="#ff7f00",
-             `SB+CBPB`="#a65628")
-
-tags <- c(`CB`="a",`SB`="b",`PB`="c",
-          `CB-SB`="d",`CB-PB`="e",`SB-PB`="f",
-          `CB-SB-PB & CB+SBPB`="g",`CB-SB-PB & PB+CBSB`="h",`CB-SB-PB & SB+CBPB`="i")
-
-# The figure
-
-fig5_log <- split(agg_stab_strain9, f=agg_stab_strain9$var_treat, drop = T)
-
-```
-
-(ref:fig-add-linear) Assessing the additivity or non-additivity of the effects of trait variation.
-Solid black lines depict the position of the two tipping points at different levels of trait variation, as simulated with the model.
-The colored, dashed lines show the expected position of tipping points if effects of diversity in different functional groups were additive.
-The expected tipping point was calculated by adding the effect sizes of trait variation of different functional groups on a linear scale.
-For example, in (d) the effect size of variation in only CB was added to the effect size of variation in only SB.
-In (g), the effect size of variation in only CB was added to the effect size of simultaneous variation in both SB and PB.
-(CB: cyanobacteria, SB: sulfate-reducing bacteria, PB: phototrophic sulfur bacteria).
-The dotted vertical lines at -8 and 0 on the x-axis show the extent of the oxygen diffusivity gradient investigated in the simulations.
-
-```{r fig-add-linear, echo = FALSE,  include=TRUE, fig.height=8, fig.width=8, fig.align="center", fig.cap='(ref:fig-add-linear)'}
-
-### Fig 5 - linear ----
-
-agg_stab_strain9 <- combine_fct("EF_lin")
-
-agg_stab_strain9_temp <- agg_stab_strain9 %>%
-  dplyr::filter(var_treat=="CB-SB-PB")
-
-agg_stab_strain9 <- agg_stab_strain9 %>%
-  dplyr::filter(var_treat!="CB-SB-PB")
-
-agg_stab_strain9 <- rbind(agg_stab_strain9,
-                          agg_stab_strain9_temp %>% filter(method %in% c("CB+SBPB","Simulated")) %>% mutate(var_treat="CB-SB-PB & CB+SBPB"),
-                          agg_stab_strain9_temp %>% filter(method %in% c("PB+CBSB","Simulated")) %>% mutate(var_treat="CB-SB-PB & PB+CBSB"),
-                          agg_stab_strain9_temp %>% filter(method %in% c("SB+CBPB","Simulated")) %>% mutate(var_treat="CB-SB-PB & SB+CBPB"))
-
-agg_stab_strain9 <- agg_stab_strain9 %>%
-  mutate(method2 = ifelse(agg_stab_strain9$method=="Simulated","Simulated","Calculated")) %>%
-  rename(Calculation=method, Method=method2)%>%
-  mutate(Calculation = factor(Calculation, levels = c("Simulated","CB+SB","CB+PB","SB+PB",
-                                                      "CB+SBPB","PB+CBSB","SB+CBPB")),
-         Method = factor(Method, levels = c("Simulated","Calculated")))
-
-fig5_lin <- split(agg_stab_strain9, f=agg_stab_strain9$var_treat, drop = T)
-
-fig5_lin <- lapply(fig5_lin, function(df){
-  tag <- tags[as.character(unique(df$var_treat))]
-  plot <- df %>%
-    filter(Species == "SB_tot", num_strains==9) %>%
-    ggplot(aes(x = stand_var, linetype=Method, col=Calculation)) +
-    geom_hline(yintercept = c(-8, 0), col = "black", linetype=3) +
-    geom_line(aes(y = hyst_min_log), size = 1) +
-    geom_line(aes(y = hyst_max_log), size = 1) +
-    facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
-    labs(y="Oxygen diffusivity\n[log10 uM per hour]",
-         x="Amount of trait variation\n[see text for units]",
-         linetype="Method",col="Calculation", tag=tag) +
-    scale_color_manual(values = colours[unique(df$Calculation)]) +
-    scale_linetype_manual(values = c(1,2))+
-    coord_flip() +
-    theme_bw()+
-    theme(legend.position="none",
-          axis.title = element_blank(),
-          axis.ticks = element_blank(),
-          axis.text = element_blank())
-
-  if(tag %in% c("a","d")){
-    plot <- plot + theme(axis.text.y = element_text(),
-                         axis.ticks.y = element_line())
-  }
-  if(tag %in% c("h","i")){
-    plot <- plot + theme(axis.text.x = element_text(),
-                         axis.ticks.x = element_line())
-  }
-  if(tag == "g"){
-    plot <- plot + theme(axis.text = element_text(),
-                         axis.ticks = element_line())
-  }
-  plot
-})
-
-ylab + Reduce("+",fig5_lin) + fig5legend +
-  plot_spacer() + xlab + plot_spacer() +
-  plot_layout(ncol = 3, heights = c(25,1), widths = c(1,21,3))
-
-# ggsave(here("experiments/1_figures_main_ms/Figure_5_lin.pdf"),
-#        width = 8, height = 8)
-```
-
-When two functional groups varied in traits, the effects of trait variation were additive when one of the groups had no diversity effect on a tipping point but non-additive when both groups had diversity effects on a tipping point (Fig.
-\@ref(fig:fig-add-linear) a-f).
-High trait variation in cyanobacteria and sulfate-reducing bacteria caused the oxic-anoxic tipping point to occur at lower oxygen diffusivity than expected assuming additivity of the individual effects of diversity in these two groups (Fig.
-\@ref(fig:fig-add-linear)d).
-When the two groups of sulfur bacteria varied in traits, the anoxic-oxic tipping point occurred at higher oxygen diffusivity than expected by additivity (Fig.
-\@ref(fig:fig-add-linear)f).
-
-When all three groups varied in traits, only the diversity effect in phototrophic sulfur bacteria on the oxic-anoxic tipping point was additive; all other effects were non-additive, especially at higher trait variation (Fig.
-\@ref(fig:fig-add-linear)g-i).
-
-# Comparing the effects of different treatments
-
-(ref:comp-comb) Another method for comparing the effects of different diversity treatments.
-Some lines (treatment combinations) are over-plotted and therefore show identical effects of some combinations.
-
-```{r comp-comb, echo = FALSE,  include=TRUE, fig.height=8, fig.width=8, fig.align="center", fig.cap='(ref:comp-comb)'}
-
-all_stab <- readRDS(here("data",
-                         microxanox_version_path,
-                         "temporal_method",
-                         "event_definition_2",
-                         "processed_data",
-                         "all_stab_data.RDS"))
-wait_time <- 1e6
-which_strain <- 9
-plot_here <- all_stab %>%
-  filter(waittime == wait_time)
-
-  p1 <- plot_here %>%
-    #filter(var_treat == "CB") %>%
-    filter(num_strains == which_strain) %>%
-    filter(Species == "SB_tot") %>%
-    ggplot(aes(x = stand_var
-               #col = as.factor(num_strains))
-    )) +
-    geom_line(aes(y = hyst_min_log, col=var_treat), lwd = 1, alpha = 0.8) +
-    geom_line(aes(y = hyst_max_log, col=var_treat), lwd = 1, alpha = 0.8) +
-    #geom_ribbon(aes(ymin = hyst_min_log, ymax = hyst_max_log),
-    #            fill = "green", alpha = 0.1) +
-    #facet_grid(var_treat ~ ., scales = "fixed") +
-    xlab("Standardised amount of trait variation") +
-    ylab(expression(log[10](oxygen~diffusivity)~(h^{-1}))) +
-    #labs(fill = "Variation in\nonly these\nfunctional groups") +
-    coord_flip() +
-    #guides(col = guide_legend(title="Number of strains"),
-    #       fill = guide_none()) +
-    theme_bw() +
-    theme(
-      legend.position="top",
-      panel.background = element_blank(),
-      #strip.text.x = element_blank()
-    ) +
-    geom_hline(yintercept = c(-8, 0), col = "grey", lwd = 3) #+
-    #geom_text(aes(x = 0.95, y = -8.1, label = label), colour = "black") +
-    #ggtitle(figure_title)
-
-  p1
-
-```
-
-# CB diversity effects
-
-Increased CB diversity causes a slight decrease in the resilience of the anoxic state.
-The following two figures show the state responses to oxygen diffusivity with low Figure \@ref(fig:ss-CB-only1) and high Figure \@ref(fig:ss-CB-only2) levels of CB diversity.
-
-The difference in the position of the anoxic to oxic tipping point is small.
-It is, in fact the smallest it could be, as it is the smallest step size in oxygen diffusivity used in the simulations.
-Furthermore, we think the presence of higher strain diversity can increase the rate of response of the system (since there is a strain with higher growth rate than in low diversity levels) and that this difference in response rates is likely responsible for the very small difference in resilience.
-
-(ref:ss-CB-only1) Stable state of the system with **low** level of diversity in only CB, and no diversity in the other two groups. All other aspects are as in Figure \@ref(fig:ss-temp-meth3).
-
-```{r ss-CB-only1, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-CB-only1)', fig.height=10, fig.width=8, fig.align="center"}
+```{r}
 wait_time <- "1e+06"
@@
                             "event_definition_2",
-                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
-#stab_9s <- readRDS(here::here(\"data", "0_ss_finding", "temporal_method", microxanox_version_path, paste0("stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS"))
+                            paste0("ss_data_-1strains_waittime", wait_time, "_event_definition_2.RDS")))
 
-#max <- max(ss_3s$PB_var_gmax_s)
-#f <- 0.625
-#fv <- f*max
+max_CB_var_gmax <- max(ss_9s$CB_var_gmax_s)
+max_SB_var_gmax <- max(ss_9s$SB_var_gmax_s)
+max_PB_var_gmax <- max(ss_9s$PB_var_gmax_s)
 
-only_CB_variable <- ss_9s %>%
+ss_9s <- ss_9s %>%
+  mutate(standvar_CB_gmax = CB_var_gmax_s / max_CB_var_gmax,
+         standvar_SB_gmax = SB_var_gmax_s / max_SB_var_gmax,
+         standvar_PB_gmax = PB_var_gmax_s / max_PB_var_gmax)
+
+```
+
+# CB
+
+```{r}
+this_dat <- ss_9s %>%
   filter(
-    abs(SB_var_gmax_s) < 0.0001,
-    abs(PB_var_gmax_s) < 0.0001
+    SB_var_gmax_s == 0,
+    PB_var_gmax_s == 0
   )
-only_CB_variable <- only_CB_variable[order(only_CB_variable$CB_var_gmax_s), ]
+this_dat <- this_dat[order(this_dat$CB_var_gmax_s), ]
 
-#only_CB_variable$CB_var_gmax_s
-
-fig_state_vs_o2diff_sidebyside_alternative(only_CB_variable[2,])
+for(i in 1:20)
+  print(fig_state_vs_o2diff_sidebyside_alternative(this_dat[i,]))
 
@@
 
-(ref:ss-CB-only2) Stable state of the system with **high** level of diversity in only CB, and no diversity in the other two groups. All other aspects are as in Figure \@ref(fig:ss-temp-meth3).
+# SB
 
-```{r ss-CB-only2, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-CB-only2)', fig.height=10, fig.width=8, fig.align="center"}
+```{r}
+this_dat <- ss_9s %>%
+  filter(
+    CB_var_gmax_s == 0,
+    PB_var_gmax_s == 0
+  )
+this_dat <- this_dat[order(this_dat$SB_var_gmax_s), ]
 
-fig_state_vs_o2diff_sidebyside_alternative(only_CB_variable[20,])
+for(i in 1:20)
+  print(fig_state_vs_o2diff_sidebyside_alternative(this_dat[i,]))
 
@@
 
-# References
+# PB
 
-Bush, T., Diao, M., Allen, R.J., Sinnige, R., Muyzer, G.
-& Huisman, J.
-(2017).
-Oxic-anoxic regime shifts mediated by feedbacks between biogeochemical processes and microbial community dynamics.
-Nat.
-Commun., 8, 789.
+```{r}
+this_dat <- ss_9s %>%
+  filter(
+    CB_var_gmax_s == 0,
+    SB_var_gmax_s == 0
+  )
+this_dat <- this_dat[order(this_dat$PB_var_gmax_s), ]
 
-Luther, G.W., Findlay, A., MacDonald, D., Owings, S., Hanson, T., Beinart, R., et al.
-(2011).
-Thermodynamics and kinetics of sulfide oxidation by oxygen: a look at inorganically controlled reactions and biologically mediated processes in the environment.
-Front.
-Microbiol., 2, 62.
+for(i in 1:20)
+  print(fig_state_vs_o2diff_sidebyside_alternative(this_dat[i,]))
+
+#fig_state_vs_o2diff(only_SB_variable[13,])
+```
+
+# CB-SB
+
+```{r}
+this_dat <- ss_9s %>%
+  filter(
+    PB_var_gmax_s == 0,
+    abs(standvar_CB_gmax - standvar_SB_gmax) < 0.00001
+  )
+this_dat <- this_dat[order(this_dat$CB_var_gmax_s), ]
+
+for(i in 1:20)
+  print(fig_state_vs_o2diff_sidebyside_alternative(this_dat[i,]))
+
+#fig_state_vs_o2diff(only_SB_variable[13,])
+```
+
+# CB-PB
+
+```{r}
+this_dat <- ss_9s %>%
+  filter(
+    SB_var_gmax_s == 0,
+    abs(standvar_CB_gmax - standvar_PB_gmax) < 0.00001
+  )
+this_dat <- this_dat[order(this_dat$CB_var_gmax_s), ]
+
+for(i in 1:20)
+  print(fig_state_vs_o2diff_sidebyside_alternative(this_dat[i,]))
+
+#fig_state_vs_o2diff(only_SB_variable[13,])
+```
+
+# SB-PB
+
+```{r}
+this_dat <- ss_9s %>%
+  filter(
+    CB_var_gmax_s == 0,
+    abs(standvar_SB_gmax - standvar_PB_gmax) < 0.00001
+  )
+this_dat <- this_dat[order(this_dat$SB_var_gmax_s), ]
+
+for(i in 1:20)
+  print(fig_state_vs_o2diff_sidebyside_alternative(this_dat[i,]))
+
+#fig_state_vs_o2diff(only_SB_variable[13,])
+```
+
+# CB-SB-PB
+
+```{r}
+this_dat <- ss_9s %>%
+  filter(
+    abs(standvar_CB_gmax - standvar_SB_gmax) < 0.00001,
+    abs(standvar_SB_gmax - standvar_PB_gmax) < 0.00001
+  )
+this_dat <- this_dat[order(this_dat$SB_var_gmax_s), ]
+
+for(i in 1:20)
+  print(fig_state_vs_o2diff_sidebyside_alternative(this_dat[i,]))
+
+#fig_state_vs_o2diff(only_SB_variable[13,])
+```

### 2022-11-16 reports/supplement/allssplots_strainvar_0.9.1.Rmd
added all ss plots

--- 2022-11-16 reports/supplement/allssplots_maxtol_0.9.1.Rmd
@@
 ---
-title: All stable state plots, with only the maximum tolerance strain
+title: All stable state plots, with strain variation
 author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
@@
                             "event_definition_2",
-                            paste0("ss_data_-1strains_waittime", wait_time, "_event_definition_2.RDS")))
+                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
 

### 2022-11-19 reports/supplement/supplement_0.9.1.Rmd
changes to the supplement

--- 2022-11-15 reports/supplement/supplement_0.9.1.Rmd
@@
 
-## SB diversity effect on the anoxic to oxic transition
+## SB diversity effect on the anoxic to oxic transition for short wait times (1e4)
 
@@
 
-When the environment ameliorates for the sulfate-reducing bacteria (i.e.
-trajectory of decreasing oxygen diffusivity), there is only limited evidence of strain replacement (in final state) along the oxygen diffusivity gradient -- either the system is oxic or the least tolerant strain dominates.
-And yet the switch to anoxic state occurs at higher oxygen diffusivity than when there is no diversity, which suggests there is some role of the more tolerant strains.
-We here show that the more tolerant strains do play a role, but only a transient one.
-The following dynamics are for the system starting oxic, and with a value of oxygen diffusivity (log10(oxygen diffusivity) = -4.8).
+We show in the main text that diversity in the sulfate-reducing bacteria results in earlier recovery of the anoxic state (Figure 3 c).
+However, there is only limited evidence of strain replacement on the trajectory of decreasing oxygen diffusivity: the most tolerant strain does increase in density prior to the tipping point but never reaches dominance – it is the strain with lowest tolerance that dominates immediately after the shift to the anoxic state.
+We here analyze temporal dynamics rather than the final state and show that the more tolerant strains do play a role, but only a transient one.
+The following dynamics are for the system starting oxic, and with a value of oxygen diffusivity $log_{10}$(oxygen diffusivity) = -4.8.
 When there is no diversity within functional groups (i.e.
 two strains that are identical) the system remains oxic (Figure \@ref(fig:sb-div-effect3)).
-When there is diversity (i.e.
-the two strains differ) then the system switches to the anoxic state (Figure \@ref(fig:sb-div-effect4)).
-In these examples there is only diversity in the two groups of sulfur bacteria.
-The most tolerant strain does at first grow, but is then outcompeted by less tolerant strains as the concentration of the inhibiting substrate (oxygen) declines.
+When there is diversity in the two groups of sulfur bacteria (i.e.
+the two strains differ) the system switches to the anoxic state (Figure \@ref(fig:sb-div-effect4)).
+The more tolerant strain of sulfate-reducing bacteria increases in density in the early phase of the simulation, reduces the concentration of oxygen by inhibiting cyanobacteria, and thus generates an environment in which the less tolerant strain is able to grow.
+Then, the more tolerant strain is outcompeted by the less tolerant strain as the concentration of the inhibiting substrate (oxygen) declines.
 
@@
 
+## Effect of low to moderate PB diversity
+
 ```{r echo = FALSE}
@@
 ```
+
+## Effect of medium to high PB diversity
+
+When there was medium to high variation in only the phototrophic sulfur bacteria, the dynamics of strains and substrates deviated from the standard pattern: at low oxygen diffusivity, all three groups coexisted.
+On the trajectory of decreasing oxygen diffusivity, cyanobacteria reappeared after their collapse (medium variation in PB, Figure xy) or never collapsed (high variation in PB, Figure xy).
+On the trajectory of increasing oxygen diffusivity, cyanobacteria coexisted with the two groups of sulfur bacteria at low oxygen diffusivity, collapsed at medium levels of oxygen diffusivity, and then increased to sole dominance at the tipping point to the oxic state.
+
+Explain pattern (Romana).
+
+The same pattern occurred for simultaneous variation in phototrophic sulfur bacteria and cyanobacteria, albeit only on the trajectory of increasing oxygen diffusivity (Figure xy).
+On the trajectory of decreasing oxygen diffusivity, medium to high variation in both groups led to sole dominance of cyanobacteria over the entire gradient of oxygen diffusivity.
+
+Owen, please add here 3 figures that match the text above: 
+(1) medium variation in only PB showing coexistence of all groups at low ox diff, 
+(2) high variation in only PB showing coexistence of all groups at low ox diff and CB never collapsing on the decreasing ox diff trajectory, 
+(3) high variation in both CB and PB.
 
@@
 
-In the SB-SB case, presence of only the high tolerance strain could cause the system to not display any alternate stable states (Figure \@ref(fig:max-tol5)).
+In the SB-CB case, presence of only the most tolerant strain led to coexistence of all groups at low levels of oxygen diffusivity when trait values were moderately high (Figure xy) or to absence of alternate stable states when trait values were high (Figure \@ref(fig:max-tol5)).
+
+Owen please add here a figure for medium trait values for the SB-CB case (only most tolerant strain), showing coexistence of all three groups at low ox diff.
 
@@
 ```
+
+## High tolerance vs. high diversity in PB
+
+Owen please add here two figures:
+(1) One for high trait variation in only PB showing coexistence of all three groups.
+(2) One for high tolerance in only PB (corresponding in trait values to the figure before) showing standard dynamics.
 

### 2022-11-20 reports/supplement/supplement_0.9.1.Rmd
changes to supplement

@@
 
-When there was medium to high variation in only the phototrophic sulfur bacteria, the dynamics of strains and substrates deviated from the standard pattern: at low oxygen diffusivity, all three groups coexisted.
-On the trajectory of decreasing oxygen diffusivity, cyanobacteria reappeared after their collapse (medium variation in PB, Figure xy) or never collapsed (high variation in PB, Figure xy).
+When there was medium to high variation in only the phototrophic sulfur bacteria (PB), the strain dynamics deviated from the standard pattern: at low oxygen diffusivity, all three functional groups coexisted.
+Specifically, on the trajectory of decreasing oxygen diffusivity, cyanobacteria reappeared at low oxygen diffusivity after their collapse at medium oxygen diffusivity (medium variation in PB, Figure xy) or never collapsed (high variation in PB, Figure xy).
 On the trajectory of increasing oxygen diffusivity, cyanobacteria coexisted with the two groups of sulfur bacteria at low oxygen diffusivity, collapsed at medium levels of oxygen diffusivity, and then increased to sole dominance at the tipping point to the oxic state.
 
-Explain pattern (Romana).
-
-The same pattern occurred for simultaneous variation in phototrophic sulfur bacteria and cyanobacteria, albeit only on the trajectory of increasing oxygen diffusivity (Figure xy).
-On the trajectory of decreasing oxygen diffusivity, medium to high variation in both groups led to sole dominance of cyanobacteria over the entire gradient of oxygen diffusivity.
+The same pattern occurred for medium to high simultaneous variation in phototrophic sulfur bacteria and cyanobacteria, albeit only on the trajectory of increasing oxygen diffusivity (Figure xy).
+On the trajectory of decreasing oxygen diffusivity, cyanobacteria dominated over the entire gradient of oxygen diffusivity, such that effects of PB diversity did not play out on this trajectory.
+
+The reason for coexistence of all three groups at low oxygen diffusivity was that the PB strain that dominated at low oxygen diffusivity (the least tolerant strain) lowered the sulfide concentrations to such low levels that cyanobacteria were able to grow.
+The higher the trait variation in PB, the higher the intrinsic growth rate of the least tolerant PB strain, and the higher its consumption of sulfide.
+Consequently, moderate variation in PB lowered the sulfide concentration such that the tipping point from anoxic to oxic occurred earlier (as discussed in the previous section), and medium to high variation in PB lowered the sulfide concentration even further such that cyanobacteria were able to grow and coexist with the two groups of sulfur bacteria at low oxygen diffusivity.
+
+At intermediate levels of oxygen diffusivities, the cyanobacteria were usually excluded (Figure xy).
+We speculate that this might be associated with the increase in sulfide prior to the collapse of the phototrophic sulfur bacteria.
+This increase in sulfide occurred simultaneously with turnover to PB strains with lower intrinsic growth rate and with a decline in PB density; these two processes likely resulted in less consumption of sulfide.
 
@@
 We then compared the tipping point positions resulting from this tolerance manipulation with the tipping point positions resulting from the diversity manipulation presented in the main text.
+In addition, we compared the dynamics of strains and substrates across the oxygen diffusivity gradient of the tolerance manipulation and the diversity manipulation.
 If the observed diversity effects are caused by the sampling effect, we expect there to be no difference between the tolerance manipulation and the diversity manipulation.
@@
 
-For most of the explored combinations and amounts of functional diversity/tolerance the tipping point positions did not differ between the diversity manipulation and the tolerance manipulation (Figure \@ref(fig:max-tol1)).
-However, in some cases there were effects, three of which are described in the follow sections.
+For most of the explored combinations and amounts of functional diversity/tolerance the tipping point positions and strain dynamics did not differ between the diversity manipulation and the tolerance manipulation (Figure \@ref(fig:max-tol1)).
+However, in some cases there were effects, which are described in the follow sections.
 
@@
 
-## High tolerance vs. high diversity in only the SB
+## Increasing tolerance vs. increasing diversity in only the SB
 
 When SB contained multiple strains varying in growth rate (and tolerance) there were only two stable states (Figure \@ref(fig:max-tol2)), as was previously reported.
-When, however, only one SB strain with very high tolerance and low maximum growth rate was present, there three stable states: the two previously found, and another where all three functional groups coexisted (Figure \@ref(fig:max-tol3)) – this never occurred when there were multiple strains varying in tolerance.
+When, however, only one SB strain with very high tolerance and low maximum growth rate was present, there were three stable states: the two previously found, and another state at low oxygen diffusivity where all three functional groups coexisted (Figure \@ref(fig:max-tol3)) – this never occurred when there were multiple SB strains varying in tolerance.
 
 Apparently, at low oxygen diffusivity levels, the absence of SB strains with high growth rate precludes the formation of a stable state that does not include cyanobacteria.
-It seems that the most tolerant SB strain does not have a high enough growth rate to itself exclude the cyanobacteria.
-Cyanobacteria are therefore always present, regardless of the oxygen diffusivity.
-We do not have an explanation of why the cyanobacteria are, however, excluded at intermediate oxygen diffusivities.
-
+The most tolerant SB strain has a low intrinsic growth rate, which leads to less production of sulfide.
+Presence of only the most tolerant SB strain therefore results in lower sulfide concentrations (Figure \@ref(fig:max-tol2) vs Figure \@ref(fig:max-tol3)), allowing growth of cyanobacteria at low oxygen diffusivity.
+
+However, cyanobacteria are excluded at intermediate oxygen diffusivity.
+We speculate that this might be associated with the increase in sulfide at intermediate oxygen diffusivity, which might be due to the decline and collapse of PB and therefore reduced consumption of sulfide.
 (ref:max-tol2) Stable states found when there is variation among nine strains of SB and the amount of variation is high. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
@@
 
-## High tolerance vs. high diversity in CB-SB
-
-In the SB-CB case, presence of only the most tolerant strain led to coexistence of all groups at low levels of oxygen diffusivity when trait values were moderately high (Figure xy) or to absence of alternate stable states when trait values were high (Figure \@ref(fig:max-tol5)).
+## Increasing tolerance vs. increasing diversity in CB-SB
+
+In the SB-CB case, presence of only the most tolerant strain led to coexistence of all groups at low levels of oxygen diffusivity when trait values were moderately high (Figure xy) or to absence of alternate stable states and sole dominance of cyanobacteria when trait values were high (Figure \@ref(fig:max-tol5)).
+As discussed in the previous section, the low intrinsic growth rate of the most tolerant SB strain led to less production of sulfide such that SB could not exclude CB.
 
@@
 
-## High tolerance vs. high diversity in PB
+## Increasing tolerance vs. increasing diversity in PB
+
+Whereas medium to high diversity in PB led to three states including one with coexistence of all three functional groups (Figure xy), presence of only the most tolerant PB strain led to only two stable states, namely the standard-pattern of either dominance of sulfur bacteria or of cyanobacteria (Figure xy).
+The most tolerant PB strain has a low intrinsic growth rate, leading to less consumption of sulfide and therefore to higher sulfide concentrations compared to a system that contains both slow- and fast-growing strains.
+Due to the higher sulfide concentrations in the system with only the most tolerant PB strain, cyanobacteria were not able to grow at low oxygen diffusivity levels.
 
@@
 
-## High tolerance vs. high diversity in CB-SB-PB
-
-When in each of the three functional groups only the most tolerant strain is present, the resilience of the oxic state is greater than when there is variation in strain tolerance within groups.
-It is not entirely clear why this effect only occurs only in this combination.
+## Increasing tolerance vs. increasing diversity in CB-SB-PB
+
+At high levels of diversity vs.
+tolerance, resilience of the oxic state is greater when in each of the three functional groups only the most tolerant strain is present rather than when there is variation in strain tolerance within groups.
+It is not entirely clear why this effect occurs only in this combination.
 

### 2022-11-21 reports/supplement/supplement_0.9.1.Rmd

@@
 
-The rate of change in population densities is given by the growth rate - death rate [Bush et al 2017](https://www.nature.com/articles/s41467-017-00912-x).
+The rate of change in population densities is given by the growth rate - death rate ([Bush et al 2017](https://www.nature.com/articles/s41467-017-00912-x)).
 Growth rate is the growth rate in absence of any inhibition multiplied by the amount of inhibition.
@@
 
+Growth of cyanobacteria depended on one substrate (phosphorus), whereas growth of sulfate-reducing bacteria (SB) and phototrophic sulfur bacteria (PB) depended on two substrates (phosphorus and oxidised sulfur for SB, and phosphorus and sulfide for PB).
+
 Inhibition of growth by a substrate was modelled with the Haldane equation:
@@
 
-For further information details of the functions used to model system, please see the original publication by Bush *et al.* (2018)
+For further information on the functions used to model the system, please see the original publication by [Bush et al 2017](https://www.nature.com/articles/s41467-017-00912-x).
 
@@
 community biomass) when species differ in their responses to environmental factors and therefore respond asynchronously to environmental fluctuations (temporal complementarity effect; Loreau & Mazancourt 2013).
-However, when considering ecosystem responses to directional environmental change or pulse disturbances rather than to environmental fluctuations, the sampling effect might be of particular importance (Steiner et al.
+However, the sampling effect might be of particular importance when considering ecosystem responses to directional environmental change or pulse disturbances rather than to environmental fluctuations (Steiner et al.
 2006): more diverse systems might absorb a greater amount of change by having a higher chance of containing species with high environmental tolerance.
@@
 
-## Do the observed diversity effects operate via the sampling effect?
-
-We investigated if the diversity effects observed in our study were in line with the sampling effect, that is, driven entirely by the presence of the most tolerant strain.
-Specifically, we ran additional simulations where functional groups contained only the strain with greatest tolerance and lowest maximum growth rate.
-That is, for each of the 20 levels of trait variation, we made simulations where each functional group had only one strain, and its trait values corresponded with those of the most tolerant strain for the given level of trait variation.
+## Investigating the mechanisms operating in our system
+
+We investigated if the diversity effects observed in our study were in line with the sampling effect, that is, driven entirely by the presence of the most tolerant strain or if the less tolerant strains played a role as well.
+To this end, we ran additional simulations where functional groups contained only the strain with greatest tolerance and lowest maximum growth rate.
+That is, rather than increasing diversity we only increased tolerance.
+Specifically, for each of the 20 levels of trait variation, we made simulations where each functional group had only one strain, and its trait values corresponded with those of the most tolerant strain for the given level of trait variation.
 We also manipulated in which of the functional groups tolerance increased.
@@
 We then compared the tipping point positions resulting from this tolerance manipulation with the tipping point positions resulting from the diversity manipulation presented in the main text.
-In addition, we compared the dynamics of strains and substrates across the oxygen diffusivity gradient of the tolerance manipulation and the diversity manipulation.
+In addition, we compared the strain dynamics across the oxygen diffusivity gradient of the tolerance manipulation and the diversity manipulation.
 If the observed diversity effects are caused by the sampling effect, we expect there to be no difference between the tolerance manipulation and the diversity manipulation.
@@
 
-For most of the explored combinations and amounts of functional diversity/tolerance the tipping point positions and strain dynamics did not differ between the diversity manipulation and the tolerance manipulation (Figure \@ref(fig:max-tol1)).
-However, in some cases there were effects, which are described in the follow sections.
+We found no difference between the diversity and the tolerance manipulation when trait values were low (Figure \@ref(fig:max-tol1)).
+When trait values were medium to high, however, we did find differences between the diversity and tolerance manipulation for most combinations except for diversity/tolerance in only CB and in SB-PB (Figure \@ref(fig:max-tol1)).
+We describe and discuss these differences in detail in the sections below.
+Briefly, in these scenarios less tolerant strains did play a role because of their high intrinsic growth rates.
+Specifically, absence of SB strains with high growth rate led to reduced production of sulfide and therefore to coexistence with cyanobacteria at low oxygen diffusivity.
+In contrast, absence of PB strains with high growth rate led to reduced consumption of sulfide and therefore precluded coexistence with cyanobacteria at low oxygen diffusivity (as observed when there was high variation in PB).
+
+Taken together, at low amounts of trait variation the diversity effects were driven entirely by the most tolerant strain, in line with a sampling effect.
+At medium to high trait variation, however, both tolerant and less tolerant strains affected the results in most combinations.
+The reason was that in the two groups of sulfur bacteria the trade-off between tolerance and growth rate had ecosystem-level effects, i.e.
+effects on the sulfide concentration and therefore on the cyanobacteria.
 
@@
 
-## Increasing tolerance vs. increasing diversity in PB
-
-Whereas medium to high diversity in PB led to three states including one with coexistence of all three functional groups (Figure xy), presence of only the most tolerant PB strain led to only two stable states, namely the standard-pattern of either dominance of sulfur bacteria or of cyanobacteria (Figure xy).
+## Increasing tolerance vs. increasing diversity in PB and in PB-CB
+
+Whereas medium to high diversity in only PB led to three states including one with coexistence of all three functional groups (Figure xy), presence of only the most tolerant PB strain led to only two stable states, namely the standard-pattern of either dominance of sulfur bacteria or of cyanobacteria (Figure xy).
 The most tolerant PB strain has a low intrinsic growth rate, leading to less consumption of sulfide and therefore to higher sulfide concentrations compared to a system that contains both slow- and fast-growing strains.
 Due to the higher sulfide concentrations in the system with only the most tolerant PB strain, cyanobacteria were not able to grow at low oxygen diffusivity levels.
+
+For the same reasons we found three states on the trajectory of increasing oxygen diffusivity for medium to high simultaneous trait variation in PB and CB but not for the corresponding tolerance manipulation (data not shown).
 
@@
 ```
-
-## Why only at high diversity/tolerance?
-
-Why do these effects only occur at high diversity/tolerance?
-The likely reason is that at high diversities the most tolerant strain has particularly low growth rate, and so it may have the tolerance required to increase and persist, but not the growth rate required to dominate.
 
@@
 
+Cardinale, B.J., Duffy, J.E., Gonzalez, A., Hooper, D.U., Perrings, C., Venail, P., et al. (2012). Biodiversity loss and its impact on humanity. Nature, 486, 59–67.
+
+Cardinale, B.J., Matulich, K.L., Hooper, D.U., Byrnes, J.E., Duffy, E., Gamfeldt, L., et al. (2011). The functional role of producer diversity in ecosystems. Am. J. Bot., 98, 572–592.
+
+Cardinale, B.J., Srivastava, D.S., Emmett Duffy, J., Wright, J.P., Downing, A.L., Sankaran, M., et al.
+(2006).
+Effects of biodiversity on the functioning of trophic groups and ecosystems.
+Nature, 443, 989–992.
+
+Fargione, J., Tilman, D., Dybzinski, R., Lambers, J.H.R., Clark, C., Harpole, W.S., et al.
+(2007).
+From selection to complementarity: shifts in the causes of biodiversity–productivity relationships in a long-term biodiversity experiment.
+Proc.
+R.
+Soc.
+B Biol.
+Sci., 274, 871–876.
+
+Hughes, A.R. & Stachowicz, J.J. (2011). Seagrass genotypic diversity increases disturbance response via complementarity and dominance. J. Ecol., 99, 445–453.
+
+Loreau, M., Barbier, M., Filotas, E., Gravel, D., Isbell, F., Miller, S.J., et al. (2021). Biodiversity as insurance: from concept to measurement and application. Biol. Rev., 96, 2333–2354.
+
+Loreau, M. & Hector, A. (2001). Partitioning selection and complementarity in biodiversity experiments. Nature, 412, 72–76.
+
+Loreau, M. & Mazancourt, C. de. (2013). Biodiversity and ecosystem stability: a synthesis of underlying mechanisms. Ecol. Lett., 16, 106–115.
+
 Luther, G.W., Findlay, A., MacDonald, D., Owings, S., Hanson, T., Beinart, R., et al.
@@
 Microbiol., 2, 62.
+
+Steiner, C.F., Long, Z.T., Krumins, J.A. & Morin, P.J. (2006). Population and Community Resilience in Multitrophic Communities. Ecology, 87, 996–1007.

### 2022-11-21 reports/stable_state_graphs/temporal/event_definition_2/3strain 1e6 wait_time/allssplots_strainvar_0.9.1.Rmd
mostly removing nonstandard stable state data

--- 2022-11-16 reports/supplement/allssplots_strainvar_0.9.1.Rmd
@@
 ---
-title: All stable state plots, with strain variation
+title: All stable state plots, with strain variation, 3 strains
 author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
@@
                             "event_definition_2",
-                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+                            paste0("ss_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))
 
@@
 
-for(i in 1:20)
+for(i in 1:20) {
+  print(paste0("Standardised level of variation = ", round(this_dat$standvar_CB_gmax[i],2)))
   print(fig_state_vs_o2diff_sidebyside_alternative(this_dat[i,]))
+}
 
@@
 
-for(i in 1:20)
+for(i in 1:20) {
+  print(paste0("Standardised level of variation = ", round(this_dat$standvar_SB_gmax[i],2)))
   print(fig_state_vs_o2diff_sidebyside_alternative(this_dat[i,]))
-
+}
 #fig_state_vs_o2diff(only_SB_variable[13,])
@@
 
-for(i in 1:20)
+for(i in 1:20) {
+  print(paste0("Standardised level of variation = ", round(this_dat$standvar_PB_gmax[i],2)))
   print(fig_state_vs_o2diff_sidebyside_alternative(this_dat[i,]))
-
+}
 #fig_state_vs_o2diff(only_SB_variable[13,])
@@
 
-for(i in 1:20)
+for(i in 1:20) {
+  print(paste0("Standardised level of variation = ", round(this_dat$standvar_CB_gmax[i],2)))
   print(fig_state_vs_o2diff_sidebyside_alternative(this_dat[i,]))
-
+}
 #fig_state_vs_o2diff(only_SB_variable[13,])

### 2022-11-21 reports/stable_state_graphs/temporal/event_definition_2/9strain 1e2 wait_time/allssplots_strainvar_0.9.1.Rmd
mostly removing nonstandard stable state data

--- 2022-11-21 reports/stable_state_graphs/temporal/event_definition_2/3strain 1e6 wait_time/allssplots_strainvar_0.9.1.Rmd
@@
 ---
-title: All stable state plots, with strain variation, 3 strains
+title: All stable state plots, with strain variation, 1e2 wait time
 author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
@@
 ```{r}
-wait_time <- "1e+06"
+wait_time <- "1e+02"
 ss_9s <- readRDS(here::here("data",
@@
                             "event_definition_2",
-                            paste0("ss_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))
+                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
 

### 2022-11-21 reports/stable_state_graphs/temporal/event_definition_2/9strain 1e3 wait_time/allssplots_strainvar_0.9.1.Rmd
mostly removing nonstandard stable state data

--- 2022-11-21 reports/stable_state_graphs/temporal/event_definition_2/3strain 1e6 wait_time/allssplots_strainvar_0.9.1.Rmd
@@
 ---
-title: All stable state plots, with strain variation, 3 strains
+title: All stable state plots, with strain variation, 1e3 wait time
 author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
@@
 ```{r}
-wait_time <- "1e+06"
+wait_time <- "1e+03"
 ss_9s <- readRDS(here::here("data",

### 2022-11-21 reports/stable_state_graphs/temporal/event_definition_2/9strain 1e5 wait_time/allssplots_strainvar_0.9.1.Rmd
mostly removing nonstandard stable state data

--- 2022-11-21 reports/stable_state_graphs/temporal/event_definition_2/3strain 1e6 wait_time/allssplots_strainvar_0.9.1.Rmd
@@
 ---
-title: All stable state plots, with strain variation, 3 strains
+title: All stable state plots, with strain variation, 1e5 wait time
 author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
@@
 ```{r}
-wait_time <- "1e+06"
+wait_time <- "1e+05"
 ss_9s <- readRDS(here::here("data",

### 2022-11-21 reports/stable_state_graphs/temporal/event_definition_2/9strain 1e6 wait_time/allssplots_strainvar_0.9.1.Rmd
mostly removing nonstandard stable state data

--- 2022-11-21 reports/stable_state_graphs/temporal/event_definition_2/9strain 1e5 wait_time/allssplots_strainvar_0.9.1.Rmd
@@
 ---
-title: All stable state plots, with strain variation, 1e5 wait time
+title: All stable state plots, with strain variation
 author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
@@
 ```{r}
-wait_time <- "1e+05"
+wait_time <- "1e+06"
 ss_9s <- readRDS(here::here("data",

### 2022-11-21 reports/supplement/supplement_0.9.1.Rmd
mostly removing nonstandard stable state data

@@
 
-The rate of change in population densities is given by the growth rate - death rate ([Bush et al 2017](https://www.nature.com/articles/s41467-017-00912-x)).
+The rate of change in population densities is given by the per capita growth rate - per capita death rate, multipled by population size ([Bush et al 2017](https://www.nature.com/articles/s41467-017-00912-x)).
 Growth rate is the growth rate in absence of any inhibition multiplied by the amount of inhibition.
@@
 (ref:repl-meth2) Stable states found with the **replication method**.
-The left column of panels refers to the stable state when oxygen diffusivity is at first high (favouring the oxic state).
-The right column refers to when oxygen diffusivity is at first low (favouring the anoxic state).
+The left column of panels refers to the stable state when cyanobacteria density is at first high (favouring the oxic state).
+The right column refers to when cyanobacteria density is at first low (favouring the anoxic state).
 Points (which sometimes are so close as to appear as thick lines) show the stable state at the end of each period of constant oxygen diffusivity.
@@
 plot_here <- all_stab %>%
-  filter(simlength == sim_length)
+  filter(simlength == sim_length) %>%
+  ## remove data where there are non-standard stable states
+## this subset is identified by inspection of stable state figures
+  filter(!(num_strains == 9 & var_treat == "CB" & stand_var > 1.00),
+         !(num_strains == 9 & var_treat == "SB" & stand_var > 1.00),
+         !(num_strains == 9 & var_treat == "PB" & stand_var > 0.70),
+         !(num_strains == 9 & var_treat == "CB-SB" & stand_var > 1.00),
+         !(num_strains == 9 & var_treat == "CB-PB" & stand_var > 0.65),
+         !(num_strains == 9 & var_treat == "SB-PB" & stand_var > 1.0),
+         !(num_strains == 9 & var_treat == "CB-SB-PB" & stand_var > 1.00))
+
 p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
@@
 plot_here <- all_stab %>%
-  filter(waittime == wait_time)
+  filter(waittime == wait_time) %>%
+  filter(!(num_strains == 9 & var_treat == "CB" & stand_var > 1.00),
+         !(num_strains == 9 & var_treat == "SB" & stand_var > 1.00),
+         !(num_strains == 9 & var_treat == "PB" & stand_var > 0.65),
+         !(num_strains == 9 & var_treat == "CB-SB" & stand_var > 1.00),
+         !(num_strains == 9 & var_treat == "CB-PB" & stand_var > 0.65),
+         !(num_strains == 9 & var_treat == "SB-PB" & stand_var > 1.0),
+         !(num_strains == 9 & var_treat == "CB-SB-PB" & stand_var > 1.00))
+
 p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
@@
 
+# Finding the separatrix
+
+In the original publication ([Bush et al 2017](<https://www.nature.com/articles/s41467-017-00912-x>)) Figure 3a shows a separatrix in the cyanobacteria abundance - oxygen diffusivity dimensions of the system.
+If the system has initial cyanobacterial abundance greater than the value at the separatrix then the cyanobacterial abundance increases, and the system goes to the oxic stable state.
+Conversely, if the system has initial cyanobacterial abundance lower than the value at the separatrix then the cyanobacterial abundance decreases, and the system goes to the anoxic stable state.
+
+It is critical to note, however, that the position of the separatrix depends on both the parameters of the system, and the initial conditions of variables other than cyanobacterial abundance.
+If the system were started with higher initial concentration, then the position of the separatrix would change (as would the values of oxygen diffusivity at which the system tipped from anoxic to oxic, and from oxic to anoxic).
+
+This issue of dependence of the position of the separatrix on the value of initial condition of multiple state variables has particular significance when there are multiple strains per functional group.
+Then one cannot just vary initial total cyanobacterial abundance (as was done to create the separatrix on Figure 3a in the original publication) but one must also define how the initial abundance of each of the strains varies.
+One might choose to make each strain have equal initial abundance, and to vary the total (as we did in our implementation of the replication method in the main article).
+
+We could, however, and arguably should, give the most tolerant strain of cyanobacteria higher initial relative abundance when total initial cyanobacterial abundance was low, and the least tolerant strain higher initial relative abundance when total cyanobacterial abundance was high.
+And we would need to specify the total and relative abundance of all cyanobacteria (and sulfur bactria) strains.
+Thus, with a system as complex as the 9 strain system, which has 31 state variables the separatrix is very high dimensional, and evaluating (and plotting) it in one dimension requires many assumptions.
+We chose to not attempt to find a meaningful set of assumptions in this study, though not because we think it would be unprofitable to do so, but rather because we did not want to risk distracting attention from findings we consider to be significant enough in their own right.
+
 # Effect of simulation duration
@@
 plot_here <- all_stab %>%
-  filter(waittime == wait_time)
+  filter(waittime == wait_time) %>%
+  filter(!(num_strains == 9 & var_treat == "CB" & stand_var > 1.00),
+         !(num_strains == 9 & var_treat == "SB" & stand_var > 1.00),
+         !(num_strains == 9 & var_treat == "PB" & stand_var > 0.65),
+         !(num_strains == 9 & var_treat == "CB-SB" & stand_var > 1.00),
+         !(num_strains == 9 & var_treat == "CB-PB" & stand_var > 0.65),
+         !(num_strains == 9 & var_treat == "SB-PB" & stand_var > 1.00),
+         !(num_strains == 9 & var_treat == "CB-SB-PB" & stand_var > 1.00))
 p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
@@
 
-(ref:div-temp-meth5) Effects of diversity with wait time of 1e2 hours. (All else as in Figure \@ref(fig:div-repl-meth1)).
-
-```{r div-temp-meth5, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth5)', fig.height=7, fig.width=6, fig.align="center"}
+```{r div-temp-meth5, echo = FALSE, eval = FALSE, include=TRUE, fig.cap='(ref:div-temp-meth5)', fig.height=7, fig.width=6, fig.align="center"}
+
+## Owen removed these results from the report, because the tipping point finding algorithm was being misled
+## by transient dynamics, and therefore was not finding the correct position of the anoxic to oxic tipping
+## point
+
+## (ref:div-temp-meth5) Effects of diversity with wait time of 1e2 hours. (All else as in Figure \@ref(fig:div-repl-meth1)).
 
@@
 The results below show the stable states as a function of oxygen diffusivity for a system with an intermediate level of diversity in all functional groups, with either 1'000'000 hours at each oxygen diffusivity level (Figure \@ref(fig:ss-temp-meth3)), or 2'000'000 hours (Figure \@ref(fig:ss-temp-meth4)).
-This shows that 1'000'000 hours duration of the simulations are sufficient to reach stable state, except very close to state transitions on the trajectory of recovery (i.e.: cyanobacteria: trajectory of increasing oxygen diffusivity; sulfate-reducing bacteria: trajectory of decreasing oxygen diffusivity).
-Very close to these transitions, even at 2'000'000 hours, the dynamics are still transient, with high tolerance strains at high density, even though they will eventually be outcompeted by low tolerance (higher growth rate) strains.
+This shows that 1'000'000 hours duration of the simulations are sufficient to reach stable state, except in regions of strain replacement, including at some state transitions.
+E.g.
+in the region of strain replacement in the sulfate-reducing bacteria recovery trajectory there is difference in strain abundances at 1'000'000 and 2'000'000 hours.
+However, the position of the tipping points (which were calculated from the total SB abundance) and the substrate concentrations did not differ between 1'000'000 and 2'000'000 hours.
 
@@
 fig_state_vs_o2diff_sidebyside_alternative(temp_meth[1,])
+```
+
+# Effect of number of strains
+
+In the main text, we present results of simulations with nine strains per functional group.
+Here we also explore the effect of number of strains (2, 3, 6, 9) on the position of the two tipping points (Figure \@ref(fig:div-stab-multstrain1)).
+At low to moderate amounts of trait variation, the number of strains did not affect the position of the tipping points.
+However, at high amounts of trait variation, resilience was lower when the functional groups had only two or three strains rather than six or nine.
+This effect was particularly pronounced when there was high variation in only SB or in SB-CB: here, simulations with two or three strains led to dramatically lower resilience of the anoxic state than simulations with six or nine strains.
+We believe that this effect is due to the greater distance in trait space between strains in simulations with two or three strains than in simulations with more strains (also see Section 5).
+
+(ref:div-stab-multstrain1)  Effects of number of strains and of diversity among strains.
+
+```{r div-stab-multstrain1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-stab-multstrain1)', fig.height=8, fig.width=8, fig.align="center"}
+all_stab <- readRDS(here("data",
+                         microxanox_version_path,
+                         "temporal_method", 
+                         "event_definition_2",
+                         "processed_data", "all_stab_data.RDS"))
+which_strains <- c(2, 3, 6, 9)
+which_wait_time<- 1e6
+figure_title <- " "
+
+plot_here111 <- all_stab %>%
+  filter(!(num_strains == 9 & var_treat == "CB" & stand_var > 1.00),
+         !(num_strains == 9 & var_treat == "SB" & stand_var > 1.00),
+         !(num_strains == 9 & var_treat == "PB" & stand_var > 0.65),
+         !(num_strains == 9 & var_treat == "CB-SB" & stand_var > 1.00),
+         !(num_strains == 9 & var_treat == "CB-PB" & stand_var > 0.65),
+         !(num_strains == 9 & var_treat == "SB-PB" & stand_var > 1.0),
+         !(num_strains == 9 & var_treat == "CB-SB-PB" & stand_var > 1.00),
+
+         !(num_strains == 6 & var_treat == "CB" & stand_var > 1.00),
+         !(num_strains == 6 & var_treat == "SB" & stand_var > 1.00),
+         !(num_strains == 6 & var_treat == "PB" & stand_var > 0.65),
+         !(num_strains == 6 & var_treat == "CB-SB" & stand_var > 1.00),
+         !(num_strains == 6 & var_treat == "CB-PB" & stand_var > 0.65),
+         !(num_strains == 6 & var_treat == "SB-PB" & stand_var > 1.00),
+         !(num_strains == 6 & var_treat == "CB-SB-PB" & stand_var > 1.00),
+
+         !(num_strains == 3 & var_treat == "CB" & stand_var > 1.00),
+         !(num_strains == 3 & var_treat == "SB" & stand_var > 1.00),
+         !(num_strains == 3 & var_treat == "PB" & stand_var > 0.65),
+         !(num_strains == 3 & var_treat == "CB-SB" & stand_var > 1.00),
+         !(num_strains == 3 & var_treat == "CB-PB" & stand_var > 0.65),
+         !(num_strains == 3 & var_treat == "SB-PB" & stand_var > 1.0),
+         !(num_strains == 3 & var_treat == "CB-SB-PB" & stand_var > 1.00),
+
+         !(num_strains == 2 & var_treat == "CB" & stand_var > 1.00),
+         !(num_strains == 2 & var_treat == "SB" & stand_var > 1.00),
+         !(num_strains == 2 & var_treat == "PB" & stand_var > 0.65),
+         !(num_strains == 2 & var_treat == "CB-SB" & stand_var > 1.00),
+         !(num_strains == 2 & var_treat == "CB-PB" & stand_var > 0.65),
+         !(num_strains == 2 & var_treat == "SB-PB" & stand_var > 1.00),
+         !(num_strains == 2 & var_treat == "CB-SB-PB" & stand_var > 1.00))
+
+fig_div_vs_o2diff_multistrain(plot_here111, which_strains,
+                              which_wait_time, figure_title)
+```
+
+# CB diversity effects
+
+Increased CB diversity causes a slight decrease in the resilience of the anoxic state.
+The following two figures show the state responses to oxygen diffusivity with low Figure \@ref(fig:ss-CB-only1) and high Figure \@ref(fig:ss-CB-only2) levels of CB diversity.
+The difference in the position of the anoxic to oxic tipping point is small.
+It is, in fact the smallest it could be, as it is the smallest step size in oxygen diffusivity used in the simulations.
+
+(ref:ss-CB-only1) Stable state of the system with **low** level of diversity in only CB, and no diversity in the other two groups. All other aspects are as in Figure \@ref(fig:ss-temp-meth3).
+
+```{r ss-CB-only1, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-CB-only1)', fig.height=10, fig.width=8, fig.align="center"}
+wait_time <- "1e+06"
+ss_9s <- readRDS(here::here("data",
+                            microxanox_version_path, 
+                            "temporal_method",
+                            "event_definition_2",
+                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+#stab_9s <- readRDS(here::here(\"data", "0_ss_finding", "temporal_method", microxanox_version_path, paste0("stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS"))
+
+#max <- max(ss_3s$PB_var_gmax_s)
+#f <- 0.625
+#fv <- f*max
+
+only_CB_variable <- ss_9s %>%
+  filter(
+    abs(SB_var_gmax_s) < 0.0001,
+    abs(PB_var_gmax_s) < 0.0001
+  )
+only_CB_variable <- only_CB_variable[order(only_CB_variable$CB_var_gmax_s), ]
+
+#only_CB_variable$CB_var_gmax_s
+
+fig_state_vs_o2diff_sidebyside_alternative(only_CB_variable[2,])
+
+#fig_state_vs_o2diff(only_SB_variable[13,])
+```
+
+(ref:ss-CB-only2) Stable state of the system with **high** level of diversity in only CB, and no diversity in the other two groups. All other aspects are as in Figure \@ref(fig:ss-temp-meth3).
+
+```{r ss-CB-only2, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-CB-only2)', fig.height=10, fig.width=8, fig.align="center"}
+
+fig_state_vs_o2diff_sidebyside_alternative(only_CB_variable[20,])
+
+#fig_state_vs_o2diff(only_SB_variable[13,])
 ```
@@
 
-(ref:pbdiv-only-3) Concentrations of three substrates (O: oxygen; SO: oxidised sulfur; SR: reduced sulfur) in a low PB diversity simulation (x-axis) versus substrate concentration in a high PB diversity simulation (y-axis).
+(ref:pbdiv-only-3) Concentrations of three substrates (O: oxygen; SO: oxidised sulfur; SR: reduced sulfur) in a low PB diversity simulation (x-axis) versus substrate concentration in a moderate PB diversity simulation (y-axis).
+(The same levels of PB diversity as in Figures \@ref(fig:pbdiv-only-1) and \@ref(fig:pbdiv-only-2), respectively).
 The figures show only a small range of oxygen diffusivity on the trajectory of increasing oxygen diffusivity.
@@
   xlab(expression(atop(log[10](concentration)~(µM), Low~PB~diversity))) +
-  ylab(expression(atop(log[10](concentration)~(µM),High~PB~diversity))) +
+  ylab(expression(atop(log[10](concentration)~(µM),Moderate~PB~diversity))) +
   labs(col=expression(paste("log"[10],"(oxygen diffusivity) (h"^{-1}, ")"))) +
@@
 Owen, please add here 3 figures that match the text above:
+
+```{r echo = FALSE}
+run_sims_this_section <- TRUE
+```
+
+```{r}
+nine_strains <- readRDS(here("data",
+                         microxanox_version_path,
+                         "temporal_method", 
+                         "event_definition_2",
+                          "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
+```
+
 (1) medium variation in only PB showing coexistence of all groups at low ox diff,
+
+```{r  eval = run_sims_this_section, echo = FALSE}
+
+nine_strain_one <- filter(nine_strains,
+       CB_var_gmax_s == 0,
+       SB_var_gmax_s == 0,
+       abs(PB_var_gmax_s - 0.064819946) < 0.001)
+
+parameter <- nine_strain_one$parameter[[1]]
+parameter$strain_parameter <- nine_strain_one$pars[[1]]
+#parameter$strain_parameter <- ss_result$pars[[1]]
+total_initial_abundances <- 10^5
+parameter <- set_temporal_ssfind_initial_state(parameter,
+                                               total_initial_abundances,
+                                               total_initial_abundances,
+                                               total_initial_abundances)
+parameter$log10a_series <- c(-7, -7)
+wait_time <-  1e5
+parameter$sim_duration <- wait_time * length(parameter$log10a_series)
+parameter$sim_sample_interval <- 10
+#parameter$sim_duration
+test1 <- run_simulation(parameter)
+
+```
+
+(ref:PB-dyn1) Temporal dynamics of an ecosystem with a , the same one as in Figure \@ref(fig:max-tol3) simulated with constant $log_{10}$ oxygen diffusivity of -7.
+
+```{r PB-dyn1, echo = FALSE,  include=TRUE, fig.cap='(ref:PB-dyn1)', fig.height=10, fig.width=8, fig.align="center"}
+p <- plot_dynamics(test1)
+p[[1]] <- p[[1]] + 
+  xlab(NULL) + 
+  ylab(expression(log[10](density)~(cells~L^{-1}))) +
+  theme_bw()
+p[[2]] <- p[[2]] + 
+  xlab(NULL) + 
+  ylab(expression(log[10](density)~(cells~L^{-1}))) +
+  theme_bw()
+p[[3]] <- p[[3]] + 
+  xlab(NULL) + 
+  ylab(expression(log[10](density)~(cells~L^{-1}))) +
+  theme_bw()
+p[[4]]$data <- p[[4]]$data %>% 
+  dplyr::filter(species != "a")
+p[[4]]$data$species <- p[[4]]$data$species %>%
+  dplyr::recode(SO = "Oxidised sulfur", O = "Oxygen", SR = "Sulfide", P = "Phosphorus")
+p[[4]] <- p[[4]] + 
+  xlab("time (h)") + 
+  ylab(expression(log[10](concentration)~(µM))) + 
+  labs(colour = "substrate") +
+  theme_bw()
+
+p
+```
+
 (2) high variation in only PB showing coexistence of all groups at low ox diff and CB never collapsing on the decreasing ox diff trajectory,
+
 (3) high variation in both CB and PB.
-
-# Effect of number of strains
-
-In the main text, we present results of simulations with nine strains per functional group.
-Here we also explore the effect of number of strains (2, 3, 6, 9) on the position of the two tipping points (Figure \@ref(fig:div-stab-multstrain1)).
-At low to moderate amounts of trait variation, the number of strains did not affect the position of the tipping points.
-However, at high amounts of trait variation, resilience was lower when the functional groups had only two or three strains rather than six or nine.
-This effect was particularly pronounced when there was high variation in only SB or in SB-CB: here, simulations with two or three strains led to dramatically lower resilience of the anoxic state than simulations with six or nine strains.
-We believe that this effect is due to the greater distance in trait space between strains in simulations with two or three strains than in simulations with more strains (also see Section 5).
-
-(ref:div-stab-multstrain1)  Effects of number of strains and of diversity among strains.
-
-```{r div-stab-multstrain1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-stab-multstrain1)', fig.height=8, fig.width=8, fig.align="center"}
-all_stab <- readRDS(here("data",
-                         microxanox_version_path,
-                         "temporal_method", 
-                         "event_definition_2",
-                         "processed_data", "all_stab_data.RDS"))
-which_strains <- c(2, 3, 6, 9)
-which_wait_time<- 1e6
-figure_title <- " "
-
-fig_div_vs_o2diff_multistrain(all_stab, which_strains,
-                              which_wait_time, figure_title)
-```
 
@@
 
-(ref:samp-effect1) A simple phenomenological model of the effect of number of strains in an ecosystem on the resilience of that ecosystem, when the resilience of a ecosystem is linearly proportional to the maximum trait value of the strains present in that ecosystem.
+```{r samp-effect1, echo = FALSE, eval= FALSE, include=TRUE, fig.cap='(ref:samp-effect1)', fig.height=5, fig.width=6, fig.align="center"}
+
+## no longer included in supplement.
+
+## (ref:samp-effect1) A simple phenomenological model of the effect of number of strains in an ecosystem on the resilience of that ecosystem, when the resilience of a ecosystem is linearly proportional to the maximum trait value of the strains present in that ecosystem.
 Each data point is a different ecosystem, with the strains in each ecosystem drawn at random from a pool of 20 strains.
@@
 
-```{r samp-effect1, echo = FALSE,  include=TRUE, fig.cap='(ref:samp-effect1)', fig.height=5, fig.width=6, fig.align="center"}
 if(!("tidyverse" %in% .packages()))
@@
 
-We investigated if the diversity effects observed in our study were in line with the sampling effect, that is, driven entirely by the presence of the most tolerant strain or if the less tolerant strains played a role as well.
-To this end, we ran additional simulations where functional groups contained only the strain with greatest tolerance and lowest maximum growth rate.
-That is, rather than increasing diversity we only increased tolerance.
+We investigated if the diversity effects observed in our study were in line with the sampling effect, that is, driven entirely by the presence of the most tolerant strain or if other strains played a role as well.
+To this end, we ran additional simulations where functional groups contained only the strain with greatest tolerance (which also necessarily had the lowest maximum growth rate).
+That is, rather than increasing diversity we only increased tolerance of a single strain.
 Specifically, for each of the 20 levels of trait variation, we made simulations where each functional group had only one strain, and its trait values corresponded with those of the most tolerant strain for the given level of trait variation.
@@
 
-To exclude that differences between the tolerance manipulation and the diversity manipulation were driven by the difference in number of strains, we also performed simulations in which we retained nine strains in each functional group but set the tolerance of all nine strains to the maximum tolerance value.
-Results were the same as those presented below from simulations with one strain.
-
 We found no difference between the diversity and the tolerance manipulation when trait values were low (Figure \@ref(fig:max-tol1)).
@@
 
-## remove data where there are no stable states
-## this subset is identified by inspection of the figure
-#all_stab <- all_stab %>%
-#  filter(!(var_treat == "CB-SB" & stand_var > 0.84 & num_strains == -1))
-
-plot_1 <- fig_div_vs_o2diff_maxtolcomp(all_stab, which_strains,
+## remove data where there are non-standard stable states
+## this subset is identified by inspection of stable state figures
+plot_here11 <- all_stab %>%
+  filter(!(num_strains == 9 & var_treat == "CB" & stand_var > 1.00),
+         !(num_strains == 9 & var_treat == "SB" & stand_var > 1.00),
+         !(num_strains == 9 & var_treat == "PB" & stand_var > 0.65),
+         !(num_strains == 9 & var_treat == "CB-SB" & stand_var > 1.00),
+         !(num_strains == 9 & var_treat == "CB-PB" & stand_var > 0.65),
+         !(num_strains == 9 & var_treat == "SB-PB" & stand_var > 1.0),
+         !(num_strains == 9 & var_treat == "CB-SB-PB" & stand_var > 1.00),
+         !(num_strains == -1 & var_treat == "CB" & stand_var > 1.00),
+         !(num_strains == -1 & var_treat == "SB" & stand_var > 0.60),
+         !(num_strains == -1 & var_treat == "PB" & stand_var > 1.00),
+         !(num_strains == -1 & var_treat == "CB-SB" & stand_var > 0.60),
+         !(num_strains == -1 & var_treat == "CB-PB" & stand_var > 1.00),
+         !(num_strains == -1 & var_treat == "SB-PB" & stand_var > 1.00),
+         !(num_strains == -1 & var_treat == "CB-SB-PB" & stand_var > 1.00))
+
+plot_1 <- fig_div_vs_o2diff_maxtolcomp(plot_here11, which_strains,
                               which_wait_time, figure_title)
@@
 
-# Finding the separatrix
-
-In the original publication ([Bush et al 2017](<https://www.nature.com/articles/s41467-017-00912-x>)) Figure 3a shows a separatrix in the cyanobacteria abundance - oxygen diffusivity dimensions of the system.
-If the system has initial cyanobacterial abundance greater than the value at the separatrix then the cyanobacterial abundance increases, and the system goes to the oxic stable state.
-Conversely, if the system has initial cyanobacterial abundance lower than the value at the separatrix then the cyanobacterial abundance decreases, and the system goes to the anoxic stable state.
-
-It is critical to note, however, that the position of the separatrix depends on both the parameters of the system, and the initial conditions of variables other than cyanobacterial abundance.
-If the system were started with higher initial concentration, then the position of the separatrix would change (as would the values of oxygen diffusivity at which the system tipped from anoxic to oxic, and from oxic to anoxic).
-
-This issue of dependence of the position of the separatrix on the value of initial condition of multiple state variables has particular significance when there are multiple strains per functional group.
-Then one cannot just vary initial total cyanobacterial abundance (as was done to create the separatrix on Figure 3a in the original publication) but one must also define how the initial abundance of each of the strains varies.
-One might choose to make each strain have equal initial abundance, and to vary the total (as we did in our implementation of the replication method in the main article).
-
-We could, however, and arguably should, give the most tolerant strain of cyanobacteria higher initial relative abundance when total initial cyanobacterial abundance was low, and the least tolerant strain higher initial relative abundance when total cyanobacterial abundance was high.
-And we would need to specify the total and relative abundance of all cyanobacteria (and sulfur bactria) strains.
-Thus, with a system as complex as the 9 strain system, which has 31 state variables the separatrix is very high dimensional, and evaluating (and plotting) it in one dimension requires many assumptions.
-We chose to not attempt to find a meaningful set of assumptions in this study, though not because we think it would be unprofitable to do so, but rather because we did not want to risk distracting attention from findings we consider to be significant enough in their own right.
-
 # (Non-)additivity
@@
 
-# Comparing the effects of different treatments
-
-(ref:comp-comb) Another method for comparing the effects of different diversity treatments.
+```{r comp-comb, echo = FALSE, eval = FALSE, include=TRUE, fig.height=8, fig.width=8, fig.align="center", fig.cap='(ref:comp-comb)'}
+
+## This code chunck makes a figure that we used but think does not need
+## to be included in the supplement.
+## (ref:comp-comb) Another method for comparing the effects of different diversity treatments.
 Some lines (treatment combinations) are over-plotted and therefore show identical effects of some combinations.
-
-```{r comp-comb, echo = FALSE,  include=TRUE, fig.height=8, fig.width=8, fig.align="center", fig.cap='(ref:comp-comb)'}
 
@@
 
-# CB diversity effects
-
-Increased CB diversity causes a slight decrease in the resilience of the anoxic state.
-The following two figures show the state responses to oxygen diffusivity with low Figure \@ref(fig:ss-CB-only1) and high Figure \@ref(fig:ss-CB-only2) levels of CB diversity.
-
-The difference in the position of the anoxic to oxic tipping point is small.
-It is, in fact the smallest it could be, as it is the smallest step size in oxygen diffusivity used in the simulations.
-Furthermore, we think the presence of higher strain diversity can increase the rate of response of the system (since there is a strain with higher growth rate than in low diversity levels) and that this difference in response rates is likely responsible for the very small difference in resilience.
-
-(ref:ss-CB-only1) Stable state of the system with **low** level of diversity in only CB, and no diversity in the other two groups. All other aspects are as in Figure \@ref(fig:ss-temp-meth3).
-
-```{r ss-CB-only1, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-CB-only1)', fig.height=10, fig.width=8, fig.align="center"}
-wait_time <- "1e+06"
-ss_9s <- readRDS(here::here("data",
-                            microxanox_version_path, 
-                            "temporal_method",
-                            "event_definition_2",
-                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
-#stab_9s <- readRDS(here::here(\"data", "0_ss_finding", "temporal_method", microxanox_version_path, paste0("stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS"))
-
-#max <- max(ss_3s$PB_var_gmax_s)
-#f <- 0.625
-#fv <- f*max
-
-only_CB_variable <- ss_9s %>%
-  filter(
-    abs(SB_var_gmax_s) < 0.0001,
-    abs(PB_var_gmax_s) < 0.0001
-  )
-only_CB_variable <- only_CB_variable[order(only_CB_variable$CB_var_gmax_s), ]
-
-#only_CB_variable$CB_var_gmax_s
-
-fig_state_vs_o2diff_sidebyside_alternative(only_CB_variable[2,])
-
-#fig_state_vs_o2diff(only_SB_variable[13,])
-```
-
-(ref:ss-CB-only2) Stable state of the system with **high** level of diversity in only CB, and no diversity in the other two groups. All other aspects are as in Figure \@ref(fig:ss-temp-meth3).
-
-```{r ss-CB-only2, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-CB-only2)', fig.height=10, fig.width=8, fig.align="center"}
-
-fig_state_vs_o2diff_sidebyside_alternative(only_CB_variable[20,])
-
-#fig_state_vs_o2diff(only_SB_variable[13,])
-```
-
 # References

### 2022-11-21 R/ms_figure_functions.R

@@ -128,116 +128,28 @@ fig_div_vs_o2diff_1strain <- function(all_stab, which_strain, figure_title) {
   
 }
 
-fig_div_vs_o2diff_multistrain <- function(all_stab,
+fig_div_vs_o2diff_multistrain <- function(all_stab111,
                                           which_strains,
                                           which_wait_time,
                                           figure_title) {
+ 
   
-  # CB_vars <- unique(all_stab$CB_var_gmax_s)
-  # SB_vars <- unique(all_stab$SB_var_gmax_s)
-  # PB_vars <- unique(all_stab$PB_var_gmax_s)
-  # 
-  # CB_all_stab <- all_stab %>%
-  #   filter(SB_var_gmax_s == 0,
-  #          PB_var_gmax_s == 0) %>%
-  #   ungroup() %>%
-  #   mutate(var_treat = "CB",
-  #          var_gmax = CB_var_gmax_s,
-  #          stand_var = var_gmax / max(var_gmax))
-  # SB_all_stab <- all_stab %>%
-  #   filter(CB_var_gmax_s == 0,
-  #          PB_var_gmax_s == 0)  %>%
-  #   ungroup() %>%
-  #   mutate(var_treat = "SB",
-  #          var_gmax = SB_var_gmax_s,
-  #          stand_var = var_gmax / max(var_gmax))
-  # PB_all_stab <- all_stab %>%
-  #   filter(CB_var_gmax_s == 0,
-  #          SB_var_gmax_s == 0) %>%
-  #   ungroup()  %>%
-  #   mutate(var_treat = "PB",
-  #          var_gmax = PB_var_gmax_s,
-  #          stand_var = var_gmax / max(var_gmax))
-  # 
-  # for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
-  #                    SB_var_gmax_s = sort(SB_vars))
-  # CBSB_all_stab <- all_stab %>%
-  #   right_join(for_join)  %>%
-  #   ungroup() %>%
-  #   mutate(var_treat = "CB-SB",
-  #          var_gmax = CB_var_gmax_s,
-  #          stand_var = var_gmax / max(var_gmax)) %>%
-  #   filter(PB_var_gmax_s == 0)
-  # 
-  # for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
-  #                    PB_var_gmax_s = sort(PB_vars))
[…]

### 2022-11-21 reports/manuscript/figures_main_ms_v1.R

@@ -62,7 +62,7 @@ plot_here <- plot_here %>%
          !(var_treat == "PB" & stand_var > 0.65),
          !(var_treat == "CB-SB" & stand_var > 1.00),
          !(var_treat == "CB-PB" & stand_var > 0.65),
-         !(var_treat == "SB-PB" & stand_var > 1.0),
+         !(var_treat == "SB-PB" & stand_var > 1.00),
          !(var_treat == "CB-SB-PB" & stand_var > 1.00))
 
 p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,

### 2022-11-22 reports/supplement/supplement_0.9.1.Rmd
update supplement

@@
 
-The following figures \@ref(fig:div-temp-meth1)-\@ref(fig:div-temp-meth5) show the effects of diversity with long to shorter wait times.
+The following figures \@ref(fig:div-temp-meth1)-\@ref(fig:div-temp-meth4) show the effects of diversity with long to shorter wait times.
 
@@
 When there was medium to high variation in only the phototrophic sulfur bacteria (PB), the strain dynamics deviated from the standard pattern: at low oxygen diffusivity, all three functional groups coexisted.
-Specifically, on the trajectory of decreasing oxygen diffusivity, cyanobacteria reappeared at low oxygen diffusivity after their collapse at medium oxygen diffusivity (medium variation in PB, Figure xy) or never collapsed (high variation in PB, Figure xy).
-On the trajectory of increasing oxygen diffusivity, cyanobacteria coexisted with the two groups of sulfur bacteria at low oxygen diffusivity, collapsed at medium levels of oxygen diffusivity, and then increased to sole dominance at the tipping point to the oxic state.
-
-The same pattern occurred for medium to high simultaneous variation in phototrophic sulfur bacteria and cyanobacteria, albeit only on the trajectory of increasing oxygen diffusivity (Figure xy).
+Specifically, on the trajectory of decreasing oxygen diffusivity, cyanobacteria reappeared at low oxygen diffusivity after their collapse (Figure \@ref(fig:PB-stabstat1)) or never fully collapsed (high variation in PB, Figure \@ref(fig:PB-stabstat2)).
+On the trajectory of increasing oxygen diffusivity, cyanobacteria coexisted with the two groups of sulfur bacteria at low oxygen diffusivity, collapsed at medium levels of oxygen diffusivity, and then increased to sole dominance at the tipping point to the oxic state (Figure \@ref(fig:PB-stabstat1)).
+
+The same pattern occurred for medium to high simultaneous variation in phototrophic sulfur bacteria and cyanobacteria, albeit only on the trajectory of increasing oxygen diffusivity (Figure \@ref(fig:CBPB-stabstat3)).
 On the trajectory of decreasing oxygen diffusivity, cyanobacteria dominated over the entire gradient of oxygen diffusivity, such that effects of PB diversity did not play out on this trajectory.
 
-The reason for coexistence of all three groups at low oxygen diffusivity was that the PB strain that dominated at low oxygen diffusivity (the least tolerant strain) lowered the sulfide concentrations to such low levels that cyanobacteria were able to grow.
-The higher the trait variation in PB, the higher the intrinsic growth rate of the least tolerant PB strain, and the higher its consumption of sulfide.
+The reason for coexistence of all three groups at low oxygen diffusivity is likely that the PB strain that dominated at low oxygen diffusivity (the least tolerant strain) lowered the sulfide concentrations to such low levels that cyanobacteria were able to grow.
+The higher the trait variation in PB, the higher the maximum growth rate of the least tolerant PB strain, and the higher its consumption of sulfide.
 Consequently, moderate variation in PB lowered the sulfide concentration such that the tipping point from anoxic to oxic occurred earlier (as discussed in the previous section), and medium to high variation in PB lowered the sulfide concentration even further such that cyanobacteria were able to grow and coexist with the two groups of sulfur bacteria at low oxygen diffusivity.
 
-At intermediate levels of oxygen diffusivities, the cyanobacteria were usually excluded (Figure xy).
+At intermediate levels of oxygen diffusivities, the cyanobacteria were excluded (Figure \@ref(fig:PB-stabstat1)).
 We speculate that this might be associated with the increase in sulfide prior to the collapse of the phototrophic sulfur bacteria.
-This increase in sulfide occurred simultaneously with turnover to PB strains with lower intrinsic growth rate and with a decline in PB density; these two processes likely resulted in less consumption of sulfide.
-
-Owen, please add here 3 figures that match the text above:
-
-```{r echo = FALSE}
-run_sims_this_section <- TRUE
-```
+This increase in sulfide occurred simultaneously with turnover to PB strains with lower maximum growth rate and with a decline in PB density; these two processes likely resulted in less consumption of sulfide.
 
 ```{r}
-nine_strains <- readRDS(here("data",
-                         microxanox_version_path,
-                         "temporal_method", 
-                         "event_definition_2",
-                          "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
-```
-
-(1) medium variation in only PB showing coexistence of all groups at low ox diff,
-
-```{r  eval = run_sims_this_section, echo = FALSE}
-
-nine_strain_one <- filter(nine_strains,
+wait_time <- "1e+06"
+ss_9s <- readRDS(here::here("data",
+                            microxanox_version_path, 
+                            "temporal_method",
+                            "event_definition_2",
+                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+
+max_CB_var_gmax <- max(ss_9s$CB_var_gmax_s)
+max_SB_var_gmax <- max(ss_9s$SB_var_gmax_s)
+max_PB_var_gmax <- max(ss_9s$PB_var_gmax_s)
+
+ss_9s <- ss_9s %>%
+  mutate(standvar_CB_gmax = CB_var_gmax_s / max_CB_var_gmax,
+         standvar_SB_gmax = SB_var_gmax_s / max_SB_var_gmax,
+         standvar_PB_gmax = PB_var_gmax_s / max_PB_var_gmax)
+```
+
+(ref:PB-stabstat1) Coexistence of all three groups at low oxygen diffusivities when only PB contains strain variation, and the amount of strain variation is moderate to high.
+This example is when the standardised amount of trait variation is 0.74 (0 being no variation, and 1 being the maximum amount in any simulation.)
+
+```{r PB-stabstat1, echo = FALSE,  include=TRUE, fig.cap='(ref:PB-stabstat1)', fig.height=10, fig.width=8, fig.align="center"}
+this_dat <- ss_9s %>%
+  filter(
     CB_var_gmax_s == 0,
+    SB_var_gmax_s == 0
+  )
+this_dat <- this_dat[order(this_dat$PB_var_gmax_s), ]
+which_one <- 15
+#print(paste0("Standardised level of variation = ",
+#round(this_dat$standvar_PB_gmax[this_one],2)))
+fig_state_vs_o2diff_sidebyside_alternative(this_dat[which_one,])
+```
+
+(ref:PB-stabstat2) High trait variation in only the PB group results in coexistence of all groups at low oxygen diffusivity levels (as in Figure \@ref(fig:PB-stabstat1)) and also no collapse in CB abundance in the decreasing oxygen diffusivity trajectory.
+This example is when the standardised amount of trait variation is 0.95 (0 being no variation, and 1 being the maximum amount in any simulation.)
+
+```{r PB-stabstat2, echo = FALSE,  include=TRUE, fig.cap='(ref:PB-stabstat2)', fig.height=10, fig.width=8, fig.align="center"}
+which_one <- 19
+#print(paste0("Standardised level of variation = ",
+#round(this_dat$standvar_PB_gmax[this_one],2)))
+fig_state_vs_o2diff_sidebyside_alternative(this_dat[which_one,])
+```
+
+(ref:CBPB-stabstat3) Stable states when there is high trait variation in both CB and PB groups.
+This example is when the standardised amount of trait variation is 0.95 (0 being no variation, and 1 being the maximum amount in any simulation.)
+
+```{r CBPB-stabstat3, echo = FALSE,  include=TRUE, fig.cap='(ref:CBPB-stabstat3)', fig.height=10, fig.width=8, fig.align="center"}
+this_dat <- ss_9s %>%
+  filter(
     SB_var_gmax_s == 0,
-       abs(PB_var_gmax_s - 0.064819946) < 0.001)
-
-parameter <- nine_strain_one$parameter[[1]]
-parameter$strain_parameter <- nine_strain_one$pars[[1]]
-#parameter$strain_parameter <- ss_result$pars[[1]]
-total_initial_abundances <- 10^5
-parameter <- set_temporal_ssfind_initial_state(parameter,
-                                               total_initial_abundances,
-                                               total_initial_abundances,
-                                               total_initial_abundances)
-parameter$log10a_series <- c(-7, -7)
-wait_time <-  1e5
-parameter$sim_duration <- wait_time * length(parameter$log10a_series)
-parameter$sim_sample_interval <- 10
-#parameter$sim_duration
-test1 <- run_simulation(parameter)
-
-```
-
-(ref:PB-dyn1) Temporal dynamics of an ecosystem with a , the same one as in Figure \@ref(fig:max-tol3) simulated with constant $log_{10}$ oxygen diffusivity of -7.
-
-```{r PB-dyn1, echo = FALSE,  include=TRUE, fig.cap='(ref:PB-dyn1)', fig.height=10, fig.width=8, fig.align="center"}
-p <- plot_dynamics(test1)
-p[[1]] <- p[[1]] + 
-  xlab(NULL) + 
-  ylab(expression(log[10](density)~(cells~L^{-1}))) +
-  theme_bw()
-p[[2]] <- p[[2]] + 
-  xlab(NULL) + 
-  ylab(expression(log[10](density)~(cells~L^{-1}))) +
-  theme_bw()
-p[[3]] <- p[[3]] + 
-  xlab(NULL) + 
-  ylab(expression(log[10](density)~(cells~L^{-1}))) +
-  theme_bw()
-p[[4]]$data <- p[[4]]$data %>% 
-  dplyr::filter(species != "a")
-p[[4]]$data$species <- p[[4]]$data$species %>%
-  dplyr::recode(SO = "Oxidised sulfur", O = "Oxygen", SR = "Sulfide", P = "Phosphorus")
-p[[4]] <- p[[4]] + 
-  xlab("time (h)") + 
-  ylab(expression(log[10](concentration)~(µM))) + 
-  labs(colour = "substrate") +
-  theme_bw()
-
-p
-```
-
-(2) high variation in only PB showing coexistence of all groups at low ox diff and CB never collapsing on the decreasing ox diff trajectory,
-
-(3) high variation in both CB and PB.
+    abs(standvar_CB_gmax - standvar_PB_gmax) < 0.00001
+  )
+this_dat <- this_dat[order(this_dat$CB_var_gmax_s), ]
+which_one <- 19
+#print(paste0("Standardised level of variation = ",
+#round(this_dat$standvar_PB_gmax[this_one],2)))
+fig_state_vs_o2diff_sidebyside_alternative(this_dat[which_one,])
+```
 
@@
 
-In the main text we show that trait variation can affect resilience.
+In the main text we show that trait variation (functional diversity) can affect resilience.
 In this supplementary section, we discuss the mechanism(s) underlying the observed diversity effects.
@@
 Research about the relationship between biodiversity and ecosystem functioning has identified two major mechanisms by which diversity affects ecosystem functioning: the selection/sampling effect and the complementarity effect (Loreau & Hector 2001).
-The sampling effect occurs when more diverse communities have higher functioning because they have a higher probability of containing the best-performing species, i.e.
-the diversity effect is driven by only one (or few) species (Cardinale et al.
+The sampling effect occurs when more diverse communities have higher functioning because they have a higher probability of containing the best-performing species, and when only one (or few) of the species in a community determine the community and ecosystem level properties, such as biomass production or stability (Cardinale et al.
 2011).
 In contrast, the complementarity effect occurs when higher ecosystem functioning in more diverse communities is due to niche differences or positive interactions among species, i.e.
-the diversity effect is driven by many species (Cardinale et al.
+the diversity effect is driven by combinations of the species in a community (Cardinale et al.
 2011).
@@
 We investigated if the diversity effects observed in our study were in line with the sampling effect, that is, driven entirely by the presence of the most tolerant strain or if other strains played a role as well.
-To this end, we ran additional simulations where functional groups contained only the strain with greatest tolerance (which also necessarily had the lowest maximum growth rate).
+To this end, we ran additional simulations where functional groups contained only the strain with greatest tolerance (which due to the tradeoff also had the lowest maximum growth rate).
 That is, rather than increasing diversity we only increased tolerance of a single strain.
@@
 We describe and discuss these differences in detail in the sections below.
-Briefly, in these scenarios less tolerant strains did play a role because of their high intrinsic growth rates.
+Briefly, in these scenarios less tolerant strains did play a role because of their high maximum growth rates.
 Specifically, absence of SB strains with high growth rate led to reduced production of sulfide and therefore to coexistence with cyanobacteria at low oxygen diffusivity.
@@
 
-When SB contained multiple strains varying in growth rate (and tolerance) there were only two stable states (Figure \@ref(fig:max-tol2)), as was previously reported.
-When, however, only one SB strain with very high tolerance and low maximum growth rate was present, there were three stable states: the two previously found, and another state at low oxygen diffusivity where all three functional groups coexisted (Figure \@ref(fig:max-tol3)) – this never occurred when there were multiple SB strains varying in tolerance.
+When SB contained multiple strains varying in growth rate (and tolerance) there were two stable states at intermediate levels of oxygen diffusivity, only one stable state at low oxygen diffusivity with only sulfur bacteria, and with only one stable state at high oxygen diffusivity with high cyanobacterial density (Figure \@ref(fig:max-tol2)), as was previously reported.
+When, however, only one SB strain with very high tolerance and low maximum growth rate was present, the stable states change: at low oxygen diffusivity  all three functional groups coexisted (Figure \@ref(fig:max-tol3)) – this never occurred when there were multiple SB strains varying in tolerance.
 
 Apparently, at low oxygen diffusivity levels, the absence of SB strains with high growth rate precludes the formation of a stable state that does not include cyanobacteria.
-The most tolerant SB strain has a low intrinsic growth rate, which leads to less production of sulfide.
+The most tolerant SB strain has a low maximum growth rate, which leads to less production of sulfide.
 Presence of only the most tolerant SB strain therefore results in lower sulfide concentrations (Figure \@ref(fig:max-tol2) vs Figure \@ref(fig:max-tol3)), allowing growth of cyanobacteria at low oxygen diffusivity.
@@
 We speculate that this might be associated with the increase in sulfide at intermediate oxygen diffusivity, which might be due to the decline and collapse of PB and therefore reduced consumption of sulfide.
+
 (ref:max-tol2) Stable states found when there is variation among nine strains of SB and the amount of variation is high. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
@@
 
-In the SB-CB case, presence of only the most tolerant strain led to coexistence of all groups at low levels of oxygen diffusivity when trait values were moderately high (Figure xy) or to absence of alternate stable states and sole dominance of cyanobacteria when trait values were high (Figure \@ref(fig:max-tol5)).
-As discussed in the previous section, the low intrinsic growth rate of the most tolerant SB strain led to less production of sulfide such that SB could not exclude CB.
-
-Owen please add here a figure for medium trait values for the SB-CB case (only most tolerant strain), showing coexistence of all three groups at low ox diff.
+In the SB-CB case, the presence of only the most tolerant strain led to coexistence of all groups at low levels of oxygen diffusivity when trait values were moderately high (Figure \@ref(fig:max-tol55)) or to absence of alternate stable states and sole dominance of cyanobacteria when trait values were high (Figure \@ref(fig:max-tol5)).
+As discussed in the previous section, the low maximum growth rate of the most tolerant SB strain led to less production of sulfide such that SB could not exclude CB.
+
+(ref:max-tol55)  Stable states found when CB and SB each contain only the single most tolerant strain with moderate tolerance. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+
+```{r max-tol55, echo = FALSE,  include=TRUE, fig.cap='(ref:max-tol55)', fig.height=10, fig.width=8, fig.align="center"}
+#max_tol_one_CBSB <- filter(maxtolonly_strains,
+#       abs(CB_var_gmax_s - 0.026592798) < 0.001,
+#       abs(SB_var_gmax_s - 0.079778395) < 0.001,
+#       PB_var_gmax_s == 0)
+max_tol_one_CBSB <- filter(maxtolonly_strains,
+       abs(CB_var_gmax_s - 0.023268699) < 0.001,
+       abs(SB_var_gmax_s - 0.069806096) < 0.001,
+       PB_var_gmax_s == 0)
+
+fig_state_vs_o2diff_sidebyside_alternative(max_tol_one_CBSB)
+```
 
@@
 
-Whereas medium to high diversity in only PB led to three states including one with coexistence of all three functional groups (Figure xy), presence of only the most tolerant PB strain led to only two stable states, namely the standard-pattern of either dominance of sulfur bacteria or of cyanobacteria (Figure xy).
-The most tolerant PB strain has a low intrinsic growth rate, leading to less consumption of sulfide and therefore to higher sulfide concentrations compared to a system that contains both slow- and fast-growing strains.
+Whereas medium to high diversity in only PB led to coexistence of all three functional groups at low oxygen diffusivity levels (Figure \@ref(fig:PB-stabstat4)), presence of only the most tolerant PB strain led to the standard-pattern of either dominance of sulfur bacteria or of cyanobacteria (Figure \@ref(fig:PB-stabstat5)).
+The most tolerant PB strain has a low maximum growth rate, leading to less consumption of sulfide and therefore to higher sulfide concentrations compared to a system that contains both slow- and fast-growing strains.
 Due to the higher sulfide concentrations in the system with only the most tolerant PB strain, cyanobacteria were not able to grow at low oxygen diffusivity levels.
 
-For the same reasons we found three states on the trajectory of increasing oxygen diffusivity for medium to high simultaneous trait variation in PB and CB but not for the corresponding tolerance manipulation (data not shown).
-
-Owen please add here two figures:
-(1) One for high trait variation in only PB showing coexistence of all three groups.
-(2) One for high tolerance in only PB (corresponding in trait values to the figure before) showing standard dynamics.
+For the same reasons we found a similar pattern on the trajectory of increasing oxygen diffusivity for medium to high simultaneous trait variation in PB and CB but not for the corresponding tolerance manipulation (data not shown).
+
+```{r}
+wait_time <- "1e+06"
+ss_9s <- readRDS(here::here("data",
+                            microxanox_version_path, 
+                            "temporal_method",
+                            "event_definition_2",
+                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+
+max_CB_var_gmax <- max(ss_9s$CB_var_gmax_s)
+max_SB_var_gmax <- max(ss_9s$SB_var_gmax_s)
+max_PB_var_gmax <- max(ss_9s$PB_var_gmax_s)
+
+ss_9s <- ss_9s %>%
+  mutate(standvar_CB_gmax = CB_var_gmax_s / max_CB_var_gmax,
+         standvar_SB_gmax = SB_var_gmax_s / max_SB_var_gmax,
+         standvar_PB_gmax = PB_var_gmax_s / max_PB_var_gmax)
+```
+
+(ref:PB-stabstat4) Coexistence of all three groups at low oxygen diffusivities when only PB contains strain variation, and the amount of strain variation is moderate to high.
+This example is when the standardised amount of trait variation is 0.89 (0 being no variation, and 1 being the maximum amount in any simulation.)
+
+```{r PB-stabstat4, echo = FALSE,  include=TRUE, fig.cap='(ref:PB-stabstat4)', fig.height=10, fig.width=8, fig.align="center"}
+this_dat <- ss_9s %>%
+  filter(
+    CB_var_gmax_s == 0,
+    SB_var_gmax_s == 0
+  )
+this_dat <- this_dat[order(this_dat$PB_var_gmax_s), ]
+which_one <- 18
+#print(paste0("Standardised level of variation = ",
+#round(this_dat$standvar_PB_gmax[this_one],2)))
+fig_state_vs_o2diff_sidebyside_alternative(this_dat[which_one,])
+```
+
+```{r}
+wait_time <- "1e+06"
+ss_tol <- readRDS(here::here("data",
+                            microxanox_version_path, 
+                            "temporal_method",
+                            "event_definition_2",
+                            paste0("ss_data_-1strains_waittime", wait_time,
+                                   "_event_definition_2.RDS")))
+
+max_CB_var_gmax <- max(ss_tol$CB_var_gmax_s)
+max_SB_var_gmax <- max(ss_tol$SB_var_gmax_s)
+max_PB_var_gmax <- max(ss_tol$PB_var_gmax_s)
+
+ss_tol <- ss_tol %>%
+  mutate(standvar_CB_gmax = CB_var_gmax_s / max_CB_var_gmax,
+         standvar_SB_gmax = SB_var_gmax_s / max_SB_var_gmax,
+         standvar_PB_gmax = PB_var_gmax_s / max_PB_var_gmax)
+```
+
+(ref:PB-stabstat5) Dynamics when there is high tolerance in only PB, with this being the same tolerance level as the most tolerant strain in Figure \@ref(fig:PB-stabstat4) immediately above.
+
+```{r PB-stabstat5, echo = FALSE,  include=TRUE, fig.cap='(ref:PB-stabstat5)', fig.height=10, fig.width=8, fig.align="center"}
+this_dat <- ss_tol %>%
+  filter(
+    CB_var_gmax_s == 0,
+    SB_var_gmax_s == 0
+  )
+this_dat <- this_dat[order(this_dat$PB_var_gmax_s), ]
+which_one <- 18
+#print(paste0("Standardised level of variation = ",
+#round(this_dat$standvar_PB_gmax[this_one],2)))
+fig_state_vs_o2diff_sidebyside_alternative(this_dat[which_one,])
+```
 
@@
 
-At high levels of diversity vs.
-tolerance, resilience of the oxic state is greater when in each of the three functional groups only the most tolerant strain is present rather than when there is variation in strain tolerance within groups.
-It is not entirely clear why this effect occurs only in this combination.
+At high levels of diversity / high levels of tolerance, resilience of the oxic state is greater in the tolerance than diversity manipulation.
+We have shown that low tolerance sulfur strains can be implicated in the oxic to anoxic transition (section \@ref(SB2))
 

### 2022-11-24 reports/supplement/supplement_0.9.1.Rmd

@@
 Research about the relationship between biodiversity and ecosystem functioning has identified two major mechanisms by which diversity affects ecosystem functioning: the selection/sampling effect and the complementarity effect (Loreau & Hector 2001).
-The sampling effect occurs when more diverse communities have higher functioning because they have a higher probability of containing the best-performing species, and when only one (or few) of the species in a community determine the community and ecosystem level properties, such as biomass production or stability (Cardinale et al.
+The sampling effect occurs when more diverse communities have higher functioning because they have a higher probability of containing a high performing species, and when only one (or few) of the species in a community determine the community and ecosystem level properties, such as biomass production or stability.
+In this case the observed effect of diversity is driven by only one (or few) species (Cardinale et al.
 2011).

### 2022-11-24 reports/supplement/supplement_0.9.1.Rmd
changes to supplement

@@
 
-Growth of cyanobacteria depended on one substrate (phosphorus), whereas growth of sulfate-reducing bacteria (SB) and phototrophic sulfur bacteria (PB) depended on two substrates (phosphorus and oxidised sulfur for SB, and phosphorus and sulfide for PB).
-
-Inhibition of growth by a substrate was modelled with the Haldane equation:
+Inhibition of growth by a substrate was modeled with the Haldane equation:
 
@@
 
-(ref:temp-meth2) Stable states found with the **temporal method**. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+(ref:temp-meth2) Stable states found with the **temporal method**.
+The left column of panels refers to the stable state when oxygen diffusivity is at first high (favouring the oxic state).
+The right column refers to when oxygen diffusivity is at first low (favouring the anoxic state).
+Points (which sometimes are so close as to appear as thick lines) show the stable state at the end of each period of constant oxygen diffusivity.
+Thin lines are for visualisation only, and join the points.
+Grey arrows show the oxygen diffusivity at which the system flips, and the direction of the flip.
+The length of the grey arrows is without meaning.
 
@@
 The thick grey vertical lines at -8 and 0 on the x-axis show the extent of the oxygen diffusivity gradient investigated in the simulations.
+Data is missing in panels e, and i, when patterns of coexistence were atypical of the classical pattern shown in Figure 1a of the main text (e.g.
+when cyanobacteria coexisted with sulfur bacteria at low oxygen diffusivities).
 **Right column of panels**: The effect size of trait variation on resilience, with positive values on the y-axis indicating that diversity has increased resilience.
@@
 As shown in Figure \@ref(fig:div-temp-eventdef1), the results with this floor abundance are similar as when 1 was added every 1,000 hours.
-Note that a coarser gradient of trait variation was used, hence the saw-tooth patterns.
-A further difference is the large decrease in resilience of the anoxic to oxic transition above moderate levels of diversity in the SB and CB-SB treatments.
-This pattern can also occur with addition of 1 abundance unit (e.g., see Figure \@ref(fig:div-temp-meth3)), and is discussed in the section that concerns this below (section [SB diversity effects]).
 
@@
 
-## Example of transient dynamics at 1e6 hours
+## 1e6 vs 2e6 hours wait time
 
@@
 E.g.
-in the region of strain replacement in the sulfate-reducing bacteria recovery trajectory there is difference in strain abundances at 1'000'000 and 2'000'000 hours.
+in the region of strain replacement in the sulfate-reducing bacteria there is difference in strain abundances at 1'000'000 and 2'000'000 hours.
 However, the position of the tipping points (which were calculated from the total SB abundance) and the substrate concentrations did not differ between 1'000'000 and 2'000'000 hours.
@@
 This effect was particularly pronounced when there was high variation in only SB or in SB-CB: here, simulations with two or three strains led to dramatically lower resilience of the anoxic state than simulations with six or nine strains.
-We believe that this effect is due to the greater distance in trait space between strains in simulations with two or three strains than in simulations with more strains (also see Section 5).
+We believe that this effect is due to the greater distance in trait space between strains in simulations with two or three strains than in simulations with more strains (also see Section 9).
 
@@
 Increased CB diversity causes a slight decrease in the resilience of the anoxic state.
-The following two figures show the state responses to oxygen diffusivity with low Figure \@ref(fig:ss-CB-only1) and high Figure \@ref(fig:ss-CB-only2) levels of CB diversity.
+The following two figures show the state responses to oxygen diffusivity with low (Figure \@ref(fig:ss-CB-only1)) and high (Figure \@ref(fig:ss-CB-only2)) levels of CB diversity.
 The difference in the position of the anoxic to oxic tipping point is small.
@@
 
-We showed above that wait times of 1e5 (Figure \@ref(fig:div-temp-meth2)) and 1e4 (Figure \@ref(fig:div-temp-meth4)) produce qualitatively and often quantitatively very similar results to those for wait times of 1e6 (Figure \@ref(fig:div-temp-meth1)).
-There is, however, a notable difference when there is variation in only SB, or in CB-SB with wait times of 1e4 (Figure \@ref(fig:div-temp-meth4)).
+We showed above that wait times of 1e5 (Figure \@ref(fig:div-temp-meth2)) and 1e4 (Figure \@ref(fig:div-temp-meth3)) produce qualitatively and often quantitatively very similar results to those for wait times of 1e6 (Figure \@ref(fig:div-temp-meth1)).
+There is, however, a notable difference when there is variation in only SB, or in CB-SB with wait times of 1e4 (Figure \@ref(fig:div-temp-meth3)).
 Here, moderate increases in diversity have the same effect as with wait times of 1e6.
@@
 The transition from anoxic to oxic occurs at approximately $log_{10}$(oxygen diffusivity) = `r round(aO_flip_sim1, 2)`.
-All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+All other aspects are the same as in Figure \@ref(fig:ss-temp-meth3).
 
@@
 The transition from anoxic to oxic occurs at approximately $log_{10}$(oxygen diffusivity) = `r round(aO_flip_sim2, 2)`.
-All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+All other aspects are the same as in Figure \@ref(fig:ss-temp-meth3).
 
@@
 When there was medium to high variation in only the phototrophic sulfur bacteria (PB), the strain dynamics deviated from the standard pattern: at low oxygen diffusivity, all three functional groups coexisted.
-Specifically, on the trajectory of decreasing oxygen diffusivity, cyanobacteria reappeared at low oxygen diffusivity after their collapse (Figure \@ref(fig:PB-stabstat1)) or never fully collapsed (high variation in PB, Figure \@ref(fig:PB-stabstat2)).
-On the trajectory of increasing oxygen diffusivity, cyanobacteria coexisted with the two groups of sulfur bacteria at low oxygen diffusivity, collapsed at medium levels of oxygen diffusivity, and then increased to sole dominance at the tipping point to the oxic state (Figure \@ref(fig:PB-stabstat1)).
+Specifically, on the trajectory of decreasing oxygen diffusivity, cyanobacteria reappeared at low oxygen diffusivity after their collapse (medium variation in PB, Figure \@ref(fig:PB-stabstat1)) or never fully collapsed (high variation in PB, Figure \@ref(fig:PB-stabstat2)).
+On the trajectory of increasing oxygen diffusivity, cyanobacteria coexisted with the two groups of sulfur bacteria at low oxygen diffusivity, collapsed at medium levels of oxygen diffusivity, and then increased to sole dominance at the tipping point to the oxic state (Figure \@ref(fig:PB-stabstat1), Figure \@ref(fig:PB-stabstat2)).
 

### 2022-11-24 reports/supplement/supplement_0.9.1.Rmd
changes supplement

@@
 
-When SB contained multiple strains varying in growth rate (and tolerance) there were two stable states at intermediate levels of oxygen diffusivity, only one stable state at low oxygen diffusivity with only sulfur bacteria, and with only one stable state at high oxygen diffusivity with high cyanobacterial density (Figure \@ref(fig:max-tol2)), as was previously reported.
+When SB contained multiple strains varying in growth rate (and tolerance) there were two stable states at intermediate levels of oxygen diffusivity, only one stable state at low oxygen diffusivity with only sulfur bacteria, and only one stable state at high oxygen diffusivity with high cyanobacterial density (Figure \@ref(fig:max-tol2)), as was previously reported.
 When, however, only one SB strain with very high tolerance and low maximum growth rate was present, the stable states change: at low oxygen diffusivity  all three functional groups coexisted (Figure \@ref(fig:max-tol3)) – this never occurred when there were multiple SB strains varying in tolerance.
@@
 
-(ref:max-tol2) Stable states found when there is variation among nine strains of SB and the amount of variation is high. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+(ref:max-tol2) Stable states found when there is variation among nine strains of SB and the amount of variation is high. All other aspects are the same as in Figure \@ref(fig:ss-temp-meth3).
 
@@
 (ref:max-tol3) Stable states found when SB contained only the most tolerant strain, with trait values corresponding with the diversity level of the previous figure.
-All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+All other aspects are the same as in Figure \@ref(fig:ss-temp-meth3).
 
@@
 
-In the SB-CB case, the presence of only the most tolerant strain led to coexistence of all groups at low levels of oxygen diffusivity when trait values were moderately high (Figure \@ref(fig:max-tol55)) or to absence of alternate stable states and sole dominance of cyanobacteria when trait values were high (Figure \@ref(fig:max-tol5)).
+In the CB-SB case, the presence of only the most tolerant strain led to coexistence of all groups at low levels of oxygen diffusivity when trait values were moderately high (Figure \@ref(fig:max-tol55)) or to absence of alternate stable states and sole dominance of cyanobacteria when trait values were high (Figure \@ref(fig:max-tol5)).
 As discussed in the previous section, the low maximum growth rate of the most tolerant SB strain led to less production of sulfide such that SB could not exclude CB.
 
-(ref:max-tol55)  Stable states found when CB and SB each contain only the single most tolerant strain with moderate tolerance. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+(ref:max-tol55)  Stable states found when CB and SB each contain only the single most tolerant strain with moderate tolerance. All other aspects are the same as in Figure \@ref(fig:ss-temp-meth3).
 
@@
 
-(ref:max-tol5)  Stable states found when CB and SB each contain only the single most tolerant strain with trait values corresponding with the diversity level of the previous figure.
-All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+(ref:max-tol5)  Stable states found when CB and SB each contain only the single most tolerant strain with high tolerance. All other aspects are the same as in Figure \@ref(fig:ss-temp-meth3).
 
@@
 
-(ref:PB-stabstat4) Coexistence of all three groups at low oxygen diffusivities when only PB contains strain variation, and the amount of strain variation is moderate to high.
+(ref:PB-stabstat4) Coexistence of all three groups at low oxygen diffusivities when only PB contains strain variation, and the amount of strain variation is medium to high.
 This example is when the standardised amount of trait variation is 0.89 (0 being no variation, and 1 being the maximum amount in any simulation.)
@@
 
-(ref:PB-stabstat5) Dynamics when there is high tolerance in only PB, with this being the same tolerance level as the most tolerant strain in Figure \@ref(fig:PB-stabstat4) immediately above.
+(ref:PB-stabstat5) Dynamics when PB contain only the most tolerant strain, with this being the same tolerance level as the most tolerant strain in Figure \@ref(fig:PB-stabstat4) immediately above.
 
@@
 
-(ref:max-tol6) Stable states found with nine strains of CB-SB-PB and high diversity. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+(ref:max-tol6) Stable states found with nine strains of CB-SB-PB and high diversity. All other aspects are the same as in Figure \@ref(fig:ss-temp-meth3).
 
@@
 (ref:max-tol7) Stable states found with the single most tolerant CB strain, SB strain, and PB strain, with trait values corresponding with the diversity level in the previous figure.
-All other aspects are the same as in Figure \@ref(fig:repl-meth2).
+All other aspects are the same as in Figure \@ref(fig:ss-temp-meth3).
 
@@
 ```
-
-When two functional groups varied in traits, the effects of trait variation were additive when one of the groups had no diversity effect on a tipping point but non-additive when both groups had diversity effects on a tipping point (Fig.
-\@ref(fig:fig-add-linear) a-f).
-High trait variation in cyanobacteria and sulfate-reducing bacteria caused the oxic-anoxic tipping point to occur at lower oxygen diffusivity than expected assuming additivity of the individual effects of diversity in these two groups (Fig.
-\@ref(fig:fig-add-linear)d).
-When the two groups of sulfur bacteria varied in traits, the anoxic-oxic tipping point occurred at higher oxygen diffusivity than expected by additivity (Fig.
-\@ref(fig:fig-add-linear)f).
-
-When all three groups varied in traits, only the diversity effect in phototrophic sulfur bacteria on the oxic-anoxic tipping point was additive; all other effects were non-additive, especially at higher trait variation (Fig.
-\@ref(fig:fig-add-linear)g-i).
 

### 2022-11-24 reports/supplement/supplement_0.9.1.Rmd
changes supplement

@@
 
-(ref:PB-stabstat1) Coexistence of all three groups at low oxygen diffusivities when only PB contains strain variation, and the amount of strain variation is moderate to high.
+(ref:PB-stabstat1) Coexistence of all three groups at low oxygen diffusivities when only PB contains strain variation, and the amount of strain variation is medium to high.
 This example is when the standardised amount of trait variation is 0.74 (0 being no variation, and 1 being the maximum amount in any simulation.)

### 2022-11-24 reports/supplement/supplement_0.9.1.Rmd
get rid of some flip arrows

--- 2022-11-24 reports/supplement/supplement_0.9.1.Rmd
@@
 
-Inhibition of growth by a substrate was modeled with the Haldane equation:
+Growth of cyanobacteria depended on one substrate (phosphorus), whereas growth of sulfate-reducing bacteria (SB) and phototrophic sulfur bacteria (PB) depended on two substrates (phosphorus and oxidised sulfur for SB, and phosphorus and sulfide for PB).
+
+Inhibition of growth by a substrate was modelled with the Haldane equation:
 
@@
 
-(ref:temp-meth2) Stable states found with the **temporal method**.
-The left column of panels refers to the stable state when oxygen diffusivity is at first high (favouring the oxic state).
-The right column refers to when oxygen diffusivity is at first low (favouring the anoxic state).
-Points (which sometimes are so close as to appear as thick lines) show the stable state at the end of each period of constant oxygen diffusivity.
-Thin lines are for visualisation only, and join the points.
-Grey arrows show the oxygen diffusivity at which the system flips, and the direction of the flip.
-The length of the grey arrows is without meaning.
+(ref:temp-meth2) Stable states found with the **temporal method**. All other aspects are the same as in Figure \@ref(fig:repl-meth2).
 
@@
 The thick grey vertical lines at -8 and 0 on the x-axis show the extent of the oxygen diffusivity gradient investigated in the simulations.
-Data is missing in panels e, and i, when patterns of coexistence were atypical of the classical pattern shown in Figure 1a of the main text (e.g.
-when cyanobacteria coexisted with sulfur bacteria at low oxygen diffusivities).
 **Right column of panels**: The effect size of trait variation on resilience, with positive values on the y-axis indicating that diversity has increased resilience.
@@
 As shown in Figure \@ref(fig:div-temp-eventdef1), the results with this floor abundance are similar as when 1 was added every 1,000 hours.
+Note that a coarser gradient of trait variation was used, hence the saw-tooth patterns.
+A further difference is the large decrease in resilience of the anoxic to oxic transition above moderate levels of diversity in the SB and CB-SB treatments.
+This pattern can also occur with addition of 1 abundance unit (e.g., see Figure \@ref(fig:div-temp-meth3)), and is discussed in the section that concerns this below (section [SB diversity effects]).
 
@@
 
-## 1e6 vs 2e6 hours wait time
+## Example of transient dynamics at 1e6 hours
 
@@
 E.g.
-in the region of strain replacement in the sulfate-reducing bacteria there is difference in strain abundances at 1'000'000 and 2'000'000 hours.
+in the region of strain replacement in the sulfate-reducing bacteria recovery trajectory there is difference in strain abundances at 1'000'000 and 2'000'000 hours.
 However, the position of the tipping points (which were calculated from the total SB abundance) and the substrate concentrations did not differ between 1'000'000 and 2'000'000 hours.
@@
 This effect was particularly pronounced when there was high variation in only SB or in SB-CB: here, simulations with two or three strains led to dramatically lower resilience of the anoxic state than simulations with six or nine strains.
-We believe that this effect is due to the greater distance in trait space between strains in simulations with two or three strains than in simulations with more strains (also see Section 9).
+We believe that this effect is due to the greater distance in trait space between strains in simulations with two or three strains than in simulations with more strains (also see Section 5).
 
@@
 Increased CB diversity causes a slight decrease in the resilience of the anoxic state.
-The following two figures show the state responses to oxygen diffusivity with low (Figure \@ref(fig:ss-CB-only1)) and high (Figure \@ref(fig:ss-CB-only2)) levels of CB diversity.
+The following two figures show the state responses to oxygen diffusivity with low Figure \@ref(fig:ss-CB-only1) and high Figure \@ref(fig:ss-CB-only2) levels of CB diversity.
 The difference in the position of the anoxic to oxic tipping point is small.
@@
 
-fig_state_vs_o2diff_sidebyside_alternative(only_CB_variable[20,])
+fig_state_vs_o2diff_sidebyside_alternative_leftfliponly(only_CB_variable[20,])
+
+#ss_result <- only_CB_variable[20,]
 
@@
 
-We showed above that wait times of 1e5 (Figure \@ref(fig:div-temp-meth2)) and 1e4 (Figure \@ref(fig:div-temp-meth3)) produce qualitatively and often quantitatively very similar results to those for wait times of 1e6 (Figure \@ref(fig:div-temp-meth1)).
-There is, however, a notable difference when there is variation in only SB, or in CB-SB with wait times of 1e4 (Figure \@ref(fig:div-temp-meth3)).
+We showed above that wait times of 1e5 (Figure \@ref(fig:div-temp-meth2)) and 1e4 (Figure \@ref(fig:div-temp-meth4)) produce qualitatively and often quantitatively very similar results to those for wait times of 1e6 (Figure \@ref(fig:div-temp-meth1)).
+There is, however, a notable difference when there is variation in only SB, or in CB-SB with wait times of 1e4 (Figure \@ref(fig:div-temp-meth4)).
 Here, moderate increases in diversity have the same effect as with wait times of 1e6.
@@
 The transition from anoxic to oxic occurs at approximately $log_{10}$(oxygen diffusivity) = `r round(aO_flip_sim1, 2)`.
-All other aspects are the same as in Figure \@ref(fig:ss-temp-meth3).
+All other aspects are the same as in Figure \@ref(fig:repl-meth2).
 
@@
 The transition from anoxic to oxic occurs at approximately $log_{10}$(oxygen diffusivity) = `r round(aO_flip_sim2, 2)`.
-All other aspects are the same as in Figure \@ref(fig:ss-temp-meth3).
+All other aspects are the same as in Figure \@ref(fig:repl-meth2).
 
@@
 When there was medium to high variation in only the phototrophic sulfur bacteria (PB), the strain dynamics deviated from the standard pattern: at low oxygen diffusivity, all three functional groups coexisted.
-Specifically, on the trajectory of decreasing oxygen diffusivity, cyanobacteria reappeared at low oxygen diffusivity after their collapse (medium variation in PB, Figure \@ref(fig:PB-stabstat1)) or never fully collapsed (high variation in PB, Figure \@ref(fig:PB-stabstat2)).
-On the trajectory of increasing oxygen diffusivity, cyanobacteria coexisted with the two groups of sulfur bacteria at low oxygen diffusivity, collapsed at medium levels of oxygen diffusivity, and then increased to sole dominance at the tipping point to the oxic state (Figure \@ref(fig:PB-stabstat1), Figure \@ref(fig:PB-stabstat2)).
+Specifically, on the trajectory of decreasing oxygen diffusivity, cyanobacteria reappeared at low oxygen diffusivity after their collapse (Figure \@ref(fig:PB-stabstat1)) or never fully collapsed (high variation in PB, Figure \@ref(fig:PB-stabstat2)).
+On the trajectory of increasing oxygen diffusivity, cyanobacteria coexisted with the two groups of sulfur bacteria at low oxygen diffusivity, collapsed at medium levels of oxygen diffusivity, and then increased to sole dominance at the tipping point to the oxic state (Figure \@ref(fig:PB-stabstat1)).
 
@@
 #round(this_dat$standvar_PB_gmax[this_one],2)))
-fig_state_vs_o2diff_sidebyside_alternative(this_dat[which_one,])
+fig_state_vs_o2diff_sidebyside_alternative_leftfliponly(this_dat[which_one,])
 ```
@@
 
-fig_state_vs_o2diff_sidebyside_alternative(max_tol_one_CBSB)
+fig_state_vs_o2diff_sidebyside_alternative_nofliparrows(max_tol_one_CBSB)
 ```

### 2022-11-24 reports/animations/report.Rmd
update animation report

@@
 author: "Owen Petchey"
-date: "6/1/2022"
+date: "`r format(Sys.time(), '%d %B, %Y')`"
 output:

### 2022-11-25 reports/old/summary1.Rmd

---
title: "Summary1"
author: "Owen Petchey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r}
library(tidyverse)
library(here)

library(microxanox)
if (packageVersion("microxanox") < package_version("0.3.0")) {
  stop("microxanox version needs to be at least 0.3.0!")
}
library(patchwork)
source(here("R/various_useful_functions.r"))
```

```{r}
stab_data_3s <- readRDS(here("experiments/3_strains/data/stab_data_1e6_x2x6_factorial.RDS")) %>%
  mutate(num_strains = 3) %>%
  select(1:6, 11:25)

stab_data_6s <- readRDS(here("experiments/6_strains/data/stab_data_1e6_x2x6_factorial.RDS")) %>%
  mutate(num_strains = 6) %>%
  select(1:6, 11:25)

stab_data_9s <- readRDS(here("experiments/9_strains/data/small_stab_data_1e6_x2x6_factorial.RDS"))

stab_data <- stab_data_3s %>%
  bind_rows(stab_data_6s) %>%
  bind_rows(stab_data_9s)

```

```{r eval = plot_ss_results}
CB_vars <- unique(stab_data$CB_var_gmax_s)
SB_vars <- unique(stab_data$SB_var_gmax_s)

CB_stab_data <- stab_data %>%
  filter(SB_var_gmax_s == 0) %>%
  mutate(var_treat = "CB",
         var_gmax = CB_var_gmax_s)

SBPB_stab_data <- stab_data %>%
  filter(CB_var_gmax_s == 0) %>%
  mutate(var_treat = "SB-PB",
         var_gmax = SB_var_gmax_s)

for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
                     SB_var_gmax_s = sort(SB_vars))
CBSBPB_stab_data <- stab_data %>%
  right_join(for_join) %>%
  mutate(var_treat = "CB-SB-PB",
         var_gmax = CB_var_gmax_s)

all_stab_results <- CB_stab_data %>%
  bind_rows(SBPB_stab_data) %>%
#  bind_rows(results3) %>%
 # bind_rows(results4) %>%
  bind_rows(CBSBPB_stab_data)

all_stab_results <- all_stab_results %>%
    mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB-PB", "CB-SB-PB")))

#saveRDS(all_stab_results, here("experiments/experiment summary/all_stab.RDS"))

#all_stab_results <- readRDS(here("experiments/experiment summary/all_stab.RDS"))
```

### Log transformed

```{r eval = plot_ss_results}
all_stab_results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax, y = hyst_range_log, col=var_treat,
             shape = as_factor(num_strains))) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

all_stab_results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = num_strains, y = hyst_range_log)) +
  facet_grid(var_gmax ~ var_treat, scales = "fixed") +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O",
         sim_length == 1e6) %>%
  ggplot(aes(x = var_gmax,
             ymin = hyst_min_log,
             ymax = hyst_max_log,
             fill=var_treat)) +
  geom_ribbon(alpha = 0.5) +
  facet_grid(num_strains ~ var_treat) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )

##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
stab_data %>%
  filter(Species == "O",
         sim_length == 1e6) %>%
  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range_log, col = hyst_range_log)) +
  geom_point(size = 3)

##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)

stab_data %>%
  filter(Species == "O",
         sim_length == 1e6) %>%
  ggplot(aes(x = CB_var_gmax_s, y = hyst_range_log, col = as.factor(SB_var_gmax_s))) +
  geom_line(size = 2)
```

# Zoom in on an effect

```{r}

ss_data_3s <- readRDS(here("experiments/3_strains/data/ss_data_1e6_x2x6_factorial.RDS")) %>%
  filter(abs(CB_var_gmax_s - 0.023268699) < 0.000001 &
           abs(SB_var_gmax_s - 0.0698061) < 0.000001)

p1  <- plot_ss_result1(ss_data_3s,
                result_index = 1,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1

ss_data_6s <- readRDS(here("experiments/6_strains/data/ss_data_1e6_x2x6_factorial.RDS"))  %>%
  filter(abs(CB_var_gmax_s - 0.023268699) < 0.000001 &
           abs(SB_var_gmax_s - 0.0698061) < 0.000001)
p1  <- plot_ss_result1(ss_data_6s,
                result_index = 1,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1

ss_data_9s <- readRDS(here("experiments/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))  %>%
  filter(abs(CB_var_gmax_s - 0.023268699) < 0.000001 &
           abs(SB_var_gmax_s - 0.0698061) < 0.000001)
p1  <- plot_ss_result1(ss_data_9s,
                result_index = 1,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1

p_overlay1 <- plot_ss_result2(ss_data_3s$ss_res[[1]],
                             ss_data_6s$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay1

p_overlay1 <- plot_ss_result2(ss_data_3s$ss_res[[1]],
                             ss_data_9s$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay1

```

A O2 diff of around -5.2 we should be able to get bistability in the 3 strain system, and only anoxic in the 9 strain. At -1.55 we should be able to get bistability in the 3 strain system, but only oxic in the 9 strain.

```{r}

parameter <- new_runsim_parameter(
  dynamic_model = ss_data_3s$ss_by_a_N_result[[1]]$dynamic_model,
  event_definition = ss_data_3s$ss_by_a_N_result[[1]]$event_definition,
  event_interval = 100000,
  noise_sigma = ss_data_3s$ss_by_a_N_result[[1]]$noise_sigma,
  minimum_abundances = ss_data_3s$ss_by_a_N_result[[1]]$minimum_abundances,
  sim_duration = 1000000,
  sim_sample_interval = 100,
  strain_parameter = ss_data_3s$ss_by_a_N_result[[1]]$strain_parameter,
  log10a_series = c(NA, NA)
)
parameter$minimum_abundances["CB"] <- 10
parameter$minimum_abundances["SB"] <- 10
parameter$minimum_abundances["PB"] <- 10

parameter$strain_parameter$initial_state[grep("SB_", names(parameter$strain_parameter$initial_state))] <- parameter$strain_parameter$initial_state[grep("SB_", names(parameter$strain_parameter$initial_state))] / length(parameter$strain_parameter$initial_state[grep("SB_", names(parameter$strain_parameter$initial_state))])

parameter$strain_parameter$initial_state[grep("PB_", names(parameter$strain_parameter$initial_state))] <- parameter$strain_parameter$initial_state[grep("PB_", names(parameter$strain_parameter$initial_state))] / length(parameter$strain_parameter$initial_state[grep("PB_", names(parameter$strain_parameter$initial_state))])

parameter$log10a_series <- c(-5.2, -5.2)

## start with high CB abundance
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/nrow(ss_data_3s$ss_by_a_N_result[[1]]$strain_parameter$CB)
sim_res_3s <- run_simulation(parameter)
plot_dynamics(sim_res_3s)

## start with low CB abundance
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^0/nrow(ss_data_3s$ss_by_a_N_result[[1]]$strain_parameter$CB)
sim_res_3s <- run_simulation(parameter)
plot_dynamics(sim_res_3s)

```

```{r}

parameter <- new_runsim_parameter(
  dynamic_model = ss_data_9s$ss_by_a_N_result[[1]]$dynamic_model,
  event_definition = ss_data_9s$ss_by_a_N_result[[1]]$event_definition,
  event_interval = 100000,
  noise_sigma = ss_data_9s$ss_by_a_N_result[[1]]$noise_sigma,
  minimum_abundances = ss_data_9s$ss_by_a_N_result[[1]]$minimum_abundances,
  sim_duration = 1000000,
  sim_sample_interval = 100,
  strain_parameter = ss_data_9s$ss_by_a_N_result[[1]]$strain_parameter,
  log10a_series = c(NA, NA)
)

parameter$minimum_abundances["CB"] <- 10
parameter$minimum_abundances["SB"] <- 10
parameter$minimum_abundances["PB"] <- 10

parameter$strain_parameter$initial_state[grep("SB_", names(parameter$strain_parameter$initial_state))] <- parameter$strain_parameter$initial_state[grep("SB_", names(parameter$strain_parameter$initial_state))] / length(parameter$strain_parameter$initial_state[grep("SB_", names(parameter$strain_parameter$initial_state))])

parameter$strain_parameter$initial_state[grep("PB_", names(parameter$strain_parameter$initial_state))] <- parameter$strain_parameter$initial_state[grep("PB_", names(parameter$strain_parameter$initial_state))] / length(parameter$strain_parameter$initial_state[grep("PB_", names(parameter$strain_parameter$initial_state))])

parameter$log10a_series <- c(-5.2, -5.2)

## start with high CB abundance
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/nrow(ss_data_9s$ss_by_a_N_result[[1]]$strain_parameter$CB)
sim_res_9s <- run_simulation(parameter)
plot_dynamics(sim_res_9s)

## start with low CB abundance
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^0/nrow(ss_data_9s$ss_by_a_N_result[[1]]$strain_parameter$CB)
sim_res_9s <- run_simulation(parameter)
plot_dynamics(sim_res_9s)

```

At -1.55 we should be able to get bistability in the 3 strain system, but only oxic in the 9 strain.

```{r}

parameter <- new_runsim_parameter(
  dynamic_model = ss_data_3s$ss_by_a_N_result[[1]]$dynamic_model,
  event_definition = ss_data_3s$ss_by_a_N_result[[1]]$event_definition,
  event_interval = 100000,
  noise_sigma = ss_data_3s$ss_by_a_N_result[[1]]$noise_sigma,
  minimum_abundances = ss_data_3s$ss_by_a_N_result[[1]]$minimum_abundances,
  sim_duration = 1000000,
  sim_sample_interval = 100,
  strain_parameter = ss_data_3s$ss_by_a_N_result[[1]]$strain_parameter,
  log10a_series = c(NA, NA)
)
parameter$minimum_abundances["CB"] <- 10
parameter$minimum_abundances["SB"] <- 10
parameter$minimum_abundances["PB"] <- 10

parameter$strain_parameter$initial_state[grep("SB_", names(parameter$strain_parameter$initial_state))] <- parameter$strain_parameter$initial_state[grep("SB_", names(parameter$strain_parameter$initial_state))] / length(parameter$strain_parameter$initial_state[grep("SB_", names(parameter$strain_parameter$initial_state))])

parameter$strain_parameter$initial_state[grep("PB_", names(parameter$strain_parameter$initial_state))] <- parameter$strain_parameter$initial_state[grep("PB_", names(parameter$strain_parameter$initial_state))] / length(parameter$strain_parameter$initial_state[grep("PB_", names(parameter$strain_parameter$initial_state))])

parameter$log10a_series <- c(-1.6, -1.6)

## start with high CB abundance
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/nrow(ss_data_3s$ss_by_a_N_result[[1]]$strain_parameter$CB)
sim_res_3s <- run_simulation(parameter)
plot_dynamics(sim_res_3s)

## start with low CB abundance
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^0/nrow(ss_data_3s$ss_by_a_N_result[[1]]$strain_parameter$CB)
sim_res_3s <- run_simulation(parameter)
plot_dynamics(sim_res_3s)

```

```{r}

parameter <- new_runsim_parameter(
  dynamic_model = ss_data_9s$ss_by_a_N_result[[1]]$dynamic_model,
  event_definition = ss_data_9s$ss_by_a_N_result[[1]]$event_definition,
  event_interval = 100000,
  noise_sigma = ss_data_9s$ss_by_a_N_result[[1]]$noise_sigma,
  minimum_abundances = ss_data_9s$ss_by_a_N_result[[1]]$minimum_abundances,
  sim_duration = 1000000,
  sim_sample_interval = 100,
  strain_parameter = ss_data_9s$ss_by_a_N_result[[1]]$strain_parameter,
  log10a_series = c(NA, NA)
)

parameter$minimum_abundances["CB"] <- 10
parameter$minimum_abundances["SB"] <- 10
parameter$minimum_abundances["PB"] <- 10

parameter$strain_parameter$initial_state[grep("SB_", names(parameter$strain_parameter$initial_state))] <- parameter$strain_parameter$initial_state[grep("SB_", names(parameter$strain_parameter$initial_state))] / length(parameter$strain_parameter$initial_state[grep("SB_", names(parameter$strain_parameter$initial_state))])

parameter$strain_parameter$initial_state[grep("PB_", names(parameter$strain_parameter$initial_state))] <- parameter$strain_parameter$initial_state[grep("PB_", names(parameter$strain_parameter$initial_state))] / length(parameter$strain_parameter$initial_state[grep("PB_", names(parameter$strain_parameter$initial_state))])

parameter$log10a_series <- c(-1.6, -1.6)

## start with high CB abundance
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/nrow(ss_data_9s$ss_by_a_N_result[[1]]$strain_parameter$CB)
sim_res_9s <- run_simulation(parameter)
plot_dynamics(sim_res_9s)

## start with low CB abundance
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^0/nrow(ss_data_9s$ss_by_a_N_result[[1]]$strain_parameter$CB)
sim_res_9s <- run_simulation(parameter)
plot_dynamics(sim_res_9s)

```

### 2022-11-25 reports/old/testing/testing_temporal_method.Rmd

--- 2021-11-13 experiments/9_strains/9_strains.Rmd
@@
 ---
-title: "9 strains"
+title: "Testing temporal method"
 author: "Owen Petchey"
-date: "6/25/2021"
-output:
-  pdf_document: default
-  html_document:
-    keep_md: yes
+date: "11/24/2021"
+output: html_document
 ---
-
-This experiment supersedes all previous ones.
-It is a factorial manipulation of diversity of the three groups.
-It takes about 50 hours to run while using 12 cores.
 
@@
 
-## R
-
-```{r setup}
-
-# rm(list = ls())
-
-knitr::opts_knit$set(
-  progress = TRUE, 
-  verbose = FALSE, 
-  cache = TRUE
-)
-
-microxanox_release <- "0.3.0"
-
-#tmplib <- tempfile()
-#dir.create(tmplib)
-
-### From '?remotes::install_github`:
-# auth_token
-#   To install from a private repo, generate a personal access token (PAT) in
-#   "https://github.com/settings/tokens" and supply to this argument. This is
-#   safer than using a password because you can easily delete a PAT without
-#   affecting any others. Defaults to the GITHUB_PAT environment variable.
-
-# remotes::install_github(
-#   "opetchey/microxanox",
-#   ref = microxanox_release,
-#   # auth_token = "ENTER YOUR TOKEN or PROVED AS ENVIRONMENT VARIABLE",
-#   build_vignettes = FALSE,
-#   force = TRUE,
-#   upgrade = FALSE,
-#   lib = tmplib
-# )
-
-#library(microxanox, lib.loc = tmplib)
-
-library(microxanox)
-if (packageVersion("microxanox") < package_version("0.3.0")) {
-  stop("microxanox version needs to be at least 0.3.0!")
-}
-library(tidyverse)
-library(patchwork)
+```{r}
+rm(list = ls())
 library(here)
 source(here("R/various_useful_functions.r"))
-zero <- 0 ## don't change
-unity <- 1 ## don't change!!!
-options(mc.cores = 7)
-eval_dynamics_flag <- FALSE
-plot_ss_results <- FALSE
-```
-
-## Version of `microxanox` package used: `r packageVersion("microxanox") `
-
-## General simulation conditions
-
-```{r}
 
@@
 
-sp <- new_strain_parameter(
-  n_CB = num_CB_strains,
-  n_PB = num_SB_strains,
-  n_SB = num_PB_strains,
-  values_initial_state = "bush_ssfig3"
-)
-
-parameter <- new_runsim_parameter(
-  dynamic_model = bushplus_dynamic_model,
-  event_definition = event_definition_1,
-  event_interval = 100,
-  noise_sigma = 0,
-  minimum_abundances = rep(1, 3),
-  sim_duration = 2000,
-  sim_sample_interval = 100,
-  strain_parameter = sp,
-  log10a_series = c(
-    log10(sp$a_O),
-    log10(sp$a_O)
-  )
-)
-names(parameter$minimum_abundances) <- c("CB", "PB", "SB")
-rm(sp)
-
+source(here("R/setup_experiment.R"))
 ```
 
-## Define diversity
-
-```{r}
-## multiplier of SBPB variation
-CB_var_multiplier <- 2
-SBPB_var_multiplier <- 6
-
-CB_gmax_div <- 0.015789474 * CB_var_multiplier
-CB_h_div <- -0.08 * CB_var_multiplier
-SB_gmax_div <- 0.015789474 * SBPB_var_multiplier
-SB_h_div <- -0.323  * SBPB_var_multiplier
-PB_gmax_div <- 0.015789474  * SBPB_var_multiplier
-PB_h_div <- -0.323  * SBPB_var_multiplier
-
-num_div_treatment_levels <- 20
-
-```
-
-## Create diversity
-
-```{r}
-var_expt <- create_diversity_factorial(
-  zero = zero, unity = unity,
-  num_div_treatment_levels = num_div_treatment_levels,
-  CB_gmax_div = CB_gmax_div, CB_h_div = CB_h_div,
-  SB_gmax_div = SB_gmax_div, SB_h_div = SB_h_div,
-  PB_gmax_div = PB_gmax_div, PB_h_div = PB_h_div,
-  default_9strain = new_strain_parameter(
-    n_CB = num_CB_strains,
-    n_SB = num_SB_strains,
-    n_PB = num_PB_strains,
-    values_initial_state =  "bush_ssfig3"
-  )
-)
-```
+## Version of `microxanox` package used: `r packageVersion("microxanox") `
 
@@
 
-# Temporal switching
+## Test runs
+
+```{r eval = FALSE}
+## Here a test of one run
+no_diverity_varexp_row <- 1
+parameter$strain_parameter <- var_expt$pars[[no_diverity_varexp_row]]
+parameter <- set_temporal_ssfind_initial_state(parameter,
+                                               10^5,
+                                               10^5,
+                                               10^5)
+no_div_res <- run_temporal_ssfind_method(parameter)
+no_div_res
+```
+
+```{r eval = FALSE}
+## here a test of an expt run
+var_expt <- var_expt[1:2,]
+expt_res <- run_temporal_ssfind_experiment(parameter,
+                                           var_expt,
+                                           total_initial_abundances = 10^5)
+```
+
+## Test plotting
 
 ```{r}
-## Here we get some rows of var_expt that correspond with particular diversity levels
-
-var_expt_levels <- var_expt[, 1:6]
-
-no_diversity <- which(rowSums(abs(var_expt_levels)) == 0)
-max_diversty_all <- which(
-  max(rowSums(abs(var_expt_levels))) == rowSums(abs(var_expt_levels))
-)
-max_only_CB_diversity <- which(
-  max(rowSums(abs(var_expt_levels[, 1:2]))) == rowSums(abs(var_expt_levels[, 1:2])) &
-  rowSums(abs(var_expt_levels[,3:6])) == 0
-)
-# var_expt_levels[381,]
-
-max_only_SBPB_diversity <- which(
-  max(rowSums(abs(var_expt_levels[, 3:6]))) == rowSums(abs(var_expt_levels[, 3:6])) &
-  rowSums(abs(var_expt_levels[, 1:2])) == 0
-)
-#var_expt_levels[20,]
-
-medium_diverity_varexp_row <- 311
+## test the plotting functions
+plot_ss_result3(expt_res, 1)
+plot_ss_result3(expt_res, 2)
+plot_ss_result4(expt_res, 1, 2)
 
@@
 
-## Oxic to anoxic
-
-### No diversity
-
-```{r eval = eval_dynamics_flag}
-parameter$sim_duration <- 80000
-```
-
-```{r eval = eval_dynamics_flag}
-parameter$log10a_series <- c(-1, -7, -7)
-parameter$strain_parameter <- var_expt$pars[[no_diversity]]
-parameter$strain_parameter$initial_state <- new_initial_state(
-  num_CB_strains,
-  num_PB_strains,
-  num_SB_strains,
-  values = "bush_ssfig3"
-)
-parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/num_CB_strains
-sim_res_novar1 <- run_simulation(parameter)
-saveRDS(sim_res_novar1, here("experiments/9_strains/data/sim_res_novar1.RDS"))
-```
+## Test get stability
 
 ```{r}
-sim_res_novar1 <- readRDS(here("experiments/9_strains/data/sim_res_novar1.RDS"))
-plot_dynamics(sim_res_novar1)
-#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
-```
+ss_object <- expt_res$ssfind_result[[1]]
 
-### With diversity
+get_stability_measures(expt_res$ssfind_result[[1]])
 
-```{r eval = eval_dynamics_flag}
-parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
-parameter$strain_parameter$initial_state <- sim_res_novar1$strain_parameter$initial_state
-sim_res_highvar1 <- run_simulation(parameter)
-saveRDS(sim_res_highvar1, here("experiments/9_strains/data/sim_res_highvar1.RDS"))
-```
-
-```{r}
-sim_res_highvar1 <- readRDS(here("experiments/9_strains/data/sim_res_highvar1.RDS"))
-plot_dynamics(sim_res_highvar1)
-#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)
+stab_data <-  expt_res %>%
+  mutate(stability_measures = list(get_stability_measures(ssfind_result))) %>%
+  unnest(cols = c(stability_measures))
 
@@
 
-## Anoxic to oxic
+## Test plot stability
 
-### No diversity
-
-```{r eval = eval_dynamics_flag}
-parameter$sim_duration <- 60000
-```
-
-```{r eval = eval_dynamics_flag}
-parameter$log10a_series <- c(-5, -3, -1, -1)
-parameter$strain_parameter <- var_expt$pars[[no_diversity]]
-parameter$strain_parameter$initial_state <- new_initial_state(
-  num_CB_strains,
-  num_PB_strains,
-  num_SB_strains,
-  values = "bush_ssfig3"
-)
-parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10/num_CB_strains
-sim_res_novar2 <- run_simulation(parameter)
-saveRDS(sim_res_novar2, here("experiments/9_strains/data/sim_res_novar2.RDS"))
-```
-
-```{r}
-sim_res_novar2 <- readRDS(here("experiments/9_strains/data/sim_res_novar2.RDS"))
-plot_dynamics(sim_res_novar2)
-#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
-```
-
-### With diversity
-
-```{r eval = eval_dynamics_flag}
-parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
-parameter$strain_parameter$initial_state <- sim_res_novar2$strain_parameter$initial_state
-sim_res_highvar2 <- run_simulation(parameter)
-saveRDS(sim_res_highvar2, here("experiments/9_strains/data/sim_res_highvar2.RDS"))
-```
-
-```{r}
-sim_res_highvar2 <- readRDS(here("experiments/9_strains/data/sim_res_highvar2.RDS"))
-plot_dynamics(sim_res_highvar2)
-#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)
-
-```
-
-## Anoxic to oxic to anoxic
-
-### No diversity
-
-```{r eval = eval_dynamics_flag}
-parameter$sim_duration <- 1000000
-```
-
-```{r eval = eval_dynamics_flag}
-parameter$minimum_abundances <- rep(100, 3)
-names(parameter$minimum_abundances) <- c("CB", "PB", "SB")
-```
-
-```{r eval = eval_dynamics_flag}
-parameter$log10a_series <- c(-1, -8, -1)
-parameter$strain_parameter <- var_expt$pars[[no_diversity]]
-parameter$strain_parameter$initial_state <- new_initial_state(
-  num_CB_strains,
-  num_PB_strains,
-  num_SB_strains,
-  values = "bush_ssfig3"
-)
-parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10/num_CB_strains
-sim_res_novar3 <- run_simulation(parameter)
-saveRDS(sim_res_novar3, here("experiments/9_strains/data/sim_res_novar3.RDS"))
-```
-
-```{r}
-sim_res_novar3 <- readRDS(here("experiments/9_strains/data/sim_res_novar3.RDS"))
-plot_dynamics(sim_res_novar3)
-#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
-```
-
-### With diversity
-
-```{r eval = eval_dynamics_flag}
-parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
-parameter$strain_parameter$initial_state <- sim_res_novar3$strain_parameter$initial_state
-sim_res_highvar3 <- run_simulation(parameter)
-saveRDS(sim_res_highvar3, here("experiments/9_strains/data/sim_res_highvar3.RDS"))
-```
-
-```{r}
-sim_res_highvar3 <- readRDS(here("experiments/9_strains/data/sim_res_highvar3.RDS"))
-plot_dynamics(sim_res_highvar3)
-#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)
-
-```
-
-### Ecosystem-environment relationship
-
-```{r eval = FALSE, echo = FALSE}
-visualise_temporal_env_eco(sim_res_novar3, sim_res_highvar3)
-```
-
-# Stable state finding
-
-## Finding
-
-### Setup parameter
-
-```{r}
-options(mc.cores = 7)
-```
-
-```{r}
-minimum_abundances <- rep(0, 3)
-names(minimum_abundances) <- c("CB", "PB", "SB")
-
-grid_num_a <- 1000 #usually 1000 ## number of a_0 values
-#grid_num_a <- 10 ## FOR TEST
-a_Os <- 10^seq(-7, -0.5, length=grid_num_a) ## sequence of a_0 values
-grid_num_N <- 2 ## number of N values
-initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
-initial_PBs <- 1e8 ## not varied
-initial_SBs <- 1e8 ## not varied
-# next line creates all possible combinations
-ss_expt <- expand.grid(N_CB = initial_CBs,
-                      N_PB = initial_PBs,
-                      N_SB = initial_SBs,
-                      a_O = a_Os)
-
-parameter <- new_ss_by_a_N_parameter(
-  dynamic_model = parameter$dynamic_model,
-  event_definition = parameter$event_definition,
-  event_interval = 1000000,
-  noise_sigma = parameter$noise_sigma,
-  minimum_abundances = minimum_abundances,
-  sim_duration = 1000000,
-  sim_sample_interval = 1000000,
-  log10a_series = parameter$log10a_series,
-  solver_method = parameter$solver_method,
-  ss_expt = ss_expt
-)
-rm(minimum_abundances, grid_num_a, a_Os, grid_num_N, initial_CBs, initial_PBs, initial_SBs, ss_expt)
-
-saveRDS(parameter, here("experiments/9_strains/data/parameter_1e6_x2x6_factorial.RDS"))
-saveRDS(var_expt, here("experiments/9_strains/data/var_expt_1e6_x2x6_factorial.RDS"))
-```
-
-### Run stable state finding
-
-*Careful, this simulation takes about 600 hours on a single core
-
-```{r run_experiment, eval = eval_dynamics_flag}
-run_ss_var_experiment(
-  parameter = readRDS(here("experiments/9_strains/data/parameter_1e6_x2x6_factorial.RDS")), 
-  var_expt = readRDS(here("experiments/9_strains/data/var_expt_1e6_x2x6_factorial.RDS"))) %>%
-saveRDS(here("experiments/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
-```
-
-### Process the stable state data
-
-Bring in various stable state datasets
-```{r eval = eval_dynamics_flag}
-cluster <- multidplyr::new_cluster(7)
-multidplyr::cluster_library(cluster, c("microxanox", "dplyr"))
-
-## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
-readRDS(here("experiments/9_strains/data/ss_data_1e6_x2x6_factorial_small.RDS")) %>%
-  mutate(sim_length = 1000000) %>% 
-  multidplyr::partition(cluster) %>%
-  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
-  collect() %>%
-  unnest(cols = c(stability_measures)) %>%
-  saveRDS(here("experiments/9_strains/data/stab_data_1e6_x2x6_factorial_small.RDS"))
-```
-
-```{r}
-## find various combinations of diversity
-var_expt <- readRDS(here("experiments/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
-stab_data <- readRDS(here("experiments/9_strains/data/stab_data_1e6_x2x6_factorial.RDS"))
-
-var_expt_levels <- var_expt[,1:6]
-
-no_diversity <- which(rowSums(abs(var_expt_levels))==0)
-max_diversty_all <- which(max(rowSums(abs(var_expt_levels))) ==
-                            rowSums(abs(var_expt_levels)))
-max_only_CB_diversity <- which(max(rowSums(abs(var_expt_levels[,1:2]))) ==
-                            rowSums(abs(var_expt_levels[,1:2])) &
-                              rowSums(abs(var_expt_levels[,3:6]))==0)
-#var_expt_levels[381,]
-
-max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
-                            rowSums(abs(var_expt_levels[,3:6])) &
-                              rowSums(abs(var_expt_levels[,1:2]))==0)
-#var_expt_levels[20,]
-
-medium_diverity_varexp_row <- 311
-
-```
-
-### Display results
-
-```{r eval = plot_ss_results}
-
-p1  <- plot_ss_result1(var_expt,
-                result_index = no_diversity,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p1
-
-p2  <- plot_ss_result1(var_expt,
-                result_index = max_diversty_all,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p2
-
-p3  <- plot_ss_result1(var_expt,
-                result_index = max_only_CB_diversity,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p3
-
-p4  <- plot_ss_result1(var_expt,
-                result_index = max_only_SBPB_diversity,
-                filename_prefix = NULL,
-                save_image_file = FALSE)
-p4
-
-p_overlay1 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
-                             var_expt[max_diversty_all,]$ss_res[[1]],
-                             xlims = c(-7, -1))
-p_overlay1
-
-p_overlay2 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
-                             var_expt[max_only_CB_diversity,]$ss_res[[1]],
-                             xlims = c(-7, -1))
-p_overlay2
-
-p_overlay3 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
-                             var_expt[max_only_SBPB_diversity,]$ss_res[[1]],
-                             xlims = c(-7, -1))
-p_overlay3
-
-```
-
-```{r eval = plot_ss_results}
-tempp1 <- var_expt[no_diversity,]$ss_res[[1]] %>%
-  filter(initial_N_CB == 1e10,
-         log10(a_O) > -4.5, log10(a_O) < -4)
-tempp2 <- var_expt[max_only_SBPB_diversity,]$ss_res[[1]] %>%
-  filter(initial_N_CB == 1e10,
-         log10(a_O) > -4.5, log10(a_O) < -4)
-
-ggplot() +
-  geom_line(mapping = aes(x = log10(tempp1$a_O),
-                          y = log10(tempp1$O))) +
-  geom_line(mapping = aes(x = log10(tempp2$a_O),
-                          y = log10(tempp2$O)),
-            col = "blue")
-
-ggplot() +
-  geom_histogram(mapping = aes(x = log10(tempp1$O) - log10(tempp2$O)),
-            col = "blue")
-
-ggplot() +
-  geom_line(mapping = aes(x = log10(tempp1$a_O),
-    y = log10(tempp1$P) - log10(tempp2$P)),
-            col = "blue")
-
-```
+Set up
 
@@
 
-#saveRDS(all_stab_results, here("experiments/experiment summary/all_stab.RDS"))
-
-#all_stab_results <- readRDS(here("experiments/experiment summary/all_stab.RDS"))
 ```
 
-### Raw
+### Log transformed
+
 ```{r eval = plot_ss_results}
+
 all_stab_results %>%
   filter(Species == "O") %>%
-  ggplot(aes(x = var_gmax, y = hyst_range_raw, col=var_treat, shape = as_factor(sim_length))) +
+  ggplot(aes(x = var_gmax, y = hyst_range_log, col=var_treat)) +
   geom_point() +
@@
   #filter(var_treat == "CB") %>%
-  filter(Species == "O",
-         sim_length == 1e6) %>%
-  ggplot(aes(x = var_gmax,
-             ymin = hyst_min_raw,
-             ymax = hyst_max_raw,
-             fill=var_treat)) +
-  geom_ribbon(alpha = 0.5) +
-  facet_wrap( ~ var_treat, nrow = 3) +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
-  labs(fill = "Variation in\nonly these\nfunctional groups") +
-  coord_flip() +
-  theme(
-    strip.background = element_blank(),
-    strip.text.x = element_blank()
-  )
-
-##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
-stab_data %>%
-  filter(Species == "O",
-         sim_length == 1e6) %>%
-  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range_raw, col = hyst_range_raw)) +
-  geom_point(size = 3)
-
-##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
-
-stab_data %>%
-  filter(Species == "O",
-         sim_length == 1e6) %>%
-  ggplot(aes(x = CB_var_gmax_s, y = hyst_range_raw, col = as.factor(SB_var_gmax_s))) +
-  geom_line(size = 2)
-```
-
-### Log transformed
-
-```{r eval = plot_ss_results}
-all_stab_results %>%
   filter(Species == "O") %>%
-  ggplot(aes(x = var_gmax, y = hyst_range_log, col=var_treat, shape = as_factor(sim_length))) +
-  geom_point() +
-  xlab("Amount of trait variation\n[see text for units]") +
-  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
-  labs(col = "Variation in\nonly these\nfunctional groups")
-##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)
-
-all_stab_results %>%
-  #filter(var_treat == "CB") %>%
-  filter(Species == "O",
-         sim_length == 1e6) %>%
   ggplot(aes(x = var_gmax,
@@
 
-##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
-stab_data %>%
-  filter(Species == "O",
-         sim_length == 1e6) %>%
-  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range_log, col = hyst_range_log)) +
-  geom_point(size = 3)
-
-##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
-
-stab_data %>%
-  filter(Species == "O",
-         sim_length == 1e6) %>%
-  ggplot(aes(x = CB_var_gmax_s, y = hyst_range_log, col = as.factor(SB_var_gmax_s))) +
-  geom_line(size = 2)
+# ##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
+# stab_data %>%
+#   filter(Species == "O",
+#          sim_length == 1e6) %>%
+#   ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range_log, col = hyst_range_log)) +
+#   geom_point(size = 3)
+# 
+# 
+# ##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
+# 
+# stab_data %>%
+#   filter(Species == "O",
+#          sim_length == 1e6) %>%
+#   ggplot(aes(x = CB_var_gmax_s, y = hyst_range_log, col = as.factor(SB_var_gmax_s))) +
+#   geom_line(size = 2)
 ```

### 2022-11-25 reports/stable_state_graphs/replication/allssplots_strainvar_0.9.1.Rmd

--- 2022-11-21 reports/stable_state_graphs/temporal/event_definition_2/9strain 1e6 wait_time/allssplots_strainvar_0.9.1.Rmd
@@
 ---
-title: All stable state plots, with strain variation
+title: All stable state plots, with strain variation, replication method of stable state finding
 author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
@@
                             microxanox_version_path, 
-                            "temporal_method",
+                            "replication_method",
                             "event_definition_2",
-                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+                            paste0("ss_data_9strains_sim_length1e+06_event_definition_2.RDS")))
 

### 2022-11-25 reports/stable_state_graphs/temporal/event_definition_1/allssplots_strainvar_0.9.1.Rmd

--- 2022-11-21 reports/stable_state_graphs/temporal/event_definition_2/9strain 1e6 wait_time/allssplots_strainvar_0.9.1.Rmd
@@
 ---
-title: All stable state plots, with strain variation
+title: All stable state plots, with strain variation, event definition 1
 author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
@@
                             "temporal_method",
-                            "event_definition_2",
-                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+                            "event_definition_1",
+                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_1.RDS")))
 

### 2022-11-25 reports/stable_state_graphs/temporal/event_definition_2/2strain 1e6 wait_time/allssplots_strainvar_0.9.1.Rmd

--- 2022-11-21 reports/stable_state_graphs/temporal/event_definition_2/9strain 1e6 wait_time/allssplots_strainvar_0.9.1.Rmd
@@
 ---
-title: All stable state plots, with strain variation
+title: All stable state plots, with strain variation, 2 strain
 author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
@@
                             "event_definition_2",
-                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
+                            paste0("ss_data_2strains_waittime", wait_time, "_event_definition_2.RDS")))
 

### 2022-11-25 reports/stable_state_graphs/temporal/event_definition_2/6strain 1e6 wait_time/allssplots_strainvar_0.9.1.Rmd

--- 2022-11-25 reports/stable_state_graphs/temporal/event_definition_2/2strain 1e6 wait_time/allssplots_strainvar_0.9.1.Rmd
@@
 ---
-title: All stable state plots, with strain variation, 2 strain
+title: All stable state plots, with strain variation, 6 strains
 author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
@@
                             "event_definition_2",
-                            paste0("ss_data_2strains_waittime", wait_time, "_event_definition_2.RDS")))
+                            paste0("ss_data_6strains_waittime", wait_time, "_event_definition_2.RDS")))
 

### 2022-11-25 reports/stable_state_graphs/temporal/event_definition_2/9strain 1e4 wait_time/allssplots_strainvar_0.9.1.Rmd

--- 2022-11-25 reports/stable_state_graphs/temporal/event_definition_2/2strain 1e6 wait_time/allssplots_strainvar_0.9.1.Rmd
@@
 ---
-title: All stable state plots, with strain variation, 2 strain
+title: All stable state plots, with strain variation, 1e4 wait time
 author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
@@
 ```{r}
-wait_time <- "1e+06"
+wait_time <- "1e+04"
 ss_9s <- readRDS(here::here("data",
@@
                             "event_definition_2",
-                            paste0("ss_data_2strains_waittime", wait_time, "_event_definition_2.RDS")))
+                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
 

### 2022-11-25 reports/stable_state_graphs/temporal/event_definition_2/9strain 1e6 wait_time/allssplots_maxtol_0.9.1.Rmd

--- 2022-11-25 reports/stable_state_graphs/temporal/event_definition_2/2strain 1e6 wait_time/allssplots_strainvar_0.9.1.Rmd
@@
 ---
-title: All stable state plots, with strain variation, 2 strain
+title: All stable state plots, with only the maximum tolerance strain
 author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
@@
                             "event_definition_2",
-                            paste0("ss_data_2strains_waittime", wait_time, "_event_definition_2.RDS")))
+                            paste0("ss_data_-1strains_waittime", wait_time, "_event_definition_2.RDS")))
 

### 2022-11-25 index.Rmd
update index
Update Index

@@
 
-[The repository on github.](https://github.com/UZH-PEG/diversity_envresp1)
+[The repository on github, revision1 branch.](https://github.com/UZH-PEG/diversity_envresp1/tree/main)
 
-[The respository on Zenodo with DOI 10.5281/zenodo.6334544.](https://doi.org/10.5281/zenodo.6334544)
+[The respository on Zenodo with DOI 10.5281/zenodo.7360272](https://doi.org/10.5281/zenodo.7360272)
 

### 2023-01-11 index.Rmd
Update index
new version figure 3, new figures in supplement

--- 2022-11-15 index.Rmd
@@
 
-[The repository on github.](https://github.com/UZH-PEG/diversity_envresp1)
+[The repository on github, current version 0.9.1.](https://github.com/UZH-PEG/diversity_envresp1/releases/tag/0.9.1)
 
-[The respository on Zenodo with DOI 10.5281/zenodo.6334544.](https://doi.org/10.5281/zenodo.6334544)
+[The respository on Zenodo with DOI 10.5281/zenodo.7360272
+](https://zenodo.org/record/7360272#.Y4CXmOzMJqs)
 

### 2023-01-11 reports/supplement/supplement_0.9.1.Rmd
new version figure 3, new figures in supplement

@@
 The thick grey vertical lines at -8 and 0 on the x-axis show the extent of the oxygen diffusivity gradient investigated in the simulations.
-Data is missing in panels e, and i, when patterns of coexistence were atypical of the classical pattern shown in Figure 1a of the main text (e.g.
+In panels e, and i, the orange region shows when patterns of coexistence were atypical of the classical pattern shown in Figure 1a of the main text (e.g.
 when cyanobacteria coexisted with sulfur bacteria at low oxygen diffusivities).
@@
 num_strains <- 9
+
 plot_here <- all_stab %>%
-  filter(simlength == sim_length) %>%
-  ## remove data where there are non-standard stable states
-## this subset is identified by inspection of stable state figures
-  filter(!(num_strains == 9 & var_treat == "CB" & stand_var > 1.00),
-         !(num_strains == 9 & var_treat == "SB" & stand_var > 1.00),
-         !(num_strains == 9 & var_treat == "PB" & stand_var > 0.70),
-         !(num_strains == 9 & var_treat == "CB-SB" & stand_var > 1.00),
-         !(num_strains == 9 & var_treat == "CB-PB" & stand_var > 0.65),
-         !(num_strains == 9 & var_treat == "SB-PB" & stand_var > 1.0),
-         !(num_strains == 9 & var_treat == "CB-SB-PB" & stand_var > 1.00))
-
-p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
+  mutate(stab_states_type = "standard",
+         stab_states_type = case_when(
+          (var_treat == "CB" & stand_var > 1.00) ~ "non-standard",
+          (var_treat == "SB" & stand_var > 1.00) ~ "non-standard",
+          (var_treat == "PB" & stand_var > 0.69) ~ "non-standard",
+          (var_treat == "CB-SB" & stand_var > 1.00) ~ "non-standard",
+          (var_treat == "CB-PB" & stand_var > 0.65) ~ "non-standard",
+          (var_treat == "SB-PB" & stand_var > 1.00) ~ "non-standard",
+          (var_treat == "CB-SB-PB" & stand_var > 1.00) ~ "non-standard"
+         ),
+         stab_states_type = ifelse(is.na(stab_states_type), "standard", "non-standard")
+  )
+
+p1 <- fig_div_vs_o2diff_1strain_7row_stable_state_type(plot_here,
                                      which_strain = num_strains,
@@
 The thick grey vertical lines at -8 and 0 on the x-axis show the extent of the oxygen diffusivity gradient investigated in the simulations.
+In panels e, and i, the orange region shows when patterns of coexistence were atypical of the classical pattern shown in Figure 1a of the main text (e.g.
+when cyanobacteria coexisted with sulfur bacteria at low oxygen diffusivities).
 **Right column of panels**: The effect size of trait variation on resilience, with positive values on the y-axis indicating that diversity has increased resilience, i.e.
@@
 num_strains <- 9
+
 plot_here <- all_stab %>%
-  filter(waittime == wait_time) %>%
-  filter(!(num_strains == 9 & var_treat == "CB" & stand_var > 1.00),
-         !(num_strains == 9 & var_treat == "SB" & stand_var > 1.00),
-         !(num_strains == 9 & var_treat == "PB" & stand_var > 0.65),
-         !(num_strains == 9 & var_treat == "CB-SB" & stand_var > 1.00),
-         !(num_strains == 9 & var_treat == "CB-PB" & stand_var > 0.65),
-         !(num_strains == 9 & var_treat == "SB-PB" & stand_var > 1.0),
-         !(num_strains == 9 & var_treat == "CB-SB-PB" & stand_var > 1.00))
-
-p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
+  mutate(stab_states_type = "standard",
+         stab_states_type = case_when(
+          (var_treat == "CB" & stand_var > 1.00) ~ "non-standard",
+          (var_treat == "SB" & stand_var > 1.00) ~ "non-standard",
+          (var_treat == "PB" & stand_var > 0.65) ~ "non-standard",
+          (var_treat == "CB-SB" & stand_var > 1.00) ~ "non-standard",
+          (var_treat == "CB-PB" & stand_var > 0.65) ~ "non-standard",
+          (var_treat == "SB-PB" & stand_var > 1.00) ~ "non-standard",
+          (var_treat == "CB-SB-PB" & stand_var > 1.00) ~ "non-standard"
+         ),
+         stab_states_type = ifelse(is.na(stab_states_type), "standard", "non-standard")
+  )
+
+p1 <- fig_div_vs_o2diff_1strain_7row_stable_state_type(plot_here,
                                      which_strain = num_strains,
-                                     figure_title = paste0(wait_time,
-                                                           " wait time,\n",
+                                     figure_title = paste0(sim_length,
+                                                           " simulation length,\n",
                                                            num_strains,
@@
 num_strains <- 9
+
 plot_here <- all_stab %>%
   filter(waittime == wait_time) %>%
-  filter(!(num_strains == 9 & var_treat == "CB" & stand_var > 1.00),
-         !(num_strains == 9 & var_treat == "SB" & stand_var > 1.00),
-         !(num_strains == 9 & var_treat == "PB" & stand_var > 0.65),
-         !(num_strains == 9 & var_treat == "CB-SB" & stand_var > 1.00),
-         !(num_strains == 9 & var_treat == "CB-PB" & stand_var > 0.65),
-         !(num_strains == 9 & var_treat == "SB-PB" & stand_var > 1.00),
-         !(num_strains == 9 & var_treat == "CB-SB-PB" & stand_var > 1.00))
-p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
+  mutate(stab_states_type = "standard",
+         stab_states_type = case_when(
+          (var_treat == "CB" & stand_var > 1.00) ~ "non-standard",
+          (var_treat == "SB" & stand_var > 1.00) ~ "non-standard",
+          (var_treat == "PB" & stand_var > 0.65) ~ "non-standard",
+          (var_treat == "CB-SB" & stand_var > 1.00) ~ "non-standard",
+          (var_treat == "CB-PB" & stand_var > 0.65) ~ "non-standard",
+          (var_treat == "SB-PB" & stand_var > 1.00) ~ "non-standard",
+          (var_treat == "CB-SB-PB" & stand_var > 1.00) ~ "non-standard"
+         ),
+         stab_states_type = ifelse(is.na(stab_states_type), "standard", "non-standard")
+  )
+
+p1 <- fig_div_vs_o2diff_1strain_7row_stable_state_type(plot_here,
                                      which_strain = num_strains,
-                                     figure_title = paste0(wait_time,
-                                                           " wait time,\n",
+                                     figure_title = paste0(sim_length,
+                                                           " simulation length,\n",
                                                            num_strains,
@@
 p1 + p2
+
 ```
@@
 (ref:div-stab-multstrain1)  Effects of number of strains and of diversity among strains.
+In panels PB and CB-PB the region with dashed lines shows when patterns of coexistence were atypical of the classical pattern shown in Figure 1a of the main text (e.g.
+when cyanobacteria coexisted with sulfur bacteria at low oxygen diffusivities).
 
@@
 plot_here111 <- all_stab %>%
-  filter(!(num_strains == 9 & var_treat == "CB" & stand_var > 1.00),
-         !(num_strains == 9 & var_treat == "SB" & stand_var > 1.00),
-         !(num_strains == 9 & var_treat == "PB" & stand_var > 0.65),
-         !(num_strains == 9 & var_treat == "CB-SB" & stand_var > 1.00),
-         !(num_strains == 9 & var_treat == "CB-PB" & stand_var > 0.65),
-         !(num_strains == 9 & var_treat == "SB-PB" & stand_var > 1.0),
-         !(num_strains == 9 & var_treat == "CB-SB-PB" & stand_var > 1.00),
-
-         !(num_strains == 6 & var_treat == "CB" & stand_var > 1.00),
-         !(num_strains == 6 & var_treat == "SB" & stand_var > 1.00),
-         !(num_strains == 6 & var_treat == "PB" & stand_var > 0.65),
-         !(num_strains == 6 & var_treat == "CB-SB" & stand_var > 1.00),
-         !(num_strains == 6 & var_treat == "CB-PB" & stand_var > 0.65),
-         !(num_strains == 6 & var_treat == "SB-PB" & stand_var > 1.00),
-         !(num_strains == 6 & var_treat == "CB-SB-PB" & stand_var > 1.00),
-
-         !(num_strains == 3 & var_treat == "CB" & stand_var > 1.00),
-         !(num_strains == 3 & var_treat == "SB" & stand_var > 1.00),
-         !(num_strains == 3 & var_treat == "PB" & stand_var > 0.65),
-         !(num_strains == 3 & var_treat == "CB-SB" & stand_var > 1.00),
-         !(num_strains == 3 & var_treat == "CB-PB" & stand_var > 0.65),
-         !(num_strains == 3 & var_treat == "SB-PB" & stand_var > 1.0),
-         !(num_strains == 3 & var_treat == "CB-SB-PB" & stand_var > 1.00),
-
-         !(num_strains == 2 & var_treat == "CB" & stand_var > 1.00),
-         !(num_strains == 2 & var_treat == "SB" & stand_var > 1.00),
-         !(num_strains == 2 & var_treat == "PB" & stand_var > 0.65),
-         !(num_strains == 2 & var_treat == "CB-SB" & stand_var > 1.00),
-         !(num_strains == 2 & var_treat == "CB-PB" & stand_var > 0.65),
-         !(num_strains == 2 & var_treat == "SB-PB" & stand_var > 1.00),
-         !(num_strains == 2 & var_treat == "CB-SB-PB" & stand_var > 1.00))
-
-fig_div_vs_o2diff_multistrain(plot_here111, which_strains,
+  mutate(stab_states_type = "standard",
+         stab_states_type = case_when(
+          (var_treat == "CB" & stand_var > 1.00) ~ "non-standard",
+          (var_treat == "SB" & stand_var > 1.00) ~ "non-standard",
+          (var_treat == "PB" & stand_var > 0.65) ~ "non-standard",
+          (var_treat == "CB-SB" & stand_var > 1.00) ~ "non-standard",
+          (var_treat == "CB-PB" & stand_var > 0.65) ~ "non-standard",
+          (var_treat == "SB-PB" & stand_var > 1.00) ~ "non-standard",
+          (var_treat == "CB-SB-PB" & stand_var > 1.00) ~ "non-standard"
+         ),
+         stab_states_type = ifelse(is.na(stab_states_type), "standard", "non-standard")
+  )
+
+# plot_here111 <- all_stab %>%
+#   filter(!(num_strains == 9 & var_treat == "CB" & stand_var > 1.00),
+#          !(num_strains == 9 & var_treat == "SB" & stand_var > 1.00),
+#          !(num_strains == 9 & var_treat == "PB" & stand_var > 0.65),
+#          !(num_strains == 9 & var_treat == "CB-SB" & stand_var > 1.00),
+#          !(num_strains == 9 & var_treat == "CB-PB" & stand_var > 0.65),
+#          !(num_strains == 9 & var_treat == "SB-PB" & stand_var > 1.0),
+#          !(num_strains == 9 & var_treat == "CB-SB-PB" & stand_var > 1.00),
+#          
+#          !(num_strains == 6 & var_treat == "CB" & stand_var > 1.00),
+#          !(num_strains == 6 & var_treat == "SB" & stand_var > 1.00),
+#          !(num_strains == 6 & var_treat == "PB" & stand_var > 0.65),
+#          !(num_strains == 6 & var_treat == "CB-SB" & stand_var > 1.00),
+#          !(num_strains == 6 & var_treat == "CB-PB" & stand_var > 0.65),
+#          !(num_strains == 6 & var_treat == "SB-PB" & stand_var > 1.00),
+#          !(num_strains == 6 & var_treat == "CB-SB-PB" & stand_var > 1.00),
+#          
+#          !(num_strains == 3 & var_treat == "CB" & stand_var > 1.00),
+#          !(num_strains == 3 & var_treat == "SB" & stand_var > 1.00),
+#          !(num_strains == 3 & var_treat == "PB" & stand_var > 0.65),
+#          !(num_strains == 3 & var_treat == "CB-SB" & stand_var > 1.00),
+#          !(num_strains == 3 & var_treat == "CB-PB" & stand_var > 0.65),
+#          !(num_strains == 3 & var_treat == "SB-PB" & stand_var > 1.0),
+#          !(num_strains == 3 & var_treat == "CB-SB-PB" & stand_var > 1.00),
+#          
+#          !(num_strains == 2 & var_treat == "CB" & stand_var > 1.00),
+#          !(num_strains == 2 & var_treat == "SB" & stand_var > 1.00),
+#          !(num_strains == 2 & var_treat == "PB" & stand_var > 0.65),
+#          !(num_strains == 2 & var_treat == "CB-SB" & stand_var > 1.00),
+#          !(num_strains == 2 & var_treat == "CB-PB" & stand_var > 0.65),
+#          !(num_strains == 2 & var_treat == "SB-PB" & stand_var > 1.00),
+#          !(num_strains == 2 & var_treat == "CB-SB-PB" & stand_var > 1.00))
+
+fig_div_vs_o2diff_multistrain_stable_state_type(plot_here111, which_strains,
                               which_wait_time, figure_title)
@@
 (ref:max-tol1) Effects of strain variation on position of tipping points compared between simulations with all (nine) strains present and simulations where only the most tolerant strain is present.
+When tipping points are shown with dashed lines then patterns of coexistence were atypical of the classical pattern shown in Figure 1a of the main text (e.g.
+when cyanobacteria coexisted with sulfur bacteria at low oxygen diffusivities).
 
@@
 
-## remove data where there are non-standard stable states
-## this subset is identified by inspection of stable state figures
 plot_here11 <- all_stab %>%
-  filter(!(num_strains == 9 & var_treat == "CB" & stand_var > 1.00),
-         !(num_strains == 9 & var_treat == "SB" & stand_var > 1.00),
-         !(num_strains == 9 & var_treat == "PB" & stand_var > 0.65),
-         !(num_strains == 9 & var_treat == "CB-SB" & stand_var > 1.00),
-         !(num_strains == 9 & var_treat == "CB-PB" & stand_var > 0.65),
-         !(num_strains == 9 & var_treat == "SB-PB" & stand_var > 1.0),
-         !(num_strains == 9 & var_treat == "CB-SB-PB" & stand_var > 1.00),
-         !(num_strains == -1 & var_treat == "CB" & stand_var > 1.00),
-         !(num_strains == -1 & var_treat == "SB" & stand_var > 0.60),
-         !(num_strains == -1 & var_treat == "PB" & stand_var > 1.00),
-         !(num_strains == -1 & var_treat == "CB-SB" & stand_var > 0.60),
-         !(num_strains == -1 & var_treat == "CB-PB" & stand_var > 1.00),
-         !(num_strains == -1 & var_treat == "SB-PB" & stand_var > 1.00),
-         !(num_strains == -1 & var_treat == "CB-SB-PB" & stand_var > 1.00))
-
-plot_1 <- fig_div_vs_o2diff_maxtolcomp(plot_here11, which_strains,
+  mutate(stab_states_type = "standard",
+         stab_states_type = case_when(
+          (num_strains == 9 & var_treat == "CB" & stand_var > 1.00) ~ "non-standard",
+          (num_strains == 9 & var_treat == "SB" & stand_var > 1.00) ~ "non-standard",
+          (num_strains == 9 & var_treat == "PB" & stand_var > 0.65) ~ "non-standard",
+          (num_strains == 9 & var_treat == "CB-SB" & stand_var > 1.00) ~ "non-standard",
+          (num_strains == 9 & var_treat == "CB-PB" & stand_var > 0.65) ~ "non-standard",
+          (num_strains == 9 & var_treat == "SB-PB" & stand_var > 1.00) ~ "non-standard",
+          (num_strains == 9 & var_treat == "CB-SB-PB" & stand_var > 1.00) ~ "non-standard",
+
+          (num_strains == -1 & var_treat == "CB" & stand_var > 1.00) ~ "non-standard",
+          (num_strains == -1 & var_treat == "SB" & stand_var > 0.60) ~ "non-standard",
+          (num_strains == -1 & var_treat == "PB" & stand_var > 1.00) ~ "non-standard",
+          (num_strains == -1 & var_treat == "CB-SB" & stand_var > 0.60) ~ "non-standard",
+          (num_strains == -1 & var_treat == "CB-PB" & stand_var > 1.00) ~ "non-standard",
+          (num_strains == -1 & var_treat == "SB-PB" & stand_var > 1.00) ~ "non-standard",
+          (num_strains == -1 & var_treat == "CB-SB-PB" & stand_var > 1.00) ~ "non-standard"
+         ),
+         stab_states_type = ifelse(is.na(stab_states_type), "standard", "non-standard")
+  )
+
+plot_1 <- fig_div_vs_o2diff_maxtolcomp_stable_state_type(plot_here11, which_strains,
                               which_wait_time, figure_title)
@@
   guides(col=guide_legend(title="Which strains are retained", title.position = "top"))
+
 ```

### 2023-01-11 reports/manuscript/figures_main_ms_v1.R

@@ -55,31 +55,84 @@ plot_here <- all_stab %>%
 ## CB all same
 ## SB all same
 
+### Version 1 -- Don't use ----
 ## filtering out some of the data for which there are non-standard ecosystem responses to the oxygen diffusivity.
-plot_here <- plot_here %>%
-  filter(!(var_treat == "CB" & stand_var > 1.00),
-         !(var_treat == "SB" & stand_var > 1.00),
-         !(var_treat == "PB" & stand_var > 0.65),
-         !(var_treat == "CB-SB" & stand_var > 1.00),
-         !(var_treat == "CB-PB" & stand_var > 0.65),
-         !(var_treat == "SB-PB" & stand_var > 1.00),
-         !(var_treat == "CB-SB-PB" & stand_var > 1.00))
+# plot_here_sub <- plot_here %>%
+#   filter(!(var_treat == "CB" & stand_var > 1.00),
+#          !(var_treat == "SB" & stand_var > 1.00),
+#          !(var_treat == "PB" & stand_var > 0.65),
+#          !(var_treat == "CB-SB" & stand_var > 1.00),
+#          !(var_treat == "CB-PB" & stand_var > 0.65),
+#          !(var_treat == "SB-PB" & stand_var > 1.00),
+#          !(var_treat == "CB-SB-PB" & stand_var > 1.00))
+# 
+# p1 <- fig_div_vs_o2diff_1strain_7row(plot_here_sub,
+#                                      which_strain = num_strains,
+#                                      figure_title = NULL
+#                                      # figure_title = paste0(wait_time,
+#                                      #                       " wait time,\n",
+#                                      #                       num_strains,
+#                                      #                       " strains")
+# )
+# p2 <- fig_resilience_vs_div(plot_here,
+#                             which_strain = num_strains,
+#                             figure_title = NULL
+# ) 
+# p1 + p2
+# ggsave(here("reports/manuscript/figure_3.pdf"),
+#        width = 6, height = 9)
 
-p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
+
+### Version 2 -- Use this ----
+## make a different line style for when the stable states are non-standard
+plot_here <- plot_here %>%
+  mutate(stab_states_type = "standard",
+         stab_states_type = case_when(
+          (var_treat == "CB" & stand_var > 1.00) ~ "non-standard",
[…]

### 2023-01-13 reports/supplement/supplement_0.9.1.Rmd
changes to supplement

@@
 $H_{j,X}$ can be thought of as a half-inhibition constant: the concentration of $X$ at which the growth rate of species $j$ is reduced by 50%.
+A higher half-inhibition constant therefore means higher tolerance of species $j$ to substrate $X$.
 
@@
 The following should be read only after the relevant text in the main report.
-We generated variation in maximum growth rate $G_{max}$ and tolerance to reduced sulfur $h_{SR}$ or oxygen $h_{O}$ by varying the range of trait values around a reference trait value.
+We generated variation in maximum growth rate $g_{max}$ and in tolerance to reduced sulfur or oxygen (i.e.
+in the half-inhibition constants $H_{SR}$ or $H_{O}$) by varying the range of trait values around a reference trait value.
 To manipulate the amount of variation in a given trait and functional group, we introduced the meta-parameter $Div$ subscripted by the trait and the functional group.
-Take for example the cyanobacteria functional group, a reference maximum growth rate parameter $G_{max,CB}$ and a reference tolerance parameter $h_{SR,CB}$.
-The amount of among strain variation in the cyanobacteria is controlled by the two meta-parameters $Div_{G_{max,CB}}$ and $Div_{h_{SR,CB}}$.
+Take for example the cyanobacteria functional group, a reference maximum growth rate parameter $g_{max,CB}$ and a reference tolerance parameter $H_{SR,CB}$.
+The amount of among strain variation in the cyanobacteria is controlled by the two meta-parameters $Div_{g_{max,CB}}$ and $Div_{H_{SR,CB}}$.
 To create a trade-off, the two meta-parameters were always of different sign.
-The among strain variation was calculated such that the growth rate of strain $i = 1$ was a factor $1/({2Div_{G_{max,CB}}})$ of the reference growth rate, and the growth rate of the $i = n$ strain was a factor $2Div_{G_{max,CB}}$ of the reference growth rate.
+The among strain variation was calculated such that the growth rate of strain $i = 1$ was a factor $1/({2Div_{g_{max,CB}}})$ of the reference growth rate, and the growth rate of the $i = n$ strain was a factor $2Div_{g_{max,CB}}$ of the reference growth rate.
 The growth rate of the $i = {2,...n-1}$ other strains was the reference growth rate multiplied by a factor that was equally distributed between the factor of the $i = 1$ and $i = n$ strain.
 This implementation of the variation and trade-off has the assumption of a linear trade-off of log-log transformed among-strain variation.
-Hence, for example, with the reference growth rate $G_{max,CB} = 0.05$, among strain variation of $Div_{G_{max,CB}} = 1$, and nine strains ($n = 9$), the growth rates of the nine strains are 0.025, 0.03, 0.035, 0.042, 0.05, 0.059, 0.071, 0.084, 0.1.
-Put another way, the growth rate parameter of the $i$-th of the $n$ strains in a functional group was calculated as $G_{max,i} = D_i * G_{max}$ where $D_i$ is the $i$-th element of the set $D = {2f(x)Div_{G_{max}} |x ∈ N, x ≤ n}$, where $f(x) = (x − (n + 1)/2)/((n − 1)/2)$.
+Hence, for example, with the reference growth rate $g_{max,CB} = 0.05$, among strain variation of $Div_{g_{max,CB}} = 1$, and nine strains ($n = 9$), the growth rates of the nine strains are 0.025, 0.03, 0.035, 0.042, 0.05, 0.059, 0.071, 0.084, 0.1.
+Put another way, the growth rate parameter of the $i$-th of the $n$ strains in a functional group was calculated as $g_{max,i} = D_i * g_{max}$ where $D_i$ is the $i$-th element of the set $D = {2f(x)Div_{g_{max}} |x ∈ N, x ≤ n}$, where $f(x) = (x − (n + 1)/2)/((n − 1)/2)$.
 
@@
 
-All three examples have the following amounts of trait variation: $Div_{G_{max,CB}}$ = `r round(CB_gmax_div, 3)`, $Div_{h_{SR,CB}}$ = `r round(CB_h_div, 3)`, $Div_{G_{max,SB}}$ = `r round(SB_gmax_div, 3)`, $Div_{h_{O,SB}}$ = `r round(SB_h_div, 3)`, $Div_{G_{max,PB}}$ = `r round(PB_gmax_div, 3)`, $Div_{h_{O,PB}}$ = `r round(PB_h_div, 3)`.
+All three examples have the following amounts of trait variation: $Div_{g_{max,CB}}$ = `r round(CB_gmax_div, 3)`, $Div_{H_{SR,CB}}$ = `r round(CB_h_div, 3)`, $Div_{g_{max,SB}}$ = `r round(SB_gmax_div, 3)`, $Div_{H_{O,SB}}$ = `r round(SB_h_div, 3)`, $Div_{g_{max,PB}}$ = `r round(PB_gmax_div, 3)`, $Div_{H_{O,PB}}$ = `r round(PB_h_div, 3)`.
 These are also the maximum amounts of trait variation explored in the simulations.

### 2023-01-17 reports/supplement/supplement_0.9.1.Rmd
changes supplement

@@
 When trait values were medium to high, however, we did find differences between the diversity and tolerance manipulation for most combinations except for diversity/tolerance in only CB and in SB-PB (Figure \@ref(fig:max-tol1)).
+Specifically, the diversity and tolerance manipulation differed either in tipping point positions (CB-SB and CB-SB-PB) or in whether coexistence patterns were atypical (SB, PB, CB-PB, CB-SB).
 We describe and discuss these differences in detail in the sections below.
 Briefly, in these scenarios less tolerant strains did play a role because of their high maximum growth rates.
-Specifically, absence of SB strains with high growth rate led to reduced production of sulfide and therefore to coexistence with cyanobacteria at low oxygen diffusivity.
+For example, absence of SB strains with high growth rate led to reduced production of sulfide and therefore to coexistence with cyanobacteria at low oxygen diffusivity or to increased resilience of the oxic state.
 In contrast, absence of PB strains with high growth rate led to reduced consumption of sulfide and therefore precluded coexistence with cyanobacteria at low oxygen diffusivity (as observed when there was high variation in PB).
@@
 Taken together, at low amounts of trait variation the diversity effects were driven entirely by the most tolerant strain, in line with a sampling effect.
-At medium to high trait variation, however, both tolerant and less tolerant strains affected the results in most combinations.
+At medium to high trait variation, however, both tolerant and less tolerant strains affected the results in many combinations.
 The reason was that in the two groups of sulfur bacteria the trade-off between tolerance and growth rate had ecosystem-level effects, i.e.
@@
 At high levels of diversity / high levels of tolerance, resilience of the oxic state is greater in the tolerance than diversity manipulation.
-We have shown that low tolerance sulfur strains can be implicated in the oxic to anoxic transition (section \@ref(SB2))
+We speculate that this is because the most tolerant SB strain has reduced ability to suppress the cyanobacteria, as we have also observed in the scenarios of tolerance in only SB and in SB-CB (described above).
 

### 2023-01-19 reports/supplement/supplement_0.9.1.Rmd
changes supplement

@@
 
-The rate of change in population densities is given by the per capita growth rate - per capita death rate, multipled by population size ([Bush et al 2017](https://www.nature.com/articles/s41467-017-00912-x)).
+The rate of change in population densities is given by the per capita growth rate - per capita death rate, multiplied by population size ([Bush et al 2017](https://www.nature.com/articles/s41467-017-00912-x)).
 Growth rate is the growth rate in absence of any inhibition multiplied by the amount of inhibition.
@@
 Taken together, at low amounts of trait variation the diversity effects were driven entirely by the most tolerant strain, in line with a sampling effect.
-At medium to high trait variation, however, both tolerant and less tolerant strains affected the results in many combinations.
+At medium to high trait variation, however, in most combinations both tolerant and less tolerant strains contributed to the diversity effects on tipping point positions or coexistence patterns.
 The reason was that in the two groups of sulfur bacteria the trade-off between tolerance and growth rate had ecosystem-level effects, i.e.

### 2023-01-25 reports/supplement/supplement_0.9.1.Rmd
Update supplement_0.9.1.Rmd

@@
 ```
+
+We have confirmed that when there is no within functional group strain variation, the dynamics of the model are not affected by the number of strains in each of the functional groups.
+This is a necessary condition for such a model [Moisset de Espanés et al.
+2021](https://onlinelibrary.wiley.com/doi/10.1111/ele.13775), and gives confidence that our methods and their implementation are correct and robust.
 
@@
 We here analyze temporal dynamics rather than the final state and show that the more tolerant strains do play a role, but only a transient one.
-The following dynamics are for the system starting oxic, and with a value of oxygen diffusivity $log_{10}$(oxygen diffusivity) = -4.8.
+The following dynamics are for oxic starting conditions and with a value of oxygen diffusivity $log_{10}$(oxygen diffusivity) = -4.8.
 When there is no diversity within functional groups (i.e.
 two strains that are identical) the system remains oxic (Figure \@ref(fig:sb-div-effect3)).
-When there is diversity in the two groups of sulfur bacteria (i.e.
-the two strains differ) the system switches to the anoxic state (Figure \@ref(fig:sb-div-effect4)).
-The more tolerant strain of sulfate-reducing bacteria increases in density in the early phase of the simulation, reduces the concentration of oxygen by inhibiting cyanobacteria, and thus generates an environment in which the less tolerant strain is able to grow.
+When there is diversity in the two groups of sulfur bacteria the system switches to the anoxic state (Figure \@ref(fig:sb-div-effect4)).
+(Note that the average trait value [on a log scale] of the two different strains is the same as the trait value of both strains in Figure \@ref(fig:sb-div-effect3).) The more tolerant strain of sulfate-reducing bacteria increases in density in the early phase of the simulation, reduces the concentration of oxygen by inhibiting cyanobacteria, and thus generates an environment in which the less tolerant strain is able to grow.
 Then, the more tolerant strain is outcompeted by the less tolerant strain as the concentration of the inhibiting substrate (oxygen) declines.

### 2023-01-26 reports/supplement/supplement_0.9.1.Rmd
various updates

@@
 print(paste0("Version of microxanox: ", microxanox_version_here))
+
 ```
@@
 
-## Investigating the mechanisms operating in our system
+## Investigating the mechanisms operating
 
@@
          stab_states_type = ifelse(is.na(stab_states_type), "standard", "non-standard")
-  )
+  ) %>%
+  mutate(hyst_min_log = ifelse(var_treat == "CB-SB" &
+                                 stab_states_type == "non-standard" &
+                                 Species == "SB_tot" &
+                                 stand_var > 0.85,
+                               -8,
+                               hyst_min_log
+                                 ))
 
@@
 
+# Log and non-log oxygen diffusivity results
+
+(ref:fig-log-nonlog) The effect of trait diversity (y-axis) viewed with a log axis (left panels) or arithmetic axis for the oxygen diffusivity gradient (x-axis).
+The positions of the tipping points (anoxic to oxic in blue, oxic to anoxic in red) and the extent of the region of bistability (green or orange shaded region) are shown.
+The left-most region is anoxic only, the middle is oxic or anoxic depending on historical conditions, and the right-most is oxic only.
+In the left panels the thick grey vertical lines at -8 and 0 on the x-axis show the extent of the oxygen diffusivity gradient investigated in the simulations.
+In panels e, f, i, and j the orange region shows when patterns of coexistence were atypical of the classical pattern shown in Figure 1a of the main text (e.g.
+when cyanobacteria coexisted with sulfur bacteria at low oxygen diffusivities).
+In the right-hand panels (arithmetic x-axis scale) the blue anoxic to oxic tipping point line often has steps.
+This is becase the simulated oxygen diffusivity levels were evenly distributed on the log-oxygen diffusivity scale, and so are relatively far apart at high oxygen diffusivities on the arithmetic scale.
+
+```{r fig-log-nonlog, echo = FALSE,  include=TRUE, fig.height=8, fig.width=8, fig.align="center", fig.cap='(ref:fig-log-nonlog)'}
+all_stab <- readRDS(here("data",
+                         microxanox_version_path,
+                         "temporal_method",
+                         "event_definition_2",
+                         "processed_data",
+                         "all_stab_data.RDS"))
+
+wait_time <- 1e6
+num_strains <- 9
+plot_here <- all_stab %>%
+  filter(waittime == wait_time)
+
+plot_here <- plot_here %>%
+  mutate(stab_states_type = "standard",
+         stab_states_type = case_when(
+           (var_treat == "CB" & stand_var > 1.00) ~ "non-standard",
+           (var_treat == "SB" & stand_var > 1.00) ~ "non-standard",
+           (var_treat == "PB" & stand_var > 0.65) ~ "non-standard",
+           (var_treat == "CB-SB" & stand_var > 1.00) ~ "non-standard",
+           (var_treat == "CB-PB" & stand_var > 0.65) ~ "non-standard",
+           (var_treat == "SB-PB" & stand_var > 1.00) ~ "non-standard",
+           (var_treat == "CB-SB-PB" & stand_var > 1.00) ~ "non-standard"
+         ),
+         stab_states_type = ifelse(is.na(stab_states_type), "standard", "non-standard")
+  )
+
+p1 <- fig_div_vs_o2diff_1strain_7row_stable_state_type(plot_here,
+                                                       which_strain = num_strains,
+                                                       figure_title = NULL
+                                                       # figure_title = paste0(wait_time,
+                                                       #                       " wait time,\n",
+                                                       #                       num_strains,
+                                                       #                       " strains")
+)
+
+p2 <- fig_div_vs_o2diff_1strain_7row_stable_state_type_nonlog(plot_here,
+                                                       which_strain = num_strains,
+                                                       figure_title = NULL
+                                                       # figure_title = paste0(wait_time,
+                                                       #                       " wait time,\n",
+                                                       #                       num_strains,
+                                                       #                       " strains")
+)
+
+p1 + p2
+
+```
+
 # References

### 2023-01-30 reports/supplement/supplement_0.9.1.Rmd
revised figure 11.1

@@
                                hyst_min_log
+                                 ),
+         hyst_max_log = ifelse(var_treat == "CB-SB" &
+                                 stab_states_type == "non-standard" &
+                                 Species == "SB_tot" &
+                                 stand_var > 0.85,
+                               -8,
+                               hyst_max_log
                                  ))

### 2023-01-30 reports/supplement/supplement_0.9.1.Rmd
changes supplement

@@
 We have confirmed that when there is no within functional group strain variation, the dynamics of the model are not affected by the number of strains in each of the functional groups.
-This is a necessary condition for such a model [Moisset de Espanés et al.
-2021](https://onlinelibrary.wiley.com/doi/10.1111/ele.13775), and gives confidence that our methods and their implementation are correct and robust.
+This is a necessary condition for such a model ([Moisset de Espanés et al.
+2021](https://onlinelibrary.wiley.com/doi/10.1111/ele.13775)), and gives confidence that our methods and their implementation are correct and robust.
 
@@
 
-# Log and non-log oxygen diffusivity results
-
-(ref:fig-log-nonlog) The effect of trait diversity (y-axis) viewed with a log axis (left panels) or arithmetic axis for the oxygen diffusivity gradient (x-axis).
+# Log and non-log oxygen diffusivity
+
+For comparability with the [Bush et al publication 2017](https://www.nature.com/articles/s41467-017-00912-x), we use a log-scale of the oxygen diffusivity gradient when displaying the effect of trait variation on tipping point positions.
+Throughout the text, we do not make comparisons when their outcome would depend on the decision to measure effect sizes on a log-scale of the environmental driver.
+For example, we compare the direction but not the magnitude of the diversity effects of the three functional groups on the resilience of the ecosystem state that they dominate (CB: oxic-anoxic tipping point; SB and PB: anoxic-oxic tipping point).
+On a logarithmic scale, the magnitude of these diversity effects depends on whether a tipping point is located at low or high oxygen diffusivity (Figure 13.1) and therefore on whether a group dominates that oxic or the anoxic state.
+
+(ref:fig-log-nonlog) The effect of trait diversity (y-axis) viewed with a log axis (left panels) or arithmetic axis (right panels) for the oxygen diffusivity gradient (x-axis).
 The positions of the tipping points (anoxic to oxic in blue, oxic to anoxic in red) and the extent of the region of bistability (green or orange shaded region) are shown.
@@
 In the right-hand panels (arithmetic x-axis scale) the blue anoxic to oxic tipping point line often has steps.
-This is becase the simulated oxygen diffusivity levels were evenly distributed on the log-oxygen diffusivity scale, and so are relatively far apart at high oxygen diffusivities on the arithmetic scale.
+This is because the simulated oxygen diffusivity levels were evenly distributed on the log-oxygen diffusivity scale, and so are relatively far apart at high oxygen diffusivities on the arithmetic scale.
 
@@
 
+Moisset de Espanés, P., Ramos-Jiliberto, R. & Soto, J.A. (2021). Avoiding artifacts when varying the number of species in ecological models. Ecol. Lett., 24, 1976–1987.
+
 Steiner, C.F., Long, Z.T., Krumins, J.A. & Morin, P.J. (2006). Population and Community Resilience in Multitrophic Communities. Ecology, 87, 996–1007.

### 2023-01-31 reports/supplement/supplement_0.9.1.Rmd
changes supplement

@@
 Throughout the text, we do not make comparisons when their outcome would depend on the decision to measure effect sizes on a log-scale of the environmental driver.
-For example, we compare the direction but not the magnitude of the diversity effects of the three functional groups on the resilience of the ecosystem state that they dominate (CB: oxic-anoxic tipping point; SB and PB: anoxic-oxic tipping point).
-On a logarithmic scale, the magnitude of these diversity effects depends on whether a tipping point is located at low or high oxygen diffusivity (Figure 13.1) and therefore on whether a group dominates that oxic or the anoxic state.
+For example, we compare the direction but not the magnitude of the diversity effects of the three functional groups on the resilience of the ecosystem state that they dominate (CB: oxic state, i.e.
+oxic-anoxic tipping point; SB and PB: anoxic state, i.e.
+anoxic-oxic tipping point).
+On a logarithmic scale, the magnitude of these diversity effects depends on whether a tipping point is located at low or high oxygen diffusivity (Figure 13.1) and therefore on whether a group dominates the oxic or the anoxic state.
 

### 2023-01-31 reports/supplement/supplement_0.9.1.Rmd
update supplement

@@
 For comparability with the [Bush et al publication 2017](https://www.nature.com/articles/s41467-017-00912-x), we use a log-scale of the oxygen diffusivity gradient when displaying the effect of trait variation on tipping point positions.
-Throughout the text, we do not make comparisons when their outcome would depend on the decision to measure effect sizes on a log-scale of the environmental driver.
+Throughout the text, we do not make comparisons when their outcome would depend on our decision to quantify diversity effects on a log-scale of oxygen diffusivity.
 For example, we compare the direction but not the magnitude of the diversity effects of the three functional groups on the resilience of the ecosystem state that they dominate (CB: oxic state, i.e.

### 2023-01-31 reports/supplement/supplement_0.9.1.Rmd
changes supplement

@@
 For comparability with the [Bush et al publication 2017](https://www.nature.com/articles/s41467-017-00912-x), we use a log-scale of the oxygen diffusivity gradient when displaying the effect of trait variation on tipping point positions.
-Throughout the text, we do not make comparisons when their outcome would depend on our decision to quantify diversity effects on a log-scale of oxygen diffusivity.
+Throughout the text, we do not make comparisons when their outcome would depend on this decision to quantify diversity effects on a log-scale of oxygen diffusivity.
 For example, we compare the direction but not the magnitude of the diversity effects of the three functional groups on the resilience of the ecosystem state that they dominate (CB: oxic state, i.e.

### 2023-01-31 reports/supplement/supplement_0.9.1.Rmd
revise some text

--- 2023-01-31 reports/supplement/supplement_0.9.1.Rmd
@@
 For comparability with the [Bush et al publication 2017](https://www.nature.com/articles/s41467-017-00912-x), we use a log-scale of the oxygen diffusivity gradient when displaying the effect of trait variation on tipping point positions.
-Throughout the text, we do not make comparisons when their outcome would depend on our decision to quantify diversity effects on a log-scale of oxygen diffusivity.
-For example, we compare the direction but not the magnitude of the diversity effects of the three functional groups on the resilience of the ecosystem state that they dominate (CB: oxic state, i.e.
+In our work, we only make comparisions where the outcome is the same when a log- or and arithmetic-scale of oxygen diffusivity was used.
+For example, compare the direction of the diversity effects of the three functional groups on the resilience of the ecosystem state that they dominate (CB: oxic state, i.e.
 oxic-anoxic tipping point; SB and PB: anoxic state, i.e.
 anoxic-oxic tipping point).
-On a logarithmic scale, the magnitude of these diversity effects depends on whether a tipping point is located at low or high oxygen diffusivity (Figure 13.1) and therefore on whether a group dominates the oxic or the anoxic state.
+The direction of the effects does not depend on the log/arithmetic scale decision.
+
+In contrast, we avoid comparisons where the outcome would differ when a log- or and arithmetic-scale of oxygen diffusivity was used.
+An example of a comparison that we avoid is of the magnitude of the diversity effect between the oxic-anoxic transition and the anoxic-anoxic transition.
+We avoid this comparison of magnitudes because with a log scale the diversity effect is larger for the oxic-anoxic transition (Figure \@ref(fig:fig-log-nonlog)n), while on an arithmetic scale the diversity effect is larger for the anoxic-oxic transition (Figure \@ref(fig:fig-log-nonlog)o).
 

### 2023-01-31 reports/supplement/supplement_0.9.1.Rmd
update supplement

@@
 
-For comparability with the [Bush et al publication 2017](https://www.nature.com/articles/s41467-017-00912-x), we use a log-scale of the oxygen diffusivity gradient when displaying the effect of trait variation on tipping point positions.
-In our work, we only make comparisions where the outcome is the same when a log- or and arithmetic-scale of oxygen diffusivity was used.
-For example, compare the direction of the diversity effects of the three functional groups on the resilience of the ecosystem state that they dominate (CB: oxic state, i.e.
+For comparability with the [Bush et al publication (2017)](https://www.nature.com/articles/s41467-017-00912-x), we use a log-scale of the oxygen diffusivity gradient when displaying the effect of trait variation on tipping point positions.
+In our work, we only make comparisons where the outcome is the same when a log- or an arithmetic-scale of oxygen diffusivity was used.
+For example, we compare the direction of the diversity effects of the three functional groups on the resilience of the ecosystem state that they dominate (CB: oxic state, i.e.
 oxic-anoxic tipping point; SB and PB: anoxic state, i.e.
@@
 
-In contrast, we avoid comparisons where the outcome would differ when a log- or and arithmetic-scale of oxygen diffusivity was used.
-An example of a comparison that we avoid is of the magnitude of the diversity effect between the oxic-anoxic transition and the anoxic-anoxic transition.
+In contrast, we avoid comparisons where the outcome would differ when a log- or an arithmetic-scale of oxygen diffusivity was used.
+An example of a comparison that we avoid is of the magnitude of the diversity effect between the oxic-anoxic transition and the anoxic-oxic transition.
 We avoid this comparison of magnitudes because with a log scale the diversity effect is larger for the oxic-anoxic transition (Figure \@ref(fig:fig-log-nonlog)n), while on an arithmetic scale the diversity effect is larger for the anoxic-oxic transition (Figure \@ref(fig:fig-log-nonlog)o).

### 2023-02-01 index.Rmd
Update links in index.Rmd

--- 2022-11-15 index.Rmd
@@
 
-[The repository on github.](https://github.com/UZH-PEG/diversity_envresp1)
+[The repository on github, current version 0.9.2.](https://github.com/UZH-PEG/diversity_envresp1/releases/tag/v0.9.2)
 
-[The respository on Zenodo with DOI 10.5281/zenodo.6334544.](https://doi.org/10.5281/zenodo.6334544)
+[The respository on Zenodo with the versioned DOI 10.5281/zenodo.7594024
+](https://zenodo.org/record/7594024#.Y9pZaC8w0Q8)
 

### 2023-04-18 index.Rmd
v1.0.0: Paper Publication Release
Update Index files with link to the version 1.0.0

--- 2022-11-25 index.Rmd
@@
 
-[The repository on github, revision1 branch.](https://github.com/UZH-PEG/diversity_envresp1/tree/main)
+[The repository on github, current version 1.0.0.](https://github.com/UZH-PEG/diversity_envresp1/releases/tag/v1.0.0)
 
-[The respository on Zenodo with DOI 10.5281/zenodo.7360272](https://doi.org/10.5281/zenodo.7360272)
+[The respository on Zenodo with the versioned DOI 10.5281/zenodo.7744094
+](https://zenodo.org/record/7744094) - UPDATED
 
